### 2022-02-05 Codes/PrepareResults.Rmd
initial submission

---
title: "Machine Learning Methods for Site-specific Input Management"
author: Shunkei Kakimto
output: word_document
---

```{r}
library(knitr)
# library(here)

knitr::opts_chunk$set(
    cache = FALSE,
    warning = FALSE,
    message = FALSE
    )

# opts_knit$set(root.dir=here())
opts_knit$set(root.dir = "~/Dropbox/ResearchProject/ML_VRA")
```

```{r, cache = FALSE}
# === packages ===#
library(sf)
library(data.table)
library(RColorBrewer)
library(patchwork)
library(grf)
library(magrittr)
library(ggplot2)
library(ggthemes)
library(viridis)
library(tidyverse)
library(ggpubr)
library(flextable)
library(officer)
library(officedown)
library(modelsummary)
library(here)
library(gridExtra)
library(DiagrammeR)
library(latex2exp)
```

# Load the data

```{r source, results = "hide", fig.show='hide', cache = FALSE }
# setwd(here())
source("./GitControlled/Codes/0_0_functions.R")
# source("./GitControlled/Codes/functions_stepwise_vs_base.R")
```

```{r setup, warning=FALSE, message=FALSE, cache= TRUE}
pCorn <- price_table[2, pCorn]
pN <- price_table[2, pN]

sp_range <- 400

field <- readRDS("./Shared/Data/for_Simulations/field_padding.rds") %>%
    filter(padding==1)%>%
    dplyr::select(unique_cell_id)

####==== (1) cell-level dataset ====####
# coef_data <- readRDS("./Shared/Data/for_Simulations/cnn_coefficients_sprange_400.rds")

# x=1
# coef_data_m <- coef_data[sim == x, ]
# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]

# sample_dt <- prepare_raw_data(1, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no")

# sample_training_cell <- sample_dt$reg_raw_data

# saveRDS(sample_training_cell, "./Shared/Data/for_writing/sample_reg_raw_data.rds")

field_cell_dt <- readRDS("./Shared/Data/for_writing/sample_reg_raw_data.rds")%>%
    .[,plot_id := ceiling(subplot_id/4)]%>%
    .[padding==1,]

field_cell_sf <- left_join(field, field_cell_dt, by="unique_cell_id")%>%
    na.omit()

# ggplot(field_cell_sf)+
#     geom_sf(aes(fill=factor(padding)), size=0)

##== area of the field ==##
# st_area(st_union(field_cell_sf%>%filter(padding==1)))

# nrow(field_cell_sf)

####==== (2) plot-level dataset without padding area ====####

field_plot_sf <- field_cell_sf%>%
    group_by(plot_id, strip_id, rate)%>%
    summarise()

# nrow(field_plot_sf)
# ggplot(field_plot_sf)+geom_sf()

####==== (3) subplot-level field without padding area ====####

# field_subplot_dt <- field_cell_dt[, .(
#     sim = mean(sim),
#     yield = mean(yield),
#     opt_N = mean(opt_N),
#     rate = mean(rate),
#     aa_n = mean(aa_n), 
#     alpha = mean(alpha),
#     beta = mean(beta),
#     ymax = mean(ymax),
#     alpha1 = mean(alpha1),
#     alpha2 = mean(alpha2),
#     beta1 = mean(beta1),
#     beta2 = mean(beta2),
#     ymax1 = mean(ymax1),
#     ymax2 = mean(ymax2),
#     theta_1 = mean(theta_1),
#     theta_2 = mean(theta_2)
#   ), by = .(subplot_id, strip_id)]%>%
#   .[,unique_subplot_id:=paste0(strip_id,"_",subplot_id)]%>%
#   .[, `:=`(
#     strip_id = NULL,
#     subplot_id = NULL
#   )]

# saveRDS(field_subplot_dt, here("Shared", "Data", "for_writing", "sample_field_subplot_dt.rds"))

field_subplot_dt <- readRDS("Shared/Data/for_writing/sample_field_subplot_dt.rds")

field_subplot_sf <- field_cell_sf%>%
    group_by(subplot_id, strip_id)%>%
    summarise()%>%
    mutate(unique_subplot_id=paste0(strip_id,"_",subplot_id))%>%
    dplyr::select(unique_subplot_id)%>%
    left_join(., field_subplot_dt, by="unique_subplot_id")

# nrow(field_subplot_sf)
# ggplot(field_subplot_sf)+geom_sf()

```

# Sample CT figure

```{r}

# library(causalTree)
# library(here)
# library(rpart)
# library(rattle)

# ===================================
# Get tree 
# ===================================

# data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
#     na.omit() %>%
#     dplyr::rename(tgtn=NPlan,tgts=SRPlan)

# data_dt <- data.table(data_sf) %>%
#     setnames(names(.),tolower(names(.)))

# tgts_ls <- data_dt[,tgts] %>% unique() %>% sort

# ctree_data <- copy(data_dt) %>%
#   .[tgts %in% tgts_ls[1:2],] %>%
#   .[,treat:=ifelse(tgts==tgts_ls[2],1,0)] %>%
#   #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
#   .[,yield:= yield*62.77]

# tree <- causalTree(
#   yield ~ slope+ecs,
#   data = ctree_data,
#   treatment = ctree_data$treat,
#   split.Rule = "CT",
#   cv.option = "CT",
#   split.Honest = T,
#   cv.Honest = T,
#   split.Bucket = F,
#   xval = 5,
#   cp = 0,
#   minsize = 20,
#   propensity = 0.5
# )

# opcp <- tree$cptable[,1][which.min(tree$cptable[,4])]
# opfit <- prune(tree, opcp)

# pdf(here("GitControlled/Writing/JournalSubmission/ctree_ex.pdf"))
# fancyRpartPlot(opfit,sub='')
# dev.off()

```

```{r}
variogram_tb <- data.frame(
    Parameters = c("ymax_ij", "alpha_ij", "beta_ij", "varepsilon_ij"),
    Range = c(400, 400, 400, 400),
    Mean = c(12000, -0.5, format(c(0,0))),
    Nugget = format(c(0, 0, 0, 0)),
    Sill =c(2000000, 0.02, format(1, nsmall = 1), 0.015)
    ) %>%
    flextable() %>%
    compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sup(as_i("i,j")))) %>%
    compose(i = 2, j = 1, part = "body", value = as_paragraph(as_i("\U03B1"), as_sup(as_i("i,j")))) %>%
    compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("\U03B2"), as_sup(as_i("i,j")))) %>%
    compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sup(as_i("i,j")))) %>%
    compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
    compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("6"))) %>%
    compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
    compose(i = 2, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
    compose(i = 4, j = 5, part = "body", value = as_paragraph("1.5", "\U2A2F", "10", as_sup("-2"))) %>%
    align(align = "center", part = "all")%>%
    align(j=1,  align = "left", part = "all")%>%
    # --- change headers labels--- #
    set_header_labels(values = list(
        Parameters = "Parameters",
        Range = "Range (m)",
        Mean = "Mean",
        Nugget = "Nugget",
        Sill = "Sill"
    ))%>%
    #- change the borders just for consistency with other tables -#
    hline_bottom(part="all") %>%
    hline_top(part="header") %>%
    footnote(
    value = as_paragraph("NOTE: About ymax, the units of of Mean, Nugget, and Sill are kg."),
     ref_symbols = NA
    ) %>%
    autofit()
```

# sample MB curve

```{r, dependson = "setup"}
# gen_yield_MB <- function(ymax, alpha, beta, N) {
#   yield <- ymax * (1 - exp(alpha + beta * N))
#   return(yield)
# }

N_rates <- field_cell_dt[,rate]%>%unique()%>%sort()

N_seq <- 0:300

        # alpha        beta     ymax
# 1: -0.6605052 -0.01572583 10886.94

dt_sample_MB_curve <- field_cell_dt[1,.(alpha,beta,ymax)]%>%
    .[rep(1:nrow(.), each = length(N_seq)), ]%>%
    .[,N:= N_seq]%>%
    .[,Yield := gen_yield_MB(ymax, alpha, beta, N)]

sample_MB_curve <- ggplot()+
    geom_point(data=dt_sample_MB_curve, 
        aes(x=N, y=Yield))+
    theme_few()+
    xlab("N(kg/ha)") + ylab("Yield(kg/ha)")

```

# Field Maps

## Division of field: plots, subplots and cells (Visualization)

```{r field-map-visualization, dependson = "setup"}

##== plot-level field without padding area ==##
# vis_field_plot <- ggplot(field_plot_sf) +
#     geom_sf(fill=NA) +
#     theme_void() +
#     labs(caption="Bottom Title") + 
#     theme(plot.title = element_text(hjust = 0.5))

####==== Example map of plot and subplots and cells ====####
##== Preparation ==##
# ex_plot <- field_plot_sf[224,]
# ex_subplots <- field_subplot_sf[ex_plot, , op = st_within]

# ex_one_subplot <- ex_subplots[1,]
# ex_cells <- field_cell_sf[ex_one_subplot, ,op=st_within]

# #-- (1) plot-level field map (base: vis_field_withoutPadding) --#
# library(latex2exp)

# plot <- 
#     ggplot()+
#         geom_sf(data=field_plot_sf)+
#         geom_sf(data=ex_plot, fill="green", size = 1)+
#         # coord_sf(expand = F) +
#         theme_void() +
#         ggtitle(TeX("$12 \\times 32$ plots")) +
#         theme(plot.title = element_text(hjust = 0.5))

# grob_plot <- ggplotGrob(plot)

# # #-- (2) create a map of subplots in a plot --##
# subplots_inPlot <- ggplot()+
#     geom_sf(data=ex_plot, fill="green")+
#     geom_sf(data = ex_subplots, fill = NA, size = 1)+
#     theme_void() +
#     ggtitle(TeX("$4 \\times 1$ subplots")) +
#     theme(plot.title = element_text(hjust = 0.5))

# grob_subplots_inPlot <- ggplotGrob(subplots_inPlot)

# # #-- (3) create a map of cells in a subplot --#
# cells_inSubplot <- 
#     ggplot()+
#     geom_sf(data=ex_one_subplot, fill="green", size = 1)+
#     geom_sf(data=ex_cells, fill=NA)+
#     theme_void() +
#     ggtitle(TeX("$6 \\times 6$ cells")) +
#     theme(
#         plot.title = element_text(hjust = 0.5, margin=margin(0,0,10,0)))

# grob_cells_inSubplot <- ggplotGrob(cells_inSubplot)

# # #-- (4)put them on the same map --#
# g_inset <- ggplot() +
#   coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)

# map_all_together <- 
#     #/*----------------------------------*/
#     #' ##  base maps 
#     #/*----------------------------------*/
#     g_inset +
#     # --- plot level --- #
#     annotation_custom(grob_plot, 
#         xmin = 0, xmax = 0.4, ymin = 0, ymax = 1) +
#     # --- subplot level --- # 
#     annotation_custom(grob_subplots_inPlot, 
#         xmin = 0.57, xmax = 0.67, ymin = 0.3, ymax = 0.8) + #hight is 5
#     # --- cell level --- # 
#     annotation_custom(grob_cells_inSubplot, 
#         xmin = 0.8, xmax = 1, ymin = 0.5, ymax = 0.7) +
#         # xmin = 0.75, xmax = 1, ymin = 0.45, ymax = 0.7) +
#     #/*----------------------------------*/
#     #' ## add line segments
#     #/*----------------------------------*/
#     # --- plot-subplot (above) --- #
#     # geom_segment(aes(x = 0.386,  xend = 0.55, y = 0.547, yend = 0.73), 
#     geom_segment(aes(x = 0.387, xend = 0.57, y = 0.534, yend = 0.717), 
#          lineend = "round", color = "grey",
#         size = 1.5
#         ) +
#     # --- plot-subplot (below) --- #
#     # geom_segment(aes(x = 0.386, xend = 0.55, y = 0.5, yend = 0.37), 
#     geom_segment(aes(x = 0.387, xend = 0.57, y = 0.485, yend = 0.352), 
#         # data = arrowA, 
#          lineend = "round", color = "grey", 
#         size = 1.5
#         )+
#     # --- subplot-cell (above) --- #
#     # geom_segment(aes(x = 0.65, xend = 0.805, y = 0.64, yend = 0.692), 
#     geom_segment(aes(x = 0.671, xend = 0.82, y = 0.626, yend = 0.661), 
#         # data = arrowA, 
#          lineend = "round", color = "grey",
#         size = 1.5
#         ) +
#     # --- subplot-cell (below) --- #
#     geom_segment(aes(x = 0.671, xend = 0.82, y = 0.532, yend = 0.506), 
#         # data = arrowA, 
#          lineend = "round", color = "grey",
#         size = 1.5
#         ) + 
#     theme_void()

# #     theme(plot.margin=unit(c(0,0,0,0),"mm"))

# file <- here("GitControlled/Writing/Re_JournalSubmission/field_devision_v2.pdf")
# ggsave(file)
# knitr::plot_crop(file)
# dev.off()
```

# Distribution Map of Field Characteristics

## Experimental N design

```{r, dependson = "setup"}

field_Ndesign <- ggplot() +
    # geom_sf(data=field_plot_sf, color='blue', size=0.8, fill=NA) +
    geom_sf(data=field_plot_sf,
        aes(fill = factor(rate)), size = 0,
        inherit.aes = FALSE,
        # alpha=0.9
        ) +
    scale_fill_viridis_d() +
    labs(fill = "Nitrogen rate\n  (kg/ha)") +
    theme_void()
    # theme(legend.position = "bottom",
    #     legend.title = element_text(size = 0.9))

```

## Yield map

```{r, dependson = "setup"}

# yield_dist <- ggplot(field_cell_dt)+
#     geom_density(aes(x=yield))

##== cell level ==##
vis_yield_cell <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = yield), size = 0) +
    scale_fill_viridis_c()+
    labs(fill = "Yield Level\n  (kg/ha)")+
    theme_void()

##== subplot yield level ==##
vis_yield_subplot <- ggplot(field_subplot_sf) +
    geom_sf(aes(fill = yield), size = 0) +
    scale_fill_viridis_c()+
    labs(fill = "Yield Level\n  (kg/ha)")+
    theme_void()

```

## opt_N map

```{r, dependson = "setup"}
opt_N_dist <- ggplot(field_cell_dt)+
    geom_density(aes(x=opt_N))

##== cell level ==##
vis_optN_cell <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = opt_N), size = 0) +
    scale_fill_viridis_c()+
    labs(fill = "EONR (kg/ha)")+
    theme_void()

##== subplot yield level ==##
vis_optN_subplot <- ggplot(field_subplot_sf) +
    geom_sf(aes(fill = opt_N), size = 0) +
    scale_fill_viridis_c()+
    labs(fill = "Yield Level\n  (kg/ha)")+
    theme_void()
```

## Field Characteristics Map

```{r, dependson = "setup"}
####==== ymax map ====####
ymax_dist <- ggplot(field_cell_dt)+
    geom_density(aes(x=ymax))

field_ymax <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = ymax), size = 0) +
    scale_fill_viridis_c()+
    ggtitle('(1) ymax')+
    labs(fill = "kg/ha")+
    theme_void()
    # theme(legend.title = element_blank())

####==== alpha map ====####
alpha_dist <- ggplot(field_cell_dt)+
    geom_density(aes(x=alpha))

field_alpha <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = alpha), size = 0) +
    scale_fill_viridis_c() +
    ggtitle(expression("(2) " ~alpha)) +
    theme_void() +
    theme(legend.title = element_blank())

####==== beta map ====####
beta_dist <- ggplot(field_cell_dt)+
    geom_density(aes(x=beta))

field_beta <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = beta), size = 0) +
    scale_fill_viridis_c()+
    ggtitle(expression("(3) " ~beta)) +
    # labs(fill = expression(~beta))+
    theme_void() +
    theme(legend.title = element_blank())

####==== m_error map ====#### (this should be m_error*det_yield, not just m_error)
# m_error_sf <-  left_join(field, coef_data_m, by="unique_cell_id")

field_m_error <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = yield_error), size = 0) +
    scale_fill_viridis_c()+
    ggtitle(expression("(d) " ~epsilon)) +
    labs(fill = "kg/ha")+
    theme_void()
    # theme(legend.title = element_blank())

# grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2, nrow=2)
```

# Results

## Source Results and Preparation

```{r source-results, message=FALSE, warning=FALSE, cache= TRUE}

# ===================================
# Forest results 
# ===================================

res_forest_all_honest <- readRDS("./Shared/Results/Summary_SimRes_Honest_full_tune.rds")

# ===================================
# CNN results 
# ===================================

res_CNN_all <- readRDS("./Shared/Results/SimRes_CNN_RMSE.rds")

# /*-------------------------------------------------------*/
#' ## Organize the data
# /*-------------------------------------------------------*/ 
#--- for reporting the results of  yield prediction and EONR estimation ---#
report_res_allML <- rbind(res_forest_all_honest, res_CNN_all)%>%
    .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF_stepwise", "CF_base"))] %>%
    .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]

report_res_subsetML <- report_res_allML %>%
    .[Method != "CF_stepwise", ]

```

# Yield prediction results

## Report R^2 of of Predicted Yield (RF, BRF, CNN)

```{r, dependson = "source-results"}

rmse_y_all <-  copy(report_res_allML)%>%
    .[Method %in% c("RF", "BRF", "CNN")]

#==== Distribution of RMSE of predicted yields ====#
plot_dis_y <- copy(rmse_y_all)%>%
    .[, Method:=factor(Method, levels = c("RF", "BRF", "CNN"))]%>%
    ggplot()+
    geom_density(aes(x=rmse_y, fill=Method), alpha=0.6)+
    facet_wrap(~Model, ncol = 1)+
    labs(x = "RMSE")+
    # labs(x = "Mean R-squared")+
    theme_few()+
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        legend.title = element_text(size=12,face="bold"),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")

#==== Summary Table ====#
table_y_prep <- copy(rmse_y_all) %>%
    .[,.(rmse_y = mean(rmse_y)), by=.(Method, Model)] %>%
    .[,rmse_y := format(round(rmse_y,1), nsmall=1)] %>%
    dcast(Model~Method, value.var = "rmse_y")

report_table_y <- copy(table_y_prep)%>%
    .[, CF_base := "-"]%>%
    mutate(
    across(
      everything(),
      as.character
        )
    )%>%
    flextable(.) %>%
    set_header_labels(values = list(
        Model = "Model",
        RF = "RF",
        BRF = "BRF",
        CNN = "CNN",
        CF_base = "CF-base"
    ))%>%
    align(align = "center", part = "all")%>%
    align(j=1,  align = "left", part = "all")%>%
    #- change the borders just for consistency with other figures -#
    hline_bottom(part="all") %>%
    hline_top(part="header") %>%
    autofit()
```

# Figure (RMSE of EONR vs RMSE of yield for RF abd BRF)

```{r}
# rmse_y_all_v2 <- rmse_y_all %>%
#     .[,`:=`(
#         rmse_y_scale = scales::rescale(rmse_y),
#         rmse_optN_scale = scales::rescale(rmse_optN)
#         ), by= .(Model, Method)]

fig_y_optN <- rmse_y_all[Method %in% c("RF", "BRF", "CNN")] %>%
    ggplot(aes(x=rmse_y, y=rmse_optN))+
    geom_point(size=0.5)+
    facet_grid(Model ~ Method) +
    # geom_smooth(method='lm', se=FALSE,  aes(colour="Regression line"), size=1) +
    # scale_colour_manual(values= "red") +
    geom_smooth(method='lm', se=FALSE,  color = "red", size=1) +
    stat_regline_equation(
        # label.x.npc = "right",
        # label.y.npc = "top", 
        label.x = 2150, label.y = 85,
        aes(label = ..rr.label..)) +
    # geom_abline(slope=1, intercept=0, color="red")+
    guides(
        fill = guide_legend(keywidth = 1, keyheight = 1),
        linetype = guide_legend(keywidth = 3, keyheight = 1),
        colour= guide_legend(keywidth = 3, keyheight = 1))+
    labs(y = " RMSE of EONR Estimation (kg/ha)")+
    labs(x = " RMSE of Yield Prediction (kg/ha)")+
    theme_few() +
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        strip.text.y = element_text(size=12,face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")

# print(fig_y_optN, preview = "docx")
# dfabline <- data.frame(
#     x = 0:3500, y=0:3500)

# figure_te <- readRDS(here("Shared/Data/for_writing/dt_TEcomparison.rds"))%>%
#     .[, Method:= case_when(
#         Method=="RF" ~ "RF",
#         Method=="BRF" ~ "BRF",
#         Method=="CF_base" ~ "CF-base")] %>%
#     .[, Method:= factor(Method, levels = c("RF", "BRF", "CF-base"))]%>%
#     ggplot() +
#     geom_point(aes(x=true_tau_base, y=tau_base), size=0.5)+
#     # geom_abline(aes(intercept = 0, slope = 1, color = "1-to-1 line"), show.legend=TRUE) +
#     geom_line(data=dfabline, aes(x=x, y=y, color="1-to-1 line")) +
#     scale_colour_manual(labels = "1-to-1 line", values="red") +
#     facet_grid(Treatment ~ Method) +
#     guides(
#         fill = guide_legend(keywidth = 1, keyheight = 1),
#         linetype = guide_legend(keywidth = 3, keyheight = 1),
#         colour= guide_legend(keywidth = 3, keyheight = 1),
#         direction = "horizontal")+
#     labs(y = "Estimated Treatment Effect")+
#     labs(x = "True Treatment Effect")+
#     theme_few() +
#     theme(
#         strip.text.x = element_text(size=12,face="bold"),
#         strip.text.y = element_text(size=12,face="bold"),
#         legend.title = element_blank(),
#         legend.text = element_text(size=12, face="bold"),
#         legend.position = "bottom")

```

## Yield Prediction vs EONR estimation : Count Table in terms of profit loss

```{r, dependson = "source-results"}

prepare_count_tab <- rmse_y_all %>%
    dcast(sim + Model ~ Method, value.var = c("Mean", "rmse_y"))%>%
    .[,which_ML_y := case_when(
        rmse_y_BRF < rmse_y_RF & rmse_y_BRF < rmse_y_CNN ~ "BRF",
        rmse_y_RF < rmse_y_BRF & rmse_y_RF < rmse_y_CNN ~ "RF",
        rmse_y_CNN < rmse_y_BRF & rmse_y_CNN < rmse_y_RF ~ "CNN"
        )]%>%
    .[,which_ML_piLoss := case_when(
        Mean_BRF < Mean_RF & Mean_BRF < Mean_CNN ~ "BRF", 
        Mean_RF < Mean_BRF &  Mean_RF < Mean_CNN ~ "RF", 
        Mean_CNN < Mean_BRF & Mean_CNN < Mean_RF ~ "CNN"
        )] %>%
    .[,index_cnst_y_piLoss := ifelse(which_ML_piLoss==which_ML_y, 1, 0)]%>%
    .[,ML_cnst_y_piLoss:= ifelse(index_cnst_y_piLoss==1, which_ML_piLoss, NA)]

    # # RF vs BRF
    # .[,rmse_y_ratio_RF_BRF := rmse_y_RF/rmse_y_BRF]%>%
    # .[,rmse_optN_ratio_RF_BRF := rmse_optN_RF/rmse_optN_BRF]%>%
    # # CNN vs RF
    # .[,rmse_y_ratio_CNN_RF := rmse_y_CNN/rmse_y_RF]%>%
    # .[,rmse_optN_ratio_CNN_RF := rmse_optN_CNN/rmse_optN_RF]%>%
    # # CNN vs BRF 
    # .[,rmse_y_ratio_CNN_BRF := rmse_y_CNN/rmse_y_BRF]%>%
    # .[,rmse_optN_ratio_CNN_BRF := rmse_optN_CNN/rmse_optN_BRF]

# nrow(.SD[ML_cnst_y_piLoss=="BRF"])
# prepare_count_tab[ML_cnst_y_piLoss=="RF",] %>% nrow()
# prepare_count_tab[ML_cnst_y_piLoss=="BRF",] %>% nrow()
# prepare_count_tab[ML_cnst_y_piLoss=="CNN",] %>% nrow()

# Summary Table 
summary_res_CNN_RF_BRF <- prepare_count_tab%>%
    .[,.(
        count_BRF = nrow(.SD[ML_cnst_y_piLoss=="BRF",]),
        count_RF = nrow(.SD[ML_cnst_y_piLoss=="RF",]),
        count_CNN = nrow(.SD[ML_cnst_y_piLoss=="CNN",]),
        count_y_BRF = nrow(.SD[which_ML_y=="BRF",]),
        count_y_RF = nrow(.SD[which_ML_y=="RF",]),
        count_y_CNN = nrow(.SD[which_ML_y=="CNN",]),
        Total= sum(index_cnst_y_piLoss)
        ), by=Model] %>%
    .[,`:=`(
         blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
        )] %>%
    .[,.(Model, blank1, count_y_RF, count_RF,  blank2, count_y_BRF, count_BRF, blank3, count_y_CNN, count_CNN ,blank4, Total)]

# summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]

#- table creation -#
report_summary_res_CNN_RF_BRF <- copy(summary_res_CNN_RF_BRF)%>%
    flextable(.) %>%
    border_remove() %>%
    delete_part(part = "header") %>%
    add_header(
        Model="Model", 
        blank1 = "", count_y_RF = "RF", count_RF = "RF",
        blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
        blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
        blank4 = "", Total = "Total",
        top = TRUE) %>%
    merge_h(part = "header") %>%
    hline_bottom(j=c(3:4, 6:7, 9:10), part = "header") %>%
    add_header(
        Model="", 
        blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
        blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
        blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
        blank4 = "", Total = "",
        top = FALSE) %>%
    hline_bottom(part="all") %>%
    hline_top(part="header") %>%
    align(align = "center", part = "all")%>%
    align(j=1,  align = "left", part = "all")%>%
    footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
     ref_symbols = NA
    ) %>%
    # set_table_properties(width = .7, layout = "autofit") %>%
    fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
    autofit() %>%
    width(j = c(3,4,6,7,9,10,12), width=0.6)%>%
    width(j = c(2,5,8,11), width=0.1)

    # set_table_properties(width = .6, layout = "autofit")

# print(report_summary_res_CNN_RF_BRF, preview = "docx")
# in terms of RMSE of yield prediction and ", "\U1D70B\U0302", as_sub("loss"), ", respectively.

```

# EONR Estimation

```{r, dependson = "source-results"}

##== Distribution ==##
plot_dis_optN <- copy(report_res_subsetML)%>%
    .[Method %in% c("RF", "BRF", "CF_base"), ]%>%
    .[, Method := case_when(
    # Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF"
    )]%>%
    .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
    )]%>%
    # .[, Method:=factor(Method, levels = c("RF", "BRF", "CF-stepwise", "CF-base"))]%>%
    .[, Method:=factor(Method, levels = c("RF", "BRF", "CF-base"))]%>%
    .[, Model:=factor(Model, 
        levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt"))] %>%
    ggplot()+
    geom_density(aes(x=rmse_optN, fill=Method), alpha=0.7)+
    # scale_fill_viridis_d()+
    facet_wrap(~Model, ncol = 1)+
    # labs(x = expression(R^2))+
    labs(x = "RMSE (kg/ha)")+
    theme_few()+
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        legend.title = element_text(size=12,face="bold"),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")

##== Summary Table  ==##

#- preparation -#
table_optN_prep <- copy(report_res_subsetML)%>%
    .[, .(
        rmse_optN = mean(rmse_optN),
        pi_loss = mean(Mean)
        ), by=.(Method, Model)]%>%
    .[,`:=`(
        rmse_optN = format(round(rmse_optN,1), nsmall=1),
        pi_loss = format(round(pi_loss,2), nsmall=2)
        )] %>%
    dcast(Model~Method, value.var = c("rmse_optN", "pi_loss")) %>%
    .[,`:=`(
         blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA, blank5 = NA
        )] %>%
    .[,.(Model, blank1, rmse_optN_RF, pi_loss_RF,  blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN ,blank4, rmse_optN_CF_base, pi_loss_CF_base)]

# table_optN_prep[Model=="aby", rmse_optN_RF]

# avg_optN <- copy(report_res_subsetML)%>%
#     .[, .(
#         Avg_rmse_optN = mean(rmse_optN),
#         Avg_pi_loss = mean(Mean)
#         ), by=Method] %>%
#     .[, `:=`(
#         Avg_rmse_optN = format(round(Avg_rmse_optN, digits=1), nsmall = 1),
#         Avg_pi_loss = format(round(Avg_pi_loss, digits=2), nsmall=2)
#         )]

#- table creation -#
report_table_optN <- copy(table_optN_prep)%>%
    mutate(
    across(
      everything(),
      as.character
        )
    )%>%
    # add_row(.after = 4) %>%
    flextable(.) %>%
    border_remove() %>%
    delete_part(part = "header") %>%
    add_header(
       Model="Model", 
        blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
        blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
        blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
        blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
        top = TRUE) %>%
    merge_h(part = "header") %>%
    hline_bottom(j=c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
    add_header(
       Model="", 
        blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
        blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
        blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
        blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
        top = FALSE) %>%
    compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
    hline_bottom(part="all") %>%
    hline_top(part="header") %>%
    align(align = "center", part = "all")%>%
    align(j=1,  align = "left", part = "all")%>%
    # autofit() %>%
    # width(j = c(2,5,8,11), width=0.3) %>%
    # fix_border_issues() 
    footnote(
        # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")),"."),
     ref_symbols = NA
    ) %>%
    fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
    autofit() %>%
    width(j = c(3,4,6,7,9,10,12,13), width=0.6)%>%
    width(j = c(2,5,8,11), width=0.1)

    # print(report_table_optN, preview = "docx")
    # autofit() 
    # width(j = c(2,5,8,11), width=0.5)
    # width(j = c(2,5,8,11), width=0.5)

# print(report_table_optN, preview = "docx")

# typology <- data.frame(
#   col_keys = names(table_optN_prep),
#   what = c(" ", " ", "RF", "RF", " ", "BRF", "BRF", " ", "CNN", "CNN", " ", "CF-base", "CF-base"),
#   measure = c(" ", " ", "RMSE", "pi_loss", " ", "RMSE", "pi_loss", " ", "RMSE", "pi_loss", " ", "RMSE", "pi_loss"),
#   stringsAsFactors = FALSE )

# copy(table_optN_prep)%>%
#     mutate(
#     across(
#       everything(),
#       as.character
#         )
#     )%>%
#     add_row(.after = 4) %>%
#     flextable(.) %>%
#     border_remove() %>%
#     add_body(
#         Model="Avg.", 
#         blank1 = NA, rmse_optN_RF = avg_optN[Method=="RF",Avg_rmse_optN], pi_loss_RF = avg_optN[Method=="RF",Avg_pi_loss],
#         blank2 = NA, rmse_optN_BRF = avg_optN[Method=="BRF",Avg_rmse_optN], pi_loss_BRF = avg_optN[Method=="BRF",Avg_pi_loss],
#         blank3 = NA, rmse_optN_CNN = avg_optN[Method=="CNN",Avg_rmse_optN], pi_loss_CNN = avg_optN[Method=="CNN",Avg_pi_loss],
#         blank4 = NA, rmse_optN_CF_base = avg_optN[Method=="CF_base",Avg_rmse_optN], pi_loss_CF_base = avg_optN[Method=="CF_base",Avg_pi_loss],
#         top = FALSE
#         )%>%
#     # delete_part(part = "header") %>%
#     set_header_df(mapping = typology, key = "col_keys") %>%
#     compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub("loss"))) %>%
#     merge_h(part = "header") %>%
#     hline_bottom(part="all") %>%
#     hline_top(part="header") %>%
#     align(align = "center", part = "all")%>%
#     align(j=1,  align = "left", part = "all")%>%
#     autofit() %>%
#     width(j = c(2,5,8,11), width=0.5)

```

# Profit Loss

## Profit loss summary and distributions
```{r}
# piLoss_summary <- report_res_subsetML[,select(.SD, Method, Model, Min.:Max., cumulative_pi_loss)]%>%
#     .[, lapply(.SD, mean), by=.(Method, Model)] %>%
#     .[, lapply(.SD,  function(x) as.numeric(format(mean(x), digits=3))), by=.(Method, Model)] %>%
#     flextable()

piLoss_density <- 
    report_res_subsetML[Method!="CNN",] %>%
    .[,Method := case_when(
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF"
    )]%>%
    .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
    )]%>%
    .[,Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
    .[, Model:=factor(Model, 
        levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt"))] %>%
    ggplot() + 
    geom_density(aes(x=Mean, fill=Method), alpha=0.5)+
    # scale_fill_viridis(discrete = TRUE, alpha=0.5) +
    # scale_fill_viridis_d()+
    # labs(x = expression(hat(pi)["loss"], " $/ha")))+
    labs(x = TeX("$\\hat{pi}_{loss}$ (\\$/ha)"))+
    facet_wrap(~Model, ncol=1) +
    theme_few()+
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        legend.title = element_text(size=12,face="bold"),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")
```

# Treatment effect comparison (CF-base vs RF vs BRF)

```{r}
####=== The original code for this figure is in "1_3_CompTeEstimation.R" ===####

figure_te <- readRDS("./Shared/Data/for_writing/dt_TEcomparison.rds")%>%
    .[, Method:= case_when(
        Method=="RF" ~ "RF",
        Method=="BRF" ~ "BRF",
        Method=="CF_base" ~ "CF-base")] %>%
    .[, Method:= factor(Method, levels = c("RF", "BRF", "CF-base"))]%>%
    ggplot() +
    geom_point(aes(x=true_tau_base, y=tau_base), size=0.5)+
    geom_abline(aes(intercept = 0, slope = 1), color="red", show.legend=TRUE) +
    facet_grid(Treatment ~ Method) +
    guides(
        fill = guide_legend(keywidth = 1, keyheight = 1),
        linetype = guide_legend(keywidth = 3, keyheight = 1),
        colour= guide_legend(keywidth = 3, keyheight = 1))+
    labs(y = "Estimated Treatment Effect (kg/ha)")+
    labs(x = "True Treatment Effect (kg/ha)")+
    theme_few() +
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        strip.text.y = element_text(size=12,face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")
```

# Examination of Treatment Effects (CF-base vs CF-stepwise)

```{r}
# ======================================================================
# Examination of te esimation (CF-stepwise vs CF-base)
# ======================================================================

# te_res <- readRDS(here("Shared/Results/res_eval_tre_effects.rds"))%>%
#     .[,.(method, N_index, R_squared)]%>%
#     .[, N_index := case_when(
#     N_index == "1-2" ~ "(N1,N2)",
#     N_index == "2-3" ~ "(N2,N3)",
#     N_index == "3-4" ~ "(N3,N4)",
#     N_index == "4-5" ~ "(N4,N5)",
#     N_index == "1-3" ~ "(N1,N3)",
#     N_index == "1-4" ~ "(N1,N4)",
#     N_index == "1-5" ~ "(N1,N5)"
#   )]%>%
#     .[,sim:=rep(1:1000, each=8)]

##== Treatment Effects Summary Table ==##

# te_res_summary <- te_res[,.(R_squared=mean(R_squared)), by=c("method", "N_index")]%>%
#     .[, R_squared:= round(R_squared,3)]%>%
#     flextable(.)%>%
#     set_header_labels(
#     values = list(
#         method="Method",
#         N_index ="N Rates Combinations",
#         R_squared = "R-squared"
#     ))%>%
#     compose(i = 1, j = 2, part = "header", value = as_paragraph("(N", as_sup("con"), ", N", as_sup("tre"), ")"))%>%
#     compose(i = 1, j = 3, part = "header", value = as_paragraph("R",as_sup("2")))%>%
#     align(align = "center", part = "all")%>%
#     align(j=1,  align = "left", part = "all")%>%
#     # align(align = "center", part = "header")%>%
#     # align_text_col(align = "center", header = TRUE, footer = TRUE)%>%
#     autofit()

##== Graph ==##
#== tre calculation ==#

# reg_data_all <- readRDS(here("Data/for_Simulations/reg_data.rds"))
# test_agg_data_all <- readRDS(here("Data/for_Simulations/test_agg_data.rds"))

# # estimate_tre() is defined in "functions_stepwise_vs_base.R"
# sim_ex <- estimate_tre(x=32, reg_data_all=reg_data_all, test_data_all=test_agg_data_all)

# sim_ex$r2

# saveRDS(sim_ex, here("Shared", "Data","for_writing","tre_demo.rds"))

# sim_output <- readRDS(here("Shared","Data","for_writing","tre_demo.rds"))

# # r2 <-sim_output$r2
# eval <- sim_output$output

# cf_step <- eval[Method=="CF-stepwise"]%>%
#   ggplot()+
#   geom_density(aes(x=value, fill=factor(variable)),alpha=0.8)+
#   facet_wrap(~N_index, ncol = 2)+
#   theme_few()+
#   theme_few()+
#       theme(
#       legend.position="bottom",
#       plot.title = element_text(hjust = 0.5),
#       panel.background = element_rect(fill = "white"),
#         axis.ticks = element_blank(),
#         legend.title = element_blank(),
#         strip.text.x = element_text(size=12,face="bold"),
#         legend.text = element_text(size=12, face="bold"),
#         )+
#         labs(
#         x = "Treatment Effects(kg/ha)",
#         colour = "Cylinders",
#         shape = "Transmission"
#       )

# cf_base <- eval[Method=="CF-base"]%>%
#   ggplot()+
#   geom_density(aes(x=value, fill=factor(variable)),alpha=0.8)+
#   facet_wrap(~N_index, ncol = 2)+
#   theme_few()+
#   theme_few()+
#       theme(
#       legend.position="bottom",
#       plot.title = element_text(hjust = 0.5),
#       panel.background = element_rect(fill = "white"),
#         axis.ticks = element_blank(),
#         legend.title = element_blank(),
#         strip.text.x = element_text(size=12,face="bold"),
#         legend.text = element_text(size=12, face="bold"),
#         )+
#         labs(
#         x = "Treatment effects(kg/ha)",
#         colour = "Cylinders",
#         shape = "Transmission"
#       )
```

# Appendix: CF-base vs CF-stepwise

```{r, dependson = "source-results"}
# ==========================================================================
# RMSE
# ==========================================================================
##== Distribution ==##
plot_dis_CF_optN <- copy(report_res_allML)%>%
    .[Method %in% c("CF_stepwise", "CF_base"), ]%>%
    .[, Method := case_when(
    Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_base" ~ "CF-base"
    )]%>%
    .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
    )]%>%
    .[, Method:=factor(Method, levels = c("CF-stepwise", "CF-base"))] %>%
    .[, Model:=factor(Model, 
        levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt"))] %>%
    ggplot()+
    geom_density(aes(x=rmse_optN, fill=Method), alpha=0.7)+
    # scale_fill_viridis_d()+
    facet_wrap(~Model, ncol = 1)+
    labs(x = "RMSE")+
    theme_few()+
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        legend.title = element_text(size=12,face="bold"),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")

##== barplot ==##
CF_optN_boxplot <- copy(report_res_allML)%>%
    .[Method %in% c("CF_stepwise", "CF_base"), ]%>%
    .[, Method := case_when(
    # Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_base" ~ "CF-base"
    )]%>%
    .[, Method:=factor(Method, levels = c("CF-stepwise", "CF-base"))]%>%
    ggplot() + 
    geom_boxplot(aes(x=Method, y=rmse_optN, fill=Method), alpha=0.5)+
    geom_jitter(aes(x=Method, y=rmse_optN, fill=Method), size=0.3, alpha=0.9) +
    # scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    scale_fill_viridis_d()+
    labs(y = " RMSE")+
    facet_grid(~Model)+
    theme_few()+
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        legend.title = element_text(size=12,face="bold"),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")

##== Summary Table  ==##

#- preparation -#
table_CF_optN_prep <- copy(report_res_allML)%>%
    .[, .(
        rmse_optN = mean(rmse_optN),
        pi_loss = mean(Mean)
        ), by=.(Method, Model)]%>%
    .[,`:=`(
        rmse_optN = format(round(rmse_optN,1), nsmall=1),
        pi_loss = format(round(pi_loss,2), nsmall=2)
        )] %>%
    dcast(Model~Method, value.var = c("rmse_optN", "pi_loss")) %>%
    .[,`:=`(
         blank1 = NA, blank2 = NA
        )] %>%
    .[,.(Model, blank1, rmse_optN_CF_base, pi_loss_CF_base, blank2, rmse_optN_CF_stepwise, pi_loss_CF_stepwise)]

# avg_CF_optN <- copy(report_res_allML)%>%
#     .[, .(
#         Avg_rmse_optN = mean(rmse_optN),
#         Avg_pi_loss = mean(Mean)
#         ), by=Method] %>%
#     .[, `:=`(
#         Avg_rmse_optN = format(round(Avg_rmse_optN, digits=1), nsmall = 1),
#         Avg_pi_loss = format(round(Avg_pi_loss, digits=2), nsmall=2)
#         )]

#- table creation -#
report_table_CF_optN <- copy(table_CF_optN_prep)%>%
    mutate(
    across(
      everything(),
      as.character
        )
    )%>%
    # add_row(.after = 4) %>%
    flextable(.) %>%
    border_remove() %>%
    delete_part(part = "header") %>%
    add_header(
        Model="Model", 
        blank1 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
        blank2 = "", rmse_optN_CF_stepwise = "CF-stepwise", pi_loss_CF_stepwise = "CF-stepwise",
        top = TRUE) %>%
    merge_h(part = "header") %>%
    hline_bottom(j=c(3:4, 6:7), part = "header") %>%
    add_header(
        Model="", 
        blank1 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
        blank2 = "", rmse_optN_CF_stepwise = "RMSE", pi_loss_CF_stepwise = "pi_loss",
        top = FALSE) %>%
    compose(i = 2, j = c(4, 7), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub("loss"))) %>%
    hline_bottom(part="all") %>%
    hline_top(part="header") %>%
    align(align = "center", part = "all")%>%
    align(j=1,  align = "left", part = "all")%>%
    # set_table_properties(width = .5, layout = "autofit")
    autofit() %>%
    width(j = c(2,5), width=0.3) %>%
    fix_border_issues()

# ==========================================================================
# profit-loss
# ==========================================================================

##== Distribution ==##
piLoss_density_CF <- copy(report_res_allML)%>%
    .[Method %in% c("CF_stepwise", "CF_base"), ]%>%
    .[, Method := case_when(
    # Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_base" ~ "CF-base"
    )]%>%
    .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
    )]%>%
    .[, Method:=factor(Method, levels = c("CF-stepwise", "CF-base"))]%>%
    .[, Model:=factor(Model, 
        levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt"))] %>%
    ggplot() + 
    geom_density(aes(x=Mean, fill=Method), alpha=0.5)+
    # scale_fill_viridis(discrete = TRUE, alpha=0.5) +
    # scale_fill_viridis_d()+
    labs(x = expression(hat(pi)["loss"]))+
    facet_wrap(~Model, ncol=1) +
    theme_few()+
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        legend.title = element_text(size=12,face="bold"),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")

##== barplot ==##
CF_piLoss_boxplot <- copy(report_res_allML)%>%
    .[Method %in% c("CF_stepwise", "CF_base"), ]%>%
    .[, Method := case_when(
    # Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_base" ~ "CF-base"
    )]%>%
    .[, Method:=factor(Method, levels = c("CF-stepwise", "CF-base"))]%>%
    ggplot() + 
    geom_boxplot(aes(x=Method, y=Mean, fill=Method), alpha=0.5)+
    # geom_jitter(aes(x=Method, y=Mean, fill=Method), size=0.3, alpha=0.9) +
    # scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    scale_fill_viridis_d()+
    labs(y = " Mean Profit-loss")+
    facet_grid(~Model)+
    theme_few()+
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        legend.title = element_text(size=12,face="bold"),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")

```

### 2022-02-05 Codes/parallel_reproducibility.rmd
initial submission

# parallel::mclapply

+ https://www.r-bloggers.com/2020/09/future-1-19-1-making-sure-proper-random-numbers-are-produced-in-parallel-processing/

+ https://stackoverflow.com/questions/30456481/controlling-seeds-with-mclapply

+ https://stackoverflow.com/questions/40536067/how-to-adjust-future-global-maxsize-in-r

+ https://www.rdocumentation.org/packages/future/versions/1.6.1/topics/future_lapply

+ https://www.jottr.org/2017/02/19/future-rng/

```{r}
library(here)
library(mgcv)
library(ggplot2)
library(grf)
library(sf)
library(measurements)
library(data.table)
library(tidyverse)
library(future.apply)
library(parallel)
#--- source functions ---#
setwd("~/Dropbox/ResearchProject/ML_VRA")
source("./GitControlled/Codes/0_3_functions_main_sim.R")

# /*----------------------------------*/
#' ## Datasets
# /*----------------------------------*/
# === prices ===#
pCorn <- price_table[2, pCorn]
pN <- price_table[2, pN]

reg_data_all <- readRDS("./Shared/Data/for_Simulations/reg_data.rds")
test_data_all <- readRDS("./Shared/Data/for_Simulations/test_agg_data.rds")
```

## Single-core case with set.seed()
```{r}
# check whether set.seed() works for single core 
x=1

set.seed(1378)
cf_temp1 <- 
	get_opt_N(
    	reg_data = reg_data_all[sim==x&padding==1,],
    	test_data = test_data_all[sim==x&padding==1,],
    	var_ls= c("alpha","beta","ymax"),
    	rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    	Method = "CF_base"
)

set.seed(1378)
cf_temp2 <- 
	get_opt_N(
    	reg_data = reg_data_all[sim==x&padding==1,],
    	test_data = test_data_all[sim==x&padding==1,],
    	var_ls= c("alpha","beta","ymax"),
    	rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    	Method = "CF_base"
)

identical(cf_temp1, cf_temp2)
```

+ In the single-core case, set.seed() works.

## Multi-core case (mclapply) with set.seed()

```{r}
set.seed(1378)

cf_temp1 <- 
	mclapply(
		1:2, function(x) {
			get_opt_N(
    			reg_data = reg_data_all[sim==x&padding==1,],
    			test_data = test_data_all[sim==x&padding==1,],
    			var_ls= c("alpha","beta","ymax"),
    			rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    			Method = "CF_base"
    			)
		},
		mc.cores = detectCores() - 2
	) %>%
	rbindlist()

set.seed(1378)

cf_temp2 <- 
	mclapply(
		1:2, function(x) {
			get_opt_N(
    			reg_data = reg_data_all[sim==x&padding==1,],
    			test_data = test_data_all[sim==x&padding==1,],
    			var_ls= c("alpha","beta","ymax"),
    			rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    			Method = "CF_base"
    			)
		},
		mc.cores = detectCores() - 2
	) %>%
	rbindlist()

identical(cf_temp1, cf_temp2)
```

+ In the multi-core case, set.seed() does not works.

## Multi-core case (mclapply) with set.seed
+ use set.seed inside of mc.lapply

```{r}

cf_temp1 <- 
	mclapply(
		1:2, function(x) {
			set.seed(1378)

			get_opt_N(
    			reg_data = reg_data_all[sim==x&padding==1,],
    			test_data = test_data_all[sim==x&padding==1,],
    			var_ls= c("alpha","beta","ymax"),
    			rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    			Method = "CF_base"
    			)
		},
		mc.cores = detectCores() - 2
	) %>%
	rbindlist()

cf_temp2 <- 
	mclapply(
		1:2, function(x) {
			set.seed(1378)

			get_opt_N(
    			reg_data = reg_data_all[sim==x&padding==1,],
    			test_data = test_data_all[sim==x&padding==1,],
    			var_ls= c("alpha","beta","ymax"),
    			rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    			Method = "CF_base"
    			)
		},
		mc.cores = detectCores() - 2
	) %>%
	rbindlist()

identical(cf_temp1, cf_temp2)
```
+ This works.

# Multi-core case (mclapply) with set.seed (`RNGkind("L'Ecuyer-CMRG")`)
+ https://stackoverflow.com/questions/30456481/controlling-seeds-with-mclapply

```{r}
RNGkind("L'Ecuyer-CMRG")

set.seed(1378)

cf_temp1 <- 
	mclapply(
		1:2, function(x) {
			get_opt_N(
    			reg_data = reg_data_all[sim==x&padding==1,],
    			test_data = test_data_all[sim==x&padding==1,],
    			var_ls= c("alpha","beta","ymax"),
    			rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    			Method = "CF_base"
    			)
		},
		mc.cores = detectCores() - 2
	) %>%
	rbindlist()

RNGkind("L'Ecuyer-CMRG")

set.seed(1378)

cf_temp2 <- 
	mclapply(
		1:2, function(x) {
			get_opt_N(
    			reg_data = reg_data_all[sim==x&padding==1,],
    			test_data = test_data_all[sim==x&padding==1,],
    			var_ls= c("alpha","beta","ymax"),
    			rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    			Method = "CF_base"
    			)
		},
		mc.cores = detectCores() - 2
	) %>%
	rbindlist()

identical(cf_temp1, cf_temp2)
```
+ This works.

# Multi-core case (mclapply) with set.seed (`mc.set.seed=TRUE`)

```{r}
set.seed(1378)

cf_temp1 <- 
	mclapply(
		1:2, function(x) {
			get_opt_N(
    			reg_data = reg_data_all[sim==x&padding==1,],
    			test_data = test_data_all[sim==x&padding==1,],
    			var_ls= c("alpha","beta","ymax"),
    			rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    			Method = "CF_base"
    			)
		},
		mc.cores = detectCores() - 2,
		mc.set.seed = TRUE
	) %>%
	rbindlist()

set.seed(1378)

cf_temp2 <- 
	mclapply(
		1:2, function(x) {
			get_opt_N(
    			reg_data = reg_data_all[sim==x&padding==1,],
    			test_data = test_data_all[sim==x&padding==1,],
    			var_ls= c("alpha","beta","ymax"),
    			rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    			Method = "CF_base"
    			)
		},
		mc.cores = detectCores() - 2,
		mc.set.seed = TRUE
	) %>%
	rbindlist()

identical(cf_temp1, cf_temp2)
```
+ This does not work

# Multi-core case (future_lapply) with set.seed (`future.seed = TRUE`)

```{r}
plan(multicore, workers = detectCores()-2)
options(future.globals.maxSize= 850*1024^2)

set.seed(1378)
cf_temp1 <- 
	future_lapply(
		1:2, function(x) {
			get_opt_N(
    			reg_data = reg_data_all[sim==x&padding==1,],
    			test_data = test_data_all[sim==x&padding==1,],
    			var_ls= c("alpha","beta","ymax"),
    			rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    			Method = "CF_base"
    			)
		},
		future.seed = TRUE
	) %>%
	rbindlist()

set.seed(1378)
cf_temp2 <- 
	future_lapply(
		1:2, function(x) {
			get_opt_N(
    			reg_data = reg_data_all[sim==x&padding==1,],
    			test_data = test_data_all[sim==x&padding==1,],
    			var_ls= c("alpha","beta","ymax"),
    			rates_ls= reg_data_all[sim==x,]$rate%>%unique()%>%sort(),
    			Method = "CF_base"
    			)
		},
		future.seed = TRUE
	) %>%
	rbindlist()

identical(cf_temp1, cf_temp2)
```

+ This works fine. I also found that this way we can avoid using the same seed every loop unlike `mclapply()`

+ For example,

```{r}
#/*----------------------------------*/
#' ## mclapply
#/*----------------------------------*/
# RNGkind("Mersenne-Twister")

func <- function(x) runif(10)

# === 1st iteration === #
set.seed(1378)

rng1 <- unlist(
    mclapply(X = 1:10,
             FUN = function(x) runif(1),
             mc.cores = detectCores()-2,
             mc.set.seed = TRUE)
)

rng2 <- unlist(
    mclapply(X = 1:10,
             FUN = function(x) runif(1),
             mc.cores = detectCores()-2,
             mc.set.seed = TRUE)
)

identical(rng1, rng2)

x1 <- c(rng1, rng2)

# === 2nd iteration === #
set.seed(1378)

rng1 <- unlist(
    mclapply(X = 1:10,
             FUN = function(x) runif(1),
             mc.cores = detectCores()-2,
             mc.set.seed = TRUE)
)

rng2 <- unlist(
    mclapply(X = 1:10,
             FUN = function(x) runif(1),
             mc.cores = detectCores()-2,
             mc.set.seed = TRUE)
)

identical(rng1, rng2)

x2 <- c(rng1, rng2)

identical(x1, x2)

#/*----------------------------------*/
#' ## future_lapply
#/*----------------------------------*/

# === 1st iteration === #
set.seed(1378)

rng1 <- unlist(
    future_lapply(X = 1:10,
             FUN = function(x) runif(1),
             future.seed = TRUE)
)

rng2 <- unlist(
    future_lapply(X = 1:10,
             FUN = function(x) runif(1),
             future.seed = TRUE)
)

identical(rng1, rng2)

x1 <- c(rng1, rng2)

# === 2nd iteration === #
set.seed(1378)

rng1 <- unlist(
    future_lapply(X = 1:10,
             FUN = function(x) runif(1),
             future.seed = TRUE)
)

rng2 <- unlist(
    future_lapply(X = 1:10,
             FUN = function(x) runif(1),
             future.seed = TRUE)
)

identical(rng1, rng2)

x2 <- c(rng1, rng2)

identical(x1, x2)
```

### 2022-02-05 Presentation/thesis_defense/presentation.Rmd
initial submission

---
title: "Machine Learning Methods for Site-specific Input Management"
author: "Shunkei Kakimoto"
output:
  xaringan::moon_reader:
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML"
    # css: [default, metropolis, metropolis-fonts] 
    css: xaringan-themer.css 
    lib_dir: libs
    nature:
      ratio: 12:8
      highlightStyle: github
      highlightLines: true
      highlightSpans: true
      countIncrementalSlides: false
---

# Table of contents

1. [Introduction to R and RStudio](#intro)
2. [Object types](#objects)
3. [Functions and packages](#functions)
4. [Some fundamentals on vector, matrix, list, and data.frame](#objects_basics)

---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  header_h1_font_size = "2.1rem",
  header_h2_font_size = "1.5rem",
  text_font_size = "0.9rem",
  code_font_size = "0.8rem"
)

```

```{r , include=FALSE}
library(knitr)
library(here)

opts_chunk$set(
  fig.align = "center", #fig.width=6, fig.height=4.5, 
  # out.width="748px", #out.length="520.75px",
  # dpi = 100, #fig.path='Figs/',
  cache = F#, echo=F, warning=F, message=F
  )

opts_knit$set(root.dir = here())
# setwd("~/Box/Teaching/UNL/DataScience") 
```

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

library(RefManageR)
BibOptions(
  check.entries = FALSE,
  bib.style = "authoryear",
  # cite.style = "alphabetic",
  style = "markdown",
  dashed = TRUE,
  max.names = 3,
  longnamesfirst=FALSE
  )

file.name <- here("Writing", "MSthesis.bib")
bib <- ReadBib(file.name)

```

```{r, include = F}
#--- load packages ---#
suppressMessages(library(data.table))
suppressMessages(library(sf))
suppressMessages(library(tidyverse))
suppressMessages(library(flextable))
suppressMessages(library(officer))
suppressMessages(library(modelsummary))
suppressMessages(library(gridExtra))
````

```{r analyses, echo=FALSE, message=FALSE, warning=FALSE, results = "hide", fig.show='hide', cache = FALSE}
#/*=================================================*/
#' # Preparation
#/*=================================================*/
# This is where you prepare datasets and results

#/*----------------------------------*/
#' ## Create figures and tablesb
#/*----------------------------------*/
# --- Convert an Rmd file into a pure R file using purl() ---#
knitr::purl(here("Codes/CNN_PrepareResults.Rmd"), output = here("Codes/CNN_PrepareResults.R"))

# --- Read the simulation results and prepare figures and tables ---#
source(here("Codes/CNN_PrepareResults.R"))
```

```{css css-setup, echo = F}
.remark-slide-number {
  font-size: 10pt;
  margin-bottom: -11.6px;
  margin-right: 10px;
  color: #FFFFFF; /* white */
  opacity: 1; /* default: 0.5 */
}

.remark-slide-content.hljs-github h1 {
  margin-top: 5px;  
  margin-bottom: 25px;  
}

.remark-slide-content.hljs-github {
  padding-top: 10px;  
  padding-left: 30px;  
  padding-right: 30px;  
}

.panel-tabs {
  <!-- color: #062A00; -->
  color: #841F27;
  margin-top: 0px;  
  margin-bottom: 0px;  
  margin-left: 0px;  
  padding-bottom: 0px;  
}

.panel-tab {
  margin-top: 0px;  
  margin-bottom: 0px;  
  margin-left: 3px;  
  margin-right: 3px;  
  padding-top: 0px;  
  padding-bottom: 0px;  
}

.panelset .panel-tabs .panel-tab {
  min-height: 40px;
}

.remark-slide th {
  border-bottom: 1px solid #ddd;
}

.remark-slide thead {
  border-bottom: 0px;
}

.gt_footnote {
  padding: 2px;  
}

.remark-slide table {
  border-collapse: collapse;
}

.remark-slide tbody {
  border-bottom: 2px solid #666;
}

.important {
  background-color: lightpink;
  border: 2px solid blue;
  font-weight: bold;
}

.bold { font-weight: bold; }

.red {
  color: #f34213;
}

.remark-code {
  display: block;
  overflow-x: auto;
  padding: .5em;
  background: #ffe7e7;
}

.hljs-github .hljs {
  background: #f2f2fd;
}

.remark-inline-code {
  padding-top: 0px;
  padding-bottom: 0px;
  background-color: #e6e6e6;
}

.r.hljs.remark-code.remark-inline-code{
  font-size: 0.9em
}

.left-full {
  width: 80%;
  float: left;
}

.left-code {
  width: 38%;
  height: 92%;
  float: left;
}

.right-plot {
  width: 60%;
  float: right;
  padding-left: 1%;
}

.left-plot {
  width: 60%;
  float: left;
  padding-right: 1%;
}

.left6 {
  width: 60%;
  height: 92%;
  float: left;
}

.left5 {
  width: 49%;
  height: 92%;
  float: left;
}

.right5 {
  width: 49%;
  float: right;
  padding-left: 1%;
}

.right4 {
  width: 39%;
  float: right;
  padding-left: 1%;
}

.left3 {
  width: 29%;
  height: 92%;
  float: left;
}

.right7 {
  width: 69%;
  float: right;
  padding-left: 1%;
}

.left4 {
  width: 38%;
  float: left;
}

.right6 {
  width: 60%;
  float: right;
  padding-left: 1%;
}

ul li{
  margin: 7px;
}

ul, li{
  margin-left: 15px; 
  padding-left: 0px; 
}

ol li{
  margin: 7px;
}

ol, li{
  margin-left: 15px; 
  padding-left: 0px; 
}

```

```{css content-box, echo = F}
.content-box { 
    box-sizing: border-box;
    background-color: #e2e2e2;
}
.content-box-blue,
.content-box-gray,
.content-box-grey,
.content-box-army,
.content-box-green,
.content-box-purple,
.content-box-red,
.content-box-yellow {
  box-sizing: border-box;
  border-radius: 5px;
  margin: 0 0 10px;
  overflow: hidden;
  padding: 0px 5px 0px 5px;
  width: 100%;
}
.content-box-blue { background-color: #F0F8FF; }
.content-box-gray { background-color: #e2e2e2; }
.content-box-grey { background-color: #F5F5F5; }
.content-box-army { background-color: #737a36; }
.content-box-green { background-color: #d9edc2; }
.content-box-purple { background-color: #e2e2f9; }
.content-box-red { background-color: #ffcccc; }
.content-box-yellow { background-color: #fef5c4; }
.content-box-blue .remark-inline-code,
.content-box-blue .remark-inline-code,
.content-box-gray .remark-inline-code,
.content-box-grey .remark-inline-code,
.content-box-army .remark-inline-code,
.content-box-green .remark-inline-code,
.content-box-purple .remark-inline-code,
.content-box-red .remark-inline-code,
.content-box-yellow .remark-inline-code { 
  background: none;
}

.full-width {
    display: flex;
    width: 100%;
    flex: 1 1 auto;
}
```

```{css blockuote, echo = F}
blockquote, .blockquote {
  display: block;
  margin-top: 0.1em;
  margin-bottom: 0.2em;
  margin-left: 5px;
  margin-right: 5px;
  border-left: solid 10px #0148A4;
  border-top: solid 2px #0148A4;
  border-bottom: solid 2px #0148A4;
  border-right: solid 2px #0148A4;
  box-shadow: 0 0 6px rgba(0,0,0,0.5);
  /* background-color: #e64626; */
  color: #e64626;
  padding: 0.5em;
  -moz-border-radius: 5px;
  -webkit-border-radius: 5px;
}

.blockquote p {
  margin-top: 0px;
  margin-bottom: 5px;
}
.blockquote > h1:first-of-type {
  margin-top: 0px;
  margin-bottom: 5px;
}
.blockquote > h2:first-of-type {
  margin-top: 0px;
  margin-bottom: 5px;
}
.blockquote > h3:first-of-type {
  margin-top: 0px;
  margin-bottom: 5px;
}
.blockquote > h4:first-of-type {
  margin-top: 0px;
  margin-bottom: 5px;
}

.text-shadow {
  text-shadow: 0 0 4px #424242;
}
```

```{css scroll, echo = F}
/******************
 * Slide scrolling
 * (non-functional)
 * not sure if it is a good idea anyway
slides > slide {
  overflow: scroll;
 padding: 5px 40px;
}
.scrollable-slide .remark-slide {
  height: 400px;
  overflow: scroll !important;
}
 ******************/

.scroll-box-8 {
  height:8em;
  overflow-y: scroll;
}
.scroll-box-10 {
  height:10em;
  overflow-y: scroll;
}
.scroll-box-12 {
  height:12em;
  overflow-y: scroll;
}
.scroll-box-14 {
  height:14em;
  overflow-y: scroll;
}
.scroll-box-16 {
  height:16em;
  overflow-y: scroll;
}
.scroll-box-18 {
  height:18em;
  overflow-y: scroll;
}
.scroll-box-20 {
  height:20em;
  overflow-y: scroll;
}
.scroll-box-24 {
  height:24em;
  overflow-y: scroll;
}
.scroll-box-30 {
  height:30em;
  overflow-y: scroll;
}
.scroll-output {
  height: 90%;
  overflow-y: scroll;
}

```

class: inverse, center, middle
name: intro

# Introduction

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

---

# Background of site-specific N managment.
+ Nitrogen is an essential nutrient for crop production
  + it helps to attain higher yield with richer grain quality (e.x., protenin content)  
+ Excess amount of nitrogen application use is not only the economic loss but also potentially causes environmental loss(e.g., nitrate leaching).

<!-- + This is the reason why site-specific nitrogen management has been gathering attention
 The aim is to apply neccessary amount of nitrogen to neccesary site of the field, By doing so, we can reudce the loss, which result in economic benefit and environmental loss.   -->

---
<!-- + This is the reason why site-specific nitrogen management has been gathering attention but -->
# Difficulty of site-specific N management
+ "for the same field cropped with the same cultuvart the optimal N rate in not constant across the field becasue of the spatial vailiability of crop growing conditions and soil properties."[`r Citet(bib, "basso2011strategic")`]
+ "Nitrogen responses vary widely across fields and years, and are affected by factors such as soil type and weathersawyer2006concepts" [`r Citet(bib, "sawyer2006concepts")`]

+ plant-soil process over N is affected by environmental condition in a highly complex way
  +

---

# Recent efforts to do site-specific input management 
+ theme: ML methods seem to be suitable for capturing heterogeneous impact of N application use on yield

+ Limitation of the current toolbox: Traditional Regression approaches 
  -> They have some limitations on capturing heterogeneity in yield response functions
  -> reuqire to pre-specifed potentially restrictive functional form
    - (this also means that ) researchers have to indentify which factors contribute to 
+ Consequeses of misspecified modeling leads to recommendation maps that do not utilize the full potential of VRA. (which result in making VRA less )

<!-- "Functional form employed in econometric analysis often lack theoretical grounding and are not sufficiently flexible to capture the multiple interactions, non-linearities and heterogeneity fso common to biological or social process in agricultural and environmental systems" -->
---

# ML methods for estimating optimal N rate
+ ML methods: 
  + can select functional forms flexibiltity in a data-driven way. 
  + can model more complex non-liner and multi-way interactions of variabels

+ The algorithm of ML methods is optimized for achiving high prediction accuracy in out-of-sample

+ The past studies have used high predictive ability of  ML methods(Random forest, Boosted random forest, LASSO, ect.) for estimating economically optimal N rates (EONR)
  + `r Citet(bib, c("Qin2018", "lawes2019", "Ransom2019"))` attempted to directly predict EONR using soil and weather information
  + `r Citet(bib, c("Wang2021", "coulibali2020"))` estimate EONR based on the identified yield response function to N 
(These studies estimate optimal nitrogen application rtates at the field levle, not site-specifically within a field)

---

# Causal inference with ML method

---

# Prediction VS Causal inference

Theme: What’s the difference?
+ Prediction and causal effect estimation are two distinctive statistical objects

For example, in our case, 
+ yield preidiction and estimation of causal impacts of a change in input level on yield are different.

+ yield prediction problem: What is the best prediction of yield for a particure site? 
  - Prediction-oriented ML methods would successfully answere this question by learning the pattern of the relationship between observed yield and field characteristics site-specifically and  find the best functional resulting low prediction error in an independent test set.

+ causal effect of an input on yield: What is the effect of changing the N application rete on yield for a particular site?
  - Such “change” in yields cannot be observed in reality
  - Sampling uncertainty
  - More of asymptotic properties about the parameter estimates are required

+ In summary, the successful prediction of yield does not necessarily mean successful identification of the causal impact of an input on yield, and vice versa. This is because their goals are different and therefore their approches are different.

---

name: objective
# Objective of the study

+ It is crucial to  estimate heterogeneous impact of N fartilization on yield for site-speicific nitrogne management.
+ CF seems to be an appealing tool for identifying the heterogeneous impacts of an input because its algorithm is optimized for that pourpose.

+ The objective of the study is to evaluate the performance of CF for site-specific input use recommneation.
  -  Specifically,  we attempt to show how we can use CF for site-specific EONR estimation. We propose two approaches with CF and test their performance comparing with RF and BRF, which are widely accepted prediction-oriented ML methods in the previous studies.

---

# The flow of the rest of the presentation
+ To study the comparative performace of CF for site-specific input use recommendation, we conduct 1000 rounds of Monte Calro simulation.

(1). Field, yield response fucntion, variation in parameters to be used for the analysis
(2). Data generation
(3). Methods
(4). Results

---

# Field setup  
<!-- plot map -->
.left5[
<!-- + The geographical field data for the simulated on-farm precision experiments was created based on an actual field of Data-Intensive Farm Management (DIFM) project [`r Citet(bib, "bullock2019")`].  -->

+ .content-box-green[**plot**]: 240 by 60 feet dimensions, 384 plots in total
+ .content-box-green[**subplot**]: Each one of the four grids in a plot, 1536 subplots in total 
+ .content-box-green[**cell**]: Each one of the six grids in a subplot, 9216 cells in total 
+ The field size is about 507 acres. 
+ The basic unit of the field is the cell, and the field characteristics data is generated on a cell basis.

```{r, echo=FALSE, out.width = "250px", fig.cap="Figure: Example of a Plot"}  
ex_plot
```
]

.right5[
```{r, echo=FALSE, out.width = "600px", fig.cap="Figure: Layout of The Simulated Field(plot-levle)"}  
plot_field
```
]

---

# Field setup  
<!-- subplot map -->
.left5[
<!-- + The geographical field data for the simulated on-farm precision experiments was created based on an actual field of Data-Intensive Farm Management (DIFM) project [`r Citet(bib, "bullock2019")`].  -->

+ .content-box-green[**plot**]: 240 by 60 feet dimensions, 384 plots in total
+ .content-box-green[**subplot**]: Each one of the four grids in a plot, 1536 subplots in total 
+ .content-box-green[**cell**]: Each one of the six grids in a subplot, 9216 cells in total 
+ The field size is about 507 acres. 
+ The basic unit of the field is the cell, and the field characteristics data is generated on a cell basis.

```{r, echo=FALSE, out.width = "250px", fig.cap="Figure: Layout of the Subplots in a Plot"}  
ex_plot_subplots
```
]

.right5[
```{r, echo=FALSE, out.width = "600px", fig.cap="Figure: Layout of The Simulated Field(subplot-level)"}  
plot_subplots
```
]
---

# Field setup  
<!-- cell map -->
.left5[
<!-- + The geographical field data for the simulated on-farm precision experiments was created based on an actual field of Data-Intensive Farm Management (DIFM) project [`r Citet(bib, "bullock2019")`].  -->

+ .content-box-green[**plot**]: 240 by 60 feet dimensions, 384 plots in total
+ .content-box-green[**subplot**]: Each one of the four grids in a plot, 1536 subplots in total 
+ .content-box-green[**cell**]: Each one of the six grids in a subplot, 9216 cells in total 
+ The field size is about 507 acres. 
+ The basic unit of the field is the cell, and the field characteristics data is generated on a cell basis.

```{r, echo=FALSE, out.width = "250px", fig.cap="Figure: Layout of the Cells in a Plot"}  
ex_plot_subplots_cells
```
]

.right5[
```{r, echo=FALSE, out.width = "600px", fig.cap="Figure: Layout of The Simulated Field(cell-levle)"}  
field_map
```
]

---

# True  site-specific yield response function
.left6[
.content-box-purple[**The Mitscherlich-Baule response functions**]
<br>
\begin{equation}
f_i(N) = ymax_i(1-exp(\alpha_i + \beta_i \cdot N))
\end{equation}
  + $ymax_i$: an asymptotic yield plateau(kg/ha)
  + $\alpha_i$: inherent soil N content
  + $\beta_i$: plant N-fertilizer uptake efficiency
  + $N$: applied N fertilization rate(kg/ha)
  + $i$: cell $i$ of the field
]

.right4[
```{r, echo=FALSE, fig.cap="Figure: An Example of the Mitscherlich-Baule response curve"}
sample_MB_curve
```
]

---

# True site-specific optimal N rate

.left6[
.content-box-purple[**The Mitscherlich-Baule response functions**]
<br>
\begin{equation}
f_i(N) = ymax_i(1-exp(\alpha_i + \beta_i \cdot N))
\end{equation}
  + $ymax_i$: an asymptotic yield plateau(kg/ha)
  + $\alpha_i$: inherent soil N content
  + $\beta_i$: plant N-fertilizer uptake efficiency
  + $N$: applied N fertilization rate(kg/ha)
  + $i$: cell $i$ of the field $(i \in \{1,...,9216\})$
<br>
<br>

.content-box-purple[**"True" site specific profit-maximizing N rate(EONR)**]

\begin{equation}
N^{opt}_i =\underset{\mathrm{N}}{argMax}(P_{C} \cdot f_i(N) - P_N \cdot N) 
\end{equation}
  + $P_C$: corn price (3.5 $/kg)
  + $P_N$: the price of N fertilizer(0.6 $/kg)

]

.right4[
```{r, echo=FALSE, fig.cap="Figure: An Example of the Mitscherlich-Baule response curve"}
sample_MB_curve
```
]

---

# True yield calculation
+ In reality, the realized crop yield is affected by spatially stochastic field characteristics such as the effects of weather conditions. 
$$
F_i(N) = ymax_i(1-exp(\alpha_i + \beta_i \cdot N))+u_i
$$
  + where, $u_i$ is the random yield disturbance term

.content-box-purple[**Assumptions about the error term**]
+ It is assumed that $\beta_i$ and $u_{i}$ are associated to some extent
  +  For example, precipitation may not only affect crop yield according to the spatial heterogeneous soil water capacity, but also can contribute to N runoff, or soil nitrate leaching[`r Citet(bib, "he2016sensitivity")`] which results in lower plant N-fertilizer uptake efficiency.

---

# Modeling assumptions
.content-box-purple[**Variations in parameters**]

.content-box-green[**Setup1. Create irrelevant site-specific parameters**]
+ $\theta1_i$, $\theta2_i$
  + irrelevant to the ture yield response function
  + correlated with $\beta_i$ to some extent

.content-box-green[**Setup2. Create two splitted site-specific parameters from each of the true response parameters**]
+ $\alpha1_i, \alpha2_i, \beta1_i, \beta2_i, ymax1_i, ymax2_i$
  + For example, $ymax_i \times r_i =ymax1_i$ and $ymax_i \times (1-r_i) =ymax2_i$ 
  + where, $r_i$ is a split ratio difined site-specifically

---

# Modeling assumptions
.content-box-purple[**Variations in parameters**]

.content-box-green[**Setup1. Create irrelevant site-specific parameters**]
+ $\theta1_i$, $\theta2_i$
  + irrelevant to the ture yield response function
  + correlated with $\beta_i$ to some extent

.content-box-green[**Setup2. Create two splitted site-specific parameters from each of the true response parameters**]
+ $\alpha1_i, \alpha2_i, \beta1_i, \beta2_i, ymax1_i, ymax2_i$
  + For example, $ymax_i \times r_i =ymax1_i$ and $ymax_i \times (1-r_i) =ymax2_i$ 
  + where, $r_i$ is a split ratio difined site-specifically

.content-box-purple[**Modeling scenarios**]

Name                                 | Combinations of parameters
------------------------------------ | ------------------------------------
.bold[aby]                           | $\alpha_i$, $\beta_i$, $ymax_i$
.bold[abytt]                         | $\alpha_i$, $\beta_i$, $ymax_i$, $\theta1_i$, $\theta2_i$
.bold[aabbyy]                        | $\alpha1_i$, $\alpha2_i$, $\beta1_i$, $\beta2_i$, $ymax1_i$, $ymax2_i$
.bold[aabbyytt]                      | $\alpha1_i$, $\alpha2_i$, $\beta1_i$, $\beta2_i$, $ymax1_i$, $ymax2_i$, $\theta1_i$, $\theta2_i$
<!-- 1. $\alpha_i$, $\beta_i$, $ymax_i$; `aby` modeling sinario 
2. $\alpha_i$, $\beta_i$, $ymax_i$, $\theta1_i$, $\theta2_i$; `abytt` modeling sinario 
3. $\alpha1_i$, $\alpha2_i$, $\beta1_i$, $\beta2_i$, $ymax1_i$, $ymax2_i$; `aabbyy` modeling sinario
4. $\alpha1_i$, $\alpha2_i$, $\beta1_i$, $\beta2_i$, $ymax1_i$, $ymax2_i$, $\theta1_i$, $\theta2_i$; `aabbyytt` modeling sinario -->

---
<!-- # Field Charateristics Data Generation: step1 -->
# Field Charateristics Data Generation

.left4[
.content-box-green[**Step1**]
+ Site-specific parameter dataset, $\{(ymax_i, \alpha_i, \beta_i, u_i, \theta1_i, \theta2_i, r_i):i = \{1,...,9216\}\}$ are simualted
  + Each parameter is simulated by generating spatially autocorrelated random fields 
  + Unconditional Gaussian geostatistical simulation based on the spherical variogram models is used
]

.right5[
```{r, echo=FALSE, fig.cap="Figure: An Example Spatial Distributions of Field Charateristics"}
grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2,nrow=2)
```
]

---
<!-- # Field Charateristics Data Generation: step2 -->
# Field Charateristics Data Generation

.left4[
.content-box-green[**Step1**]
+ Site-specific parameter dataset, $\{(ymax_i, \alpha_i, \beta_i, u_i, \theta1_i, \theta2_i, r_i):i = \{1,...,9216\}\}$ are simualted
  + Each parameter is simulated by generating spatially autocorrelated random fields 
  + Unconditional Gaussian geostatistical simulation based on the spherical variogram models is used

.content-box-green[**Step2**]
+ $\alpha1_i, \alpha2_i, \beta1_i, \beta2_i, ymax1_i, ymax2_i$ are generated
+ True optimal N $(N^{opt}_i)$ calculation
]

.right5[
```{r, echo=FALSE, fig.cap="Figure: An Example Spatial Distributions of Field Charateristics"}
grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2,nrow=2)
```
]

---
<!-- # Field Charateristics Data Generation: step3 -->
# Field Charateristics Data Generation
.pull-left[
.content-box-green[**Step1**]
+  Site-specific parameter dataset, $\{(ymax_i, \alpha_i, \beta_i, u_i, \theta1_i, \theta2_i, r_i):i = \{1,...,9216\}\}$ are simualted
  + Each parameter is simulated by generating spatially autocorrelated random fields 
  + Unconditional Gaussian geostatistical simulation based on the spherical variogram models is used

.content-box-green[**Step2**]
+ $\alpha1_i, \alpha2_i, \beta1_i, \beta2_i, ymax1_i, ymax2_i$ are generated
+ True optimal N $(N^{opt}_i)$ calculation

.content-box-purple[**Repeat step1 and step2 1000 times**]
]

.pull-right[
```{r, echo=FALSE, fig.cap="Figure: An Example Spatial Distributions of True optimal Nitrogne Rate"}
field_optN
```
]

---

# On-farm Field Experiment Data Generation

.pull-left[
.content-box-green[**Randomized N Experiment**]
+ Five different N rates are ramdomly assigned to the field's $384$ plots. 
  + The N application rates are selected from the range of true optimal N rates for that simulation round so that N rates to be used for the trial cover the range of true optimal N.

]

.pull-right[
```{r, echo=FALSE, fig.cap="Figure: An Example of Experimental Design of Nitrogen"}
field_Ndesign
```
]

---

# On-farm Field Experiment Data Generation

.pull-left[
.content-box-green[**Randomized N Experiment**]
+ Five different N rates are ramdomly assigned to the field's $384$ plots. 
  + The N application rates are selected from the range of true optimal N rates for that simulation round so that N rates to be used for the trial cover the range of true optimal N.

.content-box-green[**Yield Data Generation**]
+ $F_i(N) = ymax_i(1-exp(\alpha_i + \beta_i \cdot N))+u_i$
+ Due to physical size of the crop harvester, yield can be recorded only at subplot resolution.   
]

.pull-right[
```{r, echo=FALSE, fig.cap="Figure: An Example Spatial Distribution of True Yield(Cell-Level)"}
field_yield
```
]

---

# On-farm Field Experiment Data Generation

.pull-left[
.content-box-green[**Randomized N Experiment**]
+ Five different N rates are ramdomly assigned to the field's $384$ plots. 
  + The N application rates are selected from the range of true optimal N rates for that simulation round so that N rates to be used for the trial cover the range of true optimal N.

.content-box-green[**Yield Data Generation**]
+ $F_i(N) = ymax_i(1-exp(\alpha_i + \beta_i \cdot N))+u_i$
+ Due to physical size of the crop harvester, it is assumed that yield can be recorded only at subplot resolution.
]

.pull-right[
```{r, echo=FALSE, fig.cap="Figure: An Example Spatial Distribution of True Yield(Subplot-Level)"}
field_yield_subplot
```
]

---
class: inverse, center, middle
name: intro

# Method

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

---

# ML method: Random Forest (RF)

.left4[
+ RF is an ensemble of regression trees
+ At each of the reaf of the tree, the predicted value of a particular sample is the average of the dependent variable for all the observations fallen into that leaf
+ An individual regression tree is built by recursively splitting covariate space into two disjoint regions(leaves) using a specific value(splitting value) of a certain covariate(splitting variable)
+ The split is selected in a way that minimizes the mean square of error(MES; $[\sum_{i=1}^N (y_i - \widehat{y}_i)^2]/N$) across the two new leaves
+ The component of each regreesion tree is grown with the bootstrap sample or subsample and the splits are determined from a random subset of the covariates 
    + RF can effectively reduce the variance and attain a more precise prediction than any single tree.
+ The outcome of RF is the average of outcomes from the all the trees
]

.right6[
```{r, echo=FALSE, fig.cap="An Illustrative Example of regression tree"}
knitr::include_graphics(here("Writing", "Presentation" ,"regtree_ex.pdf"))
```
]

---

# ML method: Boosted Random Forest (BRF)
+ `Boosting` is a general method for improving the accuracy of anly given learning algolithm`r Citet(bib, c("freund1999short"))`
+ While RF builds many trees independently using the same randomized processes, BRF builds trees sequentially allowing the current tree to correct for the bias of those that were built before it.
+ `r Citet(bib, c("Ghosal2020a"))` proposed "one step of gradient boosting" method and showed it can improve the bias of RF 
+ BRF has been shown to perform better than RF in predicting yield

---

# ML method: Causal Forest (CF)

+ `r Citet(bib, c("athey2016recursive"))` and `r Citet(bib, c("Wager2018a"))` developed CF to estimate heterogeneous treatment effects 
+ CF is an ensemble of causal tree(CT)
+ At each leaf of the tree, the treatment effect is calculated as the difference in the mean yield of the treated and control groups for all the observations fallen into that leaf
+ The split is identified in a way that maximiaizes the heterogneity of treatment effects
  + the split is selected such that maximizing the variance of treatment effects across the resulting two leaves while giving a penalty to a split that creates large within-leaf variance
+ CF average the estimated treatment effects from all the CT

---

# ML method: Causal Forest (CF)
+ $N^{con}=81$(kg/ha), $N^{tre}=116$(kg/ha)
+ Covariates: $\alpha$, $\beta$, $ymax$

```{r, echo=FALSE,  out.width = "600px", out.height = "500px", fig.cap="An Illustrative Example of causal tree"}
knitr::include_graphics(here("Writing","Presentation", "ctree_ex.pdf"))
```

---

# ML method: Causal Forest (CF)
+ **Honesty condition**
  + The samples used for tree building is devided into two parts randomly. The first part is used for within-leaf treatment effet estimation, and the second part is used in deciding where to put split
  + This condition avoids overestimating the heterogeneity of treatment effects
<br />
<br />
+ **Uncounfoundedness assumption** 
  + No unobserved variables affect both treatment assignment and the outcome.

---

# Estimating EONR with RF and BRF

.content-box-purple[**Training phase**]
+ For each modeling scenario, a single yield response function is identified by RF or BRF respectively
  + Let $\widehat{g}(N,\mathbf{c})$ be an estimated yield response function

.content-box-purple[**Prediction phase**]

.content-box-green[**Identify site-specific yield response function to N**]
+ Let $\widehat{y}_{i}(N)$ be a yield response function to $N$ for some site $i$

\begin{equation}
\widehat{y}_{i}(N) \equiv \widehat{g}(N,\mathbf{c_{i}})
\end{equation}

.content-box-green[**Estimate Site-specific EONR**]

\begin{equation}
\widehat{N}^{opt}_i =\underset{\mathrm{N}}{argMax}(P_{C} \cdot \widehat{y}_{i}(N) - P_N \cdot N) 
\end{equation}

---

# Estimating EONR with CF: .content-box-purple[**Training phase**]

.content-box-green[**Setup**]
+ CF identifies heterogeneous treatment effects of N rates on yield based on the field characteristics
$$\widehat{\tau}_{N^{con} \rightarrow N^{tre}}(\mathbf{c_i})=E[Y_i(N^{tre})-Y_i(N^{con})|\mathbf{c_i}]$$
  - $Y_i(N^{tre})$, $Y_i(N^{con})$: potential yield outcomes
  - $\mathbf{c_i}$: site-specific field characteristics

+ N application rates: $N_1,N_2,N_3,N_4,N_5$, where $N_1<N_2<...<N_5$
<br />

.content-box-green[**Two approaches for estimating site-specific EONR with CF**]

Approach 1: `CF-stepwise`
+ $(N^{con},N^{tre}) \in \{(N_1, N_2),(N_2, N_3),(N_3, N_4),(N_4, N_5)\}$
+ $\widehat{\tau}_{N_1 \rightarrow N_2}(\mathbf{c_i}), \widehat{\tau}_{N_2 \rightarrow N_3}(\mathbf{c_i}), \widehat{\tau}_{N_3 \rightarrow N_4}(\mathbf{c_i}), \widehat{\tau}_{N_4 \rightarrow N_5}(\mathbf{c_i})$

Approach 2: `CF-base`
+ $(N^{con},N^{tre}) \in \{(N_1, N_2),(N_1, N_3),(N_1, N_4),(N_1, N_5)\}$
+ $\widehat{\tau}_{N_1 \rightarrow N_2}(\mathbf{c_i}), \widehat{\tau}_{N_1 \rightarrow N_3}(\mathbf{c_i}), \widehat{\tau}_{N_1 \rightarrow N_4}(\mathbf{c_i}), \widehat{\tau}_{N_1 \rightarrow N_5}(\mathbf{c_i})$

---

# Estimating EONR with CF: .content-box-purple[**Prediction phase**]

.content-box-green[**Predict *change* in yield**]
+ Let $\Delta Y_{N_1 \rightarrow N_m}(\mathbf{c_{i}})$ be the .red[*change*] in yields going from  $N_1$ to $N_m$ $(m\in\{1,2,3,4,5\})$ for some site $i$
  + when $m=1$, $\Delta Y_{N_1 \rightarrow N_1}(\mathbf{c_{i}})=0$

  `CF-stepwise`
+ $\Delta Y_{N_1 \rightarrow N_m}(\mathbf{c_{i}}) = \sum_{k=1}^{m-1} \widehat{\tau}_{N_{k} \rightarrow N_{k+1}}(\mathbf{c_{i}})$
  + For example, $\Delta Y_{N_1 \rightarrow N_3}(\mathbf{c_{i}}) = \widehat{\tau}_{N_1 \rightarrow N_2}(\mathbf{c_i}) + \widehat{\tau}_{N_2 \rightarrow N_3}(\mathbf{c_i})$

  `CF-base`
+ $\Delta Y_{N_1 \rightarrow N_m}(\mathbf{c_{i}}) = \widehat{\tau}_{N_{1} \rightarrow N_{m}}(\mathbf{c_{i}})$
  + For example, $\Delta Y_{N_1 \rightarrow N_3}(\mathbf{c_{i}}) = \widehat{\tau}_{N_1 \rightarrow N_3}(\mathbf{c_i})$

.content-box-green[**Estimate Site-specific EONR**]
+ Find the N rate that leads to maximum .red[*change*] in profit relative to the least N rate, site-specifically
$$\widehat{N}^{opt}_i =\underset{\mathrm{N \in \{N_1,N_2,N_3,N_4,N_5\}}}{argMax}(P_c \cdot\Delta Y_{N_1 \rightarrow N}(\mathbf{c_{i}}) - P_N \cdot (N - N_1))$$

---

# Flow of Entire Simulation

```{r, echo=FALSE,  out.width = "700px", fig.cap="Figure: Flow Chart of Entire Simulation"}
knitr::include_graphics(here("Writing","Presentation", "Flow_chart_all.png"))
```

---

# Results
.left5[
<br>
<br>
```{r, echo=FALSE, out.width = "500px", tab.cap="Table: Mean R-squared of Esimated site-specific EONR by Each ML Approach "}
table_res400_summary_type1
```
]

.right5[
```{r, echo=FALSE, out.width = "550px", fig.cap = "Figure: Density plots of R-squared of Estimated site-specific EONR by Each ML Approach "}
dist_case
```
]

---

# Discussions
.content-box-purple[The difference in the performance of treatment effect estimations between CF-stepwise and CF-base]
.left5[
+ Check how accurately CF-stepwise and CF-base estimate heterogeneous treatment effects 
  + Conduct the 1000 rounds of simulation using the same data we used before
  + Calculate R-squared of the estimated treatment effects 
]

.right5[
```{r, echo=FALSE, tab.cap="Table: Mean R-squared of Estimated Treatment Effects by CF-stepwise and CF-base "}
te_res_summary
```
]

---

# Discussions
.content-box-purple[The difference in the performance of treatment effect estimations between CF-stepwise and CF-base]
.left5[
+ Check how accurately CF-stepwise and CF-base estimate heterogeneous treatment effects with "aby" modeling scenario
  + Conduct the 1000 rounds of simulation using the same data we used before
  + Calculate R-squared of the estimated treatment effects

.content-box-purple[Results]

+ The performance of CF-stepwise in estimating treatment effects gets worse as N treatment rates increases.
+ The performance of CF-base gets better as N treatment rates increases.
]

.right5[
```{r, echo=FALSE, tab.cap="Table: Mean R-squared of Estimated Treatment Effects by CF-stepwise and CF-base "}
te_res_summary
```
]

---

# Discussions
.content-box-purple[The difference in the treatment effects estimation approach between CF-stepwise and CF-base]

.left5[
```{r, echo=FALSE, fig.cap="Figure: An Illustrative Example of CF-stepwiese Approach for Treatment Effect Estimation "}
sample_MB_curve_step
```
]

.right5[
```{r, echo=FALSE, fig.cap = "Figure: An Illustrative Example of CF-base Approach for Treatment Effect Estimation "}
sample_MB_curve_base
```
]

---

# Discussions
.content-box-purple[CF-stepwise]
.left5[

]

.right5[
```{r, echo=FALSE, fig.cap = "Figure: Illustrative Example Distributions of True and Estimated Treatment Effects under CF-stepwise Approach(Case: aby)"}
cf_step
```
]

---

# Discussions
.content-box-purple[CF-base]
.left5[

]

.right5[
```{r, echo=FALSE, fig.cap = "Illustrative Example Distributions of True and Estimated Treatment Effects under CF-stepwise Approach(Case: aby)"}
cf_base
```
]

---

# References

```{r, results='asis', echo=FALSE}
PrintBibliography(bib)
```

### 2022-02-05 Writing/Re_JournalSubmission/ML_VRA_format_v2.rmd
initial submission

---
title: "Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation"
author: Shunkei Kakimoto^[Corresponding author, Department of Agricultural Economics, University of Nebraska-Lincoln 102 Filley Hall 1625 Arbor Drive Lincoln, NE 68583, USA, E-mail address; skakimoto3@hunskers.unl.edu], Taro Mieno^[Department of Agricultural Economics, University of Nebraska-Lincoln, Lincoln, NE 68583, USA], Takashi S. T. Tanaka^[Artificial Intelligence Advanced Research Center, Faculty of Applied Biological Sciences, Gifu University, Gifu 501-1193, Japan], and David S. Bullock^[Department of Agricultural and Consumer Economics, University of Illinois, Urbana, IL 61801, USA]
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: yes
    global_numbering: true
    # reference_docx: word_template.docx
    reference_docx: word_template_format.docx
    # pandoc_args: ["-Fpandoc-crossref"]
bibliography: ML_VRA.bib
csl: computers-and-electronics-in-agriculture.csl
eqnPrefix: 
      - "Eq"
abstract: "Estimating site-specific crop yield response to changes in input (e.g., seed, fertilizer) management is a critical step in making economically optimal site-specific input recommendations. Past studies have attempted to estimate yield response functions using various Machine Learning (ML) methods, including the Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN) methods. This study proposes use of the Causal Forest (CF) model, which is one of the emerging ML methods that comprise \"Causal Machine Learning.\" Unlike previous prediction-oriented ML methods, CF focuses strictly on estimating heterogeneous treatment effects of inputs, rather than predicting yield. We report results of using Monte Carlo simulations assuming various production scenarios to test the effectiveness of CF in estimating site-specific economically optimal nitrogen rates (EONRs), comparing CF with the yield-prediction-oriented ML methods RF, BRF, and CNN. CF's estimations of site-specific EONRs were superior under all scenarios considered. Furthermore, we also show that the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions."  
---

```{r echo = F, results='hide', message=FALSE}
library(knitr)
# library(here)

# opts_knit$set(root.dir = here())
opts_knit$set(root.dir = "~/Dropbox/ResearchProject/ML_VRA")

options(htmltools.dir.version = FALSE)
options(knitr.duplicate.label = "allow")

opts_chunk$set(
  fig.align = "center", 
  fig.retina = 5,
  warning = F, 
  message = F,
  cache = FALSE, # <-- T
  cache.lazy = FALSE,
  echo = F
  )
```

```{r, cache = FALSE}
# === packages ===#
library(sf)
library(png)
library(data.table)
library(grf)
library(RColorBrewer)
library(patchwork)
library(plotly)
library(magrittr)
library(ggplot2)
library(viridis)
library(tmap)
library(tidyverse)
library(ggthemes)
library(mgcv)
library(ggpubr)
library(flextable)
library(officer)
library(officedown)
library(modelsummary)
library(raster)
library(bookdown)
library(png)
library(grid)
```

```{r analyses, results = "hide", fig.show='hide', cache = FALSE}
#/*=================================================*/
#' # Preparation
#/*=================================================*/
# This is where you prepare data sets and results 
# library(here)
# setwd(here())
#/*----------------------------------*/
#' ## Create figures and tablesb
#/*----------------------------------*/
# --- Convert an Rmd file into a pure R file using purl() ---#
knitr::purl("./GitControlled/Codes/PrepareResults.Rmd", output = "./GitControlled/Codes/PrepareResults.R")

# --- Read the simulation results and prepare figures and tables ---#
source("./GitControlled/Codes/PrepareResults.R")
```

# Keywords: {-}

site-specific input management, nitrogen rate, on-farm precision experimentation, machine learning, causal forest, economically optimal input rates

# Introduction

Despite the potential economic and environmental benefits of site-specific input (e.g., nitrogen (N), seed) management, the adoption rate of variable rate application technology remains relatively low [@lowenberg2019setting]. 
This is primarily because of the difficulty in estimating site-specific yield response functions accurately within a field, which is critical for the identification of site-specific economically optimal input rates (EOIRs) [@bullock1998does].

Historically, site-specific yield response functions have been estimated using the data generated from strip trials conducted on only parts of fields [@makowski2001statistical; @scharf2002corn; @bullock2002adding; @mamo2003spatial; @hurley2004estimating; @anselin2004spatial; @scharf2005field; @ruffo2006site; @Miao2006; @puntel2019development].
But recently whole-field on-farm precision experimentation (OFPE) [@bullock2019] has allowed implementation of improved statistical experimental designs (e.g., Latin Square, Randomized Block) are used for an entire field [@laurent_kyveryga_makowski_miguez_2019; @licht_witt_2019]. Data generated from whole-field OFPEs typically have greater local variation in experimental input application rates and soil/field characteristics than do strip trial designs, which has improved the statistical identification of heterogeneous impacts of input management changes on yields. The resultant availability of more spatially detailed experiment data has encouraged a resurgence of interest in estimating site-specific yield response functions. For example, @barbosa2020modeling, @krause2020random and @Gardner21 used OFPE data to estimate site-specific yield response functions and economically optimal site-specific N fertilizer and/or seed rates. These recent studies used machine learning (ML) methods extensively in place of more traditional parametric modeling approaches. @barbosa2020modeling applied the Convolutional Neural Network approach, @krause2020random used Random Forest-based approaches, and @Gardner21 used the shape-constrained generalized additive model. But this trend of applying ML methods may raise concerns. Historically, agronomy is a field that has paid meticulous attention to identifying the "causal" impacts of input management on yield through clever experimental designs. But the aforementioned recent applications of ML methodologies pay little attention to causal identification of inputs on yield, instead validating their models by yield prediction accuracy. But the ultimate goal of OFPE is the accurate prediction of EOIRs, not yields. These are distinct objectives, and achievement of one need not imply the other.

The lack of and need for causal interpretation of the results of ML research applications have been increasingly recognized, in particular in economics and medicine [@athey2017beyond; @athey2018impact; @Athey2019a; @moraffah2020causal; @Storm2020; @arti2020research; @scholkopf2021toward]. In response, causal machine learning (CML) methods were recently developed. Unlike traditional prediction-oriented ML methods, CML focuses on identifying causal impacts of an event (in our context, an increase or decrease in the input application rate). The growing academic literature applying CML methods includes @richens2020improving, who pointed out that the inability of the traditional ML methods to identify cause and effect relationships between disease and patients' characteristics could lead to misdiagnoses, and showed that CML-based diagnoses could improve the accuracy of diagnostic prediction. In addition, @carbo2020machine used a CML to identify characteristics causing bank customers to adopt online banking services, and @bozorgi2020process applied CML to study the mining processes.

In this paper, we test the accuracy of site-specific economically optimal N fertilization rates (EONRs) estimation based on Causal Forest (CF) approach developed by @athey2016recursive and @Wager2018a. We compare the EONR prediction performances of our CF-based approach to the widely used ML methods Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN). Further, we also test how yield prediction performance is related to EONR prediction performance to examine whether it is appropriate to select the model based on its ability to predict yield when the ultimate goal is to identify EOIR. We use Monte Carlo simulations, where we synthetically generate yield and soil/field characteristics datasets for a stylized "field." Because real-world "true" EOIRs cannot be measured, real-world data cannot be used to test the accuracy of statistical methods estimating EOIRs. This important difference contrasts starkly with yield prediction, since actual yields can be ground-truthed.

<!-- Our simulation results reveal that CF-based approaches provide superior performance in site-specific EOIR estimation. We also demonstrate that a method's yeidl prediction accuracy is not a good indicator of its EOIR estimation accuracy. -->

# Predicting Yield vs. Predicting Changes in Yield in Response to Changes in Input Management

In the following, we describe the fundamental information necessary to identify EOIR in general: the site-specific treatment effect of input application on yield. We then discuss the causal forest method in detail, show how it is particularly suitable to obtain this fundamental information, and contrast it to more traditional prediction-oriented ML methods, such as RF, BRF, and CNN.

## A Simple Profit-maximization Problem

Let $p$ be the price that a producer receives for a unit of a crop, $w$ be the per-unit price paid for a unit of an input, $OC$ represent other costs of production, and $y=f(I, \mathbf{c})$ describe the relationship between crop yield, the input application rate $I$ and a vector of field characteristics variables $\mathbf{c}$. A simple model of producer behavior assumes that the producer chooses a level of $I$ to maximize profits (revenues minus costs):

\begin{equation}
\max_{I} \quad pf(I, \mathbf{c}) - wI -OC. (\#eq:eqn1)
\end{equation}

Elementary calculus shows that the necessary condition for maximization is, that $\partial f(I, \mathbf{c})/\partial I - w =0$, which implicitly defines the economically optimal input application rate as a function of prices and soil/field characteristics, and may be arranged as \@ref(eq:eqn2):

\begin{equation}
\frac{\partial f(I^{*}(p,w,\mathbf{c}), \mathbf{c})}{\partial I} \equiv \frac{w}{p}. (\#eq:eqn2)
\end{equation}

Identity \@ref(eq:eqn2) states that the necessary elements of the information needed for profit maximization are the input price, the output price, and the partial derivative of the yield function with respect to the input. While knowledge of the yield function $f(I, \mathbf{c})$ in Eq. \@ref(eq:eqn1)) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the function's partial derivative is necessary.  In the following, we discuss a method of using Causal Forest methods that can provide statistical advantages to the estimation of economically optimal input application rates because it is built to estimate approximations of the derivative $\partial f/\partial I$ directly, and not the yield function $f$ itself.

## Estimating EOIR and Treatment Effects

Recent papers using ML methods to estimate the effectiveness of various agricultural input management strategies have based their analyses on estimates of a yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21). In the following, we present a Causal Forest methodology that does not rely on estimation of how the level of yield depends on the input application rate $I$, but rather relies on a discrete version of Eq. \@ref(eq:eqn2), examining the discrete changes in yield that result from discrete *changes* in the input application rate $I$.

Consider an increasing ordering of input application rates $I_1, I_2,...,I_K$. Among these K rates, for a generic site $i$ a specific EOIR can be identified if the *treatment effect* function $\Delta y_i(I_{k+1}, I_{k})$ is known. This function is defined as the discrete change in yield that results from a discrete change in the input level from $I_k$ to $I_{k+1}$, and it depends on the characteristics at the site analyzed:

$$
\Delta y_i(I_{k+1}, I_{k}) = f(I_{k+1}, \mathbf{c_i}) - f(I_{k}; \mathbf{c_i}) \quad ^\forall k = 1, \dots , K - 1
$$

Once treatment effects $\Delta y_i(I_{k+1}, I_{k})$ have been identified for every $k$, economic analysis can be conduced to identify the EOIR for site $i$. The profit change from increasing the input rate from $I_{1}$ to $I_{k}$ is

$$
P_c (\sum_1^{k-1} \Delta y_i(I_{k+1}, I_{k})) - P_I \times (I_k - I_0).
$$

The EOIR is the value $I_k$ that maximizes the profit gain "relative" to profits from $I_1$. ($I_1$ may be the EOIR if no other rates surpass the profit of $I_1$.)

## Causal Forest

CF was developed specifically for identifying heterogeneous treatment effects [@athey2016recursive; @Wager2018a]. Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf. Figure \@ref(fig:ct-ex) shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$)($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact. 
In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example.

```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
# knitr::include_graphics("./GitControlled/Writing/Re_JournalSubmission/ctree_ex.pdf")
readPNG("./GitControlled/Writing/Re_JournalSubmission/ctree_ex.png") %>% grid.raster()
```

`r ftext('NOTE: The first number in each node indicates the predicted treatment effects (in kg/ha). The number and the percentage of observations belonging to the node are shown below that.', fp_text(font.size = 9))`

The first data split criterion is whether the $\textit{ecs}$ value is greater or less than $25$. The observations with $\textit{ecs}$ greater than or equal to $25$ move to the left node, while those with $\textit{ecs}$ less than $25$ move to the right. For each of the subsamples, the treatment effect is identified as the difference in the mean yields of the treated and control groups within the subsample. The treatment effect for the low-$\textit{ecs}$ observations was $619$ kg/ha, and for the high-$\textit{ecs}$ observations was $982$ kg/ha. This means that for the impact of the increase in seed rate the treatment effect is heterogeneous over space, having a larger positive impact on yield in high-$\textit{ecs}$ areas. Trees are further developed to have more groups of subsamples to allow for more flexible representations of the heterogeneous treatment effects. The estimated CF model does not predict yield level at any site $i$ in the field, but rather estimates site-specific EOIRs by estimating treatment effects. Since CF is designed to estimate the causal effect of an input directly, it may be suspected that CF will outperform other ML methods that identify EOIR indirectly through yield prediction.

While both RF and CF build trees by recursively partitioning samples, they differ critically in their criteria for splitting. In RF, the sample is split to minimize the mean squared error (MSE) of yield prediction in building trees. Unfortunately, the MSE of treatment effect predictions is not useful for building a CT since the true treatment effects are never observable. However, @athey2016recursive showed that minimizing the expected MSE of the treatment effect is equivalent to maximizing the variance of treatment effects across the resulting two leaves and minimizing the within-leaf variance. Consequently, by splitting samples in a way that maximizes the variance of treatment effects across the resulting two leaves, CF overcomes the fundamental problem created by the unobservability of true treatment effects. CF requires that the tree-building process is "honest" for treatment effects estimation to be unbiased. Honest tree-building first randomly splits in two the training data samples, then uses one of the subsamples to determine how to split the tree, and uses the other to estimate the treatment effects [@athey2016recursive; @Wager2018a]. This honest subsampling technique avoids overestimation of the heterogeneity of estimated treatment effects. Since CF splits samples to maximize the heterogeneity of estimated treatment effects, using the same sample for both the sample splitting and treatment effect calculations renders itself sensitive to noise or outliers, allowing high noise levels to exaggerate the treatment effects.

## CF vs. Prediction-oriented ML methods

Whether the indirect (yield-prediction-first) and direct approach is used can lead to meaningful statistical differences when it comes to EOIR estimation. The conventional prediction-oriented ML methods are designed to predict yield, $y_i(I,\mathbf{c})$, well, but not necessarily treatment effects. Since the loss function used in prediction-oriented ML uses (typically squared) residuals in yield prediction, prediction-oriented ML is naturally optimized for predicting the "level" of yield instead of identifying the causal impact of the input. CF, on the other hand, is designed specifically to estimate the causal impact of input. Indeed, @Wager2018a used Monte Carlo simulations to show that CF provided more accurate estimates of heterogeneous treatment effects than those provided by RF. However, the underlying data generating process of their simulations was extremely simple, with the treatment effect influenced by only a single variable. CF has never been tested for more complicated data generating processes, such as those represented by yield response functions in which the treatment effect of an input can be affected by multiple variables in a non-linear fashion. Moreover, CF has never been compared to more advanced ML methods such as BRF and CNN that are considered to have prediction capabilities greater than RF's. The study reported here builds on @Wager2018a to compare CF to these prediction-oriented ML methods (not just RF, but also BRF and CNN) in more realistic agronomic experiment settings.

# Materials and Methods

Monte Carlo simulations were conducted for nitrogen experiments for corn production to estimate the economically optimal nitrogen rate (EONR). The first step in our simulation was to generate one thousand synthetic fields that "resembled" an actual field. <span style="color:red"> After generating one thousand synthetic fields, we repeated to evaluate each of the ML methods by one thousand times. In an individual simulation round, one of the fields was used as a training data set. As a validation data set, a different field from a training data set in that simulation round was used.</span> <!-- For each simulated field, we generated a training data set and a validation data set. --> Field characteristics and yield were simulated based on the Mitscherlich-Baule (MB) yield response function. We used the RF, BRF, and CNN ML methods to estimate yield response functions, and we used the CF method to estimate treatment effects. For each method, we estimated site-specific EONRs using the training data set, and checked the statistical performance of the predicted site-specific EONR using the validation data set. Detailed descriptions of these steps are provided below. The R codes that implement the simulation analyses are available at https://github.com/tmieno2/ML_VRA.git.

## Data Generation

### Simulated Experimental Fields
<!-- experimental field: area: 51ha, plot: 384, subplot:1536, cell:55296   -->

The simulated field was created based on an actual 51-ha Illinois field on which the Data-Intensive Farm Management (DIFM) project [@bullock2019] has run multiple OFPEs. Figure \@ref(fig:field-map) illustrates that simulated trials consisted of $384$ <span style="color:red"> 18-m </span> $\times$ <span style="color:red"> 73-m </span> "plots," each of which was assigned an N fertilizer application rate. Each plot was made up of four (4-rows $\times$ 1-column) "subplots," which were unit of analysis used in subsequent statistical analysis. Each subplot contained of a 6-rows $\times$ 6-columns grid of thirty-six <span style="color:red"> 3-m </span> $\times$ <span style="color:red"> 3-m </span> "cells." All field characteristics and yield data were generated at the cell level.

```{r field-map, fig.width=4, fig.height=3, fig.cap = "Division of field: plots, subplots and cells"}
# knitr::include_graphics("./GitControlled/Writing/Re_JournalSubmission/field_devision_v2.png")
readPNG("./GitControlled/Writing/Re_JournalSubmission/field_devision_v2.png") %>% grid.raster()
```

### Underlying Yield Response Function

We modeled the yield response function as having the following Mitscherlich-Baule functional form:

\begin{equation}
f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) N)) + \varepsilon. (\#eq:eqn3)
\end{equation}

The first term on the right-hand side of Eq. \@ref(eq:eqn3) is the deterministic yield component, which was generated assuming the commonly-used MB functional form, which is flexible in its shape, allows for the existence of a yield plateau, and has been shown to be a plausible specification for N fertilization models for corn [@frank1990; @llewelyn1997; @paris1992].
The variable $N$ in Eq. \@ref(eq:eqn3) represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot. Also in Eq. \@ref(eq:eqn3), $\alpha$, $\beta$, and $ymax$ are functions of a vector of field characteristics variables $\mathbf{c}=(c_1,...,c_K)$, which vary spatially on the field. For example, $\alpha$ and $ymax$, which affect yield independently from the applied N fertilizer rate, might be interpreted as depending on the ingredient soil N content supplied by residual N, soil organic matter, etc. $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen]. The error term of the yield $\varepsilon$ represents the composite of all the unobserved factors that affect crop yield beyond $\alpha$, $\beta$, $ymax$ and $N$.

A fictional "researcher" is modeled as having limited knowledge about which variables make up $\mathbf{c}$, or even the number of elements of $\mathbf{c}$, and has limited ability to measure the values that many of the variables that constitute $\mathbf{c}$ take on across the field. The researcher is also assumed to not know the functional forms of the yield response function.

### Cell-specific Yield Functions and Economically Optimal N Rates

Let $i \in \{1,2,...,1536\}$ index a simulated field's subplots and $j \in \{1,2,...,36\}$ index cells within a subplot. Let $N^{i}$ be the N fertilization rate on plot $i$, and let $\mathbf{c}^{i,j}$ be the value of $\mathbf{c}$ on cell $(i,j)$, Eq. \@ref(eq:eqn4) shows the yield level on cell $j$ in subplot $i$ is affected by the N rate applied on subplot $i$:

\begin{equation}
f(N^{i}, \mathbf{c}^{i,j}) = ymax(\mathbf{c}^{i,j})(1-exp(\alpha(\mathbf{c}^{i,j}) + \beta(\mathbf{c}^{i,j}) N^{i})) + \varepsilon^{i,j}. (\#eq:eqn4)
\end{equation}

To simplify notation, denote  $\alpha(\mathbf{c}^{i,j})$ as $\alpha^{i,j}$, $\beta(\mathbf{c}^{i,j})$ as $\beta^{i,j}$, and $ymax(\mathbf{c}^{i,j})$ as $ymax^{i,j}$. Then, a cell-specific yield function can be written as,

\begin{equation}
f^{i,j}(N) = ymax^{i,j}(1-exp(\alpha^{i,j} + \beta^{i,j} N^{i})) + \varepsilon^{i,j}. (\#eq:eqn5)
\end{equation}

Parameters $\alpha^{i,j}$, $\beta^{i,j}$, $\beta^{i,j}$, and $\varepsilon^{i,j}$ were modeled as spatially autocorrelated using unconditional Gaussian geostatistical simulation based on the spherical variogram model. The `gstat` package (version 2.0.6 [@gstat1; @gstat2]) in R was used for this purpose. Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha^{i,j}$, $\beta^{i,j}$, $ymax^{i,j}$, and $\varepsilon^{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project (Codes used to generate parameter values are available at https://github.com/tmieno2/ML_VRA.git.) Figure \@ref(fig:fig-parameters) shows an example of the generated parameters.

<br>

```{r variogram-parameters, tab.cap = "The parameters for the variogram modeling"}
variogram_tb
```

<br>

```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An illustrative example of spatial distributions of field characteristics"}
# field_alpha + field_beta + field_ymax
grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2, nrow=2)
```

Each cell $(i,j)$'s "true" optimal N application rate, denoted $N_{opt}^{i,j}$, was calculated by solving a profit maximization problem:

\begin{equation}
N_{opt}^{i,j} = \operatorname*{argmax}_{N}(P_{C} f^{i,j}(N) - P_N N), (\#eq:eqn6)
\end{equation}

where, $P_{C}=\$0.138/kg$ and $P_{N}=\$1.323/kg$ were the assumed prices of the corn and N fertilizer. Figure \@ref(fig:fig-optN) maps an example of the identified "true" cell-specific optimal N rates.

```{r fig-optN, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a spatial distribution of true optimal N rate"}
vis_optN_cell
```

<br>

### Trial Design

In each simulation round, five field-trial N rates were determined based on the range of the round's cell-specific EONRs. 
Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percent quantile of the round's cell-specific EONRs. Then, the five trial design rates were

$$
\begin{aligned}
N_1 &= Q_{0.05} - 20 \\
N_5 &= Q_{0.95} + 20 \\
N_2 &= N_1 + 0.25(N_5 - N_1) \\
N_3 &= N_1 + 0.50(N_5 - N_1) \\
N_4 &= N_1 + 0.75(N_5 - N_1)
\end{aligned}
$$

In each round, a Latin square design was followed to assign each plot one of the five N rates so established. Figure \@ref(fig:fig-nExp) shows an example of a trial design.

```{r fig-nExp, fig.width=3, fig.height=4, fig.cap = "An illustrative example of experimental design of N"}
field_Ndesign
```

Under this design, the N rate was orthogonal to the error term. This is important because if they were correlated, bias in the estimation of the impact of nitrogen on yield would be introduced for all of the ML methods. Since the treatment effect at each leaf is obtained simply by taking the difference of the average value of the dependent variable between the control and treated group within the leaf, CF requires the exogeneity of the treatment conditional on the independent variables to estimate the treatment effect consistently. Note that the violation of this condition leads to biased estimation for not just CF and the other ML methods, as well.

### Yield Data Generation and Aggregation

A cell-level data set for the whole field, $\{(y^{i,j}, N_{opt}^{i,j}, N^{i,j}, \mathbf{c}^{i,j}): i \in \{1,2,...,1536\}, j \in \{1,2,...,36\}\}$ was generated. For a generic cell $(i,j)$, yield $y^{i,j}$ was generated through Eq. \@ref(eq:eqn3), applying parameter values $\mathbf{c^{i,j}}=(\alpha^{i,j}, \beta^{i,j}, ymax^{i,j})$, the disturbance term level $\varepsilon^{i,j}$, and the cell's assigned experimental N rate, $N^{i,j}$ (Figure \@ref(fig:field-yield-cell)).

```{r field-yield-cell, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a yield distribution map at the cell resolution"}
vis_yield_cell
```

<br>

These were aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation. The subplot data were therefore

$$
\{(y^{i}, N_{opt}^{i}, N^{i}, \mathbf{c}^{i}) = \frac{1}{36}\sum_{j=1}^{36} (y^{i,j}, N_{opt}^{i,j}, N^{i,j}, \mathbf{c}^{i,j}): i \in \{1,2,...,1536\}\}
$$

Figure \@ref(fig:field-yield-subplot) shows an example of observed yield data. Note that data generation at the cell level was conducted to reflect the real-world spatial heterogeneity in soil/field characteristics within the subplot level. But data aggregation to the subplot level was conducted because the large sizes of harvesters make it impossible to monitor yields accurately at smaller scales.

```{r field-yield-subplot, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a yield distribution map at the subplot resolution"}
vis_yield_subplot
```

<br>

### Modeling Scenarios

To evaluate the performances of RF, BRF, CNN and CF, we examined four modeling scenarios, each defined by a dataset assumed to be available to the researcher. The first modeling scenario, denoted "aby" assumed that researchers have a dataset of the actual values $\alpha^{i,j}$, $\beta{i,j}$, $ymax^{i,j}$ for every cell $(i,j)$ and use $\alpha$, $\beta$ and $ymax$ as covariates in their ML models. This scenario represents an ideal situation for researchers, in which all the relevant variables are observed, but the true functional form of heterogeneous yield response functions are not known. More realistic scenarios can be compared with this ideal scenario.

In subsequent modeling scenarios, we made the simulated experimental data more realistic by varying the degree to which researchers understood what the needed covariates' values were those in the data set. In the second scenario, denoted "abytt," we introduced additional variables $\theta_1$ and $\theta_2$, and the researcher's dataset contained values of $\alpha^{i}$, $\beta^{i}$, $ymax^{i}$, $\theta_1^{i}$ and $\theta_2^{i}$ for all subplots $i=1,...,1536$. $\theta_1$ and $\theta_2$ had no effect on yield, but their cell-level values were spatially correlated with $\beta^{i,j}$, and so their subplot-level values were correlated with $\beta^{i}$. This scenario is meant to reflect the lack of scientific consensus about which variables explain heterogeneous yield response to N, making it likely that researchers include irrelevant variables like $\theta_1$ and $\theta_2$ in real-world data analysis.

In the third scenario, denoted "aabbyy," the researcher's dataset did not contain values of $\alpha^{i}$, $\beta^{i}$, or $ymax^{i}$. Rather, it contained subplot-level values of permutations of $\alpha$, $\beta$, and $ymax$. Specifically, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r_{\alpha}^{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r_{\beta}^{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r_{ymax}^{i,j} \in (0,1)$ to the ${ymax}^{i,j}$ variable. (There was no spatial correlation between the $r_{\alpha}^{i,j}$ and $r_{\beta}^{i,j}$ data, between $r_{\alpha}^{i,j}$ and $r_{ymax}^{i,j}$ data, or between $r_{\beta}^{i,j}$ and $r_{ymax}^{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha^{i,j}$, $\beta^{i,j}$ and $ymax^{i,j}$. 
These were 
$\alpha_{1}^{i,j} = r_{\alpha}^{i,j} \alpha^{i,j}$, $\alpha_{2}^{i,j} = (1- r_{\alpha}^{i,j}) \alpha^{i,j}$,
$\beta_{1}^{i,j} = r_{\beta}^{i,j} \beta^{i,j}$, $\beta_{2}^{i,j} = (1- r_{\beta}^{i,j}) \beta^{i,j}$,
$ymax_{1}^{i,j} = r_{ymax}^{i,j} ymax^{i,j}$, and $ymax_{2}^{i,j} = (1- r_{ymax}^{i,j}) ymax^{i,j}$.
For each $\alpha$, $\beta$ and $ymax$, these procedures created two new covariates that were highly spatially autocorrelated with the original covariate, which was meant to reflect that many of the soil/field characteristics used to analyze OFPE data are spatially correlated. The values of $\alpha^{i,j}$, $\beta^{i,j}$ and $ymax^{i,j}$ did not indicate specific soil or field characteristics, but were functions of such. In reality, scientists cannot directly observe variables that can accurately predict yield plateau level, soil N content and N uptake efficiency. Rather, they use multiple observed soil/field characteristics to explain such phenological phenomena. For example, instead of using $ymax^{i,j}$ directly, some topographical land features and soil properties such as elevation and soil sand content could be used as yield-limiting factors [@jiang2004effect; @kravchenko2000correlation]. In reality, scientists may include more than three variables as covariates. This scenario should reduce the accuracy of EONR modeling for all the models compared to the ideal case.

The fourth scenario, denoted "aabbyytt," had the same components as aabbyy, but also included the $\theta_1$ and $\theta_2$ covariates.

## Training Models and and Estimating Site-specific EONRs

### RF, BRF, and CNN

The RF, BRF, and CNN methods followed the same conceptual steps to estimate site-specific EONR: 1) estimate the yield production functions and 2) calculate site-specific EONRs based on that estimated function. For the given modeling scenario, RF and BRF predict yield by using all the available covariates as explanatory variables in the estimation process. The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for RF and BRF modeling.

CNN leaves room for researchers to determine its architecture. In this article, a slightly modified version  of one of the multi-stream CNN architectures proposed by @barbosa2020modeling, called "Late Fusion," was used. Briefly stated, explanatory variables except N rate (e.g. $\alpha^{i,j}$, $\beta^{i,j}$, etc.) enter the model as a set of $6 \times 6$ element rasters. On the other hand, the input size of the N rate is treated as $1 \times 1$ because it is spatially homogeneous within each subplot. First, each input was connected to an independent convolutional layer with eight $3 \times 3$ filters each with stride one, followed by a $2 \times 2$ max-pooling layer with stride two. Then, a fully-connected rectified linear unit (ReLU) layer with sixteen neurons was added after each max-pooling layer, followed by a single ReLU neuron. Finally, multiple neurons were concatenated and fed to the fully-connected ReLU layer with sixteen neurons, followed by an output with a linear activation function. @barbosa2020modeling demonstrated that among several CNN architectures, this architecture modeled crop yield response to N rate management best. CNN was implemented in Python v3.7.6 using Pytorch v1.7.0 [@paszke2017automatic]. The Adam optimizer [@kingma2014adam] was used with a learning rate of $0.001 \%$ (default value). To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience.

Let $\mathbf{\Omega^{i}}$ denote a list of subplot-level explanatory variables (soil/field characteristics). Further, let $\hat{g}_m(N,\mathbf{\Omega})$ denote an estimated yield response function, estimated by model $m$ ($m$ = RF, BRF, or CNN). Then, yield at $i$ from model $m$ is $\hat{g}_m(N,\mathbf{\Omega^{i}})$. The site-specific EONR for each model can then be found by solving the following profit maximization problem for all $i$ for each of the models:

$$
\hat{N}_{opt}^{i} = \operatorname*{argmax}_{N}(P_{C} \hat{g}_m(N,\mathbf{\Omega^{i}}) - P_N N) 
$$

where $P_C$ and $P_N$ are the prices of corn and N.

### CF

Unlike RF, BRF, and CNN, CF estimates the impact of a binary treatment. 
In our context, CF estimates changes in yields (i.e., $\hat{\tau}_{N^{con} \rightarrow N^{tre}}(\mathbf{\Omega^{i}})$) caused by changes in N application rates from one experimental rate (control N rate, i.e., $N^{con}$) to another experimental rate (treatment N rate, i.e., $N^{tre}$). Since we have five N application rates, four "experiments" (treatments) are identified based on four ($N^{con}$, $N^{tre}$) combinations. A possible grouping to make such pairwise N application rate combinations, which we call the "CF-base," used $(N_1, N_2),(N_1, N_3),(N_1, N_4)$, and $(N_1, N_5)$. In this approach, the treatment effect is always estimated against the lowest N rate ($N_1$) as $N^{con}$.

For estimating site-specific EONR, the trained CF-base were used to predict site-specific changes in yields resultant from changes in application rates from $N_1$ to $N_m$ $(m\in\{2,3,4,5\})$. Let $\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}})$ be the the estimated treatment effect of changing subplot $i$'s application rate from $N_1$ to $N_m$ for site $i$.

Since the CF-base approach always estimates the treatment effects using the lowest treatment rate $N_1$, the predicted treatment effects already represents the change in yields from the yield at $N_1$:

$$
\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}}) = \hat{\tau}_{N_{1} \rightarrow N_{m}}(\mathbf{\Omega^{i}})
$$

With the treatment effects from the base obtained, site-specific EONRs were identified by finding the N rate resulting in the highest profit. Yield levels were not predicted at any point in the CF-based approaches.

<!-- We consider two possible groupings to make such pairwise N application rate combinations.  The first grouping approach, which we call the "CF-base", used $(N_1, N_2),(N_1, N_3),(N_1, N_4)$, and $(N_1, N_5)$. In this approach, the treatment effect is always estimated against the lowest N rate ($N_1$) as $N^{con}$. The second grouping approach used $(N_1, N_2),(N_2, N_3),(N_3, N_4)$, and $(N_4, N_5)$. We label this approach as the "CF-stepwise". 
For estimating site-specific EONR, the trained CF-base and CF-stepwise methods were used to make predictions of site-specific changes in yields resultant from changes in application rates from $N_1$ to $N_m$ $(m\in\{2,3,4,5\})$. Let $\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}})$ be the the estimated treatment effect of changing subplot $i$'s application rate from $N_1$ to $N_m$ for site $i$. 
In the CF-stepwise approach, this value can be calculated by sequentially adding the estimated treatment effects: 
$$
\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}}) = \sum_{k=1}^{m-1} \hat{\tau}_{N_{k} \rightarrow N_{k+1}}(\mathbf{\Omega^{i}})
$$
In the CF-base approach, the treatment effects were always estimated using the the lowest treatment rate $N_1$. Therefore, the predicted treatment effects already represent the change in yields from the yield at $N_1$:
$$
\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}}) = \hat{\tau}_{N_{1} \rightarrow N_{m}}(\mathbf{\Omega^{i}})
$$

Once the treatment effects from the base were obtained, site-specific EONRs were identified by finding the N rate that leads to the highest profit. Yield levels were not predicted at any point in the CF-based approaches.  -->

RF, BRF, and CF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving honest tree-building process), and the optimal values for these parameters are selected by cross-validation. In addition to these tuning parameters, we needed to set the number of trees grown in a forest (i.e., *num.trees*). Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same dataset was used. To reduce the variance of predictions, in other words, to stabilize the prediction accuracy, we needed to assign *num.trees* a high value, $4000$.

### Model Evaluation

The accuracy of EONR estimation was judged based RMSE ($kg/ha$) of EONR estimation against the true EONR at the subplot level.
In addition, using the EONR estimates, we also calculated profit-deficit ($\$/ha$) (i.e., $\hat{\pi}_{def}$) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at $N_{opt}^{i}$. For RF, BRF, and CNN, the accuracy of yield prediction was judged based on the RMSE ($kg/ha$) of the yield prediction against the true yields at the subplot level.

# Results and Discussions

## EONR Estimation

Table \@ref(tab:table-optN-subplot-wide) shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the $1000$ simulations; it makes immediately clear that CF-base considerably outperformed the other ML methods, and that the profits based on CF-base's EONR estimates were the closest to the true maximum profits. BRF performed considerably better predicting EONR than did RF.

<br>

```{r table-optN-subplot-wide, tab.cap = "Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML methods and modeling scenarios"}
report_table_optN
# knit_print(report_table_optN)
```

<br>

Interestingly, CNN completely failed in its estimations of site-specific EONRs. This happened because the site-specific yield response functions identified by CNN were linear, and all with the same slope. Therefore, CNN failed to capture a declining marginal product of N. The constant marginal product caused the estimated EONR to take on either the lowest or highest experimental N application rate. To examine whether this problem is a product solely of the specific choice of CNN architecture, we also tested another CNN model, which was analogous to CNN-ST proposed by @barbosa2020modeling. 
This architecture also estimated that yield and N rates were perfectly linearly related, and also estimated site-specific EONR poorly. Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs. In some cases, CNN predicted yield well; but in all cases it predicting EONR poorly.

Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML methods and modeling scenarios, respectively. The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios. 
Interestingly, RF seems particularly vulnerable to the inclusion of more variables, with RMSE ($\hat{\pi}_{def}$) increasing from `r table_optN_prep[Model=="aby",rmse_optN_RF]` (`r table_optN_prep[Model=="aby", pi_loss_RF]`) in the "aby" scenario to `r table_optN_prep[Model=="aabbyytt", rmse_optN_RF]` (`r table_optN_prep[Model=="aabbyytt", pi_loss_RF]`) in the "aabbyytt" scenario. CF-base was more robust to the inclusion of additional variables. Overall, the simulations present CF-base as the clear winner in estimating EONR.

```{r dist-optN, fig.width=6, fig.height=7, fig.cap = "Distributions of RMSE of EONR estimation over simulations"}
plot_dis_optN
```

```{r dist-piLoss, fig.width=6, fig.height=7, fig.cap = "Distributions of profit deficit over simulations"}
piLoss_density
```

<br>

Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions. It plots the estimated treatment effects against true treatment effects by treatment types and ML methods (RF, BRF, and CF-base) under the "aabbyytt" scenario in one of the $1000$ simulations rounds. The figure shows that the estimated treatment effects did not exhibit significant bias, with the points clustered around the red 1-to-1 line. However, they differ substantially in the accuracy of their treatment effect estimations. Points are clustered much more tightly about the 1-to-1 line for CF-base than RF and BRF. That is, CF-base estimates treatment effects much more efficiently than do the RF and BRF methods, which focus on yield prediction rather than treatment effect estimation.

```{r plot-tre, fig.width=7, fig.height=5, fig.cap = "True treatment effects vs estimated treatment effects (scenario: aabbyytt)"}
figure_te
```

`r ftext('NOTE: The red line in the figures denotes the 1-to-1 line to show the ideal relationship between true and estimated treatment effects.', fp_text(font.size = 9))`

## Yield Prediction and EONR Estimation
For RF, BRF and CNN, Figure \@ref(fig:plot-y-optN) plots the RMSE values of EONR estimation against the RMSE values of yield prediction, and the red line shows the best-fit line describing the relationship between them. 
For all the models the regression line was almost flat, showing little if any correlation between the two measures. In other words, the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions.

```{r plot-y-optN, fig.width=7, fig.height=5, fig.cap = "The relationship in the performance between EONR estimation and yield prediction by ML methods and modeling scenarios"}
fig_y_optN
```

`r ftext('NOTE: The red line in the figures denotes the best-fit line to explain the relationship between the RMSEs of EONR prediction and yield prediction.', fp_text(font.size = 9))`

<br>

Table \@ref(tab:table-y-subplot-wide) shows the mean RMSE of yield prediction over the $1000$ simulations. Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN. Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact along with the poor performance of RF in predicting EONR show that strong predictive power of yield levels does not imply accurate prediction of EONR. Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well. While CNN performs worse than RF and BRF in "aby" and "abytt," it performs better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables. Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.

<br>

```{r table-y-subplot-wide, tab.cap = "Mean RMSE of yield prediction (kg/ha) by ML methods and modeling scenarios"}
report_table_y
```

<br>

All previous research has followed a two-step procedure to estimate site-specific EONRs. The first step is to select the model that predicts yield most accurately. The following step is to use that model to predict EONR.
Table \@ref(tab:count-table) shows that following this process led to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds examined here. For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of $1000$ iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations. That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF models best at yield prediction did not provide EONR estimates that led to high profits. Similarly, in all cases, CNN method never provided both the best yield prediction and the best EONR estimation simultaneously. In the rounds in which BRF predicted yield best, then the two-step process worked well. For example, Table \@ref(tab:count-table) shows that in the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which BRF predicted yields best, it offered the best EONR recommendations `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` times. But, BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$.

<br>

```{r count-table, tab.cap = "Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances for prediction-oriented ML methods"}
report_summary_res_CNN_RF_BRF
```

<br>

Virtually all the previous studies have used yield prediction accuracy to rank and select models. This is understandable, since whereas yield can be "ground-truthed" the true causal impact of a treatment cannot be determined from real-world data, making it impossible to cross-validate EONR. 
However, the simulation results reported here show clearly that using a model’s yield prediction accuracy as a model selection criterion is not well justified if the ultimate objective is accurate estimation of site-specific EONRs.

# Conclusion

ML methods are appealing tools that can potentially improve site-specific input rate management by capturing heterogeneous treatment effects introduced by complex non-linear and multidimensional interactions of soil and field characteristics. Many kinds of prediction-oriented ML methods have been used for this purpose. We have introduced the use of CF, a relatively new method, which, unlike prediction-oriented ML methods, focuses on the identification of heterogeneous causal effects of treatment.

We examined the use of CF-base for site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONR to those of the prediction-oriented ML methods RF, BRF, and CNN. CF-base consistently outperformed the other methods across all the modeling scenarios in terms of EOIR prediction and profit generation. We also showed that the model’s yield prediction accuracy was uncorrelated with its EONR prediction accuracy, and so yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to identify EOIR map.

Despite the relatively simple nature of the simulations, results reported provide intriguing evidence of potential advantages of CF over other ML methods when the purpose of the research is to increase the economic efficiency of input management. Of course, the reported research did not model all situations, and further research is needed. First, a drawback of the CF method is that because it does not estimate a continuous yield response function, it can only compare the economic outcomes of a limited set of experimental N rates included in the field trial that provides the data. This raises important questions about trial design. How many distinct experimental input application rates should be included? All the trial designs examined here were based on five N rates. Having examined models with additional rates would have increased the number of possible N rates from which the EONR were selected, but reduced treatment pair replications and so the estimation accuracy.

Second, the size of the field used in the OFPE can affect the relative performances of the competing methods. CF requires honest sampling for its unbiasedness property. Honest sampling comes at the cost of losing prediction accuracy of treatment effects because fewer samples are used to estimate treatment effects within leaves [@athey2016recursive]. Therefore, if the ML analyses are conducted with OFPE data from a small field, CF may not outperform other ML methods

Third, another interesting subject for future research is the potential of combining the ML methods with post-estimation spatial smoothing of the estimated EONR. It is a well known fact that soil/field characteristics are spatially correlated [@f2007methods;@goovaerts1999geostatistics]; this spatial correlation is likely to cause spatial correlation in EONRs, which would suggest that post-estimation spatial smoothing of EONRs may further improve the accuracy of EONR estimation.

Finally, a natural and fruitful extension of the reported research would be to test CF and other ML methods in a dynamic setting where multiple years of experiments are conducted, allowing weather events into the analysis as explanatory variables. Crop simulation models (e.g., APSIM, DSSAT) could be used in place of the Mitscherlich-Baule production function used here to model the underlying yield response function, which could generate more realistic data, using actual soil/field characteristics and weather instead of abstract parameters in the analysis, and so better include the dynamic nature of cropping systems in the study of N management [@archontoulis2020predicting;@puntel2016modeling;@puntel2018systems].

# Acknowledgement

This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled "Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management," (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled "Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation" (Award Number NR213A7500013G021).

\newpage

# References

<div id="refs"></div>

### 2022-02-05 Writing/Re_JournalSubmission/replies_rev_1.Rmd
initial submission

---
title: "Reply to Reviewer #1"
author: 
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
---

# Comments:

**1. The first point of the highlight describes the advantages of the CF model over other machine learning methods. The advantages of the CF model are not suitable for the highlight of this study. Therefore, I suggest that the authors revise the first point of the highlight.**
<span style="color:blue">

</span>

**2. In the second section (lines 76-184), the authors describe the fundamental information necessary to identify EOIR in general and discuss the causal forest approach in detail. The structure of the manuscript is redundant. Some of the descriptions belong to the methods section. Therefore, I suggest that the authors adjust the content of the section. Move some content to the supplement material and others to the methods section.**
<span style="color:blue">

**Materials and Method to just Method: Monte Carlo Simulations?**

The core objective is to test the CF against existing ML methods. To this core objective, ML simulations are our core method. For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood by the reader of this journal. Since, this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well. Now, if we place this inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works. Instead of this, we believe that it is beneficial to first give the readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted.

We talk about identifying site-specific economically optimal input rates in three different places. Therefore, I understand why you feel there are redundancies. However, each of them serves distinctive purposes and we would like to keep the current structure if that is acceptable to you.

Section 2.1: bluh bluh
Section 3.: true optimal N
Section 3.: estiamted optimal N

</span>

**3. The description of materials and methods section is redundant, please move some unimportant details description to supplementary materials.**

<span style="color:blue">  
We first apologogize that misleading section and subsection titles may have caused confusions about your perceived structural redundancy of this article.

We wrote the initial manuscript with avoiding redundancy in mind and we beleived that we did not have any redundancy in our paper. Therefore, we struggled tremendously to see where the redundancies are. We would really appreciate it if you could specify where you see redundancies and why so that we can address prorperly.

In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated. It is much like any emprical studies using real experiment data provides lots of details about the experiemnts. We take reproducibility seriously and we believe that the details we peovided in our manuscript is appropriate. Therefore, we had very hard time telling which is unnecessary and not. We would really appreciate it if you could specify which parts are not critical.

</span>

**4. What is the unit of the topographical slope？ (line 131)**
<span style="color:blue">

+ It is degree. <!-- The slope is obtained by dividing the rise over run. If slope is 0.005857921, it means that the field is raised by 0.005857921 m for every 1m you move horizontally.  -->
+ I added the the unit of EC (dS/m) additionally, since another reviewer pointed out the units of EC

</span>

**5. There are 3 numbers in each small frame of Figure 1, please describe the meaning of each number in detail in the figure caption. (line 137)**
<span style="color:blue">

+ I added the explanation for those numbers in the footnote. 
</span>

**6. Some formulas in the manuscript are not numbered (lines 116, 120, 268, 291, 371, 389).**
<span style="color:blue">

+ I numbered only referenced equations. Should I number all the equations?
</span>

**7. What are the exact number and proportion of test set training sets? (line 192)**
<span style="color:blue">

+ I changed this sentence "For each simulated field, we generated a training data set and a validation data set."

+ The modified version is "After generating one thousand synthetic fields, we repeated to evaluate each of the ML methods by one thousand times. In an individual simulation round, one of the fields was used as a training data set. As a validation data set, a different field from a training data set in that simulation round was used".
</span>

**8. I can’t open the code link (https://github.com/tmieno2/ML_VRA.git, lines 199 and 249) with my browsers (chrome, edge, and Firefox). Please upload the code to the public research data repositories (Zenodo, Mendeley Data, figshare, Harvard Dataverse, etc.), not GitHub. Please generate a separate DOI for your code and cite it.**
<span style="color:blue">

</span>

**9. Please convert the length units of the manuscript to international length units. (line 207)**
<span style="color:blue">

+ I converted to those units to meter (m)
  + plot size: 60-ft × 240-ft -> 18.288-m × 73.152-m
  + subplot size: 60-ft × 60-ft -> 18.288-m × 18.288-m
  + plot size: 10-ft × 10-ft -> 3.048-m × 3.048-m
</span>

**10. Please add the number of rows and columns to the plots, subplots, and cells schematics in Figure 2. (line 209)**
<span style="color:blue">

+ I added the number of rows and columns of plots, subplots and cells in Figure 2. 
</span>

**11. The titles of sections 3.2.1 and 3.2.2 do not provide useful information to the readers, please revise the titles. (lines 342 and 373)**
<span style="color:blue">

+ Current name:
  + 3.2 OFPE Experiments and Estimating Site-specific Optimal N Rates
    + 3.2.1 RF, BRF, and CNN
    + 3.2.2 CF

+ The title of section 3.2.1: Site-specific EONR estimation by RF, BRF, and CNN
+ The title of section 3.2.1: Site-specific EONR estimation by CF

+ Or, we could change the title of section 3.2 (e.g., Machine Learning Algorithm to Estimate Site-specific EONR) and use the same title for section 3.2.1 and 3.2.2
</span>

**12. The titles of 4.1 and 4.2 are confusing, please revise. (lines 410 and 457)**
<span style="color:blue">

+ Current name:
  + 4.1 EONR Estimation
  + 4.2 Yield Prediction and EONR Estimation

+ The title of section 4.2 could be changed to "The relationship between the performance of yield prediction and EONR estimation" (?)
</span>

**13. Why there are no CNN results in Figures 8,9, and 10? (lines 439, 441, and 453)**
<span style="color:blue">

+ I need to add the explanation for it in section 4.1 EONR estimation.  
</span>

**14. I suggest that the authors add to the supplementary material a table of the training accuracy of the different models.**
<span style="color:blue">

+ run simulations on training dataset, and report the results.
</span>

**15. Please add a separate section for research gaps or uncertainties. Are there any prerequisite assumptions for using the CF model?**
<span style="color:blue">

</span>

**16. Please revise the conclusion. Most of the content is discussing the uncertainty of the study. Please move the statement about uncertainty to a separate uncertainty section.**

<span style="color:blue">

</span>

### 2022-02-05 Writing/Re_JournalSubmission/replies_rev_2.Rmd
initial submission

---
title: "Reply to Reviewer #2"
author: 
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
---

# Comments:

**1. All tables and figs: No capitalization of the titles, other than first letter.**
<span style="color:blue">

+ I modified the titles of all tables and figures.
</span>

**2. Fig, 1. Indicate units for slope and EC in title.**
<span style="color:blue">

+ I added the explanation about the units of slope and EC in line 131.
</span>

**3. Table 1 and Fig. 3: show units where applicable.**
<span style="color:blue">

+ I included units in Table 1 and Fig. 3. 
</span>

**4. p. 21 l. 334: For example, instead of using , directly, some some topographical land features and soil properties (remove 1 some)**
<span style="color:blue">

+ I removed extra "some" from the sentence.
</span>

**5. p. 24: l403 The accuracy of EONR estimation was judged based on the RMSE (/h)of EONR estimation**
<span style="color:blue">

+ I added indent between "(kg/ha)" and "of"(before: "RMSE (kg/ha)of EONR", after: RMSE (kg/ha) of EONR)
</span>

**6. p. 26 l. 424. To examine whether this problem is a product solely of the specific choice**
<span style="color:blue">

+ I corrected the grammatical error. Before: "To examine whether this problem is product" to "To examine whether this problem is a product..." 
</span>

**7. P. 29 l 449: Points are clustered much more tightly about the 1-to-1 line much for CF-base than RF and BRF. (remove much)**
<span style="color:blue">

+ I removed "much" from that sentence.
</span>

**8. Table 3. Provide units.**
<span style="color:blue">

+ I added the unit (kg/ha) in the title of Table 3. Similarly, I added units in Table 2, Figure 8, 9, 10, and 11.  
</span>

### 2022-02-05 Writing/Sp_smoothing.Rmd
initial submission

---
title: "Machine Learning Methods for Site-specific Input Management"
author:
  - Shunkei Kakimoto^[University of Nebraska Lincoln, skakimoto3@hunskers.unl.edu] and Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu] 
output:
  bookdown::word_document2:
    toc: FALSE
    pandoc_args: ["-Fpandoc-crossref"]
bibliography: MSthesis.bib
eqnPrefix: 
      - "Eq"
abstract: "Abstract: Site-specific crop yield response to inputs is a complex biological process involving numerous factors and is heterogeneous within a field. Past studies have attempted to estimate optimal Nitrogen(N) fertilizer rates using various prediction-oriented  Machine Learning(ML) methods to forcast more accurate N recommendation rate. However, the problem we should be dealing with for the recommendation is to estimate heterogeneous causal impact of N fertilizer on crop yield. In other words, estimating site-specific optimal input use should be fundamentally based on a causal question. In this study, we apply Causal Forest(CF), which was recently developed by @Wager2018a and @athey2016recursive for estimating heterogeneous treatment effects, to the identification of site-specific optimal N fertilizer use. We evaluate its performance comparing with Random forest(RF) and Boosted Random Forest(BRF) under various model configurations. Futerhmore, we introduce spatial smoothing to generalize the spatial trend of the estimated site-specific optimal N rates. The data to be used for the analysis is generated with Monte Calro simulation incorporating geostatistical model. Results show that CF outperforms RF and BRF and spatial smoothing boost the accuracy of the recomendation use in all the cases. Thus we conclude that CF is a promising optimal N rate recommendation tool taking place of prediction-oriented ML methods such as RF and BRF, and spatial smoothing should be used together with it to derive more accurate estimates"
---

```{r echo = F, results='hide', message=FALSE}
library(knitr)
library(here)

# === set wd ===#
# Notes: not really necessary to set the working directory as long as this Rmd file is part of an R project and the evaluation directory was set to "Project".

opts_knit$set(root.dir = here())
# setwd(here())

options(htmltools.dir.version = FALSE)
options(knitr.duplicate.label = "allow")

opts_chunk$set(
  fig.align = "center", 
  fig.retina = 5,
  warning = F, 
  message = F,
  cache = FALSE, # <-- T
  cache.lazy = FALSE,
  echo = F
  )
```

```{r, cache = TRUE}
# === packages ===#
library(sf)
library(data.table)
library(grf)
library(RColorBrewer)
library(patchwork)
library(plotly)
library(magrittr)
library(ggplot2)
library(viridis)
library(tmap)
library(tidyverse)
library(ggthemes)
library(mgcv)
library(ggpubr)
library(flextable)
library(officer)
library(modelsummary)
library(raster)
library(bookdown)
```

```{r analyses, results = "hide", fig.show='hide', cache = FALSE}
#/*=================================================*/
#' # Preparation
#/*=================================================*/
# This is where you prepare datasets and results

#/*----------------------------------*/
#' ## Create figures and tablesb
#/*----------------------------------*/
# --- Convert an Rmd file into a pure R file using purl() ---#
# knitr::purl(here("Codes/PrepareResults.Rmd"), output = here("Codes/PrepareResults.R"))

# --- Read the simulation results and prepare figures and tables ---#
source(here("Codes", "PrepareResults.R"))
```

# Introduction {-}
<!-- 
estimation of yield response to an input
"big data" 
heterogeneity of yeild response; different marginal yield response to an additional unit of input.
"yield heterogeneity identified with yield maps from combine harvesters cannot serve as a robust indicator for the profitability of site-specific fertilizer management"
-->

<!-- + background on nitrogen management (economics, environment, precision agriculture)   -->

Modern agricultural production system, which is featured by the enlargement of fields due to capital-labour substitution, has been confronting the difficulty in taking account of the spatial and temporal within-field heterogeneity of crop <!-- and environmental taits into its --> mangement[@zhang2002precision]. Precision agriculture(PA) is the technology developed to assist  decision-making for such a complicated management <!-- of soil and crops in a field  -->utilizing the power of information technology[@cook1998precision; @finger2019precision]. One of the leading PA technologies is variable rate application(VRA) and it has been actively investigated for site-specific input managment especially for nitrogen(N) management[@Khosla2002; @ruffo2006site; @koch2004economic; @hurley2004estimating; @shanahan2008responsive].
Effiecient managment of N fertilizer is a key component of crop production from agromical, economical and environmental standpoints.<!--  N fertilization is usually conducted to assure to meet crop N demand but --> 
Inappropriate amount or timing of N application adversely affects both biomass yields and grain quality for some crops. Furthermore, inefficient use of N fertilizer not only results in economic loss but causes ambient environmental losses in such a form of nitrate leaching[@blumenthal2008importance; @dinnes2002nitrogen; @tremblay2006adapting]. \
<!-- Excess amount of N fertilizer application could cause low nitrogen-use-efficiency, resulting in economic loss and ambient environmental losses in such a form of nitrate leaching[@]. -->

While site-specific input management has been rising in importance as a management tool to derive maximum economic gains and reduce environmental losses, there still remains formidable challenges we should deal with until it becomes widely accepted among farmers. One of the biggest challenges lies in how to identify the heterogeneous yield responses to inputs based on measurable field and soil properties <!-- and dynamic facotrs such as weather conditions -->. Despite considerable effort for modeling yield response to N in the past decades, there is no general agreement on its specification to date. Earlier studies modeling yeild response functions with traditional econometric approaches[@morris2018strengths]. However, those approaches may not be approptiate to capture the complex biological process between crop yield and inputs because the process involves numerous number of factors and they are likely to be interacted in non-linear and multi-way fashion[@Miao2006; @kitchen2003soil]. 
Critically, the ability of estimating heterogeneous imapct of inputs on crop yield, which is essential for site-specific input recommendation, is ristriced in the current econometric approaches[@Storm2020].
As an alternative approach, machine learning(ML) based site-specific input use recommendation has been gathering much attention in accompanying with the availability of sufficient spatially dense data related crop and field properties based on on-farm experiments. ML method has an advantage <!-- over traditional econometric models[cite papers]  -->in handling a large number of variables which are highly interacted in a nonlinear fashion and allow modeling in a data-driven way. Under little prior knowlege about underlying yield response function, ML method is appealing to describe complex plant and soil process. Indeed, some study reviewed application of ML methods in the literature of PA have shown the promissing usefulness of ML methods as a tool for yield prediction and Nitrogen management[@Chlingaryan2018;@van2020crop].\
<!-- + the gap -->
<!-- causal analysis for site-specific input use recommendation -->
However, there is currently a scarcity of literature applied ML methods to a "within-field" site-specific input management. 
Recent on-firm experiments enables farmers to collect more spatially dense data <!-- related to underying yield response function at finer scale level --> at low cost[@bullock2020value]. According to such data availability, ML methods should be evaluated for its potential performance as a within-field site-specific N reccomendation tool. On the other hand, while ML methods are promissing, previous studies commonly showed the difficulty in estimaing optimal N rates[@Qin2018; @Wang2021; @coulibali2020]. The potential mistake those studies made is that they depend on prediction-oriented ML methods to estimate site-specific optimal N rate.<!--  For example, @Qin2018 and @Ransom2019 used various ML methods to directly predict optimal N rate. @Wang2021 and @coulibali2020 attempted to found an optimal N rate based on yield prediction. However, --> However, for site-specific input mangement, the fundamental problem we should be asking is not prediction accuracy but to correctly estimate heterogeneous causal impact of inputs. This is because an optimal input use rate for a certain site heavily depends on the small change in yield casued by change in N rate conditional on other soil and field properties for that site[@puntel2016modeling].<!--  Thus, estimation of site-specific optimal N rate is a causal reserch question. --> As far as we know, no studies applied causal anlysis with ML methods in the context of site-specific input management. 
Another thing we want to highlight is that the resulting optimal N rate from ML methods does not accout for spatial structure. In the real world, any yield monitor observation <!-- crop and field characteristics --> has spatially smooth nature[@anselin2004spatial; @lambert2004comparison]. Thus, the optimal N rate which determined by those factors also should have spatially continuous feature across all locations in a field. This property has been overlooked in the past literature. 
<!-- + objective of the paper (how it fills the important research gap you mentioned above) -->
To fill the aforementioned research gaps, in this study we want to propose an alternative approach with a ML method for a site-specific input management. Our approach consists of two parts. 
First, we estimate causal impact of an input with with a relatively newly introduced ML method called Causal Forest(CF). CF is a ML method developed by @Wager2018a and @athey2016recursive for the estimation of heterogeneous treatment effects. We use CF to identify site-specific input use rates.\
<!-- Although the building block of CF is random forest[@breiman2001random], CF is essentialy distinct from prediction oriented ML methods in that its algorithm is optimized for identifying heterogeneous causal effects of a treatment. Indeed, in economics fields, many studies has started to adopted CF for causation research instead of using traditional econometric tools.  -->
<!-- If CF could successfuly cpature the causal impact of an input based on site-specific field and soil properties and we could utilize the information of the estimated causal impact for site-specific input use recommendation rate, we could obtain more reliable and precise site-specific recommendation input use rate.  -->
Second, spatilly smoothing is induced to the estimated optimal N rate based on the other field and soil properties and the geographical locations with generalized additive model(GAM)[@hastie1990generalized].　GAM has an advantage in nonparametrically capturing the pattern of the dependent variable <!-- using an appropriate continuous function for each independent variables --> in a data-driven way and producing good prediction[@yee1991generalized; @plant2018spatial]. <!-- We fit GAM to the estimated optimal N rates resulted from the CF using the other covariates as its independent variabls, and then re-estimate the spatially smoothed optimal N rates. --> We hypothesize that a series of these procedures produces more accurate N recommendation rate than approches using conventional prediction-oriented ML methods. 
<!--  -->
The objectives of this study are therefore: (1)to evaluate the relative performance of CF for site-specifc N rate recommendation  compared to random forest and boosted random forest which are widely accepted prediction-oriented ML methods in the past studies, and (2)to evaluate if spatial smoothing with GAM could be helpful to modify the estimates of optimal N rate.\
<!-- + how do you do it (summarize, do not provide too much details) -->
We test the performance of each of the ML methods and spatial smoothing through Monte Calro simulation. One thousand roudns of siumulation is conducted in total to generate the dataset of production characteristics for the simulated fied. In data simulation process, we make some variations in covariates to be used for analysis to reflect realistic probelems we face in practice. <!-- For each simulation round, each of the ML methods are used to estimate site-specific optimal N rate and spatial smoothing is applied to it. --> <!-- R-squared($R^2$) statistic is used as a metric for the evaluation of optimal N rate resulted from both ML methods and spatial smoothing each round, then the mean of $R^2$ values are calcuated for the final result. -->\
<!-- + summarize the results -->
The results show that that the approach using CF outperformed RF and BRF in estimating site-specific optimal N rate for all the model configurations. In addition, spatial smoothing considerably improved the precision of the recommendation rate. Even after GAM is applied, the results from CF still show the best performance. Hence, we conclude that CF is a promissing ML method as a site-specific input use recommendation tool, and spatial smoothing with GAM can aid the precision of the estimation.

<!-- Flow
The reminder of this paper is organized as follows. In section 2, we review.... . Section 3 reviews.... In section 4...  -->

# Literature Review {-}
<!-- 
Think why do you need to do literature review
• to find research gap
- research gap1: 
- there is a problem in their methodology (they rely on prediction base approach)
- I want to say that ignoring to estimate yield response function in obtaining EONR is problematic;
- -> @Lory2003; 
- direct optimal N prediction fails at capturing the true optimal N rate.
-->
<!-- 
we want to propose a better approach for site-specific optimal N recommendation. 
 -->

<!-- Previous studies used ML methods mainly to directly predict optimal nitrogen recommedation rate.

but the results suggested that those infomation did not contribute to the explanation of such the valiability.

@Qin2018 used various ML methods to predicted optimal nitrogen application rate using the on-farm experiments of 47 field-years in the midwestern US. Inspite of a large set of input data related to field-level soil and historical weather data, their results suffered from high prediction error. They also found that the prediction accuracy of ML did not change between using real weather data and using weather estimates devived from the historical weather trend.

Similarly, @Ransom2019 evaluated multiple ML methods for corn nitrogen recommendation incorporating soil and weather condition. Their comparison of the perfomance of ML methods using full infomation and the reduced infomation suggested that including more input variables did not improve the perfomance of ML methods.

@lawes2019 attempted to identify which variables are useful for optimal nirtogen prediction with random forest using simulated nitrogen response trial dataset. They found that historical site mean yield of the field is the most important variable rather than variables of soil type and subsoil conditions. Further, the prediction perfomance of random forest with different sets of independent variables did not change significantly, and their predictions were consistently underestimated.

Meanwhile, @Wang2021 evaluates the perfomance of random forest for recommendation of optimal side-dress N rate.

Even though the model can predict yield with high accuracy, when it comes to the estimation of optimal N rate their model fails to explain the variability of true optimal N. Similar results are confirmed in @puntel2016modeling and @puntel2018systems, although they did not use ML methods for predicting yield. -->

<!-- draft -->
Previoius studies examined many prediction-oriented ML methods in an attempt to evaluate their potential usefulness as a decision tool for optimal N recommendation. 
@Qin2018 used various ML methods such as random forest, gradient boost regression trees forests and ridge regression to esitmate optimal N application rate for corn fields across midwestern US. However, their results suffered from high prediction error despite using a large set of input data including soil properties and historical weather data, indicating the difficualty in predicting optimal N rate directly. 
@Ransom2019 examined how ML methods can be helpful for improving N recommendation rate that is derived from existing N recommendation methods<!--  using soil and weather information -->. Although they found that ML methods especially random forest performed better at adjusting exisiting N recommendation tools significnatly, their approaches are not suitable for within-field site-specific N managment because exisiting N recommendation tools are desined for regional-scale or field-scale. Meanwhile, @Wang2021 attempted to estimate optimal side-dress N application rate for corn at infiel-scale with random forest and Lasso linear regression. Different from the approach taken by @Qin2018, they first estimated yield response function with random forest using the data of soil properties, weather condition, crop management practicies and remote sensing data, then estimated optimal N rate by finding the profit-maximizing N rate. They found that the random forest shows reasonable performance in yield prediction, but the accuracy of the resulting optimal N recommentation rates are relatively poor, suggesting that the model that has high ability for yield prediction does not necessary leads to accurate estimates of optimal N rate. Similar results are also reported in @coulibali2020 and other studies employing a different approach other than ML methods. @puntel2016modeling and @puntel2018systems used a crop simulation model to predict yield and derived the optimal N rate. They achieved high accuracy in predicting yield but had a difficulty in estimating optimal N rate. Regarding this finding, they concluded that estimating optimal N rate is highly sensitive to the small changes in yield as N varies and so, it is more complicated than predicting yields.

* What are the problems with these studies? Why are they not useful?

while they suggested the potential usefulness of ML methods as a decision makeing tool for N management compared to already prevailing N recommendation tools, their results also commonly implied that there is some limitation in estimating optimal N rate with prediction base ML methods<!--  even though the model is built with a large set of varibles which are supposed to explain the underlyign yield response functions -->. It is worthwhiel to seek an alternatinve approach with ML methods to make more reliable recommendations which is necessary to make site-specific optimal input management profitable.
<!-- there is only a limited number of studies forcused on the application of  ML methods for within-field site-specific optimal N management.  -->
The critical problem we can see in those past studies is that they attemped to use prediction-oriented ML methods for estimating yield response to N rate. They disregard an important fact; to estimate how site-specific yield changes to an additional unit of N application rate conditional on other factors.
<!-- apply an optimal amount of an input to be applied for each site to gain maximum net economic returns.  -->
<!-- For the goal, the problem the we need to deal with is to understand how the marginal net benefit of N application varies with site-specific properties whithn a certain field. Or, to put it more specifically, we can rephrase that as how site-specific yield response changes with N treatment rates conditional on other soil and field properties. -->
Idealy we wish to answer that question by applying various N rates under the completely the same condition to each site and see how yield varies by N application rates. But in reality, such an experiment is unattainable, which is know as “Fundamental Problem of Causal Inference”[@holland1986statistics].
All we can do is to <!-- just --> statistically estimate the conditional average treatment effects defined as the difference between the realized outcomes and the counterfactual potential outcomes conditional on other soil and field properties using the on-firm experiments. <!-- In other words, to estimate the ceteris paribus causal effects of treatements.  -->
Furthermore, what makes the estimation more complicated is the fact that such treatment effects are heterogenous due to the existance of factors that create within-field spatial variability[@scharf2005field; @ruffo2006site; @scharf2006spatially]. For example, higher N rete leads to greater yield at some locations, whereas yield does not respond much to change in N rate at some locations. This heterogeneity nature of the impact of N rate to yield response is what contributes the complexity of estimation of site-specific input recommendation use.
<!-- Based on the estimated unbiased treatment effects from whole field esperiments, we should determined the site-specific optimmlal N rate.\ -->
Prediction-oriented ML methods are not be able to correctly answer such a causal question. This is because prediction problem and causal inference are two different things and the algorithm of prediction-oriented ML methods are not designed for doing causal inference. Indeed, causal inference requires more of the statistical properties than prediction problem in evaluating models due to the Fundamental Problem of Causal Inference[@athey2018impact].
Hence, estimation of the heterogeneous site-specific yield responses to N should be addressed as a causal research question, not as a prediction problem. 
<!-- Indeed, the conventional predictive ML methods which are not modified for causal estimation leads to biased estimates of causal effects of interest[@athey2017beyond]. Hence, in order to deal with the challenge of VRA, we need to address it with a correct way. In this study, we want to deepen the discussion about how we can apply causal analysis in the context of VRA without giving up any merits of using ML.  -->

<!-- - uncertainty -->

* a movement in the academia to do more of causal machine learning.

<!-- why people have started to realize we need causal machine learning methods for many applications. -->
<!-- Causal estimation with ML (what is its uniqueness?) -->
<!-- While the predictive performance of ML methods has gained popularity and has been widely adopted in multidicipline fields, -->
There has been a recent movement in the field of ecnomics to do causation research with ML methods[@mullainathan2017machine; @Storm2020; @Athey2019a]. This movement was establishded by the emergence of a new ML algorithm called causal forest(CF)[@Wager2018a; @athey2016recursive] which is developed to identify heterogeneous treatment effects. 
There are several reasons for this movement. Generally, ML methods have some advantages over traditional econometric methods in the process of model building. The traditional econometric methods requires reasearchers to select variables to be included in the model and to specify one functional form for modeling by themselves as well. This process makes it difficult for reasearchers to comprehensively check alternative model specifications and there is no consensus among researchers regarding on these procedures[@athey2018impact].
Meanwhile, ML methods such as RF automatically select influential variables out of many input variables and also find the best functional form out of many alternative models based on some criterion in a data-driven way. Furthermore, although the traditional econometric methods are well established about the estimation of average casual effect, they are still struggling in heterogeneous treatment effect estimation with valid asymptotic property[@knaus2018machine]. In that light, CF can do it by taking advantage of the aforementioned strengths of ML methods. 
CF is an extention of breiman's random forests, but its algolithm is distinct from prediction-oriented ML algorithms. In a pure prediction problem, the mean squate error (MSE)($\sum(y_i - \hat{y}_i)^2$) criterion is available for model validation. That is, the model that results in the smallest prediction error based on the observed outcomes is selected as an optimized model. However, when it comes to causal infernece with ML, MSE criteria is not available becasue we never observe the true causal effects of treatment. Against this problem, @Wager2018a and @athey2016recursive modified MSE criteria of regression tree algorithm and proposed a novel "honest" criterion as a solution. The regression tree adopted this honest criterion is called "Causal tree"(CT) and it provides unbiased conditional treatment effects and the valid confidence intervals under the uncounfoundedness assumption. The detail is explained in the Methodology section. Owing to this divelopment, there is a growing economic literature appliying CF for estimating treatment effect heterogeneity[@rana2019machine;@davis2017using;@o2018causal;@hitsch2018heterogeneous].
 <!-- (while conventional CART use the same sample for building a tree and estimaiting the conditional means using MSE criteria.)Then, Each node is splitted in a way that it increases the treatment effect heterogeneity. @Wager2018a extend it to causal forests(CF) which is an ensemble of CT estimators. CF enables formal statistical inference aligned with asymptotic normality theory.   -->

<!-- minimizigng the expected MSE of predicted treatment effects is equivalent to maximizing the variance of treatment effects across leaves minus a penelty for within-leaf variance -->

<!-- regularization = conlexity of a function -->
<!-- generalization using the training data -->

<!-- ?? Why other ML methods might not be appropriate for estimating treatment effect heterogeneity ?? -->

* Objective

In this study, we would like to evaluate the peformance of CF approach for site-specific input use rocommendation comparing RF and BRF which are widely accepted ML methods in the previous studies. To assure the validity and generality of our finding, we conduct 1000-round of Monte Calro simulations under varioius model configurations. Furthermore, we apply spatial smoothing with GAM to the estimated optimal N rate and examine if spatial smoothing could contribute to their accuracy improvement.

<!-- The  general procedure has the following structure. We consider…, We… We then compare the in-sample goodness-of-fit of the model with others. …. Finally,…. -->

# Materials and Methods {-}

## Set up (Field) {-} 
The geographical data of an experimental field was created based on an actual field used in the Data-Intensive Farm Management (DIFM) project [@bullock2019]. The field consists of 1536 plots with 240 by 60 feet dementions, and the field size is about 507 acres. Each plot is subdivided into 24 subplots. In this section, we are going to explain how we simulate the field characteristics and yield data.

## Data generating process {-}
+ Yield-response function

We use Mitscherlich-Baule(MB) response functions as the underlying true yield-response function to N fertilizers for corn production. The Mitscherlich-Baule function is one of the major production functions that has been frequently investigated and applied in the literature. It features its fexibility of the shape of yield response curve <!-- allowing for both input substitution and plateau growth -->, and so it was revealed to be an plusible specification for nitrogen fertilization models for corn <!-- corn yield response to inputs -->[@frank1990; @llewelyn1997; @paris1992].
<!-- The model we are using is actually Mitscherlich model, not the Mitscherilich-Baule model? -->
In this study, we consider N as its only input. Eq.([-@eq:eqn1]) shows the equation for MB function in the study.
\begin{equation}
f(N) = ymax(1-exp(\alpha + \beta \cdot N))
\end{equation}
{#eq:eqn1}

where $ymax$ is an asymptotic yield plateau(kg), and $\alpha$ and $\beta$ ($\alpha<0, \beta<0$) are the parameters that describe soil and field properties such as inherent soil N content <!--soil-born N--> and crop N uptake <!-- soil mineralization capacity --> which characterise the process of how N fertilization affects crop yields[@llewelyn1997]. $N$ indicates applied N fertilization rate($kg \text{ } ha^{-1}$). $ymax$, $\alpha$ and $\beta$ can be regarded as uncontrollable but non-stochastic factors that affects yield response function.  Crop yield is derived as an output. $N$ is the only input variable that is controllable.
Through the study, it is assumed that the objective of a producer is to maximize profit. Then, the solution to a site-specific profit-maximizing N rate, which is optimal N rate, is calculated as the minimum N rates that can attain maximum retun to N with minimum costs as follows.

\begin{equation}
N^{opt} =\underset{\mathrm{N}}{argMax}(P_{C} \cdot f(N) - P_N \cdot N) 
\end{equation}
{#eq:eqn2}

where $N^{opt}$ is a  site-specific profit-maximizing N rate, $P_{C}$ and $P_N$ are the price of the corn (in $/kg) and  is the price of N fertilizer(in $/ha). We assume $P_{C}=3.5kg \text{ } ha^{-1}$ and $P_N=0.6kg \text{ } ha^{-1}$.
In reality, the realized crop yield is affected by unmanageable stochastic factors such as the effect of precipitation and temperature[@bullock2002adding]. All of therse effects on yield is described by adding random yield disturbance term $u$ to the above deterministic nature of yield response function Eq.([-@eq:eqn1]). Thus, the observed crop yield is generated with the following equation.

\begin{equation}
F(N) = ymax(1-exp(\alpha + \beta \cdot N))+u
\end{equation}
{#eq:eqn3}

+ Simulated data generation

One thousand sets of parameters $ymax$, $\alpha$, $\beta$ and the random yield disturbance term $u$ are simulated in a spatially autocorrelated fashion on the basis of subplot using spherical variogram models of `R` package `gstat`[@pebesma2004; @pebesma2016]. 
One spherical variogram model is generated to simulate each of the paramers respectively. It is assumed that the range is 400m and the nugget is zero about all the spatial distributions of the parameters and random error. Regarding their sill value, $2000000 \text{ } (kg \text{ } ha^{-1})^2$ for $ymax$, $0.02$ for $\alpha$, $1$ for $\beta$ and $0.015$ for $u$ are used. $u$ approximately cause error in yields by $1300 \text{ }(kg \text{ } ha^{-1})$. After identifying each variogram model, one thousand sets of the field characteristics are respectively simulated with them using Gaussian simulation.

<!-- nism: if set to a non-zero value, conditional simulation is used instead of kriging interpolation. For this, sequential Gaussian or indicator simulation is used (depending on the value of indicators), following a single random path through the data. -->

<!-- How should I explain about sp_range and so on?   -->
Figure \@ref(fig:fig-parameters) shows an example of distribution maps of $ymax$, $\alpha$, $\beta$ and $u$. The spatial distribution of $ymax$, $\alpha$ and $\beta$ are assumed to be independent each other. $ymax$ and $\alpha$ are also assumed to be independent from the random yield disturbance term $u$, but we impose an assumption on $\beta$ that it is correlated with $u$ to some extent. This assumption is reasonable to represent realistic crop production system. Soil and field properties are often affected by stochastic facotrs. For example, weather conditions such as temperatures not only have an impact on nitrogen mineralization which is the major soil N dynamics[@clark2020soil] but it also affect final crop yield through heat stress[@siebert2014impact]. In this case, temperatures not only affect crop yield directly but also have some impact on yield indirectly through affecting soil N properties which is represented by $\beta$. Once $ymax$, $\alpha$ and $\beta$ are generated, optimal N rate are calculated site-specifically by Eq.([-@eq:eqn2]). Figure \@ref(fig:fig-optN) shows an example of the distribution map of true optimal N application rate derived from the distribution of Figure \@ref(fig:fig-parameters), idicating spatially autocorrelated pattern of the optimal N in the field.
<!-- #' 0.015 means 1300 sd, -->

## Experimental Design
In each simulation round, five N fertilizer treatment rates are randomly assinged to each of the field's 1536 plots following a Latin square design. Figure \@ref(fig:fig-nExp) shows an example of experimental design. Regarding the determination of the N treatment rates to be used for each simulation round, first, minimum and maximum N treatment rates are determined so that they represent extreamly low and high N application rates respectively based on the probability density of true optimal N rates for that simulation round. Then, the rest of the three N treatments rates are obtained by finding N rates which equally partitioning the range between minimum and maximum N treatment rates into three parts. 
<!-- you might wanna explain how to calculate optimal N by showing the density plot of optimal N-->
In Figure \@ref(fig:fig-nExp), the five N treatment rates are set to be 81, 116, 150, 184 and 219 kg/ha. According to those assined N treatment rates, subplot-basis yield data is generated with Eq.([-@eq:eqn3]). Figure \@ref(fig:fig-yield) shows an example of a yeild distribution map.
The simulated data including yield and the parameters of the response functions is aggreagated by taking mean value by plot and the resulting data is used for training data. 
For testing data, due to the computational burden accompanied by Monte Carlo simulations, we use randomly selected 1000 subplots out of the simulated data different from the training data. <!-- We use this subplot-basis data as a testing data. -->

<!-- + a map of an experimental design  -->

## Methods (Causal Forest, Random Forest, and Boosted Random Forest)
We evalauate three ML methods; RF, BRF, and CF usign the simulated data explained in the above. We use R-squared($R^2$) statistic as a metric for the performance evaluation. $R^2$ is derived from a simple linear regression model where true optimal N rates are regressed on estimated optimal N rates in each simulation round.
After that, for the purpose of spatially smoothing, we fit GAM to the resulted estimates, then re-estimate site-specific optimal N rate. $R^2$ is again calculated using the re-estimated optimal N rates to see how spatial smoothing works for prediction improvement. In this section, we are going to look at the details of each of the ML methods and GAM and explain how we implement them for our analysis.

+ RF

RF is a collection of multiple deep regression trees. Individual tree is built by recursively splitting samples into two disjoint subgroups<!-- , which is called "leaves," -->  based on the covariates<!-- feature space -->. At each stage, average of response is derived as a predicted value in each group and it is evaluated to find best splitting variable and split point. The problem of a regression tree is that it is easily overfit the data, leading to high variance. This problem gets worse as a tree grows more complecatedly[@friedman2001elements; @efron2016computer]. In random forest, each tree is generated from bootstrap and the splits are determined by a random subset of the explanatory vairables at each stage. By growing many different trees and averaging the outcomes from all the trees, the generalization error converges following the Law of Large Numbers[@breiman2001random]. Hence, RF can effectively reduce the variance and attain more precise prediction comapared to any single tree. RF is robust to irerelevant variables to the responses and does not require much about its tuning[@Storm2020; @Athey2019a]. 
RF is one of the popular ML methods in the literature of precision agriculture and many studies addmitted their performance as a tool for yield prediction and as a site-specific N recommendation tool as well[@zha2020; @lawes2019; @Ransom2019; @everingham2016; @Wang2021].

+ BRF

BRF is similar to RF in the sense that their prediction is derived from the average of outcomes from individual tree in the forest. The major difference lies in their ways of building tree. While trees of RF is grown applying the same process incorporating some randomness to each building stage, trees of BRF are sequentialy grow modifying the tree based the error from the previous stage. 
<!-- find the papers that use gradiant boosting method or support the method  -->
@Ghosal2020a proposed one-step boosted forests by taking gradient boosting method(@friedman2001greedy) as a part of random forest procedure of @Wager2018a to improve its prediction. 
In one-step boosted forests, two forests are build; first one is the usual random forest build on subsamples of the training set and the second is constructed using the out-of-bag<!-- (OOB) --> residuals from the first random forests. The final output is derived as the sum of the two outputs from each if the random forests. @Ghosal2020a showed that one-step random forest outperformes usual random forest and gradiant boosting for their dataset.

<!-- In one-step boosted forests, given the current output from the tree, the loss function is calculated and  -->
<!-- @Ghosal2020a: it can be expected that more boosting stpes, instead of just one step, lead to more improvement. But the development of stopping criteria test is left to future work-->

+ CF

As aforementioned, CF is an ensemble of CT estimators and it estimates conditional average treatment effect.<!--  defined as $\hat{\tau}(x) = E[Y_1 - Y_0|X=x_i]$. Let $\mathbf{c_{i}}$ be a vector of soil and field properties of subplot $i$ and let $Y_1$ and $Y_0$ be the yield reponse with and without treatment. --> The same idea of RF is applied about taking ensemble form of multiple trees. By doing so, it works for smoothing the outputs and reducing variance. While a standard regression tree splits the samples into smaller subgroups based on the covariates, CT does that based on the treatment effect heterogeneity. 
More specifically, at each building stage of a CT, splitting variable and splitting point are determined so that the variance of treatment effects <!--  $\hat{\tau}(x)$  --> are maximized across leaves. Then, within-leaf estimates are derived as an average of the estimates of the treatment effects of the samples which are fallen in the same leaf. For these split selection and leafwise estimation, separated subsamples are used(honesty condition)[@Wager2018a; @athey2016recursive]. @Wager2018a mentions that the predictions of CF are not only an unbiased and Gaussian but also it is better than standard RF with respect to mean-square error. 
The most fundamental underlying assumtion of CT as well as CF is unconfoundedness. This assumption means that potential outcomes and treatment assignment are independent. In the study, this assumption is justified by simulating data so as to treatment assignment is completely randomized.

+ detailed explanations of how you implement them

For implementation of RF, BRF and CF, `R` package `grf`, version 1.2.0 [@tibshirani2018package] is used. In `grf` package, RF and BRF are built with the same goodness-of-fit criteria as the standard RF, which is MSE criteria. The distinct points are that each tree uses subsamples of the training data instead of bootstrap samples, and honesty condition is applied. In regards to BRF of `grf`, the boosting method of @Ghosal2020a is reatedly applied to RF of `grf`, and the number of boosting iterations is automatically selected based on corss-validation.\

+ Profit-maximizing Site-specific N rate

For RF and BRF, finding profit-maximizing site-specific N rate is straightforward. RF and BRF site-specifically identify a single yield response function given soil and field properties for that location. Let $\hat{y}_{i}(N) = \hat{g}(N,\mathbf{c_{i}})$ be an estimated yield response function to N, where $\hat{g}(\cdot)$ is the resulted model of RF or BRF, $N$ is applied nitrogen rate and $\mathbf{c_{i}}$ indicates the soil and field properties forl location $i$. Then, the profit for this location is expressed as $\pi_{i}(N) = P_{C} \cdot \hat{y}_{i}(N) - P_N \cdot N$. The optimal N rate is estimated by chaging $N$ sequentially and finding the $N$ that maximizes the profit. This process is applied to all the subplots of testing data every simulation round.\
Now consider the case of CF. Bear in mind that the goal of CF approach is to identify heterogeneous "binary" treatment effects. Since we have five N treatment rates, four CFs are built using four pairwise combinations of N treatment rates combinations respectively. Let $N_1,N_2,N_3,N_4,N_5$ be the five N treatment rates to be applied and suppose that $N_1<N_2<...<N_5$. We consider two possible approaches to make such pairwise combinations. \
First approach is the way of grouping as follows; $(N_1, N_2),(N_2, N_3),(N_3, N_4),(N_4, N_5)$. We refer to this approach as "stepwise". In this case, the estimated treatment effects for location $i$ from CFs with these pairwise combinations are discribed as
$\hat{\tau}_{N_{k} \rightarrow N_{k+1}}(\mathbf{c_{i}}) = E[Y_i(N_{k+1}) - Y_i(N_{k})|\mathbf{c_{i}}]$,
where $k\in\{1,2,3,4\}$ and $Y_i(N_{k+1})$ and $Y_i(N_{k})$ are potential yield outcomes corresponding to the two possible N treatment rates. 
Once these treatment effects are estimated, we predict change in yield due to the increase in applied $N$ rate relative to the yeild of $N_1$. It is calculated by sequentially adding the estimated treatment effects. 
Generally, the change in yield going from $N_1$ to $N_m$ (i.e. $m\in\{2,3,4,5\}$) is generally described as 
$\Delta Y_{N_1 \rightarrow N_m}(\mathbf{c_{i}}) = \sum_{k=1}^{m-1} \hat{\tau}_{N_{k} \rightarrow N_{k+1}}(\mathbf{c_{i}})$.
<!-- Thus the corresponding change in profits is $\Delta \pi_{N_1 \rightarrow N_m}(\mathbf{c_{i}})=P_c \cdot\Delta Y_{N_1 \rightarrow N_m}(\mathbf{c_{i}}) - P_N \cdot (N_m - N_1)$. -->
<!-- The profit maximizing site-specific optimal N rate can be identified by finding $N_m$ that maximizes $\Delta \pi_{N_1 \rightarrow N_m}(\mathbf{c_{i}})$. \ -->
Second approach is the way of grouping as follows:$(N_1, N_2),(N_1, N_3),(N_1, N_3),(N_1, N_5)$. We call this approach as "base". In base approach, treatment effect is always estimated in the comparison with the least treatment rate $N_1$, and therefore it already represents the change in yield relative to the yield of $N_1$. 
That is, 
$\Delta Y_{N_1 \rightarrow N_m}(\mathbf{c_{i}}) = \hat{\tau}_{N_{1} \rightarrow N_{m}}(c_{i})=E[Y_i(N_{m}) - Y_i(N_{1})|\mathbf{c_{i}}]$.
After $\Delta Y_{N_1 \rightarrow N_m}(\mathbf{c_{i}})$ is obtained in both approach, the corresponding change in profit is derived as 
$\Delta \pi_{N_1 \rightarrow N_m}(\mathbf{c_{i}})=P_c \cdot\Delta Y_{N_1 \rightarrow N_m}(\mathbf{c_{i}}) - P_N \cdot (N_m - N_1)$.
Then, the profit maximizing site-specific optimal N rate can be identified respectively by finding $N_m$ which leads to maximum change in profit defined as $\Delta \pi_{N_1 \rightarrow N_m}(\mathbf{c_{i}})$.

+ spatial smoothing <!-- (or spatial interpolation, generalize the trend) -->
<!-- ML cannot account for spatial information, and therefore the resulting optimal N rates lacks the spatially smooth distribution (read @kasampalis2018contribution)  -->

From agronomical and geographical perspectives, it is well-know fact that any field characteristic shows similaliry in its neighborhood and it varies smoothly as goes spatially further[@f2007methods;@goovaerts1999geostatistics]. The saptial distribution of optimal N rates is not an exeption becuase it is determined by varioius soil and field characteristics which have spatially smooth sturucture. However, ML methods cannot account for such a structure, and therefore the resulting estimates of optimal N rate fail to explain its saptially continuous feature. Hence, we impose spatial smoothness to the estimates of optimal N rate. Especially, we expect that spatial smoothing is greatly helpful for the estimated optimal N rates of CF to improve its prediction accuracy of recommendation N rates because, as described in the above, the valiability of the optimal N rate from CF approach can represent is limited and those values are highly discrete. We expect that generalization of the outcomes of CF could represent more realistic and accurate results.\
Considering the fact that site-specific optimal N rates depend on other field and soil properties, it is desirable to generalize the results taking such an complex relationship into consideration. For this reasons, we use generalized additive models (GAM) [@hastie1990generalized] for spatial smoothing which is the extension of generalised linear models(GLM). <!-- A generalized additive model (GAM) is a generalized linear model (GLM) in which the linear predictor is given by a user specified sum of smooth functions of the covariates plus a conventional parametric component of the linear predictor -->Compared to GLM, GAM can model the relationship between dependent variable and covariates in more flexible way as it nonparametrically identifies the functional form for each covariate, which is called as smooth function, in a data-driven manner. Thus, GAM perfomes better at identifing nonlinear effect of covariates on dependent vairable[@friedman2001elements; @yee1991generalized]. 
As covariates for GAM estimation, we include each subplot's coordinates$(X,Y)$, which are projected by CRS: WGS 84 / UTM zone 16N, and their interaction term as well as the each of the covariates used in estimating optimal N rates with ML. The smooth function related to geographical coordinates is expected to capture the spatial trend of the estimates of optimal N rate. Using the esitmated GAM, we re-estimate site-specific optimal N rates. \
For the estimates of optimal N rates(e.g. $\hat{N}^{opt}$) that are derived with a specific model configuration(described in the next section) with $p$ covariates(e.g. $c_1$, $c_2$,...$c_p$), the GAM is fitted with the following form:
$$
\hat{N}^{opt} = s_0 + s_1(c_1) + s_2(c_2) + ... + s_p(c_p)+ + s_{p+1}(X) + s_{p+2}(Y) + s_{p+3}(X \cdot Y)
$$
{#eq:eqn4}
where $s_1(\cdot), s_2(\cdot)$,..., $s_{p+3}(\cdot)$ are smooth functions and each of them represens the impact on the estimated optimal N rate. GAM is implemented with `R` package `mgcv` version 1.8-34[@wood2011fast; @wood2016smoothing; @wood2004stable; @wood2017generalized; @wood2003thin]. In the package `mgcv`, we use thin plate splines with five dimensions of the basis to estimate each of the smooth terms.

+ variations in parameters (you should check this section more carefully)

We add some variations in our covariates to be used in the regression of RF, BRF and CF. This is so as to make our simulation more plausible and to check the robustness of the performance of each of the ML methods.
In practice, we never know which variables have more explanatory power to the realized yield valiability. Furthermore, the relative importance of variables are varies by geographical location of fields[@ge2011remote]. The past studies deal with such a situation by including many variables into models. Some of those variables are highly correlated with other varibales[@Ransom2019]. We reproduce it by incorporating additional covariates(e.g. $\theta_1$,$\theta_2$).
$\theta_1$ and $\theta_2$ are generated in a way that they are spatially autocorrelated respectively and they are irerelevant to yield response function but are somewhat correlated with a factor that is influential to yield. Here, we assume that $\theta_1$ and $\theta_2$ are correlated with $\beta$.\
Furthermore, it may be unrealistic to assume that each of the parameters of the "true" yield function($ymax$, $\alpha$, $\beta$) is directly measurable. In practice, more accessible <!-- variables or  -->measurments which are highly correlated with the target variable are alternatively used when target variable are difficult to measure[@puntel2019development]. In our case, for example, $ymax$ which indicate potential yield is not directly measurable. Instead of using $ymax$, some topographical land features and soil properties such as elevation and soil sand fraction could be used as yield-limitting factors[@jiang2004effect; @kravchenko2000correlation]. Following this way, we splitted each of the variables $ymax$, $\alpha$ and $\beta$ into two variables respectively(e.g. $\alpha_1$, $\alpha_2$, $\beta_1$, $\beta_2$, $ymax_1$, $ymax_2$). Each of the splitted variables are generated by multiplying a spatially autocorrelated split ratio to the original variables, and therefore, they also show spatially autocorrelated pattern.\
Using these variables, we created four sets of covariate groups. Each of them represents different assumptions about how much amount of information about yield response function the farmer has and whether target varibales that consist of the yield response function(e.g. $\alpha$, $\beta$, $ymax$) are directly measurable. \
<!-- It might be more understandable to explain using table -->
1. "aby" includes $\alpha$, $\beta$ and $ymax$; This refelcts the situation where the farmer knows the factors that affects yield and such factors are directly measurable \
2. "abytt" includes $\alpha$, $\beta$, $ymax$, $\theta_1$, $\theta_2$; This refelcts the situation where the farmer does not know about which factors affects yield but the factors that truely affects yield are directly measurable\
3. "aabbyy" includes $\alpha_1$, $\alpha_2$, $\beta_1$, $\beta_2$, $ymax_1$ and $ymax_2$; This refelcts the situation where the farmer knows the factors that affects yield but such factors are not directly measurable\
4. "aabbyytt" includes $\alpha_1$, $\alpha_2$, $\beta_1$, $\beta_2$, $ymax_1$ $ymax_2$, $\theta_1$, $\theta_2$; This refelcts the situation where the farmer does not know which factors affects yield and the factors that truely affects yield are also not directly measurable\
These four covariate groups are used in each ML methods. Hence, in each simulation round, sixteen model configurations(4 ML methods(RF, BRF, CF_stepwise, CF_base) $\times$ 4 covariate groups) are evaluated.

# Results and Discussions {-}

<!-- in that it can capture the valiability of site-specific optimal N rate for the field by correctly estimating causal effect of nitrogen to yield -->
Table \@ref(tab:table-simSummary) shows the summarised results of 1000 MonteCalro simulation rounds.<!--  Model evaluation was conducted based on avaraged $R^2$ values for both optimal N recommendation rates from ML methods and spatial smoothing by GAM. --> Across all the models, CF_base method consistently performed the best at capturing the variability of true optimal N rates, whereas the performance of RF was the worst. Including irrelevant varibles did not affect the perfomance of each ML methods seriously, indicating that all the ML methods successfully distinguish the important varibales for modeling the effect of N to yield. 
The differences in performance of each method are clrear in looking at Figure \@ref(fig:fig-distRes). Figure \@ref(fig:fig-distRes) shows the distributions of $R^2$ values derived from the estimates of ML methods. Most of the time, CF_base consistently produces much more accurate estimates of optimal N rate. 
Although both CF_stepwise and CF_base were based on the same ML method, the results of CF_stepwise are largly different from CF_base. On the contrary, the performace of CF_stepwise was not different from BRF. As explained in the previous section, CF_stepwise esitmates treatement effects of N rate relative to the next lower N rate. In this sense, we expected that CF_stepwise is relatively better at sensitively capturing heterogeneous change in yield accompanied by an additional N application. However, in finding profit-maximizing optimal N recommendation rate, the estimated treatment effects are added sequentially asuuming the linear relationship between each treatment effects and yield difference. 
Although CF can estimate unbised treatment effect, considering the fact that the each estimated treatment effects contain more or less uncertainty or noise originated from unobservable random error and model identification, taking sum of those estimated treatment effects is likely to inflate such uncertainty, resulting in over or underestimation of "true" incaseses in yield casued by an additional N application. Meanwhile, CF_base estimates the treatement effects of each N rates relative to $N_1$, and therfore it derives change in yield relative to the yield of $N_1$ directly. Hence, CF_base is less likely to suffer from such an error compared to CF_stepwise. \
Spatial smoothing considerably improved the accuracy of optimal N recommendation rates across all the sinarios.
Figure \@ref(fig:fig-distGamRes) shows the distributions of $R^2$ values of re-estimated optimal N rate by GAM. Compared to Figure \@ref(fig:fig-distRes), we can see the obvious differences in the shape of their distributions. Although the distributions of $R^2$ of RF are still almost flatten-out, the distributions of the other methods indicate that their estimates becomes to attain more precise and consistent for all the simulation rounds. The average improvement of $R^2$ values after Spatial smoothness are $0.153$ for RF, $0.185$ for BRF, $0.134$ for CF_stepwise and $0.127$ for CF_base. The degree of improvement of CF is smaller than for RF and BRF. This is because RF and BRF can estimate continuous yield response function and thus the resulting oprimal N recommendation rate are continuous values. They can easily be transformed to spatially smooth. Whereas, the values CF can pick up as optimal N rate are limited and discrete. Due to this restriction, it is hard for GAM to make generalize the results of CF. Still, spatially smoothed CF_base approach perfomed better in estimating optimal N rate than RF and BRF overall. It is noteworthy that $R^2$ value of CF_base under "aabbyytt" modeling sinario is $0.683$, which is comparable with the BRF $R^2$ value of $0.701$ under "aby" modeling sinario. This suggest that even though there exists high uncertainty in estimating underlying "true" yield response function, CF_base with spatially smoothing can achive reasonably robust estimatation for site-specific optimal N rate.\
<!-- Another important thing is to be noted is that even thoguth "aby" modelinng sinario reflects no uncertaity in 
indicating that spatial smoothing is helpful for explaining unobservable spatila structure  -->
<!-- try to exlain the behind mechanism of CF_base and why its performance is the best  -->
In summary, CF_base approach is generally superior to RF and BRF which are currentry widely used for site-specific nitrogen recommendation tool, and CF_base with spatial smoothing are robust even though we do not have sufficient knowledge about underlying "true" yield response function for a field, which is commmon case in practice.

# Conclusion {-}
<!-- - We showed that CF_base approach which forcus on heterogeneous treatment effects of N on yield response provides more precise N recommendation rate than RF and BRF.  -->
PA is a promissing technolody for modern agricultural production system to grasp spatial and temporal within-field heterogeneity. On-farm experiments incorporating PA tehcnology enables reaserchers and farmers to collect more spatially dense data related to the underlying heterogeneous yield response function <!-- site-specific field information --> and to conduct finer scale of an input management. Given the fact that an input for a biological crop systems are are higly complicated and involves numerous factors, ML methods is appealing as a tool to describe such an complex relationship and to derive the useful inforamtion for within-field site-specific input application. In this study, we considered N fertilizer as an input to be optimazed because N is an essential nutriant for crop growth and its usage has profound impact on both economics and environment. <!-- Past studies used prediction based ML methods represented by RF and BRF for N recommendation tools in an attempt to find the best prediction model that can account for the valiability of true optimal N. However, what we need to deal with in order to know site-specific optiomal N rate is to estimate the heterogeneous causal effect of a treatemtment N rate to yield. Prediction and causal inference are two different things and prediction itself cannot tell correct information about that. --> <!-- Based on the estimated treatement effects, we should make a dicision about how much amount of N fertilizer should be applied to each site.  -->
Acknowledging that site-specific optimal N recommendation should be based on a causal question, in this study, we proposed an approach using CF[@Wager2018a; @athey2016recursive] as the recommendation tool.<!-- CF is developed to estimate heterogeous treatment effects. --> We devised two approaches using CF; CF_stepwise and CF_base, and tested their performances as N rate recommendation tool comparing RF and BRF with 1000 rounds of Monte Calro simulations. The results suggested that CF_base approach shows the best at capturing the valiability of true optimal N rates compared to RF and BRF under all the model configurations. On the other hand, the performance of CF_stepwise did not change much from BRF overall. CF-stepwise is highly likely to suffer from the bias when predicting change in yield relative to the yield of the lowest N application rate, leading to inaccurate estimates of optimal N rate. 
Another our significant finding is that spatially generalizing the estimated optimal N recommendation rates results in considerable improvement in prediction accuracy of optimal N rate estimation. We applied GAM to the resulted optimal N rates incorporing geographical coordinates and soil and field properties as well. We confimed that spatial smoothing led to great improvement in $R^2$ of all the model configurations.\
Based on these findings, we concluded that estimation of causal impact of an input on yield is crucial for site-specific input recommendation. CF is a promising tool to do that without giveing up any strengths of ML methods that past studies put an values on. Especially, we found that the combination of CF_base and spatial smoothing is more reliable tool for site-specific input management tool compared to RF, BRF. Although we only considered a single input to be optimized for farm management, our methods can be expanded for multivariate input optimization.

# Limitations {-}
<!-- temporal variability may change the causal impact of inputs on yield if we didn't consider it-->
Even though our finding shows the comparative advantages of CF over RF and BRF, there is still much room to consider more in detial in applying CF-based approach in practice. 
MB function which we emploied as an underlying true yield response function to N may not enough to represent the complexity nature of the relationship between N and yield in the real corn production system. 
Especially, it fail to represent the temporal variation of optimal N rates. Site-specific optimal N rates vary annually partly due to the carryover effect of an N fertilizer and crop-management practices applied in the previous season on soil N in the next season[@puntel2018systems].<!-- cite more papers and talk about weather uncertainty--> Although consideration of such temporal variations in optimal N also important for site-specific N management[@mamo2003spatial;@dhital2016variability], simulated yield data with MB function in this study cannot tell those temporal variations becyase every simulation is conducted independently. It would be better if we could generate each season's yield data sequentially so that previous season's management dicision affect the next season's soil properties. Previous studies adopted crop simulation models such as Agricultural Production Systems sIMulator model to represent dynamic nature of cropping system in the context of nitrogen management[@archontoulis2020predicting;@puntel2018systems;@puntel2016modeling]. Therefore, it will be fruitful future work to explor the performance of CF-based approach based on more realistic data generated with those simulation models.

<!-- + We dismiss the dynamics nature of optimal N rates.  (solution: APSIM model[@puntel2018systems;@archontoulis2020predicting])
• our model(MB function) cannot fully account for dynamic properties of optimal N rates.
•  
• temporal variability
• "carryover effects on soil N, water, residue, and soil organic matter dynamics from 1 year to the next"
• Although past studies shows that such an complicated models did not necessarily result in the improvement in site-specific optimal N rate estimates, it is not still tested using CF.

+ We dismiss some other important facotrs related to management and environmental variables
• agronomic practices ('management operations(such as tillage, seeding, weed and pest management, irrigation, and harvest)' or crop-management practices)
• soil-plant-atomosphere system and uncertainty in weather[@puntel2016modeling]

+ we need to address the ex-ante
•  -->

<!-- 
Furthermore, we did not consider an input application error in our simulation. However, in practice, an input application error is highly likely to occure because machinery may fail to apply the accurate rate of an input simply due to the machinery error or topographical feature of the field. We need to address how this application error affect the performance of CF. Similary, measurement error could affect the performance of GAM in the from of attenuation bias.  -->

<!-- 1. yearly change -->
<!-- site-specific optimal N rate changes by yearly due to
  -->

<!-- "further advancement of crop simulators is crucial for validation and improvement of the current algolithm" -->
<!-- we consider  -->

# Acknowledgement {-}
This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled “Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management,” (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled “Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation” (Award Number NR213A7500013G021).

\newpage

# Tables 
```{r table-simSummary, tab.cap = "Summary of the 1000 Monte Calro simulation's results"}
table_res400_summary
```

<!-- ```{r table-2, tab.cap = "Results of model evaluation(sp_range=600)"}
table_res600
``` -->
\newpage

# Figures
<!-- 
1. add the distribution of the resutls
2. add the distribution of each parameters -->
<!-- when you mention a figure, use "\@ref(fig:fig-1)"  -->
```{r fig-parameters, fig.width=9, fig.height=10, fig.cap = "An Example of a Distribution Maps of Field Charateristics"}
# field_alpha + field_beta + field_ymax
grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2,nrow=2)
```

\newpage

```{r fig-optN,  fig.cap = "An Example of a Distribution Map of True Optimal Nitrogen Rate"}
field_optN
```

<!-- \newpage -->

<!-- ```{r fig-error,  fig.cap = "An Example of a Distribution Map of random yield disturbance"}
field_m_error
``` -->

```{r fig-nExp, fig.cap = "An Example of Experimental Design of Nitrogen"}
field_Ndesign
```

```{r fig-yield, fig.cap = "An Example of a Yield Distribution Map"}
field_yield
```

```{r fig-distRes, fig.width=7, fig.height=10, fig.cap = "Distributions of R squared values from 1000 Monte Calro Simulations before GAM is Applied"}
dist_case
```

```{r fig-distGamRes, fig.width=7, fig.height=10, fig.cap = "Distributions of R squared values from 1000 Monte Calro Simulations after GAM is Applied"}
dist_case_gam
```

# References

<div id="refs"></div>

### 2022-02-05 Codes/0_0_functions.R

@@ -1,0 +1,1359 @@
+# /*=================================================*/
+#' # Make experiment grids (basic cell, plot, strip)
+# /*=================================================*/
+make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
+
+  # /*=================================================*/
+  #' # Define functions
+  # /*=================================================*/
+  # /*----------------------------------*/
+  #' ## make polygons
+  # /*----------------------------------*/
+  make_polygon <- function(strt_point_new, multiplier, direction) {
+    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
+    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
+    point_3 <- point_2 + ab_xy_nml * cell_height
+    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
+
+    temp_polygon <- rbind(
+      point_1,
+      point_2,
+      point_3,
+      point_4,
+      point_1
+    ) %>%
+      list() %>%
+      st_polygon()
+
+    return(temp_polygon)
+  }
+
+  # /*----------------------------------*/
+  #' ## rotation matrix
+  # /*----------------------------------*/
+  rotate_mat_p90 <- matrix(
+    c(
+      cos(pi / 2),
+      sin(pi / 2),
+      -sin(pi / 2),
+      cos(pi / 2)
+    ),
+    nrow = 2
+  )
+
+  # /*----------------------------------*/
+  #' ## Make an extended line
+  # /*----------------------------------*/
+  # make line with starting point and a desired shift
+  make_extended_line <- function(starting_point, step, multiplier, step_v) {
+    extended_line <- rbind(
+      starting_point + step * multiplier,
+      starting_point + step_v * 1000 + step * multiplier
+    ) %>%
+      st_linestring() %>%
+      list() %>%
+      st_as_sfc() %>%
+      st_set_crs(st_crs(field))
+
+    return(extended_line)
+  }
+
+  # /*----------------------------------*/
+  #' ## Check intersections
+  # /*----------------------------------*/
+  # check the intersection of the lines in the direction specified
+  check_intersection <- function(field, step, direction, step_v) {
[…]

### 2022-02-05 Codes/0_1_functions_gen_field.R

@@ -1,0 +1,335 @@
+# /*=================================================*/
+#' # Make experiment grids (basic cell, plot, strip)
+# /*=================================================*/
+make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
+
+  # /*=================================================*/
+  #' # Define functions
+  # /*=================================================*/
+  # /*----------------------------------*/
+  #' ## make polygons
+  # /*----------------------------------*/
+  make_polygon <- function(strt_point_new, multiplier, direction) {
+    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
+    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
+    point_3 <- point_2 + ab_xy_nml * cell_height
+    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
+
+    temp_polygon <- rbind(
+      point_1,
+      point_2,
+      point_3,
+      point_4,
+      point_1
+    ) %>%
+      list() %>%
+      st_polygon()
+
+    return(temp_polygon)
+  }
+
+  # /*----------------------------------*/
+  #' ## rotation matrix
+  # /*----------------------------------*/
+  rotate_mat_p90 <- matrix(
+    c(
+      cos(pi / 2),
+      sin(pi / 2),
+      -sin(pi / 2),
+      cos(pi / 2)
+    ),
+    nrow = 2
+  )
+
+  # /*----------------------------------*/
+  #' ## Make an extended line
+  # /*----------------------------------*/
+  # make line with starting point and a desired shift
+  make_extended_line <- function(starting_point, step, multiplier, step_v) {
+    extended_line <- rbind(
+      starting_point + step * multiplier,
+      starting_point + step_v * 1000 + step * multiplier
+    ) %>%
+      st_linestring() %>%
+      list() %>%
+      st_as_sfc() %>%
+      st_set_crs(st_crs(field))
+
+    return(extended_line)
+  }
+
+  # /*----------------------------------*/
+  #' ## Check intersections
+  # /*----------------------------------*/
+  # check the intersection of the lines in the direction specified
[…]

### 2022-02-05 Codes/0_2_functions_gen_analysis_data.R

@@ -1,0 +1,368 @@
+# /*=================================================*/
+#' # Assign rates to the trial design data
+# /*=================================================*/
+# data_sf <- st_as_sf(data)
+# rates_ls <- N_levels
+
+
+assign_rates <- function(data_sf, rates_ls, pattern = "fixed-latin-square", merge = TRUE) {
+  gen_sequence <- function(length) {
+    if (length %% 2 == 0) {
+      seq_r <- c(seq(1, length, by = 2), seq(length, 2, by = -2))
+    } else {
+      seq_r <- c(seq(1, length, by = 2), seq(length - 1, 2, by = -2))
+    }
+    return(seq_r)
+  }
+
+  gen_rd_seq <- function(seq_element, num) {
+    for (i in 1:num) {
+      if (i == 1) {
+        seq_return <- seq_element
+      } else {
+        if (runif(1) < 0.5) {
+          # seq_return <- c(seq_return, rev(seq_element))
+          seq_return <- c(seq_return, seq_element)
+        } else {
+          seq_return <- c(seq_return, seq_element)
+        }
+      }
+    }
+    return(seq_return)
+  }
+
+  get_seq_for_strip <- function(pattern, rate_ranks_seq, num_seq, exclude_ls = NULL) {
+    seq_possible <- gen_rd_seq(rate_ranks_seq, num_seq)
+
+    position_ls <- 1:rates_len
+    remaining_positions <- position_ls[!(position_ls %in% exclude_ls)]
+
+    if (pattern == "block_randomized") {
+      if (length(remaining_positions) == 1) {
+        position <- remaining_positions
+      } else {
+        position <- sample(remaining_positions, 1)
+      }
+    } else if (pattern == "sequential") {
+      if (all(exclude_ls != 0)) {
+        previous_position <- exclude_ls[length(exclude_ls)]
+      } else {
+        previous_position <- 0
+      }
+      position <- previous_position + 1
+    } else if (pattern == "fixed-latin-square") {
+      if (all(exclude_ls != 0)) {
+        previous_position <- exclude_ls[length(exclude_ls)]
[…]

### 2022-02-05 Codes/0_3_functions_main_sim.R

@@ -1,0 +1,457 @@
+# /*----------------------------------*/
+#' ## Economic parameters
+# /*----------------------------------*/
+price_table <- data.table(
+  # === $/kg corn ===#
+  pCorn = round(c(3.5, 3.5, 5) * 200 / 5080, digits = 3),
+  # === $/kg N ===#
+  pN = round(c(0.4, 0.6, 0.4) / 0.453592, digits = 3)
+)
+
+
+# /*=================================================*/
+#' # Run main simulations
+# /*=================================================*/
+sim_par <- function(i, reg_data, test_data, N_levels) {
+  print(paste0("working on ", i, " th iteration."))
+  # for example
+  # reg_data = train_dt; test_data = test_dt; N_levels = N_levels
+
+  # /*----------------------------------*/
+  #' ## run ML analyses
+  # /*----------------------------------*/
+
+  ## == all the combinations of variables ==##
+  var_ls_variations <- list(
+    c("alpha", "beta", "ymax"),
+    c("alpha", "beta", "ymax", "theta_1", "theta_2"),
+    c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2"),
+    c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")
+  )
+
+  #--- all the cases to consider ---#
+  case_data <- expand.grid(
+    var_ls = var_ls_variations,
+    Method = c("CF_base", "BRF", "RF")    
+  ) %>%
+  tibble()
+
+
+  results_data <- case_data %>%
+    mutate(
+      opt_N_data = future_lapply(
+        seq_len(nrow(.)),
+        function(x) {
+          ### === apply various methods to get optimal N ===###
+          get_opt_N(
+            reg_data = reg_data,
+            test_data = test_data,
+            var_ls = .$var_ls[[x]],
+            rates_ls = N_levels,
+            Method = .$Method[[x]]
+          )
+        },
+        future.seed = TRUE
+      )
+    )%>%
+    unnest(., cols= "opt_N_data")%>%
+    data.table()%>%
+    setnames("unique_cell_id", "unique_subplot_id")
+
+  return(results_data)
+     
+}
+
+
+
+
+get_opt_N <- function(reg_data, test_data, var_ls, rates_ls, Method) {
+
[…]

### 2022-02-05 Codes/1_1_generate_field.R

@@ -1,0 +1,314 @@
+# /*=================================================*/
+#' # Preparation
+# /*=================================================*/
+
+library(here)
+library(tmap)
+library(sp)
+library(sf)
+library(agricolae)
+library(lwgeom)
+library(measurements)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(parallel)
+library(mapedit)
+
+
+#--- source functions ---#
+source(here("Codes", "0_0_functions.R"))
+
+#--- github ---#
+# source("https://raw.githubusercontent.com/brittanikedge/DIFM/main/Functions.R")
+
+# ==========================================================================
+#  1. Field Data
+# ==========================================================================
+
+ffy <- "Wendte_LaueLib80_2020"
+
+#--- field boundary ---#
+field <- ffy %>%
+  file.path(here("Data"), ., "Raw/boundary.shp") %>%
+  st_read() %>%
+  st_make_valid() %>%
+  st_transform_utm() %>%
+  st_buffer(60) %>%
+  st_bbox() %>%
+  st_as_sfc() %>%
+  st_as_sf()
+
+tm_shape(field) +
+  tm_borders()
+
+#--- bbox ---#
+wf_bbox <- st_bbox(field)
+
+#--- create ab-line ---#
+ab_line <- rbind(
+  c(wf_bbox["xmin"], wf_bbox["ymin"]),
+  c(wf_bbox["xmin"], wf_bbox["ymax"])
+) %>%
+  st_linestring()
+
+# /*=================================================*/
+#' # Create polygons (plots, harvester, applicator, planter)
+# /*=================================================*/
+# /*----------------------------------*/
+#' ## Set parameters
+# /*----------------------------------*/
+starting_point <- c(wf_bbox["xmin"] - 100, wf_bbox["ymin"] - 100)
+
+# use 60 ft design with 30 ft yield monitor
+cell_height <- conv_unit(10, "ft", "m")
+polygon_width <- conv_unit(60, "ft", "m")
+
+# /*----------------------------------*/
+#' ## Create polygons
+# /*----------------------------------*/
+# group: strip id
+# basic_plot_id: ids for the small polygons
+# plot_id: plot id
+
[…]

### 2022-02-05 Codes/2_1_generate_analysis_data.R

@@ -1,0 +1,77 @@
+# /*=================================================*/
+#' # Preparation
+# /*=================================================*/
+library(here)
+library(mgcv)
+library(ggplot2)
+library(grf)
+library(sf)
+library(measurements)
+library(data.table)
+library(tidyverse)
+library(future.apply)
+library(parallel)
+
+
+#--- source functions ---#
+source(here("GitControlled/Codes/0_2_function_gen_analysis_data.R"))
+
+# /*----------------------------------*/
+#' ## Datasets
+# /*----------------------------------*/
+# field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
+# coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds")))
+
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+
+# /*=================================================*/
+#' # Generate raw dataset (cell-level)
+# /*=================================================*/
+
+##== Generate Cell-Level Field Data ==##
+raw_data <- lapply(
+	1:1000, function(x) {
+		prepare_raw_data(
+			i = x,
+			field = field,
+			coef_data_m = coef_data[sim == x, ],
+			coef_data_t = coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ],
+			app_error="no"
+		)
+	}
+)
+
+# saveRDS(raw_data, here("Shared/Data/for_Simulations/raw_reg_test_data.rds"))
+reg_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
+test_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
+
+# saveRDS(reg_raw_data, here("Shared/Data/for_Simulations/reg_raw_data.rds"))
+# saveRDS(test_raw_data, here("Shared/Data/for_Simulations/test_raw_data.rds"))
+
+# /*=================================================*/
+#' # Generate analysis dataset (subplot-level)
+# /*=================================================*/
+reg_raw_data <- readRDS(here("Shared/Data/for_Simulations/reg_raw_data.rds"))
+test_raw_data <- readRDS(here("Shared/Data/for_Simulations/test_raw_data.rds"))
+
+##== Aggregate Cell-Level Field Data to Subplot-Level Field Data ==##
+sim_data <- lapply(
[…]

### 2022-02-05 Codes/3_1_SimDataAnalysis.R

@@ -1,0 +1,232 @@
+#/*----------------------------------*/
+#' ## Preparation 
+#/*----------------------------------*/
+library(here)
+library(data.table)
+library(RColorBrewer)
+library(patchwork)
+library(ggplot2)
+library(ggthemes)
+library(viridis)
+library(hrbrthemes)
+library(tidyverse)
+library(ggpubr)
+library(here)
+
+source(here("GitControlled/Codes/0_2_functions_gen_analysis_data.R"))
+source(here("GitControlled/Codes/0_3_functions_main_sim.R"))
+
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+# === Training and Testing data sets === #
+reg_data_all <- readRDS("./Shared/Data/for_Simulations/reg_data.rds")
+test_data_all <- readRDS("./Shared/Data/for_Simulations/test_data.rds")
+
+source_dt <- 
+    bind_rows(reg_data_all, test_data_all, .id = "type") %>%
+    .[padding==1, .(sim, type, unique_cell_id, alpha, beta, ymax)] %>%
+    .[,type := case_when(type == "1" ~ "train", type == "2" ~ "test")] %>%
+    setnames('unique_cell_id', "unique_subplot_id")
+
+# ==========================================================================
+# Results of RF, BRF and CF
+# ==========================================================================
+
+# === All Results === #
+simRes_all <- 
+    readRDS(here("Shared/Results_journal/SimRes_all.rds")) %>%
+    .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
+    .[, Method := factor(Method, levels = c("RF", "BRF", "CF_base"))] 
+
+# === function for RMSE calculation === #
+rmse_general <-function(preds,actual){ 
+  sqrt(mean((actual - preds)^2))
+}
+
+
+# /*=================================================*/
+#' # RMSE of EONRs and Profit Loss calculation
+# /*=================================================*/
+pi_loss_dt <- source_dt %>%
[…]

### 2022-02-05 Codes/3_3_Stepwise_vs_Base.R

@@ -1,0 +1,222 @@
+
+# /*=================================================*/
+#' # Preparation
+# /*=================================================*/
+
+library(here)
+library(tmap)
+library(ggplot2)
+library(ggthemes)
+library(grf)
+library(sf)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(parallel)
+`
+# =========================
+# Preparation
+# =========================
+#--- source functions ---#
+source(here("Gitcontrolled", "Codes", "0_0_functions.R"))
+# source(here("Gitcontrolled", "Codes", "functions_stepwise_vs_base.R"))
+
+# field <- readRDS(here("Shared", "Data", "for_Simulations", "field_padding.rds")) %>%
+#   cbind(., st_coordinates(st_centroid(.)))
+
+# # === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+# sp_range=400
+# coef_data <- readRDS(here("Shared", "Data", "Simulations", paste0("coefficients_sprange_", sp_range, ".rds")))
+
+# ==========================================================================
+# Function 
+# ==========================================================================
+
+tre_eval_function <- function(reg_data, test_data, var_ls){
+	# x = 1
+	# reg_data = reg_data_all[sim==x&padding==1,]
+	# test_data = test_subplot_data_all[sim==x&padding==1,]
+	# var_ls = c("alpha","beta","ymax")
+	# print(paste0("working on ", x, " th iteration."))
+
+	N_levels <- reg_data[,rate]%>%unique()%>%sort()
+
+	##== CF-stepwiese ==##
+	CF_stepwise_te_dt <- CF_analysis(
+		reg_data=reg_data, 
+		var_ls=var_ls, 
+		cl_var = NA) %>%
+  CF_stepwise_calculate_te(
+    test_data = test_data, 
+    cf_results = ., 
+    var_ls = var_ls, 
+    rates_ls = N_levels)%>%
+  	.[,Method := "CF_stepwise"] %>%
+  	setnames("tau_stepwise", "tau_hat")
+
+
+  ####==== CF-base =====#####
+	CF_base_te_dt <- CF_analysis_base(
+    reg_data=reg_data, 
+    var_ls=var_ls, 
[…]

### 2022-02-05 Codes/PrepareResults.R

@@ -1,0 +1,1221 @@
+## -----------------------------------------------
+library(knitr)
+# library(here)
+
+knitr::opts_chunk$set(
+    cache = FALSE,
+    warning = FALSE,
+    message = FALSE
+    )
+
+# opts_knit$set(root.dir=here())
+opts_knit$set(root.dir = "~/Dropbox/ResearchProject/ML_VRA")
+
+
+## ---- cache = FALSE-----------------------------
+# === packages ===#
+library(sf)
+library(data.table)
+library(RColorBrewer)
+library(patchwork)
+library(grf)
+library(magrittr)
+library(ggplot2)
+library(ggthemes)
+library(viridis)
+library(tidyverse)
+library(ggpubr)
+library(flextable)
+library(officer)
+library(officedown)
+library(modelsummary)
+library(here)
+library(gridExtra)
+library(DiagrammeR)
+library(latex2exp)
+
+here::i_am("GitControlled/Codes/0_0_functions.R")
+
+## ----source, results = "hide", fig.show='hide', cache = FALSE-----------------
+# setwd(here())
+source("./GitControlled/Codes/0_0_functions.R")
+# source("./GitControlled/Codes/functions_stepwise_vs_base.R")
+
+
+## ----setup, warning=FALSE, message=FALSE, cache= TRUE----
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+sp_range <- 400
+
+field <- readRDS("./Shared/Data/for_Simulations/field_padding.rds") %>%
+    filter(padding==1)%>%
+    dplyr::select(unique_cell_id)
+
+
+####==== (1) cell-level dataset ====####
+# coef_data <- readRDS("./Shared/Data/for_Simulations/cnn_coefficients_sprange_400.rds")
+
+# x=1
+# coef_data_m <- coef_data[sim == x, ]
+# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
+
+# sample_dt <- prepare_raw_data(1, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no")
+
+# sample_training_cell <- sample_dt$reg_raw_data
+
+# saveRDS(sample_training_cell, "./Shared/Data/for_writing/sample_reg_raw_data.rds")
+
+
[…]

### 2022-02-05 Codes/functions_stepwise_vs_base.R

@@ -1,0 +1,625 @@
+
+# ==========================================================================
+#' Gaol: I want to chech the performacne of treatement effect estimation 
+#' between CF-stepwise and CF-base.
+#' 
+#'  
+# ==========================================================================
+
+prepare_data_step_base <- function(field, coef_data_m, coef_data_t) {
+  # x=1
+  # field=field; coef_data_m=coef_data[sim == x, ]; coef_data_t=coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
+  
+  # /*~~~~~~~~~~~~~~~~~~~~~~*/
+  #' ### Data preparation
+  # /*~~~~~~~~~~~~~~~~~~~~~~*/
+  # === merge field data with the coefs data ===#
+  data <- coef_data_m[data.table(field), on = "unique_cell_id"] %>%
+    .[, opt_N := (log(pN) - log(-pCorn * ymax * beta) - alpha) / beta]
+
+  test_data <- coef_data_t[data.table(field), on = "unique_cell_id"] %>%
+    .[, opt_N := (log(pN) - log(-pCorn * ymax * beta) - alpha) / beta]
+
+  # ggplot(st_as_sf(data)) +
+  #   geom_sf(aes(fill = cluster_id_1), size = 0) +
+  #   scale_fill_viridis_c()
+
+  # === check the spatial distribution of optimal N ===#
+  # left_join(field,data[,.(unique_cell_id,opt_N)],by='unique_cell_id') %>%
+  #   select(opt_N) %>%
+  #   tm_shape() +
+  #     tm_fill(col = "opt_N")
+
+  # /*~~~~~~~~~~~~~~~~~~~~~~*/
+  #' ### Assign N (5 treatment levels)
+  # /*~~~~~~~~~~~~~~~~~~~~~~*/
+  # === define experimental N rate ===#
+  all_opt_N <- data[, opt_N]
+
+  # --- for training ---#
+  # hist(all_opt_N)
+  N_levels <- seq(
+    quantile(all_opt_N, prob = 0.05) - 20,
+    quantile(all_opt_N, prob = 0.95) + 20,
+    length = 5 
+  ) %>%
+    round()
+
+  # data <- assign_rates(st_as_sf(data), N_levels, pattern = "sequential") %>%
+  data <- assign_rates(st_as_sf(data), N_levels) %>% # N_levels are assigned as "rate" variable
[…]

### 2022-02-05 Codes/others/CNN_PrepareResults.R

@@ -1,0 +1,862 @@
+library(sf)
+library(data.table)
+library(RColorBrewer)
+library(patchwork)
+library(grf)
+library(magrittr)
+library(ggplot2)
+library(ggthemes)
+library(viridis)
+library(tidyverse)
+library(ggpubr)
+library(flextable)
+library(officer)
+library(modelsummary)
+library(here)
+library(gridExtra)
+library(DiagrammeR)
+library(causalTree)
+library(rpart)
+library(rattle)
+library(sparkline)
+library(htmltools)
+library(htmlwidgets)
+library(equatags)
+library(equatiomatic)
+# ===================================
+# Load the data
+# ===================================
+source(here("Codes", "functions.R"))
+source(here("Codes", "functions_stepwise_vs_base.R"))
+
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+# ===================================
+# sample data creation 
+# ===================================
+field <- readRDS(here("Data", "Simulations", "field.rds")) %>%
+  cbind(., st_coordinates(st_centroid(.)))
+
+coef_data <- readRDS(here("Data", "Simulations", paste0("coefficients_sprange_600.rds")))
+
+coef_data_m <- coef_data[sim == 1, ]
+
+# data <- coef_data_m[data.table(field), on = "unique_cell_id"] %>%
+#     .[, opt_N := (log(pN) - log(-pCorn * ymax * beta) - alpha) / beta]
+
+# all_opt_N <- data[, opt_N]
+
+# # --- for training ---#
+# # hist(all_opt_N)
+# N_levels <- seq(
+#   quantile(all_opt_N, prob = 0.05) - 20,
+#   quantile(all_opt_N, prob = 0.95) + 20,
+#   length = 5
+#       ) %>%
+# round()
+
+# # data <- assign_rates(st_as_sf(data), N_levels, pattern = "sequential") %>%
+# data <- assign_rates(st_as_sf(data), N_levels) %>%
+#   data.table()
+
+
+# data %<>% .[, det_yield := gen_yield_MB(ymax, alpha, beta, rate)] %>%
+#     # .[,det_yield:=b0+b1*N+b2*N^2] %>%
+#     # === error ===#
+#     .[, yield := det_yield * (1 + m_error)] %>%
[…]

### 2022-02-05 Codes/others/CNN_ex_code_modified.R

@@ -1,0 +1,192 @@
+# ==========================================================================
+#' This is just an example code  for demonstration purposes
+# ==========================================================================
+
+
+library(grf) # if you don't have one, "install.packages("grf")"
+library(data.table) #if you don't have one, "install.packages("data.table")"
+library(tidyverse) #if you don't have one, "install.packages("tidyverse")"
+library(parallel) #if you don't have one, "install.packages("parallel")"
+
+
+
+# ==========================================================================
+# Load sample training and testing data
+# ==========================================================================
+#' Please note that the data(for training and testing) we are using for CF, RF and BRF are slightly different from the data for CNN.
+#' The data for CNN is more finer scale(cell-level), so your data should have more number of rows in the data.
+
+#' The shared data contains the data for just first three simulation rounds(sim=1,2,3)
+
+# === load training and testing data === # 
+# Please change the path to the folder where you downloaded and saved them
+train_data_all <- readRDS("~/OneDrive\ -\ University\ of\ Nebraska-Lincoln/ML_VRA/Data/CNN_demo/demo_train_dt.rds")
+test_data_all <- readRDS("~/OneDrive\ -\ University\ of\ Nebraska-Lincoln/ML_VRA/Data/CNN_demo/demo_test_dt.rds")
+
+
+
+# === prices ===#
+pCorn <- 0.138
+pN <- 1.323
+
+
+# /*====================================================================================*/
+#' Simulation example
+#' This is using two functions(sim_par() and BRF_analysis()) which are defined in the below
+#' So, please load them first, then run the below code
+#' 
+#' The idea is that we just reapeat the same process(training the model and testing)
+#' 
+# /*====================================================================================*/
+sim_results <- lapply(
+    1:2, function(x) {
+      sim_par(
+        i = x,
+        reg_data = train_data_all[sim==x & padding==1,], #<- padding==1 is just for our methods.
+        test_data = test_data_all[sim==x & padding==1,]
+      )
+    }
+  ) %>%
[…]

### 2022-02-05 Codes/others/cnn_honesty_yield_pred_function.R

@@ -1,0 +1,1735 @@
+# /*=================================================*/
+#' # Make experiment grids (basic cell, plot, strip)
+# /*=================================================*/
+make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
+
+  # /*=================================================*/
+  #' # Define functions
+  # /*=================================================*/
+  # /*----------------------------------*/
+  #' ## make polygons
+  # /*----------------------------------*/
+  make_polygon <- function(strt_point_new, multiplier, direction) {
+    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
+    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
+    point_3 <- point_2 + ab_xy_nml * cell_height
+    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
+
+    temp_polygon <- rbind(
+      point_1,
+      point_2,
+      point_3,
+      point_4,
+      point_1
+    ) %>%
+      list() %>%
+      st_polygon()
+
+    return(temp_polygon)
+  }
+
+  # /*----------------------------------*/
+  #' ## rotation matrix
+  # /*----------------------------------*/
+  rotate_mat_p90 <- matrix(
+    c(
+      cos(pi / 2),
+      sin(pi / 2),
+      -sin(pi / 2),
+      cos(pi / 2)
+    ),
+    nrow = 2
+  )
+
+  # /*----------------------------------*/
+  #' ## Make an extended line
+  # /*----------------------------------*/
+  # make line with starting point and a desired shift
+  make_extended_line <- function(starting_point, step, multiplier, step_v) {
+    extended_line <- rbind(
+      starting_point + step * multiplier,
+      starting_point + step_v * 1000 + step * multiplier
+    ) %>%
+      st_linestring() %>%
+      list() %>%
+      st_as_sfc() %>%
+      st_set_crs(st_crs(field))
+
+    return(extended_line)
+  }
+
+  # /*----------------------------------*/
+  #' ## Check intersections
+  # /*----------------------------------*/
+  # check the intersection of the lines in the direction specified
+  check_intersection <- function(field, step, direction, step_v) {
[…]

### 2022-02-05 Codes/others/cnn_prepare_data.R

@@ -1,0 +1,309 @@
+library(here)
+library(mgcv)
+library(tmap)
+library(ggplot2)
+library(grf)
+library(sp)
+library(sf)
+library(agricolae)
+library(lwgeom)
+library(measurements)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(future.apply)
+library(parallel)
+
+
+#--- source functions ---#
+source(here("Codes", "functions.R"))
+
+# /*----------------------------------*/
+#' ## Datasets
+# /*----------------------------------*/
+field_cnn <- readRDS(here("Data", "CNN_Simulations", "cnn_field_padding.rds"))
+
+# ggplot(st_as_sf(field_dt)) +
+#   geom_sf(aes(fill = cluster_id_1), size = 0) +
+#   geom_sf_text(aes(label = cluster_id_1))
+sp_range=400
+
+cnn_coef_data <- readRDS(here("Data", "CNN_Simulations", paste0('cnn_coefficients_sprange_',sp_range,'.rds')))
+
+
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+
+
+# For example
+x=2
+field=field_cnn
+coef_data_m=cnn_coef_data[sim == x, ]
+# coef_data_t=coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
+
+# /*~~~~~~~~~~~~~~~~~~~~~~*/
+#' ### Data preparation
+# /*~~~~~~~~~~~~~~~~~~~~~~*/
+# === merge field data with the coefs data ===#
+data <- coef_data_m[data.table(field), on = "unique_cell_id"] %>%
+  .[, opt_N := (log(pN) - log(-pCorn * ymax * beta) - alpha) / beta]
+
+
+# test_data <- coef_data_t[data.table(field), on = "unique_cell_id"] %>%
+# .[, opt_N := (log(pN) - log(-pCorn * ymax * beta) - alpha) / beta]
+
+
+# === check the spatial distribution of optimal N ===#
+# ggplot(st_as_sf(data)) +
+#   geom_sf(aes(fill = opt_N),size = 0)+
+#   scale_fill_viridis_c()
+
+# /*~~~~~~~~~~~~~~~~~~~~~~*/
+#' ### Assign N (5 N treatment rates)
+# /*~~~~~~~~~~~~~~~~~~~~~~*/
[…]

### 2022-02-05 Codes/others/cnn_related_functions_subplot.R

@@ -1,0 +1,1834 @@
+# /*=================================================*/
+#' # Make experiment grids (basic cell, plot, strip)
+# /*=================================================*/
+make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
+
+  # /*=================================================*/
+  #' # Define functions
+  # /*=================================================*/
+  # /*----------------------------------*/
+  #' ## make polygons
+  # /*----------------------------------*/
+  make_polygon <- function(strt_point_new, multiplier, direction) {
+    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
+    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
+    point_3 <- point_2 + ab_xy_nml * cell_height
+    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
+
+    temp_polygon <- rbind(
+      point_1,
+      point_2,
+      point_3,
+      point_4,
+      point_1
+    ) %>%
+      list() %>%
+      st_polygon()
+
+    return(temp_polygon)
+  }
+
+  # /*----------------------------------*/
+  #' ## rotation matrix
+  # /*----------------------------------*/
+  rotate_mat_p90 <- matrix(
+    c(
+      cos(pi / 2),
+      sin(pi / 2),
+      -sin(pi / 2),
+      cos(pi / 2)
+    ),
+    nrow = 2
+  )
+
+  # /*----------------------------------*/
+  #' ## Make an extended line
+  # /*----------------------------------*/
+  # make line with starting point and a desired shift
+  make_extended_line <- function(starting_point, step, multiplier, step_v) {
+    extended_line <- rbind(
+      starting_point + step * multiplier,
+      starting_point + step_v * 1000 + step * multiplier
+    ) %>%
+      st_linestring() %>%
+      list() %>%
+      st_as_sfc() %>%
+      st_set_crs(st_crs(field))
+
+    return(extended_line)
+  }
+
+  # /*----------------------------------*/
+  #' ## Check intersections
+  # /*----------------------------------*/
+  # check the intersection of the lines in the direction specified
+  check_intersection <- function(field, step, direction, step_v) {
[…]

### 2022-02-05 Codes/others/cnn_simulate_yield.R

@@ -1,0 +1,146 @@
+# /*=================================================*/
+#' # Preparation
+# /*=================================================*/
+library(here)
+library(mgcv)
+library(tmap)
+library(ggplot2)
+library(grf)
+library(sp)
+library(sf)
+library(agricolae)
+library(lwgeom)
+library(measurements)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(future.apply)
+library(parallel)
+
+
+#--- source functions ---#
+source(here("Codes", "cnn_honesty_yield_pred_function.R"))
+
+# /*----------------------------------*/
+#' ## Datasets
+# /*----------------------------------*/
+field_cnn <- readRDS(here("Data", "CNN_Simulations", "cnn_field_padding.rds"))
+
+# ggplot(field_cnn) +
+#   geom_sf()
+
+# ggplot(field_cnn) +
+#   geom_sf(aes(fill = factor(padding)), size = 0)
+
+sp_range=400
+
+# coef_data <- readRDS(here("Data", "CNN_Simulations", paste0('cnn_coefficients_sprange_',sp_range,'.rds')))
+
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+
+# /*=================================================*/
+#' # Simulation
+# /*=================================================*/
+train_data <- readRDS(here("Data", "CNN_Simulations", "reg_data.rds"))
+test_data <- readRDS(here("Data", "CNN_Simulations", "test_agg_data.rds"))
+
+
+sim_results <- lapply(
+	  1:100, function(x) {
+	    sim_par(
+	      i = x,
+	      reg_data = train_data[sim==x&padding==1,],
+	      test_agg_data = test_data[sim==x&padding==1,]
+	    )
+	  }
+	) %>%
+	rbindlist()%>%
+	rowwise() %>%
+	mutate(var_ls_name = paste0(var_ls, collapse = "_")) %>%
+	data.table()%>%
+	.[, var_case := factor(var_ls_name)] %>%
+	.[, .(sim, honesty,  model, var_case, r2_y)] %>%
+	.[, var_case := case_when(
[…]

### 2022-02-05 Codes/others/ex_code_for_yield_prediction.R

@@ -1,0 +1,92 @@
+# ==========================================================================
+#' Just for yield prediction with varioius N rates
+# ==========================================================================
+
+
+library(grf) # if you don't have one, "install.packages("grf")"
+library(data.table) #if you don't have one, "install.packages("data.table")"
+library(tidyverse) #if you don't have one, "install.packages("tidyverse")"
+library(parallel) #if you don't have one, "install.packages("parallel")"
+
+
+
+# === load training and testing data === # 
+#' Please note that the data(for training and testing) we are using for CF, RF and BRF are slightly different from the data for CNN.
+#' The data for CNN is more finer scale(cell-level), so your data should have more number of rows in the data.
+
+#' The shared data contains the data for just first three simulation rounds(sim=1,2,3)
+
+# Please change the path to the folder where you downloaded and saved them
+train_data_all <- readRDS("~/OneDrive\ -\ University\ of\ Nebraska-Lincoln/ML_VRA/Data/CNN_demo/demo_train_dt.rds")
+test_data_all <- readRDS("~/OneDrive\ -\ University\ of\ Nebraska-Lincoln/ML_VRA/Data/CNN_demo/demo_test_dt.rds")
+
+
+
+#=== for example (the simplest modeling scenario)===#
+var_case <- c("alpha", "beta", "ymax")
+
+
+
+#=== demostration of yield prediction with BRF ===#
+sim_res <- lapply(
+	1:3, function(x){
+	BRF_prediction(
+		i = x,
+		reg_data = train_data_all[sim==x & padding==1,], #<- padding==1 is just for our methods.
+        test_data = test_data_all[sim==x & padding==1,], #<- padding==1 is just for our methods.
+        var_ls = var_case
+		)
+	}
+)%>%
+rbindlist()
+
+
+
+
+
+#=== this is the function of BRF for yield prediction ===#
+BRF_prediction <- function(i, reg_data, test_data, var_ls) {
+  print(paste0("working on ", i, " th iteration."))
+  # For example,
+  # i=1
+  # reg_data = train_data_all[sim==1 & padding==1,]
+  # test_data = test_data_all[sim==1 & padding==1,]
+  # var_ls = c("alpha", "beta", "ymax")
+
+  # /*----------------------------------*/
+  #' Training Boosted random forest
+  # /*----------------------------------*/
[…]

### 2022-02-05 Codes/others/res_CNNvsForest.R

@@ -1,0 +1,394 @@
+# /*=================================================*/
+#' # Preparation
+# /*=================================================*/
+
+library(here)
+library(ggplot2)
+library(grf)
+library(sf)
+library(data.table)
+library(tidyverse)
+
+#--- source functions ---#
+source(here("Codes", "cnn_related_functions.R")) 
+
+#--- field ---#
+# field_cnn <- readRDS(here("Data", "CNN_Simulations", "cnn_field_padding.rds"))
+
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+#---training dataset ---#
+# raw_data <- readRDS(here("Results","cnn_raw_data_1 (1).rds"))%>%
+# 	.[,unique_cell_id := paste0(strip_id,"_",subplot_id)] %>% 
+#   .[padding==1,]
+
+reg_data <- readRDS(here("Results","cnn_reg_data_1 (1).rds"))%>%
+  .[,unique_cell_id := paste0(strip_id,"_",subplot_id)]
+
+
+reg_data_forest <- copy(reg_data) %>% 
+  .[padding==1,]
+
+# reg_data_forest$rate %>% unique() %>% sort()
+
+
+#---training dataset ---#
+test_raw_data <- readRDS(here("Results","cnn_raw_data_2 (1).rds"))
+
+
+test_agg_data <- readRDS(here("Results","cnn_reg_data_2 (1).rds"))%>%
+	.[,unique_cell_id := paste0(strip_id,"_",subplot_id)] %>%
+  .[, `:=`(
+    strip_id = NULL,
+    subplot_id = NULL
+  )]
+
+test_agg_data$rate %>% unique()
+
+
+# "cnn_reg_data_2 (1).rds" is the same as this one
+test_agg_data_opt_N <- test_raw_data[, .(
+    yield = mean(yield),
+    opt_N = mean(opt_N),
+    rate = mean(rate),
+    alpha = mean(alpha),
+    beta = mean(beta),
+    ymax = mean(ymax),
+    alpha1 = mean(alpha1),
+    alpha2 = mean(alpha2),
+    beta1 = mean(beta1),
+    beta2 = mean(beta2),
+    ymax1 = mean(ymax1),
+    ymax2 = mean(ymax2),
+    theta_1 = mean(theta_1),
+    theta_2 = mean(theta_2),
[…]

### 2022-02-05 Codes/temp_sim/0_functions.R

@@ -1,0 +1,1625 @@
+# /*=================================================*/
+#' # Make experiment grids (basic cell, plot, strip)
+# /*=================================================*/
+make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
+
+  # /*=================================================*/
+  #' # Define functions
+  # /*=================================================*/
+  # /*----------------------------------*/
+  #' ## make polygons
+  # /*----------------------------------*/
+  make_polygon <- function(strt_point_new, multiplier, direction) {
+    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
+    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
+    point_3 <- point_2 + ab_xy_nml * cell_height
+    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
+
+    temp_polygon <- rbind(
+      point_1,
+      point_2,
+      point_3,
+      point_4,
+      point_1
+    ) %>%
+      list() %>%
+      st_polygon()
+
+    return(temp_polygon)
+  }
+
+  # /*----------------------------------*/
+  #' ## rotation matrix
+  # /*----------------------------------*/
+  rotate_mat_p90 <- matrix(
+    c(
+      cos(pi / 2),
+      sin(pi / 2),
+      -sin(pi / 2),
+      cos(pi / 2)
+    ),
+    nrow = 2
+  )
+
+  # /*----------------------------------*/
+  #' ## Make an extended line
+  # /*----------------------------------*/
+  # make line with starting point and a desired shift
+  make_extended_line <- function(starting_point, step, multiplier, step_v) {
+    extended_line <- rbind(
+      starting_point + step * multiplier,
+      starting_point + step_v * 1000 + step * multiplier
+    ) %>%
+      st_linestring() %>%
+      list() %>%
+      st_as_sfc() %>%
+      st_set_crs(st_crs(field))
+
+    return(extended_line)
+  }
+
+  # /*----------------------------------*/
+  #' ## Check intersections
+  # /*----------------------------------*/
+  # check the intersection of the lines in the direction specified
+  check_intersection <- function(field, step, direction, step_v) {
[…]

### 2022-02-05 Codes/temp_sim/1_simulate.R

@@ -1,0 +1,154 @@
+# /*=================================================*/
+#' # Preparation
+# /*=================================================*/
+library(here)
+library(mgcv)
+library(ggplot2)
+library(grf)
+library(sf)
+library(measurements)
+library(data.table)
+library(tidyverse)
+library(future.apply)
+library(parallel)
+
+
+#--- source functions ---#
+source(here("GitControlled", "Codes", "temp_sim", "0_functions.R"))
+
+# /*----------------------------------*/
+#' ## Datasets
+# /*----------------------------------*/
+# field <- readRDS(here("Shared", "Data", "for_Simulations", "field_padding.rds"))
+
+sp_range=400
+
+# coef_data <- readRDS(here("Shared", "Data", "for_Simulations", paste0('coefficients_sprange_',sp_range,'.rds')))
+
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+
+# /*=================================================*/
+#' # Generate dataset 
+# /*=================================================*/
+
+##== Generate Cell-Level Field Data ==##
+raw_data <- lapply(
+	1:1000, function(x) {
+		prepare_raw_data(
+			i = x,
+			field = field,
+			coef_data_m = coef_data[sim == x, ],
+			coef_data_t = coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ],
+			app_error="no"
+		)
+	}
+)
+
+# saveRDS(raw_data, here("Shared", "Data", "for_Simulations", "raw_reg_test_data.rds"))
+reg_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
+test_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
+
+# saveRDS(reg_raw_data, here("Shared", "Data", "for_Simulations", "reg_raw_data.rds"))
+# saveRDS(test_raw_data, here("Shared", "Data", "for_Simulations", "test_raw_data.rds"))
+
+##== Aggregate Cell-Level Field Data to Subplot-Level Field Data ==##
+sim_data <- lapply(
+	1:1000, function(x) {
+		print(paste0("working on ", x, " th iteration."))
+		prepare_data_for_sim(
[…]

### 2022-02-05 Presentation/OFE_Presentation/PrepareResults_presen.R

@@ -1,0 +1,384 @@
+## -----------------------------------------------------------------------------
+library(knitr)
+library(here)
+knitr::opts_chunk$set(
+	cache = FALSE,
+	warning = FALSE,
+	message = FALSE
+	)
+
+opts_knit$set(root.dir=here())
+
+
+## ---- cache = FALSE-----------------------------------------------------------
+# === packages ===#
+library(sf)
+library(data.table)
+library(RColorBrewer)
+library(patchwork)
+library(grf)
+library(magrittr)
+library(ggplot2)
+library(ggthemes)
+library(viridis)
+library(tidyverse)
+library(ggpubr)
+library(flextable)
+library(officer)
+library(modelsummary)
+library(here)
+library(gridExtra)
+library(DiagrammeR)
+library(causalTree)
+library(rpart)
+library(rattle)
+library(webshot2) # remotes::install_github("rstudio/webshot2")
+# library(sparkline)
+# library(htmltools)
+# library(htmlwidgets)
+# library(equatags)
+# library(equatiomatic)
+
+
+
+## ----source, results = "hide", fig.show='hide', cache = FALSE-----------------
+# source(here("Codes", "functions.R"))
+source(here("Codes", "0_0_functions.R"))
+source(here("Codes", "functions_stepwise_vs_base.R"))
+
+
+## ----source-results, message=FALSE, warning=FALSE-----------------------------
+
+# ===================================
+# Forest resutls 
+# ===================================
+
+res_forest_all_honesty <- readRDS(here("Results", "CNN", "SimRes_sp_400.rds"))%>%
+    setnames("model", "Method")%>%
+    .[, var_case:=factor(var_case, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
+    .[, Method:=factor(Method, levels = c("RF", "BRF", "CF_stepwise", "CF_base"))]%>%
+    .[, Honesty := TRUE]
+
+
+res_forest_all_nohonesty <- readRDS(here("Results", "CNN", "SimRes_sp_400_nohonesty.rds"))%>%
+    setnames("model", "Method")%>%
[…]

### 2022-02-05 GitControlled/Presentation/OFE_Presentation/PrepareResults_presen.Rmd
Large revise of the manuscript and codes for re-submission

---
title: "Machine Learning Methods for Site-specific Input Management"
author: Shunkei Kakimto
output: word_document
---

```{r}
library(knitr)
library(here)
knitr::opts_chunk$set(
	cache = FALSE,
	warning = FALSE,
	message = FALSE
	)

opts_knit$set(root.dir=here())
```

```{r, cache = FALSE}
# === packages ===#
library(sf)
library(data.table)
library(RColorBrewer)
library(patchwork)
library(grf)
library(magrittr)
library(ggplot2)
library(ggthemes)
library(viridis)
library(tidyverse)
library(ggpubr)
library(flextable)
library(officer)
library(modelsummary)
library(here)
library(gridExtra)
library(DiagrammeR)
library(causalTree)
library(rpart)
library(rattle)
library(webshot2) # remotes::install_github("rstudio/webshot2")
# library(sparkline)
# library(htmltools)
# library(htmlwidgets)
# library(equatags)
# library(equatiomatic)

```

# Load the data

```{r source, results = "hide", fig.show='hide', cache = FALSE }
# source(here("Codes", "functions.R"))
source(here("GitControlled","Codes", "0_0_functions.R"))
# source(here("GitControlled","Codes", "functions_stepwise_vs_base.R"))
```

# Results

## Source Results and Preparation

```{r source-results, message=FALSE, warning=FALSE}

# ===================================
# Forest resutls 
# ===================================

res_forest_all_honesty <- readRDS(here("Shared", "Results", "CNN", "SimRes_sp_400.rds"))%>%
    setnames("model", "Method")%>%
    .[, var_case:=factor(var_case, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
    .[, Method:=factor(Method, levels = c("RF", "BRF", "CF_stepwise", "CF_base"))]%>%
    .[, Honesty := TRUE]

res_forest_all_nohonesty <- readRDS(here("Shared", "Results", "CNN", "SimRes_sp_400_nohonesty.rds"))%>%
    setnames("model", "Method")%>%
    .[, var_case:=factor(var_case, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
    .[, Method:=factor(Method, levels = c("RF", "BRF", "CF_stepwise", "CF_base"))]%>%
    .[, Honesty := FALSE]

CNN_y_eval_v1 <- readRDS(here("Shared", "Results", "CNN", "CNN_y_eval_v1.rds"))%>%
    .[,r2_y_cell:=NA]%>%
    .[,Honesty:=NA]%>%
    .[,.(Method, var_case, r2_y_cell, r2_y_agg, Honesty)]
    # .[,r2_y_agg:=round(r2_y_agg,digits=3)]

res_CNN_optN <- readRDS(here("Shared", "Results", "CNN", "res_CNN_r2_optN.rds"))%>%
    .[,Method:="CNN"]%>%
    setnames("r2_N", "r2_agg")%>%
    .[,.(Method, var_case, r2_agg)]

# /*-------------------------------------------------------*/
#' ## Organize the data
# /*-------------------------------------------------------*/
res_forest_all <- rbind(res_forest_all_honesty, res_forest_all_nohonesty)
    # .[,`:=`(
    #     r2_cell=round(r2_cell,digits=3),
    #     r2_agg=round(r2_agg,digits=3),
    #     r2_y_cell=round(r2_y_cell,digits=3),
    #     r2_y_agg=round(r2_y_agg,digits=3)
    #     )]

res_forest_yield <- res_forest_all[Method%in%c("RF","BRF"), .(Method, var_case, r2_y_cell, r2_y_agg, Honesty)]

res_forest_optN <- res_forest_all[, .(Method, var_case, r2_cell, r2_agg, Honesty)]

res_yield_all <- rbind(res_forest_yield, CNN_y_eval_v1)

```

## opt_N Estimation (subplot-level)

```{r, dependson = "source-results"}

res_optN_subplot <- copy(res_forest_optN)%>%
    .[Honesty==TRUE,.(Method, var_case, r2_agg)]%>%
    rbind(.,res_CNN_optN)%>%
    .[, Method:=factor(Method, levels = c("RF", "BRF", "CNN", "CF_stepwise", "CF_base"))]

##== Summary Table  ==##
table_optN_subplot_long <- copy(res_optN_subplot)%>%
    .[, .(r2_agg = mean(r2_agg), r2_Stdv = sd(r2_agg)), by=.(Method, var_case)]%>%
    setnames(names(.), c("Method", "Model", "R-squared", "Stdv."))%>%
    flextable()%>% 
    autofit()

table_optN_subplot_wide_prep <- copy(res_optN_subplot)%>%
    .[, .(r2_agg = mean(r2_agg)), by=.(Method, var_case)]%>%
    .[, r2_agg:= format(round(r2_agg, digits=3), nsmall = 3)]%>%
    .[,var_case:= case_when(
      var_case == "aby" ~ "Model 1",
      var_case == "abytt" ~ "Model 2",
      var_case == "aabbyy" ~ "Model 3",
      var_case == "aabbyytt" ~ "Model 4"
    )]

avg_optN <- copy(res_optN_subplot)%>%
    .[, .(Avg= mean(r2_agg)), by=Method]%>%
    .[, Avg:= format(round(Avg, 3), nsmall = 3)]%>%
    dcast(...~Method, value.var = "Avg")

table_optN_subplot_wide <- copy(table_optN_subplot_wide_prep)%>%
    dcast(var_case~Method, value.var = "r2_agg")%>%
    setnames("var_case", "Model")%>%
    mutate(
    across(
      everything(),
      as.character
        )
    ) %>% 
    add_row(Model = NA, RF = NA, BRF = NA, CF_stepwise = NA, CF_base = NA, .after = 4)%>%
    flextable(.)%>%
    add_body(
        Model="Avg.",
        RF = avg_optN[,RF],
        BRF = avg_optN[,BRF],
        CNN = avg_optN[,CNN],
        CF_stepwise = avg_optN[,CF_stepwise],
        CF_base = avg_optN[,CF_base], 
        top = FALSE
        )%>%
    theme_booktabs()%>%
    set_header_labels(values = list(
        Model = "Model",
        RF = "RF",
        BRF = "BRF",
        CNN = "CNN",
        CF_stepwise = "CF-stepwise",
        CF_base = "CF-base"
    ))%>%
    align(align = "center", part = "all")%>%
    align(j=1,  align = "left", part = "all")%>%
    # width(width = 2)%>%
    autofit()%>%
    set_caption("Table 1: Mean R-squared of EONR Estimates by ML Methods and Modeling Scenarios")%>%
    font(fontname="Helvetica", part = "all",
    # cs.family = fontname,
    # hansi.family = fontname,
    # eastasia.family = fontname
    )

# save_as_image(table_optN_subplot_wide, path = here("GitControlled", "Writing", "Presentation", "OFE_Presentation","table_optN.png"),
#     # zoom = 8,
#     webshot = "webshot2")

```

#

```{r, dependson = "source-results"}
####==== CNN vs RF vs BRF ====####
res_CNN_y <- readRDS(here("Shared", "Results", "CNN", "CNN_y_eval_v1.rds"))%>%
    .[,.(sim, Method, var_case, r2_y_agg)]%>%
    setnames("r2_y_agg", "r2_y")
    # .[,r2_y_agg:=round(r2_y_agg,digits=3)]

res_CNN_optN <- readRDS(here("Shared", "Results", "CNN", "res_CNN_r2_optN.rds"))%>%
    setnames("r2_N", "r2")

res_CNN <- res_CNN_y[res_CNN_optN, on=c("sim", "var_case")]%>%
    dcast(sim + var_case ~ Method, value.var = c("r2", "r2_y"))

res_CNN_RF_BRF <- readRDS(here("Shared", "Results", "CNN", "SimRes_sp_400.rds"))%>%
    .[,!c("r2_cell", "r2_y_cell")]%>%
    .[model%in%c("RF","BRF"),] %>%
    .[, var_case:=factor(var_case, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
    setnames("model", "Method")%>%
    setnames(c("r2_agg", "r2_y_agg"), c("r2", "r2_y"))%>%
    dcast(sim + var_case ~ Method, value.var = c("r2", "r2_y"))%>%
    .[res_CNN, on=c("sim", "var_case")]%>%
    setnames("var_case", "Model")%>%
    .[,.(sim, Model, r2_RF, r2_BRF, r2_CNN, r2_y_RF, r2_y_BRF, r2_y_CNN)]%>%
    .[,which_optN := 
        ifelse(r2_BRF>r2_RF & r2_BRF>r2_CNN, "BRF",
            ifelse(r2_RF>r2_BRF & r2_RF>r2_CNN, "RF",
                ifelse(r2_CNN>r2_BRF & r2_CNN>r2_RF, "CNN", NA)
                )
            )
        ]%>%
    .[,which_y := 
        ifelse(r2_y_BRF>r2_y_RF & r2_y_BRF>r2_y_CNN, "BRF",
            ifelse(r2_y_RF>r2_y_BRF & r2_y_RF>r2_y_CNN, "RF",
                ifelse(r2_y_CNN>r2_y_BRF & r2_y_CNN>r2_y_RF, "CNN", NA)
                )
            )
        ]%>%
    .[,index_consist := ifelse(which_optN==which_y, 1, 0)]%>%
    .[,cons_y_optN := ifelse(index_consist==1, which_optN, NA)]%>%
    # RF vs BRF
    .[,r2_y_ratio_RF_BRF := r2_y_RF/r2_y_BRF]%>%
    .[,r2_optN_ratio_RF_BRF := r2_RF/r2_BRF]%>%
    # CNN vs RF
    .[,r2_y_ratio_CNN_RF := r2_y_CNN/r2_y_RF]%>%
    .[,r2_optN_ratio_CNN_RF := r2_CNN/r2_RF]%>%
    # CNN vs BRF 
    .[,r2_y_ratio_CNN_BRF := r2_y_CNN/r2_y_BRF]%>%
    .[,r2_optN_ratio_CNN_BRF := r2_CNN/r2_BRF]

# Summary Table 
sumry_res_CNN_RF_BRF <- res_CNN_RF_BRF%>%
    .[,.(
        count_BRF = nrow(.SD[cons_y_optN=="BRF"]),
        count_RF = nrow(.SD[cons_y_optN=="RF"]),
        count_CNN = nrow(.SD[cons_y_optN=="CNN"]),
        count_y_BRF = nrow(.SD[which_y=="BRF"]),
        count_y_RF = nrow(.SD[which_y=="RF"]),
        count_y_CNN = nrow(.SD[which_y=="CNN"]),
        Total= sum(index_consist)
        ), by=Model]%>%
    .[,BRF := paste0(count_BRF, " (",count_y_BRF,")")]%>%
    .[,RF := paste0(count_RF, " (",count_y_RF,")")]%>%
    .[,CNN := paste0(count_CNN, " (",count_y_CNN,")")]%>%
    .[,Model:= case_when(
      Model == "aby" ~ "Model 1",
      Model == "abytt" ~ "Model 2",
      Model == "aabbyy" ~ "Model 3",
      Model == "aabbyytt" ~ "Model 4"
    )]%>%
    .[,.(Model, RF, BRF, CNN, Total)]%>%
    flextable()%>%
    align(align = "center", part = "all")%>%
    align(j=1,  align = "left", part = "all")%>%
    set_caption("Table 2: Count table about the number of simulation rounds where an identical ML method showed the highest R-squared in both EONR estimation and yield prediction in that round")%>%
    add_footer_row(
    values = "The number in ( ) indicates the number of rounds with the highest R-squared in yield prediction.",
    colwidths = 5
    )%>%
    font(fontname="Helvetica", part = "all",
    # cs.family = fontname,
    # hansi.family = fontname,
    # eastasia.family = fontname
    )%>%
    autofit()

# save_as_image(sumry_res_CNN_RF_BRF, path = here("GitControlled", "Writing", "Presentation", "OFE_Presentation","table_y.png"),
#     # zoom = 8, 
#     webshot = "webshot2")
```

### 2022-02-05 GitControlled/Writing/Re_JournalSubmission/ML_VRA_v2.rmd
Large revise of the manuscript and codes for re-submission

--- 2022-02-05 Writing/Re_JournalSubmission/ML_VRA_format_v2.rmd
@@
 Past studies have attempted to estimate yield response functions using various Machine Learning (ML) methods, including the Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN) methods.
-This study proposes use of the Causal Forest (CF) model, which is one of the emerging ML methods that comprise \"Causal Machine Learning.\" Unlike previous prediction-oriented ML methods, CF focuses strictly on estimating heterogeneous treatment effects of inputs, rather than predicting yield.
+This study proposes use of the Causal Forest (CF) model, which is one of the emerging ML methods that comprise \"Causal Machine Learning.\" Unlike previous yield-prediction-oriented ML methods, CF focuses strictly on estimating heterogeneous treatment effects (changes in yields that result from changes in input application rates) of inputs.
 We report results of using Monte Carlo simulations assuming various production scenarios to test the effectiveness of CF in estimating site-specific economically optimal nitrogen rates (EONRs), comparing CF with the yield-prediction-oriented ML methods RF, BRF, and CNN.
@@
 # opts_knit$set(root.dir = here())
-opts_knit$set(root.dir = "~/Dropbox/ResearchProject/ML_VRA")
+opts_knit$set(root.dir = "~/Dropbox/ResearchProject/CF_for_VRA")
 
@@
 # === packages ===#
-library(sf)
+library(tidyverse)
+library(data.table)
+
 library(png)
-library(data.table)
-library(grf)
 library(RColorBrewer)
@@
 library(tmap)
-library(tidyverse)
 library(ggthemes)
@@
 # --- Convert an Rmd file into a pure R file using purl() ---#
-knitr::purl("./GitControlled/Codes/PrepareResults.Rmd", output = "./GitControlled/Codes/PrepareResults.R")
+knitr::purl("./GitControlled/Codes/PrepareResults_1.Rmd", output = "./GitControlled/Codes/PrepareResults_1.R")
 
 # --- Read the simulation results and prepare figures and tables ---#
-source("./GitControlled/Codes/PrepareResults.R")
+source("./GitControlled/Codes/PrepareResults_1.R")
 ```
@@
 
-Despite the potential economic and environmental benefits of site-specific input (e.g., nitrogen (N), seed) management, the adoption rate of variable rate application technology remains relatively low [@lowenberg2019setting].
-This is primarily because of the difficulty in estimating site-specific yield response functions accurately within a field, which is critical for the identification of site-specific economically optimal input rates (EOIRs) [@bullock1998does].
-
+Information about crop yield response input management is critical for the identification of site-specific economically optimal input rates (EOIRs) [@bullock1998does], and the difficulty in estimating site-specific yield response functions accurately within a field is the primary explanation of the persistent relatively low the adoption rate of variable rate crop input application technology [@lowenberg2019setting].
 Historically, site-specific yield response functions have been estimated using the data generated from strip trials conducted on only parts of fields [@makowski2001statistical; @scharf2002corn; @bullock2002adding; @mamo2003spatial; @hurley2004estimating; @anselin2004spatial; @scharf2005field; @ruffo2006site; @Miao2006; @puntel2019development].
-But recently whole-field on-farm precision experimentation (OFPE) [@bullock2019] has allowed implementation of improved statistical experimental designs (e.g., Latin Square, Randomized Block) are used for an entire field [@laurent_kyveryga_makowski_miguez_2019; @licht_witt_2019].
+But recently whole-field on-farm precision experimentation (OFPE) [@bullock2019] has allowed implementation of improved statistical experimental designs (e.g., Latin Square, Randomized Block) on entire fields [@laurent_kyveryga_makowski_miguez_2019; @licht_witt_2019].
 Data generated from whole-field OFPEs typically have greater local variation in experimental input application rates and soil/field characteristics than do strip trial designs, which has improved the statistical identification of heterogeneous impacts of input management changes on yields.
@@
 @barbosa2020modeling applied the Convolutional Neural Network approach, @krause2020random used Random Forest-based approaches, and @Gardner21 used the shape-constrained generalized additive model.
-But this trend of applying ML methods may raise concerns.
-Historically, agronomy is a field that has paid meticulous attention to identifying the "causal" impacts of input management on yield through clever experimental designs.
-But the aforementioned recent applications of ML methodologies pay little attention to causal identification of inputs on yield, instead validating their models by yield prediction accuracy.
+But this trend of applying ML methods may raises concerns.
+Historically, agronomists have worked meticulously to develop clever experimental designs to identify causes of yield response to input management.
+But the aforementioned recent applications of ML methodologies pay little attention to identify such causes, instead attempting to validate their models by estimating yield prediction accuracy.
 But the ultimate goal of OFPE is the accurate prediction of EOIRs, not yields.
@@
 
-The lack of and need for causal interpretation of the results of ML research applications have been increasingly recognized, in particular in economics and medicine [@athey2017beyond; @athey2018impact; @Athey2019a; @moraffah2020causal; @Storm2020; @arti2020research; @scholkopf2021toward].
-In response, causal machine learning (CML) methods were recently developed.
-Unlike traditional prediction-oriented ML methods, CML focuses on identifying causal impacts of an event (in our context, an increase or decrease in the input application rate).
-The growing academic literature applying CML methods includes @richens2020improving, who pointed out that the inability of the traditional ML methods to identify cause and effect relationships between disease and patients' characteristics could lead to misdiagnoses, and showed that CML-based diagnoses could improve the accuracy of diagnostic prediction.
+The lack of and need for causal interpretation of the results of ML research applications have been increasingly recognized, in particular in economics and medicine [@athey2017beyond; @athey2018impact; @Athey2019a; @moraffah2020causal; @Storm2020; @arti2020research; @scholkopf2021toward], and causal machine learning (CML) methods were recently developed in response.
+Unlike traditional prediction-oriented ML methods, CML focuses on identifying causal impacts of an event (in our context, of an increase or decrease in the input application rate).
+The growing academic literature applying CML methods includes @richens2020improving, who's medical research pointed out that the inability of the traditional ML methods to identify cause-and-effect relationships between disease and patients' characteristics could lead to misdiagnoses, and showed that CML-based diagnoses could improve the accuracy of diagnostic prediction.
 In addition, @carbo2020machine used a CML to identify characteristics causing bank customers to adopt online banking services, and @bozorgi2020process applied CML to study the mining processes.
 
-In this paper, we test the accuracy of site-specific economically optimal N fertilization rates (EONRs) estimation based on Causal Forest (CF) approach developed by @athey2016recursive and @Wager2018a.
-We compare the EONR prediction performances of our CF-based approach to the widely used ML methods Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN).
-Further, we also test how yield prediction performance is related to EONR prediction performance to examine whether it is appropriate to select the model based on its ability to predict yield when the ultimate goal is to identify EOIR.
-We use Monte Carlo simulations, where we synthetically generate yield and soil/field characteristics datasets for a stylized "field." Because real-world "true" EOIRs cannot be measured, real-world data cannot be used to test the accuracy of statistical methods estimating EOIRs.
+In this paper, we use the Causal Forest (CF) approach developed by @athey2016recursive and @Wager2018a to examine the accuracy of methods that estimate site-specific economically optimal N fertilizer rates (EONRs).
+We compare the EONR prediction performances of our CF-based approach to the widely used ML methods Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN), and we examine how yield prediction performance is related to EONR prediction performance, which allow us to examine whether model selection should be based on yield prediction accuracy when the ultimate goal is EOIR identifying.
+We use Monte Carlo simulations in which we synthetically generate yield and soil/field characteristics datasets to create stylized "field." Because real-world "true" EOIRs are unobservable, real-world data cannot be used to test the accuracy of statistical methods estimating EOIRs.
 This important difference contrasts starkly with yield prediction, since actual yields can be ground-truthed.
 
-<!-- Our simulation results reveal that CF-based approaches provide superior performance in site-specific EOIR estimation.
-We also demonstrate that a method's yeidl prediction accuracy is not a good indicator of its EOIR estimation accuracy.
--->
+# Background:Using Causal Forest Methods to Predict Changes in Yield
 
-# Predicting Yield vs. Predicting Changes in Yield in Response to Changes in Input Management
-
-In the following, we describe the fundamental information necessary to identify EOIR in general: the site-specific treatment effect of input application on yield.
+In the following, we use basic microeconomic theory to describe the fundamental information necessary to identify EOIRs in general: the site-specific treatment effect of input application on yield.
 We then discuss the causal forest method in detail, show how it is particularly suitable to obtain this fundamental information, and contrast it to more traditional prediction-oriented ML methods, such as RF, BRF, and CNN.
@@
 
-Elementary calculus shows that the necessary condition for maximization is, that $\partial f(I, \mathbf{c})/\partial I - w =0$, which implicitly defines the economically optimal input application rate as a function of prices and soil/field characteristics, and may be arranged as \@ref(eq:eqn2):
+Elementary calculus shows that the necessary condition for maximization is, that $\partial f(I, \mathbf{c})/\partial I - w =0$, which implicitly defines the economically optimal input application rate as a function $I^{*}$ of prices and soil/field characteristics, and may be arranged as \@ref(eq:eqn2):
 
@@
 While knowledge of the yield function $f(I, \mathbf{c})$ in Eq.
-\@ref(eq:eqn1)) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the function's partial derivative is necessary.
+\@ref(eq:eqn1) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the function's partial derivative is necessary.
+
 In the following, we discuss a method of using Causal Forest methods that can provide statistical advantages to the estimation of economically optimal input application rates because it is built to estimate approximations of the derivative $\partial f/\partial I$ directly, and not the yield function $f$ itself.
@@
 
-Recent papers using ML methods to estimate the effectiveness of various agricultural input management strategies have based their analyses on estimates of a yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21).
+Recent studies using ML methods to estimate the effectiveness of various agricultural input management strategies have based their analyses on estimates of a yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21).
 In the following, we present a Causal Forest methodology that does not rely on estimation of how the level of yield depends on the input application rate $I$, but rather relies on a discrete version of Eq.
@@
 Consider an increasing ordering of input application rates $I_1, I_2,...,I_K$.
-Among these K rates, for a generic site $i$ a specific EOIR can be identified if the *treatment effect* function $\Delta y_i(I_{k+1}, I_{k})$ is known.
+Among these K rates, for a generic site $i$ a specific EOIR can be identified if the *treatment effect* function $\Delta y_i(I_{k+1}, I_{k})$ defined in Eq.
+\@ref(eq:eqn3)is known.
 This function is defined as the discrete change in yield that results from a discrete change in the input level from $I_k$ to $I_{k+1}$, and it depends on the characteristics at the site analyzed:
 
-$$
-\Delta y_i(I_{k+1}, I_{k}) = f(I_{k+1}, \mathbf{c_i}) - f(I_{k}; \mathbf{c_i}) \quad ^\forall k = 1, \dots , K - 1
-$$
+\begin{equation}
+\Delta y_i(I_{k+1}, I_{k}) = f(I_{k+1}, \mathbf{c_i}) - f(I_{k}; \mathbf{c_i}) \quad ^\forall k = 1, \dots , K - 1. (\#eq:eqn3)
+\end{equation}
 
-Once treatment effects $\Delta y_i(I_{k+1}, I_{k})$ have been identified for every $k$, economic analysis can be conduced to identify the EOIR for site $i$.
+Once treatment effects $\Delta y_i(I_{k+1}, I_{k})$ have been identified for every $k$, economic analysis can be conducted to identify the EOIR for site $i$.
 The profit change from increasing the input rate from $I_{1}$ to $I_{k}$ is
 
-$$
-P_c (\sum_1^{k-1} \Delta y_i(I_{k+1}, I_{k})) - P_I \times (I_k - I_0).
-$$
+\begin{equation}
+p (\sum_1^{k-1} \Delta y_i(I_{k+1}, I_{k})) - w \times (I_k - I_0). (\#eq:eqn4)
+\end{equation}
 
-The EOIR is the value $I_k$ that maximizes the profit gain "relative" to profits from $I_1$. ($I_1$ may be the EOIR if no other rates surpass the profit of $I_1$.)
+The EOIR is the value $I_k$ that maximizes the profit gain "relative" to profits from $I_1$. ($I_1$ may be the EOIR if no other rates generates greater profit.)
 
@@
 
-```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
+```{r ct-ex, out.width="50%", fig.align="center", fig.cap = "An illustrative example of causal tree"}
 # knitr::include_graphics("./GitControlled/Writing/Re_JournalSubmission/ctree_ex.pdf")
@@
 
-## CF vs. Prediction-oriented ML methods
+## Advantages of Causal Forest Analysis in the Context of On-farm Precision Experimentation
 
-Whether the indirect (yield-prediction-first) and direct approach is used can lead to meaningful statistical differences when it comes to EOIR estimation.
-The conventional prediction-oriented ML methods are designed to predict yield, $y_i(I,\mathbf{c})$, well, but not necessarily treatment effects.
-Since the loss function used in prediction-oriented ML uses (typically squared) residuals in yield prediction, prediction-oriented ML is naturally optimized for predicting the "level" of yield instead of identifying the causal impact of the input.
-CF, on the other hand, is designed specifically to estimate the causal impact of input.
+Whether the indirect (yield-prediction-first) or direct approach is used can lead to meaningful statistical differences in EOIR estimation.
+The conventional prediction-oriented ML methods are designed to predict yield, $y_{i}(I) \equiv f(I, c_{i})$, well, but not necessarily treatment effects.
+Since the loss function used in prediction-oriented ML uses (typically squared) residuals in yield prediction, prediction-oriented ML is naturally optimized for prediction the "level" of yield instead of identifying the causal impact of the input.
+But CF is designed specifically to estimate the casual impact of the input.
 Indeed, @Wager2018a used Monte Carlo simulations to show that CF provided more accurate estimates of heterogeneous treatment effects than those provided by RF.
@@
 Moreover, CF has never been compared to more advanced ML methods such as BRF and CNN that are considered to have prediction capabilities greater than RF's.
-The study reported here builds on @Wager2018a to compare CF to these prediction-oriented ML methods (not just RF, but also BRF and CNN) in more realistic agronomic experiment settings.
+Our report builds on @Wager2018a to compare CF to these prediction-oriented ML methods (not just RF, but also BRF and CNN) in more realistic agronomic experiment settings.
 
@@
 
-Monte Carlo simulations were conducted for nitrogen experiments for corn production to estimate the economically optimal nitrogen rate (EONR).
-The first step in our simulation was to generate one thousand synthetic fields that "resembled" an actual field.
-<span style="color:red"> After generating one thousand synthetic fields, we repeated to evaluate each of the ML methods by one thousand times.
-In an individual simulation round, one of the fields was used as a training data set.
-As a validation data set, a different field from a training data set in that simulation round was used.</span> <!-- For each simulated field, we generated a training data set and a validation data set.
---> Field characteristics and yield were simulated based on the Mitscherlich-Baule (MB) yield response function.
+Monte Carlo simulations were conducted for nitrogen experiments for corn production to estimate site-specific EONRs.
+The simulations’ first step generated one thousand synthetic fields that "resembled" an actual field.
+Then, for each simulation round, one of the fields was used as a training data set, and another field that is different from the one used as a training data set in that round was used as a validation data set.
+Field characteristics and yield were simulated assuming the Mitscherlich-Baule (MB) yield response function.
 We used the RF, BRF, and CNN ML methods to estimate yield response functions, and we used the CF method to estimate treatment effects.
@@
 Detailed descriptions of these steps are provided below.
-The R codes that implement the simulation analyses are available at https://github.com/tmieno2/ML_VRA.git.
+The *R* and *python* codes that implement the simulation analyses are available at https://github.com/tmieno2/ML_VRA.git.
 
@@
 The simulated field was created based on an actual 51-ha Illinois field on which the Data-Intensive Farm Management (DIFM) project [@bullock2019] has run multiple OFPEs.
-Figure \@ref(fig:field-map) illustrates that simulated trials consisted of $384$ <span style="color:red"> 18-m </span> $\times$ <span style="color:red"> 73-m </span> "plots," each of which was assigned an N fertilizer application rate.
-Each plot was made up of four (4-rows $\times$ 1-column) "subplots," which were unit of analysis used in subsequent statistical analysis.
-Each subplot contained of a 6-rows $\times$ 6-columns grid of thirty-six <span style="color:red"> 3-m </span> $\times$ <span style="color:red"> 3-m </span> "cells." All field characteristics and yield data were generated at the cell level.
+Figure \@ref(fig:field-map) illustrates that simulated trials consisted of $384$ 18.3 m $\times$ 73.2 m "plots," each of which was assigned an N fertilizer application rate.
+Each plot was made up of four (4-rows $\times$ 1-column) 18.3 m $\times$ 18.3 m "subplots," which were unit of analysis used in subsequent statistical analysis.
+Each subplot contained of a 6-rows $\times$ 6-columns grid of thirty-six 3.05 m $\times$ 3.05 m "cells." All field characteristics and yield data were generated at the cell level.
 
-```{r field-map, fig.width=4, fig.height=3, fig.cap = "Division of field: plots, subplots and cells"}
+```{r field-map, out.width="50%", fig.cap = "Partitioning of field into plots, subplots and cells"}
 # knitr::include_graphics("./GitControlled/Writing/Re_JournalSubmission/field_devision_v2.png")
@@
 
-We modeled the yield response function as having the following Mitscherlich-Baule functional form:
+We modeled the yield response function as having the following Mitscherlich-Baule functional form, which is flexible in its shape, allows for the existence of a yield plateau, and has been shown to be a plausible specification for N fertilization models for corn [@frank1990; @llewelyn1997; @paris1992].
 
 \begin{equation}
-f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) N)) + \varepsilon. (\#eq:eqn3)
+f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) N)) + \varepsilon. (\#eq:eqn5)
 \end{equation}
@@
 The first term on the right-hand side of Eq.
-\@ref(eq:eqn3) is the deterministic yield component, which was generated assuming the commonly-used MB functional form, which is flexible in its shape, allows for the existence of a yield plateau, and has been shown to be a plausible specification for N fertilization models for corn [@frank1990; @llewelyn1997; @paris1992].
-The variable $N$ in Eq.
-\@ref(eq:eqn3) represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot.
+\@ref(eq:eqn5) is the deterministic yield component.
+The variable $N$ represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot.
 Also in Eq.
@@
 
-A fictional "researcher" is modeled as having limited knowledge about which variables make up $\mathbf{c}$, or even the number of elements of $\mathbf{c}$, and has limited ability to measure the values that many of the variables that constitute $\mathbf{c}$ take on across the field.
-The researcher is also assumed to not know the functional forms of the yield response function.
+A fictional "researcher" is modeled as not knowing the function form of $f$, as having limited knowledge about which variables make up $\mathbf{c}$, or even the number of elements of $\mathbf{c}$, and as having limited ability to measure the values that many of the variables that constitute $\mathbf{c}$ take on across the field.
 
-### Cell-specific Yield Functions and Economically Optimal N Rates
+### Cell-specific Yield Functions and True Economically Optimal N Rates
 
-Let $i \in \{1,2,...,1536\}$ index a simulated field's subplots and $j \in \{1,2,...,36\}$ index cells within a subplot.
+Let $i \in \{1,2,...,1536\}$ index a simulated field's subplots and $j \in \{1,2,...,36\}$ index cells within subplots.
 Let $N^{i}$ be the N fertilization rate on plot $i$, and let $\mathbf{c}^{i,j}$ be the value of $\mathbf{c}$ on cell $(i,j)$, Eq.
-\@ref(eq:eqn4) shows the yield level on cell $j$ in subplot $i$ is affected by the N rate applied on subplot $i$:
+\@ref(eq:eqn6) shows the yield level on cell $j$ in subplot $i$ is affected by the N rate applied on subplot $i$:
 
 \begin{equation}
-f(N^{i}, \mathbf{c}^{i,j}) = ymax(\mathbf{c}^{i,j})(1-exp(\alpha(\mathbf{c}^{i,j}) + \beta(\mathbf{c}^{i,j}) N^{i})) + \varepsilon^{i,j}. (\#eq:eqn4)
+f(N^{i}, \mathbf{c}^{i,j}) = ymax(\mathbf{c}^{i,j})(1-exp(\alpha(\mathbf{c}^{i,j}) + \beta(\mathbf{c}^{i,j}) N^{i})) + \varepsilon^{i,j}. (\#eq:eqn6)
 \end{equation}
@@
 \begin{equation}
-f^{i,j}(N) = ymax^{i,j}(1-exp(\alpha^{i,j} + \beta^{i,j} N^{i})) + \varepsilon^{i,j}. (\#eq:eqn5)
+f^{i,j}(N) = ymax^{i,j}(1-exp(\alpha^{i,j} + \beta^{i,j} N^{i})) + \varepsilon^{i,j}. (\#eq:eqn7)
 \end{equation}
@@
 The `gstat` package (version 2.0.6 [@gstat1; @gstat2]) in R was used for this purpose.
-Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha^{i,j}$, $\beta^{i,j}$, $ymax^{i,j}$, and $\varepsilon^{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project (Codes used to generate parameter values are available at https://github.com/tmieno2/ML_VRA.git.) Figure \@ref(fig:fig-parameters) shows an example of the generated parameters.
+Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha^{i,j}$, $\beta^{i,j}$, $ymax^{i,j}$, and $\varepsilon^{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
+(Codes used to generate parameter values are available at https://github.com/tmieno2/ML_VRA.git.) The range and nugget of all parameters were assumed to be $400$ m and 0.
+The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$.
+Figure \@ref(fig:fig-parameters) shows an example of the generated parameters.
 
@@
 
-```{r variogram-parameters, tab.cap = "The parameters for the variogram modeling"}
-variogram_tb
-```
-
-<br>
-
-```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An illustrative example of spatial distributions of field characteristics"}
+```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics"}
 # field_alpha + field_beta + field_ymax
@@
 \begin{equation}
-N_{opt}^{i,j} = \operatorname*{argmax}_{N}(P_{C} f^{i,j}(N) - P_N N), (\#eq:eqn6)
+N_{opt}^{i,j} = \operatorname*{argmax}_{N}(P_{C} f^{i,j}(N) - P_N N), (\#eq:eqn8)
 \end{equation}
 
-where, $P_{C}=\$0.138/kg$ and $P_{N}=\$1.323/kg$ were the assumed prices of the corn and N fertilizer.
-Figure \@ref(fig:fig-optN) maps an example of the identified "true" cell-specific optimal N rates.
+where, $p =\$0.138/kg$ and $w =\$1.323/kg$ were the assumed prices of the corn and N fertilizer. Figure \@ref(fig:fig-optN) maps an example of the identified "true" cell-specific optimal N rates.
 
@@
 In each simulation round, five field-trial N rates were determined based on the range of the round's cell-specific EONRs. 
-Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percent quantile of the round's cell-specific EONRs. Then, the five trial design rates were
-
-$$
-\begin{aligned}
-N_1 &= Q_{0.05} - 20 \\
-N_5 &= Q_{0.95} + 20 \\
-N_2 &= N_1 + 0.25(N_5 - N_1) \\
-N_3 &= N_1 + 0.50(N_5 - N_1) \\
-N_4 &= N_1 + 0.75(N_5 - N_1)
-\end{aligned}
-$$
-
-In each round, a Latin square design was followed to assign each plot one of the five N rates so established. Figure \@ref(fig:fig-nExp) shows an example of a trial design.
+Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percent quantile of the round's cell-specific EONRs.
+Then, the five trial design rates were $N_1 = Q_{0.05} - 20$, $N_5 = Q_{0.95} + 20$, $N_2 = N_1 + 0.25(N_5 - N_1)$, $N_3 = N_1 + 0.50(N_5 - N_1)$, $N_4 = N_1 + 0.75(N_5 - N_1)$.
+In each round, a Latin square design was followed to assign each plot one of the five N rates so established.
+Figure \@ref(fig:fig-nExp) shows an example of a trial design.
+The N rate was orthogonal to the error term in every simulation's example of trial design.
+This is important because if they were correlated, bias in the estimation of the impact of N on yield would be introduced into all of the ML methods.
+Since the treatment effect at each leaf is obtained simply by taking the difference of the average value of the dependent variable between the control and treated group within the leaf, CF requires the exogeneity of the treatment conditional on the independent variables to estimate the treatment effect consistently.
+Note that the violation of this condition would lead to biased estimation using the CF and the other ML methods.
 
@@
 
-Under this design, the N rate was orthogonal to the error term.
-This is important because if they were correlated, bias in the estimation of the impact of nitrogen on yield would be introduced for all of the ML methods.
-Since the treatment effect at each leaf is obtained simply by taking the difference of the average value of the dependent variable between the control and treated group within the leaf, CF requires the exogeneity of the treatment conditional on the independent variables to estimate the treatment effect consistently.
-Note that the violation of this condition leads to biased estimation for not just CF and the other ML methods, as well.
+<br>
 
@@
 For a generic cell $(i,j)$, yield $y^{i,j}$ was generated through Eq.
-\@ref(eq:eqn3), applying parameter values $\mathbf{c^{i,j}}=(\alpha^{i,j}, \beta^{i,j}, ymax^{i,j})$, the disturbance term level $\varepsilon^{i,j}$, and the cell's assigned experimental N rate, $N^{i,j}$ (Figure \@ref(fig:field-yield-cell)).
+\@ref(eq:eqn5), applying parameter values $\mathbf{c^{i,j}}=(\alpha^{i,j}, \beta^{i,j}, ymax^{i,j})$, the disturbance term level $\varepsilon^{i,j}$, and the cell's assigned experimental N rate, $N^{i,j}$.
+Figure \@ref(fig:field-yield-cell) presents the yield map from one of the simulations.
 
@@
 
-These were aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation. The subplot data were therefore
+Data were aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation. The subplot data were therefore
 
-$$
-\{(y^{i}, N_{opt}^{i}, N^{i}, \mathbf{c}^{i}) = \frac{1}{36}\sum_{j=1}^{36} (y^{i,j}, N_{opt}^{i,j}, N^{i,j}, \mathbf{c}^{i,j}): i \in \{1,2,...,1536\}\}
-$$
+\begin{equation}
+\{(y^{i}, N_{opt}^{i}, N^{i}, \mathbf{c}^{i}) = \frac{1}{36}\sum_{j=1}^{36} (y^{i,j}, N_{opt}^{i,j}, N^{i,j}, \mathbf{c}^{i,j}): i \in \{1,2,...,1536\}\}. (\#eq:eqn9)
+\end{equation}
 
@@
 To evaluate the performances of RF, BRF, CNN and CF, we examined four modeling scenarios, each defined by a dataset assumed to be available to the researcher.
-The first modeling scenario, denoted "aby" assumed that researchers have a dataset of the actual values $\alpha^{i,j}$, $\beta{i,j}$, $ymax^{i,j}$ for every cell $(i,j)$ and use $\alpha$, $\beta$ and $ymax$ as covariates in their ML models.
-This scenario represents an ideal situation for researchers, in which all the relevant variables are observed, but the true functional form of heterogeneous yield response functions are not known.
+The first modeling scenario, denoted "aby" assumed that the researcher has a dataset of the actual values $\alpha^{i,j}$, $\beta{i,j}$, $ymax^{i,j}$ for every cell $(i,j)$ and use $\alpha$, $\beta$ and $ymax$ as covariates in the ML models.
+This scenario represents an ideal situation for the researcher, in which all the relevant variables are observed, but the true functional form of heterogeneous yield response functions are not known.
 More realistic scenarios can be compared with this ideal scenario.
 
-In subsequent modeling scenarios, we made the simulated experimental data more realistic by varying the degree to which researchers understood what the needed covariates' values were those in the data set.
-In the second scenario, denoted "abytt," we introduced additional variables $\theta_1$ and $\theta_2$, and the researcher's dataset contained values of $\alpha^{i}$, $\beta^{i}$, $ymax^{i}$, $\theta_1^{i}$ and $\theta_2^{i}$ for all subplots $i=1,...,1536$.
+In subsequent modeling scenarios, we made the simulated experimental data more realistic by varying the degree to which the researcher understood what the needed covariates' values were those in the data set.
+In the second scenario, denoted "abytt," we introduced additional variables $\theta_1$ and $\theta_2$, and the researcher's data set contained values of $\alpha^{i}$, $\beta^{i}$, $ymax^{i}$, $\theta_1^{i}$ and $\theta_2^{i}$ for all subplots $i=1,...,1536$.
 $\theta_1$ and $\theta_2$ had no effect on yield, but their cell-level values were spatially correlated with $\beta^{i,j}$, and so their subplot-level values were correlated with $\beta^{i}$.
-This scenario is meant to reflect the lack of scientific consensus about which variables explain heterogeneous yield response to N, making it likely that researchers include irrelevant variables like $\theta_1$ and $\theta_2$ in real-world data analysis.
+This scenario was meant to reflect the lack of scientific consensus about which variables explain heterogeneous yield response to N, making it likely that the researcher would include irrelevant variables like $\theta_1$ and $\theta_2$ in real-world data analysis.
 
-In the third scenario, denoted "aabbyy," the researcher's dataset did not contain values of $\alpha^{i}$, $\beta^{i}$, or $ymax^{i}$.
+In the third scenario, denoted "aabbyy," the researcher's data set did not contain values of $\alpha^{i}$, $\beta^{i}$, or $ymax^{i}$.
 Rather, it contained subplot-level values of permutations of $\alpha$, $\beta$, and $ymax$.
@@
 $ymax_{1}^{i,j} = r_{ymax}^{i,j} ymax^{i,j}$, and $ymax_{2}^{i,j} = (1- r_{ymax}^{i,j}) ymax^{i,j}$.
-For each $\alpha$, $\beta$ and $ymax$, these procedures created two new covariates that were highly spatially autocorrelated with the original covariate, which was meant to reflect that many of the soil/field characteristics used to analyze OFPE data are spatially correlated.
+For each $\alpha$, $\beta$ and $ymax$, these procedures created two new covariates that were highly spatially correlated with the original covariate, which was meant to reflect that many of the soil/field characteristics used to analyze OFPE data are spatially correlated.
 The values of $\alpha^{i,j}$, $\beta^{i,j}$ and $ymax^{i,j}$ did not indicate specific soil or field characteristics, but were functions of such.
@@
 
-## Training Models and and Estimating Site-specific EONRs
+## Training Models and Estimating Site-specific EONRs
 
-### RF, BRF, and CNN
+### Estimation of Site-specific EONRs by RF, BRF, and CNN
 
-The RF, BRF, and CNN methods followed the same conceptual steps to estimate site-specific EONR: 1) estimate the yield production functions and 2) calculate site-specific EONRs based on that estimated function.
+The RF, BRF, and CNN methods all followed the same conceptual steps to estimate site-specific EONR: 1) estimate the yield production functions and 2) calculate site-specific EONRs based on that estimated function.
 For the given modeling scenario, RF and BRF predict yield by using all the available covariates as explanatory variables in the estimation process.
@@
 CNN leaves room for researchers to determine its architecture.
-In this article, a slightly modified version  of one of the multi-stream CNN architectures proposed by @barbosa2020modeling, called "Late Fusion," was used.
-Briefly stated, explanatory variables except N rate (e.g.
-$\alpha^{i,j}$, $\beta^{i,j}$, etc.) enter the model as a set of $6 \times 6$ element rasters.
-On the other hand, the input size of the N rate is treated as $1 \times 1$ because it is spatially homogeneous within each subplot.
+We used a slightly modified version of one of the multi-stream CNN architectures proposed by @barbosa2020modeling, called "Late Fusion." Briefly stated, explanatory variables except N rate (e.g.
+$\alpha^{i,j}$, $\beta^{i,j}$, etc.) entered the model as a set of $6 \times 6$ element rasters.The input size of the N rate is treated as $1 \times 1$ because it is spatially homogeneous within each subplot.
 First, each input was connected to an independent convolutional layer with eight $3 \times 3$ filters each with stride one, followed by a $2 \times 2$ max-pooling layer with stride two.
@@
 @barbosa2020modeling demonstrated that among several CNN architectures, this architecture modeled crop yield response to N rate management best.
-CNN was implemented in Python v3.7.6 using Pytorch v1.7.0 [@paszke2017automatic].
+CNN was implemented in *Python* v3.7.6 using *Pytorch* v1.7.0 [@paszke2017automatic].
 The Adam optimizer [@kingma2014adam] was used with a learning rate of $0.001 \%$ (default value).
@@
 
-$$
-\hat{N}_{opt}^{i} = \operatorname*{argmax}_{N}(P_{C} \hat{g}_m(N,\mathbf{\Omega^{i}}) - P_N N) 
-$$
+\begin{equation}
+\hat{N}_{opt}^{i} = \operatorname*{argmax}_{N}(p \hat{g}_m(N, \mathbf{\Omega^{i}}) - w N), (\#eq:eqn8)
+\end{equation}
 
-where $P_C$ and $P_N$ are the prices of corn and N.
+where $p$ and $w$ are the prices of corn and N.
 
-### CF
+### Estimation of Site-specific EONRs by CF
 
@@
 
-Since the CF-base approach always estimates the treatment effects using the lowest treatment rate $N_1$, the predicted treatment effects already represents the change in yields from the yield at $N_1$:
+Since the CF-base approach always estimates the treatment effects using the lowest treatment rate $N_1$, the predicted treatment effects already represent differences in yields the from yield at $N_1$:
 
-$$
-\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}}) = \hat{\tau}_{N_{1} \rightarrow N_{m}}(\mathbf{\Omega^{i}})
-$$
+\begin{equation}
+\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}}) = \hat{\tau}_{N_{1} \rightarrow N_{m}}(\mathbf{\Omega^{i}}). (\#eq:eqn9)
+\end{equation}
 
@@
 
-<!-- We consider two possible groupings to make such pairwise N application rate combinations.
-The first grouping approach, which we call the "CF-base", used $(N_1, N_2),(N_1, N_3),(N_1, N_4)$, and $(N_1, N_5)$.
-In this approach, the treatment effect is always estimated against the lowest N rate ($N_1$) as $N^{con}$.
-The second grouping approach used $(N_1, N_2),(N_2, N_3),(N_3, N_4)$, and $(N_4, N_5)$.
-We label this approach as the "CF-stepwise".
-For estimating site-specific EONR, the trained CF-base and CF-stepwise methods were used to make predictions of site-specific changes in yields resultant from changes in application rates from $N_1$ to $N_m$ $(m\in\{2,3,4,5\})$.
-Let $\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}})$ be the the estimated treatment effect of changing subplot $i$'s application rate from $N_1$ to $N_m$ for site $i$.
-In the CF-stepwise approach, this value can be calculated by sequentially adding the estimated treatment effects: 
-$$
-\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}}) = \sum_{k=1}^{m-1} \hat{\tau}_{N_{k} \rightarrow N_{k+1}}(\mathbf{\Omega^{i}})
-$$
-In the CF-base approach, the treatment effects were always estimated using the the lowest treatment rate $N_1$.
-Therefore, the predicted treatment effects already represent the change in yields from the yield at $N_1$:
-$$
-\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}}) = \hat{\tau}_{N_{1} \rightarrow N_{m}}(\mathbf{\Omega^{i}})
-$$
-
-Once the treatment effects from the base were obtained, site-specific EONRs were identified by finding the N rate that leads to the highest profit.
-Yield levels were not predicted at any point in the CF-based approaches.
--->
-
-RF, BRF, and CF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving honest tree-building process), and the optimal values for these parameters are selected by cross-validation.
-In addition to these tuning parameters, we needed to set the number of trees grown in a forest (i.e., *num.trees*).
-Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same dataset was used.
-To reduce the variance of predictions, in other words, to stabilize the prediction accuracy, we needed to assign *num.trees* a high value, $4000$.
+RF, BRF, and CF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving honest tree-building process), and the optimal values for these parameters were selected by cross-validation.
+It was also necessary to set the number of trees grown in a forest (*num.trees*).
+Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same data set was used.
+To reduce the variance of predictions for prediction accuracy, we needed to assign *num.trees* a high value, $4000$.
 
@@
 
-The accuracy of EONR estimation was judged based RMSE ($kg/ha$) of EONR estimation against the true EONR at the subplot level.
-In addition, using the EONR estimates, we also calculated profit-deficit ($\$/ha$) (i.e., $\hat{\pi}_{def}$) relative to the true maximum profit at the subplot level.
-The maximized profit is the profit under the true yield response functions evaluated at $N_{opt}^{i}$.
+The accuracy of EONR estimation was judged based RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level.
+Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) we calculated relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N_{opt}^{i}$.
 For RF, BRF, and CNN, the accuracy of yield prediction was judged based on the RMSE ($kg/ha$) of the yield prediction against the true yields at the subplot level.
@@
 
-Table \@ref(tab:table-optN-subplot-wide) shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the $1000$ simulations; it makes immediately clear that CF-base considerably outperformed the other ML methods, and that the profits based on CF-base's EONR estimates were the closest to the true maximum profits.
+Table \@ref(tab:table-optN-subplot-wide) shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the one thousand simulations; it makes immediately clear that CF-base considerably outperformed the other ML methods, and that the profits based on CF-base's EONR estimates were the closest to the true maximum profits.
 BRF performed considerably better predicting EONR than did RF.
@@
 To examine whether this problem is a product solely of the specific choice of CNN architecture, we also tested another CNN model, which was analogous to CNN-ST proposed by @barbosa2020modeling.
-This architecture also estimated that yield and N rates were perfectly linearly related, and also estimated site-specific EONR poorly.
+This architecture also estimated that yield and N rates were perfectly linearly related, and so estimated site-specific EONR poorly.
 Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs.
-In some cases, CNN predicted yield well; but in all cases it predicting EONR poorly.
+In their work, in some cases, CNN predicted yield well; but in all cases predicted EONR poorly.
 
-Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML methods and modeling scenarios, respectively.
+Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML methods and modeling scenarios, respectively (CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always take $62.8$ kg/ha and \$$58.99$/ha, respectively).
 The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios.
@@
 Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions.
-It plots the estimated treatment effects against true treatment effects by treatment types and ML methods (RF, BRF, and CF-base) under the "aabbyytt" scenario in one of the $1000$ simulations rounds.
-The figure shows that the estimated treatment effects did not exhibit significant bias, with the points clustered around the red 1-to-1 line.
-However, they differ substantially in the accuracy of their treatment effect estimations.
-Points are clustered much more tightly about the 1-to-1 line for CF-base than RF and BRF.
-That is, CF-base estimates treatment effects much more efficiently than do the RF and BRF methods, which focus on yield prediction rather than treatment effect estimation.
+It plots the estimated treatment effects against true treatment effects by treatment types and ML methods (RF, BRF, and CF-base) under the "aabbyytt" scenario in one of the one thousand simulations rounds.
+The figure shows points clustered around the red 1-to-1 line, meaning that the estimated treatment effects did not exhibit significant bias.
+However, the models differed substantially in the accuracy of their treatment effect estimations.
+Points are clustered more tightly about the 1-to-1 line for CF-base than RF and BRF.
+That is, CF-base estimated treatment effects much more efficiently than did RF and BRF, which focus on yield prediction rather than treatment effect estimation.
 
@@
 
-## Yield Prediction and EONR Estimation
-For RF, BRF and CNN, Figure \@ref(fig:plot-y-optN) plots the RMSE values of EONR estimation against the RMSE values of yield prediction, and the red line shows the best-fit line describing the relationship between them.
+## The relationship between yield prediction performance and EONR prediction performance
+For RF, BRF and CNN, Figure \@ref(fig:plot-y-optN) plots the RMSE values of EONR estimation against the RMSE values of yield prediction, and the red lines show the best-fit line describing the relationship between them.
 For all the models the regression line was almost flat, showing little if any correlation between the two measures.
-In other words, the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions.
+In other words, the quality of a model's yield predictions provided little if any information about the quality of its EONR predictions.
 
@@
 
-Table \@ref(tab:table-y-subplot-wide) shows the mean RMSE of yield prediction over the $1000$ simulations.
+Table \@ref(tab:table-y-subplot-wide) shows the mean RMSE of yield prediction over the one thousand simulations.
 Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN.
@@
 Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well.
-While CNN performs worse than RF and BRF in "aby" and "abytt," it performs better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables.
+While CNN performed worse than RF and BRF in "aby" and "abytt," it performed better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables.
 Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.
@@
 All previous research has followed a two-step procedure to estimate site-specific EONRs.
-The first step is to select the model that predicts yield most accurately.
-The following step is to use that model to predict EONR.
-Table \@ref(tab:count-table) shows that following this process led to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds examined here.
+The first step was to select the model that predicts yield most accurately, and the following step used the selected model to predict EONR.
+Table \@ref(tab:count-table) shows that following this process led to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds.
 For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of $1000$ iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations.
 That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF models best at yield prediction did not provide EONR estimates that led to high profits.
-Similarly, in all cases, CNN method never provided both the best yield prediction and the best EONR estimation simultaneously.
-In the rounds in which BRF predicted yield best, then the two-step process worked well.
-For example, Table \@ref(tab:count-table) shows that in the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which BRF predicted yields best, it offered the best EONR recommendations `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` times.
-But, BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$.
+Similarly, in no cased did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously.
+For example, Table \@ref(tab:count-table) shows that BRF predicted yield best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best.
+But, BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.
 
@@
 We examined the use of CF-base for site-specific input management recommendations.
-Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONR to those of the prediction-oriented ML methods RF, BRF, and CNN.
-CF-base consistently outperformed the other methods across all the modeling scenarios in terms of EOIR prediction and profit generation.
-We also showed that the model’s yield prediction accuracy was uncorrelated with its EONR prediction accuracy, and so yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to identify EOIR map.
+Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN.
+CF-base consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation.
+We also showed that the model’s yield prediction accuracy was uncorrelated with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map.
 
@@
 All the trial designs examined here were based on five N rates.
-Having examined models with additional rates would have increased the number of possible N rates from which the EONR were selected, but reduced treatment pair replications and so the estimation accuracy.
+Having examined models with additional rates would have increased the number of possible N rates from which the EONR were selected, but reduced treatment pair replications and estimation accuracy.
 
@@
 Honest sampling comes at the cost of losing prediction accuracy of treatment effects because fewer samples are used to estimate treatment effects within leaves [@athey2016recursive].
-Therefore, if the ML analyses are conducted with OFPE data from a small field, CF may not outperform other ML methods
+Therefore, in the case in which ML analyses are conducted with OFPE data from a small field, CF may not outperform other ML methods
 
 Third, another interesting subject for future research is the potential of combining the ML methods with post-estimation spatial smoothing of the estimated EONR.
-It is a well known fact that soil/field characteristics are spatially correlated [@f2007methods;@goovaerts1999geostatistics]; this spatial correlation is likely to cause spatial correlation in EONRs, which would suggest that post-estimation spatial smoothing of EONRs may further improve the accuracy of EONR estimation.
+It is well known that soil/field characteristics are spatially correlated [@f2007methods;@goovaerts1999geostatistics]; this spatial correlation is likely to cause spatial correlation in EONRs, which would suggest that post-estimation spatial smoothing of EONRs may further improve the accuracy of EONR estimation.
 
-Finally, a natural and fruitful extension of the reported research would be to test CF and other ML methods in a dynamic setting where multiple years of experiments are conducted, allowing weather events into the analysis as explanatory variables.
-Crop simulation models (e.g., APSIM, DSSAT) could be used in place of the Mitscherlich-Baule production function used here to model the underlying yield response function, which could generate more realistic data, using actual soil/field characteristics and weather instead of abstract parameters in the analysis, and so better include the dynamic nature of cropping systems in the study of N management [@archontoulis2020predicting;@puntel2016modeling;@puntel2018systems].
+Finally, a natural and fruitful extension of the reported research would be to test CF and other ML methods in a dynamic setting on which multiple years of experiments are conducted, allowing weather events into the analysis as explanatory variables.
+Crop simulation models (e.g., APSIM, DSSAT) could replace the Mitscherlich-Baule production function used here to model the underlying yield response function, which could generate more realistic data, using actual soil/field characteristics and weather instead of abstract parameters in the analysis, and so better include the dynamic nature of cropping systems in the study of N management [@archontoulis2020predicting;@puntel2016modeling;@puntel2018systems].
 

### 2022-02-05 GitControlled/Writing/Re_JournalSubmission/replies_rev_2.rmd
Large revise of the manuscript and codes for re-submission

--- 2022-02-05 Writing/Re_JournalSubmission/replies_rev_2.Rmd
@@
 title: "Reply to Reviewer #2"
-author: 
+author: Shunkei Kakimoto
 output:
@@
 
-+ I modified the titles of all tables and figures.
++ I modified all the titles of tables and figures.
 </span>
@@
 
-+ I included units in Table 1 and Fig. 3. 
++ I removed Table 1. Instead, I explained about those parameters in section 3.1.3. I added units of "ymax" and "$\varepsilon$" to Figure 3.
 </span>
@@
 
-+ I added indent between "(kg/ha)" and "of"(before: "RMSE (kg/ha)of EONR", after: RMSE (kg/ha) of EONR)
++ I corrected the typo. 
 </span>
@@
 
-+ I added the unit (kg/ha) in the title of Table 3. Similarly, I added units in Table 2, Figure 8, 9, 10, and 11.  
++ I added the unit (kg/ha) to the Table: Mean RMSE of Yield Prediction by ML Methods and Modeling Scenarios. Similarly, I provided units to other result tables.
 </span>

### 2022-02-05 Codes/0_1_functions_gen_field.R

@@ -1,335 +1,0 @@
-# /*=================================================*/
-#' # Make experiment grids (basic cell, plot, strip)
-# /*=================================================*/
-make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
-
-  # /*=================================================*/
-  #' # Define functions
-  # /*=================================================*/
-  # /*----------------------------------*/
-  #' ## make polygons
-  # /*----------------------------------*/
-  make_polygon <- function(strt_point_new, multiplier, direction) {
-    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
-    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
-    point_3 <- point_2 + ab_xy_nml * cell_height
-    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
-
-    temp_polygon <- rbind(
-      point_1,
-      point_2,
-      point_3,
-      point_4,
-      point_1
-    ) %>%
-      list() %>%
-      st_polygon()
-
-    return(temp_polygon)
-  }
-
-  # /*----------------------------------*/
-  #' ## rotation matrix
-  # /*----------------------------------*/
-  rotate_mat_p90 <- matrix(
-    c(
-      cos(pi / 2),
-      sin(pi / 2),
-      -sin(pi / 2),
-      cos(pi / 2)
-    ),
-    nrow = 2
-  )
-
-  # /*----------------------------------*/
-  #' ## Make an extended line
-  # /*----------------------------------*/
-  # make line with starting point and a desired shift
-  make_extended_line <- function(starting_point, step, multiplier, step_v) {
-    extended_line <- rbind(
-      starting_point + step * multiplier,
-      starting_point + step_v * 1000 + step * multiplier
-    ) %>%
-      st_linestring() %>%
-      list() %>%
-      st_as_sfc() %>%
-      st_set_crs(st_crs(field))
-
-    return(extended_line)
-  }
-
-  # /*----------------------------------*/
-  #' ## Check intersections
-  # /*----------------------------------*/
-  # check the intersection of the lines in the direction specified
[…]

### 2022-02-05 Codes/0_3_functions_main_sim.R

@@ -1,457 +1,0 @@
-# /*----------------------------------*/
-#' ## Economic parameters
-# /*----------------------------------*/
-price_table <- data.table(
-  # === $/kg corn ===#
-  pCorn = round(c(3.5, 3.5, 5) * 200 / 5080, digits = 3),
-  # === $/kg N ===#
-  pN = round(c(0.4, 0.6, 0.4) / 0.453592, digits = 3)
-)
-
-
-# /*=================================================*/
-#' # Run main simulations
-# /*=================================================*/
-sim_par <- function(i, reg_data, test_data, N_levels) {
-  print(paste0("working on ", i, " th iteration."))
-  # for example
-  # reg_data = train_dt; test_data = test_dt; N_levels = N_levels
-
-  # /*----------------------------------*/
-  #' ## run ML analyses
-  # /*----------------------------------*/
-
-  ## == all the combinations of variables ==##
-  var_ls_variations <- list(
-    c("alpha", "beta", "ymax"),
-    c("alpha", "beta", "ymax", "theta_1", "theta_2"),
-    c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2"),
-    c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")
-  )
-
-  #--- all the cases to consider ---#
-  case_data <- expand.grid(
-    var_ls = var_ls_variations,
-    Method = c("CF_base", "BRF", "RF")    
-  ) %>%
-  tibble()
-
-
-  results_data <- case_data %>%
-    mutate(
-      opt_N_data = future_lapply(
-        seq_len(nrow(.)),
-        function(x) {
-          ### === apply various methods to get optimal N ===###
-          get_opt_N(
-            reg_data = reg_data,
-            test_data = test_data,
-            var_ls = .$var_ls[[x]],
-            rates_ls = N_levels,
-            Method = .$Method[[x]]
-          )
-        },
-        future.seed = TRUE
-      )
-    )%>%
-    unnest(., cols= "opt_N_data")%>%
-    data.table()%>%
-    setnames("unique_cell_id", "unique_subplot_id")
-
-  return(results_data)
-     
-}
-
-
-
-
-get_opt_N <- function(reg_data, test_data, var_ls, rates_ls, Method) {
-
[…]

### 2022-02-05 Codes/1_2_generate_coefficients.R

@@ -1,255 +1,0 @@
-# /*=================================================*/
-#' # Preparation
-# /*=================================================*/
-library(here)
-library(tmap)
-library(sp)
-library(sf)
-library(agricolae)
-library(lwgeom)
-library(measurements)
-library(raster)
-library(data.table)
-library(tidyverse)
-library(gstat)
-
-
-
-#--- source functions ---#
-source(here("Codes", "functions.R"))
-
-# /*----------------------------------*/
-#' ## Field data
-# /*----------------------------------*/
-
-field_padding <- readRDS(here("Data", "CNN_Simulations", "field_padding.rds"))
-
-
-# /*=================================================*/
-#' # Generate coefficients
-# /*=================================================*/
-xy <- dplyr::select(field_padding, unique_cell_id) %>%
-  cbind(., st_coordinates(st_centroid(.))) %>%
-  st_drop_geometry() %>%
-  data.table()
-
-gen_coefs <- function(mean, psill, range, coef_name, nsim, xy) {
-  
-  g_N <- gstat(
-    formula = z ~ 1,
-    locations = ~ X + Y,
-    dummy = T,
-    beta = mean,
-    model = vgm(
-      psill = psill,
-      range = range,
-      nugget = 0,
-      model = "Sph" # changed from "Exp", "Sph"
-
-    ),
-    nmax = 50 # number of nearest observations
-  )
-
-  b_sim <- predict(g_N, newdata = xy, nsim = nsim) %>%
-    data.table()%>%
-    melt(id.vars = c("X", "Y")) %>%
-    # data.table() %>%
-    setnames(c("variable", "value"), c("sim", coef_name)) %>%
-    .[, sim := as.numeric(gsub("sim", "", sim))] %>%
-    xy[., on = c("X", "Y")] %>%
-    .[, c("unique_cell_id", "sim", coef_name), with = FALSE]
-
-  return(b_sim)
-}
-
-
-sp_range <- 400
-B <- 1000
-
-#--- ymax ---#
-ymax <- gen_coefs(
-  mean = 12000,
[…]

### 2022-02-05 Codes/2_1_generate_analysis_data.R

@@ -1,77 +1,0 @@
-# /*=================================================*/
-#' # Preparation
-# /*=================================================*/
-library(here)
-library(mgcv)
-library(ggplot2)
-library(grf)
-library(sf)
-library(measurements)
-library(data.table)
-library(tidyverse)
-library(future.apply)
-library(parallel)
-
-
-#--- source functions ---#
-source(here("GitControlled/Codes/0_2_function_gen_analysis_data.R"))
-
-# /*----------------------------------*/
-#' ## Datasets
-# /*----------------------------------*/
-# field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
-# coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds")))
-
-# === prices ===#
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-
-
-# /*=================================================*/
-#' # Generate raw dataset (cell-level)
-# /*=================================================*/
-
-##== Generate Cell-Level Field Data ==##
-raw_data <- lapply(
-	1:1000, function(x) {
-		prepare_raw_data(
-			i = x,
-			field = field,
-			coef_data_m = coef_data[sim == x, ],
-			coef_data_t = coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ],
-			app_error="no"
-		)
-	}
-)
-
-# saveRDS(raw_data, here("Shared/Data/for_Simulations/raw_reg_test_data.rds"))
-reg_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
-test_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
-
-# saveRDS(reg_raw_data, here("Shared/Data/for_Simulations/reg_raw_data.rds"))
-# saveRDS(test_raw_data, here("Shared/Data/for_Simulations/test_raw_data.rds"))
-
-# /*=================================================*/
-#' # Generate analysis dataset (subplot-level)
-# /*=================================================*/
-reg_raw_data <- readRDS(here("Shared/Data/for_Simulations/reg_raw_data.rds"))
-test_raw_data <- readRDS(here("Shared/Data/for_Simulations/test_raw_data.rds"))
-
-##== Aggregate Cell-Level Field Data to Subplot-Level Field Data ==##
-sim_data <- lapply(
[…]

### 2022-02-05 Codes/2_2_main_sim.R

@@ -1,76 +1,0 @@
-# /*===== Run on RGUI =====*/
-
-#/*----------------------------------*/
-#' ## Preparation
-#/*----------------------------------*/
-library(here)
-library(grf)
-library(data.table)
-library(tidyverse)
-library(future.apply)
-library(parallel)
-
-
-#--- source functions ---#
-setwd("~/Dropbox/ResearchProject/ML_VRA")
-source("./GitControlled/Codes/0_3_functions_main_sim.R")
-
-# /*----------------------------------*/
-#' ## Datasets
-# /*----------------------------------*/
-# === prices ===#
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-reg_data_all <- readRDS("./Shared/Data/for_Simulations/reg_data.rds")
-test_data_all <- readRDS("./Shared/Data/for_Simulations/test_data.rds")
-
-
-# x=1
-# train_dt <- reg_data_all[sim==x&padding==1,]
-# test_dt <- test_data_all[sim==x&padding==1,]
-# N_levels <- reg_data_all[sim==x,]$rate%>%unique()%>%sort()
-
-
-
-# /*=================================================*/
-#' # Simulation 
-# /*=================================================*/
-
-# === set up for parallel computations === #
-plan(multicore, workers = availableCores()-2)
-options(future.globals.maxSize= 850*1024^2)
-set.seed(1378)
-
-# --- Number of iterations --- #
-B=1000
-
-# === run simulation === #
-sim_results <- lapply(
-	  1:B, function(x) {
-	    sim_par(
-	      i = x,
-	      reg_data = reg_data_all[sim==x&padding==1,],
-	      test_data = test_data_all[sim==x&padding==1,],
-	      N_levels = reg_data_all[sim==x,]$rate%>%unique()%>%sort()
-	    )
-	  }
-	) %>%
-	rbindlist()%>%
-	rowwise() %>%
-	mutate(var_ls_name = paste0(var_ls, collapse = "_")) %>%
-	data.table()%>%
-	.[, Method := factor(Method, levels = c("RF", "BRF", "CF_base"))] %>%
-	.[, Model := factor(var_ls_name)] %>%
-	.[, Model := case_when(
-    	Model == "alpha_beta_ymax" ~ "aby",
-    	Model == "alpha_beta_ymax_theta_1_theta_2" ~ "abytt",
[…]

### 2022-02-05 Codes/3_1_SimDataAnalysis.R

@@ -1,232 +1,0 @@
-#/*----------------------------------*/
-#' ## Preparation 
-#/*----------------------------------*/
-library(here)
-library(data.table)
-library(RColorBrewer)
-library(patchwork)
-library(ggplot2)
-library(ggthemes)
-library(viridis)
-library(hrbrthemes)
-library(tidyverse)
-library(ggpubr)
-library(here)
-
-source(here("GitControlled/Codes/0_2_functions_gen_analysis_data.R"))
-source(here("GitControlled/Codes/0_3_functions_main_sim.R"))
-
-# === prices ===#
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-
-# === Training and Testing data sets === #
-reg_data_all <- readRDS("./Shared/Data/for_Simulations/reg_data.rds")
-test_data_all <- readRDS("./Shared/Data/for_Simulations/test_data.rds")
-
-source_dt <- 
-    bind_rows(reg_data_all, test_data_all, .id = "type") %>%
-    .[padding==1, .(sim, type, unique_cell_id, alpha, beta, ymax)] %>%
-    .[,type := case_when(type == "1" ~ "train", type == "2" ~ "test")] %>%
-    setnames('unique_cell_id', "unique_subplot_id")
-
-# ==========================================================================
-# Results of RF, BRF and CF
-# ==========================================================================
-
-# === All Results === #
-simRes_all <- 
-    readRDS(here("Shared/Results_journal/SimRes_all.rds")) %>%
-    .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
-    .[, Method := factor(Method, levels = c("RF", "BRF", "CF_base"))] 
-
-# === function for RMSE calculation === #
-rmse_general <-function(preds,actual){ 
-  sqrt(mean((actual - preds)^2))
-}
-
-
-# /*=================================================*/
-#' # RMSE of EONRs and Profit Loss calculation
-# /*=================================================*/
-pi_loss_dt <- source_dt %>%
[…]

### 2022-02-05 Codes/3_2_CompTeEstimation.R

@@ -1,129 +1,0 @@
-# /*=================================================*/
-#' # Preparation
-# /*=================================================*/
-library(here)
-library(ggplot2)
-library(grf)
-library(sf)
-library(here)
-library(data.table)
-library(tidyverse)
-library(ggthemes)
-
-
-#/*----------------------------------*/
-#' ## Preparation
-#/*----------------------------------*/
-
-#--- source functions ---#
-source(here("GitControlled/Codes/0_3_functions_main_sim.R"))
-
-
-#--- load the data ---#  
-reg_data_all <- readRDS(here("Shared", "Data", "for_Simulations", "reg_data.rds"))
-test_data_all <- readRDS(here("Shared", "Data", "for_Simulations", "test_agg_data.rds"))
-
-
-#--- pick a single simulation round ---#
-x = 1
-reg_data_sample <- reg_data_all[sim==x & padding==1,]
-test_data_sample <- test_data_all[sim==x & padding==1,]
-N_levels <- reg_data_sample$rate%>%unique()%>%sort()
-
-
-#--- all the cases to be considered ---#
-te_var_ls_variations <- list(
-    c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")
-    )
-
-te_case_data <- expand.grid(
-    var_ls = te_var_ls_variations,
-    Method = c("CF_base", "BRF", "RF")    
-  ) %>%
-  tibble()
-
-
-# /*================================================================*/
-#' # Treatment Effect Calculation (CF-base vs RF vs BRF)
-# /*================================================================*/
-
-# === set up for parallel computations === #
-plan(multicore, workers = availableCores()-2)
-options(future.globals.maxSize= 850*1024^2)
-set.seed(1378)
-
-te_dt_allML <- te_case_data %>%
-	mutate(
-		te_data = future_lapply(
-			seq_len(nrow(.)),
-			function(x) {
-				 get_te_dt(
-            test_data = test_data_sample,
-            var_ls = .$var_ls[[x]],
-            rates_ls = N_levels,
-            Method = .$Method[[x]]
-          )
-        },
-      future.seed = TRUE
-    )
-  )%>%
-  unnest(., cols= "te_data")%>%
-  data.table()%>%
[…]

### 2022-02-05 Codes/MACF/0_0_functions.R

@@ -1,1678 +1,0 @@
-# /*=================================================*/
-#' # Make experiment grids (basic cell, plot, strip)
-# /*=================================================*/
-make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
-
-  # /*=================================================*/
-  #' # Define functions
-  # /*=================================================*/
-  # /*----------------------------------*/
-  #' ## make polygons
-  # /*----------------------------------*/
-  make_polygon <- function(strt_point_new, multiplier, direction) {
-    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
-    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
-    point_3 <- point_2 + ab_xy_nml * cell_height
-    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
-
-    temp_polygon <- rbind(
-      point_1,
-      point_2,
-      point_3,
-      point_4,
-      point_1
-    ) %>%
-      list() %>%
-      st_polygon()
-
-    return(temp_polygon)
-  }
-
-  # /*----------------------------------*/
-  #' ## rotation matrix
-  # /*----------------------------------*/
-  rotate_mat_p90 <- matrix(
-    c(
-      cos(pi / 2),
-      sin(pi / 2),
-      -sin(pi / 2),
-      cos(pi / 2)
-    ),
-    nrow = 2
-  )
-
-  # /*----------------------------------*/
-  #' ## Make an extended line
-  # /*----------------------------------*/
-  # make line with starting point and a desired shift
-  make_extended_line <- function(starting_point, step, multiplier, step_v) {
-    extended_line <- rbind(
-      starting_point + step * multiplier,
-      starting_point + step_v * 1000 + step * multiplier
-    ) %>%
-      st_linestring() %>%
-      list() %>%
-      st_as_sfc() %>%
-      st_set_crs(st_crs(field))
-
-    return(extended_line)
-  }
-
-  # /*----------------------------------*/
-  #' ## Check intersections
-  # /*----------------------------------*/
-  # check the intersection of the lines in the direction specified
-  check_intersection <- function(field, step, direction, step_v) {
[…]

### 2022-02-05 Codes/MACF/1_2_SimDataAnalysis.R

@@ -1,92 +1,0 @@
-# ==========================================================================
-# Preparation
-# ==========================================================================
-library(here)
-library(data.table)
-library(RColorBrewer)
-library(patchwork)
-library(ggplot2)
-library(ggthemes)
-library(viridis)
-library(hrbrthemes)
-library(tidyverse)
-library(ggpubr)
-library(here)
-library(gridExtra)
-library(measurements)
-
-source(here("GitControlled", "Codes_MACF", "0_0_functions.R"))
-
-
-# ==========================================================================
-# Optimal N: RF, BRF, CF-stepwise, CF-base
-# ==========================================================================
-
-####==== source data ====#####
-# simRes_honest_source <- readRDS(here("Shared", "Results", "SimRes_withHonesty_source.rds"))%>%
-#     setnames(c("model","var_case"), c("Method", "Model")) %>%
-#     .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
-#     .[, Method:=factor(Method, levels = c("RF", "BRF", "CF_stepwise", "CF_base"))]
-
-simRes_honest_source <- readRDS(here("Shared", "Results_MACF", "SimRes_MACF_BRF_RF_100.rds"))%>%
-    setnames(c("model","var_case"), c("Method", "Model")) %>%
-    .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
-    .[, Method:=factor(Method, levels = c("RF", "BRF", "MACF"))]
-
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-
-rmse_general <-function(preds,actual){ 
-  sqrt(mean((actual - preds)^2))
-}
-
-
-# ===================================
-# RMSE and profit loss calculation
-# ===================================
-# (1) calculate profit loss relative to the maximum profit for each simulation
-# (2) get the summary of profit loss for all the methods.
-
-
-pi_loss_dt <- readRDS(here("Shared", "Data", "for_Simulations", "test_agg_data.rds")) %>%
-    .[padding==1,.(sim, unique_cell_id, alpha, beta, ymax)]%>%
-    setnames('unique_cell_id', "unique_subplot_id") %>%
[…]

### 2022-02-05 Codes/PrepareResults.R

@@ -1,1221 +1,0 @@
-## -----------------------------------------------
-library(knitr)
-# library(here)
-
-knitr::opts_chunk$set(
-    cache = FALSE,
-    warning = FALSE,
-    message = FALSE
-    )
-
-# opts_knit$set(root.dir=here())
-opts_knit$set(root.dir = "~/Dropbox/ResearchProject/ML_VRA")
-
-
-## ---- cache = FALSE-----------------------------
-# === packages ===#
-library(sf)
-library(data.table)
-library(RColorBrewer)
-library(patchwork)
-library(grf)
-library(magrittr)
-library(ggplot2)
-library(ggthemes)
-library(viridis)
-library(tidyverse)
-library(ggpubr)
-library(flextable)
-library(officer)
-library(officedown)
-library(modelsummary)
-library(here)
-library(gridExtra)
-library(DiagrammeR)
-library(latex2exp)
-
-here::i_am("GitControlled/Codes/0_0_functions.R")
-
-## ----source, results = "hide", fig.show='hide', cache = FALSE-----------------
-# setwd(here())
-source("./GitControlled/Codes/0_0_functions.R")
-# source("./GitControlled/Codes/functions_stepwise_vs_base.R")
-
-
-## ----setup, warning=FALSE, message=FALSE, cache= TRUE----
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-sp_range <- 400
-
-field <- readRDS("./Shared/Data/for_Simulations/field_padding.rds") %>%
-    filter(padding==1)%>%
-    dplyr::select(unique_cell_id)
-
-
-####==== (1) cell-level dataset ====####
-# coef_data <- readRDS("./Shared/Data/for_Simulations/cnn_coefficients_sprange_400.rds")
-
-# x=1
-# coef_data_m <- coef_data[sim == x, ]
-# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
-
-# sample_dt <- prepare_raw_data(1, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no")
-
-# sample_training_cell <- sample_dt$reg_raw_data
-
-# saveRDS(sample_training_cell, "./Shared/Data/for_writing/sample_reg_raw_data.rds")
-
-
[…]

### 2022-02-05 Codes/eval_res_CNN_ST.R

@@ -1,230 +1,0 @@
-library(here)
-library(ggplot2)
-library(grf)
-library(sf)
-library(data.table)
-library(tidyverse)
-library(ggthemes)
-library(gridExtra)
-library(parallel)
-
-#--- source functions ---#
-source(here("Codes", "cnn_related_functions.R")) 
-
-#--- field ---#
-field_cnn <- readRDS(here("Data", "CNN_Simulations", "cnn_field_padding.rds"))
-
-# === prices ===#
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-
-# /*=================================================*/
-#' # Preparation: Load the Results 
-# /*=================================================*/
-
-#=== load the source data for training and testing ===#
-# training <- readRDS(here("Data", "CNN_Simulations", "reg_raw_data.rds"))
-# testing <- readRDS(here("Data", "CNN_Simulations", "test_raw_data.rds"))
-
-
-# training_cell <- readRDS(here("Data", "CNN_Simulations", "reg_raw_data.rds"))
-
-training_subplot <- readRDS(here("Data", "CNN_Simulations", "reg_data.rds"))%>%
-	setnames("unique_cell_id", "id")%>%
-	.[padding==1, ]
-
-
-testing_subplot <- readRDS(here("Data", "CNN_Simulations", "test_agg_data.rds"))%>%
-	setnames("unique_cell_id", "id")%>%
-	.[padding==1, ]
-
-
-nonpadding_id <- testing_subplot$id%>%unique()
-
-
-
-
-##== for comparison: CF, BRF, RF resutls ==##
-res_forest <- readRDS(here("CNN_Results", "SimRes_sp_400.rds"))
-
-
-
-#=== load the CNN_ST results ===#
-cnn_st_aby_source <- read_csv(here("CNN_Results", "alldata_model1_CNN_ST.csv"))%>%
-	data.table()%>%
-	setnames("pred", "yield_hat")%>%
-	.[,.(id, rate, yield_hat, sim)]%>%
-	.[, var_case:= "aby"]
-
-
-
-
-
-#=== combine CNN resutls into one dataset ===#
[…]

### 2022-02-05 Codes/others/CNN_PrepareResults.R

@@ -1,862 +1,0 @@
-library(sf)
-library(data.table)
-library(RColorBrewer)
-library(patchwork)
-library(grf)
-library(magrittr)
-library(ggplot2)
-library(ggthemes)
-library(viridis)
-library(tidyverse)
-library(ggpubr)
-library(flextable)
-library(officer)
-library(modelsummary)
-library(here)
-library(gridExtra)
-library(DiagrammeR)
-library(causalTree)
-library(rpart)
-library(rattle)
-library(sparkline)
-library(htmltools)
-library(htmlwidgets)
-library(equatags)
-library(equatiomatic)
-# ===================================
-# Load the data
-# ===================================
-source(here("Codes", "functions.R"))
-source(here("Codes", "functions_stepwise_vs_base.R"))
-
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-
-# ===================================
-# sample data creation 
-# ===================================
-field <- readRDS(here("Data", "Simulations", "field.rds")) %>%
-  cbind(., st_coordinates(st_centroid(.)))
-
-coef_data <- readRDS(here("Data", "Simulations", paste0("coefficients_sprange_600.rds")))
-
-coef_data_m <- coef_data[sim == 1, ]
-
-# data <- coef_data_m[data.table(field), on = "unique_cell_id"] %>%
-#     .[, opt_N := (log(pN) - log(-pCorn * ymax * beta) - alpha) / beta]
-
-# all_opt_N <- data[, opt_N]
-
-# # --- for training ---#
-# # hist(all_opt_N)
-# N_levels <- seq(
-#   quantile(all_opt_N, prob = 0.05) - 20,
-#   quantile(all_opt_N, prob = 0.95) + 20,
-#   length = 5
-#       ) %>%
-# round()
-
-# # data <- assign_rates(st_as_sf(data), N_levels, pattern = "sequential") %>%
-# data <- assign_rates(st_as_sf(data), N_levels) %>%
-#   data.table()
-
-
-# data %<>% .[, det_yield := gen_yield_MB(ymax, alpha, beta, rate)] %>%
-#     # .[,det_yield:=b0+b1*N+b2*N^2] %>%
-#     # === error ===#
-#     .[, yield := det_yield * (1 + m_error)] %>%
[…]

### 2022-02-05 Codes/others/CNN_ex_code_modified.R

@@ -1,192 +1,0 @@
-# ==========================================================================
-#' This is just an example code  for demonstration purposes
-# ==========================================================================
-
-
-library(grf) # if you don't have one, "install.packages("grf")"
-library(data.table) #if you don't have one, "install.packages("data.table")"
-library(tidyverse) #if you don't have one, "install.packages("tidyverse")"
-library(parallel) #if you don't have one, "install.packages("parallel")"
-
-
-
-# ==========================================================================
-# Load sample training and testing data
-# ==========================================================================
-#' Please note that the data(for training and testing) we are using for CF, RF and BRF are slightly different from the data for CNN.
-#' The data for CNN is more finer scale(cell-level), so your data should have more number of rows in the data.
-
-#' The shared data contains the data for just first three simulation rounds(sim=1,2,3)
-
-# === load training and testing data === # 
-# Please change the path to the folder where you downloaded and saved them
-train_data_all <- readRDS("~/OneDrive\ -\ University\ of\ Nebraska-Lincoln/ML_VRA/Data/CNN_demo/demo_train_dt.rds")
-test_data_all <- readRDS("~/OneDrive\ -\ University\ of\ Nebraska-Lincoln/ML_VRA/Data/CNN_demo/demo_test_dt.rds")
-
-
-
-# === prices ===#
-pCorn <- 0.138
-pN <- 1.323
-
-
-# /*====================================================================================*/
-#' Simulation example
-#' This is using two functions(sim_par() and BRF_analysis()) which are defined in the below
-#' So, please load them first, then run the below code
-#' 
-#' The idea is that we just reapeat the same process(training the model and testing)
-#' 
-# /*====================================================================================*/
-sim_results <- lapply(
-    1:2, function(x) {
-      sim_par(
-        i = x,
-        reg_data = train_data_all[sim==x & padding==1,], #<- padding==1 is just for our methods.
-        test_data = test_data_all[sim==x & padding==1,]
-      )
-    }
-  ) %>%
[…]

### 2022-02-05 Codes/others/cnn_honesty_yield_pred_function.R

@@ -1,1735 +1,0 @@
-# /*=================================================*/
-#' # Make experiment grids (basic cell, plot, strip)
-# /*=================================================*/
-make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
-
-  # /*=================================================*/
-  #' # Define functions
-  # /*=================================================*/
-  # /*----------------------------------*/
-  #' ## make polygons
-  # /*----------------------------------*/
-  make_polygon <- function(strt_point_new, multiplier, direction) {
-    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
-    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
-    point_3 <- point_2 + ab_xy_nml * cell_height
-    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
-
-    temp_polygon <- rbind(
-      point_1,
-      point_2,
-      point_3,
-      point_4,
-      point_1
-    ) %>%
-      list() %>%
-      st_polygon()
-
-    return(temp_polygon)
-  }
-
-  # /*----------------------------------*/
-  #' ## rotation matrix
-  # /*----------------------------------*/
-  rotate_mat_p90 <- matrix(
-    c(
-      cos(pi / 2),
-      sin(pi / 2),
-      -sin(pi / 2),
-      cos(pi / 2)
-    ),
-    nrow = 2
-  )
-
-  # /*----------------------------------*/
-  #' ## Make an extended line
-  # /*----------------------------------*/
-  # make line with starting point and a desired shift
-  make_extended_line <- function(starting_point, step, multiplier, step_v) {
-    extended_line <- rbind(
-      starting_point + step * multiplier,
-      starting_point + step_v * 1000 + step * multiplier
-    ) %>%
-      st_linestring() %>%
-      list() %>%
-      st_as_sfc() %>%
-      st_set_crs(st_crs(field))
-
-    return(extended_line)
-  }
-
-  # /*----------------------------------*/
-  #' ## Check intersections
-  # /*----------------------------------*/
-  # check the intersection of the lines in the direction specified
-  check_intersection <- function(field, step, direction, step_v) {
[…]

### 2022-02-05 Codes/others/cnn_prepare_data.R

@@ -1,309 +1,0 @@
-library(here)
-library(mgcv)
-library(tmap)
-library(ggplot2)
-library(grf)
-library(sp)
-library(sf)
-library(agricolae)
-library(lwgeom)
-library(measurements)
-library(raster)
-library(data.table)
-library(tidyverse)
-library(future.apply)
-library(parallel)
-
-
-#--- source functions ---#
-source(here("Codes", "functions.R"))
-
-# /*----------------------------------*/
-#' ## Datasets
-# /*----------------------------------*/
-field_cnn <- readRDS(here("Data", "CNN_Simulations", "cnn_field_padding.rds"))
-
-# ggplot(st_as_sf(field_dt)) +
-#   geom_sf(aes(fill = cluster_id_1), size = 0) +
-#   geom_sf_text(aes(label = cluster_id_1))
-sp_range=400
-
-cnn_coef_data <- readRDS(here("Data", "CNN_Simulations", paste0('cnn_coefficients_sprange_',sp_range,'.rds')))
-
-
-# === prices ===#
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-
-
-
-# For example
-x=2
-field=field_cnn
-coef_data_m=cnn_coef_data[sim == x, ]
-# coef_data_t=coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
-
-# /*~~~~~~~~~~~~~~~~~~~~~~*/
-#' ### Data preparation
-# /*~~~~~~~~~~~~~~~~~~~~~~*/
-# === merge field data with the coefs data ===#
-data <- coef_data_m[data.table(field), on = "unique_cell_id"] %>%
-  .[, opt_N := (log(pN) - log(-pCorn * ymax * beta) - alpha) / beta]
-
-
-# test_data <- coef_data_t[data.table(field), on = "unique_cell_id"] %>%
-# .[, opt_N := (log(pN) - log(-pCorn * ymax * beta) - alpha) / beta]
-
-
-# === check the spatial distribution of optimal N ===#
-# ggplot(st_as_sf(data)) +
-#   geom_sf(aes(fill = opt_N),size = 0)+
-#   scale_fill_viridis_c()
-
-# /*~~~~~~~~~~~~~~~~~~~~~~*/
-#' ### Assign N (5 N treatment rates)
-# /*~~~~~~~~~~~~~~~~~~~~~~*/
[…]

### 2022-02-05 Codes/others/cnn_related_functions_subplot.R

@@ -1,1834 +1,0 @@
-# /*=================================================*/
-#' # Make experiment grids (basic cell, plot, strip)
-# /*=================================================*/
-make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
-
-  # /*=================================================*/
-  #' # Define functions
-  # /*=================================================*/
-  # /*----------------------------------*/
-  #' ## make polygons
-  # /*----------------------------------*/
-  make_polygon <- function(strt_point_new, multiplier, direction) {
-    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
-    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
-    point_3 <- point_2 + ab_xy_nml * cell_height
-    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
-
-    temp_polygon <- rbind(
-      point_1,
-      point_2,
-      point_3,
-      point_4,
-      point_1
-    ) %>%
-      list() %>%
-      st_polygon()
-
-    return(temp_polygon)
-  }
-
-  # /*----------------------------------*/
-  #' ## rotation matrix
-  # /*----------------------------------*/
-  rotate_mat_p90 <- matrix(
-    c(
-      cos(pi / 2),
-      sin(pi / 2),
-      -sin(pi / 2),
-      cos(pi / 2)
-    ),
-    nrow = 2
-  )
-
-  # /*----------------------------------*/
-  #' ## Make an extended line
-  # /*----------------------------------*/
-  # make line with starting point and a desired shift
-  make_extended_line <- function(starting_point, step, multiplier, step_v) {
-    extended_line <- rbind(
-      starting_point + step * multiplier,
-      starting_point + step_v * 1000 + step * multiplier
-    ) %>%
-      st_linestring() %>%
-      list() %>%
-      st_as_sfc() %>%
-      st_set_crs(st_crs(field))
-
-    return(extended_line)
-  }
-
-  # /*----------------------------------*/
-  #' ## Check intersections
-  # /*----------------------------------*/
-  # check the intersection of the lines in the direction specified
-  check_intersection <- function(field, step, direction, step_v) {
[…]

### 2022-02-05 Codes/others/cnn_simulate_yield.R

@@ -1,146 +1,0 @@
-# /*=================================================*/
-#' # Preparation
-# /*=================================================*/
-library(here)
-library(mgcv)
-library(tmap)
-library(ggplot2)
-library(grf)
-library(sp)
-library(sf)
-library(agricolae)
-library(lwgeom)
-library(measurements)
-library(raster)
-library(data.table)
-library(tidyverse)
-library(future.apply)
-library(parallel)
-
-
-#--- source functions ---#
-source(here("Codes", "cnn_honesty_yield_pred_function.R"))
-
-# /*----------------------------------*/
-#' ## Datasets
-# /*----------------------------------*/
-field_cnn <- readRDS(here("Data", "CNN_Simulations", "cnn_field_padding.rds"))
-
-# ggplot(field_cnn) +
-#   geom_sf()
-
-# ggplot(field_cnn) +
-#   geom_sf(aes(fill = factor(padding)), size = 0)
-
-sp_range=400
-
-# coef_data <- readRDS(here("Data", "CNN_Simulations", paste0('cnn_coefficients_sprange_',sp_range,'.rds')))
-
-# === prices ===#
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-
-
-# /*=================================================*/
-#' # Simulation
-# /*=================================================*/
-train_data <- readRDS(here("Data", "CNN_Simulations", "reg_data.rds"))
-test_data <- readRDS(here("Data", "CNN_Simulations", "test_agg_data.rds"))
-
-
-sim_results <- lapply(
-	  1:100, function(x) {
-	    sim_par(
-	      i = x,
-	      reg_data = train_data[sim==x&padding==1,],
-	      test_agg_data = test_data[sim==x&padding==1,]
-	    )
-	  }
-	) %>%
-	rbindlist()%>%
-	rowwise() %>%
-	mutate(var_ls_name = paste0(var_ls, collapse = "_")) %>%
-	data.table()%>%
-	.[, var_case := factor(var_ls_name)] %>%
-	.[, .(sim, honesty,  model, var_case, r2_y)] %>%
-	.[, var_case := case_when(
[…]

### 2022-02-05 Codes/others/ex_code_for_yield_prediction.R

@@ -1,92 +1,0 @@
-# ==========================================================================
-#' Just for yield prediction with varioius N rates
-# ==========================================================================
-
-
-library(grf) # if you don't have one, "install.packages("grf")"
-library(data.table) #if you don't have one, "install.packages("data.table")"
-library(tidyverse) #if you don't have one, "install.packages("tidyverse")"
-library(parallel) #if you don't have one, "install.packages("parallel")"
-
-
-
-# === load training and testing data === # 
-#' Please note that the data(for training and testing) we are using for CF, RF and BRF are slightly different from the data for CNN.
-#' The data for CNN is more finer scale(cell-level), so your data should have more number of rows in the data.
-
-#' The shared data contains the data for just first three simulation rounds(sim=1,2,3)
-
-# Please change the path to the folder where you downloaded and saved them
-train_data_all <- readRDS("~/OneDrive\ -\ University\ of\ Nebraska-Lincoln/ML_VRA/Data/CNN_demo/demo_train_dt.rds")
-test_data_all <- readRDS("~/OneDrive\ -\ University\ of\ Nebraska-Lincoln/ML_VRA/Data/CNN_demo/demo_test_dt.rds")
-
-
-
-#=== for example (the simplest modeling scenario)===#
-var_case <- c("alpha", "beta", "ymax")
-
-
-
-#=== demostration of yield prediction with BRF ===#
-sim_res <- lapply(
-	1:3, function(x){
-	BRF_prediction(
-		i = x,
-		reg_data = train_data_all[sim==x & padding==1,], #<- padding==1 is just for our methods.
-        test_data = test_data_all[sim==x & padding==1,], #<- padding==1 is just for our methods.
-        var_ls = var_case
-		)
-	}
-)%>%
-rbindlist()
-
-
-
-
-
-#=== this is the function of BRF for yield prediction ===#
-BRF_prediction <- function(i, reg_data, test_data, var_ls) {
-  print(paste0("working on ", i, " th iteration."))
-  # For example,
-  # i=1
-  # reg_data = train_data_all[sim==1 & padding==1,]
-  # test_data = test_data_all[sim==1 & padding==1,]
-  # var_ls = c("alpha", "beta", "ymax")
-
-  # /*----------------------------------*/
-  #' Training Boosted random forest
-  # /*----------------------------------*/
[…]

### 2022-02-05 Codes/others/res_CNNvsForest.R

@@ -1,394 +1,0 @@
-# /*=================================================*/
-#' # Preparation
-# /*=================================================*/
-
-library(here)
-library(ggplot2)
-library(grf)
-library(sf)
-library(data.table)
-library(tidyverse)
-
-#--- source functions ---#
-source(here("Codes", "cnn_related_functions.R")) 
-
-#--- field ---#
-# field_cnn <- readRDS(here("Data", "CNN_Simulations", "cnn_field_padding.rds"))
-
-# === prices ===#
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-
-#---training dataset ---#
-# raw_data <- readRDS(here("Results","cnn_raw_data_1 (1).rds"))%>%
-# 	.[,unique_cell_id := paste0(strip_id,"_",subplot_id)] %>% 
-#   .[padding==1,]
-
-reg_data <- readRDS(here("Results","cnn_reg_data_1 (1).rds"))%>%
-  .[,unique_cell_id := paste0(strip_id,"_",subplot_id)]
-
-
-reg_data_forest <- copy(reg_data) %>% 
-  .[padding==1,]
-
-# reg_data_forest$rate %>% unique() %>% sort()
-
-
-#---training dataset ---#
-test_raw_data <- readRDS(here("Results","cnn_raw_data_2 (1).rds"))
-
-
-test_agg_data <- readRDS(here("Results","cnn_reg_data_2 (1).rds"))%>%
-	.[,unique_cell_id := paste0(strip_id,"_",subplot_id)] %>%
-  .[, `:=`(
-    strip_id = NULL,
-    subplot_id = NULL
-  )]
-
-test_agg_data$rate %>% unique()
-
-
-# "cnn_reg_data_2 (1).rds" is the same as this one
-test_agg_data_opt_N <- test_raw_data[, .(
-    yield = mean(yield),
-    opt_N = mean(opt_N),
-    rate = mean(rate),
-    alpha = mean(alpha),
-    beta = mean(beta),
-    ymax = mean(ymax),
-    alpha1 = mean(alpha1),
-    alpha2 = mean(alpha2),
-    beta1 = mean(beta1),
-    beta2 = mean(beta2),
-    ymax1 = mean(ymax1),
-    ymax2 = mean(ymax2),
-    theta_1 = mean(theta_1),
-    theta_2 = mean(theta_2),
[…]

### 2022-02-05 Codes/temp_sim/0_functions.R

@@ -1,1625 +1,0 @@
-# /*=================================================*/
-#' # Make experiment grids (basic cell, plot, strip)
-# /*=================================================*/
-make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
-
-  # /*=================================================*/
-  #' # Define functions
-  # /*=================================================*/
-  # /*----------------------------------*/
-  #' ## make polygons
-  # /*----------------------------------*/
-  make_polygon <- function(strt_point_new, multiplier, direction) {
-    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
-    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
-    point_3 <- point_2 + ab_xy_nml * cell_height
-    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
-
-    temp_polygon <- rbind(
-      point_1,
-      point_2,
-      point_3,
-      point_4,
-      point_1
-    ) %>%
-      list() %>%
-      st_polygon()
-
-    return(temp_polygon)
-  }
-
-  # /*----------------------------------*/
-  #' ## rotation matrix
-  # /*----------------------------------*/
-  rotate_mat_p90 <- matrix(
-    c(
-      cos(pi / 2),
-      sin(pi / 2),
-      -sin(pi / 2),
-      cos(pi / 2)
-    ),
-    nrow = 2
-  )
-
-  # /*----------------------------------*/
-  #' ## Make an extended line
-  # /*----------------------------------*/
-  # make line with starting point and a desired shift
-  make_extended_line <- function(starting_point, step, multiplier, step_v) {
-    extended_line <- rbind(
-      starting_point + step * multiplier,
-      starting_point + step_v * 1000 + step * multiplier
-    ) %>%
-      st_linestring() %>%
-      list() %>%
-      st_as_sfc() %>%
-      st_set_crs(st_crs(field))
-
-    return(extended_line)
-  }
-
-  # /*----------------------------------*/
-  #' ## Check intersections
-  # /*----------------------------------*/
-  # check the intersection of the lines in the direction specified
-  check_intersection <- function(field, step, direction, step_v) {
[…]

### 2022-02-05 Codes/temp_sim/1_simulate.R

@@ -1,154 +1,0 @@
-# /*=================================================*/
-#' # Preparation
-# /*=================================================*/
-library(here)
-library(mgcv)
-library(ggplot2)
-library(grf)
-library(sf)
-library(measurements)
-library(data.table)
-library(tidyverse)
-library(future.apply)
-library(parallel)
-
-
-#--- source functions ---#
-source(here("GitControlled", "Codes", "temp_sim", "0_functions.R"))
-
-# /*----------------------------------*/
-#' ## Datasets
-# /*----------------------------------*/
-# field <- readRDS(here("Shared", "Data", "for_Simulations", "field_padding.rds"))
-
-sp_range=400
-
-# coef_data <- readRDS(here("Shared", "Data", "for_Simulations", paste0('coefficients_sprange_',sp_range,'.rds')))
-
-# === prices ===#
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-
-
-# /*=================================================*/
-#' # Generate dataset 
-# /*=================================================*/
-
-##== Generate Cell-Level Field Data ==##
-raw_data <- lapply(
-	1:1000, function(x) {
-		prepare_raw_data(
-			i = x,
-			field = field,
-			coef_data_m = coef_data[sim == x, ],
-			coef_data_t = coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ],
-			app_error="no"
-		)
-	}
-)
-
-# saveRDS(raw_data, here("Shared", "Data", "for_Simulations", "raw_reg_test_data.rds"))
-reg_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
-test_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
-
-# saveRDS(reg_raw_data, here("Shared", "Data", "for_Simulations", "reg_raw_data.rds"))
-# saveRDS(test_raw_data, here("Shared", "Data", "for_Simulations", "test_raw_data.rds"))
-
-##== Aggregate Cell-Level Field Data to Subplot-Level Field Data ==##
-sim_data <- lapply(
-	1:1000, function(x) {
-		print(paste0("working on ", x, " th iteration."))
-		prepare_data_for_sim(
[…]

### 2022-02-05 GitControlled/Codes/0_0_functions.R

@@ -1,0 +1,1382 @@
+# /*=================================================*/
+#' # Make experiment grids (basic cell, plot, strip)
+# /*=================================================*/
+make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
+
+  # /*=================================================*/
+  #' # Define functions
+  # /*=================================================*/
+  # /*----------------------------------*/
+  #' ## make polygons
+  # /*----------------------------------*/
+  make_polygon <- function(strt_point_new, multiplier, direction) {
+    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
+    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
+    point_3 <- point_2 + ab_xy_nml * cell_height
+    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
+
+    temp_polygon <- rbind(
+      point_1,
+      point_2,
+      point_3,
+      point_4,
+      point_1
+    ) %>%
+      list() %>%
+      st_polygon()
+
+    return(temp_polygon)
+  }
+
+  # /*----------------------------------*/
+  #' ## rotation matrix
+  # /*----------------------------------*/
+  rotate_mat_p90 <- matrix(
+    c(
+      cos(pi / 2),
+      sin(pi / 2),
+      -sin(pi / 2),
+      cos(pi / 2)
+    ),
+    nrow = 2
+  )
+
+  # /*----------------------------------*/
+  #' ## Make an extended line
+  # /*----------------------------------*/
+  # make line with starting point and a desired shift
+  make_extended_line <- function(starting_point, step, multiplier, step_v) {
+    extended_line <- rbind(
+      starting_point + step * multiplier,
+      starting_point + step_v * 1000 + step * multiplier
+    ) %>%
+      st_linestring() %>%
+      list() %>%
+      st_as_sfc() %>%
+      st_set_crs(st_crs(field))
+
+    return(extended_line)
+  }
+
+  # /*----------------------------------*/
+  #' ## Check intersections
+  # /*----------------------------------*/
+  # check the intersection of the lines in the direction specified
+  check_intersection <- function(field, step, direction, step_v) {
[…]

### 2022-02-05 GitControlled/Codes/0_1_functions_gen_analysis_data.R

@@ -1,0 +1,704 @@
+# /*=================================================*/
+#' # Make experiment grids (basic cell, plot, strip)
+# /*=================================================*/
+make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
+
+  # /*=================================================*/
+  #' # Define functions
+  # /*=================================================*/
+  # /*----------------------------------*/
+  #' ## make polygons
+  # /*----------------------------------*/
+  make_polygon <- function(strt_point_new, multiplier, direction) {
+    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
+    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
+    point_3 <- point_2 + ab_xy_nml * cell_height
+    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
+
+    temp_polygon <- rbind(
+      point_1,
+      point_2,
+      point_3,
+      point_4,
+      point_1
+    ) %>%
+      list() %>%
+      st_polygon()
+
+    return(temp_polygon)
+  }
+
+  # /*----------------------------------*/
+  #' ## rotation matrix
+  # /*----------------------------------*/
+  rotate_mat_p90 <- matrix(
+    c(
+      cos(pi / 2),
+      sin(pi / 2),
+      -sin(pi / 2),
+      cos(pi / 2)
+    ),
+    nrow = 2
+  )
+
+  # /*----------------------------------*/
+  #' ## Make an extended line
+  # /*----------------------------------*/
+  # make line with starting point and a desired shift
+  make_extended_line <- function(starting_point, step, multiplier, step_v) {
+    extended_line <- rbind(
+      starting_point + step * multiplier,
+      starting_point + step_v * 1000 + step * multiplier
+    ) %>%
+      st_linestring() %>%
+      list() %>%
+      st_as_sfc() %>%
+      st_set_crs(st_crs(field))
+
+    return(extended_line)
+  }
+
+  # /*----------------------------------*/
+  #' ## Check intersections
+  # /*----------------------------------*/
+  # check the intersection of the lines in the direction specified
[…]

### 2022-02-05 GitControlled/Codes/1_2_generate_coefficients.R

@@ -1,0 +1,255 @@
+# /*=================================================*/
+#' # Preparation
+# /*=================================================*/
+library(here)
+library(tmap)
+library(sp)
+library(sf)
+library(agricolae)
+library(lwgeom)
+library(measurements)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(gstat)
+
+
+
+#--- source functions ---#
+source(here("Codes", "functions.R"))
+
+# /*----------------------------------*/
+#' ## Field data
+# /*----------------------------------*/
+
+field_padding <- readRDS(here("Data", "CNN_Simulations", "field_padding.rds"))
+
+
+# /*=================================================*/
+#' # Generate coefficients
+# /*=================================================*/
+xy <- dplyr::select(field_padding, unique_cell_id) %>%
+  cbind(., st_coordinates(st_centroid(.))) %>%
+  st_drop_geometry() %>%
+  data.table()
+
+gen_coefs <- function(mean, psill, range, coef_name, nsim, xy) {
+  
+  g_N <- gstat(
+    formula = z ~ 1,
+    locations = ~ X + Y,
+    dummy = T,
+    beta = mean,
+    model = vgm(
+      psill = psill,
+      range = range,
+      nugget = 0,
+      model = "Sph" # changed from "Exp", "Sph"
+
+    ),
+    nmax = 50 # number of nearest observations
+  )
+
+  b_sim <- predict(g_N, newdata = xy, nsim = nsim) %>%
+    data.table()%>%
+    melt(id.vars = c("X", "Y")) %>%
+    # data.table() %>%
+    setnames(c("variable", "value"), c("sim", coef_name)) %>%
+    .[, sim := as.numeric(gsub("sim", "", sim))] %>%
+    xy[., on = c("X", "Y")] %>%
+    .[, c("unique_cell_id", "sim", coef_name), with = FALSE]
+
+  return(b_sim)
+}
+
+
+sp_range <- 400
+B <- 1000
+
+#--- ymax ---#
+ymax <- gen_coefs(
+  mean = 12000,
[…]

### 2022-02-05 GitControlled/Codes/2_1_generate_analysis_data.R

@@ -1,0 +1,77 @@
+# /*=================================================*/
+#' # Preparation
+# /*=================================================*/
+library(here)
+library(mgcv)
+library(ggplot2)
+library(grf)
+library(sf)
+library(measurements)
+library(data.table)
+library(tidyverse)
+library(future.apply)
+library(parallel)
+
+
+#--- source functions ---#
+source(here("GitControlled/Codes/0_2_function_gen_analysis_data.R"))
+
+# /*----------------------------------*/
+#' ## Datasets
+# /*----------------------------------*/
+# field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
+# coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds")))
+
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+field <- readRDS("./Shared/Data/for_Simulations/field_padding.rds")
+
+# /*=================================================*/
+#' # Generate raw dataset (cell-level)
+# /*=================================================*/
+
+##== Generate Cell-Level Field Data ==##
+raw_data <- lapply(
+	1:1000, function(x) {
+		prepare_raw_data(
+			i = x,
+			field = field,
+			coef_data_m = coef_data[sim == x, ],
+			coef_data_t = coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ],
+			app_error="no"
+		)
+	}
+)
+
+# saveRDS(raw_data, here("Shared/Data/for_Simulations/raw_reg_test_data.rds"))
+reg_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
+test_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
+
+# saveRDS(reg_raw_data, here("Shared/Data/for_Simulations/reg_raw_data.rds"))
+# saveRDS(test_raw_data, here("Shared/Data/for_Simulations/test_raw_data.rds"))
+
+# /*=================================================*/
+#' # Generate analysis dataset (subplot-level)
+# /*=================================================*/
+reg_raw_data <- readRDS(here("Shared/Data/for_Simulations/reg_raw_data.rds"))
+test_raw_data <- readRDS(here("Shared/Data/for_Simulations/test_raw_data.rds"))
+
[…]

### 2022-02-05 GitControlled/Codes/2_2_main_sim.R

@@ -1,0 +1,76 @@
+# /*===== Run on RGUI =====*/
+
+#/*----------------------------------*/
+#' ## Preparation
+#/*----------------------------------*/
+library(here)
+library(grf)
+library(data.table)
+library(tidyverse)
+library(future.apply)
+library(parallel)
+
+
+#--- source functions ---#
+setwd("~/Dropbox/ResearchProject/ML_VRA")
+source("./GitControlled/Codes/0_3_functions_main_sim.R")
+
+# /*----------------------------------*/
+#' ## Datasets
+# /*----------------------------------*/
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+reg_data_all <- readRDS("./Shared/Data/for_Simulations/reg_data.rds")
+test_data_all <- readRDS("./Shared/Data/for_Simulations/test_data.rds")
+
+
+# x=1
+# train_dt <- reg_data_all[sim==x&padding==1,]
+# test_dt <- test_data_all[sim==x&padding==1,]
+# N_levels <- reg_data_all[sim==x,]$rate%>%unique()%>%sort()
+
+
+
+# /*=================================================*/
+#' # Simulation 
+# /*=================================================*/
+
+# === set up for parallel computations === #
+plan(multicore, workers = availableCores()-2)
+options(future.globals.maxSize= 850*1024^2)
+set.seed(1378)
+
+# --- Number of iterations --- #
+B=1000
+
+# === run simulation === #
+sim_results <- lapply(
+	  1:B, function(x) {
+	    sim_par(
+	      i = x,
+	      reg_data = reg_data_all[sim==x&padding==1,],
+	      test_data = test_data_all[sim==x&padding==1,],
+	      N_levels = reg_data_all[sim==x,]$rate%>%unique()%>%sort()
+	    )
+	  }
+	) %>%
+	rbindlist()%>%
+	rowwise() %>%
+	mutate(var_ls_name = paste0(var_ls, collapse = "_")) %>%
+	data.table()%>%
+	.[, Method := factor(Method, levels = c("RF", "BRF", "CF_base"))] %>%
+	.[, Model := factor(var_ls_name)] %>%
+	.[, Model := case_when(
+    	Model == "alpha_beta_ymax" ~ "aby",
+    	Model == "alpha_beta_ymax_theta_1_theta_2" ~ "abytt",
[…]

### 2022-02-05 GitControlled/Codes/3_1_SimDataAnalysis.R

@@ -1,0 +1,241 @@
+# ==========================================================================
+# Objective:
+#' + Calculate profit-deficits and RMSE of EONR 
+#' + Calculate RMSE of yield predictions for RF, BRF and CNN
+#'      + For CNN results, estimate  EONR in this codes
+#' + Finally, put together those results into one data set
+# ==========================================================================
+
+#/*----------------------------------*/
+#' ## Preparation 
+#/*----------------------------------*/
+library(here)
+library(data.table)
+library(RColorBrewer)
+library(patchwork)
+library(ggplot2)
+library(ggthemes)
+library(viridis)
+library(hrbrthemes)
+library(tidyverse)
+library(ggpubr)
+library(here)
+
+source(here("GitControlled/Codes/0_1_functions_gen_analysis_data.R"))
+source(here("GitControlled/Codes/0_2_functions_main_sim.R"))
+
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+# === Load Training and Testing data sets for evaluation === #
+# reg_data_all <- readRDS("./Shared/Data/for_Simulations/reg_data.rds")
+test_data_all <- readRDS("./Shared/Data/for_Simulations/test_data.rds")
+
+source_dt <- 
+    # bind_rows(reg_data_all, test_data_all, .id = "type") %>%
+    reg_data_all
+    .[padding==1, .(sim, type, unique_cell_id, alpha, beta, ymax)] %>%
+    .[,type := case_when(type == "1" ~ "train", type == "2" ~ "test")] %>%
+    setnames('unique_cell_id', "unique_subplot_id")
+
+# ==========================================================================
+# Results of RF, BRF and CF
+# ==========================================================================
+
+# === All Results === #
+simRes_all <- 
+    readRDS(here("Shared/Results_journal/SimRes_all.rds")) %>%
+    .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
[…]

### 2022-02-05 GitControlled/Codes/3_2_CompTeEstimation.R

@@ -1,0 +1,129 @@
+# /*=================================================*/
+#' # Preparation
+# /*=================================================*/
+library(here)
+library(ggplot2)
+library(grf)
+library(sf)
+library(here)
+library(data.table)
+library(tidyverse)
+library(ggthemes)
+
+
+#/*----------------------------------*/
+#' ## Preparation
+#/*----------------------------------*/
+
+#--- source functions ---#
+source(here("GitControlled/Codes/0_3_functions_main_sim.R"))
+
+
+#--- load the data ---#  
+reg_data_all <- readRDS(here("Shared", "Data", "for_Simulations", "reg_data.rds"))
+test_data_all <- readRDS(here("Shared", "Data", "for_Simulations", "test_agg_data.rds"))
+
+
+#--- pick a single simulation round ---#
+x = 1
+reg_data_sample <- reg_data_all[sim==x & padding==1,]
+test_data_sample <- test_data_all[sim==x & padding==1,]
+N_levels <- reg_data_sample$rate%>%unique()%>%sort()
+
+
+#--- all the cases to be considered ---#
+te_var_ls_variations <- list(
+    c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")
+    )
+
+te_case_data <- expand.grid(
+    var_ls = te_var_ls_variations,
+    Method = c("CF_base", "BRF", "RF")    
+  ) %>%
+  tibble()
+
+
+# /*================================================================*/
+#' # Treatment Effect Calculation (CF-base vs RF vs BRF)
+# /*================================================================*/
+
+# === set up for parallel computations === #
+plan(multicore, workers = availableCores()-2)
+options(future.globals.maxSize= 850*1024^2)
+set.seed(1378)
+
+te_dt_allML <- te_case_data %>%
+	mutate(
+		te_data = future_lapply(
+			seq_len(nrow(.)),
+			function(x) {
+				 get_te_dt(
+            test_data = test_data_sample,
+            var_ls = .$var_ls[[x]],
+            rates_ls = N_levels,
+            Method = .$Method[[x]]
+          )
+        },
+      future.seed = TRUE
+    )
+  )%>%
+  unnest(., cols= "te_data")%>%
+  data.table()%>%
[…]

### 2022-02-05 GitControlled/Codes/MACF/0_0_functions.R

@@ -1,0 +1,1678 @@
+# /*=================================================*/
+#' # Make experiment grids (basic cell, plot, strip)
+# /*=================================================*/
+make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
+
+  # /*=================================================*/
+  #' # Define functions
+  # /*=================================================*/
+  # /*----------------------------------*/
+  #' ## make polygons
+  # /*----------------------------------*/
+  make_polygon <- function(strt_point_new, multiplier, direction) {
+    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
+    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
+    point_3 <- point_2 + ab_xy_nml * cell_height
+    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
+
+    temp_polygon <- rbind(
+      point_1,
+      point_2,
+      point_3,
+      point_4,
+      point_1
+    ) %>%
+      list() %>%
+      st_polygon()
+
+    return(temp_polygon)
+  }
+
+  # /*----------------------------------*/
+  #' ## rotation matrix
+  # /*----------------------------------*/
+  rotate_mat_p90 <- matrix(
+    c(
+      cos(pi / 2),
+      sin(pi / 2),
+      -sin(pi / 2),
+      cos(pi / 2)
+    ),
+    nrow = 2
+  )
+
+  # /*----------------------------------*/
+  #' ## Make an extended line
+  # /*----------------------------------*/
+  # make line with starting point and a desired shift
+  make_extended_line <- function(starting_point, step, multiplier, step_v) {
+    extended_line <- rbind(
+      starting_point + step * multiplier,
+      starting_point + step_v * 1000 + step * multiplier
+    ) %>%
+      st_linestring() %>%
+      list() %>%
+      st_as_sfc() %>%
+      st_set_crs(st_crs(field))
+
+    return(extended_line)
+  }
+
+  # /*----------------------------------*/
+  #' ## Check intersections
+  # /*----------------------------------*/
+  # check the intersection of the lines in the direction specified
+  check_intersection <- function(field, step, direction, step_v) {
[…]

### 2022-02-05 GitControlled/Codes/MACF/1_2_SimDataAnalysis.R

@@ -1,0 +1,92 @@
+# ==========================================================================
+# Preparation
+# ==========================================================================
+library(here)
+library(data.table)
+library(RColorBrewer)
+library(patchwork)
+library(ggplot2)
+library(ggthemes)
+library(viridis)
+library(hrbrthemes)
+library(tidyverse)
+library(ggpubr)
+library(here)
+library(gridExtra)
+library(measurements)
+
+source(here("GitControlled", "Codes_MACF", "0_0_functions.R"))
+
+
+# ==========================================================================
+# Optimal N: RF, BRF, CF-stepwise, CF-base
+# ==========================================================================
+
+####==== source data ====#####
+# simRes_honest_source <- readRDS(here("Shared", "Results", "SimRes_withHonesty_source.rds"))%>%
+#     setnames(c("model","var_case"), c("Method", "Model")) %>%
+#     .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
+#     .[, Method:=factor(Method, levels = c("RF", "BRF", "CF_stepwise", "CF_base"))]
+
+simRes_honest_source <- readRDS(here("Shared", "Results_MACF", "SimRes_MACF_BRF_RF_100.rds"))%>%
+    setnames(c("model","var_case"), c("Method", "Model")) %>%
+    .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
+    .[, Method:=factor(Method, levels = c("RF", "BRF", "MACF"))]
+
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+rmse_general <-function(preds,actual){ 
+  sqrt(mean((actual - preds)^2))
+}
+
+
+# ===================================
+# RMSE and profit loss calculation
+# ===================================
+# (1) calculate profit loss relative to the maximum profit for each simulation
+# (2) get the summary of profit loss for all the methods.
+
+
+pi_loss_dt <- readRDS(here("Shared", "Data", "for_Simulations", "test_agg_data.rds")) %>%
+    .[padding==1,.(sim, unique_cell_id, alpha, beta, ymax)]%>%
+    setnames('unique_cell_id', "unique_subplot_id") %>%
[…]

### 2022-02-05 GitControlled/Codes/PrepareResults_0.R

@@ -1,0 +1,146 @@
+# ==========================================================================
+# Prepare field data set for writing
+# ==========================================================================
+#' Objective:
+#' + create field data sets by cells, subplots, and plots
+#' + create a figure of an example causal tree 
+
+
+library(here)
+library(sf)
+library(data.table)
+library(ggplot2)
+library(ggthemes)
+library(viridis)
+library(tidyverse)
+library(ggpubr)
+library(grf)
+
+source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")
+
+
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+# /*=================================================*/
+#' # Field Data Sets
+# /*=================================================*/
+
+#/*----------------------------------*/
+#' ## (1) cell-level data set 
+#/*----------------------------------*/
+# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
+field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
+
+coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))
+
+x=1
+coef_data_m <- coef_data[sim == x, ]
+coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
+
+
+sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
+	.$reg_raw_data
+
+field_cell_sf <- 
+	left_join(select(field, unique_cell_id), field_cell_dt, by="unique_cell_id")%>%
+    na.omit() %>%
+    mutate(plot_id = ceiling(subplot_id/4)) %>%
+    filter(padding==1)
+   
+saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))
+
+
+#/*----------------------------------*/
+#' ## (2) subplot-level field without padding area 
+#/*----------------------------------*/
+
+field_subplot_sf <- 
+	field_cell_sf %>%
+	group_by(subplot_id, strip_id) %>%
+	summarise(
[…]

### 2022-02-05 GitControlled/Codes/eval_res_CNN.R

@@ -1,0 +1,356 @@
+# /*=================================================*/
+#' # Preparation
+# /*=================================================*/
+
+library(here)
+library(ggplot2)
+library(grf)
+library(sf)
+library(data.table)
+library(tidyverse)
+library(ggthemes)
+library(gridExtra)
+library(parallel)
+
+#--- source functions ---#
+source(here("Gitcontrolled","Codes", "0_0_functions.R")) 
+
+#--- field ---#
+field_cnn <- readRDS(here("Shared", "Data", "for_Simulations", "field_padding.rds"))
+
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+#=== load the source data for training and testing ===#
+training_agg <- readRDS(here("Shared", "Data", "for_Simulations", "reg_data.rds"))%>%
+	setnames("unique_cell_id", "id")%>%
+	.[padding==1, ]
+
+
+testing_v1 <- readRDS(here("Shared", "Data", "for_Simulations", "test_agg_data.rds"))%>%
+	setnames("unique_cell_id", "id")%>%
+	.[padding==1, ]
+
+
+nonpadding_id <- testing_v1$id%>%unique()
+
+
+
+
+##== for comparison: CF, BRF, RF resutls ==##
+# res_forest <- readRDS(here("Shared", "Results", "SimRes_sp_400.rds"))
+
+
+
+#=== load the CNN results Ver1===#
+aby_source_v1 <- read_csv(here("Shared", "Results", "alldata_model1.csv"))%>%
+	data.table()%>%
+	setnames("pred", "yield_hat")%>%
+	.[,.(id, rate, yield_hat, sim)]%>%
+	.[, var_case:= "aby"]
+
+abytt_source_v1 <- read_csv(here("Shared", "Results", "alldata_model2.csv"))%>%
+	data.table()%>%
+	setnames("pred", "yield_hat")%>%
+	.[,.(id, rate, yield_hat, sim)]%>%
+	.[, var_case:= "abytt"]
+
[…]

### 2022-02-05 GitControlled/Codes/eval_res_CNN_ST.R

@@ -1,0 +1,230 @@
+library(here)
+library(ggplot2)
+library(grf)
+library(sf)
+library(data.table)
+library(tidyverse)
+library(ggthemes)
+library(gridExtra)
+library(parallel)
+
+#--- source functions ---#
+source(here("Codes", "cnn_related_functions.R")) 
+
+#--- field ---#
+field_cnn <- readRDS(here("Data", "CNN_Simulations", "cnn_field_padding.rds"))
+
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+
+# /*=================================================*/
+#' # Preparation: Load the Results 
+# /*=================================================*/
+
+#=== load the source data for training and testing ===#
+# training <- readRDS(here("Data", "CNN_Simulations", "reg_raw_data.rds"))
+# testing <- readRDS(here("Data", "CNN_Simulations", "test_raw_data.rds"))
+
+
+# training_cell <- readRDS(here("Data", "CNN_Simulations", "reg_raw_data.rds"))
+
+training_subplot <- readRDS(here("Data", "CNN_Simulations", "reg_data.rds"))%>%
+	setnames("unique_cell_id", "id")%>%
+	.[padding==1, ]
+
+
+testing_subplot <- readRDS(here("Data", "CNN_Simulations", "test_agg_data.rds"))%>%
+	setnames("unique_cell_id", "id")%>%
+	.[padding==1, ]
+
+
+nonpadding_id <- testing_subplot$id%>%unique()
+
+
+
+
+##== for comparison: CF, BRF, RF resutls ==##
+res_forest <- readRDS(here("CNN_Results", "SimRes_sp_400.rds"))
+
+
+
+#=== load the CNN_ST results ===#
+cnn_st_aby_source <- read_csv(here("CNN_Results", "alldata_model1_CNN_ST.csv"))%>%
+	data.table()%>%
+	setnames("pred", "yield_hat")%>%
+	.[,.(id, rate, yield_hat, sim)]%>%
+	.[, var_case:= "aby"]
+
+
+
+
+
+#=== combine CNN resutls into one dataset ===#
[…]

### 2022-02-05 Presentation/DIFM/knitr_rmd.R

@@ -1,3 +1,0 @@
-library(here)
-library(rmarkdown)
-rmarkdown::render(here("GitControlled/Presentation", "presentation_x.rmd"))

### 2022-02-05 Presentation/OFE_Presentation/PrepareResults_presen.R

@@ -1,384 +1,0 @@
-## -----------------------------------------------------------------------------
-library(knitr)
-library(here)
-knitr::opts_chunk$set(
-	cache = FALSE,
-	warning = FALSE,
-	message = FALSE
-	)
-
-opts_knit$set(root.dir=here())
-
-
-## ---- cache = FALSE-----------------------------------------------------------
-# === packages ===#
-library(sf)
-library(data.table)
-library(RColorBrewer)
-library(patchwork)
-library(grf)
-library(magrittr)
-library(ggplot2)
-library(ggthemes)
-library(viridis)
-library(tidyverse)
-library(ggpubr)
-library(flextable)
-library(officer)
-library(modelsummary)
-library(here)
-library(gridExtra)
-library(DiagrammeR)
-library(causalTree)
-library(rpart)
-library(rattle)
-library(webshot2) # remotes::install_github("rstudio/webshot2")
-# library(sparkline)
-# library(htmltools)
-# library(htmlwidgets)
-# library(equatags)
-# library(equatiomatic)
-
-
-
-## ----source, results = "hide", fig.show='hide', cache = FALSE-----------------
-# source(here("Codes", "functions.R"))
-source(here("Codes", "0_0_functions.R"))
-source(here("Codes", "functions_stepwise_vs_base.R"))
-
-
-## ----source-results, message=FALSE, warning=FALSE-----------------------------
-
-# ===================================
-# Forest resutls 
-# ===================================
-
-res_forest_all_honesty <- readRDS(here("Results", "CNN", "SimRes_sp_400.rds"))%>%
-    setnames("model", "Method")%>%
-    .[, var_case:=factor(var_case, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]%>%
-    .[, Method:=factor(Method, levels = c("RF", "BRF", "CF_stepwise", "CF_base"))]%>%
-    .[, Honesty := TRUE]
-
-
-res_forest_all_nohonesty <- readRDS(here("Results", "CNN", "SimRes_sp_400_nohonesty.rds"))%>%
-    setnames("model", "Method")%>%
[…]

### 2022-02-06 Codes/PrepareResults_1.Rmd
Correct the structure of CF_for_VRA folder

--- 2022-02-05 Codes/PrepareResults.Rmd
@@
 # === packages ===#
+# --- data wrangling--- #
 library(sf)
 library(data.table)
+library(tidyverse)
+
+# --- figure making --- #
 library(RColorBrewer)
 library(patchwork)
-library(grf)
-library(magrittr)
 library(ggplot2)
@@
 library(viridis)
-library(tidyverse)
 library(ggpubr)
+library(gridExtra)
+library(DiagrammeR)
+
+# --- table making --- #
 library(flextable)
@@
 library(modelsummary)
-library(here)
-library(gridExtra)
-library(DiagrammeR)
 library(latex2exp)
@@
 
-```{r source, results = "hide", fig.show='hide', cache = FALSE }
+<!-- ```{r source, results = "hide", fig.show='hide', cache = FALSE }
 # setwd(here())
-source("./GitControlled/Codes/0_0_functions.R")
-# source("./GitControlled/Codes/functions_stepwise_vs_base.R")
+# source("./GitControlled/Codes/0_0_functions.R")
+``` -->
+
+```{r setup, warning=FALSE, message=FALSE, cache= FALSE}
+# field <- readRDS("./Shared/Data/for_Simulations/field_padding.rds") %>%
+#     filter(padding==1)%>%
+#     dplyr::select(unique_cell_id)
+
+# === plot-level field data set  === #
+field_plot_sf <- readRDS("./Shared/Results/for_writing/sample_field_plot_sf.rds")
+# === subplot-level field data set  === #
+field_subplot_sf <- readRDS("./Shared/Results/for_writing/sample_field_subplot_sf.rds")
+# === cell-level field data set  === #
+field_cell_sf <- readRDS("./Shared/Results/for_writing/sample_field_cell_sf.rds")
 ```
 
-```{r setup, warning=FALSE, message=FALSE, cache= TRUE}
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-sp_range <- 400
-
-field <- readRDS("./Shared/Data/for_Simulations/field_padding.rds") %>%
-    filter(padding==1)%>%
-    dplyr::select(unique_cell_id)
-
-####==== (1) cell-level dataset ====####
-# coef_data <- readRDS("./Shared/Data/for_Simulations/cnn_coefficients_sprange_400.rds")
-
-# x=1
-# coef_data_m <- coef_data[sim == x, ]
-# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
-
-# sample_dt <- prepare_raw_data(1, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no")
-
-# sample_training_cell <- sample_dt$reg_raw_data
-
-# saveRDS(sample_training_cell, "./Shared/Data/for_writing/sample_reg_raw_data.rds")
-
-field_cell_dt <- readRDS("./Shared/Data/for_writing/sample_reg_raw_data.rds")%>%
-    .[,plot_id := ceiling(subplot_id/4)]%>%
-    .[padding==1,]
-
-field_cell_sf <- left_join(field, field_cell_dt, by="unique_cell_id")%>%
-    na.omit()
-
-# ggplot(field_cell_sf)+
-#     geom_sf(aes(fill=factor(padding)), size=0)
-
-##== area of the field ==##
-# st_area(st_union(field_cell_sf%>%filter(padding==1)))
-
-# nrow(field_cell_sf)
-
-####==== (2) plot-level dataset without padding area ====####
-
-field_plot_sf <- field_cell_sf%>%
-    group_by(plot_id, strip_id, rate)%>%
-    summarise()
-
-# nrow(field_plot_sf)
-# ggplot(field_plot_sf)+geom_sf()
-
-####==== (3) subplot-level field without padding area ====####
-
-# field_subplot_dt <- field_cell_dt[, .(
-#     sim = mean(sim),
-#     yield = mean(yield),
-#     opt_N = mean(opt_N),
-#     rate = mean(rate),
-#     aa_n = mean(aa_n), 
-#     alpha = mean(alpha),
-#     beta = mean(beta),
-#     ymax = mean(ymax),
-#     alpha1 = mean(alpha1),
-#     alpha2 = mean(alpha2),
-#     beta1 = mean(beta1),
-#     beta2 = mean(beta2),
-#     ymax1 = mean(ymax1),
-#     ymax2 = mean(ymax2),
-#     theta_1 = mean(theta_1),
-#     theta_2 = mean(theta_2)
-#   ), by = .(subplot_id, strip_id)]%>%
-#   .[,unique_subplot_id:=paste0(strip_id,"_",subplot_id)]%>%
-#   .[, `:=`(
-#     strip_id = NULL,
-#     subplot_id = NULL
-#   )]
-
-# saveRDS(field_subplot_dt, here("Shared", "Data", "for_writing", "sample_field_subplot_dt.rds"))
-
-field_subplot_dt <- readRDS("Shared/Data/for_writing/sample_field_subplot_dt.rds")
-
-field_subplot_sf <- field_cell_sf%>%
-    group_by(subplot_id, strip_id)%>%
-    summarise()%>%
-    mutate(unique_subplot_id=paste0(strip_id,"_",subplot_id))%>%
-    dplyr::select(unique_subplot_id)%>%
-    left_join(., field_subplot_dt, by="unique_subplot_id")
-
-# nrow(field_subplot_sf)
-# ggplot(field_subplot_sf)+geom_sf()
-
-```
-
-# Sample CT figure
-
-```{r}
-
-# library(causalTree)
-# library(here)
-# library(rpart)
-# library(rattle)
-
-# ===================================
-# Get tree 
-# ===================================
-
-# data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
-#     na.omit() %>%
-#     dplyr::rename(tgtn=NPlan,tgts=SRPlan)
-
-# data_dt <- data.table(data_sf) %>%
-#     setnames(names(.),tolower(names(.)))
-
-# tgts_ls <- data_dt[,tgts] %>% unique() %>% sort
-
-# ctree_data <- copy(data_dt) %>%
-#   .[tgts %in% tgts_ls[1:2],] %>%
-#   .[,treat:=ifelse(tgts==tgts_ls[2],1,0)] %>%
-#   #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
-#   .[,yield:= yield*62.77]
-
-# tree <- causalTree(
-#   yield ~ slope+ecs,
-#   data = ctree_data,
-#   treatment = ctree_data$treat,
-#   split.Rule = "CT",
-#   cv.option = "CT",
-#   split.Honest = T,
-#   cv.Honest = T,
-#   split.Bucket = F,
-#   xval = 5,
-#   cp = 0,
-#   minsize = 20,
-#   propensity = 0.5
-# )
-
-# opcp <- tree$cptable[,1][which.min(tree$cptable[,4])]
-# opfit <- prune(tree, opcp)
-
-# pdf(here("GitControlled/Writing/JournalSubmission/ctree_ex.pdf"))
-# fancyRpartPlot(opfit,sub='')
-# dev.off()
-
-```
+# Variogram Prameter Table
 
@@
     autofit()
-```
-
-# sample MB curve
-
-```{r, dependson = "setup"}
-# gen_yield_MB <- function(ymax, alpha, beta, N) {
-#   yield <- ymax * (1 - exp(alpha + beta * N))
-#   return(yield)
-# }
-
-N_rates <- field_cell_dt[,rate]%>%unique()%>%sort()
-
-N_seq <- 0:300
-
-        # alpha        beta     ymax
-# 1: -0.6605052 -0.01572583 10886.94
-
-dt_sample_MB_curve <- field_cell_dt[1,.(alpha,beta,ymax)]%>%
-    .[rep(1:nrow(.), each = length(N_seq)), ]%>%
-    .[,N:= N_seq]%>%
-    .[,Yield := gen_yield_MB(ymax, alpha, beta, N)]
-
-sample_MB_curve <- ggplot()+
-    geom_point(data=dt_sample_MB_curve, 
-        aes(x=N, y=Yield))+
-    theme_few()+
-    xlab("N(kg/ha)") + ylab("Yield(kg/ha)")
-
 ```
@@
 ```{r, dependson = "setup"}
-
 field_Ndesign <- ggplot() +
-    # geom_sf(data=field_plot_sf, color='blue', size=0.8, fill=NA) +
     geom_sf(data=field_plot_sf,
@@
         inherit.aes = FALSE,
-        # alpha=0.9
         ) +
@@
     theme_void()
-    # theme(legend.position = "bottom",
-    #     legend.title = element_text(size = 0.9))
-
 ```
@@
 
-# yield_dist <- ggplot(field_cell_dt)+
-#     geom_density(aes(x=yield))
-
-##== cell level ==##
+# === cell-level === #
 vis_yield_cell <- ggplot(field_cell_sf) +
@@
 
-##== subplot yield level ==##
+# === subplot-level === #
 vis_yield_subplot <- ggplot(field_subplot_sf) +
@@
     theme_void()
-
 ```
@@
 ```{r, dependson = "setup"}
-opt_N_dist <- ggplot(field_cell_dt)+
-    geom_density(aes(x=opt_N))
 
-##== cell level ==##
+# === cell-level === #
 vis_optN_cell <- ggplot(field_cell_sf) +
@@
     labs(fill = "EONR (kg/ha)")+
-    theme_void()
-
-##== subplot yield level ==##
-vis_optN_subplot <- ggplot(field_subplot_sf) +
-    geom_sf(aes(fill = opt_N), size = 0) +
-    scale_fill_viridis_c()+
-    labs(fill = "Yield Level\n  (kg/ha)")+
     theme_void()
@@
 ####==== ymax map ====####
-ymax_dist <- ggplot(field_cell_dt)+
-    geom_density(aes(x=ymax))
-
 field_ymax <- ggplot(field_cell_sf) +
@@
     theme_void()
-    # theme(legend.title = element_blank())
 
 ####==== alpha map ====####
-alpha_dist <- ggplot(field_cell_dt)+
-    geom_density(aes(x=alpha))
-
 field_alpha <- ggplot(field_cell_sf) +
@@
     scale_fill_viridis_c() +
-    ggtitle(expression("(2) " ~alpha)) +
+    ggtitle(TeX("(2)  $\\alpha$")) +
+    # ggtitle(expression("(2) " ~alpha)) +
     theme_void() +
@@
 ####==== beta map ====####
-beta_dist <- ggplot(field_cell_dt)+
-    geom_density(aes(x=beta))
-
 field_beta <- ggplot(field_cell_sf) +
@@
     scale_fill_viridis_c()+
-    ggtitle(expression("(3) " ~beta)) +
-    # labs(fill = expression(~beta))+
+    ggtitle(TeX("(3)  $\\beta$")) +
     theme_void() +
@@
     scale_fill_viridis_c()+
-    ggtitle(expression("(d) " ~epsilon)) +
+    ggtitle(TeX("(4)  $\\epsilon$")) +
     labs(fill = "kg/ha")+
     theme_void()
-    # theme(legend.title = element_blank())
 
@@
 
-```{r source-results, message=FALSE, warning=FALSE, cache= TRUE}
+```{r source-results, message=FALSE, warning=FALSE, cache= FALSE}
 
@@
 
-## Report R^2 of of Predicted Yield (RF, BRF, CNN)
+## Report RMSE of of Yield Prediction (RF, BRF, CNN)
 
@@
 ```{r}
-# rmse_y_all_v2 <- rmse_y_all %>%
-#     .[,`:=`(
-#         rmse_y_scale = scales::rescale(rmse_y),
-#         rmse_optN_scale = scales::rescale(rmse_optN)
-#         ), by= .(Model, Method)]
-
 fig_y_optN <- rmse_y_all[Method %in% c("RF", "BRF", "CNN")] %>%
@@
 # print(fig_y_optN, preview = "docx")
-# dfabline <- data.frame(
-#     x = 0:3500, y=0:3500)
-
-# figure_te <- readRDS(here("Shared/Data/for_writing/dt_TEcomparison.rds"))%>%
-#     .[, Method:= case_when(
-#         Method=="RF" ~ "RF",
-#         Method=="BRF" ~ "BRF",
-#         Method=="CF_base" ~ "CF-base")] %>%
-#     .[, Method:= factor(Method, levels = c("RF", "BRF", "CF-base"))]%>%
-#     ggplot() +
-#     geom_point(aes(x=true_tau_base, y=tau_base), size=0.5)+
-#     # geom_abline(aes(intercept = 0, slope = 1, color = "1-to-1 line"), show.legend=TRUE) +
-#     geom_line(data=dfabline, aes(x=x, y=y, color="1-to-1 line")) +
-#     scale_colour_manual(labels = "1-to-1 line", values="red") +
-#     facet_grid(Treatment ~ Method) +
-#     guides(
-#         fill = guide_legend(keywidth = 1, keyheight = 1),
-#         linetype = guide_legend(keywidth = 3, keyheight = 1),
-#         colour= guide_legend(keywidth = 3, keyheight = 1),
-#         direction = "horizontal")+
-#     labs(y = "Estimated Treatment Effect")+
-#     labs(x = "True Treatment Effect")+
-#     theme_few() +
-#     theme(
-#         strip.text.x = element_text(size=12,face="bold"),
-#         strip.text.y = element_text(size=12,face="bold"),
-#         legend.title = element_blank(),
-#         legend.text = element_text(size=12, face="bold"),
-#         legend.position = "bottom")
+# dfabline <- data.frame(x = 0:3500, y=0:3500)
 
@@
 
-    # # RF vs BRF
-    # .[,rmse_y_ratio_RF_BRF := rmse_y_RF/rmse_y_BRF]%>%
-    # .[,rmse_optN_ratio_RF_BRF := rmse_optN_RF/rmse_optN_BRF]%>%
-    # # CNN vs RF
-    # .[,rmse_y_ratio_CNN_RF := rmse_y_CNN/rmse_y_RF]%>%
-    # .[,rmse_optN_ratio_CNN_RF := rmse_optN_CNN/rmse_optN_RF]%>%
-    # # CNN vs BRF 
-    # .[,rmse_y_ratio_CNN_BRF := rmse_y_CNN/rmse_y_BRF]%>%
-    # .[,rmse_optN_ratio_CNN_BRF := rmse_optN_CNN/rmse_optN_BRF]
-
-# nrow(.SD[ML_cnst_y_piLoss=="BRF"])
-# prepare_count_tab[ML_cnst_y_piLoss=="RF",] %>% nrow()
-# prepare_count_tab[ML_cnst_y_piLoss=="BRF",] %>% nrow()
-# prepare_count_tab[ML_cnst_y_piLoss=="CNN",] %>% nrow()
-
-# Summary Table 
+# === Summary Table === #
 summary_res_CNN_RF_BRF <- prepare_count_tab%>%
@@
 
-# summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]
-
-#- table creation -#
+# === Table creation === #
 report_summary_res_CNN_RF_BRF <- copy(summary_res_CNN_RF_BRF)%>%
@@
     width(j = c(2,5,8,11), width=0.1)
-
-    # set_table_properties(width = .6, layout = "autofit")
-
-# print(report_summary_res_CNN_RF_BRF, preview = "docx")
-# in terms of RMSE of yield prediction and ", "\U1D70B\U0302", as_sub("loss"), ", respectively.
-
 ```
@@
 
-##== Distribution ==##
+# === Distribution of RMSE of EONR estimates === #
+
 plot_dis_optN <- copy(report_res_subsetML)%>%
@@
 
-##== Summary Table  ==##
+# === Summary Table === #
 
-#- preparation -#
+# --- prepation --- #
 table_optN_prep <- copy(report_res_subsetML)%>%
@@
     .[,.(Model, blank1, rmse_optN_RF, pi_loss_RF,  blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN ,blank4, rmse_optN_CF_base, pi_loss_CF_base)]
-
-# table_optN_prep[Model=="aby", rmse_optN_RF]
-
-# avg_optN <- copy(report_res_subsetML)%>%
-#     .[, .(
-#         Avg_rmse_optN = mean(rmse_optN),
-#         Avg_pi_loss = mean(Mean)
-#         ), by=Method] %>%
-#     .[, `:=`(
-#         Avg_rmse_optN = format(round(Avg_rmse_optN, digits=1), nsmall = 1),
-#         Avg_pi_loss = format(round(Avg_pi_loss, digits=2), nsmall=2)
-#         )]
 
@@
     width(j = c(2,5,8,11), width=0.1) 
-
-    # print(report_table_optN, preview = "docx")
-    # autofit() 
-    # width(j = c(2,5,8,11), width=0.5)
-    # width(j = c(2,5,8,11), width=0.5)
-
-# print(report_table_optN, preview = "docx")
-
-# typology <- data.frame(
-#   col_keys = names(table_optN_prep),
-#   what = c(" ", " ", "RF", "RF", " ", "BRF", "BRF", " ", "CNN", "CNN", " ", "CF-base", "CF-base"),
-#   measure = c(" ", " ", "RMSE", "pi_loss", " ", "RMSE", "pi_loss", " ", "RMSE", "pi_loss", " ", "RMSE", "pi_loss"),
-#   stringsAsFactors = FALSE )
-
-# copy(table_optN_prep)%>%
-#     mutate(
-#     across(
-#       everything(),
-#       as.character
-#         )
-#     )%>%
-#     add_row(.after = 4) %>%
-#     flextable(.) %>%
-#     border_remove() %>%
-#     add_body(
-#         Model="Avg.", 
-#         blank1 = NA, rmse_optN_RF = avg_optN[Method=="RF",Avg_rmse_optN], pi_loss_RF = avg_optN[Method=="RF",Avg_pi_loss],
-#         blank2 = NA, rmse_optN_BRF = avg_optN[Method=="BRF",Avg_rmse_optN], pi_loss_BRF = avg_optN[Method=="BRF",Avg_pi_loss],
-#         blank3 = NA, rmse_optN_CNN = avg_optN[Method=="CNN",Avg_rmse_optN], pi_loss_CNN = avg_optN[Method=="CNN",Avg_pi_loss],
-#         blank4 = NA, rmse_optN_CF_base = avg_optN[Method=="CF_base",Avg_rmse_optN], pi_loss_CF_base = avg_optN[Method=="CF_base",Avg_pi_loss],
-#         top = FALSE
-#         )%>%
-#     # delete_part(part = "header") %>%
-#     set_header_df(mapping = typology, key = "col_keys") %>%
-#     compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub("loss"))) %>%
-#     merge_h(part = "header") %>%
-#     hline_bottom(part="all") %>%
-#     hline_top(part="header") %>%
-#     align(align = "center", part = "all")%>%
-#     align(j=1,  align = "left", part = "all")%>%
-#     autofit() %>%
-#     width(j = c(2,5,8,11), width=0.5)
-
 ```
@@
 ```{r}
-# piLoss_summary <- report_res_subsetML[,select(.SD, Method, Model, Min.:Max., cumulative_pi_loss)]%>%
-#     .[, lapply(.SD, mean), by=.(Method, Model)] %>%
-#     .[, lapply(.SD,  function(x) as.numeric(format(mean(x), digits=3))), by=.(Method, Model)] %>%
-#     flextable()
-
 piLoss_density <- 
@@
 
-figure_te <- readRDS("./Shared/Data/for_writing/dt_TEcomparison.rds")%>%
+figure_te <- readRDS("./Shared/Results/for_writing/dt_TEcomparison.rds")%>%
     .[, Method:= case_when(
@@
 ```
-
-# Examination of Treatment Effects (CF-base vs CF-stepwise)
-
-```{r}
-# ======================================================================
-# Examination of te esimation (CF-stepwise vs CF-base)
-# ======================================================================
-
-# te_res <- readRDS(here("Shared/Results/res_eval_tre_effects.rds"))%>%
-#     .[,.(method, N_index, R_squared)]%>%
-#     .[, N_index := case_when(
-#     N_index == "1-2" ~ "(N1,N2)",
-#     N_index == "2-3" ~ "(N2,N3)",
-#     N_index == "3-4" ~ "(N3,N4)",
-#     N_index == "4-5" ~ "(N4,N5)",
-#     N_index == "1-3" ~ "(N1,N3)",
-#     N_index == "1-4" ~ "(N1,N4)",
-#     N_index == "1-5" ~ "(N1,N5)"
-#   )]%>%
-#     .[,sim:=rep(1:1000, each=8)]
-
-##== Treatment Effects Summary Table ==##
-
-# te_res_summary <- te_res[,.(R_squared=mean(R_squared)), by=c("method", "N_index")]%>%
-#     .[, R_squared:= round(R_squared,3)]%>%
-#     flextable(.)%>%
-#     set_header_labels(
-#     values = list(
-#         method="Method",
-#         N_index ="N Rates Combinations",
-#         R_squared = "R-squared"
-#     ))%>%
-#     compose(i = 1, j = 2, part = "header", value = as_paragraph("(N", as_sup("con"), ", N", as_sup("tre"), ")"))%>%
-#     compose(i = 1, j = 3, part = "header", value = as_paragraph("R",as_sup("2")))%>%
-#     align(align = "center", part = "all")%>%
-#     align(j=1,  align = "left", part = "all")%>%
-#     # align(align = "center", part = "header")%>%
-#     # align_text_col(align = "center", header = TRUE, footer = TRUE)%>%
-#     autofit()
-
-##== Graph ==##
-#== tre calculation ==#
-
-# reg_data_all <- readRDS(here("Data/for_Simulations/reg_data.rds"))
-# test_agg_data_all <- readRDS(here("Data/for_Simulations/test_agg_data.rds"))
-
-# # estimate_tre() is defined in "functions_stepwise_vs_base.R"
-# sim_ex <- estimate_tre(x=32, reg_data_all=reg_data_all, test_data_all=test_agg_data_all)
-
-# sim_ex$r2
-
-# saveRDS(sim_ex, here("Shared", "Data","for_writing","tre_demo.rds"))
-
-# sim_output <- readRDS(here("Shared","Data","for_writing","tre_demo.rds"))
-
-# # r2 <-sim_output$r2
-# eval <- sim_output$output
-
-# cf_step <- eval[Method=="CF-stepwise"]%>%
-#   ggplot()+
-#   geom_density(aes(x=value, fill=factor(variable)),alpha=0.8)+
-#   facet_wrap(~N_index, ncol = 2)+
-#   theme_few()+
-#   theme_few()+
-#       theme(
-#       legend.position="bottom",
-#       plot.title = element_text(hjust = 0.5),
-#       panel.background = element_rect(fill = "white"),
-#         axis.ticks = element_blank(),
-#         legend.title = element_blank(),
-#         strip.text.x = element_text(size=12,face="bold"),
-#         legend.text = element_text(size=12, face="bold"),
-#         )+
-#         labs(
-#         x = "Treatment Effects(kg/ha)",
-#         colour = "Cylinders",
-#         shape = "Transmission"
-#       )
-
-# cf_base <- eval[Method=="CF-base"]%>%
-#   ggplot()+
-#   geom_density(aes(x=value, fill=factor(variable)),alpha=0.8)+
-#   facet_wrap(~N_index, ncol = 2)+
-#   theme_few()+
-#   theme_few()+
-#       theme(
-#       legend.position="bottom",
-#       plot.title = element_text(hjust = 0.5),
-#       panel.background = element_rect(fill = "white"),
-#         axis.ticks = element_blank(),
-#         legend.title = element_blank(),
-#         strip.text.x = element_text(size=12,face="bold"),
-#         legend.text = element_text(size=12, face="bold"),
-#         )+
-#         labs(
-#         x = "Treatment effects(kg/ha)",
-#         colour = "Cylinders",
-#         shape = "Transmission"
-#       )
-```
-
-# Appendix: CF-base vs CF-stepwise
-
-```{r, dependson = "source-results"}
-# ==========================================================================
-# RMSE
-# ==========================================================================
-##== Distribution ==##
-plot_dis_CF_optN <- copy(report_res_allML)%>%
-    .[Method %in% c("CF_stepwise", "CF_base"), ]%>%
-    .[, Method := case_when(
-    Method == "CF_stepwise" ~ "CF-stepwise",
-    Method == "CF_base" ~ "CF-base"
-    )]%>%
-    .[, Model := case_when(
-    Model == "aby" ~ "Scenario: aby",
-    Model == "abytt" ~ "Scenario: abytt",
-    Model == "aabbyy" ~ "Scenario: aabbyy",
-    Model == "aabbyytt" ~ "Scenario: aabbyytt"
-    )]%>%
-    .[, Method:=factor(Method, levels = c("CF-stepwise", "CF-base"))] %>%
-    .[, Model:=factor(Model, 
-        levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt"))] %>%
-    ggplot()+
-    geom_density(aes(x=rmse_optN, fill=Method), alpha=0.7)+
-    # scale_fill_viridis_d()+
-    facet_wrap(~Model, ncol = 1)+
-    labs(x = "RMSE")+
-    theme_few()+
-    theme(
-        strip.text.x = element_text(size=12,face="bold"),
-        legend.title = element_text(size=12,face="bold"),
-        legend.text = element_text(size=12, face="bold"),
-        legend.position = "bottom")
-
-##== barplot ==##
-CF_optN_boxplot <- copy(report_res_allML)%>%
-    .[Method %in% c("CF_stepwise", "CF_base"), ]%>%
-    .[, Method := case_when(
-    # Method == "CF_stepwise" ~ "CF-stepwise",
-    Method == "CF_stepwise" ~ "CF-stepwise",
-    Method == "CF_base" ~ "CF-base"
-    )]%>%
-    .[, Method:=factor(Method, levels = c("CF-stepwise", "CF-base"))]%>%
-    ggplot() + 
-    geom_boxplot(aes(x=Method, y=rmse_optN, fill=Method), alpha=0.5)+
-    geom_jitter(aes(x=Method, y=rmse_optN, fill=Method), size=0.3, alpha=0.9) +
-    # scale_fill_viridis(discrete = TRUE, alpha=0.6) +
-    scale_fill_viridis_d()+
-    labs(y = " RMSE")+
-    facet_grid(~Model)+
-    theme_few()+
-    theme(
-        strip.text.x = element_text(size=12,face="bold"),
-        legend.title = element_text(size=12,face="bold"),
-        legend.text = element_text(size=12, face="bold"),
-        legend.position = "bottom")
-
-##== Summary Table  ==##
-
-#- preparation -#
-table_CF_optN_prep <- copy(report_res_allML)%>%
-    .[, .(
-        rmse_optN = mean(rmse_optN),
-        pi_loss = mean(Mean)
-        ), by=.(Method, Model)]%>%
-    .[,`:=`(
-        rmse_optN = format(round(rmse_optN,1), nsmall=1),
-        pi_loss = format(round(pi_loss,2), nsmall=2)
-        )] %>%
-    dcast(Model~Method, value.var = c("rmse_optN", "pi_loss")) %>%
-    .[,`:=`(
-         blank1 = NA, blank2 = NA
-        )] %>%
-    .[,.(Model, blank1, rmse_optN_CF_base, pi_loss_CF_base, blank2, rmse_optN_CF_stepwise, pi_loss_CF_stepwise)]
-
-# avg_CF_optN <- copy(report_res_allML)%>%
-#     .[, .(
-#         Avg_rmse_optN = mean(rmse_optN),
-#         Avg_pi_loss = mean(Mean)
-#         ), by=Method] %>%
-#     .[, `:=`(
-#         Avg_rmse_optN = format(round(Avg_rmse_optN, digits=1), nsmall = 1),
-#         Avg_pi_loss = format(round(Avg_pi_loss, digits=2), nsmall=2)
-#         )]
-
-#- table creation -#
-report_table_CF_optN <- copy(table_CF_optN_prep)%>%
-    mutate(
-    across(
-      everything(),
-      as.character
-        )
-    )%>%
-    # add_row(.after = 4) %>%
-    flextable(.) %>%
-    border_remove() %>%
-    delete_part(part = "header") %>%
-    add_header(
-        Model="Model", 
-        blank1 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
-        blank2 = "", rmse_optN_CF_stepwise = "CF-stepwise", pi_loss_CF_stepwise = "CF-stepwise",
-        top = TRUE) %>%
-    merge_h(part = "header") %>%
-    hline_bottom(j=c(3:4, 6:7), part = "header") %>%
-    add_header(
-        Model="", 
-        blank1 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
-        blank2 = "", rmse_optN_CF_stepwise = "RMSE", pi_loss_CF_stepwise = "pi_loss",
-        top = FALSE) %>%
-    compose(i = 2, j = c(4, 7), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub("loss"))) %>%
-    hline_bottom(part="all") %>%
-    hline_top(part="header") %>%
-    align(align = "center", part = "all")%>%
-    align(j=1,  align = "left", part = "all")%>%
-    # set_table_properties(width = .5, layout = "autofit")
-    autofit() %>%
-    width(j = c(2,5), width=0.3) %>%
-    fix_border_issues()
-
-# ==========================================================================
-# profit-loss
-# ==========================================================================
-
-##== Distribution ==##
-piLoss_density_CF <- copy(report_res_allML)%>%
-    .[Method %in% c("CF_stepwise", "CF_base"), ]%>%
-    .[, Method := case_when(
-    # Method == "CF_stepwise" ~ "CF-stepwise",
-    Method == "CF_stepwise" ~ "CF-stepwise",
-    Method == "CF_base" ~ "CF-base"
-    )]%>%
-    .[, Model := case_when(
-    Model == "aby" ~ "Scenario: aby",
-    Model == "abytt" ~ "Scenario: abytt",
-    Model == "aabbyy" ~ "Scenario: aabbyy",
-    Model == "aabbyytt" ~ "Scenario: aabbyytt"
-    )]%>%
-    .[, Method:=factor(Method, levels = c("CF-stepwise", "CF-base"))]%>%
-    .[, Model:=factor(Model, 
-        levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt"))] %>%
-    ggplot() + 
-    geom_density(aes(x=Mean, fill=Method), alpha=0.5)+
-    # scale_fill_viridis(discrete = TRUE, alpha=0.5) +
-    # scale_fill_viridis_d()+
-    labs(x = expression(hat(pi)["loss"]))+
-    facet_wrap(~Model, ncol=1) +
-    theme_few()+
-    theme(
-        strip.text.x = element_text(size=12,face="bold"),
-        legend.title = element_text(size=12,face="bold"),
-        legend.text = element_text(size=12, face="bold"),
-        legend.position = "bottom")
-
-##== barplot ==##
-CF_piLoss_boxplot <- copy(report_res_allML)%>%
-    .[Method %in% c("CF_stepwise", "CF_base"), ]%>%
-    .[, Method := case_when(
-    # Method == "CF_stepwise" ~ "CF-stepwise",
-    Method == "CF_stepwise" ~ "CF-stepwise",
-    Method == "CF_base" ~ "CF-base"
-    )]%>%
-    .[, Method:=factor(Method, levels = c("CF-stepwise", "CF-base"))]%>%
-    ggplot() + 
-    geom_boxplot(aes(x=Method, y=Mean, fill=Method), alpha=0.5)+
-    # geom_jitter(aes(x=Method, y=Mean, fill=Method), size=0.3, alpha=0.9) +
-    # scale_fill_viridis(discrete = TRUE, alpha=0.6) +
-    scale_fill_viridis_d()+
-    labs(y = " Mean Profit-loss")+
-    facet_grid(~Model)+
-    theme_few()+
-    theme(
-        strip.text.x = element_text(size=12,face="bold"),
-        legend.title = element_text(size=12,face="bold"),
-        legend.text = element_text(size=12, face="bold"),
-        legend.position = "bottom")
-
-```

### 2022-02-06 Presentation/DIFM/presentation_x.rmd
Correct the structure of CF_for_VRA folder

---
title: "Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation"
author: "Taro Mieno, University of Nebraska Lincoln"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
bibliography: ML_VRA.bib
csl: computers-and-electronics-in-agriculture.csl
---
class: middle

```{r, child = 'setup.Rmd', cache = FALSE}
```

```{r, include = F, cache = FALSE}
#--- load packages ---#
suppressMessages(library(data.table))
suppressMessages(library(tidyverse))
suppressMessages(library(DT))
suppressMessages(library(sf))
suppressMessages(library(here))
suppressMessages(library(flextable))
suppressMessages(library(printr))
suppressMessages(library(tidycensus))
suppressMessages(library(tmap))
suppressMessages(library(RefManageR))

here::i_am("GitControlled/Presentation/ML_VRA.bib")

```

```{r tmap-layout, cache = FALSE}
tm_layout_to_add <-
  tm_layout(
    legend.outside = "TRUE",
    frame = FALSE,
    legend.title.size = 2,
    legend.text.size = 1.5
  )
```

```{r setup, include=FALSE, cache = FALSE}
options(htmltools.dir.version = FALSE)
BibOptions(
  check.entries = FALSE,
  bib.style = "authoryear",
  style = "markdown",
  dashed = TRUE,
  max.names = 1,
  longnamesfirst = FALSE
)
file.name <- here("GitControlled/Presentation", "ML_VRA.bib")
bib <- ReadBib(file.name)
```

```{r figure_setup, cache = F}
theme_update(
  axis.title.x =
    element_text(
      size = 9, angle = 0, hjust = .5, vjust = -0.3, face = "plain"
    ),
  axis.title.y =
    element_text(
      size = 9, angle = 90, hjust = .5, vjust = .9, face = "plain"
    ),
  axis.text.x =
    element_text(
      size = 7, angle = 0, hjust = .5, vjust = 1.5, face = "plain"
    ),
  axis.text.y =
    element_text(
      size = 7, angle = 0, hjust = 1, vjust = 0, face = "plain"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 7, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.title =
    element_text(
      size = 7, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 7),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 9),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

```{r analyses, include = FALSE, cache = TRUE}
# /*=================================================*/
#' # Preparation
# /*=================================================*/
# This is where you prepare data sets and results

# /*----------------------------------*/
#' ## Create figures and tablesb
# /*----------------------------------*/
# --- Convert an Rmd file into a pure R file using purl() ---#
knitr::purl(here("GitControlled/Codes/PrepareResults.Rmd"), output = here("GitControlled/Codes/PrepareResults.R"))

# --- Read the simulation results and prepare figures and tables ---#
source(here("GitControlled/Codes/PrepareResults.R"))
```

# Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

+ Shunkei Kakimoto, University of Nebraska Lincoln
+ Taro Mieno, University of Nebraska Lincoln 
+ Takashi Tanaka, Gifu University, Japan
+ David S. Bullock, University of Illinois

---
class: middle

# Site-specific Economically Optimal Input Rates

+ On-farm Precision Experimentation (OFPE)
  - more spatially granular data of yield, inputs of interest (e.g., fertilizer, seed)
  - other field/soil characteristics
+ Steps:
  1. Run input experiments
  2. Collect data
  3. <span style = "color: red;"> Estimate yield response function based on the data </span>  
  4. Estimate the economically optimal site-specific input rates

---
class: middle

# Yield Response and EOIR Estimation

+ Application of various machine learning methods
  - Random Forest `r Citep(bib, c("krause2020random", "MARQUESRAMOS2020105791"))`
  - Convolutional Neural Network `r Citep(bib, "barbosa2020modeling")`
+ Many studies
  + stop at predicting yields without identifying EOIR
  + use information that is not available to farmers at the time of their management decision making

---
class: middle

# Yield and EOIR prediction

Consider this stylized conceptual model:

$$Yield = f(I, c, x) + g(c, x)$$

+ <span style = "color: red;"> $f(I, c, x)$ </span>: $0.4$ at maximum
+ $g(c, x)$: $0.6$ at maximum

```{r }
data.table(
  model = rep(c("model 1", "model 2", "model 3"), each = 2),
  component = rep(c("f", "g"), 3),
  explained = c(0.3, 0.5, 0.3, 0.6, 0.4, 0.4),
  `R-squared` = c(0.8, 0.8, 0.9, 0.9, 0.8, 0.8)
) %>%
  flextable() %>%
  color(i = c(3, 4), j = 1, color = "blue") %>%
  color(i = c(5, 6), j = 1, color = "red") %>%
  merge_v(j = c(1, 4)) %>%
  hline(i = c(2, 4, 6)) %>%
  fix_border_issues() %>%
  align(j = c(2, 3, 4), align = "center") %>%
  autofit()

```

---
class: middle

.content-box-red[**Key**]: You want to estimate accurately the part that matters for EOIR suggestion, not overall.

---
class: middle

# Predicting Yield <span style = "color: red;"> Level </span> is Sufficient, but not Necessary

+ Consider a very simple profit maximization problem

$$\max_{I} \quad pf(I, \mathbf{c}) - wI$$

+ $p$: crop price
+ $f(\cdot)$: yield function
+ $I$: input
+ $c$: collection of other variables
+ $w$: input price

--

.content-box-red[**First order condition**]:

$$\frac{\partial f(I^{*}(p,w,\mathbf{c}), \mathbf{c})}{\partial I} \equiv \frac{w}{p}$$

What you need is the impact of input on yield (difference in yield moving from one rate to another)

---
class: middle

# Causal Forest and other traditional ML methods

+ Traditional ML methods (e.g., Random Forest, Boosted Regression Forest, CNN) 
  - is designed to estimate the <span style = "color: red;"> level </span> of the dependent variable (yield) well
  - once the yield model is trained, you can estimate the impact of a treatment (just plug in two different rates and see the difference in their predicted yield values)

+ Causal Forest (a causal machine learning method)
  - is designed to estimate heterogeneous treatment effects directly without predicting yield levels

---
class: middle

# Causal Forest: Illustration (Corn, Seed Rate Experiment)

.left4[
<br>
+ A causal forest is an ensemble of causal trees
+ Treatment effect is calculated at each leaf

<br>

.content-box-blue[Experiment:]

+ **Control**: $27,000$ seeds/acre
+ **Treated**: $31,000$ seeds/acre

.content-box-blue[Characteristics:]
+ Slope (`slope`)
+ Electrical Conductivity (`ecs`) 
]

.right6[
```{r c-tree, echo = F, out.width = "100%"}
include_graphics(here("GitControlled/Presentation", "ctree.png"))
```
]

---
class: middle

# Research Question

+ Does Causal Forest (CF) outperform traditional ML approaches in estimating site-specific EOIR and result in higher economic profits?

+ Can you trust yield prediction accuracy as the criteria to select a model when your ultimate goal is to find the model that produces the highest economic profit?

---
class: middle

# Method

+ Monte Carlo simulation
  - hypothetical field, on which OFPEs are run
  - site-specific yield response functions are known (to researchers)
  - site-specific economically optimal input rates are known for a given combination of crop and input prices

<span style = "color: red;"> Important Note </span>: Using real-world data, you are never ever able to test which model performs the best in terms of the economic performance of site-specific input recommendations because you do not observe true yield response functions

---
class: middle

# Yield Response Functions

Yield response function is assumed to follow Mitscherlich-Baule functional form:

$$f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) N)) + \varepsilon$$

+ $c$: a collection of site-specific characteristics
+ $\varepsilon$: error

--

Researchers observe and use yield, N, and $c$ to train models.

---
class: middle

# Data Generation: Nitrogen Rate (Trial Design)
.left4[
<br>
<br>
Each plot is assigned a single N rate according to the fixed trial design
]

.right6[
```{r fig-nExp, out.width="100%", cache = TRUE}
field_Ndesign
```
]

---
class: middle

# Data Generation: Characteristics and Error

.left4[
<br>
<br>
Characteristics $(c)$ and error term are generated so that they are spatially correlated 
]

.right6[
```{r fig-parameters, out.width="100%", cache = TRUE}
# field_alpha + field_beta + field_ymax
grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol = 2, nrow = 2)
```
]

---
class: middle

# Data Generation: Yield

.left4[
<br>
<br>
Yield is generated based on N, $c$, and error term
]

.right6[
```{r field-yield-cell, out.width="100%", cache = TRUE}
vis_yield_cell
```
]

---
class: middle

# Modeling Scenarios

Researchers observe all the variables (characteristics) that govern site-specific yield response functions, but do not know the functional form.

$$f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) N)) + \varepsilon$$

+ **aby**: $\alpha$, $\beta$, ymax 
+ **abytt**: $\alpha$, $\beta$, ymax, $\theta_1$, $\theta_2$ $(\theta$s are irrelevant variables)
+ **aabbyy**: 
  - $\alpha_1$, $\alpha_2$ $(\alpha = \alpha_1 + \alpha_2)$ 
  - $\beta_1$, $\beta_2$ $(\beta = \beta_1 + \beta_2)$ 
  - $ymax_1$, $ymax_2$ $(ymax = ymax_1 + ymax_2)$
+ **aabbyytt**: $\alpha_1$, $\alpha_2$, $\beta_1$, $\beta_2$, $ymax_1$, $ymax_2$, $\theta_1$, $\theta_2$

---
class: middle

# Estimation Methods

+ Random Forest
+ Boosted Regression Forest
+ Convolutional Neural Network (follows the architecture of `r Citet(bib, "barbosa2020modeling")`)
+ Causal Forest (CF)

---
class: middle

# Results: Economic Performance

```{r  echo = F, out.width = "80%"}
include_graphics(here("GitControlled/Presentation", "results_table.png"))
```

---
class: middle

# Treatment Effect Estimation Accuracy: subplot-level

```{r plot-tre, fig.dim = c(6, 4), cache = TRUE}
figure_te
```

---
class: middle

# Yield Prediction vs Profitability Performance

```{r  echo = F, out.width = "80%"}
include_graphics(here("GitControlled/Presentation", "yield_profit.png"))
```

---
class: middle

# Conclusions

## Economic Performance
+ Random Forest should not be used. It is simply worse than BRF and CF and vulnerable to irrelevant variables.
+ CF outperforms RF, BRF, CNN
+ **Caveats**:
  * CNN used a particular architecture suggested by `r Citep(bib, "barbosa2020modeling")`, and other architectures may perform better
  * If the experimental settings differ (yield response functions, trial design, etx), the results can of course be different (I already found a case where BRF performs better than CF just yesterday)

--

## Yield Prediction vs EONR Prediction
+ Yield prediction accuracy has very little to do with EONR prediction accuracy
+ Picking a model based on yield prediction accuracy does not necessarily lead you to a model that is good at predicting EONR

---
class: middle

# Extensions

+ Collaborate across the teams to see which model works the best under what condition?
+ Can we identify factors that lets us know what approach to use with some confidence?

### 2022-02-06 Presentation/OFE_Presentation/presen_script.rmd
Correct the structure of CF_for_VRA folder

---
title: "Machine Learning Methods for Site-specific Input Management"
author: Shunkei Kakimto
output: word_document
bibliography: MSthesis.bib
---

```{r}
library(knitr)
library(here)
knitr::opts_chunk$set(
	cache = FALSE,
	warning = FALSE,
	message = FALSE
	)

# opts_knit$set(root.dir=here())
```

## Introduction(2 min)

### Slide 1 (11sec)
Hello, my name is Shunkei Kakimoto. I'm a graduate student in Agricultural Economics at the university of Nebraska-Lincoln. Today, I'll be talking about a new machine learning method for site-specific input recommendation.

### Background (15sec)
The application of Machine Learning methods for site-specific economically optimal input rates, called EOIR ,have been getting more attention in recent years.

For example, @barbosa2020modeling applied Convolutional Neural Network methods and @krause2020random used Random Forest-based approaches.

### Research Gap (30sec)
The conventional ML methods focus on the accuracy of yield prediction, and the past studies relied on the models’ predictive power of yield for validity of their models.

However, EOIR recommendation should be based on the causal identification of input on yield, rather than yield prediction. Having good yield prediction capability does **not** necessarily mean that it is also capable of estimating EOIR well because they are **two** distinct objectives.

### New Trend of Causal Machine Learning Application (28sec)
The lack of causal interpretation from existing popular machine learning methods has been increasingly recognized in many scientific fields, and this has led to an emerging branch of machine learning methods, called causal machine learning.
Causal machine learning methods focus on identifying causal impacts of an event.

In this study, we use causal forest which was developed for estimating heterogeneous causal impacts of a treatment based on observed characteristics.

### Research Questions (35sec)

Through our study, we propose two causal forest-based methods and we named them CF-stepwise and CF-base. Using those methods, we address the following two research questions.

The first question is that  In terms of estimating EOIR, how do causal forest-based methods compare to other prediction-oriented ML methods?

The second question is whether the predictive ability of yield is a good indicator of the performance of EOIR estimation?

##  Methods (30 sec)
To address those questions, we conducted one thousand rounds of Monte Carlo simulations under four different production scenarios, and compared the performance in estimating economically optimal nitrogen rates of causal forest -based methods to other methods.

For prediction-oriented ML methods, we investigated their yield prediction performances in contrast with their EONR estimation performances.

We use R-squared as an evaluation metric.

## Results (1:10min)
### Key Results: EONR estimation (25 sec)

Table 1 shows the mean R-squared of the estimated EONR for each ML method and modeling scenario over the 1000 simulations. CF-base showed the best accuracy. Meanwhile, the performance of CF-stepwise did not change as much as other ML methods. Part of the reason why is because the predicted treatment effects from CF-stepwise are more susceptible to prediction errors than CF-base.

### Key Results: EONR estimation and Yield Prediction

To examine the consistency between yield prediction performance and EONR estimation performance of an ML method, we counted the number of simulation rounds where a single ML method consistently showed the highest R-squared in both yield prediction and EONR estimation. 
Table 2 shows the result. For example, in model 1, RF attained the highest R-squared for yield prediction 363 times, and out of those simulation rounds RF attained the highest R-squared for EONR estimation 57 times. 
If the model with the highest yield predictive performance is likely to result in the highest EONR estimation performances as well, the two numbers should be close.
However, overall there is no such a consistent relationship between these numbers.

### Key Findings (20 sec)
In conclusion, through this study, we found that our proposed CF-base method is capable of estimating site-specific EONR more accurately than other prediction-oriented ML methods,  and the ability of predicting yield does not necessarily translate to good performance in estimating EONR.

Thank you for your time.

### 2022-02-06 Presentation/OFE_Presentation/presen_slides.rmd
Correct the structure of CF_for_VRA folder

---
title: Machine Learning Methods for Site-specific Input Management
author:
  - Shunkei Kakimoto$^1$, Taro Mieno$^1$ and Takashi S. T. Tanaka$^2$
institute: $^1$Agricultural Economics, University of Nebraska Lincoln  $^2$Applied Biological Sciences, Gifu University
date: "September 1st 2021"
fontsize: 12pt
mathspec: true # for metropolis theme
aspectratio: 169 # 16:9
#classoption: handout
output:
 beamer_presentation:
   theme: "Madrid" 
   # https://deic-web.uab.cat/~iblanes/beamer_gallery/index_by_theme.html
   #theme: "metropolis" # special
   colortheme: "whale"
   # https://deic-web.uab.cat/~iblanes/beamer_gallery/index_by_color.html
   fonttheme: "professionalfonts"
   # https://deic-web.uab.cat/~iblanes/beamer_gallery/index_by_font.html
   latex_engine: xelatex # for metropolis theme
   toc: false
   number_sections: false
   slide_level: 1
   keep_tex: true
    # includes:
    #   in_header: preamble.tex
# compact-title: ture # to remove markdown generated title frame
header-includes:
  - \usepackage{fancyvrb}
  - \usepackage{graphicx}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  # - \setbeamertemplate{page number in head/foot}[]{}
  # - \AtBeginSection{}
bibliography: MSthesis.bib
---

```{r setup, include=FALSE}
library(here)
library(knitr)

# opts_knit$set(root.dir = here())

opts_chunk$set(
  fig.align = "center", 
  fig.retina = 5,
  warning = F, 
  message = F,
  cache = FALSE, # <-- T
  cache.lazy = FALSE,
  echo = F
  )
```

```{r, cache = TRUE}
# === packages ===#
library(sf)
library(data.table)
library(grf)
library(RColorBrewer)
library(patchwork)
library(plotly)
library(magrittr)
library(ggplot2)
library(viridis)
library(tmap)
library(tidyverse)
library(ggthemes)
library(mgcv)
library(ggpubr)
library(flextable)
library(officer)
library(modelsummary)
library(raster)
library(bookdown)
```

# Background
+ The application of Machine Learning(ML) methods for site-specific economically optimal input rates (EOIR) (e.g., seed, fertilizer) have been getting more attention in recent years
\newline
  + @barbosa2020modeling applied Convolutional Neural Network
  + @krause2020random used Random Forest-based approaches
  + @Gardner21, @Wang2021, @coulibali2020, etc.

---

# Research Gap

+ The conventional ML methods focus on predicting yield well rather than causal identification of input on yield
+ The past studies have used predictive ability of yield for validity of their models.
\newline

## note
+ EOIR estimation should be based on the change in yields associated with the change in input levels *ceteris paribus*
+ Having good yield prediction capability does not necessarily mean it is also capable of estimating EOIR well
<!-- + Because causal identification between yield and input is necessary for estimation of EONR, and such causal inference and having good prediction is different two distinct object -->

---

# New Trend of Causal Machine Learning Application 
+ Causal Machine Learning (CML) methods:
  + Unlike the conventional prediction-oriented ML methods, CML focuses on identifying causal impacts of an event (in our context, an increase or decrease in input rate for example)
  \newline
+ **Causal Forest (CF) ** [@Wager2018a; @athey2016recursive]:
  + CF estimates heterogeneous causal impacts of a treatment (a change in the input level) based on observed characteristics (e.g., organic matter)
<!-- + Hence, CF seems particularly suitable for estimating site-specific yield response functions and then EOIR.  -->

---

# Research Questions

##
+ In terms of estimating EOIR, how do CF-based methods (CF-stepwise and CF-base) compare to other prediction-oriented ML methods: Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN)?
\newline
+ Is the predictive ability of yield a good indicator of the performance of EOIR estimation?

---

# Methods
+ Conduct one thousand rounds of Monte Carlo simulations under four different production scenarios
+ Compare the performance in estimating economically optimal nitrogen rates (EONR) of CF-based methods (CF-base and CF-stepwise) to other methods: RF, BRF, and CNN
+ For RF, BRF, and CNN, contrast their EONR performances against their yield prediction performances
<!-- +  Evaluation metric: R-squared of estimated EONR and R-squared of predicted yield -->

---

# Key Results: EONR estimation

```{r res-N, out.width = "70%"}
# knit_print(table_optN_subplot_wide)
knitr::include_graphics("table_optN.png")
```

---

# Key Results: EONR estimation and Yield Prediction

```{r res-yield, out.width = "70%"}
# knit_print(table_optN_subplot_wide)
knitr::include_graphics("table_y.png")
```
---

# Key Findings
## 
+ The proposed CF-base method is capable of estimating site-specific EONR more accurately than other prediction-oriented ML methods 
\newline
+ The ability of predicting yield does not necessarily translate to good performance in estimating EONR.

---

# References {.allowframebreaks}

### 2022-02-06 Presentation/OFE_Presentation/presen_slides.tex
Correct the structure of CF_for_VRA folder

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
  ignorenonframetext,
  aspectratio=169,
]{beamer}
\title{Machine Learning Methods for Site-specific Input Management}
\author{Shunkei Kakimoto\(^1\), Taro Mieno\(^1\) and Takashi S. T.
Tanaka\(^2\)}
\date{September 1st 2021}
\institute{\(^1\)Agricultural Economics, University of Nebraska Lincoln
\(^2\)Applied Biological Sciences, Gifu University}

\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \ifXeTeX
    \usepackage{mathspec}
  \else
    \usepackage{unicode-math}
  \fi
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usetheme[]{Madrid}
\usecolortheme{whale}
\usefonttheme{professionalfonts}
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Machine Learning Methods for Site-specific Input Management},
  pdfauthor={Shunkei Kakimoto\^{}1, Taro Mieno\^{}1 and Takashi S. T. Tanaka\^{}2},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{fancyvrb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}
\frame{\titlepage}

\begin{frame}{Background}
\protect\hypertarget{background}{}
\begin{itemize}
\tightlist
\item
  The application of Machine Learning(ML) methods for site-specific
  economically optimal input rates (EOIR) (e.g., seed, fertilizer) have
  been getting more attention in recent years \newline

  \begin{itemize}
  \tightlist
  \item
    Barbosa et al. (2020) applied Convolutional Neural Network
  \item
    Krause et al. (2020) used Random Forest-based approaches
  \item
    Grant Gardner (2021), Wang et al. (2021), Coulibali, Cambouris, and
    Parent (2020), etc.
  \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Research Gap}
\protect\hypertarget{research-gap}{}
\begin{itemize}
\tightlist
\item
  The conventional ML methods focus on predicting yield well rather than
  causal identification of input on yield
\item
  The past studies have used predictive ability of yield for validity of
  their models. \newline
\end{itemize}

\begin{block}{note}
\protect\hypertarget{note}{}
\begin{itemize}
\tightlist
\item
  EOIR estimation should be based on the change in yields associated
  with the change in input levels \emph{ceteris paribus}
\item
  Having good yield prediction capability does not necessarily mean it
  is also capable of estimating EOIR well
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{New Trend of Causal Machine Learning Application}
\protect\hypertarget{new-trend-of-causal-machine-learning-application}{}
\begin{itemize}
\tightlist
\item
  Causal Machine Learning (CML) methods:

  \begin{itemize}
  \tightlist
  \item
    Unlike the conventional prediction-oriented ML methods, CML focuses
    on identifying causal impacts of an event (in our context, an
    increase or decrease in input rate for example) \newline
  \end{itemize}
\item
  \textbf{Causal Forest (CF) } (Wager and Athey 2018; Athey and Imbens
  2016):

  \begin{itemize}
  \tightlist
  \item
    CF estimates heterogeneous causal impacts of a treatment (a change
    in the input level) based on observed characteristics (e.g., organic
    matter)
  \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Research Questions}
\protect\hypertarget{research-questions}{}
\begin{block}{}
\protect\hypertarget{section}{}
\begin{itemize}
\tightlist
\item
  In terms of estimating EOIR, how do CF-based methods (CF-stepwise and
  CF-base) compare to other prediction-oriented ML methods: Random
  Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural
  Network (CNN)? \newline
\item
  Is the predictive ability of yield a good indicator of the performance
  of EOIR estimation?
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Methods}
\protect\hypertarget{methods}{}
\begin{itemize}
\tightlist
\item
  Conduct one thousand rounds of Monte Carlo simulations under four
  different production scenarios
\item
  Compare the performance in estimating economically optimal nitrogen
  rates (EONR) of CF-based methods (CF-base and CF-stepwise) to other
  methods: RF, BRF, and CNN
\item
  For RF, BRF, and CNN, contrast their EONR performances against their
  yield prediction performances
\end{itemize}
\end{frame}

\begin{frame}{Key Results: EONR estimation}
\protect\hypertarget{key-results-eonr-estimation}{}
\begin{center}\includegraphics[width=0.7\linewidth]{table_optN} \end{center}
\end{frame}

\begin{frame}{Key Results: EONR estimation and Yield Prediction}
\protect\hypertarget{key-results-eonr-estimation-and-yield-prediction}{}
\begin{center}\includegraphics[width=0.7\linewidth]{table_y} \end{center}
\end{frame}

\begin{frame}{Key Findings}
\protect\hypertarget{key-findings}{}
\begin{block}{}
\protect\hypertarget{section-1}{}
\begin{itemize}
\tightlist
\item
  The proposed CF-base method is capable of estimating site-specific
  EONR more accurately than other prediction-oriented ML methods
  \newline
\item
  The ability of predicting yield does not necessarily translate to good
  performance in estimating EONR.
\end{itemize}
\end{block}
\end{frame}

\begin{frame}[allowframebreaks]{References}
\protect\hypertarget{references}{}
\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-athey2016recursive}{}}%
Athey, Susan, and Guido Imbens. 2016. {``Recursive Partitioning for
Heterogeneous Causal Effects.''} \emph{Proceedings of the National
Academy of Sciences} 113 (27): 7353--60.

\leavevmode\vadjust pre{\hypertarget{ref-barbosa2020modeling}{}}%
Barbosa, Alexandre, Rodrigo Trevisan, Naira Hovakimyan, and Nicolas F
Martin. 2020. {``Modeling Yield Response to Crop Management Using
Convolutional Neural Networks.''} \emph{Computers and Electronics in
Agriculture} 170: 105197.

\leavevmode\vadjust pre{\hypertarget{ref-coulibali2020}{}}%
Coulibali, Zonlehoua, Athyna Nancy Cambouris, and Serge-Étienne Parent.
2020. {``Site-Specific Machine Learning Predictive Fertilization Models
for Potato Crops in Eastern Canada.''} \emph{PloS One} 15 (8): e0230888.

\leavevmode\vadjust pre{\hypertarget{ref-Gardner21}{}}%
Grant Gardner, David S Bullock, Taro Mieno. 2021. {``An Economic
Evaluation of Site-Specific Input Application r x Maps: Evaluation
Framework and Case Study.''} \emph{Precision Agriculture}.

\leavevmode\vadjust pre{\hypertarget{ref-krause2020random}{}}%
Krause, M, Savanna Crossman, Todd DuMond, Rodman Lott, Jason Swede,
Scott Arliss, Ron Robbins, Daniel Ochs, and Michael A Gore. 2020.
{``Random Forest Regression for Optimizing Variable Planting Rates for
Corn and Soybean Using Topographical and Soil Data.''}

\leavevmode\vadjust pre{\hypertarget{ref-Wager2018a}{}}%
Wager, Stefan, and Susan Athey. 2018. {``{Estimation and Inference of
Heterogeneous Treatment Effects using Random Forests}.''} \emph{Journal
of the American Statistical Association} 113 (523): 1228--42.
\url{https://doi.org/10.1080/01621459.2017.1319839}.

\leavevmode\vadjust pre{\hypertarget{ref-Wang2021}{}}%
Wang, Xinbing, Yuxin Miao, Rui Dong, Hainie Zha, Tingting Xia, Zhichao
Chen, Krzysztof Kusnierek, Guohua Mi, Hong Sun, and Minzan Li. 2021.
{``{Machine learning-based in-season nitrogen status diagnosis and
side-dress nitrogen recommendation for corn}.''} \emph{European Journal
of Agronomy} 123 (May 2020): 126193.
\url{https://doi.org/10.1016/j.eja.2020.126193}.

\end{CSLReferences}
\end{frame}

\end{document}

### 2022-02-06 Writing/JournalSubmission/CoverLetter.rmd
Correct the structure of CF_for_VRA folder

---
title: ""
author: Shunkei Kakimoto
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
    # reference_docx: word_template_format.docx
    # pandoc_args: ["-Fpandoc-crossref"]
---

Date:

To whom it may concern:

We wish to submit an original research article entitled "Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation" for consideration by Computers and Electronics in Agriculture.

We confirm this work is original and has not been published anywhere else. It is not currently being considered for publication elsewhere.

This paper covers a new machine learning approach to site-specific input management. Our proposed approach outperforms methods currently in use. This manuscript is appropriate for publication by Computers and Electronics in Agriculture because it innovates estimation of site-specific crop yield responses specifically to changes in input (e.g., seed, fertilizer).

Current machine learning methods focus on output yield prediction. Our approach specifically estimates the heterogeneous causal effects of nitrogen rates on yields which cannot be achieved through current methods. This manuscript contributes to further innovation and development of site-specific input management.

We have no conflicts of interest to disclose.

Please contact me with any concerns about this manuscript at: skakimoto3@huskers.unl.edu. Contact information for my co-authors is as follows: \
Taro Mieno: tmieno2@unl.edu \
Takashi S.T. Tanaka: takashit@gifu-u.ac.jp \
David S. Bullock: dsbulloc@illinois.edu \

Thank you for considering our manuscript.

Sincerely,

Shunkei Kakimoto

### 2022-02-06 Writing/JournalSubmission/ML_VRA_format.rmd
Correct the structure of CF_for_VRA folder

--- 2022-02-05 Writing/Re_JournalSubmission/ML_VRA_format_v2.rmd
@@
 library(knitr)
-# library(here)
+library(here)
 
-# opts_knit$set(root.dir = here())
-opts_knit$set(root.dir = "~/Dropbox/ResearchProject/ML_VRA")
+# === set wd ===#
+# Notes: not really necessary to set the working directory as long as this Rmd file is part of an R project and the evaluation directory was set to "Project".
+
+opts_knit$set(root.dir = here())
+# setwd(here())
+# opts_knit$set(root.dir = "~/OneDrive - University of Nebraska-Lincoln/ML_VRA")
 
@@
 
-```{r, cache = FALSE}
+```{r, cache = TRUE}
 # === packages ===#
@@
 library(bookdown)
-library(png)
-library(grid)
 ```
@@
 # This is where you prepare data sets and results
-# library(here)
-# setwd(here())
+
 #/*----------------------------------*/
@@
 # --- Convert an Rmd file into a pure R file using purl() ---#
-knitr::purl("./GitControlled/Codes/PrepareResults.Rmd", output = "./GitControlled/Codes/PrepareResults.R")
+knitr::purl(here("GitControlled/Codes/PrepareResults.Rmd"), output = here("GitControlled/Codes/PrepareResults.R"))
 
 # --- Read the simulation results and prepare figures and tables ---#
-source("./GitControlled/Codes/PrepareResults.R")
+source(here("GitControlled/Codes/PrepareResults.R"))
 ```
@@
 # Introduction
+
+<!-- + background on nitrogen management (economics, environment, precision agriculture)   -->
+
+<!-- The modern agricultural production system which is featured by the enlargement of fields due to capital-labor substitution, has been confronting the difficulty of considering the spatial and temporal within-field heterogeneity of crop management[@zhang2002precision].
+Precision agriculture(PA) is the combination of technologies and practices developed to assist decision-making for such complicated management utilizing the power of information technology[@cook1998precision; @finger2019precision].
+One of the leading PA technologies is variable rate application(VRA), and it has been actively investigated for site-specific input management, especially for nitrogen and seed management [@Khosla2002; @shanahan2004feasibility; @ruffo2006site; @koch2004economic; @ping2008site; @shanahan2008responsive; @munnaf2020site ;@munnaf2021map].
+Efficient management of N fertilizer is a critical component of crop production from the agronomic, economic, and environmental standpoints.
+Inappropriate amount or timing of N application adversely affects both biomass yields and grain quality for some crops.
+Furthermore, inefficient use of N fertilizer not only results in economic loss but causes ambient environmental degradation[@blumenthal2008importance; @dinnes2002nitrogen; @tremblay2006adapting].
+\ -->
 
@@
 Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf.
-Figure \@ref(fig:ct-ex) shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$)($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
+Figure \@ref(fig:ct-ex) shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$) and topographical $\textit{slope}$ as variables to explain the heterogeneity of the impact of the treatment impact.
 In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example.
 
-```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
-# knitr::include_graphics("./GitControlled/Writing/Re_JournalSubmission/ctree_ex.pdf")
-readPNG("./GitControlled/Writing/Re_JournalSubmission/ctree_ex.png") %>% grid.raster()
+```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An Illustrative Example of Causal Tree"}
+knitr::include_graphics(here("GitControlled/Writing/JournalSubmission/ctree_ex.png"))
 ```
-
-`r ftext('NOTE: The first number in each node indicates the predicted treatment effects (in kg/ha).
-The number and the percentage of observations belonging to the node are shown below that.', fp_text(font.size = 9))`
 
@@
 The first step in our simulation was to generate one thousand synthetic fields that "resembled" an actual field.
-<span style="color:red"> After generating one thousand synthetic fields, we repeated to evaluate each of the ML methods by one thousand times.
-In an individual simulation round, one of the fields was used as a training data set.
-As a validation data set, a different field from a training data set in that simulation round was used.</span> <!-- For each simulated field, we generated a training data set and a validation data set.
---> Field characteristics and yield were simulated based on the Mitscherlich-Baule (MB) yield response function.
+For each simulated field, we generated a training data set and a validation data set.
+Field characteristics and yield were simulated based on the Mitscherlich-Baule (MB) yield response function.
 We used the RF, BRF, and CNN ML methods to estimate yield response functions, and we used the CF method to estimate treatment effects.
@@
 <!-- experimental field: area: 51ha, plot: 384, subplot:1536, cell:55296   -->
+<!-- field with padding: area: 57ha, plot: 476, subplot:1700, cell:61200   -->
 
 The simulated field was created based on an actual 51-ha Illinois field on which the Data-Intensive Farm Management (DIFM) project [@bullock2019] has run multiple OFPEs.
-Figure \@ref(fig:field-map) illustrates that simulated trials consisted of $384$ <span style="color:red"> 18-m </span> $\times$ <span style="color:red"> 73-m </span> "plots," each of which was assigned an N fertilizer application rate.
+Figure \@ref(fig:field-map) illustrates that simulated trials consisted of $384$ 60-ft $\times$ 240-ft "plots," each of which was assigned an N fertilizer application rate.
 Each plot was made up of four (4-rows $\times$ 1-column) "subplots," which were unit of analysis used in subsequent statistical analysis.
-Each subplot contained of a 6-rows $\times$ 6-columns grid of thirty-six <span style="color:red"> 3-m </span> $\times$ <span style="color:red"> 3-m </span> "cells." All field characteristics and yield data were generated at the cell level.
+Each subplot contained of a 6-rows $\times$ 6-columns grid of thirty-six 10-ft $\times$ 10-ft "cells." All field characteristics and yield data were generated at the cell level.
 
-```{r field-map, fig.width=4, fig.height=3, fig.cap = "Division of field: plots, subplots and cells"}
-# knitr::include_graphics("./GitControlled/Writing/Re_JournalSubmission/field_devision_v2.png")
-readPNG("./GitControlled/Writing/Re_JournalSubmission/field_devision_v2.png") %>% grid.raster()
+```{r field-map, fig.width=4, fig.height=3, fig.cap = "Division of Field: plots, subplots and cells"}
+knitr::include_graphics(here("GitControlled/Writing/JournalSubmission/field_devision.png"))
+
 ```
@@
 
-```{r variogram-parameters, tab.cap = "The parameters for the variogram modeling"}
+```{r variogram-parameters, tab.cap = "The Parameters for the Variogram Modeling"}
 variogram_tb
@@
 
-```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An illustrative example of spatial distributions of field characteristics"}
+```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics"}
 # field_alpha + field_beta + field_ymax
@@
 
-```{r fig-optN, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a spatial distribution of true optimal N rate"}
+```{r fig-optN, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of a Spatial Distribution of True Optimal N Rate"}
 vis_optN_cell
@@
 
-```{r fig-nExp, fig.width=3, fig.height=4, fig.cap = "An illustrative example of experimental design of N"}
+```{r fig-nExp, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of Experimental Design of N"}
 field_Ndesign
@@
 
-```{r field-yield-cell, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a yield distribution map at the cell resolution"}
+```{r field-yield-cell, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of a Yield Distribution Map at the Cell resolution"}
 vis_yield_cell
@@
 
-```{r field-yield-subplot, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a yield distribution map at the subplot resolution"}
+```{r field-yield-subplot, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of a Yield Distribution Map at the Subplot resolution"}
 vis_yield_subplot
@@
 Rather, they use multiple observed soil/field characteristics to explain such phenological phenomena.
-For example, instead of using $ymax^{i,j}$ directly, some topographical land features and soil properties such as elevation and soil sand content could be used as yield-limiting factors [@jiang2004effect; @kravchenko2000correlation].
+For example, instead of using $ymax^{i,j}$ directly, some some topographical land features and soil properties such as elevation and soil sand content could be used as yield-limiting factors [@jiang2004effect; @kravchenko2000correlation].
 In reality, scientists may include more than three variables as covariates.
@@
 
-## Training Models and and Estimating Site-specific EONRs
+## OFPE Experiments and Estimating Site-specific Optimal N Rates
 
@@
 
-The accuracy of EONR estimation was judged based RMSE ($kg/ha$) of EONR estimation against the true EONR at the subplot level.
+The accuracy of EONR estimation was judged based RMSE ($kg/ha$)of EONR estimation against the true EONR at the subplot level.
 In addition, using the EONR estimates, we also calculated profit-deficit ($\$/ha$) (i.e., $\hat{\pi}_{def}$) relative to the true maximum profit at the subplot level.
@@
 
-```{r table-optN-subplot-wide, tab.cap = "Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML methods and modeling scenarios"}
+```{r table-optN-subplot-wide, tab.cap = "Mean RMSE of EONR Estimation and Profit-deficit by ML Methods and Modeling Scenarios"}
 report_table_optN
@@
 The constant marginal product caused the estimated EONR to take on either the lowest or highest experimental N application rate.
-To examine whether this problem is a product solely of the specific choice of CNN architecture, we also tested another CNN model, which was analogous to CNN-ST proposed by @barbosa2020modeling.
+To examine whether this problem is product solely of the specific choice of CNN architecture, we also tested another CNN model, which was analogous to CNN-ST proposed by @barbosa2020modeling.
 This architecture also estimated that yield and N rates were perfectly linearly related, and also estimated site-specific EONR poorly.
@@
 
-```{r dist-optN, fig.width=6, fig.height=7, fig.cap = "Distributions of RMSE of EONR estimation over simulations"}
+```{r dist-optN, fig.width=6, fig.height=7, fig.cap = "Distributions of RMSE of EONR Estimation over Simulations"}
 plot_dis_optN
@@
 
-```{r dist-piLoss, fig.width=6, fig.height=7, fig.cap = "Distributions of profit deficit over simulations"}
+```{r dist-piLoss, fig.width=6, fig.height=7, fig.cap = "Distributions of Profit Deficit over Simulations"}
 piLoss_density
@@
 However, they differ substantially in the accuracy of their treatment effect estimations.
-Points are clustered much more tightly about the 1-to-1 line for CF-base than RF and BRF.
+Points are clustered much more tightly about the 1-to-1 line much for CF-base than RF and BRF.
 That is, CF-base estimates treatment effects much more efficiently than do the RF and BRF methods, which focus on yield prediction rather than treatment effect estimation.
 
-```{r plot-tre, fig.width=7, fig.height=5, fig.cap = "True treatment effects vs estimated treatment effects (scenario: aabbyytt)"}
+```{r plot-tre, fig.width=7, fig.height=5, fig.cap = "True Treatment Effects vs Estimated Treatment Effects (Scenario: aabbyytt)"}
 figure_te
@@
 
-```{r plot-y-optN, fig.width=7, fig.height=5, fig.cap = "The relationship in the performance between EONR estimation and yield prediction by ML methods and modeling scenarios"}
+```{r plot-y-optN, fig.width=7, fig.height=5, fig.cap = "The Relationship in the Performance between EONR Estimation and Yield Prediction by ML Methods and Modeling Scenarios"}
 fig_y_optN
@@
 
-```{r table-y-subplot-wide, tab.cap = "Mean RMSE of yield prediction (kg/ha) by ML methods and modeling scenarios"}
+```{r table-y-subplot-wide, tab.cap = "Mean RMSE of Yield Prediction by ML Methods and Modeling Scenarios"}
 report_table_y
@@
 
-```{r count-table, tab.cap = "Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances for prediction-oriented ML methods"}
+```{r count-table, tab.cap = "Relationship between the EONR Prediction Performances (as measured by profit) and the Yield Prediction Performances for Prediction-oriented ML Methods"}
 report_summary_res_CNN_RF_BRF

### 2022-02-06 Writing/JournalSubmission/ML_for_VRA.Rmd
Correct the structure of CF_for_VRA folder

--- 2022-02-06 Writing/JournalSubmission/ML_VRA_format.rmd
@@
     global_numbering: true
-    # reference_docx: word_template.docx
-    reference_docx: word_template_format.docx
+    reference_docx: word_template.docx
+    # reference_docx: word_template_format.docx
     # pandoc_args: ["-Fpandoc-crossref"]
@@
 library(sf)
-library(png)
 library(data.table)
@@
 
-# Keywords: {-}
+# Keywords:
 
@@
 In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example.
-
-```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An Illustrative Example of Causal Tree"}
-knitr::include_graphics(here("GitControlled/Writing/JournalSubmission/ctree_ex.png"))
-```
-
 The first data split criterion is whether the $\textit{ecs}$ value is greater or less than $25$.
@@
 
-```{r field-map, fig.width=4, fig.height=3, fig.cap = "Division of Field: plots, subplots and cells"}
-knitr::include_graphics(here("GitControlled/Writing/JournalSubmission/field_devision.png"))
-
-```
-
 ### Underlying Yield Response Function
@@
 
-<br>
-
-```{r variogram-parameters, tab.cap = "The Parameters for the Variogram Modeling"}
-variogram_tb
-```
-
-<br>
-
-```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics"}
-# field_alpha + field_beta + field_ymax
-grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2, nrow=2)
-```
-
 Each cell $(i,j)$'s "true" optimal N application rate, denoted $N_{opt}^{i,j}$, was calculated by solving a profit maximization problem:
@@
 
-```{r fig-optN, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of a Spatial Distribution of True Optimal N Rate"}
-vis_optN_cell
-```
-
-<br>
-
 ### Trial Design
@@
 In each simulation round, five field-trial N rates were determined based on the range of the round's cell-specific EONRs. 
-Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percent quantile of the round's cell-specific EONRs. Then, the five trial design rates were
+Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percent quantile of the round's cell-specific EONRs. Then, the five trial design rates were \
 
@@
 
-In each round, a Latin square design was followed to assign each plot one of the five N rates so established. Figure \@ref(fig:fig-nExp) shows an example of a trial design.
-
-```{r fig-nExp, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of Experimental Design of N"}
-field_Ndesign
-```
-
+In each round, a Latin square design was followed to assign each plot one of the five N rates so established.
+Figure \@ref(fig:fig-nExp) shows an example of a trial design.
 Under this design, the N rate was orthogonal to the error term.
@@
 Note that the violation of this condition leads to biased estimation for not just CF and the other ML methods, as well.
+
+<!-- Resulting mean yield of $1.1250\times10^4 \text{ } kg/ha$. The magnitude of the error term is set to vary yields by approximately $1245 \text{ }(kg/ha)$ on average from deterministic yields. 
+ -->
 
@@
 \@ref(eq:eqn3), applying parameter values $\mathbf{c^{i,j}}=(\alpha^{i,j}, \beta^{i,j}, ymax^{i,j})$, the disturbance term level $\varepsilon^{i,j}$, and the cell's assigned experimental N rate, $N^{i,j}$ (Figure \@ref(fig:field-yield-cell)).
-
-```{r field-yield-cell, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of a Yield Distribution Map at the Cell resolution"}
-vis_yield_cell
-```
-
-<br>
-
-These were aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation. The subplot data were therefore
+These were aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation.
+The subplot data were therefore
 
@@
 But data aggregation to the subplot level was conducted because the large sizes of harvesters make it impossible to monitor yields accurately at smaller scales.
-
-```{r field-yield-subplot, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of a Yield Distribution Map at the Subplot resolution"}
-vis_yield_subplot
-```
-
-<br>
 
@@
 BRF performed considerably better predicting EONR than did RF.
-
-<br>
-
-```{r table-optN-subplot-wide, tab.cap = "Mean RMSE of EONR Estimation and Profit-deficit by ML Methods and Modeling Scenarios"}
-report_table_optN
-# knit_print(report_table_optN)
-```
-
-<br>
-
 Interestingly, CNN completely failed in its estimations of site-specific EONRs.
@@
 
-```{r dist-optN, fig.width=6, fig.height=7, fig.cap = "Distributions of RMSE of EONR Estimation over Simulations"}
-plot_dis_optN
-```
-
-```{r dist-piLoss, fig.width=6, fig.height=7, fig.cap = "Distributions of Profit Deficit over Simulations"}
-piLoss_density
-```
-
-<br>
-
 Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions.
 It plots the estimated treatment effects against true treatment effects by treatment types and ML methods (RF, BRF, and CF-base) under the "aabbyytt" scenario in one of the $1000$ simulations rounds.
-The figure shows that the estimated treatment effects did not exhibit significant bias, with the points clustered around the red 1-to-1 line.
+<!-- To illustrate differences between the ML methods, -->The figure shows that the estimated treatment effects did not exhibit significant bias, with the points clustered around the red 1-to-1 line.
 However, they differ substantially in the accuracy of their treatment effect estimations.
@@
 
-```{r plot-tre, fig.width=7, fig.height=5, fig.cap = "True Treatment Effects vs Estimated Treatment Effects (Scenario: aabbyytt)"}
-figure_te
-```
+## Yield Prediction and EONR Estimation
 
-`r ftext('NOTE: The red line in the figures denotes the 1-to-1 line to show the ideal relationship between true and estimated treatment effects.', fp_text(font.size = 9))`
-
-## Yield Prediction and EONR Estimation
-For RF, BRF and CNN, Figure \@ref(fig:plot-y-optN) plots the RMSE values of EONR estimation against the RMSE values of yield prediction, and the red line shows the best-fit line describing the relationship between them.
+For RF, BRF and CNN, Figure \@ref(fig:plot-y-optN) plots the RMSE values of EONR estimation against the RMSE values of yield prediction, and the red line shows the regression line describing the relationship between them.
 For all the models the regression line was almost flat, showing little if any correlation between the two measures.
 In other words, the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions.
-
-```{r plot-y-optN, fig.width=7, fig.height=5, fig.cap = "The Relationship in the Performance between EONR Estimation and Yield Prediction by ML Methods and Modeling Scenarios"}
-fig_y_optN
-```
-
-`r ftext('NOTE: The red line in the figures denotes the best-fit line to explain the relationship between the RMSEs of EONR prediction and yield prediction.', fp_text(font.size = 9))`
-
-<br>
+<!-- For all the models the figure shows little if any correlation between the two measures.
+In other words, the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions.
+-->
 
@@
 Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.
-
-<br>
-
-```{r table-y-subplot-wide, tab.cap = "Mean RMSE of Yield Prediction by ML Methods and Modeling Scenarios"}
-report_table_y
-```
-
-<br>
 
@@
 But, BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$.
-
-<br>
-
-```{r count-table, tab.cap = "Relationship between the EONR Prediction Performances (as measured by profit) and the Yield Prediction Performances for Prediction-oriented ML Methods"}
-report_summary_res_CNN_RF_BRF
-```
-
-<br>
 
@@
 
-# Acknowledgement
+# Funding
 
@@
 
+# Tables
+
+<br>
+
+```{r variogram-parameters, tab.cap = "The Parameters for the Variogram Modeling"}
+variogram_tb
+```
+
+\newpage
+
+<br>
+
+```{r table-optN-subplot-wide, tab.cap = "Mean RMSE of EONR Estimation and Profit-deficit by ML Methods and Modeling Scenarios"}
+report_table_optN
+# knit_print(report_table_optN)
+```
+
+<br>
+
+<br>
+
+```{r table-y-subplot-wide, tab.cap = "Mean RMSE of Yield Prediction by ML Methods and Modeling Scenarios"}
+report_table_y
+```
+
+\newpage
+
+<br>
+
+```{r count-table, tab.cap = "Relationship between the EONR Prediction Performances (as measured by profit) and the Yield Prediction Performances for Prediction-oriented ML Methods"}
+report_summary_res_CNN_RF_BRF
+```
+
+\newpage
+
+# Figures
+
+<br>
+<!-- 
+1. add the distribution of the resutls
+2. add the distribution of each parameters -->
+<!-- when you mention a figure, use "Figure \@ref(fig:fig-1)"  -->
+
+```{r ct-ex, fig.width=7, fig.height=10, fig.align="center", fig.cap = "An Illustrative Example of Causal Tree"}
+knitr::include_graphics(here("GitControlled/Writing/JournalSubmission/ctree_ex.pdf"))
+```
+
+<br>
+
+<br>
+
+```{r field-map, fig.width=7, fig.height=10, fig.cap = "Division of Field: plots, subplots and cells"}
+knitr::include_graphics(here("GitControlled/Writing/JournalSubmission/field_devision.pdf"))
+```
+
+```{r fig-parameters, fig.width=9, fig.height=10, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics"}
+# field_alpha + field_beta + field_ymax
+grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2, nrow=2)
+```
+
+```{r fig-optN,  fig.cap = "An Illustrative Example of a Spatial Distribution of True Optimal N Rate"}
+vis_optN_cell
+```
+
+<!-- \newpage -->
+
+```{r fig-nExp, fig.width=7, fig.height=9, fig.cap = "An Illustrative Example of Experimental Design of N"}
+field_Ndesign
+```
+
+```{r field-yield-cell, fig.cap = "An Illustrative Example of a Yield Distribution Map at the Cell resolution"}
+vis_yield_cell
+```
+
+```{r field-yield-subplot, fig.cap = "An Illustrative Example of a Yield Distribution Map at the Subplot resolution"}
+vis_yield_subplot
+```
+
+```{r dist-optN, fig.width=7, fig.height=8, fig.cap = "Distributions of RMSE of EONR Estimation over Simulations"}
+plot_dis_optN
+```
+
+```{r dist-piLoss, fig.width=7, fig.height=8, fig.cap = "Distributions of Profit Deficit over Simulations"}
+piLoss_density
+```
+
+```{r plot-tre, fig.width=8, fig.height=9, fig.cap = "True Treatment Effects vs Estimated Treatment Effects (Scenario: aabbyytt)"}
+figure_te
+```
+
+`r ftext('NOTE: The red line in the figures denotes the 1-to-1 line to show the ideal relationship between true and estimated treatment effects.', fp_text(font.size = 9))`
+
+```{r plot-y-optN, fig.width=8, fig.height=9, fig.cap = "The Relationship in the Performance between EONR Estimation and Yield Prediction by ML Methods and Modeling Scenarios"}
+fig_y_optN
+```
+
+`r ftext('NOTE: The red line in the figures denotes the best-fit line to explain the relationship between the RMSEs of EONR prediction and yield prediction.', fp_text(font.size = 9))`
+
 # References

### 2022-02-06 Writing/Re_JournalSubmission/replies_rev_1.rmd
Correct the structure of CF_for_VRA folder

--- 2022-02-05 Writing/Re_JournalSubmission/replies_rev_1.Rmd
@@
 title: "Reply to Reviewer #1"
-author: 
+author: Shunkei Kakimoto
 output:
@@
 
-**Materials and Method to just Method: Monte Carlo Simulations?**
-
-The core objective is to test the CF against existing ML methods.
-To this core objective, ML simulations are our core method.
-For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood by the reader of this journal.
-Since, this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well.
-Now, if we place this inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works.
-Instead of this, we believe that it is beneficial to first give the readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted.
-
-We talk about identifying site-specific economically optimal input rates in three different places.
-Therefore, I understand why you feel there are redundancies.
-However, each of them serves distinctive purposes and we would like to keep the current structure if that is acceptable to you.
-
-Section 2.1: bluh bluh
-Section 3.: true optimal N
-Section 3.: estiamted optimal N
-
 </span>
@@
 **3. The description of materials and methods section is redundant, please move some unimportant details description to supplementary materials.**
-
 <span style="color:blue">
-We first apologogize that misleading section and subsection titles may have caused confusions about your perceived structural redundancy of this article.
-
-We wrote the initial manuscript with avoiding redundancy in mind and we beleived that we did not have any redundancy in our paper.
-Therefore, we struggled tremendously to see where the redundancies are.
-We would really appreciate it if you could specify where you see redundancies and why so that we can address prorperly.
-
-In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated.
-It is much like any emprical studies using real experiment data provides lots of details about the experiemnts.
-We take reproducibility seriously and we believe that the details we peovided in our manuscript is appropriate.
-Therefore, we had very hard time telling which is unnecessary and not.
-We would really appreciate it if you could specify which parts are not critical.
 
@@
 
-+ It is degree. <!-- The slope is obtained by dividing the rise over run. If slope is 0.005857921, it means that the field is raised by 0.005857921 m for every 1m you move horizontally.  -->
-+ I added the the unit of EC (dS/m) additionally, since another reviewer pointed out the units of EC
++ I provided the unit in the text. It is degree.
 
@@
 
-+ I added the explanation for those numbers in the footnote. 
++ I added the explanation for those numbers as a footnote in the figure. 
 </span>
@@
 
-+ I numbered only referenced equations. Should I number all the equations?
++ I numbered all the formulas. 
 </span>
@@
 
-+ I changed this sentence "For each simulated field, we generated a training data set and a validation data set."
++ I modified this sentence "For each simulated field, we generated a training data set and a validation data set." For each simulation round, one of the fields was used as a training data set, and another field that is different from the one used as a training data set in that round was used as a validation data set.
 
-+ The modified version is "After generating one thousand synthetic fields, we repeated to evaluate each of the ML methods by one thousand times.
-In an individual simulation round, one of the fields was used as a training data set.
-As a validation data set, a different field from a training data set in that simulation round was used".
 </span>
@@
 <span style="color:blue">  
++ I uploaded to the simulation codes and the data on Mendeley Data. The link is suggested on section 3: Materials and Methods.
 
@@
 + I converted to those units to meter (m)
-  + plot size: 60-ft × 240-ft -> 18.288-m × 73.152-m
-  + subplot size: 60-ft × 60-ft -> 18.288-m × 18.288-m
-  + plot size: 10-ft × 10-ft -> 3.048-m × 3.048-m
+
 </span>
@@
 
-+ I added the number of rows and columns of plots, subplots and cells in Figure 2. 
++ I updated Figure 2. The number of rows and columns of plots, subplots, and cells schematics are indicated each map in Figure 2.
 </span>
@@
 
-+ Current name:
-  + 3.2 OFPE Experiments and Estimating Site-specific Optimal N Rates
-    + 3.2.1 RF, BRF, and CNN
-    + 3.2.2 CF
-
-+ The title of section 3.2.1: Site-specific EONR estimation by RF, BRF, and CNN
-+ The title of section 3.2.1: Site-specific EONR estimation by CF
-
-+ Or, we could change the title of section 3.2 (e.g., Machine Learning Algorithm to Estimate Site-specific EONR) and use the same title for section 3.2.1 and 3.2.2
++ I changed the title of section 3.2 to "Training Models and Estimating Site-specific EONRs".
+Further, I revised the title of sections 3.2.1 and 3.2.2 to "Estimation of site-specific EONRs by RF, BRF, and CNN" and "Estimation of site-specific EONRs by CF", respectively.
 </span>
@@
 
-+ Current name:
-  + 4.1 EONR Estimation
-  + 4.2 Yield Prediction and EONR Estimation
-
-+ The title of section 4.2 could be changed to "The relationship between the performance of yield prediction and EONR estimation" (?)
++ I changed the title of section 4.2 to "The relationships between yield prediction performance and EONR prediction performance". 
 </span>
@@
 
-+ I need to add the explanation for it in section 4.1 EONR estimation.  
++ As explained in section 4.1, CNN completely failed to predict site-specific EONR because the estimated yield response function were always linear (please see the Table 1).
+Therefore, I do not think that visualizing the CNN results provide any meaningful implications to understand its performance of EONR estimation performance.
++ I added the explanation for not showing CNN results in Figures 8,9, and 10.
+("CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always take $62.8$ kg/ha and \$$58.99$/ha, respectively")
+
 </span>

### 2022-02-06 Writing/Re_JournalSubmission/ML_VRA_v2.rmd
rewriting the second section

--- 2022-02-05 GitControlled/Writing/Re_JournalSubmission/ML_VRA_v2.rmd
@@
 
-# Background:Using Causal Forest Methods to Predict Changes in Yield
+# Predicting Yield vs. Predicting Changes in Yield in Response to Changes in Input Management
 
-In the following, we use basic microeconomic theory to describe the fundamental information necessary to identify EOIRs in general: the site-specific treatment effect of input application on yield.
+In the following, we describe the fundamental information necessary to identify EOIR in general: the site-specific treatment effect of input application on yield.
 We then discuss the causal forest method in detail, show how it is particularly suitable to obtain this fundamental information, and contrast it to more traditional prediction-oriented ML methods, such as RF, BRF, and CNN.
 
-## A Simple Profit-maximization Problem
+## Estimating EOIR and Treatment Effects
 
@@
 
-Elementary calculus shows that the necessary condition for maximization is, that $\partial f(I, \mathbf{c})/\partial I - w =0$, which implicitly defines the economically optimal input application rate as a function $I^{*}$ of prices and soil/field characteristics, and may be arranged as \@ref(eq:eqn2):
+Elementary calculus shows that the necessary condition for maximization is, that $\partial f(I, \mathbf{c})/\partial I - w =0$, which implicitly defines the economically optimal input application rate as a function of prices and soil/field characteristics, and may be arranged as \@ref(eq:eqn2):
 
@@
 While knowledge of the yield function $f(I, \mathbf{c})$ in Eq.
-\@ref(eq:eqn1) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the function's partial derivative is necessary.
+\@ref(eq:eqn1)) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the _change_ in yield in response to a change in input rate is.
 
-In the following, we discuss a method of using Causal Forest methods that can provide statistical advantages to the estimation of economically optimal input application rates because it is built to estimate approximations of the derivative $\partial f/\partial I$ directly, and not the yield function $f$ itself.
-
-## Estimating EOIR and Treatment Effects
-
-Recent studies using ML methods to estimate the effectiveness of various agricultural input management strategies have based their analyses on estimates of a yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21).
-In the following, we present a Causal Forest methodology that does not rely on estimation of how the level of yield depends on the input application rate $I$, but rather relies on a discrete version of Eq.
-\@ref(eq:eqn2), examining the discrete changes in yield that result from discrete *changes* in the input application rate $I$.
-
-Consider an increasing ordering of input application rates $I_1, I_2,...,I_K$.
-Among these K rates, for a generic site $i$ a specific EOIR can be identified if the *treatment effect* function $\Delta y_i(I_{k+1}, I_{k})$ defined in Eq.
-\@ref(eq:eqn3)is known.
-This function is defined as the discrete change in yield that results from a discrete change in the input level from $I_k$ to $I_{k+1}$, and it depends on the characteristics at the site analyzed:
-
-\begin{equation}
-\Delta y_i(I_{k+1}, I_{k}) = f(I_{k+1}, \mathbf{c_i}) - f(I_{k}; \mathbf{c_i}) \quad ^\forall k = 1, \dots , K - 1. (\#eq:eqn3)
-\end{equation}
-
-Once treatment effects $\Delta y_i(I_{k+1}, I_{k})$ have been identified for every $k$, economic analysis can be conducted to identify the EOIR for site $i$.
-The profit change from increasing the input rate from $I_{1}$ to $I_{k}$ is
-
-\begin{equation}
-p (\sum_1^{k-1} \Delta y_i(I_{k+1}, I_{k})) - w \times (I_k - I_0). (\#eq:eqn4)
-\end{equation}
-
-The EOIR is the value $I_k$ that maximizes the profit gain "relative" to profits from $I_1$. ($I_1$ may be the EOIR if no other rates generates greater profit.)
+Recent papers using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21) and then derive changes in yield associated with changes in input rate to estimate site-specific input recommendations.
+On the other hand, Causal Forest is designed specifically to estimate a discrete version of Eq.
+\@ref(eq:eqn2) directly, examining the discrete changes in yield that result from discrete *changes* in the input application rate $I$, bypassing the estimation of $f(I, \mathbf{c})$.
+It may be suspected that CF will outperform other ML methods that identify EOIR indirectly through yield prediction.
+We now details how CF works below and why CF may perform better in predicting EOIR than other prediction-oriented ML methods used in the previous studies.
 
@@
 
-```{r ct-ex, out.width="50%", fig.align="center", fig.cap = "An illustrative example of causal tree"}
+```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
 # knitr::include_graphics("./GitControlled/Writing/Re_JournalSubmission/ctree_ex.pdf")
@@
 Trees are further developed to have more groups of subsamples to allow for more flexible representations of the heterogeneous treatment effects.
-The estimated CF model does not predict yield level at any site $i$ in the field, but rather estimates site-specific EOIRs by estimating treatment effects.
-Since CF is designed to estimate the causal effect of an input directly, it may be suspected that CF will outperform other ML methods that identify EOIR indirectly through yield prediction.
+The estimated heterogeneous treatments effects can then be used to identify site-specific EOIRs.
+It is noteworth that at no point CF estimates yield _level_.
 
@@
 
-## Advantages of Causal Forest Analysis in the Context of On-farm Precision Experimentation
+## CF vs. Prediction-oriented ML methods
 
-Whether the indirect (yield-prediction-first) or direct approach is used can lead to meaningful statistical differences in EOIR estimation.
-The conventional prediction-oriented ML methods are designed to predict yield, $y_{i}(I) \equiv f(I, c_{i})$, well, but not necessarily treatment effects.
-Since the loss function used in prediction-oriented ML uses (typically squared) residuals in yield prediction, prediction-oriented ML is naturally optimized for prediction the "level" of yield instead of identifying the causal impact of the input.
-But CF is designed specifically to estimate the casual impact of the input.
+Whether the indirect (yield-prediction-first) and direct approach is used can lead to meaningful statistical differences when it comes to EOIR estimation.
+The conventional prediction-oriented ML methods are designed to predict yield, $y_i(I,\mathbf{c})$, well, but not necessarily treatment effects.
+Since the loss function used in prediction-oriented ML uses (typically squared) residuals in yield prediction, prediction-oriented ML is naturally optimized for predicting the "level" of yield instead of identifying the causal impact of the input on yield.
+CF, on the other hand, is designed specifically to estimate the causal impact of input.
 Indeed, @Wager2018a used Monte Carlo simulations to show that CF provided more accurate estimates of heterogeneous treatment effects than those provided by RF.
 However, the underlying data generating process of their simulations was extremely simple, with the treatment effect influenced by only a single variable.
-CF has never been tested for more complicated data generating processes, such as those represented by yield response functions in which the treatment effect of an input can be affected by multiple variables in a non-linear fashion.
+CF has not been tested for more complicated data generating processes, such as those represented by yield response functions in which the treatment effect of an input can be affected by multiple variables in a non-linear fashion.
 Moreover, CF has never been compared to more advanced ML methods such as BRF and CNN that are considered to have prediction capabilities greater than RF's.
-Our report builds on @Wager2018a to compare CF to these prediction-oriented ML methods (not just RF, but also BRF and CNN) in more realistic agronomic experiment settings.
+The study reported here builds on @Wager2018a to compare CF to these prediction-oriented ML methods (not just RF, but also BRF and CNN) in more realistic agronomic experiment settings.
 

### 2022-02-06 Writing/Re_JournalSubmission/replies_rev_1.rmd
changes in response to reviewer 1

@@
 
+**Materials and Method to just Method: Monte Carlo Simulations?**
+
+We do see a redundancy of expalining how CF can be used to identify site-specific input recommendations.
+It is explained twice in 2.2 and 3.2.2, while 2.2 is intended for a more general case than 3.2.2 that is specific to our simulations.
+Therefore, we decided to take out 2.2.
+We also renamed 2.1 to "Estimating EOIR and Treatment Effects"
+
+The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations.
+To this core objective, ML simulations are our core method.
+For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal.
+However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well.
+Now, if we place such description inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works.
+Instead of this, we believe that it is beneficial to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted.
+Therefore, we kept 2.3 and 2.4 in the current manuscript.
+
+We talk about identifying site-specific economically optimal input rates in three different places.
+However, each of them serves distinctive purposes and we would like to keep the current structure if that is acceptable to you.
+
+Section 2.1: bluh bluh
+Section 3.: true optimal N
+Section 3.: estiamted optimal N
+
 </span>
@@
 **3. The description of materials and methods section is redundant, please move some unimportant details description to supplementary materials.**
+
 <span style="color:blue">  
+We first apologogize that misleading section and subsection titles may have caused confusions about your perceived structural redundancy of this article.
+
+We wrote the initial manuscript with avoiding redundancy in mind and we beleived that we did not have any redundancy in our paper.
+Therefore, we struggled tremendously to see where the redundancies are.
+We would really appreciate it if you could specify where you see redundancies and why so that we can address prorperly.
+
+In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated.
+It is much like any emprical studies using real experiment data provides lots of details about the experiemnts.
+We take reproducibility seriously and we believe that the details we peovided in our manuscript is appropriate.
+Therefore, we had very hard time telling which is unnecessary and not.
+We would really appreciate it if you could specify which parts are not critical.
 

### 2022-02-06 Codes/PrepareResults.rmd
restructuring of the folders and files

# Set up

```{r set-up, cache = F}
library(knitr)
library(here)

here::i_am("GitControlled/Writing/manuscript_cea.rmd")

knitr::opts_chunk$set(
  cache = TRUE,
  warning = FALSE,
  message = FALSE
)
```

```{r packages, cache = FALSE, include = FALSE}
# === packages ===#
# --- data wrangling--- #
library(sf)
library(data.table)
library(tidyverse)

# --- figure making --- #
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(viridis)
library(ggpubr)
library(gridExtra)
library(DiagrammeR)

# --- table making --- #
library(flextable)
library(officer)
library(officedown)
library(modelsummary)
library(latex2exp)
```

# Read the data

```{r setup, warning=FALSE, message=FALSE, cache= FALSE}
# field <- readRDS("Shared/Data/for_Simulations/field_padding.rds") %>%
#     filter(padding==1)%>%
#     dplyr::select(unique_cell_id)

# === plot-level field data set  === #
field_plot_sf <-
  here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
  readRDS()

# === subplot-level field data set  === #
field_subplot_sf <-
  here("Shared/Results/for_writing/sample_field_subplot_sf.rds") %>%
  readRDS()

# === cell-level field data set  === #
field_cell_sf <-
  here("Shared/Results/for_writing/sample_field_cell_sf.rds") %>%
  readRDS()
```

# Variogram Prameter Table

```{r}
variogram_tb <-
  data.frame(
    Parameters = c("ymax_ij", "alpha_ij", "beta_ij", "varepsilon_ij"),
    Range = c(400, 400, 400, 400),
    Mean = c(12000, -0.5, format(c(0, 0))),
    Nugget = format(c(0, 0, 0, 0)),
    Sill = c(2000000, 0.02, format(1, nsmall = 1), 0.015)
  ) %>%
  flextable() %>%
  compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sup(as_i("i,j")))) %>%
  compose(i = 2, j = 1, part = "body", value = as_paragraph(as_i("\U03B1"), as_sup(as_i("i,j")))) %>%
  compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("\U03B2"), as_sup(as_i("i,j")))) %>%
  compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sup(as_i("i,j")))) %>%
  compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("6"))) %>%
  compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 2, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
  compose(i = 4, j = 5, part = "body", value = as_paragraph("1.5", "\U2A2F", "10", as_sup("-2"))) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # --- change headers labels--- #
  set_header_labels(values = list(
    Parameters = "Parameters",
    Range = "Range (m)",
    Mean = "Mean",
    Nugget = "Nugget",
    Sill = "Sill"
  )) %>%
  #- change the borders just for consistency with other tables -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  footnote(
    value = as_paragraph("NOTE: About ymax, the units of of Mean, Nugget, and Sill are kg."),
    ref_symbols = NA
  ) %>%
  autofit()
```

# Field Maps

## Division of field: plots, subplots and cells (Visualization)

```{r field-map-visualization, dependson = "setup"}

# == plot-level field without padding area ==##
vis_field_plot <-
  ggplot(field_plot_sf) +
  geom_sf(fill = NA) +
  theme_void() +
  labs(caption = "Bottom Title") +
  theme(plot.title = element_text(hjust = 0.5))

### ==== Example map of plot and subplots and cells ====####
# == Preparation ==##
ex_plot <- field_plot_sf[224, ]
ex_subplots <- field_subplot_sf[ex_plot, , op = st_within]

ex_one_subplot <- ex_subplots[1, ]
ex_cells <- field_cell_sf[ex_one_subplot, , op = st_within]

#-- (1) plot-level field map (base: vis_field_withoutPadding) --#
library(latex2exp)

plot <-
  ggplot() +
  geom_sf(data = field_plot_sf) +
  geom_sf(data = ex_plot, fill = "green", size = 1) +
  # coord_sf(expand = F) +
  theme_void() +
  ggtitle(TeX("$12 \\times 32$ plots")) +
  theme(plot.title = element_text(hjust = 0.5))

grob_plot <- ggplotGrob(plot)

# #-- (2) create a map of subplots in a plot --##
subplots_inPlot <- ggplot() +
  geom_sf(data = ex_plot, fill = "green") +
  geom_sf(data = ex_subplots, fill = NA, size = 1) +
  theme_void() +
  ggtitle(TeX("$4 \\times 1$ subplots")) +
  theme(plot.title = element_text(hjust = 0.5))

grob_subplots_inPlot <- ggplotGrob(subplots_inPlot)

# #-- (3) create a map of cells in a subplot --#
cells_inSubplot <-
  ggplot() +
  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
  geom_sf(data = ex_cells, fill = NA) +
  theme_void() +
  ggtitle(TeX("$6 \\times 6$ cells")) +
  theme(
    plot.title = element_text(hjust = 0.5, margin = margin(0, 0, 10, 0))
  )

grob_cells_inSubplot <- ggplotGrob(cells_inSubplot)

# #-- (4)put them on the same map --#
g_inset <- ggplot() +
  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)

map_all_together <-
  # /*----------------------------------*/
  #' ##  base maps
  # /*----------------------------------*/
  g_inset +
  # --- plot level --- #
  annotation_custom(grob_plot,
    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1
  ) +
  # --- subplot level --- #
  annotation_custom(grob_subplots_inPlot,
    xmin = 0.57, xmax = 0.67, ymin = 0.3, ymax = 0.8
  ) + # hight is 5
  # --- cell level --- #
  annotation_custom(grob_cells_inSubplot,
    xmin = 0.8, xmax = 1, ymin = 0.5, ymax = 0.7
  ) +
  # xmin = 0.75, xmax = 1, ymin = 0.45, ymax = 0.7) +
  # /*----------------------------------*/
  #' ## add line segments
  # /*----------------------------------*/
  # --- plot-subplot (above) --- #
  # geom_segment(aes(x = 0.386,  xend = 0.55, y = 0.547, yend = 0.73),
  geom_segment(aes(x = 0.387, xend = 0.57, y = 0.534, yend = 0.717),
    lineend = "round", color = "grey",
    size = 1.5
  ) +
  # --- plot-subplot (below) --- #
  # geom_segment(aes(x = 0.386, xend = 0.55, y = 0.5, yend = 0.37),
  geom_segment(aes(x = 0.387, xend = 0.57, y = 0.485, yend = 0.352),
    # data = arrowA,
    lineend = "round", color = "grey",
    size = 1.5
  ) +
  # --- subplot-cell (above) --- #
  # geom_segment(aes(x = 0.65, xend = 0.805, y = 0.64, yend = 0.692),
  geom_segment(aes(x = 0.671, xend = 0.82, y = 0.626, yend = 0.661),
    # data = arrowA,
    lineend = "round", color = "grey",
    size = 1.5
  ) +
  # --- subplot-cell (below) --- #
  geom_segment(aes(x = 0.671, xend = 0.82, y = 0.532, yend = 0.506),
    # data = arrowA,
    lineend = "round", color = "grey",
    size = 1.5
  ) +
  theme_void()

#     theme(plot.margin=unit(c(0,0,0,0),"mm"))

file <- here("GitControlled/Writing/field_structure.png")
ggsave(file)
knitr::plot_crop(file)
dev.off()
```

# Distribution Map of Field Characteristics

## Experimental N design

```{r, dependson = "setup"}
field_Ndesign <-
  ggplot() +
  geom_sf(
    data = field_plot_sf,
    aes(fill = factor(rate)), size = 0,
    inherit.aes = FALSE,
  ) +
  scale_fill_viridis_d() +
  labs(fill = "Nitrogen rate\n  (kg/ha)") +
  theme_void()
```

## Yield map

```{r, dependson = "setup"}
# === cell-level === #
vis_yield_cell <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = yield), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "Yield Level\n  (kg/ha)") +
  theme_void()

# === subplot-level === #
vis_yield_subplot <-
  ggplot(field_subplot_sf) +
  geom_sf(aes(fill = yield), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "Yield Level\n  (kg/ha)") +
  theme_void()
```

## opt_N map

```{r, dependson = "setup"}
# === cell-level === #
vis_optN_cell <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = opt_N), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "EONR (kg/ha)") +
  theme_void()
```

## Field Characteristics Map

```{r, dependson = "setup"}
#### ==== ymax map ====####
field_ymax <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = ymax), size = 0) +
  scale_fill_viridis_c() +
  ggtitle("(1) ymax") +
  labs(fill = "kg/ha") +
  theme_void()

#### ==== alpha map ====####
field_alpha <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = alpha), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(TeX("(2)  $\\alpha$")) +
  # ggtitle(expression("(2) " ~alpha)) +
  theme_void() +
  theme(legend.title = element_blank())

#### ==== beta map ====####
field_beta <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = beta), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(TeX("(3)  $\\beta$")) +
  theme_void() +
  theme(legend.title = element_blank())

#### ==== m_error map ====#### (this should be m_error*det_yield, not just m_error)
# m_error_sf <-  left_join(field, coef_data_m, by="unique_cell_id")

field_m_error <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = yield_error), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(TeX("(4)  $\\epsilon$")) +
  labs(fill = "kg/ha") +
  theme_void()

# grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2, nrow=2)
```

# Results

## Source Results and Preparation

```{r source-results, message=FALSE, warning=FALSE, cache= FALSE}

# ===================================
# Forest results
# ===================================

res_forest_all_honest <-
  here("Shared/Results/Summary_SimRes_Honest_full_tune.rds") %>%
  readRDS()

# ===================================
# CNN results
# ===================================

res_CNN_all <-
  here("Shared/Results/SimRes_CNN_RMSE.rds") %>%
  readRDS()

# /*-------------------------------------------------------*/
#' ## Organize the data
# /*-------------------------------------------------------*/
#--- for reporting the results of  yield prediction and EONR estimation ---#
report_res_allML <-
  rbind(res_forest_all_honest, res_CNN_all) %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF_stepwise", "CF_base"))] %>%
  .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]

report_res_subsetML <-
  report_res_allML %>%
  .[Method != "CF_stepwise", ]
```

# Yield prediction results

## Report RMSE of of Yield Prediction (RF, BRF, CNN)

```{r, dependson = "source-results"}

rmse_y_all <-
  copy(report_res_allML) %>%
  .[Method %in% c("RF", "BRF", "CNN")]

# ==== Distribution of RMSE of predicted yields ====#
plot_dis_y <-
  copy(rmse_y_all) %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN"))] %>%
  ggplot() +
  geom_density(aes(x = rmse_y, fill = Method), alpha = 0.6) +
  facet_wrap(~Model, ncol = 1) +
  labs(x = "RMSE") +
  # labs(x = "Mean R-squared")+
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )

# ==== Summary Table ====#
table_y_prep <-
  copy(rmse_y_all) %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y")

report_table_y <-
  copy(table_y_prep) %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```

# Figure (RMSE of EONR vs RMSE of yield for RF abd BRF)

```{r}
fig_y_optN <-
  rmse_y_all[Method %in% c("RF", "BRF", "CNN")] %>%
  ggplot(aes(x = rmse_y, y = rmse_optN)) +
  geom_point(size = 0.5) +
  facet_grid(Model ~ Method) +
  # geom_smooth(method='lm', se=FALSE,  aes(colour="Regression line"), size=1) +
  # scale_colour_manual(values= "red") +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 1) +
  stat_regline_equation(
    # label.x.npc = "right",
    # label.y.npc = "top",
    label.x = 2150, label.y = 85,
    aes(label = ..rr.label..)
  ) +
  # geom_abline(slope=1, intercept=0, color="red")+
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_blank(),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )

# print(fig_y_optN, preview = "docx")
# dfabline <- data.frame(x = 0:3500, y=0:3500)
```

## Yield Prediction vs EONR estimation : Count Table in terms of profit loss

```{r, dependson = "source-results"}

prepare_count_tab <-
  rmse_y_all %>%
  dcast(sim + Model ~ Method, value.var = c("Mean", "rmse_y")) %>%
  .[, which_ML_y := case_when(
    rmse_y_BRF < rmse_y_RF & rmse_y_BRF < rmse_y_CNN ~ "BRF",
    rmse_y_RF < rmse_y_BRF & rmse_y_RF < rmse_y_CNN ~ "RF",
    rmse_y_CNN < rmse_y_BRF & rmse_y_CNN < rmse_y_RF ~ "CNN"
  )] %>%
  .[, which_ML_piLoss := case_when(
    Mean_BRF < Mean_RF & Mean_BRF < Mean_CNN ~ "BRF",
    Mean_RF < Mean_BRF & Mean_RF < Mean_CNN ~ "RF",
    Mean_CNN < Mean_BRF & Mean_CNN < Mean_RF ~ "CNN"
  )] %>%
  .[, index_cnst_y_piLoss := ifelse(which_ML_piLoss == which_ML_y, 1, 0)] %>%
  .[, ML_cnst_y_piLoss := ifelse(index_cnst_y_piLoss == 1, which_ML_piLoss, NA)]

# === Summary Table === #
summary_res_CNN_RF_BRF <-
  prepare_count_tab %>%
  .[, .(
    count_BRF = nrow(.SD[ML_cnst_y_piLoss == "BRF", ]),
    count_RF = nrow(.SD[ML_cnst_y_piLoss == "RF", ]),
    count_CNN = nrow(.SD[ML_cnst_y_piLoss == "CNN", ]),
    count_y_BRF = nrow(.SD[which_ML_y == "BRF", ]),
    count_y_RF = nrow(.SD[which_ML_y == "RF", ]),
    count_y_CNN = nrow(.SD[which_ML_y == "CNN", ]),
    Total = sum(index_cnst_y_piLoss)
  ), by = Model] %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
  )] %>%
  .[, .(Model, blank1, count_y_RF, count_RF, blank2, count_y_BRF, count_BRF, blank3, count_y_CNN, count_CNN, blank4, Total)]

# === Table creation === #
report_summary_res_CNN_RF_BRF <-
  copy(summary_res_CNN_RF_BRF) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  # set_table_properties(width = .7, layout = "autofit") %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10, 12), width = 0.6) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

# EONR Estimation

```{r, dependson = "source-results"}

# === Distribution of RMSE of EONR estimates === #

plot_dis_optN <-
  copy(report_res_subsetML) %>%
  .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
  .[, Method := case_when(
    # Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF"
  )] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  # .[, Method:=factor(Method, levels = c("RF", "BRF", "CF-stepwise", "CF-base"))]%>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = rmse_optN, fill = Method), alpha = 0.7) +
  # scale_fill_viridis_d()+
  facet_wrap(~Model, ncol = 1) +
  # labs(x = expression(R^2))+
  labs(x = "RMSE (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )

# === Summary Table === #

# --- prepation --- #
table_optN_prep <-
  copy(report_res_subsetML) %>%
  .[, .(
    rmse_optN = mean(rmse_optN),
    pi_loss = mean(Mean)
  ), by = .(Method, Model)] %>%
  .[, `:=`(
    rmse_optN = format(round(rmse_optN, 1), nsmall = 1),
    pi_loss = format(round(pi_loss, 2), nsmall = 2)
  )] %>%
  dcast(Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA, blank5 = NA
  )] %>%
  .[, .(Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]

#- table creation -#
report_table_optN <-
  copy(table_optN_prep) %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  # add_row(.after = 4) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # autofit() %>%
  # width(j = c(2,5,8,11), width=0.3) %>%
  # fix_border_issues()
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

# Profit Loss

## Profit loss summary and distributions
```{r}
piLoss_density <-
  report_res_subsetML[Method != "CNN", ] %>%
  .[, Method := case_when(
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF"
  )] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = Mean, fill = Method), alpha = 0.5) +
  # scale_fill_viridis(discrete = TRUE, alpha=0.5) +
  # scale_fill_viridis_d()+
  # labs(x = expression(hat(pi)["loss"], " $/ha")))+
  labs(x = TeX("$\\hat{pi}_{loss}$ (\\$/ha)")) +
  facet_wrap(~Model, ncol = 1) +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )
```

# Treatment effect comparison (CF-base vs RF vs BRF)

```{r}
#### === The original code for this figure is in "1_3_CompTeEstimation.R" ===####

figure_te <-
  here("Shared/Results/for_writing/dt_TEcomparison.rds") %>%
  readRDS() %>%
  .[, Method := case_when(
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF",
    Method == "CF_base" ~ "CF-base"
  )] %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
  ggplot() +
  geom_point(aes(x = true_tau_base, y = tau_base), size = 0.5) +
  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
  facet_grid(Treatment ~ Method) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = "Estimated Treatment Effect (kg/ha)") +
  labs(x = "True Treatment Effect (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_blank(),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )
```

### 2022-02-06 Writing/CEA_2nd_round/replies_rev_1.rmd
restructuring of the folders and files

--- 2022-02-06 Writing/Re_JournalSubmission/replies_rev_1.rmd
@@
 Therefore, I suggest that the authors revise the first point of the highlight.**
+
 <span style="color:blue">  
+Yes, we agree with your point, and we have decided to simply drop it from our highlights.
 

### 2022-02-06 Writing/CEA_submission/Highlights.rmd
restructuring of the folders and files

---
title: "Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation"
author: Shunkei Kakimoto, Taro Mieno, Takashi S. T. Tanaka, and David S. Bullock
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
    # reference_docx: word_template_format.docx
    # pandoc_args: ["-Fpandoc-crossref"]
bibliography: ML_VRA.bib
csl: computers-and-electronics-in-agriculture.csl
eqnPrefix: 
      - "Eq"
---

# Highlights:

+ Causal Forest is a novel machine learning method focusing on the identification of heterogeneous causal effects of treatment unlike the conventional machine learning methods.

+ Causal Forest outperforms Random Forest, Boosted Random Forest, and Convolutional Neural Network in estimating site-specific EONR.

+ The model's yield prediction accuracy provides little if any information about its EONR prediction accuracy.

### 2022-02-06 Writing/manuscript_cea.rmd
restructuring of the folders and files

--- 2022-02-06 Writing/Re_JournalSubmission/ML_VRA_v2.rmd
@@
 
-```{r echo = F, results='hide', message=FALSE}
+```{r echo = F, include = FALSE}
 library(knitr)
-# library(here)
-
+library(here)
+here::i_am("GitControlled/Writing/manuscript_cea.rmd")
 # opts_knit$set(root.dir = here())
-opts_knit$set(root.dir = "~/Dropbox/ResearchProject/CF_for_VRA")
 
@@
 ```{r analyses, results = "hide", fig.show='hide', cache = FALSE}
-#/*=================================================*/
-#' # Preparation
-#/*=================================================*/
-# This is where you prepare data sets and results 
-# library(here)
-# setwd(here())
-#/*----------------------------------*/
-#' ## Create figures and tablesb
-#/*----------------------------------*/
+# /*=================================================*/
+#' # Create figures and tables
+# /*=================================================*/
 # --- Convert an Rmd file into a pure R file using purl() ---#
-knitr::purl("./GitControlled/Codes/PrepareResults_1.Rmd", output = "./GitControlled/Codes/PrepareResults_1.R")
+knitr::purl(
+  here("GitControlled/Codes/PrepareResults.rmd"),
+  output = here("GitControlled/Codes/PrepareResults.R")
+)
 
 # --- Read the simulation results and prepare figures and tables ---#
-source("./GitControlled/Codes/PrepareResults_1.R")
+source(here("GitControlled/Codes/PrepareResults.R"))
 ```
@@
 
-## Estimating EOIR and Treatment Effects
+## EOIR Estimation and Treatment Effects
 
@@
 While knowledge of the yield function $f(I, \mathbf{c})$ in Eq.
-\@ref(eq:eqn1)) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the _change_ in yield in response to a change in input rate is.
+\@ref(eq:eqn1)) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the "change" in yield in response to a change in input rate is.
 
@@
 CF was developed specifically for identifying heterogeneous treatment effects [@athey2016recursive; @Wager2018a].
-Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf.
-Figure \@ref(fig:ct-ex) shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$)($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
-In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example.
-
-```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
-# knitr::include_graphics("./GitControlled/Writing/Re_JournalSubmission/ctree_ex.pdf")
-readPNG("./GitControlled/Writing/Re_JournalSubmission/ctree_ex.png") %>% grid.raster()
-```
-
-`r ftext('NOTE: The first number in each node indicates the predicted treatment effects (in kg/ha).
-The number and the percentage of observations belonging to the node are shown below that.', fp_text(font.size = 9))`
-
-The first data split criterion is whether the $\textit{ecs}$ value is greater or less than $25$.
-The observations with $\textit{ecs}$ greater than or equal to $25$ move to the left node, while those with $\textit{ecs}$ less than $25$ move to the right.
-For each of the subsamples, the treatment effect is identified as the difference in the mean yields of the treated and control groups within the subsample.
-The treatment effect for the low-$\textit{ecs}$ observations was $619$ kg/ha, and for the high-$\textit{ecs}$ observations was $982$ kg/ha.
-This means that for the impact of the increase in seed rate the treatment effect is heterogeneous over space, having a larger positive impact on yield in high-$\textit{ecs}$ areas.
-Trees are further developed to have more groups of subsamples to allow for more flexible representations of the heterogeneous treatment effects.
-The estimated heterogeneous treatments effects can then be used to identify site-specific EOIRs.
-It is noteworth that at no point CF estimates yield _level_.
+Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf (please see Appendix for an example of a causal tree).
 
@@
 Monte Carlo simulations were conducted for nitrogen experiments for corn production to estimate site-specific EONRs.
-The simulations’ first step generated one thousand synthetic fields that "resembled" an actual field.
+The simulations' first step generated one thousand synthetic fields that "resembled" an actual field.
 Then, for each simulation round, one of the fields was used as a training data set, and another field that is different from the one used as a training data set in that round was used as a validation data set.
@@
 ```{r field-map, out.width="50%", fig.cap = "Partitioning of field into plots, subplots and cells"}
-# knitr::include_graphics("./GitControlled/Writing/Re_JournalSubmission/field_devision_v2.png")
-readPNG("./GitControlled/Writing/Re_JournalSubmission/field_devision_v2.png") %>% grid.raster()
+# knitr::include_graphics("./GitControlled/Writing/field_structure.png")
+readPNG(here("GitControlled/Writing/field_structure.png")) %>% grid.raster()
 ```
@@
 
-```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics"}
+```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics", cache = TRUE}
 # field_alpha + field_beta + field_ymax
-grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2, nrow=2)
+grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol = 2, nrow = 2)
 ```
@@
 
-### Modeling Scenarios
+## Modeling Scenarios
 
@@
 
-### Estimation of Site-specific EONRs by RF, BRF, and CNN
+### Training and Estimation of Site-specific EONRs by RF, BRF, and CNN
 
@@
 The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for RF and BRF modeling.
+RF, BRF, and CF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving honest tree-building process), and the optimal values for these parameters were selected by cross-validation.
+Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same data set was used.
+To reduce the variance of predictions for prediction accuracy, we set the number of trees (*num.trees*) at a high value, $4000$.
 
@@
 
-### Estimation of Site-specific EONRs by CF
+### Training and Estimation of Site-specific EONRs by CF
 
@@
 
-With the treatment effects from the base obtained, site-specific EONRs were identified by finding the N rate resulting in the highest profit.
+With the treatment effects from the base obtained, site-specific EONRs were identified by finding the N rate resulting in the highest profit for each $i$.
 Yield levels were not predicted at any point in the CF-based approaches.
-
-RF, BRF, and CF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving honest tree-building process), and the optimal values for these parameters were selected by cross-validation.
-It was also necessary to set the number of trees grown in a forest (*num.trees*).
-Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same data set was used.
-To reduce the variance of predictions for prediction accuracy, we needed to assign *num.trees* a high value, $4000$.
 
@@
 This is understandable, since whereas yield can be "ground-truthed" the true causal impact of a treatment cannot be determined from real-world data, making it impossible to cross-validate EONR.
-However, the simulation results reported here show clearly that using a model’s yield prediction accuracy as a model selection criterion is not well justified if the ultimate objective is accurate estimation of site-specific EONRs.
+However, the simulation results reported here show clearly that using a model's yield prediction accuracy as a model selection criterion is not well justified if the ultimate objective is accurate estimation of site-specific EONRs.
 
@@
 CF-base consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation.
-We also showed that the model’s yield prediction accuracy was uncorrelated with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map.
+We also showed that the model's yield prediction accuracy was uncorrelated with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map.
 
@@
 <div id="refs"></div>
+
+\newpage
+
+# (APPENDIX) Appendix {-}
+
+# Appendix A: Causal Tree Example {-}
+
+Figure \@ref(fig:ct-ex) shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$)($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
+In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example.
+
+```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
+# knitr::include_graphics("./GitControlled/Writing/ctree_ex.pdf")
+readPNG(here("GitControlled/Writing/ctree_ex.png")) %>% grid.raster()
+```
+
+`r ftext('NOTE: The first number in each node indicates the predicted treatment effects (in kg/ha).
+The number and the percentage of observations belonging to the node are shown below that.', fp_text(font.size = 9))`
+
+The first data split criterion is whether the $\textit{ecs}$ value is greater or less than $25$.
+The observations with $\textit{ecs}$ greater than or equal to $25$ move to the left node, while those with $\textit{ecs}$ less than $25$ move to the right.
+For each of the subsamples, the treatment effect is identified as the difference in the mean yields of the treated and control groups within the subsample.
+The treatment effect for the low-$\textit{ecs}$ observations was $619$ kg/ha, and for the high-$\textit{ecs}$ observations was $982$ kg/ha.
+This means that for the impact of the increase in seed rate the treatment effect is heterogeneous over space, having a larger positive impact on yield in high-$\textit{ecs}$ areas.
+Trees are further developed to have more groups of subsamples to allow for more flexible representations of the heterogeneous treatment effects.
+The estimated heterogeneous treatments effects can then be used to identify site-specific EOIRs.
+It is noteworth that at no point CF estimates yield "level".

### 2022-02-06 Codes/PrepareResults.R

@@ -1,0 +1,672 @@
+## ----set-up, cache = F-----------------------------
+library(knitr)
+library(here)
+
+here::i_am("GitControlled/Writing/manuscript_cea.rmd")
+
+knitr::opts_chunk$set(
+  cache = TRUE,
+  warning = FALSE,
+  message = FALSE
+)
+
+
+## ----packages, cache = FALSE, include = FALSE------
+# === packages ===#
+# --- data wrangling--- #
+library(sf)
+library(data.table)
+library(tidyverse)
+
+# --- figure making --- #
+library(RColorBrewer)
+library(patchwork)
+library(ggplot2)
+library(ggthemes)
+library(viridis)
+library(ggpubr)
+library(gridExtra)
+library(DiagrammeR)
+
+# --- table making --- #
+library(flextable)
+library(officer)
+library(officedown)
+library(modelsummary)
+library(latex2exp)
+
+
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE----
+# field <- readRDS("Shared/Data/for_Simulations/field_padding.rds") %>%
+#     filter(padding==1)%>%
+#     dplyr::select(unique_cell_id)
+
+# === plot-level field data set  === #
+field_plot_sf <-
+  here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
+  readRDS()
+
+# === subplot-level field data set  === #
+field_subplot_sf <-
+  here("Shared/Results/for_writing/sample_field_subplot_sf.rds") %>%
+  readRDS()
+
+# === cell-level field data set  === #
+field_cell_sf <-
+  here("Shared/Results/for_writing/sample_field_cell_sf.rds") %>%
+  readRDS()
+
+
+## --------------------------------------------------
+variogram_tb <-
+  data.frame(
+    Parameters = c("ymax_ij", "alpha_ij", "beta_ij", "varepsilon_ij"),
+    Range = c(400, 400, 400, 400),
+    Mean = c(12000, -0.5, format(c(0, 0))),
+    Nugget = format(c(0, 0, 0, 0)),
+    Sill = c(2000000, 0.02, format(1, nsmall = 1), 0.015)
+  ) %>%
+  flextable() %>%
+  compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sup(as_i("i,j")))) %>%
[…]

### 2022-02-06 Codes/PrepareResults_0.R

@@ -1,146 +1,0 @@
-# ==========================================================================
-# Prepare field data set for writing
-# ==========================================================================
-#' Objective:
-#' + create field data sets by cells, subplots, and plots
-#' + create a figure of an example causal tree 
-
-
-library(here)
-library(sf)
-library(data.table)
-library(ggplot2)
-library(ggthemes)
-library(viridis)
-library(tidyverse)
-library(ggpubr)
-library(grf)
-
-source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")
-
-
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-
-# /*=================================================*/
-#' # Field Data Sets
-# /*=================================================*/
-
-#/*----------------------------------*/
-#' ## (1) cell-level data set 
-#/*----------------------------------*/
-# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
-field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
-
-coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))
-
-x=1
-coef_data_m <- coef_data[sim == x, ]
-coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
-
-
-sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
-	.$reg_raw_data
-
-field_cell_sf <- 
-	left_join(select(field, unique_cell_id), field_cell_dt, by="unique_cell_id")%>%
-    na.omit() %>%
-    mutate(plot_id = ceiling(subplot_id/4)) %>%
-    filter(padding==1)
-   
-saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))
-
-
-#/*----------------------------------*/
-#' ## (2) subplot-level field without padding area 
-#/*----------------------------------*/
-
-field_subplot_sf <- 
-	field_cell_sf %>%
-	group_by(subplot_id, strip_id) %>%
-	summarise(
[…]

### 2022-02-06 Codes/PrepareResults_1.R

@@ -1,622 +1,0 @@
-## -----------------------------------------------------------------------------
-library(knitr)
-# library(here)
-
-knitr::opts_chunk$set(
-    cache = FALSE,
-    warning = FALSE,
-    message = FALSE
-    )
-
-# opts_knit$set(root.dir=here())
-opts_knit$set(root.dir = "~/Dropbox/ResearchProject/ML_VRA")
-
-
-## ---- cache = FALSE-----------------------------------------------------------
-# === packages ===#
-# --- data wrangling--- #
-library(sf)
-library(data.table)
-library(tidyverse)
-
-# --- figure making --- #
-library(RColorBrewer)
-library(patchwork)
-library(ggplot2)
-library(ggthemes)
-library(viridis)
-library(ggpubr)
-library(gridExtra)
-library(DiagrammeR)
-
-# --- table making --- #
-library(flextable)
-library(officer)
-library(officedown)
-library(modelsummary)
-library(latex2exp)
-
-
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE------------------------
-# field <- readRDS("./Shared/Data/for_Simulations/field_padding.rds") %>%
-#     filter(padding==1)%>%
-#     dplyr::select(unique_cell_id)
-
-
-# === plot-level field data set  === #
-field_plot_sf <- readRDS("./Shared/Results/for_writing/sample_field_plot_sf.rds")
-# === subplot-level field data set  === #
-field_subplot_sf <- readRDS("./Shared/Results/for_writing/sample_field_subplot_sf.rds")
-# === cell-level field data set  === #
-field_cell_sf <- readRDS("./Shared/Results/for_writing/sample_field_cell_sf.rds")
-
-
-## -----------------------------------------------------------------------------
-variogram_tb <- data.frame(
-    Parameters = c("ymax_ij", "alpha_ij", "beta_ij", "varepsilon_ij"),
-    Range = c(400, 400, 400, 400),
-    Mean = c(12000, -0.5, format(c(0,0))),
-    Nugget = format(c(0, 0, 0, 0)),
-    Sill =c(2000000, 0.02, format(1, nsmall = 1), 0.015)
-    ) %>%
-    flextable() %>%
-    compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sup(as_i("i,j")))) %>%
[…]

### 2022-02-06 Codes/knit_manuscript.R

@@ -1,0 +1,1 @@
+rmarkdown::render(here::here("GitControlled/Writing/manuscript_cea.rmd"))

### 2022-02-06 Codes/PrepareResults.rmd
add Ctree

@@
 ```
+
+```{r}
+# /*=================================================*/
+#' # Sample CT figure (cach)
+# /*=================================================*/
+
+library(causalTree)
+library(here)
+library(rpart)
+library(rattle)
+
+data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
+    na.omit() %>%
+    dplyr::rename(tgtn=NPlan,tgts=SRPlan)
+
+data_dt <- data.table(data_sf) %>%
+    setnames(names(.),tolower(names(.)))
+
+tgts_ls <- data_dt[,tgts] %>% unique() %>% sort
+
+ctree_data <- copy(data_dt) %>%
+  .[tgts %in% tgts_ls[1:2],] %>%
+  .[,treat:=ifelse(tgts==tgts_ls[2],1,0)] %>%
+  #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
+  .[,yield:= yield*62.77]
+
+tree <- causalTree(
+  yield ~ slope+ecs,
+  data = ctree_data,
+  treatment = ctree_data$treat,
+  split.Rule = "CT",
+  cv.option = "CT",
+  split.Honest = T,
+  cv.Honest = T,
+  split.Bucket = F,
+  xval = 5,
+  cp = 0,
+  minsize = 20,
+  propensity = 0.5
+)
+
+opcp <- tree$cptable[,1][which.min(tree$cptable[,4])]
+opfit <- prune(tree, opcp)
+
+# pdf(here("GitControlled/Writing/JournalSubmission/ctree_ex.png"))
+fancyRpartPlot(opfit,sub='')
+# dev.off()
+```

### 2022-02-06 Codes/PrepareResults.R

@@ -1,4 +1,4 @@
-## ----set-up, cache = F-----------------------------
+## ----set-up, cache = F------------------------------------------------------------------------
 library(knitr)
 library(here)
 
@@ -11,7 +11,7 @@ knitr::opts_chunk$set(
 )
 
 
-## ----packages, cache = FALSE, include = FALSE------
+## ----packages, cache = FALSE, include = FALSE-------------------------------------------------
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -36,7 +36,7 @@ library(modelsummary)
 library(latex2exp)
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE----
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE----------------------------------------
 # field <- readRDS("Shared/Data/for_Simulations/field_padding.rds") %>%
 #     filter(padding==1)%>%
 #     dplyr::select(unique_cell_id)
@@ -57,7 +57,7 @@ field_cell_sf <-
   readRDS()
 
 
-## --------------------------------------------------
+## ---------------------------------------------------------------------------------------------
 variogram_tb <-
   data.frame(
     Parameters = c("ymax_ij", "alpha_ij", "beta_ij", "varepsilon_ij"),
@@ -96,7 +96,7 @@ variogram_tb <-
   autofit()
 
 
-## ----field-map-visualization, dependson = "setup"----
+## ----field-map-visualization, dependson = "setup"---------------------------------------------
 
 # == plot-level field without padding area ==##
 vis_field_plot <-
@@ -216,7 +216,7 @@ knitr::plot_crop(file)
 dev.off()
 
 
-## ---- dependson = "setup"--------------------------
+## ---- dependson = "setup"---------------------------------------------------------------------
 field_Ndesign <-
   ggplot() +
   geom_sf(
@@ -229,7 +229,7 @@ field_Ndesign <-
   theme_void()
 
 
-## ---- dependson = "setup"--------------------------
+## ---- dependson = "setup"---------------------------------------------------------------------
 # === cell-level === #
 vis_yield_cell <-
   ggplot(field_cell_sf) +
@@ -247,7 +247,7 @@ vis_yield_subplot <-
   theme_void()
 
 
-## ---- dependson = "setup"--------------------------
+## ---- dependson = "setup"---------------------------------------------------------------------
 # === cell-level === #
 vis_optN_cell <-
   ggplot(field_cell_sf) +
[…]

### 2022-02-06 Codes/PrepareResults.rmd
ctree added to manuscript

--- 2022-02-06 Codes/PrepareResults.rmd
@@
 ```
+
+```{r}
+# /*=================================================*/
+#' # Sample CT figure (cach)
+# /*=================================================*/
+
+library(causalTree)
+library(here)
+library(rpart)
+library(rattle)
+
+data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
+  na.omit() %>%
+  dplyr::rename(tgtn = NPlan, tgts = SRPlan)
+
+data_dt <- data.table(data_sf) %>%
+  setnames(names(.), tolower(names(.)))
+
+tgts_ls <- data_dt[, tgts] %>%
+  unique() %>%
+  sort()
+
+ctree_data <- copy(data_dt) %>%
+  .[tgts %in% tgts_ls[1:2], ] %>%
+  .[, treat := ifelse(tgts == tgts_ls[2], 1, 0)] %>%
+  #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
+  .[, yield := yield * 62.77]
+
+tree <- causalTree(
+  yield ~ slope + ecs,
+  data = ctree_data,
+  treatment = ctree_data$treat,
+  split.Rule = "CT",
+  cv.option = "CT",
+  split.Honest = T,
+  cv.Honest = T,
+  split.Bucket = F,
+  xval = 5,
+  cp = 0,
+  minsize = 20,
+  propensity = 0.5
+)
+
+opcp <- tree$cptable[, 1][which.min(tree$cptable[, 4])]
+opfit <- prune(tree, opcp)
+```

### 2022-02-06 Writing/manuscript_cea.rmd
ctree added to manuscript

@@
 ```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
-# knitr::include_graphics("./GitControlled/Writing/ctree_ex.pdf")
-readPNG(here("GitControlled/Writing/ctree_ex.png")) %>% grid.raster()
+fancyRpartPlot(opfit, sub = "")
 ```

### 2022-02-06 Codes/PrepareResults.rmd
add sample field data

--- 2022-02-06 Codes/PrepareResults.rmd
@@
 ```
+
+```{r}
+source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")
+
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+# /*=================================================*/
+#' # Field Data Sets
+# /*=================================================*/
+
+#/*----------------------------------*/
+#' ## (1) cell-level data set 
+#/*----------------------------------*/
+# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
+field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
+
+coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))
+
+x=1
+coef_data_m <- coef_data[sim == x, ]
+coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
+
+sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
+  .$reg_raw_data
+
+field_cell_sf <- 
+  left_join(select(field, unique_cell_id), field_cell_dt, by="unique_cell_id")%>%
+    na.omit() %>%
+    mutate(plot_id = ceiling(subplot_id/4)) %>%
+    filter(padding==1)
+
+saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))
+
+#/*----------------------------------*/
+#' ## (2) subplot-level field without padding area 
+#/*----------------------------------*/
+
+field_subplot_sf <- 
+  field_cell_sf %>%
+  group_by(subplot_id, strip_id) %>%
+  summarise(
+    sim = mean(sim),
+      yield = mean(yield),
+      opt_N = mean(opt_N),
+      rate = mean(rate),
+      aa_n = mean(aa_n), 
+      alpha = mean(alpha),
+      beta = mean(beta),
+      ymax = mean(ymax),
+      alpha1 = mean(alpha1),
+      alpha2 = mean(alpha2),
+      beta1 = mean(beta1),
+      beta2 = mean(beta2),
+      ymax1 = mean(ymax1),
+      ymax2 = mean(ymax2),
+      theta_1 = mean(theta_1),
+      theta_2 = mean(theta_2)
+  ) %>%
+  mutate(unique_subplot_id = paste0(strip_id,"_",subplot_id))%>%
+  select(!c(strip_id, subplot_id))
+
+saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
+```

### 2022-02-06 Codes/PrepareResults.rmd

@@
   na.omit() %>%
-    dplyr::rename(tgtn=NPlan,tgts=SRPlan)
+  dplyr::rename(tgtn = NPlan, tgts = SRPlan)
 
 data_dt <- data.table(data_sf) %>%
-    setnames(names(.),tolower(names(.)))
+  setnames(names(.), tolower(names(.)))
 
-tgts_ls <- data_dt[,tgts] %>% unique() %>% sort
+tgts_ls <- data_dt[, tgts] %>%
+  unique() %>%
+  sort()
 
 ctree_data <- copy(data_dt) %>%
-  .[tgts %in% tgts_ls[1:2],] %>%
-  .[,treat:=ifelse(tgts==tgts_ls[2],1,0)] %>%
+  .[tgts %in% tgts_ls[1:2], ] %>%
+  .[, treat := ifelse(tgts == tgts_ls[2], 1, 0)] %>%
   #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
-  .[,yield:= yield*62.77]
+  .[, yield := yield * 62.77]
 
 tree <- causalTree(
-  yield ~ slope+ecs,
+  yield ~ slope + ecs,
   data = ctree_data,
@@
 
-opcp <- tree$cptable[,1][which.min(tree$cptable[,4])]
+opcp <- tree$cptable[, 1][which.min(tree$cptable[, 4])]
 opfit <- prune(tree, opcp)
-
-# pdf(here("GitControlled/Writing/JournalSubmission/ctree_ex.png"))
-fancyRpartPlot(opfit,sub='')
-# dev.off()
 ```

### 2022-02-06 Codes/PrepareResults.rmd
set figure options

--- 2022-02-06 Codes/PrepareResults.rmd
@@
 library(latex2exp)
+```
+
+# Set the figure options
+```{r figure_setup, cache = F}
+theme_update(
+  axis.title.x =
+    element_text(
+      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain"
+    ),
+  axis.title.y =
+    element_text(
+      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain"
+    ),
+  axis.text.x =
+    element_text(
+      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain"
+    ),
+  axis.text.y =
+    element_text(
+      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"
+    ),
+  axis.ticks =
+    element_line(
+      size = 0.3, linetype = "solid"
+    ),
+  axis.ticks.length = unit(.15, "cm"),
+  #--- legend ---#
+  legend.text =
+    element_text(
+      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
+    ),
+  legend.title =
+    element_text(
+      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
+    ),
+  legend.key.size = unit(0.5, "cm"),
+  #--- strip (for faceting) ---#
+  strip.text = element_text(size = 10),
+  #--- plot title ---#
+  plot.title = element_text(family = "Times", face = "bold", size = 12),
+  #--- margin ---#
+  # plot.margin = margin(0, 0, 0, 0, "cm"),
+  #--- panel ---#
+  panel.grid.major = element_blank(),
+  panel.grid.minor = element_blank(),
+  panel.background = element_blank(),
+  panel.border = element_rect(fill = NA)
+)
 ```
@@
 ```
+
+```{r}
+source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")
+
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+# /*=================================================*/
+#' # Field Data Sets
+# /*=================================================*/
+
+# /*----------------------------------*/
+#' ## (1) cell-level data set
+# /*----------------------------------*/
+# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
+field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
+
+coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))
+
+x <- 1
+coef_data_m <- coef_data[sim == x, ]
+coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
+
+sample_dt_cell <- prepare_raw_data(x, field = field, coef_data_m = coef_data_m, coef_data_t = coef_data_t, app_error = "no") %>%
+  .$reg_raw_data
+
+field_cell_sf <-
+  left_join(select(field, unique_cell_id), field_cell_dt, by = "unique_cell_id") %>%
+  na.omit() %>%
+  mutate(plot_id = ceiling(subplot_id / 4)) %>%
+  filter(padding == 1)
+
+saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))
+
+# /*----------------------------------*/
+#' ## (2) subplot-level field without padding area
+# /*----------------------------------*/
+
+field_subplot_sf <-
+  field_cell_sf %>%
+  group_by(subplot_id, strip_id) %>%
+  summarise(
+    sim = mean(sim),
+    yield = mean(yield),
+    opt_N = mean(opt_N),
+    rate = mean(rate),
+    aa_n = mean(aa_n),
+    alpha = mean(alpha),
+    beta = mean(beta),
+    ymax = mean(ymax),
+    alpha1 = mean(alpha1),
+    alpha2 = mean(alpha2),
+    beta1 = mean(beta1),
+    beta2 = mean(beta2),
+    ymax1 = mean(ymax1),
+    ymax2 = mean(ymax2),
+    theta_1 = mean(theta_1),
+    theta_2 = mean(theta_2)
+  ) %>%
+  mutate(unique_subplot_id = paste0(strip_id, "_", subplot_id)) %>%
+  select(!c(strip_id, subplot_id))
+
+saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
+```

### 2022-02-07 Codes/PrepareResults.rmd
made significant modifications to the manuscript and response to reviewers

@@
 knitr::opts_chunk$set(
-  cache = TRUE,
-  warning = FALSE,
-  message = FALSE
+  cache = TRUE
 )
 ```
-
 ```{r packages, cache = FALSE, include = FALSE}
@@
 
-library(causalTree)
-library(here)
-library(rpart)
-library(rattle)
-
 data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
@@
 ```
-
-```{r}
-source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")
-
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-# /*=================================================*/
-#' # Field Data Sets
-# /*=================================================*/
-
-# /*----------------------------------*/
-#' ## (1) cell-level data set
-# /*----------------------------------*/
-# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
-field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
-
-coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))
-
-x <- 1
-coef_data_m <- coef_data[sim == x, ]
-coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
-
-sample_dt_cell <- prepare_raw_data(x, field = field, coef_data_m = coef_data_m, coef_data_t = coef_data_t, app_error = "no") %>%
-  .$reg_raw_data
-
-field_cell_sf <-
-  left_join(select(field, unique_cell_id), field_cell_dt, by = "unique_cell_id") %>%
-  na.omit() %>%
-  mutate(plot_id = ceiling(subplot_id / 4)) %>%
-  filter(padding == 1)
-
-saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))
-
-# /*----------------------------------*/
-#' ## (2) subplot-level field without padding area
-# /*----------------------------------*/
-
-field_subplot_sf <-
-  field_cell_sf %>%
-  group_by(subplot_id, strip_id) %>%
-  summarise(
-    sim = mean(sim),
-    yield = mean(yield),
-    opt_N = mean(opt_N),
-    rate = mean(rate),
-    aa_n = mean(aa_n),
-    alpha = mean(alpha),
-    beta = mean(beta),
-    ymax = mean(ymax),
-    alpha1 = mean(alpha1),
-    alpha2 = mean(alpha2),
-    beta1 = mean(beta1),
-    beta2 = mean(beta2),
-    ymax1 = mean(ymax1),
-    ymax2 = mean(ymax2),
-    theta_1 = mean(theta_1),
-    theta_2 = mean(theta_2)
-  ) %>%
-  mutate(unique_subplot_id = paste0(strip_id, "_", subplot_id)) %>%
-  select(!c(strip_id, subplot_id))
-
-saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
-```

### 2022-02-07 Writing/CEA_2nd_round/replies_rev_1.rmd
made significant modifications to the manuscript and response to reviewers

@@
 
+We have moved an example of causal tree (previously in seciton 2.3), but decide to keep the explanation of how CF works.
 The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations.
@@
 
-We talk about identifying site-specific economically optimal input rates in three different places.
-However, each of them serves distinctive purposes and we would like to keep the current structure if that is acceptable to you.
-
-Section 2.1: bluh bluh
-Section 3.: true optimal N
-Section 3.: estiamted optimal N
-
 </span>
@@
 <span style="color:blue">
-We first apologogize that misleading section and subsection titles may have caused confusions about your perceived structural redundancy of this article.
 
-We wrote the initial manuscript with avoiding redundancy in mind and we beleived that we did not have any redundancy in our paper.
-Therefore, we struggled tremendously to see where the redundancies are.
-We would really appreciate it if you could specify where you see redundancies and why so that we can address prorperly.
+In rereponse to this comments, we made several changes.
+
+First, we consolidated 3.1.2 and 3.1.3 in the previous round into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we dropped detailed explanation of the conceptual framework behind the yield response functions based on cell-leve characteristics, $c_i$, and moved it to the supplemnentary appendix (Appendix B).
+We also removed our detailed description of how parameters and error term were generated and moved it to Appendix C along with relevant tables and figures (spefically table x and figures x, y, z) <span style = "color: blue;"> Shun put table and figure numbers here </span>.
+
+Second, we consolidated 3.1.4 and 3.1.5 in the previous round into a single subsubsection called "Trial Design and Yield Data Generation for Modeling." In doing so, we cut some texts and combined figure x and y in the previous round into a single figure (figure x in the current manuscript).
+
+Third, we removed detailed description of how some parameters are splitted into two parts and moved it to the Appendix.
 
@@
 It is much like any emprical studies using real experiment data provides lots of details about the experiemnts.
-We take reproducibility seriously and we believe that the details we peovided in our manuscript is appropriate.
-Therefore, we had very hard time telling which is unnecessary and not.
-We would really appreciate it if you could specify which parts are not critical.
+We take reproducibility seriously and we believe that the details we peovided in our current manuscript is appropriate and it is hard for us to further slim down the section.
+Moreover, we believe we no longer have any redundancy in this section any more.
 
@@
 
-+ I provided the unit in the text. It is degree.
+It is degree. The unit is now provided in Appendix A.
 
@@
 
-+ I added the explanation for those numbers as a footnote in the figure. 
+The explanation for those numbers are added as a footnote to the figure (Figure <span style = "color: blue;"> Shun, figure number </span>). 
 </span>
@@
 **6. Some formulas in the manuscript are not numbered (lines 116, 120, 268, 291, 371, 389).**
+
 <span style="color:blue">  
-
-+ I numbered all the formulas. 
+All the formulas are now numbered. 
 </span>
@@
 
-+ I modified this sentence "For each simulated field, we generated a training data set and a validation data set." For each simulation round, one of the fields was used as a training data set, and another field that is different from the one used as a training data set in that round was used as a validation data set.
+We aplogogize that we are not clear on this respect.
+
+Trainign dataset and test dataset are completely separate.
+Models are trained on the entirety of the train data for each simulation, and then the trained model is tested against a test dataset that are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$.
+The train dataset, however, was split into several parts when cross-validation was performed in determing the optimal hyperparameters at each simulation round.
+
+We added the following paragraph to section <span style = "color: blue;"> Shun section number here </span> to make this point clear.
+
+"For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset.
+For example, for simulation number 1, train dataset from simulation number 2 was used as the test dataset.
+This process works because the train datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$).
+Furtehr, each of the "train" datasets are generated independet of one another.
+Thefore, for a particular simulation round, the dataset in any of the other simualtions can serve as a valid test dataset.
+This practice avoid creating another set of 1000 simulations fields unnecessarily."
 
@@
 Please generate a separate DOI for your code and cite it.**
+
 <span style="color:blue">  
-+ I uploaded to the simulation codes and the data on Mendeley Data. The link is suggested on section 3: Materials and Methods.
+We realized that the github repository was private and that was why you were not able to access it. We made a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).
+
+The simulation codes and the data were also shared on Mendeley Data (<span style = "color: blue;"> Shun, provide the link here </span>) according to the Editor's suggestion for the ease of access.
+The link is also provided <span style = "color: blue;"> Shun, be speficic about where it is </span>.
 
@@
 
-+ I converted to those units to meter (m)
+All the lenth units were converted to meter (m)
 
@@
 
-+ I updated Figure 2. The number of rows and columns of plots, subplots, and cells schematics are indicated each map in Figure 2.
+The number of rows and columns of plots, subplots, and cells schematics are now indicated Figure 2.
 </span>
@@
 **11. The titles of sections 3.2.1 and 3.2.2 do not provide useful information to the readers, please revise the titles. (lines 342 and 373)**
+
 <span style="color:blue">  
-
-+ I changed the title of section 3.2 to "Training Models and Estimating Site-specific EONRs".
-Further, I revised the title of sections 3.2.1 and 3.2.2 to "Estimation of site-specific EONRs by RF, BRF, and CNN" and "Estimation of site-specific EONRs by CF", respectively.
+We realized that section 3.1 has also a bad title.
+Therefore, we changed it to "Training Models and Estimating Site-specific EONRs".
+Further, the title of sections 3.2.1 and 3.2.2 were changed to "Estimation of site-specific EONRs by RF, BRF, and CNN" and "Estimation of site-specific EONRs by CF", respectively.
 </span>
@@
 
-+ I changed the title of section 4.2 to "The relationships between yield prediction performance and EONR prediction performance". 
+The title of 4.1 was changed to "Comparison of EONR estimation accuracy" to reflect its contents.
+The title of section 4.2 was changed to "The relationship between yield and EONR prediction performances".
 </span>
@@
 **15. Please add a separate section for research gaps or uncertainties. Are there any prerequisite assumptions for using the CF model?**
+
 <span style="color:blue">

### 2022-02-07 Writing/appendix.rmd
made significant modifications to the manuscript and response to reviewers

--- 2022-02-06 Writing/manuscript_cea.rmd
@@
----
-title: "Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation"
-author: Shunkei Kakimoto^[Corresponding author, Department of Agricultural Economics, University of Nebraska-Lincoln 102 Filley Hall 1625 Arbor Drive Lincoln, NE 68583, USA, E-mail address; skakimoto3@hunskers.unl.edu], Taro Mieno^[Department of Agricultural Economics, University of Nebraska-Lincoln, Lincoln, NE 68583, USA], Takashi S.
-T.
-Tanaka^[Artificial Intelligence Advanced Research Center, Faculty of Applied Biological Sciences, Gifu University, Gifu 501-1193, Japan], and David S.
-Bullock^[Department of Agricultural and Consumer Economics, University of Illinois, Urbana, IL 61801, USA]
-output:
-  bookdown::word_document2:
-    fig_caption: yes
-    number_sections: yes
-    global_numbering: true
-    # reference_docx: word_template.docx
-    reference_docx: word_template_format.docx
-    # pandoc_args: ["-Fpandoc-crossref"]
-bibliography: ML_VRA.bib
-csl: computers-and-electronics-in-agriculture.csl
-eqnPrefix: 
-      - "Eq"
-abstract: "Estimating site-specific crop yield response to changes in input (e.g., seed, fertilizer) management is a critical step in making economically optimal site-specific input recommendations.
-Past studies have attempted to estimate yield response functions using various Machine Learning (ML) methods, including the Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN) methods.
-This study proposes use of the Causal Forest (CF) model, which is one of the emerging ML methods that comprise \"Causal Machine Learning.\" Unlike previous yield-prediction-oriented ML methods, CF focuses strictly on estimating heterogeneous treatment effects (changes in yields that result from changes in input application rates) of inputs.
-We report results of using Monte Carlo simulations assuming various production scenarios to test the effectiveness of CF in estimating site-specific economically optimal nitrogen rates (EONRs), comparing CF with the yield-prediction-oriented ML methods RF, BRF, and CNN.
-CF's estimations of site-specific EONRs were superior under all scenarios considered.
-Furthermore, we also show that the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions."
----
-
-```{r echo = F, include = FALSE}
-library(knitr)
-library(here)
-here::i_am("GitControlled/Writing/manuscript_cea.rmd")
-# opts_knit$set(root.dir = here())
-
-options(htmltools.dir.version = FALSE)
-options(knitr.duplicate.label = "allow")
-
-opts_chunk$set(
-  fig.align = "center",
-  fig.retina = 5,
-  warning = F,
-  message = F,
-  cache = FALSE, # <-- T
-  cache.lazy = FALSE,
-  echo = F
-)
-```
-
-```{r, cache = FALSE}
-# === packages ===#
-library(tidyverse)
-library(data.table)
-
-library(png)
-library(RColorBrewer)
-library(patchwork)
-library(plotly)
-library(magrittr)
-library(ggplot2)
-library(viridis)
-library(tmap)
-library(ggthemes)
-library(mgcv)
-library(ggpubr)
-library(flextable)
-library(officer)
-library(officedown)
-library(modelsummary)
-library(raster)
-library(bookdown)
-library(png)
-library(grid)
-```
-
-```{r analyses, results = "hide", fig.show='hide', cache = FALSE}
-# /*=================================================*/
-#' # Create figures and tables
-# /*=================================================*/
-# --- Convert an Rmd file into a pure R file using purl() ---#
-knitr::purl(
-  here("GitControlled/Codes/PrepareResults.rmd"),
-  output = here("GitControlled/Codes/PrepareResults.R")
-)
-
-# --- Read the simulation results and prepare figures and tables ---#
-source(here("GitControlled/Codes/PrepareResults.R"))
-```
-
-# Keywords: {-}
-
-site-specific input management, nitrogen rate, on-farm precision experimentation, machine learning, causal forest, economically optimal input rates
-
-# Introduction
-
-Information about crop yield response input management is critical for the identification of site-specific economically optimal input rates (EOIRs) [@bullock1998does], and the difficulty in estimating site-specific yield response functions accurately within a field is the primary explanation of the persistent relatively low the adoption rate of variable rate crop input application technology [@lowenberg2019setting].
-Historically, site-specific yield response functions have been estimated using the data generated from strip trials conducted on only parts of fields [@makowski2001statistical; @scharf2002corn; @bullock2002adding; @mamo2003spatial; @hurley2004estimating; @anselin2004spatial; @scharf2005field; @ruffo2006site; @Miao2006; @puntel2019development].
-But recently whole-field on-farm precision experimentation (OFPE) [@bullock2019] has allowed implementation of improved statistical experimental designs (e.g., Latin Square, Randomized Block) on entire fields [@laurent_kyveryga_makowski_miguez_2019; @licht_witt_2019].
-Data generated from whole-field OFPEs typically have greater local variation in experimental input application rates and soil/field characteristics than do strip trial designs, which has improved the statistical identification of heterogeneous impacts of input management changes on yields.
-The resultant availability of more spatially detailed experiment data has encouraged a resurgence of interest in estimating site-specific yield response functions.
-For example, @barbosa2020modeling, @krause2020random and @Gardner21 used OFPE data to estimate site-specific yield response functions and economically optimal site-specific N fertilizer and/or seed rates.
-These recent studies used machine learning (ML) methods extensively in place of more traditional parametric modeling approaches.
-@barbosa2020modeling applied the Convolutional Neural Network approach, @krause2020random used Random Forest-based approaches, and @Gardner21 used the shape-constrained generalized additive model.
-But this trend of applying ML methods may raises concerns.
-Historically, agronomists have worked meticulously to develop clever experimental designs to identify causes of yield response to input management.
-But the aforementioned recent applications of ML methodologies pay little attention to identify such causes, instead attempting to validate their models by estimating yield prediction accuracy.
-But the ultimate goal of OFPE is the accurate prediction of EOIRs, not yields.
-These are distinct objectives, and achievement of one need not imply the other.
-
-The lack of and need for causal interpretation of the results of ML research applications have been increasingly recognized, in particular in economics and medicine [@athey2017beyond; @athey2018impact; @Athey2019a; @moraffah2020causal; @Storm2020; @arti2020research; @scholkopf2021toward], and causal machine learning (CML) methods were recently developed in response.
-Unlike traditional prediction-oriented ML methods, CML focuses on identifying causal impacts of an event (in our context, of an increase or decrease in the input application rate).
-The growing academic literature applying CML methods includes @richens2020improving, who's medical research pointed out that the inability of the traditional ML methods to identify cause-and-effect relationships between disease and patients' characteristics could lead to misdiagnoses, and showed that CML-based diagnoses could improve the accuracy of diagnostic prediction.
-In addition, @carbo2020machine used a CML to identify characteristics causing bank customers to adopt online banking services, and @bozorgi2020process applied CML to study the mining processes.
-
-In this paper, we use the Causal Forest (CF) approach developed by @athey2016recursive and @Wager2018a to examine the accuracy of methods that estimate site-specific economically optimal N fertilizer rates (EONRs).
-We compare the EONR prediction performances of our CF-based approach to the widely used ML methods Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN), and we examine how yield prediction performance is related to EONR prediction performance, which allow us to examine whether model selection should be based on yield prediction accuracy when the ultimate goal is EOIR identifying.
-We use Monte Carlo simulations in which we synthetically generate yield and soil/field characteristics datasets to create stylized "field." Because real-world "true" EOIRs are unobservable, real-world data cannot be used to test the accuracy of statistical methods estimating EOIRs.
-This important difference contrasts starkly with yield prediction, since actual yields can be ground-truthed.
-
-# Predicting Yield vs. Predicting Changes in Yield in Response to Changes in Input Management
-
-In the following, we describe the fundamental information necessary to identify EOIR in general: the site-specific treatment effect of input application on yield.
-We then discuss the causal forest method in detail, show how it is particularly suitable to obtain this fundamental information, and contrast it to more traditional prediction-oriented ML methods, such as RF, BRF, and CNN.
-
-## EOIR Estimation and Treatment Effects
-
-Let $p$ be the price that a producer receives for a unit of a crop, $w$ be the per-unit price paid for a unit of an input, $OC$ represent other costs of production, and $y=f(I, \mathbf{c})$ describe the relationship between crop yield, the input application rate $I$ and a vector of field characteristics variables $\mathbf{c}$.
-A simple model of producer behavior assumes that the producer chooses a level of $I$ to maximize profits (revenues minus costs):
-
-\begin{equation}
-\max_{I} \quad pf(I, \mathbf{c}) - wI -OC. (\#eq:eqn1)
-\end{equation}
-
-Elementary calculus shows that the necessary condition for maximization is, that $\partial f(I, \mathbf{c})/\partial I - w =0$, which implicitly defines the economically optimal input application rate as a function of prices and soil/field characteristics, and may be arranged as \@ref(eq:eqn2):
-
-\begin{equation}
-\frac{\partial f(I^{*}(p,w,\mathbf{c}), \mathbf{c})}{\partial I} \equiv \frac{w}{p}. (\#eq:eqn2)
-\end{equation}
-
-Identity \@ref(eq:eqn2) states that the necessary elements of the information needed for profit maximization are the input price, the output price, and the partial derivative of the yield function with respect to the input.
-While knowledge of the yield function $f(I, \mathbf{c})$ in Eq.
-\@ref(eq:eqn1)) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the "change" in yield in response to a change in input rate is.
-
-Recent papers using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21) and then derive changes in yield associated with changes in input rate to estimate site-specific input recommendations.
-On the other hand, Causal Forest is designed specifically to estimate a discrete version of Eq.
-\@ref(eq:eqn2) directly, examining the discrete changes in yield that result from discrete *changes* in the input application rate $I$, bypassing the estimation of $f(I, \mathbf{c})$.
-It may be suspected that CF will outperform other ML methods that identify EOIR indirectly through yield prediction.
-We now details how CF works below and why CF may perform better in predicting EOIR than other prediction-oriented ML methods used in the previous studies.
-
-## Causal Forest
-
-CF was developed specifically for identifying heterogeneous treatment effects [@athey2016recursive; @Wager2018a].
-Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf (please see Appendix for an example of a causal tree).
-
-While both RF and CF build trees by recursively partitioning samples, they differ critically in their criteria for splitting.
-In RF, the sample is split to minimize the mean squared error (MSE) of yield prediction in building trees.
-Unfortunately, the MSE of treatment effect predictions is not useful for building a CT since the true treatment effects are never observable.
-However, @athey2016recursive showed that minimizing the expected MSE of the treatment effect is equivalent to maximizing the variance of treatment effects across the resulting two leaves and minimizing the within-leaf variance.
-Consequently, by splitting samples in a way that maximizes the variance of treatment effects across the resulting two leaves, CF overcomes the fundamental problem created by the unobservability of true treatment effects.
-CF requires that the tree-building process is "honest" for treatment effects estimation to be unbiased.
-Honest tree-building first randomly splits in two the training data samples, then uses one of the subsamples to determine how to split the tree, and uses the other to estimate the treatment effects [@athey2016recursive; @Wager2018a].
-This honest subsampling technique avoids overestimation of the heterogeneity of estimated treatment effects.
-Since CF splits samples to maximize the heterogeneity of estimated treatment effects, using the same sample for both the sample splitting and treatment effect calculations renders itself sensitive to noise or outliers, allowing high noise levels to exaggerate the treatment effects.
-
-## CF vs. Prediction-oriented ML methods
-
-Whether the indirect (yield-prediction-first) and direct approach is used can lead to meaningful statistical differences when it comes to EOIR estimation.
-The conventional prediction-oriented ML methods are designed to predict yield, $y_i(I,\mathbf{c})$, well, but not necessarily treatment effects.
-Since the loss function used in prediction-oriented ML uses (typically squared) residuals in yield prediction, prediction-oriented ML is naturally optimized for predicting the "level" of yield instead of identifying the causal impact of the input on yield.
-CF, on the other hand, is designed specifically to estimate the causal impact of input.
-Indeed, @Wager2018a used Monte Carlo simulations to show that CF provided more accurate estimates of heterogeneous treatment effects than those provided by RF.
-However, the underlying data generating process of their simulations was extremely simple, with the treatment effect influenced by only a single variable.
-CF has not been tested for more complicated data generating processes, such as those represented by yield response functions in which the treatment effect of an input can be affected by multiple variables in a non-linear fashion.
-Moreover, CF has never been compared to more advanced ML methods such as BRF and CNN that are considered to have prediction capabilities greater than RF's.
-The study reported here builds on @Wager2018a to compare CF to these prediction-oriented ML methods (not just RF, but also BRF and CNN) in more realistic agronomic experiment settings.
-
-# Materials and Methods
-
-Monte Carlo simulations were conducted for nitrogen experiments for corn production to estimate site-specific EONRs.
-The simulations' first step generated one thousand synthetic fields that "resembled" an actual field.
-Then, for each simulation round, one of the fields was used as a training data set, and another field that is different from the one used as a training data set in that round was used as a validation data set.
-Field characteristics and yield were simulated assuming the Mitscherlich-Baule (MB) yield response function.
-We used the RF, BRF, and CNN ML methods to estimate yield response functions, and we used the CF method to estimate treatment effects.
-For each method, we estimated site-specific EONRs using the training data set, and checked the statistical performance of the predicted site-specific EONR using the validation data set.
-Detailed descriptions of these steps are provided below.
-The *R* and *python* codes that implement the simulation analyses are available at https://github.com/tmieno2/ML_VRA.git.
-
-## Data Generation
-
-### Simulated Experimental Fields
-<!-- experimental field: area: 51ha, plot: 384, subplot:1536, cell:55296   -->
-
-The simulated field was created based on an actual 51-ha Illinois field on which the Data-Intensive Farm Management (DIFM) project [@bullock2019] has run multiple OFPEs.
-Figure \@ref(fig:field-map) illustrates that simulated trials consisted of $384$ 18.3 m $\times$ 73.2 m "plots," each of which was assigned an N fertilizer application rate.
-Each plot was made up of four (4-rows $\times$ 1-column) 18.3 m $\times$ 18.3 m "subplots," which were unit of analysis used in subsequent statistical analysis.
-Each subplot contained of a 6-rows $\times$ 6-columns grid of thirty-six 3.05 m $\times$ 3.05 m "cells." All field characteristics and yield data were generated at the cell level.
-
-```{r field-map, out.width="50%", fig.cap = "Partitioning of field into plots, subplots and cells"}
-# knitr::include_graphics("./GitControlled/Writing/field_structure.png")
-readPNG(here("GitControlled/Writing/field_structure.png")) %>% grid.raster()
-```
-
-### Underlying Yield Response Function
-
-We modeled the yield response function as having the following Mitscherlich-Baule functional form, which is flexible in its shape, allows for the existence of a yield plateau, and has been shown to be a plausible specification for N fertilization models for corn [@frank1990; @llewelyn1997; @paris1992].
-
-\begin{equation}
-f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) N)) + \varepsilon. (\#eq:eqn5)
-\end{equation}
-
-The first term on the right-hand side of Eq.
-\@ref(eq:eqn5) is the deterministic yield component.
-The variable $N$ represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot.
-Also in Eq.
-\@ref(eq:eqn3), $\alpha$, $\beta$, and $ymax$ are functions of a vector of field characteristics variables $\mathbf{c}=(c_1,...,c_K)$, which vary spatially on the field.
-For example, $\alpha$ and $ymax$, which affect yield independently from the applied N fertilizer rate, might be interpreted as depending on the ingredient soil N content supplied by residual N, soil organic matter, etc.
-$\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen].
-The error term of the yield $\varepsilon$ represents the composite of all the unobserved factors that affect crop yield beyond $\alpha$, $\beta$, $ymax$ and $N$.
-
-A fictional "researcher" is modeled as not knowing the function form of $f$, as having limited knowledge about which variables make up $\mathbf{c}$, or even the number of elements of $\mathbf{c}$, and as having limited ability to measure the values that many of the variables that constitute $\mathbf{c}$ take on across the field.
-
-### Cell-specific Yield Functions and True Economically Optimal N Rates
-
-Let $i \in \{1,2,...,1536\}$ index a simulated field's subplots and $j \in \{1,2,...,36\}$ index cells within subplots.
-Let $N^{i}$ be the N fertilization rate on plot $i$, and let $\mathbf{c}^{i,j}$ be the value of $\mathbf{c}$ on cell $(i,j)$, Eq.
-\@ref(eq:eqn6) shows the yield level on cell $j$ in subplot $i$ is affected by the N rate applied on subplot $i$:
-
-\begin{equation}
-f(N^{i}, \mathbf{c}^{i,j}) = ymax(\mathbf{c}^{i,j})(1-exp(\alpha(\mathbf{c}^{i,j}) + \beta(\mathbf{c}^{i,j}) N^{i})) + \varepsilon^{i,j}. (\#eq:eqn6)
-\end{equation}
-
-To simplify notation, denote  $\alpha(\mathbf{c}^{i,j})$ as $\alpha^{i,j}$, $\beta(\mathbf{c}^{i,j})$ as $\beta^{i,j}$, and $ymax(\mathbf{c}^{i,j})$ as $ymax^{i,j}$.
-Then, a cell-specific yield function can be written as,
-
-\begin{equation}
-f^{i,j}(N) = ymax^{i,j}(1-exp(\alpha^{i,j} + \beta^{i,j} N^{i})) + \varepsilon^{i,j}. (\#eq:eqn7)
-\end{equation}
-
-Parameters $\alpha^{i,j}$, $\beta^{i,j}$, $\beta^{i,j}$, and $\varepsilon^{i,j}$ were modeled as spatially autocorrelated using unconditional Gaussian geostatistical simulation based on the spherical variogram model.
-The `gstat` package (version 2.0.6 [@gstat1; @gstat2]) in R was used for this purpose.
-Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha^{i,j}$, $\beta^{i,j}$, $ymax^{i,j}$, and $\varepsilon^{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
-(Codes used to generate parameter values are available at https://github.com/tmieno2/ML_VRA.git.) The range and nugget of all parameters were assumed to be $400$ m and 0.
-The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$.
-Figure \@ref(fig:fig-parameters) shows an example of the generated parameters.
-
-<br>
-
-```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics", cache = TRUE}
-# field_alpha + field_beta + field_ymax
-grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol = 2, nrow = 2)
-```
-
-Each cell $(i,j)$'s "true" optimal N application rate, denoted $N_{opt}^{i,j}$, was calculated by solving a profit maximization problem:
-
-\begin{equation}
-N_{opt}^{i,j} = \operatorname*{argmax}_{N}(P_{C} f^{i,j}(N) - P_N N), (\#eq:eqn8)
-\end{equation}
-
-where, $p =\$0.138/kg$ and $w =\$1.323/kg$ were the assumed prices of the corn and N fertilizer. Figure \@ref(fig:fig-optN) maps an example of the identified "true" cell-specific optimal N rates.
-
-```{r fig-optN, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a spatial distribution of true optimal N rate"}
-vis_optN_cell
-```
-
-<br>
-
-### Trial Design
-
-In each simulation round, five field-trial N rates were determined based on the range of the round's cell-specific EONRs. 
-Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percent quantile of the round's cell-specific EONRs.
-Then, the five trial design rates were $N_1 = Q_{0.05} - 20$, $N_5 = Q_{0.95} + 20$, $N_2 = N_1 + 0.25(N_5 - N_1)$, $N_3 = N_1 + 0.50(N_5 - N_1)$, $N_4 = N_1 + 0.75(N_5 - N_1)$.
-In each round, a Latin square design was followed to assign each plot one of the five N rates so established.
-Figure \@ref(fig:fig-nExp) shows an example of a trial design.
-The N rate was orthogonal to the error term in every simulation's example of trial design.
-This is important because if they were correlated, bias in the estimation of the impact of N on yield would be introduced into all of the ML methods.
-Since the treatment effect at each leaf is obtained simply by taking the difference of the average value of the dependent variable between the control and treated group within the leaf, CF requires the exogeneity of the treatment conditional on the independent variables to estimate the treatment effect consistently.
-Note that the violation of this condition would lead to biased estimation using the CF and the other ML methods.
-
-```{r fig-nExp, fig.width=3, fig.height=4, fig.cap = "An illustrative example of experimental design of N"}
-field_Ndesign
-```
-
-<br>
-
-### Yield Data Generation and Aggregation
-
-A cell-level data set for the whole field, $\{(y^{i,j}, N_{opt}^{i,j}, N^{i,j}, \mathbf{c}^{i,j}): i \in \{1,2,...,1536\}, j \in \{1,2,...,36\}\}$ was generated.
-For a generic cell $(i,j)$, yield $y^{i,j}$ was generated through Eq.
-\@ref(eq:eqn5), applying parameter values $\mathbf{c^{i,j}}=(\alpha^{i,j}, \beta^{i,j}, ymax^{i,j})$, the disturbance term level $\varepsilon^{i,j}$, and the cell's assigned experimental N rate, $N^{i,j}$.
-Figure \@ref(fig:field-yield-cell) presents the yield map from one of the simulations.
-
-```{r field-yield-cell, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a yield distribution map at the cell resolution"}
-vis_yield_cell
-```
-
-<br>
-
-Data were aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation. The subplot data were therefore
-
-\begin{equation}
-\{(y^{i}, N_{opt}^{i}, N^{i}, \mathbf{c}^{i}) = \frac{1}{36}\sum_{j=1}^{36} (y^{i,j}, N_{opt}^{i,j}, N^{i,j}, \mathbf{c}^{i,j}): i \in \{1,2,...,1536\}\}. (\#eq:eqn9)
-\end{equation}
-
-Figure \@ref(fig:field-yield-subplot) shows an example of observed yield data.
-Note that data generation at the cell level was conducted to reflect the real-world spatial heterogeneity in soil/field characteristics within the subplot level.
-But data aggregation to the subplot level was conducted because the large sizes of harvesters make it impossible to monitor yields accurately at smaller scales.
-
-```{r field-yield-subplot, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a yield distribution map at the subplot resolution"}
-vis_yield_subplot
-```
-
-<br>
-
-## Modeling Scenarios
-
-To evaluate the performances of RF, BRF, CNN and CF, we examined four modeling scenarios, each defined by a dataset assumed to be available to the researcher.
-The first modeling scenario, denoted "aby" assumed that the researcher has a dataset of the actual values $\alpha^{i,j}$, $\beta{i,j}$, $ymax^{i,j}$ for every cell $(i,j)$ and use $\alpha$, $\beta$ and $ymax$ as covariates in the ML models.
-This scenario represents an ideal situation for the researcher, in which all the relevant variables are observed, but the true functional form of heterogeneous yield response functions are not known.
-More realistic scenarios can be compared with this ideal scenario.
-
-In subsequent modeling scenarios, we made the simulated experimental data more realistic by varying the degree to which the researcher understood what the needed covariates' values were those in the data set.
-In the second scenario, denoted "abytt," we introduced additional variables $\theta_1$ and $\theta_2$, and the researcher's data set contained values of $\alpha^{i}$, $\beta^{i}$, $ymax^{i}$, $\theta_1^{i}$ and $\theta_2^{i}$ for all subplots $i=1,...,1536$.
-$\theta_1$ and $\theta_2$ had no effect on yield, but their cell-level values were spatially correlated with $\beta^{i,j}$, and so their subplot-level values were correlated with $\beta^{i}$.
-This scenario was meant to reflect the lack of scientific consensus about which variables explain heterogeneous yield response to N, making it likely that the researcher would include irrelevant variables like $\theta_1$ and $\theta_2$ in real-world data analysis.
-
-In the third scenario, denoted "aabbyy," the researcher's data set did not contain values of $\alpha^{i}$, $\beta^{i}$, or $ymax^{i}$.
-Rather, it contained subplot-level values of permutations of $\alpha$, $\beta$, and $ymax$.
-Specifically, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r_{\alpha}^{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r_{\beta}^{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r_{ymax}^{i,j} \in (0,1)$ to the ${ymax}^{i,j}$ variable.
-(There was no spatial correlation between the $r_{\alpha}^{i,j}$ and $r_{\beta}^{i,j}$ data, between $r_{\alpha}^{i,j}$ and $r_{ymax}^{i,j}$ data, or between $r_{\beta}^{i,j}$ and $r_{ymax}^{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha^{i,j}$, $\beta^{i,j}$ and $ymax^{i,j}$.
-These were 
-$\alpha_{1}^{i,j} = r_{\alpha}^{i,j} \alpha^{i,j}$, $\alpha_{2}^{i,j} = (1- r_{\alpha}^{i,j}) \alpha^{i,j}$,
-$\beta_{1}^{i,j} = r_{\beta}^{i,j} \beta^{i,j}$, $\beta_{2}^{i,j} = (1- r_{\beta}^{i,j}) \beta^{i,j}$,
-$ymax_{1}^{i,j} = r_{ymax}^{i,j} ymax^{i,j}$, and $ymax_{2}^{i,j} = (1- r_{ymax}^{i,j}) ymax^{i,j}$.
-For each $\alpha$, $\beta$ and $ymax$, these procedures created two new covariates that were highly spatially correlated with the original covariate, which was meant to reflect that many of the soil/field characteristics used to analyze OFPE data are spatially correlated.
-The values of $\alpha^{i,j}$, $\beta^{i,j}$ and $ymax^{i,j}$ did not indicate specific soil or field characteristics, but were functions of such.
-In reality, scientists cannot directly observe variables that can accurately predict yield plateau level, soil N content and N uptake efficiency.
-Rather, they use multiple observed soil/field characteristics to explain such phenological phenomena.
-For example, instead of using $ymax^{i,j}$ directly, some topographical land features and soil properties such as elevation and soil sand content could be used as yield-limiting factors [@jiang2004effect; @kravchenko2000correlation].
-In reality, scientists may include more than three variables as covariates.
-This scenario should reduce the accuracy of EONR modeling for all the models compared to the ideal case.
-
-The fourth scenario, denoted "aabbyytt," had the same components as aabbyy, but also included the $\theta_1$ and $\theta_2$ covariates.
-
-## Training Models and Estimating Site-specific EONRs
-
-### Training and Estimation of Site-specific EONRs by RF, BRF, and CNN
-
-The RF, BRF, and CNN methods all followed the same conceptual steps to estimate site-specific EONR: 1) estimate the yield production functions and 2) calculate site-specific EONRs based on that estimated function.
-For the given modeling scenario, RF and BRF predict yield by using all the available covariates as explanatory variables in the estimation process.
-The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for RF and BRF modeling.
-RF, BRF, and CF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving honest tree-building process), and the optimal values for these parameters were selected by cross-validation.
-Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same data set was used.
-To reduce the variance of predictions for prediction accuracy, we set the number of trees (*num.trees*) at a high value, $4000$.
-
-CNN leaves room for researchers to determine its architecture.
-We used a slightly modified version of one of the multi-stream CNN architectures proposed by @barbosa2020modeling, called "Late Fusion." Briefly stated, explanatory variables except N rate (e.g.
-$\alpha^{i,j}$, $\beta^{i,j}$, etc.) entered the model as a set of $6 \times 6$ element rasters.The input size of the N rate is treated as $1 \times 1$ because it is spatially homogeneous within each subplot.
-First, each input was connected to an independent convolutional layer with eight $3 \times 3$ filters each with stride one, followed by a $2 \times 2$ max-pooling layer with stride two.
-Then, a fully-connected rectified linear unit (ReLU) layer with sixteen neurons was added after each max-pooling layer, followed by a single ReLU neuron.
-Finally, multiple neurons were concatenated and fed to the fully-connected ReLU layer with sixteen neurons, followed by an output with a linear activation function.
-@barbosa2020modeling demonstrated that among several CNN architectures, this architecture modeled crop yield response to N rate management best.
-CNN was implemented in *Python* v3.7.6 using *Pytorch* v1.7.0 [@paszke2017automatic].
-The Adam optimizer [@kingma2014adam] was used with a learning rate of $0.001 \%$ (default value).
-To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience.
-
-Let $\mathbf{\Omega^{i}}$ denote a list of subplot-level explanatory variables (soil/field characteristics).
-Further, let $\hat{g}_m(N,\mathbf{\Omega})$ denote an estimated yield response function, estimated by model $m$ ($m$ = RF, BRF, or CNN).
-Then, yield at $i$ from model $m$ is $\hat{g}_m(N,\mathbf{\Omega^{i}})$.
-The site-specific EONR for each model can then be found by solving the following profit maximization problem for all $i$ for each of the models:
-
-\begin{equation}
-\hat{N}_{opt}^{i} = \operatorname*{argmax}_{N}(p \hat{g}_m(N, \mathbf{\Omega^{i}}) - w N), (\#eq:eqn8)
-\end{equation}
-
-where $p$ and $w$ are the prices of corn and N.
-
-### Training and Estimation of Site-specific EONRs by CF
-
-Unlike RF, BRF, and CNN, CF estimates the impact of a binary treatment.
-In our context, CF estimates changes in yields (i.e., $\hat{\tau}_{N^{con} \rightarrow N^{tre}}(\mathbf{\Omega^{i}})$) caused by changes in N application rates from one experimental rate (control N rate, i.e., $N^{con}$) to another experimental rate (treatment N rate, i.e., $N^{tre}$).
-Since we have five N application rates, four "experiments" (treatments) are identified based on four ($N^{con}$, $N^{tre}$) combinations.
-A possible grouping to make such pairwise N application rate combinations, which we call the "CF-base," used $(N_1, N_2),(N_1, N_3),(N_1, N_4)$, and $(N_1, N_5)$.
-In this approach, the treatment effect is always estimated against the lowest N rate ($N_1$) as $N^{con}$.
-
-For estimating site-specific EONR, the trained CF-base were used to predict site-specific changes in yields resultant from changes in application rates from $N_1$ to $N_m$ $(m\in\{2,3,4,5\})$.
-Let $\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}})$ be the the estimated treatment effect of changing subplot $i$'s application rate from $N_1$ to $N_m$ for site $i$.
-
-Since the CF-base approach always estimates the treatment effects using the lowest treatment rate $N_1$, the predicted treatment effects already represent differences in yields the from yield at $N_1$:
-
-\begin{equation}
-\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}}) = \hat{\tau}_{N_{1} \rightarrow N_{m}}(\mathbf{\Omega^{i}}). (\#eq:eqn9)
-\end{equation}
-
-With the treatment effects from the base obtained, site-specific EONRs were identified by finding the N rate resulting in the highest profit for each $i$.
-Yield levels were not predicted at any point in the CF-based approaches.
-
-### Model Evaluation
-
-The accuracy of EONR estimation was judged based RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level.
-Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) we calculated relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N_{opt}^{i}$.
-For RF, BRF, and CNN, the accuracy of yield prediction was judged based on the RMSE ($kg/ha$) of the yield prediction against the true yields at the subplot level.
-
-# Results and Discussions
-
-## EONR Estimation
-
-Table \@ref(tab:table-optN-subplot-wide) shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the one thousand simulations; it makes immediately clear that CF-base considerably outperformed the other ML methods, and that the profits based on CF-base's EONR estimates were the closest to the true maximum profits.
-BRF performed considerably better predicting EONR than did RF.
-
-<br>
-
-```{r table-optN-subplot-wide, tab.cap = "Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML methods and modeling scenarios"}
-report_table_optN
-# knit_print(report_table_optN)
-```
-
-<br>
-
-Interestingly, CNN completely failed in its estimations of site-specific EONRs.
-This happened because the site-specific yield response functions identified by CNN were linear, and all with the same slope.
-Therefore, CNN failed to capture a declining marginal product of N.
-The constant marginal product caused the estimated EONR to take on either the lowest or highest experimental N application rate.
-To examine whether this problem is a product solely of the specific choice of CNN architecture, we also tested another CNN model, which was analogous to CNN-ST proposed by @barbosa2020modeling.
-This architecture also estimated that yield and N rates were perfectly linearly related, and so estimated site-specific EONR poorly.
-Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs.
-In their work, in some cases, CNN predicted yield well; but in all cases predicted EONR poorly.
-
-Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML methods and modeling scenarios, respectively (CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always take $62.8$ kg/ha and \$$58.99$/ha, respectively).
-The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios.
-Interestingly, RF seems particularly vulnerable to the inclusion of more variables, with RMSE ($\hat{\pi}_{def}$) increasing from `r table_optN_prep[Model=="aby",rmse_optN_RF]` (`r table_optN_prep[Model=="aby", pi_loss_RF]`) in the "aby" scenario to `r table_optN_prep[Model=="aabbyytt", rmse_optN_RF]` (`r table_optN_prep[Model=="aabbyytt", pi_loss_RF]`) in the "aabbyytt" scenario.
-CF-base was more robust to the inclusion of additional variables.
-Overall, the simulations present CF-base as the clear winner in estimating EONR.
-
-```{r dist-optN, fig.width=6, fig.height=7, fig.cap = "Distributions of RMSE of EONR estimation over simulations"}
-plot_dis_optN
-```
-
-```{r dist-piLoss, fig.width=6, fig.height=7, fig.cap = "Distributions of profit deficit over simulations"}
-piLoss_density
-```
-
-<br>
-
-Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions.
-It plots the estimated treatment effects against true treatment effects by treatment types and ML methods (RF, BRF, and CF-base) under the "aabbyytt" scenario in one of the one thousand simulations rounds.
-The figure shows points clustered around the red 1-to-1 line, meaning that the estimated treatment effects did not exhibit significant bias.
-However, the models differed substantially in the accuracy of their treatment effect estimations.
-Points are clustered more tightly about the 1-to-1 line for CF-base than RF and BRF.
-That is, CF-base estimated treatment effects much more efficiently than did RF and BRF, which focus on yield prediction rather than treatment effect estimation.
-
-```{r plot-tre, fig.width=7, fig.height=5, fig.cap = "True treatment effects vs estimated treatment effects (scenario: aabbyytt)"}
-figure_te
-```
-
-`r ftext('NOTE: The red line in the figures denotes the 1-to-1 line to show the ideal relationship between true and estimated treatment effects.', fp_text(font.size = 9))`
-
-## The relationship between yield prediction performance and EONR prediction performance
-For RF, BRF and CNN, Figure \@ref(fig:plot-y-optN) plots the RMSE values of EONR estimation against the RMSE values of yield prediction, and the red lines show the best-fit line describing the relationship between them.
-For all the models the regression line was almost flat, showing little if any correlation between the two measures.
-In other words, the quality of a model's yield predictions provided little if any information about the quality of its EONR predictions.
-
-```{r plot-y-optN, fig.width=7, fig.height=5, fig.cap = "The relationship in the performance between EONR estimation and yield prediction by ML methods and modeling scenarios"}
-fig_y_optN
-```
-
-`r ftext('NOTE: The red line in the figures denotes the best-fit line to explain the relationship between the RMSEs of EONR prediction and yield prediction.', fp_text(font.size = 9))`
-
-<br>
-
-Table \@ref(tab:table-y-subplot-wide) shows the mean RMSE of yield prediction over the one thousand simulations.
-Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN.
-Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact along with the poor performance of RF in predicting EONR show that strong predictive power of yield levels does not imply accurate prediction of EONR.
-Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well.
-While CNN performed worse than RF and BRF in "aby" and "abytt," it performed better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables.
-Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.
-
-<br>
-
-```{r table-y-subplot-wide, tab.cap = "Mean RMSE of yield prediction (kg/ha) by ML methods and modeling scenarios"}
-report_table_y
-```
-
-<br>
-
-All previous research has followed a two-step procedure to estimate site-specific EONRs.
-The first step was to select the model that predicts yield most accurately, and the following step used the selected model to predict EONR.
-Table \@ref(tab:count-table) shows that following this process led to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds.
-For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of $1000$ iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations.
-That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF models best at yield prediction did not provide EONR estimates that led to high profits.
-Similarly, in no cased did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously.
-For example, Table \@ref(tab:count-table) shows that BRF predicted yield best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best.
-But, BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.
-
-<br>
-
-```{r count-table, tab.cap = "Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances for prediction-oriented ML methods"}
-report_summary_res_CNN_RF_BRF
-```
-
-<br>
-
-Virtually all the previous studies have used yield prediction accuracy to rank and select models.
-This is understandable, since whereas yield can be "ground-truthed" the true causal impact of a treatment cannot be determined from real-world data, making it impossible to cross-validate EONR.
-However, the simulation results reported here show clearly that using a model's yield prediction accuracy as a model selection criterion is not well justified if the ultimate objective is accurate estimation of site-specific EONRs.
-
-# Conclusion
-
-ML methods are appealing tools that can potentially improve site-specific input rate management by capturing heterogeneous treatment effects introduced by complex non-linear and multidimensional interactions of soil and field characteristics.
-Many kinds of prediction-oriented ML methods have been used for this purpose.
-We have introduced the use of CF, a relatively new method, which, unlike prediction-oriented ML methods, focuses on the identification of heterogeneous causal effects of treatment.
-
-We examined the use of CF-base for site-specific input management recommendations.
-Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN.
-CF-base consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation.
-We also showed that the model's yield prediction accuracy was uncorrelated with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map.
-
-Despite the relatively simple nature of the simulations, results reported provide intriguing evidence of potential advantages of CF over other ML methods when the purpose of the research is to increase the economic efficiency of input management.
-Of course, the reported research did not model all situations, and further research is needed.
-First, a drawback of the CF method is that because it does not estimate a continuous yield response function, it can only compare the economic outcomes of a limited set of experimental N rates included in the field trial that provides the data.
-This raises important questions about trial design.
-How many distinct experimental input application rates should be included?
-All the trial designs examined here were based on five N rates.
-Having examined models with additional rates would have increased the number of possible N rates from which the EONR were selected, but reduced treatment pair replications and estimation accuracy.
-
-Second, the size of the field used in the OFPE can affect the relative performances of the competing methods.
-CF requires honest sampling for its unbiasedness property.
-Honest sampling comes at the cost of losing prediction accuracy of treatment effects because fewer samples are used to estimate treatment effects within leaves [@athey2016recursive].
-Therefore, in the case in which ML analyses are conducted with OFPE data from a small field, CF may not outperform other ML methods
-
-Third, another interesting subject for future research is the potential of combining the ML methods with post-estimation spatial smoothing of the estimated EONR.
-It is well known that soil/field characteristics are spatially correlated [@f2007methods;@goovaerts1999geostatistics]; this spatial correlation is likely to cause spatial correlation in EONRs, which would suggest that post-estimation spatial smoothing of EONRs may further improve the accuracy of EONR estimation.
-
-Finally, a natural and fruitful extension of the reported research would be to test CF and other ML methods in a dynamic setting on which multiple years of experiments are conducted, allowing weather events into the analysis as explanatory variables.
-Crop simulation models (e.g., APSIM, DSSAT) could replace the Mitscherlich-Baule production function used here to model the underlying yield response function, which could generate more realistic data, using actual soil/field characteristics and weather instead of abstract parameters in the analysis, and so better include the dynamic nature of cropping systems in the study of N management [@archontoulis2020predicting;@puntel2016modeling;@puntel2018systems].
-
-# Acknowledgement
-
-This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled "Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management," (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled "Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation" (Award Number NR213A7500013G021).
-
-\newpage
-
-# References
-
-<div id="refs"></div>
-
-\newpage
-
-# (APPENDIX) Appendix {-}
-
-# Appendix A: Causal Tree Example {-}
+# Appendix A: Causal Tree Example {#ctree-ex}
 
 Figure \@ref(fig:ct-ex) shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$)($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
-In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example.
 
-```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
+```{r ct-ex, fig.width=5, fig.height=5, fig.align="center", fig.cap = "An illustrative example of causal tree"}
 fancyRpartPlot(opfit, sub = "")
@@
 
-`r ftext('NOTE: The first number in each node indicates the predicted treatment effects (in kg/ha).
-The number and the percentage of observations belonging to the node are shown below that.', fp_text(font.size = 9))`
+NOTE: The first number in each node indicates the predicted treatment effects (in kg/ha). The number and the percentage of observations belonging to the node are shown below that.
 
+In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example.
 The first data split criterion is whether the $\textit{ecs}$ value is greater or less than $25$.
@@
 It is noteworth that at no point CF estimates yield "level".
+
+# Appendix B: Parameter Generation
+
+## Base parameters $\alpha$, $\beta$, and $ymax$ {#par-gen}
+Parameters $\alpha^{i,j}$, $\beta^{i,j}$, $ymax^{i,j}$, and $\varepsilon^{i,j}$ were modeled as spatially autocorrelated using unconditional Gaussian geostatistical simulation based on the spherical variogram model.
+The `gstat` package (version 2.0.6 [@gstat1; @gstat2]) in R was used for this purpose
+
+Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha^{i,j}$, $\beta^{i,j}$, $ymax^{i,j}$, and $\varepsilon^{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
+(Codes used to generate parameter values are available at https://github.com/tmieno2/ML_VRA.git.) The range and nugget of all parameters were assumed to be $400$ m and 0.
+The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$.
+See Figure \@ref(fig:fig-parameters) for an example of the generated parameters.
+
+```{r fig-optN, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a spatial distribution of true optimal N rate"}
+
+vis_optN_cell
+```
+
+```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics", cache = TRUE}
+# field_alpha + field_beta + field_ymax
+grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol = 2, nrow = 2)
+```
+
+## Splitting the base parameters {#split-pars}
+
+For scenarios "aabbyy" and "aabbyytt", each of the base parameters $\alpha$, $\beta$, and $ymax$ are splitted into two part in a spatially correlated manner.
+Speficiallu, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r_{\alpha}^{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r_{\beta}^{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r_{ymax}^{i,j} \in (0,1)$ to the ${ymax}^{i,j}$ variable.
+Each of the weight variables are generated using unconditional Gaussian geostatistical simulation just like the base parameters.
+(There was no spatial correlation between the $r_{\alpha}^{i,j}$ and $r_{\beta}^{i,j}$ data, between $r_{\alpha}^{i,j}$ and $r_{ymax}^{i,j}$ data, or between $r_{\beta}^{i,j}$ and $r_{ymax}^{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha^{i,j}$, $\beta^{i,j}$ and $ymax^{i,j}$.
+These were
+$\alpha_{1}^{i,j} = r_{\alpha}^{i,j} \alpha^{i,j}$, $\alpha_{2}^{i,j} = (1- r_{\alpha}^{i,j}) \alpha^{i,j}$,
+$\beta_{1}^{i,j} = r_{\beta}^{i,j} \beta^{i,j}$, $\beta_{2}^{i,j} = (1- r_{\beta}^{i,j}) \beta^{i,j}$,
+$ymax_{1}^{i,j} = r_{ymax}^{i,j} ymax^{i,j}$, and $ymax_{2}^{i,j} = (1- r_{ymax}^{i,j}) ymax^{i,j}$.
+The codes used to implement the abovementioned parameter splitting is available at https://github.com/tmieno2/ML_VRA.git.

### 2022-02-07 Writing/manuscript_cea.rmd
made significant modifications to the manuscript and response to reviewers

@@
 
-```{r echo = F, include = FALSE}
+```{r echo = F, include = FALSE, cache = F}
 library(knitr)
@@
   message = F,
-  cache = FALSE, # <-- T
-  cache.lazy = FALSE,
+  cache = TRUE,
   echo = F
@@
 library(data.table)
-
+library(sf)
 library(png)
@@
 library(grid)
+library(causalTree)
+library(rpart)
+library(rattle)
 ```
@@
 CF was developed specifically for identifying heterogeneous treatment effects [@athey2016recursive; @Wager2018a].
-Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf (please see Appendix for an example of a causal tree).
+Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf (see Appendix \@ref(ctree-ex) for an example of a causal tree that can help further clarify how CF works).
 
@@
 The simulations' first step generated one thousand synthetic fields that "resembled" an actual field.
-Then, for each simulation round, one of the fields was used as a training data set, and another field that is different from the one used as a training data set in that round was used as a validation data set.
 Field characteristics and yield were simulated assuming the Mitscherlich-Baule (MB) yield response function.
@@
 
-### Underlying Yield Response Function
+### Cell-specific Yield Functions and True Economically Optimal N Rates
 
-We modeled the yield response function as having the following Mitscherlich-Baule functional form, which is flexible in its shape, allows for the existence of a yield plateau, and has been shown to be a plausible specification for N fertilization models for corn [@frank1990; @llewelyn1997; @paris1992].
+We modeled the yield response function as having the Mitscherlich-Baule functional form, which is flexible in its shape, allows for the existence of a yield plateau, and has been shown to be a plausible specification for N fertilization models for corn [@frank1990; @llewelyn1997; @paris1992].
+
+Let $i \in \{1,2,\dots,1536\}$ index a simulated field's subplots and $j \in \{1,2,\dots,36\}$ index cells within subplots.
+Let $N_{i}$ be the N fertilization rate on subplot $i$.
+Eq.
+\@ref(eq:eqn6) shows the yield level on cell $j$ in subplot $i$:
 
 \begin{equation}
-f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) N)) + \varepsilon. (\#eq:eqn5)
+f(N_{i}: \alpha_{i,j}, \beta_{i,j}, ymax_{i,j}) = ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) + \varepsilon^{i,j}. (\#eq:eqn6)
 \end{equation}
@@
 The first term on the right-hand side of Eq.
-\@ref(eq:eqn5) is the deterministic yield component.
+\@ref(eq:eqn6) is the deterministic yield component.
 The variable $N$ represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot.
 Also in Eq.
-\@ref(eq:eqn3), $\alpha$, $\beta$, and $ymax$ are functions of a vector of field characteristics variables $\mathbf{c}=(c_1,...,c_K)$, which vary spatially on the field.
+\@ref(eq:eqn6), $\alpha$, $\beta$, and $ymax$ are spatially varying parameters that govern how yield level is determined in conjunction with the applied N rate.
+They reflect local cell-level production conditions, such as soil characteristics and topography.
 For example, $\alpha$ and $ymax$, which affect yield independently from the applied N fertilizer rate, might be interpreted as depending on the ingredient soil N content supplied by residual N, soil organic matter, etc.
@@
 The error term of the yield $\varepsilon$ represents the composite of all the unobserved factors that affect crop yield beyond $\alpha$, $\beta$, $ymax$ and $N$.
+Each cell $(i,j)$'s "true" optimal N application rate, denoted $N^{opt}_{i,j}$, was calculated by solving a profit maximization problem by cell assuming that the prices of corn and N fertilizer were $\$0.138/kg$ and $\$1.323/kg$, respectively.
+These prices are used consistently for our simualtions.
+See Appendix \@ref(par-gen) for further details on how the paremeters were generated and sample maps of the parameters and true economically optimal N rates.
 
-A fictional "researcher" is modeled as not knowing the function form of $f$, as having limited knowledge about which variables make up $\mathbf{c}$, or even the number of elements of $\mathbf{c}$, and as having limited ability to measure the values that many of the variables that constitute $\mathbf{c}$ take on across the field.
-
-### Cell-specific Yield Functions and True Economically Optimal N Rates
-
-Let $i \in \{1,2,...,1536\}$ index a simulated field's subplots and $j \in \{1,2,...,36\}$ index cells within subplots.
-Let $N^{i}$ be the N fertilization rate on plot $i$, and let $\mathbf{c}^{i,j}$ be the value of $\mathbf{c}$ on cell $(i,j)$, Eq.
-\@ref(eq:eqn6) shows the yield level on cell $j$ in subplot $i$ is affected by the N rate applied on subplot $i$:
-
-\begin{equation}
-f(N^{i}, \mathbf{c}^{i,j}) = ymax(\mathbf{c}^{i,j})(1-exp(\alpha(\mathbf{c}^{i,j}) + \beta(\mathbf{c}^{i,j}) N^{i})) + \varepsilon^{i,j}. (\#eq:eqn6)
-\end{equation}
-
-To simplify notation, denote  $\alpha(\mathbf{c}^{i,j})$ as $\alpha^{i,j}$, $\beta(\mathbf{c}^{i,j})$ as $\beta^{i,j}$, and $ymax(\mathbf{c}^{i,j})$ as $ymax^{i,j}$.
-Then, a cell-specific yield function can be written as,
-
-\begin{equation}
-f^{i,j}(N) = ymax^{i,j}(1-exp(\alpha^{i,j} + \beta^{i,j} N^{i})) + \varepsilon^{i,j}. (\#eq:eqn7)
-\end{equation}
-
-Parameters $\alpha^{i,j}$, $\beta^{i,j}$, $\beta^{i,j}$, and $\varepsilon^{i,j}$ were modeled as spatially autocorrelated using unconditional Gaussian geostatistical simulation based on the spherical variogram model.
-The `gstat` package (version 2.0.6 [@gstat1; @gstat2]) in R was used for this purpose.
-Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha^{i,j}$, $\beta^{i,j}$, $ymax^{i,j}$, and $\varepsilon^{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
-(Codes used to generate parameter values are available at https://github.com/tmieno2/ML_VRA.git.) The range and nugget of all parameters were assumed to be $400$ m and 0.
-The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$.
-Figure \@ref(fig:fig-parameters) shows an example of the generated parameters.
-
-<br>
-
-```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics", cache = TRUE}
-# field_alpha + field_beta + field_ymax
-grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol = 2, nrow = 2)
-```
-
-Each cell $(i,j)$'s "true" optimal N application rate, denoted $N_{opt}^{i,j}$, was calculated by solving a profit maximization problem:
-
-\begin{equation}
-N_{opt}^{i,j} = \operatorname*{argmax}_{N}(P_{C} f^{i,j}(N) - P_N N), (\#eq:eqn8)
-\end{equation}
-
-where, $p =\$0.138/kg$ and $w =\$1.323/kg$ were the assumed prices of the corn and N fertilizer. Figure \@ref(fig:fig-optN) maps an example of the identified "true" cell-specific optimal N rates.
-
-```{r fig-optN, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a spatial distribution of true optimal N rate"}
-vis_optN_cell
-```
-
-<br>
-
-### Trial Design
+### Trial Design and Yield Data Generation for Modeling
 
@@
 In each round, a Latin square design was followed to assign each plot one of the five N rates so established.
-Figure \@ref(fig:fig-nExp) shows an example of a trial design.
+The left-most panel of Figure \@ref(fig:fig-nExp-yield) shows an example of a trial design.
 The N rate was orthogonal to the error term in every simulation's example of trial design.
@@
 
-```{r fig-nExp, fig.width=3, fig.height=4, fig.cap = "An illustrative example of experimental design of N"}
-field_Ndesign
-```
-
-<br>
-
-### Yield Data Generation and Aggregation
-
-A cell-level data set for the whole field, $\{(y^{i,j}, N_{opt}^{i,j}, N^{i,j}, \mathbf{c}^{i,j}): i \in \{1,2,...,1536\}, j \in \{1,2,...,36\}\}$ was generated.
-For a generic cell $(i,j)$, yield $y^{i,j}$ was generated through Eq.
-\@ref(eq:eqn5), applying parameter values $\mathbf{c^{i,j}}=(\alpha^{i,j}, \beta^{i,j}, ymax^{i,j})$, the disturbance term level $\varepsilon^{i,j}$, and the cell's assigned experimental N rate, $N^{i,j}$.
-Figure \@ref(fig:field-yield-cell) presents the yield map from one of the simulations.
-
-```{r field-yield-cell, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a yield distribution map at the cell resolution"}
-vis_yield_cell
-```
-
-<br>
-
-Data were aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation. The subplot data were therefore
+A cell-level data set for the whole field, $\{(y_{i,j}, N^{opt}_{i,j}, N_{i,j}, \mathbf{c}_{i,j}): i \in \{1,2,\dots,1536\}, j \in \{1,2,\dots,36\}\}$ was generated by plugging in the parameter values, the error term, and the assigned nitrogen rates into \@ref(eq:eqn6).
+The cell-level data were then aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation.
+The subplot data were therefore
 
 \begin{equation}
-\{(y^{i}, N_{opt}^{i}, N^{i}, \mathbf{c}^{i}) = \frac{1}{36}\sum_{j=1}^{36} (y^{i,j}, N_{opt}^{i,j}, N^{i,j}, \mathbf{c}^{i,j}): i \in \{1,2,...,1536\}\}. (\#eq:eqn9)
+\{(y_{i}, N^{opt}_{i}, N_{i}) = \frac{1}{36}\sum_{j=1}_{36} (y_{i,j}, N^{opt}_{i,j}, N_{i,j}): i \in \{1,2,\dots,1536\}\}. (\#eq:eqn9)
 \end{equation}
 
-Figure \@ref(fig:field-yield-subplot) shows an example of observed yield data.
+The right panel of Figure \@ref(fig:fig-nExp-yield) shows an example of observed yield data.
 Note that data generation at the cell level was conducted to reflect the real-world spatial heterogeneity in soil/field characteristics within the subplot level.
@@
 
-```{r field-yield-subplot, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a yield distribution map at the subplot resolution"}
-vis_yield_subplot
+```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "An example of experimental design of N and generated yield at the subplot resolution"}
+
+(field_Ndesign + ggtitle("(a) Trial Design")) |
+  (vis_yield_subplot + ggtitle("(b) Simulated Yield Level"))
 ```
-
-<br>
 
@@
 To evaluate the performances of RF, BRF, CNN and CF, we examined four modeling scenarios, each defined by a dataset assumed to be available to the researcher.
-The first modeling scenario, denoted "aby" assumed that the researcher has a dataset of the actual values $\alpha^{i,j}$, $\beta{i,j}$, $ymax^{i,j}$ for every cell $(i,j)$ and use $\alpha$, $\beta$ and $ymax$ as covariates in the ML models.
+The first modeling scenario, denoted "aby" assumed that the researcher has a dataset of the actual values $\alpha_{i}$, $\beta_{i}$, $ymax_{i}$ in the yield response function for every subplot $i$ and use $\alpha$, $\beta$ and $ymax$ as covariates in the ML models.
 This scenario represents an ideal situation for the researcher, in which all the relevant variables are observed, but the true functional form of heterogeneous yield response functions are not known.
@@
 In subsequent modeling scenarios, we made the simulated experimental data more realistic by varying the degree to which the researcher understood what the needed covariates' values were those in the data set.
-In the second scenario, denoted "abytt," we introduced additional variables $\theta_1$ and $\theta_2$, and the researcher's data set contained values of $\alpha^{i}$, $\beta^{i}$, $ymax^{i}$, $\theta_1^{i}$ and $\theta_2^{i}$ for all subplots $i=1,...,1536$.
-$\theta_1$ and $\theta_2$ had no effect on yield, but their cell-level values were spatially correlated with $\beta^{i,j}$, and so their subplot-level values were correlated with $\beta^{i}$.
-This scenario was meant to reflect the lack of scientific consensus about which variables explain heterogeneous yield response to N, making it likely that the researcher would include irrelevant variables like $\theta_1$ and $\theta_2$ in real-world data analysis.
+In the second scenario, denoted "abytt," we introduced additional variables $\theta^1$ and $\theta^2$, and the researcher's data set contained values of $\alpha_{i}$, $\beta_{i}$, $ymax_{i}$, $\theta^1_{i}$ and $\theta^2_{i}$ for all subplots $i=1,\dots,1536$.
+$\theta^1$ and $\theta^2$ had no effect on yield, but they were spatially correlated with $\beta^{i}.
+This scenario was meant to reflect the lack of scientific consensus about which variables explain heterogeneous yield response to N, making it likely that the researcher would include irrelevant variables like $\theta^1$ and $\theta^2$ in real-world data analysis.
 
-In the third scenario, denoted "aabbyy," the researcher's data set did not contain values of $\alpha^{i}$, $\beta^{i}$, or $ymax^{i}$.
+In the third scenario, denoted "aabbyy," the researcher's data set did not contain values of $\alpha_{i}$, $\beta_{i}$, or $ymax_{i}$.
 Rather, it contained subplot-level values of permutations of $\alpha$, $\beta$, and $ymax$.
-Specifically, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r_{\alpha}^{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r_{\beta}^{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r_{ymax}^{i,j} \in (0,1)$ to the ${ymax}^{i,j}$ variable.
-(There was no spatial correlation between the $r_{\alpha}^{i,j}$ and $r_{\beta}^{i,j}$ data, between $r_{\alpha}^{i,j}$ and $r_{ymax}^{i,j}$ data, or between $r_{\beta}^{i,j}$ and $r_{ymax}^{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha^{i,j}$, $\beta^{i,j}$ and $ymax^{i,j}$.
-These were 
-$\alpha_{1}^{i,j} = r_{\alpha}^{i,j} \alpha^{i,j}$, $\alpha_{2}^{i,j} = (1- r_{\alpha}^{i,j}) \alpha^{i,j}$,
-$\beta_{1}^{i,j} = r_{\beta}^{i,j} \beta^{i,j}$, $\beta_{2}^{i,j} = (1- r_{\beta}^{i,j}) \beta^{i,j}$,
-$ymax_{1}^{i,j} = r_{ymax}^{i,j} ymax^{i,j}$, and $ymax_{2}^{i,j} = (1- r_{ymax}^{i,j}) ymax^{i,j}$.
-For each $\alpha$, $\beta$ and $ymax$, these procedures created two new covariates that were highly spatially correlated with the original covariate, which was meant to reflect that many of the soil/field characteristics used to analyze OFPE data are spatially correlated.
-The values of $\alpha^{i,j}$, $\beta^{i,j}$ and $ymax^{i,j}$ did not indicate specific soil or field characteristics, but were functions of such.
+Each of the three parameters were split into two parts in a spatially correlated manner, and six new covariates were created (see Appendix \@ref(split-pars) for the details about this prameter splitting process).
+These were $\alpha^{1}_{i}$, $\alpha^{2}_{i}$, $\beta^{1}_{i}$, $\beta^{2}_{i}$, $ymax^{1}_{i}$, and $ymax^{2}_{i}$.
+The two splitted variables were spatially correlated to reflect that many of the soil/field characteristics used to analyze OFPE data are spatially correlated.
+The values of $\alpha_{i}$, $\beta_{i}$ and $ymax_{i}$ did not indicate specific soil or field characteristics, but were functions of such.
 In reality, scientists cannot directly observe variables that can accurately predict yield plateau level, soil N content and N uptake efficiency.
 Rather, they use multiple observed soil/field characteristics to explain such phenological phenomena.
-For example, instead of using $ymax^{i,j}$ directly, some topographical land features and soil properties such as elevation and soil sand content could be used as yield-limiting factors [@jiang2004effect; @kravchenko2000correlation].
+For example, instead of using $ymax_{i}$ directly, some topographical land features and soil properties such as elevation and soil sand content could be used as yield-limiting factors [@jiang2004effect; @kravchenko2000correlation].
 In reality, scientists may include more than three variables as covariates.
@@
 The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for RF and BRF modeling.
-RF, BRF, and CF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving honest tree-building process), and the optimal values for these parameters were selected by cross-validation.
+RF ann BRF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving honest tree-building process), and the optimal values for these parameters were selected by cross-validation.
 Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same data set was used.
@@
 In this approach, the treatment effect is always estimated against the lowest N rate ($N_1$) as $N^{con}$.
+The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for CF estimation.
+Just like RF and BRF, hyperparameters were tuned using cross-validatiaon.
 
@@
 
-### Model Evaluation
+### Evaluation of yield and EONR predictions
 
-The accuracy of EONR estimation was judged based RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level.
-Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) we calculated relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N_{opt}^{i}$.
+For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset.
+For example, for simulation number 1, train dataset from simulation number 2 was used as the test dataset.
+This process works because the train datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$).
+Furtehr, each of the "train" datasets are generated independet of one another.
+Thefore, for a particular simulation round, the dataset in any of the other simualtions can serve as a valid test dataset.
+This practice avoid creating another set of 1000 simulations fields unnecessarily.
+
+The accuracy of EONR estimation was judged based on RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level.
+Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) we calculated relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N^{opt}^{i}$.
 For RF, BRF, and CNN, the accuracy of yield prediction was judged based on the RMSE ($kg/ha$) of the yield prediction against the true yields at the subplot level.
@@
 
-## EONR Estimation
+## Comparison of EONR estimation accuracy
 
@@
 
-## The relationship between yield prediction performance and EONR prediction performance
+## The relationship between yield and EONR prediction performances.
+
 For RF, BRF and CNN, Figure \@ref(fig:plot-y-optN) plots the RMSE values of EONR estimation against the RMSE values of yield prediction, and the red lines show the best-fit line describing the relationship between them.
@@
 
-```{r plot-y-optN, fig.width=7, fig.height=5, fig.cap = "The relationship in the performance between EONR estimation and yield prediction by ML methods and modeling scenarios"}
+```{r plot-y-optN, fig.width=7, fig.height=7, fig.cap = "The relationship in the performance between EONR estimation and yield prediction by ML methods and modeling scenarios"}
 fig_y_optN
@@
 
-# Conclusion
-
-ML methods are appealing tools that can potentially improve site-specific input rate management by capturing heterogeneous treatment effects introduced by complex non-linear and multidimensional interactions of soil and field characteristics.
-Many kinds of prediction-oriented ML methods have been used for this purpose.
-We have introduced the use of CF, a relatively new method, which, unlike prediction-oriented ML methods, focuses on the identification of heterogeneous causal effects of treatment.
-
-We examined the use of CF-base for site-specific input management recommendations.
-Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN.
-CF-base consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation.
-We also showed that the model's yield prediction accuracy was uncorrelated with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map.
+# Limitations and Future Studies
 
@@
 
+# Conclusion
+
+ML methods are appealing tools that can potentially improve site-specific input rate management by capturing heterogeneous treatment effects introduced by complex non-linear and multidimensional interactions of soil and field characteristics.
+Many kinds of prediction-oriented ML methods have been used for this purpose.
+We have introduced the use of CF, a relatively new method, which, unlike prediction-oriented ML methods, focuses on the identification of heterogeneous causal effects of treatment.
+
+We examined the use of CF-base for site-specific input management recommendations.
+Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN.
+CF-base consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation.
+We also showed that the model's yield prediction accuracy was uncorrelated with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map.
+
 # Acknowledgement
@@
 
-# (APPENDIX) Appendix {-}
+# Supplementary Appendix {-}
 
-# Appendix A: Causal Tree Example {-}
-
-Figure \@ref(fig:ct-ex) shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$)($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
-In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example.
-
-```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
-fancyRpartPlot(opfit, sub = "")
+```{r, child = "appendix.Rmd"}
 ```
-
-`r ftext('NOTE: The first number in each node indicates the predicted treatment effects (in kg/ha).
-The number and the percentage of observations belonging to the node are shown below that.', fp_text(font.size = 9))`
-
-The first data split criterion is whether the $\textit{ecs}$ value is greater or less than $25$.
-The observations with $\textit{ecs}$ greater than or equal to $25$ move to the left node, while those with $\textit{ecs}$ less than $25$ move to the right.
-For each of the subsamples, the treatment effect is identified as the difference in the mean yields of the treated and control groups within the subsample.
-The treatment effect for the low-$\textit{ecs}$ observations was $619$ kg/ha, and for the high-$\textit{ecs}$ observations was $982$ kg/ha.
-This means that for the impact of the increase in seed rate the treatment effect is heterogeneous over space, having a larger positive impact on yield in high-$\textit{ecs}$ areas.
-Trees are further developed to have more groups of subsamples to allow for more flexible representations of the heterogeneous treatment effects.
-The estimated heterogeneous treatments effects can then be used to identify site-specific EOIRs.
-It is noteworth that at no point CF estimates yield "level".

### 2022-02-07 Codes/PrepareResults.R

@@ -1,17 +1,14 @@
-## ----set-up, cache = F------------------------------------------------------------------------
+## ----set-up, cache = F----
 library(knitr)
 library(here)
 
 here::i_am("GitControlled/Writing/manuscript_cea.rmd")
 
 knitr::opts_chunk$set(
-  cache = TRUE,
-  warning = FALSE,
-  message = FALSE
+  cache = TRUE
 )
 
-
-## ----packages, cache = FALSE, include = FALSE-------------------------------------------------
+## ----packages, cache = FALSE, include = FALSE----
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -36,7 +33,54 @@ library(modelsummary)
 library(latex2exp)
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE----------------------------------------
+## ----figure_setup, cache = F----
+theme_update(
+  axis.title.x =
+    element_text(
+      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain"
+    ),
+  axis.title.y =
+    element_text(
+      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain"
+    ),
+  axis.text.x =
+    element_text(
+      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain"
+    ),
+  axis.text.y =
+    element_text(
+      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"
+    ),
+  axis.ticks =
+    element_line(
+      size = 0.3, linetype = "solid"
+    ),
+  axis.ticks.length = unit(.15, "cm"),
+  #--- legend ---#
+  legend.text =
+    element_text(
+      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
+    ),
+  legend.title =
+    element_text(
+      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
+    ),
+  legend.key.size = unit(0.5, "cm"),
+  #--- strip (for faceting) ---#
+  strip.text = element_text(size = 10),
+  #--- plot title ---#
+  plot.title = element_text(family = "Times", face = "bold", size = 12),
+  #--- margin ---#
+  # plot.margin = margin(0, 0, 0, 0, "cm"),
+  #--- panel ---#
+  panel.grid.major = element_blank(),
+  panel.grid.minor = element_blank(),
+  panel.background = element_blank(),
+  panel.border = element_rect(fill = NA)
+)
+
+
[…]

### 2022-02-07 Writing/manuscript_cea.rmd
further modifications to the manuscript and replies

@@
 Virtually all the previous studies have used yield prediction accuracy to rank and select models.
-This is understandable, since whereas yield can be "ground-truthed" the true causal impact of a treatment cannot be determined from real-world data, making it impossible to cross-validate EONR.
+This is understandable, since whereas yield can be "ground-truthed" the true causal impact of a treatment cannot be determined from real-world data, making it impossible to cross-validate EONR prediction.
 However, the simulation results reported here show clearly that using a model's yield prediction accuracy as a model selection criterion is not well justified if the ultimate objective is accurate estimation of site-specific EONRs.

### 2022-02-07 Codes/PrepareResults.rmd
update font type and figure of field structure

--- 2022-02-06 Codes/PrepareResults.rmd
@@
 # --- figure making --- #
+library(ggbrace)
 library(RColorBrewer)
@@
 library(latex2exp)
+```
+
+# figure and table set up
+
+```{r}
+theme_update(
+  axis.title.x =
+    element_text(
+      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain", family = "Cambria"
+    ),
+  axis.title.y =
+    element_text(
+      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain", family = "Cambria"
+    ),
+  axis.text.x =
+    element_text(
+      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain", family = "Cambria"
+    ),
+  axis.text.y =
+    element_text(
+      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain", family = "Cambria"
+    ),
+  axis.ticks =
+    element_line(
+      size = 0.3, linetype = "solid"
+    ),
+  axis.ticks.length = unit(.15, "cm"),
+  #--- legend ---#
+  legend.text =
+    element_text(
+      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
+    ),
+  legend.title =
+    element_text(
+      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
+    ),
+  legend.key.size = unit(0.5, "cm"),
+  #--- strip (for faceting) ---#
+  strip.text = element_text(size = 10),
+  #--- plot title ---#
+  plot.title = element_text(family = "Times", face = "bold", size = 12),
+  #--- margin ---#
+  # plot.margin = margin(0, 0, 0, 0, "cm"),
+  #--- panel ---#
+  panel.grid.major = element_blank(),
+  panel.grid.minor = element_blank(),
+  panel.background = element_blank(),
+  panel.border = element_rect(fill = NA)
+)
+
+set_flextable_defaults(
+  font.family = "Cambria"
+  )
 ```
@@
   footnote(
-    value = as_paragraph("NOTE: About ymax, the units of of Mean, Nugget, and Sill are kg."),
+    value = as_paragraph("NOTE: About ymax, the units of Mean, Nugget, and Sill are kg."),
     ref_symbols = NA
@@
 ## Division of field: plots, subplots and cells (Visualization)
++ https://stackoverflow.com/questions/35633239/add-curly-braces-to-ggplot2-and-then-use-ggsave
+
++
 
@@
 
-# == plot-level field without padding area ==##
-vis_field_plot <-
-  ggplot(field_plot_sf) +
-  geom_sf(fill = NA) +
-  theme_void() +
-  labs(caption = "Bottom Title") +
-  theme(plot.title = element_text(hjust = 0.5))
-
-### ==== Example map of plot and subplots and cells ====####
-# == Preparation ==##
+# === Preparation === #
 ex_plot <- field_plot_sf[224, ]
@@
 
-#-- (1) plot-level field map (base: vis_field_withoutPadding) --#
-library(latex2exp)
+one_subplot <- ex_subplots[3,]
 
+#-- (1) plot-level field map  --#
 plot <-
@@
   geom_sf(data = ex_plot, fill = "green", size = 1) +
-  # coord_sf(expand = F) +
-  theme_void() +
+  coord_sf(expand = FALSE) +
+  # theme_void() +
   ggtitle(TeX("$12 \\times 32$ plots")) +
@@
 
-# #-- (2) create a map of subplots in a plot --##
-subplots_inPlot <- ggplot() +
+#-- (2) create a map of subplots in a plot --##
+subplots_inPlot <- 
+  ggplot() +
   geom_sf(data = ex_plot, fill = "green") +
   geom_sf(data = ex_subplots, fill = NA, size = 1) +
+  geom_sf(data = ex_subplots[2,], fill = "skyblue", size = 1) +
+  coord_sf(expand = FALSE) +
   theme_void() +
@@
 
-# #-- (3) create a map of cells in a subplot --#
+#-- (3) create a map of cells in a subplot --#
 cells_inSubplot <-
@@
   geom_sf(data = ex_cells, fill = NA) +
+  geom_sf(data = ex_cells[2,], fill = "skyblue", size = 1) +
+  coord_sf(expand = FALSE) +
   theme_void() +
@@
     theme(
-    plot.title = element_text(hjust = 0.5, margin = margin(0, 0, 10, 0))
+    plot.title = element_text(hjust = 0.5)
   )
@@
 
-# #-- (4)put them on the same map --#
-g_inset <- ggplot() +
-  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)
-
-map_all_together <-
+#-- (4)put them on the same map --#
+field_structure <-
+  ggplot() +
+  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)+
   # /*----------------------------------*/
@@
   # /*----------------------------------*/
-  g_inset +
   # --- plot level --- #
   annotation_custom(grob_plot,
-    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1
-  ) +
+    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1) +
   # --- subplot level --- #
   annotation_custom(grob_subplots_inPlot,
-    xmin = 0.57, xmax = 0.67, ymin = 0.3, ymax = 0.8
-  ) + # hight is 5
+    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7) + 
   # --- cell level --- #
   annotation_custom(grob_cells_inSubplot,
-    xmin = 0.8, xmax = 1, ymin = 0.5, ymax = 0.7
-  ) +
-  # xmin = 0.75, xmax = 1, ymin = 0.45, ymax = 0.7) +
-  # /*----------------------------------*/
-  #' ## add line segments
-  # /*----------------------------------*/
-  # --- plot-subplot (above) --- #
-  # geom_segment(aes(x = 0.386,  xend = 0.55, y = 0.547, yend = 0.73),
-  geom_segment(aes(x = 0.387, xend = 0.57, y = 0.534, yend = 0.717),
-    lineend = "round", color = "grey",
-    size = 1.5
-  ) +
-  # --- plot-subplot (below) --- #
-  # geom_segment(aes(x = 0.386, xend = 0.55, y = 0.5, yend = 0.37),
-  geom_segment(aes(x = 0.387, xend = 0.57, y = 0.485, yend = 0.352),
-    # data = arrowA,
-    lineend = "round", color = "grey",
-    size = 1.5
-  ) +
-  # --- subplot-cell (above) --- #
-  # geom_segment(aes(x = 0.65, xend = 0.805, y = 0.64, yend = 0.692),
-  geom_segment(aes(x = 0.671, xend = 0.82, y = 0.626, yend = 0.661),
-    # data = arrowA,
-    lineend = "round", color = "grey",
-    size = 1.5
-  ) +
-  # --- subplot-cell (below) --- #
-  geom_segment(aes(x = 0.671, xend = 0.82, y = 0.532, yend = 0.506),
-    # data = arrowA,
-    lineend = "round", color = "grey",
-    size = 1.5
-  ) +
+    xmin = 0.8, xmax = 0.8+0.2, ymin = 0.382, ymax = 0.382 +0.2) +
+  #/*----------------------------------*/
+  #' ## Add braces
+  #/*----------------------------------*/
+  # --- between plot and subplot --- #
+  geom_brace(aes(c(0.43,0.43+0.1), c(0.353, 0.661)), color ="red", rotate = 270, inherit.data=F) +
+  # --- between subplot and cell --- #
+  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.381, 0.549)), color ="red", rotate = 270, inherit.data=F) +
+  #/*----------------------------------*/
+  #' ## add annotations
+  #/*----------------------------------*/
+  # --- annotation for plot --- #
+  geom_segment(aes(x = 0.42, xend = 0.393, y = 0.60, yend = 0.515),
+    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
+  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.015, label = "plot") +
+  # --- annotation for subplot --- #
+  geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
+    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
+  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot") +
+  # --- annotation for cell --- #
+  geom_segment(aes(x = 0.89, xend = 0.86, y = 0.349, yend = 0.394),
+    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
+  annotate("text", x = 0.89 + 0.015, y = 0.349 - 0.01, label = "cell") +
+  # coord_sf(expand = FALSE) +
   theme_void() 
-
-#     theme(plot.margin=unit(c(0,0,0,0),"mm"))
-
-file <- here("GitControlled/Writing/field_structure.png")
-ggsave(file)
-knitr::plot_crop(file)
-dev.off()
 ```
@@
 
-```{r}
+# Create
+
+```{r, cache = TRUE}
 # /*=================================================*/
-#' # Sample CT figure (cach)
+#' # Sample CT figure 
 # /*=================================================*/
@@
 library(causalTree)
-library(here)
-library(rpart)
 library(rattle)
@@
     na.omit() %>%
-  dplyr::rename(tgtn = NPlan, tgts = SRPlan)
+    dplyr::rename(tgtn=NPlan,tgts=SRPlan)
 
 data_dt <- data.table(data_sf) %>%
-  setnames(names(.), tolower(names(.)))
+    setnames(names(.),tolower(names(.)))
 
-tgts_ls <- data_dt[, tgts] %>%
-  unique() %>%
-  sort()
+tgts_ls <- data_dt[,tgts] %>% unique() %>% sort
 
 ctree_data <- copy(data_dt) %>%
-  .[tgts %in% tgts_ls[1:2], ] %>%
-  .[, treat := ifelse(tgts == tgts_ls[2], 1, 0)] %>%
+  .[tgts %in% tgts_ls[1:2],] %>%
+  .[,treat:=ifelse(tgts==tgts_ls[2],1,0)] %>%
   #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
-  .[, yield := yield * 62.77]
+  .[,yield:= yield*62.77]
 
 tree <- causalTree(
-  yield ~ slope + ecs,
+  yield ~ slope+ecs,
   data = ctree_data,
@@
 
-opcp <- tree$cptable[, 1][which.min(tree$cptable[, 4])]
+opcp <- tree$cptable[,1][which.min(tree$cptable[,4])]
 opfit <- prune(tree, opcp)
+
 ```
 
+# Prepare sample field data set by plot, subplot, and cell resolution (one-time run)
+
 ```{r}
-source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")
+# source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")
 
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
+# pCorn <- price_table[2, pCorn]
+# pN <- price_table[2, pN]
 
@@
 # + NOTE: I needed to do the following things, because the existing raw data does not have m_error
-field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
+# field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
 
-coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))
+# coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))
 
-x=1
-coef_data_m <- coef_data[sim == x, ]
-coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
+# x=1
+# coef_data_m <- coef_data[sim == x, ]
+# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
 
-sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
-  .$reg_raw_data
+# sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
+#   .$reg_raw_data
 
-field_cell_sf <- 
-  left_join(select(field, unique_cell_id), field_cell_dt, by="unique_cell_id")%>%
-    na.omit() %>%
-    mutate(plot_id = ceiling(subplot_id/4)) %>%
-    filter(padding==1)
+# field_cell_sf <- 
+#   left_join(select(field, unique_cell_id), field_cell_dt, by="unique_cell_id")%>%
+#     na.omit() %>%
+#     mutate(plot_id = ceiling(subplot_id/4)) %>%
+#     filter(padding==1)
 
-saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))
+# saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))
 
@@
 
-field_subplot_sf <- 
-  field_cell_sf %>%
-  group_by(subplot_id, strip_id) %>%
-  summarise(
-    sim = mean(sim),
-      yield = mean(yield),
-      opt_N = mean(opt_N),
-      rate = mean(rate),
-      aa_n = mean(aa_n), 
-      alpha = mean(alpha),
-      beta = mean(beta),
-      ymax = mean(ymax),
-      alpha1 = mean(alpha1),
-      alpha2 = mean(alpha2),
-      beta1 = mean(beta1),
-      beta2 = mean(beta2),
-      ymax1 = mean(ymax1),
-      ymax2 = mean(ymax2),
-      theta_1 = mean(theta_1),
-      theta_2 = mean(theta_2)
-  ) %>%
-  mutate(unique_subplot_id = paste0(strip_id,"_",subplot_id))%>%
-  select(!c(strip_id, subplot_id))
+# field_subplot_sf <- 
+#   field_cell_sf %>%
+#   group_by(subplot_id, strip_id) %>%
+#   summarise(
+#     sim = mean(sim),
+#       yield = mean(yield),
+#       opt_N = mean(opt_N),
+#       rate = mean(rate),
+#       aa_n = mean(aa_n), 
+#       alpha = mean(alpha),
+#       beta = mean(beta),
+#       ymax = mean(ymax),
+#       alpha1 = mean(alpha1),
+#       alpha2 = mean(alpha2),
+#       beta1 = mean(beta1),
+#       beta2 = mean(beta2),
+#       ymax1 = mean(ymax1),
+#       ymax2 = mean(ymax2),
+#       theta_1 = mean(theta_1),
+#       theta_2 = mean(theta_2)
+#   ) %>%
+#   mutate(unique_subplot_id = paste0(strip_id,"_",subplot_id))%>%
+#   select(!c(strip_id, subplot_id))
 
-saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
+# saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
+
+#/*----------------------------------*/
+#' ## (3) plot-level dataset without padding area  
+#/*----------------------------------*/
+# field_plot_sf <- field_cell_sf%>%
+#     group_by(plot_id, strip_id, rate)%>%
+#     summarise()
+
+# saveRDS(field_plot_sf, here("Shared/Results/for_writing/sample_field_plot_sf.rds"))
 ```

### 2022-02-07 Writing/manuscript_cea.rmd
update font type and figure of field structure

--- 2022-02-06 Writing/manuscript_cea.rmd
@@
 
-```{r field-map, out.width="50%", fig.cap = "Partitioning of field into plots, subplots and cells"}
-# knitr::include_graphics("./GitControlled/Writing/field_structure.png")
-readPNG(here("GitControlled/Writing/field_structure.png")) %>% grid.raster()
+```{r field-map, fig.width=8, fig.height=8, fig.cap = "Partitioning of field into plots, subplots and cells"}
+field_structure
 ```
@@
 ```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
-fancyRpartPlot(opfit, sub = "")
+fancyRpartPlot(opfit,sub='')
 ```

### 2022-02-07 Writing/manuscript_cea.rmd
changes in appendix and manuscript

--- 2022-02-07 Writing/manuscript_cea.rmd
@@
 \begin{equation}
-f(N_{i}: \alpha_{i,j}, \beta_{i,j}, ymax_{i,j}) = ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) + \varepsilon^{i,j}. (\#eq:eqn6)
+f(N_{i}: \alpha_{i,j}, \beta_{i,j}, ymax_{i,j}) = ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) + \varepsilon_{i,j}. (\#eq:eqn6)
 \end{equation}
@@
 They reflect local cell-level production conditions, such as soil characteristics and topography.
-For example, $\alpha$ and $ymax$, which affect yield independently from the applied N fertilizer rate, might be interpreted as depending on the ingredient soil N content supplied by residual N, soil organic matter, etc.
+For example, $\alpha$, which represents what the yield would be when no nitrogen is applied in conjunction with $ymax$, may reflect soil organic matter and residual nitrogen from previous year's production.
+$ymax$, which determines the maximum yield attainable, may include other micro nutrients like phosphorus, soil depth among others.
 $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen].
@@
 In the second scenario, denoted "abytt," we introduced additional variables $\theta^1$ and $\theta^2$, and the researcher's data set contained values of $\alpha_{i}$, $\beta_{i}$, $ymax_{i}$, $\theta^1_{i}$ and $\theta^2_{i}$ for all subplots $i=1,\dots,1536$.
-$\theta^1$ and $\theta^2$ had no effect on yield, but they were spatially correlated with $\beta^{i}.
+$\theta^1$ and $\theta^2$ had no effect on yield, but they were spatially correlated with $\beta_{i}$.
 This scenario was meant to reflect the lack of scientific consensus about which variables explain heterogeneous yield response to N, making it likely that the researcher would include irrelevant variables like $\theta^1$ and $\theta^2$ in real-world data analysis.
@@
 We used a slightly modified version of one of the multi-stream CNN architectures proposed by @barbosa2020modeling, called "Late Fusion." Briefly stated, explanatory variables except N rate (e.g.
-$\alpha^{i,j}$, $\beta^{i,j}$, etc.) entered the model as a set of $6 \times 6$ element rasters.The input size of the N rate is treated as $1 \times 1$ because it is spatially homogeneous within each subplot.
+$\alpha_{i,j}$, $\beta_{i,j}$, etc.) entered the model as a set of $6 \times 6$ element rasters.The input size of the N rate is treated as $1 \times 1$ because it is spatially homogeneous within each subplot.
 First, each input was connected to an independent convolutional layer with eight $3 \times 3$ filters each with stride one, followed by a $2 \times 2$ max-pooling layer with stride two.
@@
 
-Let $\mathbf{\Omega^{i}}$ denote a list of subplot-level explanatory variables (soil/field characteristics).
+Let $\mathbf{\Omega_{i}}$ denote a list of subplot-level explanatory variables (soil/field characteristics).
 Further, let $\hat{g}_m(N,\mathbf{\Omega})$ denote an estimated yield response function, estimated by model $m$ ($m$ = RF, BRF, or CNN).
-Then, yield at $i$ from model $m$ is $\hat{g}_m(N,\mathbf{\Omega^{i}})$.
+Then, yield at $i$ from model $m$ is $\hat{g}_m(N,\mathbf{\Omega_{i}})$.
 The site-specific EONR for each model can then be found by solving the following profit maximization problem for all $i$ for each of the models:
@@
 \begin{equation}
-\hat{N}_{opt}^{i} = \operatorname*{argmax}_{N}(p \hat{g}_m(N, \mathbf{\Omega^{i}}) - w N), (\#eq:eqn8)
+\hat{N}^{opt}_{i} = \operatorname*{argmax}_{N}(p \hat{g}_m(N, \mathbf{\Omega_{i}}) - w N), (\#eq:eqn8)
 \end{equation}
@@
 Unlike RF, BRF, and CNN, CF estimates the impact of a binary treatment.
-In our context, CF estimates changes in yields (i.e., $\hat{\tau}_{N^{con} \rightarrow N^{tre}}(\mathbf{\Omega^{i}})$) caused by changes in N application rates from one experimental rate (control N rate, i.e., $N^{con}$) to another experimental rate (treatment N rate, i.e., $N^{tre}$).
+In our context, CF estimates changes in yields (i.e., $\hat{\tau}_{N^{con} \rightarrow N^{tre}}(\mathbf{\Omega_{i}})$) caused by changes in N application rates from one experimental rate (control N rate, i.e., $N^{con}$) to another experimental rate (treatment N rate, i.e., $N^{tre}$).
 Since we have five N application rates, four "experiments" (treatments) are identified based on four ($N^{con}$, $N^{tre}$) combinations.
@@
 For estimating site-specific EONR, the trained CF-base were used to predict site-specific changes in yields resultant from changes in application rates from $N_1$ to $N_m$ $(m\in\{2,3,4,5\})$.
-Let $\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}})$ be the the estimated treatment effect of changing subplot $i$'s application rate from $N_1$ to $N_m$ for site $i$.
+Let $\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega_{i}})$ be the the estimated treatment effect of changing subplot $i$'s application rate from $N_1$ to $N_m$ for site $i$.
 
@@
 \begin{equation}
-\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega^{i}}) = \hat{\tau}_{N_{1} \rightarrow N_{m}}(\mathbf{\Omega^{i}}). (\#eq:eqn9)
+\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega_{i}}) = \hat{\tau}_{N_{1} \rightarrow N_{m}}(\mathbf{\Omega_{i}}). (\#eq:eqn9)
 \end{equation}
@@
 The accuracy of EONR estimation was judged based on RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level.
-Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) we calculated relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N^{opt}^{i}$.
+Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) we calculated relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N^{opt}_{i}$.
 For RF, BRF, and CNN, the accuracy of yield prediction was judged based on the RMSE ($kg/ha$) of the yield prediction against the true yields at the subplot level.

### 2022-02-07 Writing/CEA_2nd_round/replies_rev_1.rmd

@@
 
-**Materials and Method to just Method: Monte Carlo Simulations?**
-
 We do see a redundancy of expalining how CF can be used to identify site-specific input recommendations.
-It is explained twice in 2.2 and 3.2.2, while 2.2 is intended for a more general case than 3.2.2 that is specific to our simulations.
+It was explained twice in 2.2 and 3.2.2, while 2.2 is intended for a more general case than 3.2.2 that is specific to our simulations.
 Therefore, we decided to take out 2.2.
-We also renamed 2.1 to "Estimating EOIR and Treatment Effects"
+We also renamed 2.1 to "Estimating EOIR and Treatment Effects."
 
@@
 The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations.
-To this core objective, ML simulations are our core method.
-For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal.
+To this core objective, ML simulation is our core method.
+For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give too much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal.
 However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well.
 Now, if we place such description inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works.
-Instead of this, we believe that it is beneficial to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted.
-Therefore, we kept 2.3 and 2.4 in the current manuscript.
+Insted, we believe that it is better to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted.
+Therefore, we kept 2.3 and 2.4 (in the previous round) in the current manuscript.
 
@@
 We take reproducibility seriously and we believe that the details we peovided in our current manuscript is appropriate and it is hard for us to further slim down the section.
-Moreover, we believe we no longer have any redundancy in this section any more.
+Moreover, we believe we no longer have any redundancy in this section.
 
@@
 
-It is degree. The unit is now provided in Appendix A.
+It is degree. The unit is now provided in the description of the figure in Appendix A. Please not that this example is just for illustrating how CF works.
 
@@
 <span style="color:blue">  
-All the formulas are now numbered. 
+All the formulas are now numbered. <span style = "color: blue;"> Shun, make sure this happens right before you submit. </span>
 </span>
@@
 Trainign dataset and test dataset are completely separate.
-Models are trained on the entirety of the train data for each simulation, and then the trained model is tested against a test dataset that are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$.
-The train dataset, however, was split into several parts when cross-validation was performed in determing the optimal hyperparameters at each simulation round.
+For a given simulation round, training dataset in another round of simulation acts as a "test" dataset.
+The "test" dataset are created independently from one another and are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$.
+Therefor, in MC simulations, a dataset in a given simulation serves as a train data, and served as a test data for another simulation round.
+The train dataset, however, was split into several parts when cross-validation was performed in determing the optimal hyperparameters within a given simulation round.
 
@@
 **8.
-I can’t open the code link (https://github.com/tmieno2/ML_VRA.git, lines 199 and 249) with my browsers (chrome, edge, and Firefox).
+I can't open the code link (https://github.com/tmieno2/ML_VRA.git, lines 199 and 249) with my browsers (chrome, edge, and Firefox).
 Please upload the code to the public research data repositories (Zenodo, Mendeley Data, figshare, Harvard Dataverse, etc.), not GitHub.
@@
 <span style="color:blue">  
-We realized that the github repository was private and that was why you were not able to access it. We made a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).
-
 The simulation codes and the data were also shared on Mendeley Data (<span style = "color: blue;"> Shun, provide the link here </span>) according to the Editor's suggestion for the ease of access.
@@
 
+<span style = "color: blue;"> Shun, make sure you cite the code and data. </span>
+
+We realized that the github repository was private and that was why you were not able to access it. We made a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).
 </span>
@@
 **9. Please convert the length units of the manuscript to international length units. (line 207)**
+
 <span style="color:blue">  
-
 All the lenth units were converted to meter (m)
-
 </span>
@@
 **10. Please add the number of rows and columns to the plots, subplots, and cells schematics in Figure 2. (line 209)**
+
 <span style="color:blue">  
-
 The number of rows and columns of plots, subplots, and cells schematics are now indicated Figure 2.
@@
 **12. The titles of 4.1 and 4.2 are confusing, please revise. (lines 410 and 457)**
+
 <span style="color:blue">  
-
 The title of 4.1 was changed to "Comparison of EONR estimation accuracy" to reflect its contents.
@@
 **13. Why there are no CNN results in Figures 8,9, and 10? (lines 439, 441, and 453)**
+
 <span style="color:blue">
 
-+ As explained in section 4.1, CNN completely failed to predict site-specific EONR because the estimated yield response function were always linear (please see the Table 1).
-Therefore, I do not think that visualizing the CNN results provide any meaningful implications to understand its performance of EONR estimation performance.
+As explained in section 4.1, CNN failed to predict site-specific EONR because the estimated yield response function were always linear (please see the Table 1).
+Consequently, I do not think that visualizing the CNN results provide any meaningful implications to understand its performance of EONR estimation performance.
+
 + I added the explanation for not showing CNN results in Figures 8,9, and 10.
 ("CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always take $62.8$ kg/ha and \$$58.99$/ha, respectively")
-
 </span>
@@
 **14. I suggest that the authors add to the supplementary material a table of the training accuracy of the different models.**
+
 <span style="color:blue">  
-
 + run simulations on training dataset, and report the results.
@@
 <span style="color:blue">  
-
+We added a new section called "Limitations and Future Studies" before the Conclustion section.
+One of the important assumptions that needs to be satisfied for CF to provides consistent estimation of treatment effects is that the treatment (N rates here) is uncorrelated with unobservable characteristics.
+Other assumtions are relatively minor.
+Note that, this is not just for CF, but also for RF, BRF, and CNN.
+Whenever the variable of interest (N rates here), their estiamtion of its impact on the dependent variable is biased in general.
+Fortunatley, in OFPE settings, we can randomize or patternize the input rates in a way that the input rates are uncorrelated to the unobserved variables.
+Therefore, the violation of this assumption is not as much of a concener as in a setting where observational data is used.
+We discuss these in the "Trial Design and Yield Data Generation for Modeling" section.
 </span>
@@
 <span style="color:blue">  
-
+We moved the descriptions of the limitations (uncertainty) of the study to a separate section as mentioned earlier in our reply to your comment 14.
 </span>

### 2022-02-07 Writing/CEA_2nd_round/replies_rev_2.rmd

---
title: "Reply to Reviewer #2"
author: Shunkei Kakimoto
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
---

# Comments:

**1. All tables and figs: No capitalization of the titles, other than first letter.**

<span style="color:blue"> 
We modified all the titles of tables and figures according to your suggestions.
</span>

**2. Fig, 1. Indicate units for slope and EC in title.**
<span style="color:blue"> 
The units of slope and EC are added in the description, which can be found in Appendix A.
</span>

**3. Table 1 and Fig. 3: show units where applicable.**
<span style="color:blue">

+ I removed Table 1. Instead, I explained about those parameters in section 3.1.3. I added units of "ymax" and "$\varepsilon$" to Figure 3.
</span>

**4. p. 21 l. 334: For example, instead of using , directly, some some topographical land features and soil properties (remove 1 some)**

<span style="color:blue"> 
The extra "some" was removed from the sentence.
</span>

**5. p. 24 l. 403: The accuracy of EONR estimation was judged based on the RMSE (/h)of EONR estimation**

<span style="color:blue"> 
The typo was corrected. 
</span>

**6. p. 26 l. 424: To examine whether this problem is a product solely of the specific choice**

<span style="color:blue">  
The grammatical error was corrected. 
</span>

**7. P. 29 l 449: Points are clustered much more tightly about the 1-to-1 line much for CF-base than RF and BRF. (remove much)**
<span style="color:blue">  
We removed "much" from the sentence.
</span>

**8. Table 3. Provide units.**
<span style="color:blue">

The unit (kg/ha) was provided in Table <span style = "color: blue;"> Shun say the table number here </span>. Similarly, units are provided to other result tables.
</span>

### 2022-02-07 Writing/appendix.rmd

@@
 
-# Appendix B: Parameter Generation
+# Appendix B: Understanding yield response functions better
+
+Another way to writing Eq. \@ref(eq:eqn6) that may help understanding the yield response (Eq. \@ref(eq:eqn6)) better conceptually is as follows:
+
+\begin{alinged}
+f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) N)) + \varepsilon. 
+\end{alinged}
+
+In this formulation, it is made clear that the base parameters $\alpha$, $\beta$, and $ymax$ are functions of a vector of field characteristics variables $\mathbf{c}=(c_1,\dots,c_K)$, which vary spatially on the field.
+
+Which of $c_1,\dots,c_K$ has an influence vary by the parameters.
+For example, $\alpha$ represents what the yield would be when no nitrogen is applied in conjunction with $ymax$ because when $N = 0$, $yield = ymax * (1-exp(\alpha))$.
+So, $\alpha$ is a function of soil organic matter and residual nitrogen among $\mathbf{c}$.
+$ymax$ determines the maximum yield attainable.
+So, $ymax$ is a function of other micro nutrients like phosphorus and soil depth among $\mathbf{c}$.
+$\beta$ reflects how efficiently the crop uses N to create grain mass.
+So, it may be a function of soil properties that affect the availability of applied N fertilizer to the crop, such as N immobilization, leaching, denitrification, and volatilization among $\mathbf{c}$.
+
+Each subplot has different values of $\mathbf{c}$, and yield at the subplot level can be written as
+
+\begin{equation}
+f(N_{i}, \mathbf{c}_{i}) = ymax(\mathbf{c}_{i})(1-exp(\alpha(\mathbf{c}_{i}) + \beta(\mathbf{c}_{i}) N_{i})) + \varepsilon_{i}. 
+\end{equation}
+
+The simplified notation of this equation, where $c_i$ is dropped, is \@ref(eq:eqn6) in section <span style = "color: blue;"> section number here </span>.
+
+<span style = "color: blue;"> Shun, number the equations </span>
+
+# Appendix C: Parameter generation
 
 ## Base parameters $\alpha$, $\beta$, and $ymax$ {#par-gen}
-Parameters $\alpha^{i,j}$, $\beta^{i,j}$, $ymax^{i,j}$, and $\varepsilon^{i,j}$ were modeled as spatially autocorrelated using unconditional Gaussian geostatistical simulation based on the spherical variogram model.
+Parameters $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$ were modeled as spatially autocorrelated using unconditional Gaussian geostatistical simulation based on the spherical variogram model.
 The `gstat` package (version 2.0.6 [@gstat1; @gstat2]) in R was used for this purpose
 
-Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha^{i,j}$, $\beta^{i,j}$, $ymax^{i,j}$, and $\varepsilon^{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
+Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
 (Codes used to generate parameter values are available at https://github.com/tmieno2/ML_VRA.git.) The range and nugget of all parameters were assumed to be $400$ m and 0.
@@
 
-```{r fig-optN, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a spatial distribution of true optimal N rate"}
+<span style = "color: blue;"> Shun, combnine all the figures </span>
 
-vis_optN_cell
+```{r variogram-parameters, tab.cap = "The Parameters for the Variogram Models"}
+variogram_tb
 ```
 
-```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics", cache = TRUE}
-# field_alpha + field_beta + field_ymax
-grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol = 2, nrow = 2)
+```{r fig-parameters, fig.width=7, fig.height=9, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics", cache = TRUE}
+
+field_alpha + field_beta + field_ymax + field_m_error + vis_optN_cell + plot_layout(ncol = 2)
 ```
@@
 For scenarios "aabbyy" and "aabbyytt", each of the base parameters $\alpha$, $\beta$, and $ymax$ are splitted into two part in a spatially correlated manner.
-Speficiallu, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r_{\alpha}^{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r_{\beta}^{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r_{ymax}^{i,j} \in (0,1)$ to the ${ymax}^{i,j}$ variable.
+Speficiallu, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r^{\alpha}_{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r^{\beta}_{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r^{ymax}_{i,j} \in (0,1)$ to the ${ymax}_{i,j}$ variable.
 Each of the weight variables are generated using unconditional Gaussian geostatistical simulation just like the base parameters.
-(There was no spatial correlation between the $r_{\alpha}^{i,j}$ and $r_{\beta}^{i,j}$ data, between $r_{\alpha}^{i,j}$ and $r_{ymax}^{i,j}$ data, or between $r_{\beta}^{i,j}$ and $r_{ymax}^{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha^{i,j}$, $\beta^{i,j}$ and $ymax^{i,j}$.
+(There was no spatial correlation between the $r^{\alpha}_{i,j}$ and $r^{\beta}_{i,j}$ data, between $r^{\alpha}_{i,j}$ and $r^{ymax}_{i,j}$ data, or between $r^{\beta}_{i,j}$ and $r^{ymax}_{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha_{i,j}$, $\beta_{i,j}$ and $ymax_{i,j}$.
 These were
-$\alpha_{1}^{i,j} = r_{\alpha}^{i,j} \alpha^{i,j}$, $\alpha_{2}^{i,j} = (1- r_{\alpha}^{i,j}) \alpha^{i,j}$,
-$\beta_{1}^{i,j} = r_{\beta}^{i,j} \beta^{i,j}$, $\beta_{2}^{i,j} = (1- r_{\beta}^{i,j}) \beta^{i,j}$,
-$ymax_{1}^{i,j} = r_{ymax}^{i,j} ymax^{i,j}$, and $ymax_{2}^{i,j} = (1- r_{ymax}^{i,j}) ymax^{i,j}$.
+$\alpha_{1}_{i,j} = r^{\alpha}_{i,j} \alpha_{i,j}$, $\alpha_{2}_{i,j} = (1- r^{\alpha}_{i,j}) \alpha_{i,j}$,
+$\beta_{1}_{i,j} = r^{\beta}_{i,j} \beta_{i,j}$, $\beta_{2}_{i,j} = (1- r^{\beta}_{i,j}) \beta_{i,j}$,
+$ymax_{1}_{i,j} = r^{ymax}_{i,j} ymax_{i,j}$, and $ymax_{2}_{i,j} = (1- r^{ymax}_{i,j}) ymax_{i,j}$.
 The codes used to implement the abovementioned parameter splitting is available at https://github.com/tmieno2/ML_VRA.git.
+
+<span style = "color: blue;"> Shun, provide the link to Mandeley data and cite it </span>

### 2022-02-07 Codes/PrepareResults.rmd

@@
 
-opcp <- tree$cptable[,1][which.min(tree$cptable[,4])]
+opcp <- tree$cptable[, 1][which.min(tree$cptable[, 4])]
 opfit <- prune(tree, opcp)
@@
 ```
-
-# Prepare sample field data set by plot, subplot, and cell resolution (one-time run)
-
-```{r}
-# source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")
-
-# pCorn <- price_table[2, pCorn]
-# pN <- price_table[2, pN]
-
-# /*=================================================*/
-#' # Field Data Sets
-# /*=================================================*/
-
-#/*----------------------------------*/
-#' ## (1) cell-level data set 
-#/*----------------------------------*/
-# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
-# field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
-
-# coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))
-
-# x=1
-# coef_data_m <- coef_data[sim == x, ]
-# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
-
-# sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
-#   .$reg_raw_data
-
-# field_cell_sf <- 
-#   left_join(select(field, unique_cell_id), field_cell_dt, by="unique_cell_id")%>%
-#     na.omit() %>%
-#     mutate(plot_id = ceiling(subplot_id/4)) %>%
-#     filter(padding==1)
-
-# saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))
-
-#/*----------------------------------*/
-#' ## (2) subplot-level field without padding area 
-#/*----------------------------------*/
-
-# field_subplot_sf <- 
-#   field_cell_sf %>%
-#   group_by(subplot_id, strip_id) %>%
-#   summarise(
-#     sim = mean(sim),
-#       yield = mean(yield),
-#       opt_N = mean(opt_N),
-#       rate = mean(rate),
-#       aa_n = mean(aa_n), 
-#       alpha = mean(alpha),
-#       beta = mean(beta),
-#       ymax = mean(ymax),
-#       alpha1 = mean(alpha1),
-#       alpha2 = mean(alpha2),
-#       beta1 = mean(beta1),
-#       beta2 = mean(beta2),
-#       ymax1 = mean(ymax1),
-#       ymax2 = mean(ymax2),
-#       theta_1 = mean(theta_1),
-#       theta_2 = mean(theta_2)
-#   ) %>%
-#   mutate(unique_subplot_id = paste0(strip_id,"_",subplot_id))%>%
-#   select(!c(strip_id, subplot_id))
-
-# saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
-
-#/*----------------------------------*/
-#' ## (3) plot-level dataset without padding area  
-#/*----------------------------------*/
-# field_plot_sf <- field_cell_sf%>%
-#     group_by(plot_id, strip_id, rate)%>%
-#     summarise()
-
-# saveRDS(field_plot_sf, here("Shared/Results/for_writing/sample_field_plot_sf.rds"))
-```

### 2022-02-07 Codes/PrepareResults.rmd

@@
 ```{r}
+
 theme_update(

### 2022-02-08 Writing/manuscript_cea.rmd
test
Update figures and tables

@@
 
-(field_Ndesign + ggtitle("(a) Trial Design")) |
-  (vis_yield_subplot + ggtitle("(b) Simulated Yield Level"))
+# (field_Ndesign + ggtitle("(a) Trial Design")) |
+#   (vis_yield_subplot + ggtitle("(b) Simulated Yield Level"))
+field_Ndesign | vis_yield_subplot
 ```
@@
 report_table_optN
-# knit_print(report_table_optN)
 ```
@@
 
-`r ftext('NOTE: The red line in the figures denotes the 1-to-1 line to show the ideal relationship between true and estimated treatment effects.', fp_text(font.size = 9))`
+`r ftext('NOTE: The red line in the figures denotes the 1-to-1 line to show the ideal relationship between true and estimated treatment effects.', fp_text(font.size = 9, font.family = "Times New Roman"))`
 
@@
 
-`r ftext('NOTE: The red line in the figures denotes the best-fit line to explain the relationship between the RMSEs of EONR prediction and yield prediction.', fp_text(font.size = 9))`
+`r ftext('NOTE: The red line in the figures denotes the best-fit line to explain the relationship between the RMSEs of EONR prediction and yield prediction.', fp_text(font.size = 9, font.family = "Times New Roman"))`
 

### 2022-02-08 Codes/PrepareResults.rmd

@@
 knitr::opts_chunk$set(
-  cache = TRUE
+  # cache = TRUE
+  cache = FALSE
 )
@@
 # --- figure making --- #
+# library(extrafont)
 library(ggbrace)
@@
 library(flextable)
+library(ftExtra)
 library(officer)
@@
 ```{r}
+theme_figure <- 
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    axis.text.x = element_blank(),
+    axis.text.y = element_blank(),
+    axis.ticks = element_blank(),
+    rect = element_blank(),
+    text  = element_text(family = "Times New Roman")
+    )
 
-theme_update(
-  axis.title.x =
-    element_text(
-      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain", family = "Cambria"
-    ),
-  axis.title.y =
-    element_text(
-      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain", family = "Cambria"
-    ),
-  axis.text.x =
-    element_text(
-      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain", family = "Cambria"
-    ),
-  axis.text.y =
-    element_text(
-      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain", family = "Cambria"
-    ),
-  axis.ticks =
-    element_line(
-      size = 0.3, linetype = "solid"
-    ),
-  axis.ticks.length = unit(.15, "cm"),
-  #--- legend ---#
-  legend.text =
-    element_text(
-      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
-    ),
-  legend.title =
-    element_text(
-      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
-    ),
-  legend.key.size = unit(0.5, "cm"),
-  #--- strip (for faceting) ---#
-  strip.text = element_text(size = 10),
-  #--- plot title ---#
-  plot.title = element_text(family = "Times", face = "bold", size = 12),
-  #--- margin ---#
-  # plot.margin = margin(0, 0, 0, 0, "cm"),
-  #--- panel ---#
+theme_dist <- 
+  theme_bw()+
+  theme(
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
-  panel.background = element_blank(),
-  panel.border = element_rect(fill = NA)
+    strip.text.x = element_text(size = 12, face = "bold"),
+    legend.title = element_text(size = 12, face = "bold"),
+    legend.text = element_text(size = 12, face = "bold"),
+    legend.position = "bottom",
+    text  = element_text(family = "Times New Roman")
     )
 
+  # theme(    
+  #   strip.text.x = element_text(size = 12, face = "bold"),
+  #   legend.title = element_text(size = 12, face = "bold"),
+  #   legend.text = element_text(size = 12, face = "bold"),
+  #   legend.position = "bottom",
+  #   text  = element_text(family = "Times New Roman")
+  # )
+
 set_flextable_defaults(
-  font.family = "Cambria"
+  font.family = "Times New Roman"
   )
@@
 ```{r}
+
 variogram_tb <-
   data.frame(
-    Parameters = c("ymax_ij", "alpha_ij", "beta_ij", "varepsilon_ij"),
+    Parameters = c("alpha_ij", "beta_ij", "ymax_ij", "varepsilon_ij"),
     Range = c(400, 400, 400, 400),
-    Mean = c(12000, -0.5, format(c(0, 0))),
+    Mean = c(-0.5, format(0), 12000, format(0)),
     Nugget = format(c(0, 0, 0, 0)),
-    Sill = c(2000000, 0.02, format(1, nsmall = 1), 0.015)
+    Sill = c(0.02, format(1, nsmall = 1), 2000000, 0.015)
   ) %>%
   flextable() %>%
-  compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sup(as_i("i,j")))) %>%
-  compose(i = 2, j = 1, part = "body", value = as_paragraph(as_i("\U03B1"), as_sup(as_i("i,j")))) %>%
-  compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("\U03B2"), as_sup(as_i("i,j")))) %>%
-  compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sup(as_i("i,j")))) %>%
-  compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
-  compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("6"))) %>%
-  compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
-  compose(i = 2, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
+  compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("\U03B1"), as_sub(as_i("i,j")))) %>%
+  compose(i = 2, j = 1, part = "body", value = as_paragraph(as_i("\U03B2"), as_sub(as_i("i,j")))) %>%
+  compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sub(as_i("i,j")))) %>%
+  compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sub(as_i("i,j")))) %>%
+  compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
+  compose(i = 3, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
+  compose(i = 3, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("6"))) %>%
   compose(i = 4, j = 5, part = "body", value = as_paragraph("1.5", "\U2A2F", "10", as_sup("-2"))) %>%
@@
   footnote(
-    value = as_paragraph("NOTE: About ymax, the units of Mean, Nugget, and Sill are kg."),
+    value = as_paragraph("NOTE: Only in ", as_i("ymax"), " are consistent units of measurement used for Mean, Nugget, and Sill ", "(", as_i("kg"),")."),
     ref_symbols = NA
@@
 #-- (1) plot-level field map  --#
+
 plot <-
@@
   coord_sf(expand = FALSE) +
-  # theme_void() +
-  ggtitle(TeX("$12 \\times 32$ plots")) +
-  theme(plot.title = element_text(hjust = 0.5))
+  ggtitle("12 \u00D7 12 subplots") +
+  # ggtitle(TeX("$12 \\times 32$ plots")) +
+  theme_figure
 
@@
   theme_void() +
-  ggtitle(TeX("$4 \\times 1$ subplots")) +
-  theme(plot.title = element_text(hjust = 0.5))
+  # ggtitle(TeX("$4 \\times 1$ subplots")) +
+  ggtitle("4 \u00D7 1 subplots") +
+  theme_figure
 
@@
   theme_void() +
-  ggtitle(TeX("$6 \\times 6$ cells")) +
-    theme(
-    plot.title = element_text(hjust = 0.5)
-  )
+  # ggtitle(TeX("$6 \\times 6$ cells")) +
+  ggtitle("6 \u00D7 6 cells") +
+  theme_figure
 
@@
   # --- annotation for plot --- #
-  geom_segment(aes(x = 0.42, xend = 0.393, y = 0.60, yend = 0.515),
+  geom_segment(aes(x = 0.42, xend = 0.383, y = 0.60, yend = 0.52),
     arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
-  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.015, label = "plot") +
+  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.015, label = "plot", family="Times New Roman") +
   # --- annotation for subplot --- #
@@
     arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
-  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot") +
+  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot", , family="Times New Roman") +
   # --- annotation for cell --- #
@@
     arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
-  annotate("text", x = 0.89 + 0.015, y = 0.349 - 0.01, label = "cell") +
-  # coord_sf(expand = FALSE) +
+  annotate("text", x = 0.89 + 0.015, y = 0.349 - 0.01, label = "cell", , family="Times New Roman") +
   theme_void()
@@
   labs(fill = "Nitrogen rate\n  (kg/ha)") +
-  theme_void()
+  ggtitle("(a) Trial Design") +
+  theme_figure
 ```
@@
 ```{r, dependson = "setup"}
-# === cell-level === #
-vis_yield_cell <-
-  ggplot(field_cell_sf) +
-  geom_sf(aes(fill = yield), size = 0) +
-  scale_fill_viridis_c() +
-  labs(fill = "Yield Level\n  (kg/ha)") +
-  theme_void()
-
 # === subplot-level === #
@@
   labs(fill = "Yield Level\n  (kg/ha)") +
-  theme_void()
+  ggtitle("(b) Simulated Yield Level") +
+  theme_figure
 ```
@@
 ```{r, dependson = "setup"}
-# === cell-level === #
-vis_optN_cell <-
-  ggplot(field_cell_sf) +
-  geom_sf(aes(fill = opt_N), size = 0) +
-  scale_fill_viridis_c() +
-  labs(fill = "EONR (kg/ha)") +
-  theme_void()
+
 ```
@@
 ```{r, dependson = "setup"}
-#### ==== ymax map ====####
+# === alpha map === #
+field_alpha <-
+  ggplot(field_cell_sf) +
+  geom_sf(aes(fill = alpha), size = 0) +
+  scale_fill_viridis_c() +
+  ggtitle(expression("(1) " ~alpha)) +
+  theme(legend.title = element_blank()) +
+  theme_figure
+
+# === beta map === #
+field_beta <-
+  ggplot(field_cell_sf) +
+  geom_sf(aes(fill = beta), size = 0) +
+  scale_fill_viridis_c() +
+  ggtitle(expression("(2) " ~beta)) +
+  theme(legend.title = element_blank()) +
+  theme_figure
+
+# === ymax map === #
 field_ymax <-
@@
   scale_fill_viridis_c() +
-  ggtitle("(1) ymax") +
-  labs(fill = "kg/ha") +
-  theme_void()
+  ggtitle("(3) ymax (kg/ha)") +
+  theme(legend.title = element_blank()) +
+  theme_figure
 
-#### ==== alpha map ====####
-field_alpha <-
-  ggplot(field_cell_sf) +
-  geom_sf(aes(fill = alpha), size = 0) +
-  scale_fill_viridis_c() +
-  ggtitle(TeX("(2)  $\\alpha$")) +
-  # ggtitle(expression("(2) " ~alpha)) +
-  theme_void() +
-  theme(legend.title = element_blank())
-
-#### ==== beta map ====####
-field_beta <-
-  ggplot(field_cell_sf) +
-  geom_sf(aes(fill = beta), size = 0) +
-  scale_fill_viridis_c() +
-  ggtitle(TeX("(3)  $\\beta$")) +
-  theme_void() +
-  theme(legend.title = element_blank())
-
-#### ==== m_error map ====#### (this should be m_error*det_yield, not just m_error)
+# === m_error map === #
+# + this should be m_error*det_yield, not just m_error
 # m_error_sf <-  left_join(field, coef_data_m, by="unique_cell_id")
@@
   scale_fill_viridis_c() +
-  ggtitle(TeX("(4)  $\\epsilon$")) +
-  labs(fill = "kg/ha") +
-  theme_void()
+  ggtitle(expression(paste("(4) " ~epsilon, " (kg/ha)"))) +
+  theme(legend.title = element_blank()) +
+  theme_figure
 
-# grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2, nrow=2)
+# === optN map === #
+field_optN <-
+  ggplot(field_cell_sf) +
+  geom_sf(aes(fill = opt_N), size = 0) +
+  scale_fill_viridis_c() +
+  ggtitle("(5) EONR (kg/ha)") +
+  theme(legend.title = element_blank()) +
+  theme_figure
 ```
@@
 #--- for reporting the results of  yield prediction and EONR estimation ---#
-report_res_allML <-
+res_allML <-
   rbind(res_forest_all_honest, res_CNN_all) %>%
-  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF_stepwise", "CF_base"))] %>%
+  .[Method %in% c("RF", "BRF", "CNN", "CF_base")] %>%
+  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF_base"))] %>%
   .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]
-
-report_res_subsetML <-
-  report_res_allML %>%
-  .[Method != "CF_stepwise", ]
 ```
@@
 rmse_y_all <-
-  copy(report_res_allML) %>%
+  copy(res_allML) %>%
   .[Method %in% c("RF", "BRF", "CNN")]
-
-# ==== Distribution of RMSE of predicted yields ====#
-plot_dis_y <-
-  copy(rmse_y_all) %>%
-  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN"))] %>%
-  ggplot() +
-  geom_density(aes(x = rmse_y, fill = Method), alpha = 0.6) +
-  facet_wrap(~Model, ncol = 1) +
-  labs(x = "RMSE") +
-  # labs(x = "Mean R-squared")+
-  theme_few() +
-  theme(
-    strip.text.x = element_text(size = 12, face = "bold"),
-    legend.title = element_text(size = 12, face = "bold"),
-    legend.text = element_text(size = 12, face = "bold"),
-    legend.position = "bottom"
-  )
 
@@
   stat_regline_equation(
-    # label.x.npc = "right",
-    # label.y.npc = "top",
     label.x = 2150, label.y = 85,
@@
   ) +
-  # geom_abline(slope=1, intercept=0, color="red")+
   guides(
@@
     legend.position = "bottom"
-  )
+  ) +
+  theme_figure
 
@@
 # === Distribution of RMSE of EONR estimates === #
-
 plot_dis_optN <-
-  copy(report_res_subsetML) %>%
-  .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
+  copy(res_allML) %>%
+  # .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
   .[, Method := case_when(
-    # Method == "CF_stepwise" ~ "CF-stepwise",
     Method == "CF_base" ~ "CF-base",
     Method == "RF" ~ "RF",
-    Method == "BRF" ~ "BRF"
+    Method == "BRF" ~ "BRF",
+    Method == "CNN" ~ "CNN"
   )] %>%
@@
   # .[, Method:=factor(Method, levels = c("RF", "BRF", "CF-stepwise", "CF-base"))]%>%
-  .[, Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
+  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF-base"))] %>%
   .[, Model := factor(Model,
@@
   labs(x = "RMSE (kg/ha)") +
-  theme_few() +
-  theme(
-    strip.text.x = element_text(size = 12, face = "bold"),
-    legend.title = element_text(size = 12, face = "bold"),
-    legend.text = element_text(size = 12, face = "bold"),
-    legend.position = "bottom"
-  )
+  theme_dist
 
@@
 table_optN_prep <-
-  copy(report_res_subsetML) %>%
+  copy(res_allML) %>%
   .[, .(
@@
 piLoss_density <-
-  report_res_subsetML[Method != "CNN", ] %>%
+  copy(res_allML) %>%
   .[, Method := case_when(
@@
     Method == "RF" ~ "RF",
-    Method == "BRF" ~ "BRF"
+    Method == "BRF" ~ "BRF",
+    Method == "CNN" ~ "CNN"
   )] %>%
@@
   )] %>%
-  .[, Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
+  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF-base"))] %>%
   .[, Model := factor(Model,
@@
   ggplot() +
-  geom_density(aes(x = Mean, fill = Method), alpha = 0.5) +
+  geom_density(aes(x = Mean, fill = Method), alpha = 0.7) +
   # scale_fill_viridis(discrete = TRUE, alpha=0.5) +
   # scale_fill_viridis_d()+
-  # labs(x = expression(hat(pi)["loss"], " $/ha")))+
-  labs(x = TeX("$\\hat{pi}_{loss}$ (\\$/ha)")) +
+  labs(x = expression(paste(hat(pi)["loss"], " ($/ha)"))) +
+  # labs(x = TeX("$\\hat{pi}_{loss}$ (\\$/ha)")) +
   facet_wrap(~Model, ncol = 1) +
-  theme_few() +
-  theme(
-    strip.text.x = element_text(size = 12, face = "bold"),
-    legend.title = element_text(size = 12, face = "bold"),
-    legend.text = element_text(size = 12, face = "bold"),
-    legend.position = "bottom"
-  )
+  theme_dist
+
 ```
@@
     legend.position = "bottom"
-  )
+  ) +
+  theme_figure
 ```
@@
 ```
+
+# Preparation for exmaple field maps (one-time run)
+
+```{r}
+# source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")
+
+# pCorn <- price_table[2, pCorn]
+# pN <- price_table[2, pN]
+
+# /*=================================================*/
+#' # Field Data Sets
+# /*=================================================*/
+
+#/*----------------------------------*/
+#' ## (1) cell-level data set 
+#/*----------------------------------*/
+# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
+# field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
+
+# coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))
+
+# x=1
+# coef_data_m <- coef_data[sim == x, ]
+# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
+
+# sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
+#   .$reg_raw_data
+
+# field_cell_sf <- 
+#   left_join(dplyr::select(field, unique_cell_id), sample_dt_cell, by="unique_cell_id")%>%
+#     na.omit() %>%
+#     mutate(plot_id = ceiling(subplot_id/4)) %>%
+#     filter(padding==1)
+
+# saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))
+
+#/*----------------------------------*/
+#' ## (2) subplot-level field without padding area 
+#/*----------------------------------*/
+
+# field_subplot_sf <- 
+#   field_cell_sf %>%
+#   group_by(subplot_id, strip_id) %>%
+#   summarise(
+#     sim = mean(sim),
+#       yield = mean(yield),
+#       opt_N = mean(opt_N),
+#       rate = mean(rate),
+#       aa_n = mean(aa_n), 
+#       alpha = mean(alpha),
+#       beta = mean(beta),
+#       ymax = mean(ymax),
+#       alpha1 = mean(alpha1),
+#       alpha2 = mean(alpha2),
+#       beta1 = mean(beta1),
+#       beta2 = mean(beta2),
+#       ymax1 = mean(ymax1),
+#       ymax2 = mean(ymax2),
+#       theta_1 = mean(theta_1),
+#       theta_2 = mean(theta_2)
+#   ) %>%
+#   mutate(unique_subplot_id = paste0(strip_id,"_",subplot_id))%>%
+#   dplyr::select(!c(strip_id, subplot_id))
+
+# saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
+
+#/*----------------------------------*/
+#' ## (3) plot-level dataset without padding area  
+#/*----------------------------------*/
+# field_plot_sf <- field_cell_sf%>%
+#     group_by(plot_id, strip_id, rate)%>%
+#     summarise()
+
+# saveRDS(field_plot_sf, here("Shared/Results/for_writing/sample_field_plot_sf.rds"))
+```

### 2022-02-08 Codes/PrepareResults.rmd
1. position of R2 labels are changed and the figure height increased to 7.5 2. minor changes in manuscript

@@
   # scale_colour_manual(values= "red") +
-  geom_smooth(method = "lm", se = FALSE, color = "red", size = 1) +
+  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
   stat_regline_equation(
-    label.x = 2150, label.y = 85,
-    aes(label = ..rr.label..)
+    label.x = 2050, label.y = 90,
+    aes(label = ..rr.label..),
+    size = 3
   ) +
@@
   ) +
+  ylim(NA, 95) +
   labs(y = " RMSE of EONR Estimation (kg/ha)") +

### 2022-02-08 Writing/manuscript_cea.rmd
minor changes in manuscript
1. position of R2 labels are changed and the figure height increased to 7.5 2. minor changes in manuscript

@@
 \begin{equation}
-\hat{N}^{opt}_{i} = \operatorname*{argmax}_{N}(p \hat{g}_m(N, \mathbf{\Omega_{i}}) - w N), (\#eq:eqn8)
+\hat{N}^{opt}_{i} = \operatorname*{argmax}_{N}(p \cdot\hat{g}_m(N, \mathbf{\Omega_{i}}) - w \cdot N), (\#eq:eqn8)
 \end{equation}
@@
 
-```{r plot-y-optN, fig.width=7, fig.height=7, fig.cap = "The relationship in the performance between EONR estimation and yield prediction by ML methods and modeling scenarios"}
+```{r plot-y-optN, fig.width=7, fig.height=7.5, fig.cap = "The relationship in the performance between EONR estimation and yield prediction by ML method and modeling scenario"}
 fig_y_optN

### 2022-02-08 Codes/PrepareResults.R

@@ -1,4 +1,4 @@
-## ----set-up, cache = F------------------------------------------------------------------------
+## ----set-up, cache = F-------
 library(knitr)
 library(here)
 
@@ -9,7 +9,7 @@ knitr::opts_chunk$set(
   cache = FALSE
 )
 
-## ----packages, cache = FALSE, include = FALSE-------------------------------------------------
+## ----packages, cache = FALSE, include = FALSE----
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -37,7 +37,7 @@ library(modelsummary)
 library(latex2exp)
 
 
-## ---------------------------------------------------------------------------------------------
+## ----------------------------
 theme_figure <- 
   theme(
     plot.title = element_text(hjust = 0.5),
@@ -73,7 +73,7 @@ set_flextable_defaults(
   )
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE----------------------------------------
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE----
 # field <- readRDS("Shared/Data/for_Simulations/field_padding.rds") %>%
 #     filter(padding==1)%>%
 #     dplyr::select(unique_cell_id)
@@ -94,7 +94,7 @@ field_cell_sf <-
   readRDS()
 
 
-## ---------------------------------------------------------------------------------------------
+## ----------------------------
 
 
 
@@ -135,7 +135,7 @@ variogram_tb <-
   autofit()
 
 
-## ----field-map-visualization, dependson = "setup"---------------------------------------------
+## ----field-map-visualization, dependson = "setup"----
 
 # === Preparation === #
 ex_plot <- field_plot_sf[224, ]
@@ -233,7 +233,7 @@ field_structure <-
   theme_void()
 
 
-## ---- dependson = "setup"---------------------------------------------------------------------
+## ---- dependson = "setup"----
 field_Ndesign <-
   ggplot() +
   geom_sf(
@@ -247,7 +247,7 @@ field_Ndesign <-
   theme_figure
 
 
-## ---- dependson = "setup"---------------------------------------------------------------------
+## ---- dependson = "setup"----
 # === subplot-level === #
 vis_yield_subplot <-
   ggplot(field_subplot_sf) +
@@ -258,11 +258,11 @@ vis_yield_subplot <-
   theme_figure
 
 
-## ---- dependson = "setup"---------------------------------------------------------------------
[…]

### 2022-02-08 Codes/PrepareResults.rmd

@@
 
-# Treatment effect comparison (CF-base vs RF vs BRF)
+# Treatment effect comparison
 
@@
     Method == "BRF" ~ "BRF",
+    Method == "CNN" ~ "CNN",
     Method == "CF_base" ~ "CF-base"
   )] %>%
-  .[, Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
+  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF-base"))] %>%
   ggplot() +
-  geom_point(aes(x = true_tau_base, y = tau_base), size = 0.5) +
+  geom_point(aes(x = true_te_base, y = te_base), size = 0.5) +
   geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +

### 2022-02-08 Writing/CEA_2nd_round/replies_rev_1.rmd
final changes before Dave's review

@@
 title: "Reply to Reviewer #1"
-author: Shunkei Kakimoto
 output:
   bookdown::word_document2:
-    fig_caption: yes
     number_sections: no
-    global_numbering: true
-    reference_docx: word_template.docx
+    reference_docx: word_template_format.docx
 ---
 
-# Comments:
+Thank you so much for your comments.
+By addressing them, we believe the manuscript is improved significantly.
+You can find our replies to your comments.
+Your comments are in bold, and out replies are in a regular font.
+
+<br>
 
@@
 Yes, we agree with your point, and we have decided to simply drop it from our highlights.
+</span>
 
-</span>
+<br>
 
@@
 <span style="color:blue">
+
+<br>
 
@@
 Therefore, we kept 2.3 and 2.4 (in the previous round) in the current manuscript.
+</span>
 
-</span>
+<br>
 
@@
 <span style="color:blue">  
-
 In rereponse to this comments, we made several changes.
@@
 Moreover, we believe we no longer have any redundancy in this section.
-
 </span>
 
+<br>
+
 **4. What is the unit of the topographical slope？ (line 131)**
+
 <span style="color:blue">  
-
 It is degree. The unit is now provided in the description of the figure in Appendix A. Please not that this example is just for illustrating how CF works.
-
 </span>
 
+<br>
+
 **5. There are 3 numbers in each small frame of Figure 1, please describe the meaning of each number in detail in the figure caption. (line 137)**
+
 <span style="color:blue">  
+Explanations for those numbers are added as a footnote to the figure. The figure is now in the appendix and called Figure A.1. 
+</span>
 
-The explanation for those numbers are added as a footnote to the figure (Figure <span style = "color: blue;"> Shun, figure number </span>). 
-</span>
+<br>
 
@@
 
+<br>
+
 **7. What are the exact number and proportion of test set training sets? (line 192)**
+
 <span style="color:blue">  
-
 We aplogogize that we are not clear on this respect.
@@
 Trainign dataset and test dataset are completely separate.
-For a given simulation round, training dataset in another round of simulation acts as a "test" dataset.
-The "test" dataset are created independently from one another and are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$.
-Therefor, in MC simulations, a dataset in a given simulation serves as a train data, and served as a test data for another simulation round.
+For a given simulation round, the training dataset in another round of simulation acts as a "test" dataset.
+These datasets are created independently from one another and are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$.
+Therefor, in MC simulations, the dataset in a given simulation serves as a train dataset, and served as a test data for another simulation round.
 The train dataset, however, was split into several parts when cross-validation was performed in determing the optimal hyperparameters within a given simulation round.
@@
 Furtehr, each of the "train" datasets are generated independet of one another.
-Thefore, for a particular simulation round, the dataset in any of the other simualtions can serve as a valid test dataset.
+Thefore, for a particular simulation round, the dataset in any of the other simualtion rounds can serve as a valid test dataset.
 This practice avoid creating another set of 1000 simulations fields unnecessarily."
+</span>
 
-</span>
+<br>
 
@@
 
+<br>
+
 **9. Please convert the length units of the manuscript to international length units. (line 207)**
@@
 </span>
+
+<br>
 
@@
 
+<br>
+
 **11. The titles of sections 3.2.1 and 3.2.2 do not provide useful information to the readers, please revise the titles. (lines 342 and 373)**
@@
 <span style="color:blue">  
-We realized that section 3.1 has also a bad title.
+We realized that section 3.1 also had a uninformative title.
 Therefore, we changed it to "Training Models and Estimating Site-specific EONRs".
@@
 The title of section 4.2 was changed to "The relationship between yield and EONR prediction performances".
+They acurrately reflect what they describe.
 </span>
+
+<br>
 
@@
 As explained in section 4.1, CNN failed to predict site-specific EONR because the estimated yield response function were always linear (please see the Table 1).
-Consequently, I do not think that visualizing the CNN results provide any meaningful implications to understand its performance of EONR estimation performance.
+Therefore, we thought that visualizing the CNN results are not insightful.
+However, we have decided to include CNN results to Figures 8, 9, and 10 in the previous version.
+The figures are now Figures 3, 4, and 5.
 
-+ I added the explanation for not showing CNN results in Figures 8,9, and 10.
-("CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always take $62.8$ kg/ha and \$$58.99$/ha, respectively")
 </span>
+
+<br>
 
@@
 <span style="color:blue">  
-+ run simulations on training dataset, and report the results.
+Shun is running simulations on training dataset and will report the results.
 </span>
+
+<br>
 
@@
 
+<br>
+
 **16. Please revise the conclusion. Most of the content is discussing the uncertainty of the study. Please move the statement about uncertainty to a separate uncertainty section.**

### 2022-02-08 Writing/CEA_2nd_round/replies_rev_2.rmd
final changes before Dave's review

@@
 title: "Reply to Reviewer #2"
-author: Shunkei Kakimoto
 output:
@@
     global_numbering: true
-    reference_docx: word_template.docx
+    reference_docx: word_template_format.docx
 ---
@@
 **2. Fig, 1. Indicate units for slope and EC in title.**
+
 <span style="color:blue"> 
@@
 
-+ I removed Table 1. Instead, I explained about those parameters in section 3.1.3. I added units of "ymax" and "$\varepsilon$" to Figure 3.
+Units are added to the table and figure where applicable. They are now in Appendix C.
 </span>
@@
 **7. P. 29 l 449: Points are clustered much more tightly about the 1-to-1 line much for CF-base than RF and BRF. (remove much)**
+
 <span style="color:blue">  
@@
 **8. Table 3. Provide units.**
+
 <span style="color:blue"> 
-
-The unit (kg/ha) was provided in Table <span style = "color: blue;"> Shun say the table number here </span>. Similarly, units are provided to other result tables.
+The unit (kg/ha) was provided in the table (it is now Table 2). Similarly, units are provided to the other result tables.
 </span>

### 2022-02-08 Writing/manuscript_cea.rmd
final changes before Dave's review

@@
 Furtehr, each of the "train" datasets are generated independet of one another.
-Thefore, for a particular simulation round, the dataset in any of the other simualtions can serve as a valid test dataset.
+Thefore, for a particular simulation round, the dataset in any of the other simualtion rounds can serve as a valid test dataset.
 This practice avoid creating another set of 1000 simulations fields unnecessarily.
@@
 
-We examined the use of CF-base for site-specific input management recommendations.
+We examined the use of CF for site-specific input management recommendations.
 Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN.
-CF-base consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation.
-We also showed that the model's yield prediction accuracy was uncorrelated with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map.
+CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation.
+Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF.
+It is recommended that BRF is used in place of RF according to out results.
+Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.
+
+We also showed that the model's yield prediction accuracy has little to do with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map.
+Many studies seek to predict yield level accurately using deep learning methods.
+However, the usefulness of such models may be questionable when it comes to using them for making management decisions.
+Further examinations into this issues is warranted.
 

### 2022-02-10 Codes/PrepareResults.rmd
Organize codes

@@
   # scale_fill_viridis_d()+
-  labs(x = expression(paste(hat(pi)["loss"], " ($/ha)"))) +
-  # labs(x = TeX("$\\hat{pi}_{loss}$ (\\$/ha)")) +
+  labs(x = expression(paste(hat(pi)["def"], " ($/ha)"))) +
   facet_wrap(~Model, ncol = 1) +

### 2022-02-10 Codes/0_0_functions.R

@@ -1,1382 +1,0 @@
-# /*=================================================*/
-#' # Make experiment grids (basic cell, plot, strip)
-# /*=================================================*/
-make_trial_grids <- function(field, ab_line, starting_point, plot_width, cell_height) {
-
-  # /*=================================================*/
-  #' # Define functions
-  # /*=================================================*/
-  # /*----------------------------------*/
-  #' ## make polygons
-  # /*----------------------------------*/
-  make_polygon <- function(strt_point_new, multiplier, direction) {
-    point_1 <- strt_point_new + cell_height * ab_xy_nml * (multiplier - 1)
-    point_2 <- point_1 - plot_width * direction * ab_xy_nml_p90
-    point_3 <- point_2 + ab_xy_nml * cell_height
-    point_4 <- point_3 + plot_width * direction * ab_xy_nml_p90
-
-    temp_polygon <- rbind(
-      point_1,
-      point_2,
-      point_3,
-      point_4,
-      point_1
-    ) %>%
-      list() %>%
-      st_polygon()
-
-    return(temp_polygon)
-  }
-
-  # /*----------------------------------*/
-  #' ## rotation matrix
-  # /*----------------------------------*/
-  rotate_mat_p90 <- matrix(
-    c(
-      cos(pi / 2),
-      sin(pi / 2),
-      -sin(pi / 2),
-      cos(pi / 2)
-    ),
-    nrow = 2
-  )
-
-  # /*----------------------------------*/
-  #' ## Make an extended line
-  # /*----------------------------------*/
-  # make line with starting point and a desired shift
-  make_extended_line <- function(starting_point, step, multiplier, step_v) {
-    extended_line <- rbind(
-      starting_point + step * multiplier,
-      starting_point + step_v * 1000 + step * multiplier
-    ) %>%
-      st_linestring() %>%
-      list() %>%
-      st_as_sfc() %>%
-      st_set_crs(st_crs(field))
-
-    return(extended_line)
-  }
-
-  # /*----------------------------------*/
-  #' ## Check intersections
-  # /*----------------------------------*/
-  # check the intersection of the lines in the direction specified
-  check_intersection <- function(field, step, direction, step_v) {
[…]

### 2022-02-12 Codes/PrepareResults.rmd
Incorporate Dr.Bullock's comments and add Mendeley data citation (additional)

@@
 
-  # theme(    
-  #   strip.text.x = element_text(size = 12, face = "bold"),
-  #   legend.title = element_text(size = 12, face = "bold"),
-  #   legend.text = element_text(size = 12, face = "bold"),
-  #   legend.position = "bottom",
-  #   text  = element_text(family = "Times New Roman")
-  # )
-
 set_flextable_defaults(
@@
 ```{r setup, warning=FALSE, message=FALSE, cache= FALSE}
-# field <- readRDS("Shared/Data/for_Simulations/field_padding.rds") %>%
-#     filter(padding==1)%>%
-#     dplyr::select(unique_cell_id)
-
 # === plot-level field data set  === #
@@
   coord_sf(expand = FALSE) +
+  # theme_void() +
   ggtitle("12 \u00D7 12 subplots") +
-  # ggtitle(TeX("$12 \\times 32$ plots")) +
   theme_figure
@@
   coord_sf(expand = FALSE) +
-  theme_void() +
-  # ggtitle(TeX("$4 \\times 1$ subplots")) +
+  # theme_void() +
   ggtitle("4 \u00D7 1 subplots") +
@@
   coord_sf(expand = FALSE) +
-  theme_void() +
-  # ggtitle(TeX("$6 \\times 6$ cells")) +
+  # theme_void() +
   ggtitle("6 \u00D7 6 cells") +
@@
   # --- between plot and subplot --- #
-  geom_brace(aes(c(0.43,0.43+0.1), c(0.353, 0.661)), color ="red", rotate = 270, inherit.data=F) +
+  geom_brace(aes(c(0.43,0.43+0.1), c(0.372-0.004, 0.645+0.013)), color ="red", rotate = 270, inherit.data=F) +
   # --- between subplot and cell --- #
-  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.381, 0.549)), color ="red", rotate = 270, inherit.data=F) +
+  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.401-0.002, 0.529 +0.011)), color ="red", rotate = 270, inherit.data=F) +
   #/*----------------------------------*/
@@
     arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
-  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.015, label = "plot", family="Times New Roman") +
+  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.02, label = "plot", family="Times New Roman") +
   # --- annotation for subplot --- #
@@
   # --- annotation for cell --- #
-  geom_segment(aes(x = 0.89, xend = 0.86, y = 0.349, yend = 0.394),
+  geom_segment(aes(x = 0.9, xend = 0.87, y = 0.365, yend = 0.41),
     arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
-  annotate("text", x = 0.89 + 0.015, y = 0.349 - 0.01, label = "cell", , family="Times New Roman") +
+  annotate("text", x = 0.9 + 0.02, y = 0.365 - 0.005, label = "cell", , family="Times New Roman") +
   theme_void()
@@
 ```
-
-# Preparation for exmaple field maps (one-time run)
-
-```{r}
-# source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")
-
-# pCorn <- price_table[2, pCorn]
-# pN <- price_table[2, pN]
-
-# /*=================================================*/
-#' # Field Data Sets
-# /*=================================================*/
-
-#/*----------------------------------*/
-#' ## (1) cell-level data set 
-#/*----------------------------------*/
-# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
-# field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))
-
-# coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))
-
-# x=1
-# coef_data_m <- coef_data[sim == x, ]
-# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
-
-# sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
-#   .$reg_raw_data
-
-# field_cell_sf <- 
-#   left_join(dplyr::select(field, unique_cell_id), sample_dt_cell, by="unique_cell_id")%>%
-#     na.omit() %>%
-#     mutate(plot_id = ceiling(subplot_id/4)) %>%
-#     filter(padding==1)
-
-# saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))
-
-#/*----------------------------------*/
-#' ## (2) subplot-level field without padding area 
-#/*----------------------------------*/
-
-# field_subplot_sf <- 
-#   field_cell_sf %>%
-#   group_by(subplot_id, strip_id) %>%
-#   summarise(
-#     sim = mean(sim),
-#       yield = mean(yield),
-#       opt_N = mean(opt_N),
-#       rate = mean(rate),
-#       aa_n = mean(aa_n), 
-#       alpha = mean(alpha),
-#       beta = mean(beta),
-#       ymax = mean(ymax),
-#       alpha1 = mean(alpha1),
-#       alpha2 = mean(alpha2),
-#       beta1 = mean(beta1),
-#       beta2 = mean(beta2),
-#       ymax1 = mean(ymax1),
-#       ymax2 = mean(ymax2),
-#       theta_1 = mean(theta_1),
-#       theta_2 = mean(theta_2)
-#   ) %>%
-#   mutate(unique_subplot_id = paste0(strip_id,"_",subplot_id))%>%
-#   dplyr::select(!c(strip_id, subplot_id))
-
-# saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
-
-#/*----------------------------------*/
-#' ## (3) plot-level dataset without padding area  
-#/*----------------------------------*/
-# field_plot_sf <- field_cell_sf%>%
-#     group_by(plot_id, strip_id, rate)%>%
-#     summarise()
-
-# saveRDS(field_plot_sf, here("Shared/Results/for_writing/sample_field_plot_sf.rds"))
-```

### 2022-02-12 Writing/CEA_2nd_round/replies_rev_1.rmd
Incorporate Dr.Bullock's comments and add Mendeley data citation (additional)

@@
     number_sections: no
-    reference_docx: word_template_format.docx
+    reference_docx: ../word_template_format.docx
 ---
 
-Thank you so much for your comments.
-By addressing them, we believe the manuscript is improved significantly.
-You can find our replies to your comments.
-Your comments are in bold, and out replies are in a regular font.
+Thank you so much for your comments. By addressing them, we believe the manuscript is improved significantly. Below you will find your comments in bold and our replies in a regular font.
 
@@
 <span style="color:blue">  
-Yes, we agree with your point, and we have decided to simply drop it from our highlights.
+We agree with your point, and we have dropped the discussion of the advantages of the CF model from our highlights.
 </span>
@@
 
-We do see a redundancy of expalining how CF can be used to identify site-specific input recommendations.
-It was explained twice in 2.2 and 3.2.2, while 2.2 is intended for a more general case than 3.2.2 that is specific to our simulations.
-Therefore, we decided to take out 2.2.
-We also renamed 2.1 to "Estimating EOIR and Treatment Effects."
+We do see a redundancy in our explanation of how CF can be used to identify site-specific input recommendations.
+It was explained twice, once each in subsections 2.2 and 3.2.2.
+We have deletedthe explanation in 2.2 and also changed the heading in 2.1 to "Estimating EOIR and Treatment Effects."
 
-We have moved an example of causal tree (previously in seciton 2.3), but decide to keep the explanation of how CF works.
+We have moved an example of a causal tree (previously in seciton 2.3), but have kept the explanation of how CF works.
 The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations.
-To this core objective, ML simulation is our core method.
-For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give too much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal.
-However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well.
-Now, if we place such description inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works.
-Insted, we believe that it is better to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted.
-Therefore, we kept 2.3 and 2.4 (in the previous round) in the current manuscript.
+
+ML simulation is the core method we use to pursue this core objective.
+For this reason the Materials and Methods section features no explanation of how CF works.
+We also provide little explanation of RF, BRF, and CNN methods, which are well-established and familiar to many readers of this journal.
+However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present in detail how it works and the conditions necessary for it to work well.
+We believe that if we placed such a description of how CF works inside the Materials and Method section, it will unnecessarily distract the reader by breaking the flow of the explanation of the MC simulation procedures.
+We feel that the narrative will flow better if it first informs readers about the potential advantages of CF over existing prediction-oriented ML methods before moving into a description of the MC simulations in the Materials and Method section.
+Therefore, we have kept in the current manuscript the discussion located in subsection 2.3 and 2.4 of the original manuscript.
 </span>
@@
 
-First, we consolidated 3.1.2 and 3.1.3 in the previous round into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we dropped detailed explanation of the conceptual framework behind the yield response functions based on cell-leve characteristics, $c_i$, and moved it to the supplemnentary appendix (Appendix B).
-We also removed our detailed description of how parameters and error term were generated and moved it to Appendix C along with relevant tables and figures (spefically table x and figures x, y, z) <span style = "color: blue;"> Shun put table and figure numbers here </span>.
+First, in the new manuscript we consolidated the original manuscript's 3.1.2 and 3.1.3 into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we moved to the supplementary appendix (Appendix B) the detailed explanation of the conceptual framework behind the yield response functions based on cell-level characteristics, $c_i$.
+In addition, we moved to Appendix C our detailed discussion of parameters and error term generation, which included a number of tables and figures.
+<span style = "color: blue;"> Shun put table and figure numbers here </span>.
 
-Second, we consolidated 3.1.4 and 3.1.5 in the previous round into a single subsubsection called "Trial Design and Yield Data Generation for Modeling." In doing so, we cut some texts and combined figure x and y in the previous round into a single figure (figure x in the current manuscript).
+Second, we consolidated subsection 3.1.4 and 3.1.5 of the original manuscript into a single subsubsection called "Trial Design and Yield Data Generation for Modeling." In doing so, we removed some text and combined the original manuscript's figures x and y in the single figure z in the current manuscript.
 
-Third, we removed detailed description of how some parameters are splitted into two parts and moved it to the Appendix.
+Third, we moved to an appendix the previous manuscript’s detailed description of parameter splitting.
 
-In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated.
-It is much like any emprical studies using real experiment data provides lots of details about the experiemnts.
-We take reproducibility seriously and we believe that the details we peovided in our current manuscript is appropriate and it is hard for us to further slim down the section.
-Moreover, we believe we no longer have any redundancy in this section.
+We believe that the detailed presentation of data generation is crucial in our reporting of MC procedures, as it would be in the report of any empirical study using real experiment data provides.
+In both cases, results are highly dependent procedures.
+We believe further slimming of the description would hinder anyone attempting to reproduce our results.
+That said, we have worked hard to remove redundancies in this section of the manuscript.
 </span>
@@
 <span style="color:blue">  
-It is degree. The unit is now provided in the description of the figure in Appendix A. Please not that this example is just for illustrating how CF works.
+It is degree. The unit is now provided in the description of the figure in Appendix A. Please note that the purpose of the example is simply to illustrate how CF works.
 </span>
@@
 <span style="color:blue">  
-Explanations for those numbers are added as a footnote to the figure. The figure is now in the appendix and called Figure A.1. 
+Explanations for those numbers are added as a footnote to the figure. The figure is now in an appendix and called Figure A.1. 
 </span>
@@
 <span style="color:blue">  
-All the formulas are now numbered. <span style = "color: blue;"> Shun, make sure this happens right before you submit. </span>
+All the formulas are now numbered.
 </span>
@@
 <span style="color:blue">  
-We aplogogize that we are not clear on this respect.
+We apologize for not making this cleaner in the original manuscript.
+The training data set and test data set were completely separate in our analysis.
+For a given simulation round, the training data set from another round acted as a "test" dataset.
+These data sets were created independently and with different underlying field parameters $\alpha$, $\beta$, and $ymax$.
+Training data sets, however, were split into several parts for cross-validation in determining a round's optimal values of its hyperparameters.
+In addition, we added the following paragraph section 3.3.3 to make this point clear.
 
-Trainign dataset and test dataset are completely separate.
-For a given simulation round, the training dataset in another round of simulation acts as a "test" dataset.
-These datasets are created independently from one another and are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$.
-Therefor, in MC simulations, the dataset in a given simulation serves as a train dataset, and served as a test data for another simulation round.
-The train dataset, however, was split into several parts when cross-validation was performed in determing the optimal hyperparameters within a given simulation round.
-
-We added the following paragraph to section <span style = "color: blue;"> Shun section number here </span> to make this point clear.
-
-"For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset.
-For example, for simulation number 1, train dataset from simulation number 2 was used as the test dataset.
-This process works because the train datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$).
-Furtehr, each of the "train" datasets are generated independet of one another.
-Thefore, for a particular simulation round, the dataset in any of the other simualtion rounds can serve as a valid test dataset.
-This practice avoid creating another set of 1000 simulations fields unnecessarily."
+"For evaluation of yield and EONR predictions, a data set from a different simulation round was used as the test data set.
+For example, for simulation number 1, the training data set from simulation number 2 was used as the test data set.
+This process works because the training data sets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$).
+Further, all training data sets were generated independently, so for any particular simulation round, the data set from any other round could serve as a valid test data set.
+This practice made the creation of one thousand additional simulations fields unnecessary."
 </span>
@@
 <span style="color:blue">  
-The simulation codes and the data were also shared on Mendeley Data (<span style = "color: blue;"> Shun, provide the link here </span>) according to the Editor's suggestion for the ease of access.
-The link is also provided <span style = "color: blue;"> Shun, be speficic about where it is </span>.
-
-<span style = "color: blue;"> Shun, make sure you cite the code and data. </span>
-
-We realized that the github repository was private and that was why you were not able to access it. We made a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).
+We have followed the Editor's suggestion by sharing the simulation codes and the data on Mendeley Data (https://data.mendeley.com/datasets/y7cdhzww6w/draft?a=2e33b309-ca5c-49bc-95ce-9b3920d5544a) to increase the accessibility.
+The name of the data set is "Codes and Data Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation", and two folders are included in this data set: "Codes" and  "Data".
+The "Code" folder contains all the simulation codes, and the "Data" folder contains a boundary polygon data of a field which is necessary to create field data for this study.
+Please read README.md for the steps to reproduce.
+In addition, we created a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA))
 </span>
@@
 <span style="color:blue">  
-All the lenth units were converted to meter (m)
+Done
 </span>
@@
 <span style="color:blue">  
-The number of rows and columns of plots, subplots, and cells schematics are now indicated Figure 2.
+Done. Please see Figure 2. 
 </span>
@@
 <span style="color:blue">  
-We realized that section 3.1 also had a uninformative title.
-Therefore, we changed it to "Training Models and Estimating Site-specific EONRs".
-Further, the title of sections 3.2.1 and 3.2.2 were changed to "Estimation of site-specific EONRs by RF, BRF, and CNN" and "Estimation of site-specific EONRs by CF", respectively.
+We changed the title of 3.2 to "Training Models and Estimating Site-specific EONRs", and the title of 3.2.1 and 3.2.2 to "Training and Estimation of Site-specific EONRs by RF, BRF, and CNN" and "Training and Estimation of Site-specific EONRs by CF".
 </span>
@@
 <span style="color:blue">  
-The title of 4.1 was changed to "Comparison of EONR estimation accuracy" to reflect its contents.
-The title of section 4.2 was changed to "The relationship between yield and EONR prediction performances".
-They acurrately reflect what they describe.
+To better reflect the contents of 4.1, we changed its title to "Comparison of EONR Estimation Accuracy." We changed the title of 4.2 to "The Relationship between Yield and EONR Prediction Performances." Both new headings provide more accurate descriptions of their subsection's contents.
 </span>
@@
 
-As explained in section 4.1, CNN failed to predict site-specific EONR because the estimated yield response function were always linear (please see the Table 1).
-Therefore, we thought that visualizing the CNN results are not insightful.
-However, we have decided to include CNN results to Figures 8, 9, and 10 in the previous version.
-The figures are now Figures 3, 4, and 5.
+As explained in section 4.1, CNN failed to predict site-specific EONR because the estimated yield response function were always linear (Table 1).
+Therefore, we thought that visualizing the CNN results would not provide much insight.
+However, we have decided to include CNN results in Figures 8, 9, and 10 of the previous manuscript.
+which are Figures 3, 4, and 5 of the revised manuiscript.
 
@@
 <span style="color:blue">  
-We added a new section called "Limitations and Future Studies" before the Conclustion section.
-One of the important assumptions that needs to be satisfied for CF to provides consistent estimation of treatment effects is that the treatment (N rates here) is uncorrelated with unobservable characteristics.
-Other assumtions are relatively minor.
+We have added a section called “Limitations and Future Studies” before the Conclusion section of the revised manuscript.
+One of the important conditions for CF to provide consistent estimation of treatment effects is that the treatment (N rates here) is uncorrelated with unobservable characteristics.
+Other assumptions are relatively minor.
 Note that, this is not just for CF, but also for RF, BRF, and CNN.
-Whenever the variable of interest (N rates here), their estiamtion of its impact on the dependent variable is biased in general.
-Fortunatley, in OFPE settings, we can randomize or patternize the input rates in a way that the input rates are uncorrelated to the unobserved variables.
-Therefore, the violation of this assumption is not as much of a concener as in a setting where observational data is used.
-We discuss these in the "Trial Design and Yield Data Generation for Modeling" section.
+Whenever the variable of interest (N rates here), their estimation of its impact on the dependent variable is biased in general.
+Fortunately, in OFPE settings we can randomize or geographically pattern input rates to make them uncorrelated with unobserved variables.
+Therefore, the violation of this assumption is not as much of a concern as in a setting where observational data is used.
+We discuss these in the “Trial Design and Yield Data Generation for Modeling” section.
 </span>
@@
 <span style="color:blue">  
-We moved the descriptions of the limitations (uncertainty) of the study to a separate section as mentioned earlier in our reply to your comment 14.
+As mentioned earlier in our reply to your comment 14, in the revised manuscript we have moved the descriptions of the limitations (uncertainty) of the study to a separate section. 
 </span>

### 2022-02-12 Writing/appendix.rmd
math equation fixes
Update figures and tables
1. position of R2 labels are changed and the figure height increased to 7.5 2. minor changes in manuscript
Incorporate Dr.Bullock's comments and add Mendeley data citation (additional)

@@
 
-NOTE: The first number in each node indicates the predicted treatment effects (in kg/ha). The number and the percentage of observations belonging to the node are shown below that.
+`r ftext('NOTE: The first number in each node indicates the predicted treatment effects (in kg/ha).
+The number and the percentage of observations belonging to the node are shown below that.', fp_text(font.size = 9, font.family = "Times New Roman"))`
 
@@
 The estimated heterogeneous treatments effects can then be used to identify site-specific EOIRs.
-It is noteworth that at no point CF estimates yield "level".
+It is noteworth that at no point CF estimates yield "level."
 
@@
 \begin{alinged}
-f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) N)) + \varepsilon. 
+f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) \cdot N)) + \varepsilon. 
 \end{alinged}
@@
 \begin{equation}
-f(N_{i}, \mathbf{c}_{i}) = ymax(\mathbf{c}_{i})(1-exp(\alpha(\mathbf{c}_{i}) + \beta(\mathbf{c}_{i}) N_{i})) + \varepsilon_{i}. 
+f(N_{i}, \mathbf{c}_{i}) = ymax(\mathbf{c}_{i})(1-exp(\alpha(\mathbf{c}_{i}) + \beta(\mathbf{c}_{i})\cdot N_{i})) + \varepsilon_{i}. 
 \end{equation}
@@
 Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
-(Codes used to generate parameter values are available at https://github.com/tmieno2/ML_VRA.git.) The range and nugget of all parameters were assumed to be $400$ m and 0.
+(Codes used to generate parameter values are available at @Kakimoto2022codes.) The range and nugget of all parameters were assumed to be $400$ m and 0.
 The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$.
@@
 
-field_alpha + field_beta + field_ymax + field_m_error + vis_optN_cell + plot_layout(ncol = 2)
+field_alpha + field_beta + field_ymax + field_m_error + field_optN + plot_layout(ncol = 2)
 ```
@@
 
-For scenarios "aabbyy" and "aabbyytt", each of the base parameters $\alpha$, $\beta$, and $ymax$ are splitted into two part in a spatially correlated manner.
-Speficiallu, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r^{\alpha}_{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r^{\beta}_{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r^{ymax}_{i,j} \in (0,1)$ to the ${ymax}_{i,j}$ variable.
+For scenarios "aabbyy" and "aabbyytt," each of the base parameters $\alpha$, $\beta$, and $ymax$ are splitted into two part in a spatially correlated manner.
+Specifically, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r^{\alpha}_{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r^{\beta}_{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r^{ymax}_{i,j} \in (0,1)$ to the ${ymax}_{i,j}$ variable.
 Each of the weight variables are generated using unconditional Gaussian geostatistical simulation just like the base parameters.
@@
 These were
-$\alpha_{1}_{i,j} = r^{\alpha}_{i,j} \alpha_{i,j}$, $\alpha_{2}_{i,j} = (1- r^{\alpha}_{i,j}) \alpha_{i,j}$,
-$\beta_{1}_{i,j} = r^{\beta}_{i,j} \beta_{i,j}$, $\beta_{2}_{i,j} = (1- r^{\beta}_{i,j}) \beta_{i,j}$,
-$ymax_{1}_{i,j} = r^{ymax}_{i,j} ymax_{i,j}$, and $ymax_{2}_{i,j} = (1- r^{ymax}_{i,j}) ymax_{i,j}$.
-The codes used to implement the abovementioned parameter splitting is available at https://github.com/tmieno2/ML_VRA.git.
-
-<span style = "color: blue;"> Shun, provide the link to Mandeley data and cite it </span>
+$\alpha^{1}_{i,j} = r^{\alpha}_{i,j} \cdot \alpha_{i,j}$, $\alpha^{2}_{i,j} = (1- r^{\alpha}_{i,j}) \cdot \alpha_{i,j}$,
+$\beta^{1}_{i,j} = r^{\beta}_{i,j} \cdot\beta_{i,j}$, $\beta^{2}_{i,j} = (1- r^{\beta}_{i,j}) \cdot\beta_{i,j}$,
+$ymax^{1}_{i,j} = r^{ymax}_{i,j} \cdot ymax_{i,j}$, and $ymax^{2}_{i,j} = (1- r^{ymax}_{i,j}) \cdot ymax_{i,j}$.
+The codes used to implement the abovementioned parameter splitting is available at @Kakimoto2022codes.

### 2022-02-12 Codes/1_1_generate_field.R

@@ -15,8 +15,8 @@ library(parallel)
 library(mapedit)
 
 
-#--- source functions ---#
-source(here("Gitcontrolled", "Codes", "0_1_functions_gen_analysis_data.R"))
+# === Load Functions === #
+source(here("Codes", "0_1_functions_gen_analysis_data.R"))
 
 # ==========================================================================
 #  1. Field Data
@@ -34,7 +34,7 @@ field_boundary <- ffy %>%
   st_bbox() %>%
   st_as_sfc() %>%
   st_as_sf()
-  
+
 
 # /*=================================================*/
 #' # 1. Base Field 
@@ -184,7 +184,7 @@ field_grid_within_subplot <-
   mapedit:::combine_list_of_sf()
 
 # --- Merge with field_expd --- #
-field_padding <- 
+analysis_field <- 
   left_join(
     field_grid_within_subplot, st_drop_geometry(field_expd), by="unique_cell_id")%>%
     cbind(., st_coordinates(st_centroid(.)))%>%
@@ -195,7 +195,7 @@ field_padding <-
 
 # ggplot()+
 #   geom_sf(data=field_base, fill="green", size=0, alpha=0.6) +
-#   geom_sf(data=field_padding, fill=NA)
+#   geom_sf(data=analysis_field, fill=NA)
 
 # /*========================================*/
 #' 4. Create "padding" indicator
@@ -204,14 +204,14 @@ field_padding <-
 base_bdary <- st_union(field_base)
 
 padding_idx <- 
-  field_padding %>%
+  analysis_field %>%
   st_centroid() %>%
   dplyr::select(unique_cell_id) %>%
   mutate(padding = ifelse(st_within(., base_bdary, sparse=FALSE), 1, 0))%>%
   st_drop_geometry()%>%
   data.table()
 
-res_field_padding <- left_join(field_padding, padding_idx, by="unique_cell_id")
+analysis_field <- left_join(analysis_field, padding_idx, by="unique_cell_id")
 
 
-saveRDS(res_field_padding, here("Shared/Data/for_Simulations/field_padding.rds"))
+saveRDS(analysis_field, here("Data/for_Simulations/analysis_field.rds"))

### 2022-02-12 Codes/2_2_main_sim.R

@@ -1,73 +1,0 @@
-# /*===== Run on R GUI =====*/
-
-#/*----------------------------------*/
-#' ## Preparation
-#/*----------------------------------*/
-library(here)
-library(grf)
-library(data.table)
-library(tidyverse)
-library(future.apply)
-
-# === Source Functions === #
-setwd("~/Dropbox/ResearchProject/CF_for_VRA")
-source("./GitControlled/Codes/0_2_functions_main_sim.R")
-
-# /*----------------------------------*/
-#' ## Datasets
-# /*----------------------------------*/
-# === prices ===#
-pCorn <- price_table[2, pCorn]
-pN <- price_table[2, pN]
-
-reg_data_all <- readRDS("./Shared/Data/for_Simulations/reg_data.rds")
-test_data_all <- readRDS("./Shared/Data/for_Simulations/test_data.rds")
-
-# x=1
-# train_dt <- reg_data_all[sim==x&padding==1,]
-# test_dt <- test_data_all[sim==x&padding==1,]
-# N_levels <- reg_data_all[sim==x,]$rate%>%unique()%>%sort()
-
-# /*=================================================*/
-#' # Simulation by scenarios
-# /*=================================================*/
-# + run a 1000 simulations by individual scenarios
-# + the 1000 simulation results will be saved per each scenario
-
-# === set up for parallel computations === #
-plan(multicore, workers = availableCores()-2)
-options(future.globals.maxSize= 850*1024^2)
-
-# --- modeling scenario --- #
-var_ls_variations <- list(
-    c("alpha", "beta", "ymax"),
-    c("alpha", "beta", "ymax", "theta_1", "theta_2"),
-    c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2"),
-    c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")
-  )
-
-# --- Number of iterations --- #
-B=1000
-
-# === start simulation === #
-for (var in var_ls_variations){
-		# var = c("alpha", "beta", "ymax")
-		set.seed(1378)
-		# --- for each modeling scenario run: --- #
-		sim_results <- lapply(1:B, 
-			function(x){
-				sim_par(
-					i = x,
-					var_ls = var,
-					reg_data = reg_data_all[sim==x&padding==1,],
[…]

### 2022-02-12 Codes/3_2_CompTeEstimation.R

@@ -98,7 +98,7 @@ forest_te_dt <-
 
 # === load CNN results (case: aabbyytt) === #
 res_cnn <- 
-	fread(here("Shared/Results/CNN_rawRes_onEval/0_alldata_model4.csv"))%>%
+	fread(here("Shared/Results/CNN_rawRes_onEval/alldata_model4.csv"))%>%
 	setnames("pred", "yield_hat")%>%
 	.[sim==1, rate %in% N_levels, .(id, rate, yield_hat, sim)] %>%
 	.[, c("subplot_id", "strip_id") := tstrsplit(id, "_", fixed=TRUE)] %>%

### 2022-02-12 Writing/CEA_2nd_round/replies_rev_2.rmd

@@
     global_numbering: true
-    reference_docx: word_template_format.docx
+    reference_docx: ../word_template_format.docx
 ---

### 2022-02-12 Writing/manuscript_cea.rmd

@@
   message = F,
-  cache = TRUE,
+  cache = T,
   echo = F
@@
 In this paper, we use the Causal Forest (CF) approach developed by @athey2016recursive and @Wager2018a to examine the accuracy of methods that estimate site-specific economically optimal N fertilizer rates (EONRs).
-We compare the EONR prediction performances of our CF-based approach to the widely used ML methods Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN), and we examine how yield prediction performance is related to EONR prediction performance, which allow us to examine whether model selection should be based on yield prediction accuracy when the ultimate goal is EOIR identifying.
+We compare the EONR prediction performances of our CF-based approach to the widely used ML methods Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN), and we examine how yield prediction performance is related to EONR prediction performance, which allow us to examine whether model selection should be based on yield prediction accuracy when the ultimate goal is EOIR identification.
 We use Monte Carlo simulations in which we synthetically generate yield and soil/field characteristics datasets to create stylized "field." Because real-world "true" EOIRs are unobservable, real-world data cannot be used to test the accuracy of statistical methods estimating EOIRs.
@@
 While knowledge of the yield function $f(I, \mathbf{c})$ in Eq.
-\@ref(eq:eqn1)) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the "change" in yield in response to a change in input rate is.
+\@ref(eq:eqn1) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the "change" in yield in response to a change in input rate is.
 
-Recent papers using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21) and then derive changes in yield associated with changes in input rate to estimate site-specific input recommendations.
+Recent studies using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21) and then derive changes in yield associated with changes in input rate to estimate site-specific input recommendations.
 On the other hand, Causal Forest is designed specifically to estimate a discrete version of Eq.
@@
 Detailed descriptions of these steps are provided below.
-The *R* and *python* codes that implement the simulation analyses are available at https://github.com/tmieno2/ML_VRA.git.
+The *R* and *python* codes that implement the simulation analyses are available at @Kakimoto2022codes.
 
@@
 For example, $\alpha$, which represents what the yield would be when no nitrogen is applied in conjunction with $ymax$, may reflect soil organic matter and residual nitrogen from previous year's production.
-$ymax$, which determines the maximum yield attainable, may include other micro nutrients like phosphorus, soil depth among others.
+$ymax$, which determines the maximum yield attainable, may include other micro nutrients like phosphorus and soil depth.
 $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen].
@@
 The N rate was orthogonal to the error term in every simulation's example of trial design.
-This is important because if they were correlated, bias in the estimation of the impact of N on yield would be introduced into all of the ML methods.
+This is important because if they were correlated, bias in the estimation of the impact of N on yield would be introduced into all the ML methods.
 Since the treatment effect at each leaf is obtained simply by taking the difference of the average value of the dependent variable between the control and treated group within the leaf, CF requires the exogeneity of the treatment conditional on the independent variables to estimate the treatment effect consistently.
@@
 ```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "An example of experimental design of N and generated yield at the subplot resolution"}
-
-# (field_Ndesign + ggtitle("(a) Trial Design")) |
-#   (vis_yield_subplot + ggtitle("(b) Simulated Yield Level"))
 field_Ndesign | vis_yield_subplot
@@
 Rather, it contained subplot-level values of permutations of $\alpha$, $\beta$, and $ymax$.
-Each of the three parameters were split into two parts in a spatially correlated manner, and six new covariates were created (see Appendix \@ref(split-pars) for the details about this prameter splitting process).
+Each of the three parameters were split into two parts in a spatially correlated manner, and six new covariates were created (see Appendix \@ref(split-pars) for the details about this parameter-splitting process).
 These were $\alpha^{1}_{i}$, $\alpha^{2}_{i}$, $\beta^{1}_{i}$, $\beta^{2}_{i}$, $ymax^{1}_{i}$, and $ymax^{2}_{i}$.
-The two splitted variables were spatially correlated to reflect that many of the soil/field characteristics used to analyze OFPE data are spatially correlated.
+The two split variables were spatially correlated to reflect that many of the soil/field characteristics used to analyze OFPE data are spatially correlated.
 The values of $\alpha_{i}$, $\beta_{i}$ and $ymax_{i}$ did not indicate specific soil or field characteristics, but were functions of such.
@@
 The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for RF and BRF modeling.
-RF ann BRF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving honest tree-building process), and the optimal values for these parameters were selected by cross-validation.
+RF ann BRF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving an honest tree-building process), and the optimal values for these parameters were selected by cross-validation.
 Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same data set was used.
@@
 
-Since the CF-base approach always estimates the treatment effects using the lowest treatment rate $N_1$, the predicted treatment effects already represent differences in yields the from yield at $N_1$:
+Since the CF-base approach always estimates the treatment effects using the lowest treatment rate $N_1$, the predicted treatment effects already represent differences in yields from yield at $N_1$:
 
@@
 
-For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset.
-For example, for simulation number 1, train dataset from simulation number 2 was used as the test dataset.
-This process works because the train datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$).
-Furtehr, each of the "train" datasets are generated independet of one another.
-Thefore, for a particular simulation round, the dataset in any of the other simualtion rounds can serve as a valid test dataset.
-This practice avoid creating another set of 1000 simulations fields unnecessarily.
+For evaluation of yield and EONR predictions, a data set from a different simulation round was used as the test data set.
+For example, for simulation number 1, the training data set from simulation number 2 was used as the test data set.
+This process works because the training data sets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$).
+Further, all training data sets were generated independently, so for any particular simulation round, the data set from any other round could serve as a valid test data set.
+This practice made the creation of one thousand additional simulations fields unnecessary.
 
 The accuracy of EONR estimation was judged based on RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level.
-Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) we calculated relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N^{opt}_{i}$.
+Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N^{opt}_{i}$.
 For RF, BRF, and CNN, the accuracy of yield prediction was judged based on the RMSE ($kg/ha$) of the yield prediction against the true yields at the subplot level.
@@
 
-## Comparison of EONR estimation accuracy
+## Comparison of EONR Estimation Accuracy
 
@@
 
-Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML methods and modeling scenarios, respectively (CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always take $62.8$ kg/ha and \$$58.99$/ha, respectively).
-The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios.
+Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML methods and modeling scenarios, respectively (CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always took values $62.8$ kg/ha and \$$58.99$/ha, respectively.) The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios.
 Interestingly, RF seems particularly vulnerable to the inclusion of more variables, with RMSE ($\hat{\pi}_{def}$) increasing from `r table_optN_prep[Model=="aby",rmse_optN_RF]` (`r table_optN_prep[Model=="aby", pi_loss_RF]`) in the "aby" scenario to `r table_optN_prep[Model=="aabbyytt", rmse_optN_RF]` (`r table_optN_prep[Model=="aabbyytt", pi_loss_RF]`) in the "aabbyytt" scenario.
@@
 Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions.
-It plots the estimated treatment effects against true treatment effects by treatment types and ML methods (RF, BRF, and CF-base) under the "aabbyytt" scenario in one of the one thousand simulations rounds.
+It plots the estimated treatment effects against true treatment effects by treatment types and ML methods under the "aabbyytt" scenario in one of the one thousand simulations rounds.
 The figure shows points clustered around the red 1-to-1 line, meaning that the estimated treatment effects did not exhibit significant bias.
@@
 
-## The relationship between yield and EONR prediction performances.
+## The Relationship between Yield and EONR Prediction Performances.
 
@@
 
-```{r plot-y-optN, fig.width=7, fig.height=7.5, fig.cap = "The relationship in the performance between EONR estimation and yield prediction by ML method and modeling scenario"}
+```{r plot-y-optN, fig.width=7, fig.height=7.5, fig.cap = "The relationship in the performance between EONR estimation and yield prediction, by ML method and modeling scenario"}
 fig_y_optN
@@
 That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF models best at yield prediction did not provide EONR estimates that led to high profits.
-Similarly, in no cased did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously.
+Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously.
 For example, Table \@ref(tab:count-table) shows that BRF predicted yield best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best.
-But, BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.
+But BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.
 
@@
 
-```{r count-table, tab.cap = "Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances for prediction-oriented ML methods"}
+```{r count-table, tab.cap = "Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances of prediction-oriented ML methods"}
 report_summary_res_CNN_RF_BRF
@@
 ML methods are appealing tools that can potentially improve site-specific input rate management by capturing heterogeneous treatment effects introduced by complex non-linear and multidimensional interactions of soil and field characteristics.
-Many kinds of prediction-oriented ML methods have been used for this purpose.
+Several kinds of prediction-oriented ML methods have been used for this purpose.
 We have introduced the use of CF, a relatively new method, which, unlike prediction-oriented ML methods, focuses on the identification of heterogeneous causal effects of treatment.
 
-We examined the use of CF for site-specific input management recommendations.
+We examined the use of CF in the generation of site-specific input management recommendations.
 Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN.
@@
 Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF.
-It is recommended that BRF is used in place of RF according to out results.
 Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.
 
-We also showed that the model's yield prediction accuracy has little to do with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map.
+We also showed that the model's yield prediction accuracy has little to do with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map.
 Many studies seek to predict yield level accurately using deep learning methods.
-However, the usefulness of such models may be questionable when it comes to using them for making management decisions.
-Further examinations into this issues is warranted.
+Our results question usefulness of such models in the making of management decisions.
+Further examinations into these issues are warranted.
 
-# Acknowledgement
+# Acknowledgements
 

### 2022-02-13 Writing/CEA_2nd_round/replies_rev_1.rmd
minor changes

@@
 We believe that the detailed presentation of data generation is crucial in our reporting of MC procedures, as it would be in the report of any empirical study using real experiment data provides.
-In both cases, results are highly dependent procedures.
+In both cases, results are dependent procedures.
 We believe further slimming of the description would hinder anyone attempting to reproduce our results.
@@
 Please read README.md for the steps to reproduce.
-In addition, we created a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA))
+In addition, we also created a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).
 </span>
@@
 Note that, this is not just for CF, but also for RF, BRF, and CNN.
-Whenever the variable of interest (N rates here), their estimation of its impact on the dependent variable is biased in general.
+Whenever the variable of interest (N rates here) is correlated with the unobservables (error term), their estimation of its impact on the dependent variable is biased in general.
 Fortunately, in OFPE settings we can randomize or geographically pattern input rates to make them uncorrelated with unobserved variables.

### 2022-02-13 Writing/appendix.rmd
minor changes

@@
 Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
-(Codes used to generate parameter values are available at @Kakimoto2022codes.) The range and nugget of all parameters were assumed to be $400$ m and 0.
-The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$.
+(Codes used to generate parameter values are publicly accessible as a Mendeley dataset [@Kakimoto2022codes].) The range and nugget of all parameters were assumed to be $400$ m and 0.
+The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12,000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$.
 See Figure \@ref(fig:fig-parameters) for an example of the generated parameters.
@@
 $ymax^{1}_{i,j} = r^{ymax}_{i,j} \cdot ymax_{i,j}$, and $ymax^{2}_{i,j} = (1- r^{ymax}_{i,j}) \cdot ymax_{i,j}$.
-The codes used to implement the abovementioned parameter splitting is available at @Kakimoto2022codes.
+The codes used to implement the abovementioned parameter splitting are publicly accessible as a Mendeley dataset [@Kakimoto2022codes].

### 2022-02-13 Codes/PrepareResults.R

@@ -1,4 +1,4 @@
-## ----set-up, cache = F------------------------------------------------------------------------
+## ----set-up, cache = F-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 library(knitr)
 library(here)
 
@@ -9,7 +9,7 @@ knitr::opts_chunk$set(
   cache = FALSE
 )
 
-## ----packages, cache = FALSE, include = FALSE-------------------------------------------------
+## ----packages, cache = FALSE, include = FALSE--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -37,7 +37,7 @@ library(modelsummary)
 library(latex2exp)
 
 
-## ---------------------------------------------------------------------------------------------
+## ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 theme_figure <- 
   theme(
     plot.title = element_text(hjust = 0.5),
@@ -65,7 +65,7 @@ set_flextable_defaults(
   )
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE----------------------------------------
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 # === plot-level field data set  === #
 field_plot_sf <-
   here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
@@ -82,7 +82,7 @@ field_cell_sf <-
   readRDS()
 
 
-## ---------------------------------------------------------------------------------------------
+## ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 
 
 
@@ -123,7 +123,7 @@ variogram_tb <-
   autofit()
 
 
-## ----field-map-visualization, dependson = "setup"---------------------------------------------
+## ----field-map-visualization, dependson = "setup"----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 
 # === Preparation === #
 ex_plot <- field_plot_sf[224, ]
@@ -217,7 +217,7 @@ field_structure <-
   theme_void()
 
 
-## ---- dependson = "setup"---------------------------------------------------------------------
+## ---- dependson = "setup"----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 field_Ndesign <-
[…]

### 2022-02-14 Codes/PrepareResults.rmd
New results and added training accuracy of the ML methods to supplementary

@@
 library(modelsummary)
-library(latex2exp)
 ```
@@
     strip.text.x = element_text(size = 12, face = "bold"),
+    strip.text.y = element_text(size = 12, face = "bold"),
     legend.title = element_text(size = 12, face = "bold"),
@@
 ```{r}
-
 variogram_tb <-
@@
 ## Division of field: plots, subplots and cells (Visualization)
-+ https://stackoverflow.com/questions/35633239/add-curly-braces-to-ggplot2-and-then-use-ggsave
-
-+
 
@@
 # === m_error map === #
-# + this should be m_error*det_yield, not just m_error
-# m_error_sf <-  left_join(field, coef_data_m, by="unique_cell_id")
-
 field_m_error <-
@@
 
-## Source Results and Preparation
+## Source Results
 
 ```{r source-results, message=FALSE, warning=FALSE, cache= FALSE}
-
-# ===================================
-# Forest results
-# ===================================
-
-res_forest_all_honest <-
-  here("Shared/Results/Summary_SimRes_Honest_full_tune.rds") %>%
-  readRDS()
-
-# ===================================
-# CNN results
-# ===================================
-
-res_CNN_all <-
-  here("Shared/Results/SimRes_CNN_RMSE.rds") %>%
-  readRDS()
-
-# /*-------------------------------------------------------*/
-#' ## Organize the data
-# /*-------------------------------------------------------*/
-#--- for reporting the results of  yield prediction and EONR estimation ---#
-res_allML <-
-  rbind(res_forest_all_honest, res_CNN_all) %>%
-  .[Method %in% c("RF", "BRF", "CNN", "CF_base")] %>%
-  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF_base"))] %>%
-  .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]
+# === Load Results === #
+allML_summary_bySim <- readRDS(here("Shared/Results/for_writing/allML_summary_bySim.rds"))
 ```
@@
 ```{r, dependson = "source-results"}
+# === Set up === #
+res_y_train <-
+  allML_summary_bySim %>%
+  .[type == "train" & Method %in% c("RF", "BRF", "CNN")]
 
-rmse_y_all <-
-  copy(res_allML) %>%
-  .[Method %in% c("RF", "BRF", "CNN")]
+res_y_test <-
+  allML_summary_bySim %>%
+  .[type == "test" & Method %in% c("RF", "BRF", "CNN")]
 
 # ==== Summary Table ====#
-table_y_prep <-
-  copy(rmse_y_all) %>%
+# --- on training data sets--- #
+report_table_y_train <-
+  res_y_train %>%
   .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
   .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
-  dcast(Model ~ Method, value.var = "rmse_y")
+  dcast(Model ~ Method, value.var = "rmse_y") %>%
+  .[, CF_base := "-"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  flextable(.) %>%
+  set_header_labels(values = list(
+    Model = "Model",
+    RF = "RF",
+    BRF = "BRF",
+    CNN = "CNN",
+    CF_base = "CF-base"
+  )) %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  #- change the borders just for consistency with other figures -#
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  autofit()
 
+# --- on testing data sets--- #
 report_table_y <-
-  copy(table_y_prep) %>%
+  res_y_test %>%
+  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
+  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
+  dcast(Model ~ Method, value.var = "rmse_y") %>%
   .[, CF_base := "-"] %>%
@@
 fig_y_optN <-
-  rmse_y_all[Method %in% c("RF", "BRF", "CNN")] %>%
+  res_y_test %>%
+  .[Method %in% c("RF", "BRF", "CNN")] %>%
   ggplot(aes(x = rmse_y, y = rmse_optN)) +
@@
   facet_grid(Model ~ Method) +
-  # geom_smooth(method='lm', se=FALSE,  aes(colour="Regression line"), size=1) +
-  # scale_colour_manual(values= "red") +
   geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
@@
 ```{r, dependson = "source-results"}
-
+# === Preparation === #
 prepare_count_tab <-
-  rmse_y_all %>%
-  dcast(sim + Model ~ Method, value.var = c("Mean", "rmse_y")) %>%
+  res_y_test %>%
+  dcast(sim + Model ~ Method, value.var = c("pi_loss", "rmse_y")) %>%
   .[, which_ML_y := case_when(
@@
   .[, which_ML_piLoss := case_when(
-    Mean_BRF < Mean_RF & Mean_BRF < Mean_CNN ~ "BRF",
-    Mean_RF < Mean_BRF & Mean_RF < Mean_CNN ~ "RF",
-    Mean_CNN < Mean_BRF & Mean_CNN < Mean_RF ~ "CNN"
+    pi_loss_BRF < pi_loss_RF & pi_loss_BRF < pi_loss_CNN ~ "BRF",
+    pi_loss_RF < pi_loss_BRF & pi_loss_RF < pi_loss_CNN ~ "RF",
+    pi_loss_CNN < pi_loss_BRF & pi_loss_CNN < pi_loss_RF ~ "CNN"
   )] %>%
@@
 report_summary_res_CNN_RF_BRF <-
-  copy(summary_res_CNN_RF_BRF) %>%
+  summary_res_CNN_RF_BRF %>%
   flextable(.) %>%
@@
 ```{r, dependson = "source-results"}
-
-# === Distribution of RMSE of EONR estimates === #
+#/*----------------------------------*/
+#' ## Distribution of RMSE of EONR estimates
+#/*----------------------------------*/
 plot_dis_optN <-
-  copy(res_allML) %>%
+  allML_summary_bySim %>%
+  .[type=="test",] %>%
   # .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
-  .[, Method := case_when(
-    Method == "CF_base" ~ "CF-base",
-    Method == "RF" ~ "RF",
-    Method == "BRF" ~ "BRF",
-    Method == "CNN" ~ "CNN"
-  )] %>%
+  .[Method == "CF_base", Method := "CF_base"] %>%
   .[, Model := case_when(
@@
   )] %>%
-  # .[, Method:=factor(Method, levels = c("RF", "BRF", "CF-stepwise", "CF-base"))]%>%
-  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF-base"))] %>%
   .[, Model := factor(Model,
@@
   geom_density(aes(x = rmse_optN, fill = Method), alpha = 0.7) +
-  # scale_fill_viridis_d()+
   facet_wrap(~Model, ncol = 1) +
-  # labs(x = expression(R^2))+
   labs(x = "RMSE (kg/ha)") +
@@
 
-# === Summary Table === #
-
-# --- prepation --- #
+#/*----------------------------------*/
+#' ## Summary Table
+#/*----------------------------------*/
+# === Preparation === #
 table_optN_prep <-
-  copy(res_allML) %>%
+  allML_summary_bySim %>%
   .[, .(
-    rmse_optN = mean(rmse_optN),
-    pi_loss = mean(Mean)
-  ), by = .(Method, Model)] %>%
-  .[, `:=`(
-    rmse_optN = format(round(rmse_optN, 1), nsmall = 1),
-    pi_loss = format(round(pi_loss, 2), nsmall = 2)
-  )] %>%
-  dcast(Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
+    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
+    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
+  ), by = .(type, Method, Model)] %>%
+  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
   .[, `:=`(
@@
   )] %>%
-  .[, .(Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]
+  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]
 
-#- table creation -#
+# === Summary Table (Training Data sets) === #
+report_table_optN_train <-
+  table_optN_prep %>%
+  .[type=="train", !"type"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  # add_row(.after = 4) %>%
+  flextable(.) %>%
+  border_remove() %>%
+  delete_part(part = "header") %>%
+  add_header(
+    Model = "Model",
+    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
+    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
+    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
+    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
+    top = TRUE
+  ) %>%
+  merge_h(part = "header") %>%
+  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
+  add_header(
+    Model = "",
+    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
+    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
+    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
+    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
+    top = FALSE
+  ) %>%
+  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  # autofit() %>%
+  # width(j = c(2,5,8,11), width=0.3) %>%
+  # fix_border_issues()
+  footnote(
+    # i = 1, j = c(4, 7, 10, 13), part = "header",
+    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
+    ref_symbols = NA
+  ) %>%
+  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
+  autofit() %>%
+  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
+  width(j = c(2, 5, 8, 11), width = 0.1)
+
+# === Summary Table (Testing Data sets) === #
 report_table_optN <-
-  copy(table_optN_prep) %>%
+  table_optN_prep %>%
+  .[type=="test", !"type"] %>%
   mutate(
@@
 piLoss_density <-
-  copy(res_allML) %>%
-  .[, Method := case_when(
-    Method == "CF_base" ~ "CF-base",
-    Method == "RF" ~ "RF",
-    Method == "BRF" ~ "BRF",
-    Method == "CNN" ~ "CNN"
-  )] %>%
+  allML_summary_bySim %>%
+  .[type == "test", ] %>%
+  .[Method == "CF_base", Method := "CF-base"] %>%
   .[, Model := case_when(
@@
   )] %>%
-  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF-base"))] %>%
   .[, Model := factor(Model,
@@
   ggplot() +
-  geom_density(aes(x = Mean, fill = Method), alpha = 0.7) +
-  # scale_fill_viridis(discrete = TRUE, alpha=0.5) +
-  # scale_fill_viridis_d()+
+  geom_density(aes(x = pi_loss, fill = Method), alpha = 0.7) +
   labs(x = expression(paste(hat(pi)["def"], " ($/ha)"))) +
@@
   theme_dist
-
 ```
@@
 ```{r}
-#### === The original code for this figure is in "1_3_CompTeEstimation.R" ===####
-
 figure_te <-
@@
   readRDS() %>%
-  .[, Method := case_when(
-    Method == "RF" ~ "RF",
-    Method == "BRF" ~ "BRF",
-    Method == "CNN" ~ "CNN",
-    Method == "CF_base" ~ "CF-base"
-  )] %>%
-  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF-base"))] %>%
+  .[Method == "CF_base", Method := "CF-base"] %>%
   ggplot() +
@@
   labs(x = "True Treatment Effect (kg/ha)") +
-  theme_few() +
-  theme(
-    strip.text.x = element_text(size = 12, face = "bold"),
-    strip.text.y = element_text(size = 12, face = "bold"),
-    legend.title = element_blank(),
-    legend.text = element_text(size = 12, face = "bold"),
-    legend.position = "bottom"
-  ) +
-  theme_figure
+  theme_dist
 ```
 
-# Create
+# An Example of a Causal Tree
 
@@
 # /*=================================================*/
-
 library(causalTree)
@@
 opfit <- prune(tree, opcp)
-
 ```

### 2022-02-14 Writing/appendix.rmd
New results and added training accuracy of the ML methods to supplementary

@@
 
-```{r ct-ex, fig.width=5, fig.height=5, fig.align="center", fig.cap = "An illustrative example of causal tree"}
+```{r ct-ex, fig.width=5, fig.height=5, fig.align="center", fig.cap = "An illustrative example of a causal tree"}
 fancyRpartPlot(opfit, sub = "")
@@
 
-# Appendix B: Understanding yield response functions better
+# Appendix B: Understanding Yield Response Functions Better
 
@@
 
-\begin{alinged}
+\begin{equation}
 f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) \cdot N)) + \varepsilon. 
-\end{alinged}
+\end{equation}
 
@@
 
-# Appendix C: Parameter generation
+# Appendix C: Parameter Generation
 
@@
 
-```{r variogram-parameters, tab.cap = "The Parameters for the Variogram Models"}
+```{r variogram-parameters, tab.cap = "The parameters for the Variogram models"}
 variogram_tb
@@
 
-```{r fig-parameters, fig.width=7, fig.height=9, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics", cache = TRUE}
+```{r fig-parameters, fig.width=7, fig.height=9, fig.cap = "An Illustrative wxample of spatial distributions of field characteristics", cache = TRUE}
 
@@
 
-## Splitting the base parameters {#split-pars}
+## Splitting the Base Parameters {#split-pars}
 
@@
 The codes used to implement the abovementioned parameter splitting are publicly accessible as a Mendeley dataset [@Kakimoto2022codes].
+
+# Appendix C: Training Accuracy of the ML methods
+
+During the simulations, we evaluated the training accuracy using the same ML models we presented in the Result and Discussion section. 
+Table \@ref(tab:table-optN-train) shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the one thousand simulations using the training datasets as testing datasets.
+Overall, the performances of each ML method did not change between training and testing datasets.
+Regarding CNN, the identified site-specific yield response functions were perfectly linear as we confirmed in the testing results.
+
+```{r table-optN-train, tab.cap = "Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML methods and modeling scenarios on training datasets"}
+report_table_optN_train
+```
+
+Table \@ref(tab:table-y-train) shows the mean RMSE of yield prediction over the one thousand simulations using the training datasets as testing datasets.
+Interestingly, the performances of the prediction-oriented ML methods in predicting yields were relatively improved compared with the test results.
+Despite the improvement of prediction-oriented ML methods in yield prediction accuracy, it did not result in the more accurate EONR estimates.
+This supports our argument that the model’s yield prediction accuracy has little to do with its EONR prediction accuracy.
+
+```{r table-y-train, tab.cap = "Mean RMSE of yield prediction (kg/ha) by ML methods and modeling scenarios on training datasets"}
+report_table_y_train
+```

### 2022-02-14 Writing/manuscript_cea.rmd
minor changes
New results and added training accuracy of the ML methods to supplementary

@@
 We used the RF, BRF, and CNN ML methods to estimate yield response functions, and we used the CF method to estimate treatment effects.
-For each method, we estimated site-specific EONRs using the training data set, and checked the statistical performance of the predicted site-specific EONR using the validation data set.
+For each method, we estimated site-specific EONRs using the training dataset, and checked the statistical performance of the predicted site-specific EONR using the validation dataset.
 Detailed descriptions of these steps are provided below.
-The *R* and *python* codes that implement the simulation analyses are available at @Kakimoto2022codes.
+The *R* and *python* codes that implement the simulation analyses are publicly accessible as a Mendeley dataset [@Kakimoto2022codes].
 
@@
 
-A cell-level data set for the whole field, $\{(y_{i,j}, N^{opt}_{i,j}, N_{i,j}, \mathbf{c}_{i,j}): i \in \{1,2,\dots,1536\}, j \in \{1,2,\dots,36\}\}$ was generated by plugging in the parameter values, the error term, and the assigned nitrogen rates into \@ref(eq:eqn6).
+A cell-level dataset for the whole field, $\{(y_{i,j}, N^{opt}_{i,j}, N_{i,j}, \mathbf{c}_{i,j}): i \in \{1,2,\dots,1536\}, j \in \{1,2,\dots,36\}\}$ was generated by plugging in the parameter values, the error term, and the assigned nitrogen rates into \@ref(eq:eqn6).
 The cell-level data were then aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation.
@@
 
-In subsequent modeling scenarios, we made the simulated experimental data more realistic by varying the degree to which the researcher understood what the needed covariates' values were those in the data set.
-In the second scenario, denoted "abytt," we introduced additional variables $\theta^1$ and $\theta^2$, and the researcher's data set contained values of $\alpha_{i}$, $\beta_{i}$, $ymax_{i}$, $\theta^1_{i}$ and $\theta^2_{i}$ for all subplots $i=1,\dots,1536$.
+In subsequent modeling scenarios, we made the simulated experimental data more realistic by varying the degree to which the researcher understood what the needed covariates' values were those in the dataset.
+In the second scenario, denoted "abytt," we introduced additional variables $\theta^1$ and $\theta^2$, and the researcher's dataset contained values of $\alpha_{i}$, $\beta_{i}$, $ymax_{i}$, $\theta^1_{i}$ and $\theta^2_{i}$ for all subplots $i=1,\dots,1536$.
 $\theta^1$ and $\theta^2$ had no effect on yield, but they were spatially correlated with $\beta_{i}$.
@@
 
-In the third scenario, denoted "aabbyy," the researcher's data set did not contain values of $\alpha_{i}$, $\beta_{i}$, or $ymax_{i}$.
+In the third scenario, denoted "aabbyy," the researcher's dataset did not contain values of $\alpha_{i}$, $\beta_{i}$, or $ymax_{i}$.
 Rather, it contained subplot-level values of permutations of $\alpha$, $\beta$, and $ymax$.
@@
 RF ann BRF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving an honest tree-building process), and the optimal values for these parameters were selected by cross-validation.
-Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same data set was used.
-To reduce the variance of predictions for prediction accuracy, we set the number of trees (*num.trees*) at a high value, $4000$.
+Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same dataset was used.
+To reduce the variance of predictions for prediction accuracy, we set the number of trees (*num.trees*) at a high value, $2000$.
 
@@
 
-For evaluation of yield and EONR predictions, a data set from a different simulation round was used as the test data set.
-For example, for simulation number 1, the training data set from simulation number 2 was used as the test data set.
-This process works because the training data sets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$).
-Further, all training data sets were generated independently, so for any particular simulation round, the data set from any other round could serve as a valid test data set.
+For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset.
+For example, for simulation number 1, the training dataset from simulation number 2 was used as the test dataset.
+This process works because the training datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$).
+Further, all training datasets were generated independently, so for any particular simulation round, the dataset from any other round could serve as a valid test dataset.
 This practice made the creation of one thousand additional simulations fields unnecessary.
@@
 
-Table \@ref(tab:table-optN-subplot-wide) shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the one thousand simulations; it makes immediately clear that CF-base considerably outperformed the other ML methods, and that the profits based on CF-base's EONR estimates were the closest to the true maximum profits.
+Table \@ref(tab:table-optN) shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the one thousand simulations; it makes immediately clear that CF-base considerably outperformed the other ML methods, and that the profits based on CF-base's EONR estimates were the closest to the true maximum profits.
 BRF performed considerably better predicting EONR than did RF.
@@
 
-```{r table-optN-subplot-wide, tab.cap = "Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML methods and modeling scenarios"}
+```{r table-optN, tab.cap = "Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML methods and modeling scenarios"}
 report_table_optN
@@
 
-Table \@ref(tab:table-y-subplot-wide) shows the mean RMSE of yield prediction over the one thousand simulations.
+Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations.
 Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN.
@@
 
-```{r table-y-subplot-wide, tab.cap = "Mean RMSE of yield prediction (kg/ha) by ML methods and modeling scenarios"}
+```{r table-y, tab.cap = "Mean RMSE of yield prediction (kg/ha) by ML methods and modeling scenarios"}
 report_table_y

### 2022-02-14 Codes/2_2_Forest_main_sim.R

@@ -51,23 +51,23 @@ B=1000
 
 # === start simulation === #
 for (var in var_ls_variations){
-		# var = c("alpha", "beta", "ymax")
-		set.seed(1378)
-		# --- for each modeling scenario run: --- #
-		sim_results <- lapply(1:B, 
-			function(x){
-				sim_par(
-					i = x,
-					var_ls = var,
-					reg_data = reg_data_all[sim==x&padding==1,],
-	      			test_data = test_data_all[sim==x&padding==1,],
-	      			N_levels = reg_data_all[sim==x,]$rate%>%unique()%>%sort()
-	      		)
-			}
-		) %>%
-		rbindlist()
+	# var = c("alpha", "beta", "ymax")
+	set.seed(1378)
+	# --- for each modeling scenario run: --- #
+	sim_results <- lapply(1:B, 
+		function(x){
+			sim_par(
+				i = x,
+				var_ls = var,
+				reg_data = reg_data_all[sim==x&padding==1,],
+	      		test_data = test_data_all[sim==x&padding==1,],
+	      		N_levels = reg_data_all[sim==x,]$rate%>%unique()%>%sort()
+	      	)
+		}
+	) %>%
+	rbindlist()
 
-		saveRDS(sim_results, paste0("./Shared/Results/Forest_rawRes/forest_SimRes_", paste0(var, collapse = "_"), ".rds"))
+	saveRDS(sim_results, paste0("./Shared/Results/Forest_rawRes/forest_SimRes_", paste0(var, collapse = "_"), ".rds"))
 }
 
 

### 2022-02-14 Codes/4_prepare_results.R

@@ -1,66 +1,93 @@
+# ==========================================================================
+# Prepare field data set for writing
+# ==========================================================================
+#' Objective:
+#' + create field data sets by cells, subplots, and plots
+library(here)
+library(sf)
+library(data.table)
+library(ggplot2)
+library(ggthemes)
+library(viridis)
+library(tidyverse)
+library(ggpubr)
+
+
+# === Load Functions === #
 source(here("GitControlled/Codes/0_1_functions_gen_analysis_data.R"))
 
-
+# === Prices === #
 pCorn <- price_table[2, pCorn]
 pN <- price_table[2, pN]
-
-field_cell_dt <- data.table(field_cell_sf)
 
 # /*=================================================*/
 #' # Field Data Sets
 # /*=================================================*/
 
-# /*----------------------------------*/
-#' ## (1) cell-level data set
-# /*----------------------------------*/
+#/*----------------------------------*/
+#' ## (1) cell-level data set 
+#/*----------------------------------*/
 # + NOTE: I needed to do the following things, because the existing raw data does not have m_error
 field <- readRDS(here("Shared/Data/for_Simulations/analysis_field.rds"))
 
 coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))
 
-x <- 1
+x=1
 coef_data_m <- coef_data[sim == x, ]
 coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]
 
-
-sample_dt_cell <- prepare_raw_data(x, field = field, coef_data_m = coef_data_m, coef_data_t = coef_data_t, app_error = "no") %>%
+sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
   .$reg_raw_data
 
-field_cell_sf <-
-  left_join(dplyr::select(field, unique_cell_id), field_cell_dt, by = "unique_cell_id") %>%
-  na.omit() %>%
-  mutate(plot_id = ceiling(subplot_id / 4)) %>%
-  filter(padding == 1)
-
+field_cell_sf <- 
+  left_join(select(field, unique_cell_id), sample_dt_cell, by="unique_cell_id")%>%
[…]

### 2022-02-14 Codes/PrepareResults.R

@@ -1,4 +1,4 @@
-## ----set-up, cache = F-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+## ----set-up, cache = F------------------------------------------------------------------------
 library(knitr)
 library(here)
 
@@ -9,7 +9,7 @@ knitr::opts_chunk$set(
   cache = FALSE
 )
 
-## ----packages, cache = FALSE, include = FALSE--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+## ----packages, cache = FALSE, include = FALSE-------------------------------------------------
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -34,10 +34,9 @@ library(ftExtra)
 library(officer)
 library(officedown)
 library(modelsummary)
-library(latex2exp)
 
 
-## ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+## ---------------------------------------------------------------------------------------------
 theme_figure <- 
   theme(
     plot.title = element_text(hjust = 0.5),
@@ -54,6 +53,7 @@ theme_dist <-
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     strip.text.x = element_text(size = 12, face = "bold"),
+    strip.text.y = element_text(size = 12, face = "bold"),
     legend.title = element_text(size = 12, face = "bold"),
     legend.text = element_text(size = 12, face = "bold"),
     legend.position = "bottom",
@@ -65,7 +65,7 @@ set_flextable_defaults(
   )
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE----------------------------------------
 # === plot-level field data set  === #
 field_plot_sf <-
   here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
@@ -82,10 +82,7 @@ field_cell_sf <-
   readRDS()
 
 
[…]

### 2022-02-15 Writing/CEA_2nd_round/replies_rev_1.rmd
Edit the formatting for re-submission to CEA

@@
 First, in the new manuscript we consolidated the original manuscript's 3.1.2 and 3.1.3 into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we moved to the supplementary appendix (Appendix B) the detailed explanation of the conceptual framework behind the yield response functions based on cell-level characteristics, $c_i$.
-In addition, we moved to Appendix C our detailed discussion of parameters and error term generation, which included a number of tables and figures.
-<span style = "color: blue;"> Shun put table and figure numbers here </span>.
+In addition, we moved to Appendix C our detailed discussion of parameters and error term generation, which included a number of tables and figures (Table C.1.1, Figure C.1.1).
 
@@
 <span style="color:blue">  
-Shun is running simulations on training dataset and will report the results.
+We have newly added the results of training accuracy to Appendix D. 
 </span>

### 2022-02-15 Codes/PrepareResults.R

@@ -117,6 +117,10 @@ variogram_tb <-
     value = as_paragraph("NOTE: Only in ", as_i("ymax"), " are consistent units of measurement used for Mean, Nugget, and Sill ", "(", as_i("kg"),")."),
     ref_symbols = NA
   ) %>%
+  # set_caption(
+  #   caption = "Table C.1: The parameters for the Variogram models",
+  #   style = "Table Caption"
+  # ) %>%
   autofit()
 
 
@@ -141,7 +145,7 @@ plot <-
   geom_sf(data = ex_plot, fill = "green", size = 1) +
   coord_sf(expand = FALSE) +
   # theme_void() +
-  ggtitle("12 \u00D7 12 subplots") +
+  ggtitle("12 \u00D7 32 plots") +
   theme_figure
 
 
@@ -224,7 +228,7 @@ field_Ndesign <-
   ) +
   scale_fill_viridis_d() +
   labs(fill = "Nitrogen rate\n  (kg/ha)") +
-  ggtitle("(a) Trial Design") +
+  ggtitle("(1) Trial Design") +
   theme_figure
 
 
@@ -235,7 +239,7 @@ vis_yield_subplot <-
   geom_sf(aes(fill = yield), size = 0) +
   scale_fill_viridis_c() +
   labs(fill = "Yield Level\n  (kg/ha)") +
-  ggtitle("(b) Simulated Yield Level") +
+  ggtitle("(2) Simulated Yield Level") +
   theme_figure
 
 
@@ -304,7 +308,6 @@ res_y_train <-
 res_y_test <-
   allML_summary_bySim %>%
   .[type == "test" & Method %in% c("RF", "BRF", "CNN")]
-
 
 # ==== Summary Table ====#
 # --- on training data sets--- #
@@ -386,18 +389,7 @@ fig_y_optN <-
   ylim(NA, 95) +
   labs(y = " RMSE of EONR Estimation (kg/ha)") +
   labs(x = " RMSE of Yield Prediction (kg/ha)") +
-  theme_few() +
-  theme(
-    strip.text.x = element_text(size = 12, face = "bold"),
-    strip.text.y = element_text(size = 12, face = "bold"),
-    legend.title = element_blank(),
-    legend.text = element_text(size = 12, face = "bold"),
-    legend.position = "bottom"
-  ) +
-  theme_figure
-
-# print(fig_y_optN, preview = "docx")
[…]

### 2022-02-15 Codes/PrepareResults.rmd

@@
   ) %>%
+  # set_caption(
+  #   caption = "Table C.1: The parameters for the Variogram models",
+  #   style = "Table Caption"
+  # ) %>%
   autofit()
@@
   # theme_void() +
-  ggtitle("12 \u00D7 12 subplots") +
+  ggtitle("12 \u00D7 32 plots") +
   theme_figure
@@
   labs(fill = "Nitrogen rate\n  (kg/ha)") +
-  ggtitle("(a) Trial Design") +
+  ggtitle("(1) Trial Design") +
   theme_figure
@@
   labs(fill = "Yield Level\n  (kg/ha)") +
-  ggtitle("(b) Simulated Yield Level") +
+  ggtitle("(2) Simulated Yield Level") +
   theme_figure
@@
   labs(x = " RMSE of Yield Prediction (kg/ha)") +
-  theme_few() +
-  theme(
-    strip.text.x = element_text(size = 12, face = "bold"),
-    strip.text.y = element_text(size = 12, face = "bold"),
-    legend.title = element_blank(),
-    legend.text = element_text(size = 12, face = "bold"),
-    legend.position = "bottom"
-  ) +
-  theme_figure
-
-# print(fig_y_optN, preview = "docx")
-# dfabline <- data.frame(x = 0:3500, y=0:3500)
+  theme_dist
 ```
@@
   # .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
-  .[Method == "CF_base", Method := "CF_base"] %>%
+  .[Method == "CF_base", Method := "CF-base"] %>%
   .[, Model := case_when(
@@
   geom_density(aes(x = pi_loss, fill = Method), alpha = 0.7) +
-  labs(x = expression(paste(hat(pi)["def"], " ($/ha)"))) +
+  labs(x = expression(paste(hat(pi)[italic("def")], " ($/ha)"))) +
   facet_wrap(~Model, ncol = 1) +

### 2022-02-15 Writing/appendix.rmd

--- 2022-02-13 Writing/appendix.rmd
@@
-# Appendix A: Causal Tree Example {#ctree-ex}
+<!-- NOTE: Erase the extra Figure, Table and section numbers manually-->
 
-Figure \@ref(fig:ct-ex) shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$)($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
+## Appendix A: Causal Tree Example {-}
 
-```{r ct-ex, fig.width=5, fig.height=5, fig.align="center", fig.cap = "An illustrative example of causal tree"}
-fancyRpartPlot(opfit, sub = "")
+Figure A.1 shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$)($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
+
+```{r ct-ex, fig.width=5, fig.height=5, fig.align="center", fig.cap = "Figure A.1: An illustrative example of a causal tree"}
+par(family="Times")
+fancyRpartPlot(opfit, sub="")
 ```
@@
 
-# Appendix B: Understanding yield response functions better
+## Appendix B: Understanding Yield Response Functions Better {-}
 
-Another way to writing Eq. \@ref(eq:eqn6) that may help understanding the yield response (Eq. \@ref(eq:eqn6)) better conceptually is as follows:
+Another way to writing Eq. \@ref(eq:eqn3) that may help understanding the yield response Eq. (B.1) better conceptually is as follows:
 
-\begin{alinged}
-f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) \cdot N)) + \varepsilon. 
-\end{alinged}
+$$
+f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) \cdot N)) + \varepsilon. \qquad \text{(B.1)}
+$$
 
@@
 
-\begin{equation}
-f(N_{i}, \mathbf{c}_{i}) = ymax(\mathbf{c}_{i})(1-exp(\alpha(\mathbf{c}_{i}) + \beta(\mathbf{c}_{i})\cdot N_{i})) + \varepsilon_{i}. 
-\end{equation}
+$$
+f(N_{i}, \mathbf{c}_{i}) = ymax(\mathbf{c}_{i})(1-exp(\alpha(\mathbf{c}_{i}) + \beta(\mathbf{c}_{i})\cdot N_{i})) + \varepsilon_{i}. \qquad \text{(B.2)}
+$$
 
-The simplified notation of this equation, where $c_i$ is dropped, is \@ref(eq:eqn6) in section <span style = "color: blue;"> section number here </span>.
+The simplified notation of this equation, where $c_i$ is dropped, is Eq. \@ref(eq:eqn3) in section 3.1.2.
 
-<span style = "color: blue;"> Shun, number the equations </span>
+## Appendix C: Parameter Generation {-}
 
-# Appendix C: Parameter generation
-
-## Base parameters $\alpha$, $\beta$, and $ymax$ {#par-gen}
+### C.1 $\quad$ Base parameters **$\alpha$**, **$\beta$**, and **$ymax$** {-}
 Parameters $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$ were modeled as spatially autocorrelated using unconditional Gaussian geostatistical simulation based on the spherical variogram model.
@@
 
-Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
+Table C.1.1 shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
 (Codes used to generate parameter values are publicly accessible as a Mendeley dataset [@Kakimoto2022codes].) The range and nugget of all parameters were assumed to be $400$ m and 0.
-The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12,000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$.
-See Figure \@ref(fig:fig-parameters) for an example of the generated parameters.
+The means of $\alpha$, $\beta$, $ymax$, and $\varepsilon$ were assumed to be $-0.5$, $0$, $12,000$ kg/ha, and $0$, and their sills were assumed to be $0.02$, $1.0$, $2.0 \times 10^{6}$ kg/ha, and $0.015$.
+See Figure C.1.1 for an example of the generated parameters.
 
-<span style = "color: blue;"> Shun, combnine all the figures </span>
-
-```{r variogram-parameters, tab.cap = "The Parameters for the Variogram Models"}
+```{r, tab.cap = "Table C.1.1: The parameters for the variogram models"}
 variogram_tb
@@
 
-```{r fig-parameters, fig.width=7, fig.height=9, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics", cache = TRUE}
-
+```{r, fig.width=7, fig.height=9, fig.cap = "Figure C.1.1: An illustrative example of spatial distributions of field characteristics", cache = TRUE}
 field_alpha + field_beta + field_ymax + field_m_error + field_optN + plot_layout(ncol = 2)
@@
 
-## Splitting the base parameters {#split-pars}
+### C.2 $\quad$ Splitting the Base Parameters {-}
 
@@
 The codes used to implement the abovementioned parameter splitting are publicly accessible as a Mendeley dataset [@Kakimoto2022codes].
+
+## Appendix D:  Training Accuracy of the ML methods {-}
+
+During the simulations, we evaluated the training accuracy using the same ML models we presented in the Result and Discussion section. 
+Table D.1 shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the one thousand simulations using the training datasets as testing datasets.
+Overall, the performances of each ML method did not change between training and testing datasets.
+Regarding CNN, the identified site-specific yield response functions were perfectly linear as we confirmed in the test results.
+
+```{r table-optN-train, tab.cap = "Table D.1: Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on training datasets"}
+report_table_optN_train
+```
+
+Table D.2 shows the mean RMSE of yield prediction over the one thousand simulations using the training datasets as testing datasets.
+Interestingly, the performances of the prediction-oriented ML methods in predicting yields were relatively improved compared with the test results.
+Despite the improvement of prediction-oriented ML methods in yield prediction accuracy, it did not result in the more accurate EONR estimates.
+This also supports our argument that the model’s yield prediction accuracy has little to do with its EONR prediction accuracy.
+
+```{r table-y-train, tab.cap = "Table D.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on training datasets"}
+report_table_y_train
+```

### 2022-02-15 Writing/manuscript_cea.rmd

@@
 CF was developed specifically for identifying heterogeneous treatment effects [@athey2016recursive; @Wager2018a].
-Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf (see Appendix \@ref(ctree-ex) for an example of a causal tree that can help further clarify how CF works).
+Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf (see Appendix A for an example of a causal tree that can help further clarify how CF works).
 
@@
 The simulated field was created based on an actual 51-ha Illinois field on which the Data-Intensive Farm Management (DIFM) project [@bullock2019] has run multiple OFPEs.
-Figure \@ref(fig:field-map) illustrates that simulated trials consisted of $384$ 18.3 m $\times$ 73.2 m "plots," each of which was assigned an N fertilizer application rate.
+Figure \@ref(fig:field-map) illustrates that simulated trials consisted of 384 18.3 m $\times$ 73.2 m "plots," each of which was assigned an N fertilizer application rate.
 Each plot was made up of four (4-rows $\times$ 1-column) 18.3 m $\times$ 18.3 m "subplots," which were unit of analysis used in subsequent statistical analysis.
@@
 Eq.
-\@ref(eq:eqn6) shows the yield level on cell $j$ in subplot $i$:
+\@ref(eq:eqn3) shows the yield level on cell $j$ in subplot $i$:
 
 \begin{equation}
-f(N_{i}: \alpha_{i,j}, \beta_{i,j}, ymax_{i,j}) = ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) + \varepsilon_{i,j}. (\#eq:eqn6)
+f(N_{i}: \alpha_{i,j}, \beta_{i,j}, ymax_{i,j}) = ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) + \varepsilon_{i,j}. (\#eq:eqn3)
 \end{equation}
@@
 The first term on the right-hand side of Eq.
-\@ref(eq:eqn6) is the deterministic yield component.
+\@ref(eq:eqn3) is the deterministic yield component.
 The variable $N$ represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot.
 Also in Eq.
-\@ref(eq:eqn6), $\alpha$, $\beta$, and $ymax$ are spatially varying parameters that govern how yield level is determined in conjunction with the applied N rate.
+\@ref(eq:eqn3), $\alpha$, $\beta$, and $ymax$ are spatially varying parameters that govern how yield level is determined in conjunction with the applied N rate.
 They reflect local cell-level production conditions, such as soil characteristics and topography.
@@
 These prices are used consistently for our simualtions.
-See Appendix \@ref(par-gen) for further details on how the paremeters were generated and sample maps of the parameters and true economically optimal N rates.
+See Appendix C.1 for further details on how the paremeters were generated and sample maps of the parameters and true economically optimal N rates.
 
@@
 
-A cell-level dataset for the whole field, $\{(y_{i,j}, N^{opt}_{i,j}, N_{i,j}, \mathbf{c}_{i,j}): i \in \{1,2,\dots,1536\}, j \in \{1,2,\dots,36\}\}$ was generated by plugging in the parameter values, the error term, and the assigned nitrogen rates into \@ref(eq:eqn6).
+A cell-level dataset for the whole field, $\{(y_{i,j}, N^{opt}_{i,j}, N_{i,j}, \mathbf{c}_{i,j}): i \in \{1,2,\dots,1536\}, j \in \{1,2,\dots,36\}\}$ was generated by plugging in the parameter values, the error term, and the assigned nitrogen rates into Eq.
+\@ref(eq:eqn3).
 The cell-level data were then aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation.
@@
 \begin{equation}
-\{(y_{i}, N^{opt}_{i}, N_{i}) = \frac{1}{36}\sum_{j=1}_{36} (y_{i,j}, N^{opt}_{i,j}, N_{i,j}): i \in \{1,2,\dots,1536\}\}. (\#eq:eqn9)
+\{(y_{i}, N^{opt}_{i}, N_{i}) = \frac{1}{36}\sum_{j=1}^{36} (y_{i,j}, N^{opt}_{i,j}, N_{i,j}): i \in \{1,2,\dots,1536\}\}. (\#eq:eqn4)
 \end{equation}
@@
 Rather, it contained subplot-level values of permutations of $\alpha$, $\beta$, and $ymax$.
-Each of the three parameters were split into two parts in a spatially correlated manner, and six new covariates were created (see Appendix \@ref(split-pars) for the details about this parameter-splitting process).
+Each of the three parameters were split into two parts in a spatially correlated manner, and six new covariates were created (see Appendix C.2 for the details about this parameter-splitting process).
 These were $\alpha^{1}_{i}$, $\alpha^{2}_{i}$, $\beta^{1}_{i}$, $\beta^{2}_{i}$, $ymax^{1}_{i}$, and $ymax^{2}_{i}$.
@@
 The RF, BRF, and CNN methods all followed the same conceptual steps to estimate site-specific EONR: 1) estimate the yield production functions and 2) calculate site-specific EONRs based on that estimated function.
-For the given modeling scenario, RF and BRF predict yield by using all the available covariates as explanatory variables in the estimation process.
+For the given modeling scenario, RF, BRF and CNN predict yield by using all the available covariates as explanatory variables in the estimation process.
 The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for RF and BRF modeling.
@@
 @barbosa2020modeling demonstrated that among several CNN architectures, this architecture modeled crop yield response to N rate management best.
-CNN was implemented in *Python* v3.7.6 using *Pytorch* v1.7.0 [@paszke2017automatic].
+CNN was implemented in Python v3.7.6 using Pytorch v1.7.0 [@paszke2017automatic].
 The Adam optimizer [@kingma2014adam] was used with a learning rate of $0.001 \%$ (default value).
@@
 \begin{equation}
-\hat{N}^{opt}_{i} = \operatorname*{argmax}_{N}(p \cdot\hat{g}_m(N, \mathbf{\Omega_{i}}) - w \cdot N), (\#eq:eqn8)
+\hat{N}^{opt}_{i} = \operatorname*{argmax}_{N}(p \cdot\hat{g}_m(N, \mathbf{\Omega_{i}}) - w \cdot N), (\#eq:eqn5)
 \end{equation}
@@
 \begin{equation}
-\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega_{i}}) = \hat{\tau}_{N_{1} \rightarrow N_{m}}(\mathbf{\Omega_{i}}). (\#eq:eqn9)
+\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega_{i}}) = \hat{\tau}_{N_{1} \rightarrow N_{m}}(\mathbf{\Omega_{i}}). (\#eq:eqn6)
 \end{equation}
@@
 
-Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML methods and modeling scenarios, respectively (CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always took values $62.8$ kg/ha and \$$58.99$/ha, respectively.) The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios.
-Interestingly, RF seems particularly vulnerable to the inclusion of more variables, with RMSE ($\hat{\pi}_{def}$) increasing from `r table_optN_prep[Model=="aby",rmse_optN_RF]` (`r table_optN_prep[Model=="aby", pi_loss_RF]`) in the "aby" scenario to `r table_optN_prep[Model=="aabbyytt", rmse_optN_RF]` (`r table_optN_prep[Model=="aabbyytt", pi_loss_RF]`) in the "aabbyytt" scenario.
+Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML methods and modeling scenarios, respectively.
+The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios.
+Interestingly, RF seems particularly vulnerable to the inclusion of more variables, with RMSE ($\hat{\pi}_{def}$) increasing from `r table_optN_prep[type=="test" & Model=="aby",rmse_optN_RF]` (`r table_optN_prep[type=="test" & Model=="aby", pi_loss_RF]`) in the "aby" scenario to `r table_optN_prep[type=="test" & Model=="aabbyytt", rmse_optN_RF]` (`r table_optN_prep[type=="test" & Model=="aabbyytt", pi_loss_RF]`) in the "aabbyytt" scenario.
 CF-base was more robust to the inclusion of additional variables.
@@
 It plots the estimated treatment effects against true treatment effects by treatment types and ML methods under the "aabbyytt" scenario in one of the one thousand simulations rounds.
-The figure shows points clustered around the red 1-to-1 line, meaning that the estimated treatment effects did not exhibit significant bias.
+Except in the cases of CNN, the figure shows points clustered around the red 1-to-1 line, meaning that the estimated treatment effects did not exhibit significant bias.
 However, the models differed substantially in the accuracy of their treatment effect estimations.
-Points are clustered more tightly about the 1-to-1 line for CF-base than RF and BRF.
+Points are clustered more tightly about the 1-to-1 line for CF-base than RF, BRF and CNN.
 That is, CF-base estimated treatment effects much more efficiently than did RF and BRF, which focus on yield prediction rather than treatment effect estimation.

### 2022-02-19 Codes/PrepareResults.rmd
made changes for publication

@@
   labs(fill = "Nitrogen rate\n  (kg/ha)") +
-  ggtitle("(1) Trial Design") +
+  ggtitle("(1) Trial design") +
   theme_figure
@@
   scale_fill_viridis_c() +
-  labs(fill = "Yield Level\n  (kg/ha)") +
-  ggtitle("(2) Simulated Yield Level") +
+  labs(fill = "Yield level\n  (kg/ha)") +
+  ggtitle("(2) Simulated yield level") +
   theme_figure
@@
 
-data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
-  na.omit() %>%
-  dplyr::rename(tgtn = NPlan, tgts = SRPlan)
+# data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
+#   na.omit() %>%
+#   dplyr::rename(tgtn = NPlan, tgts = SRPlan) %>%
 
-data_dt <- data.table(data_sf) %>%
-  setnames(names(.), tolower(names(.)))
+# data_dt <- data.table(data_sf) %>%
+#   setnames(names(.), tolower(names(.))) %>%
+#   .[,.(tgts, yield, slope, ecs)]
+
+# saveRDS(data_dt, here("Shared/Results/for_writing/ctree_data.rds"))
+
+data_dt <- readRDS(here("Shared/Results/for_writing/ctree_data.rds"))
 
@@
 opfit <- prune(tree, opcp)
+# fancyRpartPlot(opfit, sub="")
 ```

### 2022-02-19 Writing/CEA_2nd_round/replies_rev_1.rmd
made changes for publication

@@
 It was explained twice, once each in subsections 2.2 and 3.2.2.
-We have deletedthe explanation in 2.2 and also changed the heading in 2.1 to "Estimating EOIR and Treatment Effects."
+We have deletedthe explanation in 2.2 and also changed the heading in 2.1 to "EOIR Estimation and Treatment Effects."
 
@@
 
-Second, we consolidated subsection 3.1.4 and 3.1.5 of the original manuscript into a single subsubsection called "Trial Design and Yield Data Generation for Modeling." In doing so, we removed some text and combined the original manuscript's figures x and y in the single figure z in the current manuscript.
+Second, we consolidated subsection 3.1.4 and 3.1.5 of the original manuscript into a single subsubsection called "Trial Design and Yield Data Generation for Modeling." In doing so, we removed some text and combined the original manuscript's figures 5 and 7 in the single figure 2 in the current manuscript.
 
-Third, we moved to an appendix the previous manuscript’s detailed description of parameter splitting.
+Third, we moved to Appendix C.2 the previous manuscript’s detailed description of parameter splitting.
 
@@
 <span style="color:blue">  
-Done
+We modified the length units (line 162) 
 </span>
@@
 <span style="color:blue">  
-Done. Please see Figure 2. 
+We modified the figure. Please see Figure 1. 
 </span>
@@
 However, we have decided to include CNN results in Figures 8, 9, and 10 of the previous manuscript.
-which are Figures 3, 4, and 5 of the revised manuiscript.
+which are Figures 3, 4, and 5 of the revised manuscript.
 

### 2022-02-19 Writing/manuscript_cea.rmd
made changes for publication

@@
 Table \@ref(tab:count-table) shows that following this process led to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds.
-For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of $1000$ iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations.
+For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of 1000 iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations.
 That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF models best at yield prediction did not provide EONR estimates that led to high profits.
 Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously.
-For example, Table \@ref(tab:count-table) shows that BRF predicted yield best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best.
+In the rounds in which BRF predicted yield best, then the two-step process worked well.
+For example, Table \@ref(tab:count-table) shows that BRF predicted EONR best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best.
 But BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.

### 2022-02-19 Codes/PrepareResults.R

@@ -1,4 +1,4 @@
-## ----set-up, cache = F------------------------------------------------------------------------
+## ----set-up, cache = F----------------------------------------------------------------------------------------------------------------------------
 library(knitr)
 library(here)
 
@@ -9,7 +9,7 @@ knitr::opts_chunk$set(
   cache = FALSE
 )
 
-## ----packages, cache = FALSE, include = FALSE-------------------------------------------------
+## ----packages, cache = FALSE, include = FALSE-----------------------------------------------------------------------------------------------------
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -36,7 +36,7 @@ library(officedown)
 library(modelsummary)
 
 
-## ---------------------------------------------------------------------------------------------
+## -------------------------------------------------------------------------------------------------------------------------------------------------
 theme_figure <- 
   theme(
     plot.title = element_text(hjust = 0.5),
@@ -65,7 +65,7 @@ set_flextable_defaults(
   )
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE----------------------------------------
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE--------------------------------------------------------------------------------------------
 # === plot-level field data set  === #
 field_plot_sf <-
   here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
@@ -82,7 +82,7 @@ field_cell_sf <-
   readRDS()
 
 
-## ---------------------------------------------------------------------------------------------
+## -------------------------------------------------------------------------------------------------------------------------------------------------
 variogram_tb <-
   data.frame(
     Parameters = c("alpha_ij", "beta_ij", "ymax_ij", "varepsilon_ij"),
@@ -124,7 +124,7 @@ variogram_tb <-
   autofit()
 
 
-## ----field-map-visualization, dependson = "setup"---------------------------------------------
+## ----field-map-visualization, dependson = "setup"-------------------------------------------------------------------------------------------------
 
 # === Preparation === #
 ex_plot <- field_plot_sf[224, ]
@@ -218,7 +218,7 @@ field_structure <-
   theme_void()
 
 
-## ---- dependson = "setup"---------------------------------------------------------------------
[…]

### 2022-02-19 Writing/CEA_2nd_round/replies_rev_2.rmd

@@
 
-# Comments:
+Thank you so much for your comments. By addressing them, we believe the manuscript is improved significantly. Below you will find your comments in bold and our replies in a regular font.
+
+<br>
 
@@
 <span style="color:blue"> 
-The extra "some" was removed from the sentence.
+The extra "some" was removed from the sentence (see p15 l.249).
 </span>
@@
 <span style="color:blue"> 
-The typo was corrected. 
+The typo was corrected (see p19 l.320). 
 </span>
@@
 <span style="color:blue">  
-The grammatical error was corrected. 
+The grammatical error was corrected (see p20 l.340). 
 </span>
@@
 <span style="color:blue">  
-We removed "much" from the sentence.
+We removed "much" from the sentence (see p24 l.366).
 </span>

### 2022-02-19 Writing/appendix.rmd

@@
 
-Figure A.1 shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$)($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
+Figure A.1 shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$) ($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
 

### 2022-03-15 Writing/CEA_2nd_round/replies_rev_1.rmd
minor edits
CEA 3rd round

@@
 
-Thank you so much for your comments. By addressing them, we believe the manuscript is improved significantly. Below you will find your comments in bold and our replies in a regular font.
+Thank you so much for your comments. By addressing them, we believe the manuscript has improved significantly. Below you will find your comments in bold and our replies in regular font.
 
@@
 First, in the new manuscript we consolidated the original manuscript's 3.1.2 and 3.1.3 into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we moved to the supplementary appendix (Appendix B) the detailed explanation of the conceptual framework behind the yield response functions based on cell-level characteristics, $c_i$.
-In addition, we moved to Appendix C our detailed discussion of parameters and error term generation, which included a number of tables and figures (Table C.1.1, Figure C.1.1).
+In addition, we moved to Appendix C our detailed discussion of parameters and error term generation, which included a number of tables and figures (Table C.1, Figure C.1).
 
@@
 <span style="color:blue">  
-We have followed the Editor's suggestion by sharing the simulation codes and the data on Mendeley Data (https://data.mendeley.com/datasets/y7cdhzww6w/draft?a=2e33b309-ca5c-49bc-95ce-9b3920d5544a) to increase the accessibility.
+We have followed the Editor's suggestion by sharing the simulation codes and the data on Mendeley Data (https://doi.org/10.17632/y7cdhzww6w.1) to increase the accessibility.
 The name of the data set is "Codes and Data Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation", and two folders are included in this data set: "Codes" and  "Data".
@@
 Please read README.md for the steps to reproduce.
-In addition, we also created a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).
+In addition, we also created a public github repository named VRA_with_CF (https://github.com/Shunkei3/VRA_with_CF.git).
 </span>
@@
 <span style="color:blue">  
-We modified the length units (line 162) 
+We modified the length units (line 163) 
 </span>

### 2022-03-15 Writing/CEA_2nd_round/replies_rev_2.rmd

--- 2022-02-12 Writing/CEA_2nd_round/replies_rev_2.rmd
@@
 
-# Comments:
+Thank you so much for your comments. By addressing them, we believe the manuscript has improved significantly. Below you will find your comments in bold and our replies in regular font.
+
+<br>
 
@@
 <span style="color:blue"> 
-The extra "some" was removed from the sentence.
+The extra "some" was removed from the sentence (see p15 l.250).
 </span>
@@
 <span style="color:blue"> 
-The typo was corrected. 
+The typo was corrected (see p19 l.321). 
 </span>
@@
 <span style="color:blue">  
-The grammatical error was corrected. 
+The grammatical error was corrected (see p20 l.341). 
 </span>
@@
 <span style="color:blue">  
-We removed "much" from the sentence.
+We removed "much" from the sentence (see p24 l.367).
 </span>

### 2022-03-15 Writing/appendix.rmd

--- 2022-02-15 Writing/appendix.rmd
@@
 
-Figure A.1 shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$)($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
+Figure A.1 shows an example of a CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$) ($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
 
@@
 The number and the percentage of observations belonging to the node are shown below that.', fp_text(font.size = 9, font.family = "Times New Roman"))`
+
+<br>
 
@@
 
-Table C.1.1 shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
-(Codes used to generate parameter values are publicly accessible as a Mendeley dataset [@Kakimoto2022codes].) The range and nugget of all parameters were assumed to be $400$ m and 0.
+Table C.1 shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
+(Codes used to generate parameter values are publicly accessible as a Mendeley dataset [@Kakimoto2022codes], or as a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.) The range and nugget of all parameters were assumed to be $400$ m and 0.
 The means of $\alpha$, $\beta$, $ymax$, and $\varepsilon$ were assumed to be $-0.5$, $0$, $12,000$ kg/ha, and $0$, and their sills were assumed to be $0.02$, $1.0$, $2.0 \times 10^{6}$ kg/ha, and $0.015$.
-See Figure C.1.1 for an example of the generated parameters.
+See Figure C.1 for an example of the generated parameters.
 
-```{r, tab.cap = "Table C.1.1: The parameters for the variogram models"}
+<br>
+
+```{r, tab.cap = "Table C.1: The parameters for the variogram models"}
 variogram_tb
@@
 
-```{r, fig.width=7, fig.height=9, fig.cap = "Figure C.1.1: An illustrative example of spatial distributions of field characteristics", cache = TRUE}
+<br>
+
+```{r, fig.width=7, fig.height=9, fig.cap = "Figure C.1: An illustrative example of spatial distributions of field characteristics", cache = TRUE}
 field_alpha + field_beta + field_ymax + field_m_error + field_optN + plot_layout(ncol = 2)
 ```
+
+<br>
 
@@
 
-During the simulations, we evaluated the training accuracy using the same ML models we presented in the Result and Discussion section. 
+In this section, the performance of the models in terms of profitability, EONR estimation, and yield estimation when the trained models are evaluated against the training datasets instead of the separate testing datasets as supplementary information.
+
 Table D.1 shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the one thousand simulations using the training datasets as testing datasets.
-Overall, the performances of each ML method did not change between training and testing datasets.
-Regarding CNN, the identified site-specific yield response functions were perfectly linear as we confirmed in the test results.
+RF and BRF performs slightly better compared to the case when they are evaluated against the separate testing datasets.
+However, the relative ranking of the models is the same.
+
+<br>
 
@@
 
-Table D.2 shows the mean RMSE of yield prediction over the one thousand simulations using the training datasets as testing datasets.
-Interestingly, the performances of the prediction-oriented ML methods in predicting yields were relatively improved compared with the test results.
-Despite the improvement of prediction-oriented ML methods in yield prediction accuracy, it did not result in the more accurate EONR estimates.
-This also supports our argument that the model’s yield prediction accuracy has little to do with its EONR prediction accuracy.
+<br>
+
+Table D.2 presents the training accuracy of yield prediction: namely, the yield prediction accuracy when the trained model is evaluated using the training datasets as opposed to separate testing datasets.
+
+\newpage
 

### 2022-03-15 Writing/manuscript_cea.rmd
minor edits

@@
 CF was developed specifically for identifying heterogeneous treatment effects [@athey2016recursive; @Wager2018a].
-Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf (see Appendix A for an example of a causal tree that can help further clarify how CF works).
+Like RF, CF works by building an ensemble of trees, called *causal trees* (CTs), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf (see Appendix A for an example of a CT that can help further clarify how CF works).
 
@@
 Detailed descriptions of these steps are provided below.
-The *R* and *python* codes that implement the simulation analyses are publicly accessible as a Mendeley dataset [@Kakimoto2022codes].
+The R and python codes that implement the simulation analyses are publicly accessible as a Mendeley dataset [@Kakimoto2022codes], or as a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.
 
@@
 
-```{r table-optN, tab.cap = "Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML methods and modeling scenarios"}
+```{r table-optN, tab.cap = "Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario"}
 report_table_optN
@@
 
-Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML methods and modeling scenarios, respectively.
+Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML method and modeling scenario, respectively.
 The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios.
@@
 Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions.
-It plots the estimated treatment effects against true treatment effects by treatment types and ML methods under the "aabbyytt" scenario in one of the one thousand simulations rounds.
+It plots the estimated treatment effects against true treatment effects by treatment type and ML method under the "aabbyytt" scenario in one of the one thousand simulations rounds.
 Except in the cases of CNN, the figure shows points clustered around the red 1-to-1 line, meaning that the estimated treatment effects did not exhibit significant bias.
@@
 
-```{r table-y, tab.cap = "Mean RMSE of yield prediction (kg/ha) by ML methods and modeling scenarios"}
+```{r table-y, tab.cap = "Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario"}
 report_table_y
@@
 Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously.
-In the rounds in which BRF predicted yield best, then the two-step process worked well.
+In the rounds in which BRF predicted yield best, the two-step process worked well.
 For example, Table \@ref(tab:count-table) shows that BRF predicted EONR best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best.
@@
 
-<br>
+\newpage
 

### 2022-03-15 Writing/CEA_3rd_round/replies_rev_1.rmd

---
title: "Reply to Editor"
output:
  bookdown::word_document2:
    number_sections: no
    reference_docx: ../word_template_format.docx
---

Thank you so much for your comments. By addressing them, we believe the manuscript has improved significantly. Below you will find your comments in bold and our replies in regular font.

<br>

**1. The CNN result seems to be rather constant than linear. Please include a chart showing the CNN performance per training epoch to allow the reader to assess how good the CNN model converged.**

<span style="color:blue">

</span>

<br>

**2. Line 70. Why can't EOIRs be estimated by the intervention studies mentioned in 28ff?**

<span style="color:blue">

</span>

<br>

**3. Line 194 simualtions**

<span style="color:blue">

</span>

<br>

**4. Line 194 How exactly were the simulation parameters (table c.1, figure c.1) inspired by the field study (line 161ff) ?**

<span style="color:blue">

</span>

<br>

**5. Line 321 It seems RSME was never defined.**

<span style="color:blue">

</span>

<br>

**6. In principle, your ML models have to learn to replicate equation 3, right? You have to explain better why RSME for yield and EONR can be uncorrelated when they are directly related through Eq. 3 and 5. There must be an effect of yield prediction error on EONR. By definition, a 100% perfect yield prediction should reduce the EONR error to the effect of epsilon in Eq. 3. (As a side note, in this case the correlation between the RSMEs would also be zero.) A larger RSME for yield prediction would simultaneously increase the RSME of EONR until the EONR virtually becomes a random variable. Your comparison in Figure 6 may not be insightful in this regard. It might be confounded by effects from different prediction performance for different simulation parameters i.e. the prediction performance might be different depending on where you are in the hyperbola from Eq.3 . If the prediction performance is not uniform or the prediction error is of a similar size as the achievable yield increase, then it is natural that the RSMEs of EONR and yield prediction are not correlated. Figure C1.4 indicates that the effect size of the random error epsilon alone is already in the range of the achievable yield increase. I recommend to add a simulation of different ML performances and different epsilon values to test their effects.**

<span style="color:blue">

</span>

<br>

**7. Please insert a plot for true yield vs yield prediction to enable the reader to estimate the achieved prediction performance.**

<span style="color:blue">

</span>

<br>

**8. Please show to which degree N affected yield and how the relation between yield estimation error and the effect of N on yield increase was. I would like to see whether the models were able to reproduce the effect of N on yield at all.**

<span style="color:blue">

</span>

<br>

**9. Please extend the introduction by restating numbers for the state of the art of yield and EONR prediction performance from previous studies (as far as such numbers are available) to prevent that all of your readers have to consult the cited references.**

<span style="color:blue">

</span>

<br>

**10. Please discuss your results with regard to the state of the art (again as specific as possible) and discuss whether your yield prediction performance and your simulation approach (e.g. epsilon effect size) may have affected the results for EONR prediction.**

<span style="color:blue">

</span>

<br>

### 2022-03-16 Writing/CEA_3rd_round/replies_rev.rmd

---
title: "Reply to Editor"
output:
  bookdown::word_document2:
    number_sections: no
    reference_docx: ../word_template_format.docx
---

We appreciate your comments and

<br>

**1. The CNN result seems to be rather constant than linear. Please include a chart showing the CNN performance per training epoch to allow the reader to assess how good the CNN model converged.**

<span style="color:blue">  
Please see Figure xx in Appendix xx that shows the convergence of CNN for a single simulation round. We cannot show this kind of figure for all the simulation rounds. But, any interested readers can replicate our work as the codes will be accessible publicly.
</span>

<br>

**2. Line 70. Why can't EOIRs be estimated by the intervention studies mentioned in 28ff?**

<span style="color:blue">  
We do not say EOIR cannot be estimated by studies mentioned in 28ff. Indeed, any methods can "estimate" EOIR. However, no method can estimate the "true" EONR and we will 
"never" know true EONRs for real fields. We can only esimate them. This principle is at the core of statistical analysis. We never observe how data is generated (the underlying laws that govern how the world works whether it is physical, biological, or economic), but we can "estimate" (approximate) what thye look like. This means that when we try to evaluate how different models perofrm in predicting EONR using real data, we simply do not have a valid benchmark to compare against. Some may ask, then why don't we use models' yield prediction abililty because yield is observable. And this is precisely the dangerous practice that we show is wrong.

Please note that this is a stark contrast to "yield" (not EOIR) prediction because yields ARE observable and models can be verified. However, that is not the case for EOIR. This is why you need MC simulations where the data generating process (how yield responds to N, and how field characteristics affect yield response to N) is "known" to the researcher. This way, we can test model's ability to predict EONR, not yield. Any journal article that proposes a new statistical method always accompany the theory of why their method works (consistency of their estimation, etc) with MC simulations where the researchers determines how data is generated and apply their method. This is because we can never test the statistical property of a statistical method in principle using the real data. For example, please see (Shun, cite CF paper here.)

</span>

<br>

**3. Line 194 simualtions**

<span style="color:blue">

</span>

<br>

**4. Line 194 How exactly were the simulation parameters (table c.1, figure c.1) inspired by the field study (line 161ff) ?**

<span style="color:blue">

</span>

<br>

**5. Line 321 It seems RSME was never defined.**

<span style="color:blue">  
Please see page xx, line yy for the precise definition of the RMSE for yield and EONR predictions.
</span>

<br>

**6. In principle, your ML models have to learn to replicate equation 3, right? You have to explain better why RSME for yield and EONR can be uncorrelated when they are directly related through Eq. 3 and 5. There must be an effect of yield prediction error on EONR. By definition, a 100% perfect yield prediction should reduce the EONR error to the effect of epsilon in Eq. 3. (As a side note, in this case the correlation between the RSMEs would also be zero.) A larger RSME for yield prediction would simultaneously increase the RSME of EONR until the EONR virtually becomes a random variable. Your comparison in Figure 6 may not be insightful in this regard. It might be confounded by effects from different prediction performance for different simulation parameters i.e. the prediction performance might be different depending on where you are in the hyperbola from Eq.3 . If the prediction performance is not uniform or the prediction error is of a similar size as the achievable yield increase, then it is natural that the RSMEs of EONR and yield prediction are not correlated. Figure C1.4 indicates that the effect size of the random error epsilon alone is already in the range of the achievable yield increase. I recommend to add a simulation of different ML performances and different epsilon values to test their effects.**

<span style="color:blue">

We actually realized the results presented in Figure 6 is completely invalid. As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges. The biggest problem of the relationship we identified is that the maximum profit of the field is very different across simulations (the field in some simulations are simply more profitable than the fields in other simulations). So, basically, the observed variation in achieved profits by estimated site-specific EONR is dominated simply by how profitable fields are on average. For this reason, we eliminated the figure and also dropped our cliam that yield prediction and EONR prediction are uncorrelated. Thank you so much for spotting this embarassing mistake from our side.

However, please note that our cliam that better yield prediction does "not necessarily" lead to higher profit remains intact. This is evident in Table 1 and the analysis behind this table is valid. This happens because you can prefict yield well for a "wrong" reason, attributing parts of variations in yield to something other than its true driver.

approximating yield response function , predicting yield levels at the observed points

Estiamting the structure well leads to a better prediction of yield, however better prediction of yield does not necessarily mean a better prediction of the structure of the yield response function (yield response curve) because you can predicte yield levels at the observed rate for wrong reasons.

</span>

<br>

**7. Please insert a plot for true yield vs yield prediction to enable the reader to estimate the achieved prediction performance.**

Please see Figure xxx that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a sigle simulation round. RMSE is presented in the figure as well. As we have 1000 simulations, it is simply infeasible to present figures like this for all the simulation rounds. But, this figure provides a better sense of the value of RMSE and how good the fit is.

<span style="color:blue">

</span>

<br>

**8. Please show to which degree N affected yield and how the relation between yield estimation error and the effect of N on yield increase was. I would like to see whether the models were able to reproduce the effect of N on yield at all.**

Please see Figure xxx for illustrations of how yield responds to N site-specifically for xxx sites within a field. Please note that Figure xxx (Figure 5) presents exactly the moldes' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc). As you can see in the figure, RF underestimates the impact of N on yield severely, which leads to the underestimation of EONR. BRF suffers negative bias as well. On the contrary, CF does not suffer this bias. Of couese, the worst of all is CNN, which thinks that the impact of N on yield is almost nascent as you can see in Figure 5. On top of negative bias RF and BRF suffer, their estiamtion of the impact of N is also less accurate than CF. That is why CF performs better than RF and BRF in profit. Please note that CF does not even estimate (3). It estimates the change in yield when N is increased from one rate to another rate as discussed in the paper.

<span style="color:blue">

</span>

<br>

**9. Please extend the introduction by restating numbers for the state of the art of yield and EONR prediction performance from previous studies (as far as such numbers are available) to prevent that all of your readers have to consult the cited references.**

<span style="color:blue">  
Please see page xx, line xx for a new list of studies that attempt to estimate EONR. Please note that this study has no interest in studies that just predict yield without trying to show how they can use it for EONR estimation. Prediction of yield is almost always not the goal of farmers. We are listing studies that predict yields (or estimate yield resposne function to be more precise) and then predict EOIR based on them. Also, there is no study that test the performance of EONR using real data. This is because that is fundamentally impossible as we mentioned above. There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (Shun cite a paper that does this). But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field? That is because they do not (and will never) know the true EONR for each field. Moreover, the objective of such studies are fundamentally different from ours. Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR. We conside those studies not very relevant. Including those studies will simply bloat the introduction. 
</span>

<br>

**10. Please discuss your results with regard to the state of the art (again as specific as possible) and discuss whether your yield prediction performance and your simulation approach (e.g. epsilon effect size) may have affected the results for EONR prediction.**

<span style="color:blue">

</span>

<br>

### 2022-03-16 Writing/appendix.rmd

@@
 ```
+
+<br>
+
+## Appendix E: CNN performance per training epoch
+The below figure shows training and validation loss measured by mean square error (MSE) over the number of epochs in one of the thousand CNN simulation under aabbyytt scenario.
+
+```{r, fig.width=4, fig.height=4, fig.cap = "An example of CNN performance per training epoch (scenario: aabbyytt)"}
+knitr::include_graphics(here("GitControlled/Writing/loss_model4_simID1.png"))
+```

### 2022-03-16 Codes/PrepareResults.rmd

@@
   readRDS()
+```
+
+# Illustrative yield response curve
+
++ show to *which degree N affects yield* (yield response to N) 
++ show how the relation between yield estimation error and the effect of N on yield increase is ()
+
+## MB yield response to N
+
+```{r}
+#/*--------------------------------*/
+#' ## Preparation
+#/*--------------------------------*/
+# --- MB function --- #
+gen_yield_MB <- function(ymax, alpha, beta, N) {
+  yield <- ymax * (1 - exp(alpha + beta * N))
+  return(yield)
+}
+
+# --- extract sites that have wide range of true optimal N --- #
+get_rows_optN <- function(data, value, range) {
+  res <- data %>%
+    .[opt_N %between% c(quantile(opt_N, prob = value - range), quantile(opt_N, prob = value + range))
+    ] %>%
+    .[,group := value]
+}
+
+prep_coef_dt <- 
+  field_cell_sf %>%
+  data.table() %>%
+  .[sim==1,.(unique_cell_id, opt_N, alpha, beta, ymax, m_error)]
+
+set.seed(3957)
+
+coef_dt <- 
+  lapply(
+    c(0.1, 0.5, 0.9), 
+    function(x) get_rows_optN(data=prep_coef_dt, value = x, range = .0005)) %>%
+  bind_rows() %>%
+  # --- select one site from each group --- #
+  .[,.SD[sample(.N, size = 1)], by = group]
+
+seq_N <- 
+  seq(min(coef_dt[,opt_N]) -50, max(coef_dt[,opt_N])+100, by=1) %>%
+  round()
+
+res_y_dt <-  
+  coef_dt %>%
+  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
+  .[, N := seq_N, by = group] %>%
+  .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
+  .[, yield := det_yield*(1 + m_error)] %>%
+  .[, opt_N := round(opt_N)] %>%
+  melt(id.vars = c("group", "N", "opt_N"), measure.vars = c("det_yield", "yield")) %>%
+  .[, variable := case_when(
+    variable == "det_yield" ~ "Yield",
+    variable == "yield" ~ "Yield including errors"
+  )]
+
+#/*--------------------------------*/
+#' ## Visualization
+#/*--------------------------------*/
+sub_dt <- res_y_dt[variable=="Yield" & N == opt_N]
+
+# --- MB function to N --- #
+vis_res_y <- ggplot(res_y_dt[variable=="Yield"]) +
+  geom_line(aes(x=N, y=value, color=factor(group))) +
+  geom_point(data= sub_dt, aes(x=opt_N, y=value)) +
+  geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
+  labs(y = "Yield (kg/ha)") +
+  labs(x = "N (kg/ha)") +
+  theme_dist +
+  theme(legend.position = "none")
+
+# ggplot(res_y_dt) +
+#   geom_smooth(aes(x=N, y=value, color=factor(group))) +
+#   facet_wrap(~variable, ncol = 2) +
+#   labs(y = "Yield (kg/ha)") +
+#   labs(x = "N (kg/ha)") +
+#   theme_dist
+```
+
+## MB yield response and estimated yield response by BRF
++ true yield response curves for two sites within a field
++ points true yield evaluated at the N rate that was actually applied at the site
++ RF-estimated yield at all the potential experimental rates including the actual rate that was applied
+
+```{r}
+# /*===========================================*/
+#'=  Prepare illustrative yield response curve estimated by RF =
+# /*===========================================*/
+
+#/*--------------------------------*/
+#' ## Preparation
+#/*--------------------------------*/
+# --- ML functions --- #
+library(grf)
+source(here("GitControlled/Codes/0_2_functions_main_sim.R"))
+
+# === Data === #
+field_subplot_test_dt <- readRDS(here("Shared/Results/for_writing/field_subplot_test_dt.rds"))
+
+train_dt <- 
+  field_subplot_sf %>%
+  data.table()
+
+test_dt <- 
+  field_subplot_test_dt %>%
+  data.table()
+
+# /*===== Train ML =====*/
+temp_var_ls <- c("alpha", "beta", "ymax")
+
+set.seed(1356)
+
+# RF <- 
+#   RF_run(
+#     reg_data = train_dt,
+#     var_ls = temp_var_ls
+#   )
+
+BRF <- 
+  BRF_run(
+    reg_data = train_dt,
+    var_ls = temp_var_ls
+  )
+
+# === Yield prediction === #
+# --- All N experimental rates --- #
+N_rate <- test_dt[,aa_n] %>% unique() %>% sort()
+# For illustration purpose, we use site where either 2nd and 4th N rates are actually application
+tg_N_rate <- N_rate[c(2,4)]
+
+# --- for true yield response function --- #
+seq_N <- 
+  seq(min(N_rate) -30, max(N_rate)+30, by=1)
+# seq_N <- 
+#   seq(min(N_rate), max(N_rate), by=1)
+
+res_true <- 
+  test_dt %>%
+  .[aa_n %in% tg_N_rate] %>%
+  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
+  .[, N := seq_N, by = unique_subplot_id] %>%
+  .[,det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
+  .[,yield := det_yield*(1 + m_error)]
+
+# --- for predicted yield at five experimental N rates --- #
+res_pred <- 
+  test_dt %>%
+  .[aa_n %in% tg_N_rate] %>%
+  .[rep(1:nrow(.), each = length(N_rate)),] %>%
+  .[, N := N_rate, by = unique_subplot_id] %>%
+  # .[,pred_y_RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
+  .[,pred_y_BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])]
+
+# === For visualization === #
+set.seed(2032)
+low <- 
+  res_true[aa_n == tg_N_rate[1]] %>%
+  get_rows_optN(data=., value = 0.2, range = .005) %>%
+  .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1), unique_subplot_id] %>%
+  unique()
+
+high <- 
+  res_true[aa_n == tg_N_rate[2]] %>%
+  get_rows_optN(data=., value = 0.8, range = .005) %>%
+  .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1), unique_subplot_id] %>%
+  unique()
+
+vis_res_true <- res_true[unique_subplot_id %in% c(low, high)]
+vis_res_pred <- res_pred[unique_subplot_id %in% c(low, high)]
+
+vis_pred_y_res <- 
+  ggplot() +
+    # --- true yield response curve --- #
+    geom_line(
+      data=vis_res_true, aes(x=N, y=yield, group=factor(unique_subplot_id))
+    ) +
+    # --- Predicted yield points --- #
+    geom_point(
+      data=vis_res_pred, aes(x=N, y=pred_y_BRF, group=factor(unique_subplot_id)), color="red"
+    ) +
+    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield), color = 'blue') +
+    geom_segment(data = vis_res_true[aa_n==N], aes(x = aa_n, xend=aa_n, y = yield, yend=-Inf), linetype = "dashed") +
+    labs(y = "Yield (kg/ha)") +
+    labs(x = "N (kg/ha)") +
+    theme_dist +
+    theme(legend.position = "none")
 ```
@@
 
-# Figure (RMSE of EONR vs RMSE of yield for RF abd BRF)
+## Figure (RMSE of EONR vs RMSE of yield for RF abd BRF)
 
@@
   labs(x = " RMSE of Yield Prediction (kg/ha)") +
+  theme_dist
+```
+
+## True Yields vs Predicted Yields by models
+
+```{r}
+sample_simRes_test_y <- readRDS(here("Shared/Results/for_writing/sample_simRes_test_y.rds"))
+
+rmse <- sample_simRes_test_y %>%
+  .[, .(
+    rmse_y_det = rmse_general(pred_yield, det_yield),
+    rmse_y = rmse_general(pred_yield, yield)
+    ), by= .(Method, Model)]
+
+# === Function for RMSE Calculation === #
+rmse_general <-function(preds,actual){ 
+  sqrt(mean((actual - preds)^2)) %>%
+  round(.,1) %>%
+  format(, nsmall = 1)
+
+}
+
+rmse <- sample_simRes_test_y %>%
+  .[, .(
+    rmse_y_det = paste0("RMSE = " ,rmse_general(pred_yield, det_yield)),
+    rmse_y = paste0("RMSE = ", rmse_general(pred_yield, yield))
+    ), by= .(Method, Model)]
+
+vis_y_pred <- ggplot(sample_simRes_test_y) +
+  geom_point(aes(x=det_yield, y=pred_yield), size = 0.5) +
+  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
+  geom_text(data=rmse, aes(x=-Inf,y=+Inf,label=rmse_y_det),
+              hjust = -0.1,  vjust = 3, size=3.5, family = "Times New Roman") +
+  facet_grid(Model ~ Method) +
+  guides(
+    fill = guide_legend(keywidth = 1, keyheight = 1),
+    linetype = guide_legend(keywidth = 3, keyheight = 1),
+    colour = guide_legend(keywidth = 3, keyheight = 1)
+  ) +
+  labs(y = "Predicted Yield (kg/ha)") +
+  labs(x = "True Yield without error (kg/ha)") +
   theme_dist
@@
 opfit <- prune(tree, opcp)
-# fancyRpartPlot(opfit, sub="")
+# fancyRpartPlot(opfit, sub="", shadow.col = "")
 ```

### 2022-03-16 Writing/manuscript_cea.rmd

@@
 Each cell $(i,j)$'s "true" optimal N application rate, denoted $N^{opt}_{i,j}$, was calculated by solving a profit maximization problem by cell assuming that the prices of corn and N fertilizer were $\$0.138/kg$ and $\$1.323/kg$, respectively.
-These prices are used consistently for our simualtions.
+These prices are used consistently for our simulations.
 See Appendix C.1 for further details on how the paremeters were generated and sample maps of the parameters and true economically optimal N rates.
@@
 
-The accuracy of EONR estimation was judged based on RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level.
+The accuracy of EONR estimation was judged based on RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level:
+
+\begin{equation}
+\mbox{RMSE of EONR estimation} = \sqrt{\frac{1}{1536}\sum_{i=1}^{1536}(N^{opt}_{i} - \hat{N}^{opt}_{i})^2}. (\#eq:eqn7)
+\end{equation}
+
 Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N^{opt}_{i}$.
-For RF, BRF, and CNN, the accuracy of yield prediction was judged based on the RMSE ($kg/ha$) of the yield prediction against the true yields at the subplot level.
+For RF, BRF, and CNN, the accuracy of yield prediction was judged based on the RMSE ($kg/ha$) of the yield prediction against the true yields at the subplot level:
+
+\begin{equation}
+\mbox{RMSE of yield prediction} = \sqrt{\frac{1}{1536}\sum_{i=1}^{1536}(y_{i} - \hat{y}_{i})^2}. (\#eq:eqn8)
+\end{equation}
 

### 2022-03-16 Writing/CEA_3rd_round/replies_rev.rmd
additional figures in appendix

@@
     reference_docx: ../word_template_format.docx
+bibliography: ../ ML_VRA.bib
 ---
@@
 <span style="color:blue">  
-Please see Figure xx in Appendix xx that shows the convergence of CNN for a single simulation round.
+Please see Figure E.1 in Appendix E that shows the convergence of CNN for a single simulation round.
 We cannot show this kind of figure for all the simulation rounds.
@@
 "never" know true EONRs for real fields.
-We can only esimate them.
+We can only estimate them.
 This principle is at the core of statistical analysis.
-We never observe how data is generated (the underlying laws that govern how the world works whether it is physical, biological, or economic), but we can "estimate" (approximate) what thye look like.
-This means that when we try to evaluate how different models perofrm in predicting EONR using real data, we simply do not have a valid benchmark to compare against.
-Some may ask, then why don't we use models' yield prediction abililty because yield is observable.
+We never observe how data is generated (the underlying laws that govern how the world works whether it is physical, biological, or economic), but we can "estimate" (approximate) what they look like.
+This means that when we try to evaluate how different models perform in predicting EONR using real data, we simply do not have a valid benchmark to compare against.
+Some may ask, then why don't we use models' yield prediction ability because yield is observable.
 And this is precisely the dangerous practice that we show is wrong.
@@
 This is because we can never test the statistical property of a statistical method in principle using the real data.
-For example, please see (Shun, cite CF paper here.)
+For example, please see @Wager2018a and @oprescu2019orthogonal
 
@@
 <span style="color:blue">  
-
+The typo was corrected.
 </span>
@@
 <span style="color:blue">  
-Please see page xx, line yy for the precise definition of the RMSE for yield and EONR predictions.
+Please see page 19, line 323 and 328 for the precise definition of the RMSE for yield and EONR predictions.
 </span>
@@
 So, basically, the observed variation in achieved profits by estimated site-specific EONR is dominated simply by how profitable fields are on average.
-For this reason, we eliminated the figure and also dropped our cliam that yield prediction and EONR prediction are uncorrelated.
-Thank you so much for spotting this embarassing mistake from our side.
+For this reason, we eliminated the figure and also dropped our claim that yield prediction and EONR prediction are uncorrelated.
+Thank you so much for spotting this embarrassing mistake from our side.
 
-However, please note that our cliam that better yield prediction does "not necessarily" lead to higher profit remains intact.
+However, please note that our claim that better yield prediction does "not necessarily" lead to higher profit remains intact.
 This is evident in Table 1 and the analysis behind this table is valid.
-This happens because you can prefict yield well for a "wrong" reason, attributing parts of variations in yield to something other than its true driver.
+This happens because you can predict yield well for a "wrong" reason, attributing parts of variations in yield to something other than its true driver.
 
@@
 
-Estiamting the structure well leads to a better prediction of yield, however better prediction of yield does not necessarily mean a better prediction of the structure of the yield response function (yield response curve) because you can predicte yield levels at the observed rate for wrong reasons.
+Estimating the structure well leads to a better prediction of yield, however better prediction of yield does not necessarily mean a better prediction of the structure of the yield response function (yield response curve) because you can predict yield levels at the observed rate for wrong reasons.
 
@@
 
-Please see Figure xxx that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a sigle simulation round.
+Please see Figure H.1 that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a single simulation round.
 RMSE is presented in the figure as well.
@@
 
-Please see Figure xxx for illustrations of how yield responds to N site-specifically for xxx sites within a field.
-Please note that Figure xxx (Figure 5) presents exactly the moldes' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc).
+Please see Figure F.1 for illustrations of how yield responds to N site-specifically for three sites within a field.
+Please note that Figure xxx (Figure 5) presents exactly the models' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc).
 As you can see in the figure, RF underestimates the impact of N on yield severely, which leads to the underestimation of EONR.
@@
 On the contrary, CF does not suffer this bias.
-Of couese, the worst of all is CNN, which thinks that the impact of N on yield is almost nascent as you can see in Figure 5.
-On top of negative bias RF and BRF suffer, their estiamtion of the impact of N is also less accurate than CF.
+Of course, the worst of all is CNN, which thinks that the impact of N on yield is almost nascent as you can see in Figure 5.
+On top of negative bias RF and BRF suffer, their estimation of the impact of N is also less accurate than CF.
 That is why CF performs better than RF and BRF in profit.
@@
 Prediction of yield is almost always not the goal of farmers.
-We are listing studies that predict yields (or estimate yield resposne function to be more precise) and then predict EOIR based on them.
+We are listing studies that predict yields (or estimate yield response function to be more precise) and then predict EOIR based on them.
 Also, there is no study that test the performance of EONR using real data.

### 2022-03-16 Writing/appendix.rmd
additional figures in appendix

--- 2022-03-15 Writing/appendix.rmd
@@
 
+\newpage
+
 ## Appendix B: Understanding Yield Response Functions Better {-}
@@
 The simplified notation of this equation, where $c_i$ is dropped, is Eq. \@ref(eq:eqn3) in section 3.1.2.
+
+\newpage
 
@@
 
+\newpage
+
 ## Appendix D:  Training Accuracy of the ML methods {-}
@@
 
-\newpage
+<br>
 
@@
 ```
+
+\newpage
+
+## Appendix E: CNN performance per training epoch
+The below figure shows training and validation loss measured by mean square error (MSE) over the number of epochs in a single simulation round under aabbyytt scenario.
+
+```{r cnn-epoch, fig.width=5, fig.height=4, fig.cap = "Figure E.1: An example of CNN performance per training epoch (scenario: aabbyytt)"}
+knitr::include_graphics(here("GitControlled/Writing/loss_model4_simID1.png"))
+```
+
+\newpage
+
+## Appendix F: MB-yield response curves
+The below figure shows some examples of site-specific Mitscherlich-Baule yield function to illustrate how yield responds to N.
+
+```{r vis-MB-curve, fig.cap = "Figure F.1: Examples of Mitscherlich-Baule yield response curve"}
+vis_MB_curve
+```
+
+\newpage
+
+## Appendix G: The difference between predicting yields and predicting change in yields
+
+```{r, vis-MB-BRF-y, fig.cap = "Figure G.1: Predicted (scenario: aby)"}
+vis_MB_BRF_y
+```
+
+\newpage
+
+## Appendix H: True Yields vs Predicted Yields by models
+
+```{r vis-y-pred, fig.width=7, fig.height=7.5, fig.cap = "Figure H.1: True yields without error and predicted yields"}
+vis_y_pred
+```

### 2022-03-16 Codes/knit_manuscript.R

@@ -8,4 +8,4 @@ rmarkdown::render(here::here("GitControlled/Writing/CEA_2nd_round/replies_rev_1.
 rmarkdown::render(here::here("GitControlled/Writing/CEA_2nd_round/replies_rev_2.rmd"))
 
 #* reply to editor
-rmarkdown::render(here::here("GitControlled/Writing/CEA_3rd_round/replies_editor.rmd"))
+rmarkdown::render(here::here("GitControlled/Writing/CEA_3rd_round/replies_rev.rmd"))

### 2022-03-16 Codes/PrepareResults.rmd

@@
 ## MB yield response to N
++ for comment 8
++ The figure illustrates how yield responds to N
 
@@
 # --- MB function to N --- #
-vis_res_y <- ggplot(res_y_dt[variable=="Yield"]) +
-  geom_line(aes(x=N, y=value, color=factor(group))) +
+vis_MB_curve <- ggplot(res_y_dt[variable=="Yield"]) +
+  geom_line(aes(x=N, y=value, group=factor(group))) +
   geom_point(data= sub_dt, aes(x=opt_N, y=value)) +
@@
 ## MB yield response and estimated yield response by BRF
-+ true yield response curves for two sites within a field
-+ points true yield evaluated at the N rate that was actually applied at the site
-+ RF-estimated yield at all the potential experimental rates including the actual rate that was applied
++ As a response to comment 6
++ The figure shows the true yield response function and predicted yields at five N experiment by BRF
 
@@
 
-vis_pred_y_res <- 
+vis_MB_BRF_y <- 
   ggplot() +
@@
 ## True Yields vs Predicted Yields by models
++ for comment 7
++ a figure plots true yields (without error, epsilon) against predicted yields by model (without CF of course) for a single simulation round with RMSE printed for each model.
 

### 2022-03-17 Writing/appendix.rmd
some texts added for explaining why yield prediction does not mean good eonr prediction

@@
 ```{r ct-ex, fig.width=5, fig.height=5, fig.align="center", fig.cap = "Figure A.1: An illustrative example of a causal tree"}
-par(family="Times")
-fancyRpartPlot(opfit, sub="")
+par(family = "Times")
+fancyRpartPlot(opfit, sub = "")
 ```
@@
 For each of the subsamples, the treatment effect is identified as the difference in the mean yields of the treated and control groups within the subsample.
-The treatment effect for the low-$\textit{ecs}$ observations was $619$ kg/ha, and for the high-$\textit{ecs}$ observations was $982$ kg/ha.
-This means that for the impact of the increase in seed rate the treatment effect is heterogeneous over space, having a larger positive impact on yield in high-$\textit{ecs}$ areas.
+The treatment effect for the high-$\textit{ecs}$ observations was $619$ kg/ha, and for the low-$\textit{ecs}$ observations was $982$ kg/ha.
+This means that for the impact of the increase in seed rate the treatment effect is heterogeneous over space, having a larger positive impact on yield in low-$\textit{ecs}$ areas.
 Trees are further developed to have more groups of subsamples to allow for more flexible representations of the heterogeneous treatment effects.

### 2022-03-17 Writing/manuscript_cea.rmd
some texts added for explaining why yield prediction does not mean good eonr prediction

@@
 Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs.
-In their work, in some cases, CNN predicted yield well; but in all cases predicted EONR poorly.
 
-Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML method and modeling scenario, respectively.
+Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the RMSEs of the EONR estimations and $\hat{\pi}_{def}$ obtained from the 1000 simualtion rounds by ML method and modeling scenario, respectively.
 The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios.
@@
 
-For RF, BRF and CNN, Figure \@ref(fig:plot-y-optN) plots the RMSE values of EONR estimation against the RMSE values of yield prediction, and the red lines show the best-fit line describing the relationship between them.
-For all the models the regression line was almost flat, showing little if any correlation between the two measures.
-In other words, the quality of a model's yield predictions provided little if any information about the quality of its EONR predictions.
-
-```{r plot-y-optN, fig.width=7, fig.height=7.5, fig.cap = "The relationship in the performance between EONR estimation and yield prediction, by ML method and modeling scenario"}
-fig_y_optN
-```
-
-`r ftext('NOTE: The red line in the figures denotes the best-fit line to explain the relationship between the RMSEs of EONR prediction and yield prediction.', fp_text(font.size = 9, font.family = "Times New Roman"))`
-
-<br>
-
 Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations.
 Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN.
-Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact along with the poor performance of RF in predicting EONR show that strong predictive power of yield levels does not imply accurate prediction of EONR.
+Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact along with the poor performance of RF in predicting EONR presented in \@ref(tab:table-optN) show that strong predictive power of yield levels does not imply accurate prediction of EONR.
 Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well.
@@
 
+Table \@ref(tab:xxx) illustrates the distinction between yield prediction and yield response function prediction.
+
+In essence, good performance in predicinting yield "levels" at the observed points does not mean good performanc ein predicting yield response function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied.
+This happens because you can predict yield leves for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels.
+This is because prediction-oriented ML methods focus on predicting yield levels well at the "observed" points, but not the points that were not seen.
+This is by construction because they are trained to minimize the error in yield "level" prediction at the "observed" points.
+In contrast, CF focuses to recover the yield response functions well (or alternatively the causal impact of N on yield at different discrete rates of N).
+Our results how that this distinction between prediction-oriented ML methods and CF can result in economically meanigful difference, where CF outperforms.
+
 <br>
@@
 For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of 1000 iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations.
-That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF models best at yield prediction did not provide EONR estimates that led to high profits.
+That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF model performed the best at yield prediction among RF, BRF, and CNN, but did not provide EONR estimates that led to the highest profit.
 Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously.

### 2022-03-17 Codes/PrepareResults.R

@@ -1,4 +1,4 @@
-## ----set-up, cache = F-------------------------------------------------------------------------
+## ----set-up, cache = F-------------------
 library(knitr)
 library(here)
 
@@ -9,7 +9,7 @@ knitr::opts_chunk$set(
   cache = FALSE
 )
 
-## ----packages, cache = FALSE, include = FALSE--------------------------------------------------
+## ----packages, cache = FALSE, include = FALSE----
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -36,7 +36,7 @@ library(officedown)
 library(modelsummary)
 
 
-## ----------------------------------------------------------------------------------------------
+## ----------------------------------------
 theme_figure <- 
   theme(
     plot.title = element_text(hjust = 0.5),
@@ -65,7 +65,7 @@ set_flextable_defaults(
   )
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE-----------------------------------------
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE----
 # === plot-level field data set  === #
 field_plot_sf <-
   here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
@@ -82,7 +82,7 @@ field_cell_sf <-
   readRDS()
 
 
-## ----------------------------------------------------------------------------------------------
+## ----------------------------------------
 #/*--------------------------------*/
 #' ## Preparation
 #/*--------------------------------*/
@@ -155,7 +155,7 @@ vis_MB_curve <- ggplot(res_y_dt[variable=="Yield"]) +
 #   theme_dist
 
 
-## ----------------------------------------------------------------------------------------------
+## ----------------------------------------
 # /*===========================================*/
 #'=  Prepare illustrative yield response curve estimated by RF =
 # /*===========================================*/
@@ -261,7 +261,7 @@ vis_MB_BRF_y <-
     theme(legend.position = "none")
 
 
-## ----------------------------------------------------------------------------------------------
+## ----------------------------------------
 variogram_tb <-
   data.frame(
     Parameters = c("alpha_ij", "beta_ij", "ymax_ij", "varepsilon_ij"),
@@ -303,7 +303,7 @@ variogram_tb <-
   autofit()
 
 
-## ----field-map-visualization, dependson = "setup"----------------------------------------------
[…]

### 2022-03-17 Writing/manuscript_cea.rmd
bit of rewriting.

@@
 
+Distinction between yield prediction and yield response function estimation.
+
 Table \@ref(tab:xxx) illustrates the distinction between yield prediction and yield response function prediction.
 
-In essence, good performance in predicinting yield "levels" at the observed points does not mean good performanc ein predicting yield response function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied.
-This happens because you can predict yield leves for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels.
+In essence, good performance in predicinting yield "levels" at the "observed" points does not mean good performanc in predicting yield response function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied.
+This happens because you can predict yield "levels" for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels.
+Roughly speaking, the training process would twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits the obejective of predicting yield at the "observed" nitrogen rate for each site.
 This is because prediction-oriented ML methods focus on predicting yield levels well at the "observed" points, but not the points that were not seen.
@@
 In contrast, CF focuses to recover the yield response functions well (or alternatively the causal impact of N on yield at different discrete rates of N).
-Our results how that this distinction between prediction-oriented ML methods and CF can result in economically meanigful difference, where CF outperforms.
+Our results show that this distinction between prediction-oriented ML methods and CF is crucial and using the former may result in significant economic loss relative to CF.
 

### 2022-03-17 Codes/PrepareResults.rmd
code change and new figures F1 and G1

@@
 
-set.seed(3957)
+set.seed(34864)
 
@@
   lapply(
-    c(0.1, 0.5, 0.9), 
+    c(0.01, 0.25, 0.5, 0.75, 0.99), 
     function(x) get_rows_optN(data=prep_coef_dt, value = x, range = .0005)) %>%
@@
     variable == "yield" ~ "Yield including errors"
+  )] %>%
+  .[,group := case_when(
+    group == 0.01 ~ "site 1",
+    group == 0.25 ~ "site 2",
+    group == 0.5 ~ "site 3",
+    group == 0.75 ~ "site 4",
+    group == 0.99 ~ "site 5"
     )]
@@
 # --- MB function to N --- #
-vis_MB_curve <- ggplot(res_y_dt[variable=="Yield"]) +
-  geom_line(aes(x=N, y=value, group=factor(group))) +
-  geom_point(data= sub_dt, aes(x=opt_N, y=value)) +
-  geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
+vis_MB_curve <- 
+  ggplot(res_y_dt[variable=="Yield"]) +
+    geom_line(
+      aes(x=N, y=value, color=factor(group)), size=1
+    ) +
+    geom_point(data= sub_dt, aes(x=opt_N, y=value, alpha = "Yield at EONR"), color = "red", size = 2) +
+    # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
+    scale_alpha_manual(
+      name = NULL,
+      values = 1,
+      breaks = "Yield at EONR",
+      guide = guide_legend(override.aes = list(linetype = 0,
+        shape = 16,
+        color = "red")
+        ) 
+    ) +
     labs(y = "Yield (kg/ha)") +
@@
     theme_dist +
-  theme(legend.position = "none")
-
-# ggplot(res_y_dt) +
-#   geom_smooth(aes(x=N, y=value, color=factor(group))) +
-#   facet_wrap(~variable, ncol = 2) +
-#   labs(y = "Yield (kg/ha)") +
-#   labs(x = "N (kg/ha)") +
-#   theme_dist
+    theme(legend.title = element_blank()) +
+    guides(color=guide_legend(nrow=2, byrow=TRUE))
 ```
@@
 # /*===== Train ML =====*/
-temp_var_ls <- c("alpha", "beta", "ymax")
+temp_var_ls <- c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")
 
@@
 
-# RF <- 
-#   RF_run(
-#     reg_data = train_dt,
-#     var_ls = temp_var_ls
-#   )
+RF <- 
+  RF_run(
+    reg_data = train_dt,
+    var_ls = temp_var_ls
+  )
 
@@
 # For illustration purpose, we use site where either 2nd and 4th N rates are actually application
-tg_N_rate <- N_rate[c(2,4)]
+tg_N_rate <- N_rate[c(2,3,4)]
 
@@
   .[, N := N_rate, by = unique_subplot_id] %>%
-  # .[,pred_y_RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
-  .[,pred_y_BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])]
+  .[,RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
+  .[,BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
+  melt(id.vars = c("unique_subplot_id", "yield", "aa_n", "N"), measure.vars = c("RF", "BRF"))
+
+# find_examples_main  <- 
+#   res_pred %>%
+#   .[variable == "BRF" & aa_n==N,] %>%
+#   .[, y_diff_brf := abs(yield - value)] %>%
+#   .[y_diff_brf < 700, unique_subplot_id]
 
 # === For visualization === #
-set.seed(2032)
-low <- 
-  res_true[aa_n == tg_N_rate[1]] %>%
-  get_rows_optN(data=., value = 0.2, range = .005) %>%
-  .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1), unique_subplot_id] %>%
-  unique()
-
-high <- 
-  res_true[aa_n == tg_N_rate[2]] %>%
-  get_rows_optN(data=., value = 0.8, range = .005) %>%
-  .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1), unique_subplot_id] %>%
-  unique()
-
-vis_res_true <- res_true[unique_subplot_id %in% c(low, high)]
-vis_res_pred <- res_pred[unique_subplot_id %in% c(low, high)]
+# set.seed(1256)
+
+# low <- 
+#   res_true[aa_n == tg_N_rate[1]] %>%
+#   get_rows_optN(data=., value = 0.2, range = 0.1) %>%
+#   .[unique_subplot_id %in% find_examples_main] %>%
+#   # .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1),] %>%
+#   .[, unique_subplot_id] %>%
+#   unique()
+
+# # length(low)
+
+# medium <-
+#    res_true[aa_n == tg_N_rate[1]] %>%
+#   get_rows_optN(data=., value = 0.5, range = 0.1) %>%
+#   .[unique_subplot_id %in% find_examples_main] %>%
+#   # .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1),] %>%
+#   .[, unique_subplot_id] %>%
+#   unique()
+
+# high <- 
+#   res_true[aa_n == tg_N_rate[3]] %>%
+#   get_rows_optN(data=., value = 0.9, range = 0.1) %>%
+#   .[unique_subplot_id %in% find_examples_main] %>%
+#   .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1), unique_subplot_id] %>%
+#   unique()
+
+# vis_res_true <- res_true[unique_subplot_id %in% c(low, medium, high)]
+# vis_res_pred <- res_pred[unique_subplot_id %in% c(low, medium, high)]
+
+# low: *13_41*, 15_34
+# medium: *8_41*, 8_42, 27_10
+# high: 4_21
+
+vis_res_true <- 
+  res_true[unique_subplot_id %in% c("15_34", "8_41", "4_21")] %>%
+  .[,site := case_when(
+    unique_subplot_id == "15_34" ~ "site 1",
+    unique_subplot_id == "8_41" ~ "site 2",
+    unique_subplot_id == "4_21" ~ "site 3",
+    )]
+
+vis_res_pred <- 
+  res_pred[unique_subplot_id %in% c("15_34", "8_41", "4_21")] %>%
+  .[,site := case_when(
+    unique_subplot_id == "15_34" ~ "site 1",
+    unique_subplot_id == "8_41" ~ "site 2",
+    unique_subplot_id == "4_21" ~ "site 3",
+    )]
 
@@
     geom_line(
-      data=vis_res_true, aes(x=N, y=yield, group=factor(unique_subplot_id))
+      data=vis_res_true, aes(x=N, y=yield, color = site), size=1
     ) +
@@
     geom_point(
-      data=vis_res_pred, aes(x=N, y=pred_y_BRF, group=factor(unique_subplot_id)), color="red"
+      data=vis_res_pred, aes(x=N, y=value, color = site, alpha = "Predicts"), shape=2, size = 2, stroke = 1
     ) +
-    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield), color = 'blue') +
-    geom_segment(data = vis_res_true[aa_n==N], aes(x = aa_n, xend=aa_n, y = yield, yend=-Inf), linetype = "dashed") +
+    # --- Yield at applied N rate --- #
+    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 2) +
+    facet_wrap(~variable) +
+    scale_alpha_manual(
+      name = NULL,
+      values = c(1, 1),
+      breaks = c("Predicts", "True yield at actual N rate that was applied"),
+      guide = guide_legend(override.aes = list(linetype = c(0, 1),
+        shape = c(2, 16),
+        color = c("black", "blue")) 
+        ) 
+    ) +
     labs(y = "Yield (kg/ha)") +
@@
     theme_dist +
-    theme(legend.position = "none")
+    theme(legend.title = element_blank()) +
+    guides(color=guide_legend(nrow=2, byrow=TRUE))
 ```
@@
 
+# === Function for RMSE Calculation === #
+rmse_general <-function(preds,actual){ 
+  sqrt(mean((actual - preds)^2)) %>%
+  round(.,1) %>%
+  format(, nsmall = 1)
+}
+
 rmse <- sample_simRes_test_y %>%
@@
     ), by= .(Method, Model)]
-
-# === Function for RMSE Calculation === #
-rmse_general <-function(preds,actual){ 
-  sqrt(mean((actual - preds)^2)) %>%
-  round(.,1) %>%
-  format(, nsmall = 1)
-
-}
 

### 2022-03-17 Writing/CEA_3rd_round/replies_rev.rmd
some texts added for explaining why yield prediction does not mean good eonr prediction
code change and new figures F1 and G1

@@
 
+<span style="color:blue">  
 Please see Figure H.1 that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a single simulation round.
@@
 But, this figure provides a better sense of the value of RMSE and how good the fit is.
-
-<span style="color:blue">
-
 </span>
@@
 Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR.
-We conside those studies not very relevant.
+We consider those studies not very relevant.
 Including those studies will simply bloat the introduction.

### 2022-03-17 Codes/1_2_generate_coefficient.R

@@ -37,12 +37,12 @@ b <- 1000
 
 
 #/*--------------------------------------------------------*/
-#' ## (1) Generate raw coefficients (Medium m_error: psill = 0.002, roughly 1300 sd)
+#' ## (1) Generate raw coefficients (Medium m_error: psill = 0.015, roughly 1300 sd)
 #/*--------------------------------------------------------*/
 # --- start simulation --- #
 coef_data <- 
   gen_coefs_par(
-    B = 100, 
+    B = b, 
     geo_xy = xy,
     sp_range = Range,
     psill_merror = 0.015
@@ -77,7 +77,7 @@ set.seed(57864)
 # --- start simulation --- #
 coef_data_high <- 
   gen_coefs_par(
-    B = 100, 
+    B = b, 
     geo_xy = xy,
     sp_range = Range,
     psill_merror = 0.028

### 2022-03-17 Codes/2_1_generate_analysis_data.R

@@ -89,7 +89,7 @@ coef_data_low <-
 #' ## Generate Cell-level Data sets
 #/*--------------------------------*/
 raw_data <- lapply(
-	1:1000, function(x) {
+	1:100, function(x) {
 		prepare_raw_data(
 			i = x,
 			field = field,
@@ -104,6 +104,10 @@ raw_data <- lapply(
 reg_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
 test_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
 
+
+saveRDS(reg_raw_data, here("Shared/Data/for_Simulations/reg_raw_data_low_error.rds"))
+saveRDS(test_raw_data, here("Shared/Data/for_Simulations/test_raw_data_low_error.rds"))
+
 #/*--------------------------------*/
 #' ## Generate analysis dataset (subplot-level)
 #/*--------------------------------*/
@@ -113,7 +117,7 @@ test_raw_data <- readRDS(here("Shared/Data/for_Simulations/test_raw_data_low_err
 
 ##== Aggregate Cell-Level Field Data to Subplot-Level Field Data ==##
 sim_data <- lapply(
-	1:1000, function(x) {
+	1:100, function(x) {
 		# print(paste0("working on ", x, " th iteration."))
 		prepare_data_for_sim(
 			reg_raw_data = reg_raw_data[sim==x,],

### 2022-03-17 Codes/PrepareResults.R

@@ -1,4 +1,4 @@
-## ----set-up, cache = F-------------------
+## ----set-up, cache = F-------------------------------------------------------------------------
 library(knitr)
 library(here)
 
@@ -9,7 +9,7 @@ knitr::opts_chunk$set(
   cache = FALSE
 )
 
-## ----packages, cache = FALSE, include = FALSE----
+## ----packages, cache = FALSE, include = FALSE--------------------------------------------------
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -36,7 +36,7 @@ library(officedown)
 library(modelsummary)
 
 
-## ----------------------------------------
+## ----------------------------------------------------------------------------------------------
 theme_figure <- 
   theme(
     plot.title = element_text(hjust = 0.5),
@@ -65,7 +65,7 @@ set_flextable_defaults(
   )
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE----
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE-----------------------------------------
 # === plot-level field data set  === #
 field_plot_sf <-
   here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
@@ -82,7 +82,7 @@ field_cell_sf <-
   readRDS()
 
 
-## ----------------------------------------
+## ----------------------------------------------------------------------------------------------
 #/*--------------------------------*/
 #' ## Preparation
 #/*--------------------------------*/
@@ -105,11 +105,11 @@ prep_coef_dt <-
   data.table() %>%
   .[sim==1,.(unique_cell_id, opt_N, alpha, beta, ymax, m_error)]
 
-set.seed(3957)
+set.seed(34864)
 
 coef_dt <- 
   lapply(
-    c(0.1, 0.5, 0.9), 
+    c(0.01, 0.25, 0.5, 0.75, 0.99), 
     function(x) get_rows_optN(data=prep_coef_dt, value = x, range = .0005)) %>%
   bind_rows() %>%
   # --- select one site from each group --- #
@@ -130,32 +130,44 @@ res_y_dt <-
   .[, variable := case_when(
     variable == "det_yield" ~ "Yield",
     variable == "yield" ~ "Yield including errors"
-  )]  
+  )] %>%
[…]

### 2022-03-17 Codes/PrepareResults.rmd

@@
     geom_line(
-      aes(x=N, y=value, color=factor(group)), size=1
+      aes(x=N, y=value, group=factor(group))
     ) +
-    geom_point(data= sub_dt, aes(x=opt_N, y=value, alpha = "Yield at EONR"), color = "red", size = 2) +
+    geom_point(data= sub_dt, aes(x=opt_N, y=value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
     # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
@@
 
-# find_examples_main  <- 
-#   res_pred %>%
-#   .[variable == "BRF" & aa_n==N,] %>%
-#   .[, y_diff_brf := abs(yield - value)] %>%
-#   .[y_diff_brf < 700, unique_subplot_id]
+find_examples_main  <- 
+  res_pred %>%
+  .[variable == "BRF" & aa_n==N,] %>%
+  .[, y_diff_brf := abs(yield - value)] %>%
+  .[y_diff_brf < 500, unique_subplot_id]
+  # .[y_diff_brf < 500 & y_diff_brf < 1000, unique_subplot_id]
 
@@
 # low <- 
-#   res_true[aa_n == tg_N_rate[1]] %>%
-#   get_rows_optN(data=., value = 0.2, range = 0.1) %>%
+#   res_true[aa_n == tg_N_rate[3]] %>%
+#   get_rows_optN(data=., value = 0.9, range = 0.1) %>%
 #   .[unique_subplot_id %in% find_examples_main] %>%
@@
 
-# # length(low)
-
-# medium <-
-#    res_true[aa_n == tg_N_rate[1]] %>%
-#   get_rows_optN(data=., value = 0.5, range = 0.1) %>%
-#   .[unique_subplot_id %in% find_examples_main] %>%
-#   # .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1),] %>%
-#   .[, unique_subplot_id] %>%
-#   unique()
-
-# high <- 
-#   res_true[aa_n == tg_N_rate[3]] %>%
-#   get_rows_optN(data=., value = 0.9, range = 0.1) %>%
-#   .[unique_subplot_id %in% find_examples_main] %>%
-#   .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1), unique_subplot_id] %>%
-#   unique()
-
-# vis_res_true <- res_true[unique_subplot_id %in% c(low, medium, high)]
-# vis_res_pred <- res_pred[unique_subplot_id %in% c(low, medium, high)]
-
-# low: *13_41*, 15_34
-# medium: *8_41*, 8_42, 27_10
+# length(low)
+# x <- 16
+# i= x:(x+1)
+# vis_res_true <- res_true[unique_subplot_id %in% low[i]]
+# vis_res_pred <- res_pred[unique_subplot_id %in% low[i]]
+# ggplot() +
+#     geom_line(
+#       data=vis_res_true, aes(x=N, y=yield, color = unique_subplot_id)
+#     ) +
+#     geom_point(
+#       data=vis_res_pred, aes(x=N, y=value, color = unique_subplot_id, alpha = "Predicts"), shape=2, size = 1.5
+#     ) +
+#     geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
+#     facet_wrap(~variable) +
+#     scale_alpha_manual(
+#       name = NULL,
+#       values = c(1, 1),
+#       breaks = c("Predicts", "True yield at actual N rate that was applied"),
+#       guide = guide_legend(override.aes = list(linetype = c(0, 1),
+#         shape = c(2, 16),
+#         color = c("black", "blue")) 
+#         ) 
+#     ) +
+#     labs(y = "Yield (kg/ha)") +
+#     labs(x = "N (kg/ha)") +
+#     theme_dist +
+#     theme(legend.title = element_blank()) +
+#     guides(color=guide_legend(nrow=2, byrow=TRUE))
+
+# tg_N_rate <- N_rate[2]
+# low: 13_41, 15_34, 15_35, 11_40
+# medium: 8_41, *8_42*, *8_43*, 27_10
 # high: 4_21
 
+# tg_N_rate <- N_rate[3]
+# **2_18**, 10_42 ***6_47***
+
+# tg_N_rate <- N_rate[4]
+# 10_49
+
+# final
+# + *2_18* (more than 14500)
+# + *8_42* (11500) 
+# + *8_43* (11300)
+# + **6_47** (11100)
+
+# c("2_18", "8_42")
+# c("2_18", "6_47") **
+
+# vis_res_true <- res_true[unique_subplot_id %in% c("2_18", "6_47")]
+# vis_res_pred <- res_pred[unique_subplot_id %in% c("2_18", "6_47")]
+# ggplot() +
+#     geom_line(
+#       data=vis_res_true, aes(x=N, y=yield, color = unique_subplot_id)
+#     ) +
+#     geom_point(
+#       data=vis_res_pred, aes(x=N, y=value, color = unique_subplot_id, alpha = "Predicts"), shape=2, size = 1.5
+#     ) +
+#     geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
+#     facet_wrap(~variable) +
+#     scale_alpha_manual(
+#       name = NULL,
+#       values = c(1, 1),
+#       breaks = c("Predicts", "True yield at actual N rate that was applied"),
+#       guide = guide_legend(override.aes = list(linetype = c(0, 1),
+#         shape = c(2, 16),
+#         color = c("black", "blue")) 
+#         ) 
+#     ) +
+#     labs(y = "Yield (kg/ha)") +
+#     labs(x = "N (kg/ha)") +
+#     theme_dist +
+#     theme(legend.title = element_blank()) +
+#     guides(color=guide_legend(nrow=2, byrow=TRUE))
+
 vis_res_true <- 
-  res_true[unique_subplot_id %in% c("15_34", "8_41", "4_21")] %>%
+  res_true[unique_subplot_id %in% c("2_18", "6_47")] %>%
   .[,site := case_when(
-    unique_subplot_id == "15_34" ~ "site 1",
-    unique_subplot_id == "8_41" ~ "site 2",
-    unique_subplot_id == "4_21" ~ "site 3",
+    unique_subplot_id == "2_18" ~ "site 1",
+    unique_subplot_id == "6_47" ~ "site 2"
     )]
@@
 vis_res_pred <- 
-  res_pred[unique_subplot_id %in% c("15_34", "8_41", "4_21")] %>%
+  res_pred[unique_subplot_id %in% c("2_18", "6_47")] %>%
   .[,site := case_when(
-    unique_subplot_id == "15_34" ~ "site 1",
-    unique_subplot_id == "8_41" ~ "site 2",
-    unique_subplot_id == "4_21" ~ "site 3",
+    unique_subplot_id == "2_18" ~ "site 1",
+    unique_subplot_id == "6_47" ~ "site 2"
     )]
@@
     geom_line(
-      data=vis_res_true, aes(x=N, y=yield, color = site), size=1
+      data=vis_res_true, aes(x=N, y=yield, group = site)
     ) +
@@
     geom_point(
-      data=vis_res_pred, aes(x=N, y=value, color = site, alpha = "Predicts"), shape=2, size = 2, stroke = 1
+      data=vis_res_pred, aes(x=N, y=value, group = site, alpha = "Predicts"), shape=2, size = 1.5
     ) +
     # --- Yield at applied N rate --- #
-    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 2) +
+    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
     facet_wrap(~variable) +
@@
 
-## Figure (RMSE of EONR vs RMSE of yield for RF abd BRF)
+## Figure (RMSE of EONR vs RMSE of yield for RF and BRF)
 
 ```{r}
-fig_y_optN <-
+# fig_y_optN <-
+  # res_y_test %>%
+  # .[Method %in% c("RF", "BRF", "CNN")] %>%
+  # ggplot(aes(x = rmse_y, y = rmse_optN)) +
+  # geom_point(size = 0.5) +
+  # facet_grid(Model ~ Method) +
+  # geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
+  # stat_regline_equation(
+  #   label.x = 2050, label.y = 90,
+  #   aes(label = ..rr.label..),
+  #   size = 3
+  # ) +
+  # guides(
+  #   fill = guide_legend(keywidth = 1, keyheight = 1),
+  #   linetype = guide_legend(keywidth = 3, keyheight = 1),
+  #   colour = guide_legend(keywidth = 3, keyheight = 1)
+  # ) +
+  # ylim(NA, 95) +
+  # labs(y = " RMSE of EONR Estimation (kg/ha)") +
+  # labs(x = " RMSE of Yield Prediction (kg/ha)") +
+  # theme_dist
+```
+
+```{r}
+vis_RMSE_y_eonr <- 
   res_y_test %>%
-  .[Method %in% c("RF", "BRF", "CNN")] %>%
-  ggplot(aes(x = rmse_y, y = rmse_optN)) +
-  geom_point(size = 0.5) +
-  facet_grid(Model ~ Method) +
-  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
-  stat_regline_equation(
-    label.x = 2050, label.y = 90,
-    aes(label = ..rr.label..),
-    size = 3
+  .[sim %in% c(10, 20, 30) & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
+  ggplot() +
+  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
+  scale_shape_manual(values = c(21, 23, 25)) +
+  guides(
+    fill = guide_legend(override.aes=list(shape=21))
   ) +
-  guides(
-    fill = guide_legend(keywidth = 1, keyheight = 1),
-    linetype = guide_legend(keywidth = 3, keyheight = 1),
-    colour = guide_legend(keywidth = 3, keyheight = 1)
-  ) +
+  labs(fill="Simulation Round", shape="Method") +
+  # guides(fill = "none") +
+  # facet_wrap( ~ Model, ncol = 2) +
   ylim(NA, 95) +

### 2022-03-17 Writing/appendix.rmd

@@
 
-```{r, vis-MB-BRF-y, fig.cap = "Figure G.1: Predicted (scenario: aby)"}
+```{r, vis-MB-BRF-y, fig.width=7, fig.height=5, fig.cap = "Figure G.1: Predicted (scenario: aabbyytt)"}
 vis_MB_BRF_y
@@
 ```
+
+## Appendix I: The Relationship between Yield and EONR Prediction Performances (scenario: aabbyytt)
+
+```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "Figure I.1: The Relationship between Yield and EONR Prediction Performances"}
+vis_RMSE_y_eonr
+```

### 2022-03-18 Writing/manuscript_cea.rmd
minor edits

@@
 This happens because you can predict yield "levels" for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels.
-Roughly speaking, the training process would twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits the obejective of predicting yield at the "observed" nitrogen rate for each site.
+Roughly speaking, the training process would twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits the obejective of predicting yield at the "observed" nitrogen rate for each site well.
 This is because prediction-oriented ML methods focus on predicting yield levels well at the "observed" points, but not the points that were not seen.

### 2022-03-18 Codes/PrepareResults.R

@@ -1,4 +1,4 @@
-## ----set-up, cache = F-------------------------------------------------------------------------
+## ----set-up, cache = F--------
 library(knitr)
 library(here)
 
@@ -9,7 +9,7 @@ knitr::opts_chunk$set(
   cache = FALSE
 )
 
-## ----packages, cache = FALSE, include = FALSE--------------------------------------------------
+## ----packages, cache = FALSE, include = FALSE----
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -36,7 +36,7 @@ library(officedown)
 library(modelsummary)
 
 
-## ----------------------------------------------------------------------------------------------
+## -----------------------------
 theme_figure <- 
   theme(
     plot.title = element_text(hjust = 0.5),
@@ -65,7 +65,7 @@ set_flextable_defaults(
   )
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE-----------------------------------------
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE----
 # === plot-level field data set  === #
 field_plot_sf <-
   here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
@@ -82,7 +82,7 @@ field_cell_sf <-
   readRDS()
 
 
-## ----------------------------------------------------------------------------------------------
+## -----------------------------
 #/*--------------------------------*/
 #' ## Preparation
 #/*--------------------------------*/
@@ -164,10 +164,11 @@ vis_MB_curve <-
     labs(y = "Yield (kg/ha)") +
     labs(x = "N (kg/ha)") +
     theme_dist +
-    theme(legend.title = element_blank())
+    theme(legend.title = element_blank()) +
+    guides(color=guide_legend(nrow=2, byrow=TRUE))
 
 
-## ----------------------------------------------------------------------------------------------
+## -----------------------------
 # /*===========================================*/
 #'=  Prepare illustrative yield response curve estimated by RF =
 # /*===========================================*/
@@ -325,10 +326,11 @@ vis_MB_BRF_y <-
     labs(y = "Yield (kg/ha)") +
     labs(x = "N (kg/ha)") +
     theme_dist +
-    theme(legend.title = element_blank())
+    theme(legend.title = element_blank()) +
+    guides(color=guide_legend(nrow=2, byrow=TRUE))
 
 
-## ----------------------------------------------------------------------------------------------
+## -----------------------------
[…]

### 2022-03-18 Codes/PrepareResults.rmd
Edits by TM on many fronts.

@@
 theme_dist <-
-  theme_bw()+
+  theme_bw() +
   theme(
@@
 ```{r}
-#/*--------------------------------*/
+# /*--------------------------------*/
 #' ## Preparation
-#/*--------------------------------*/
+# /*--------------------------------*/
 # --- MB function --- #
@@
   res <- data %>%
-    .[opt_N %between% c(quantile(opt_N, prob = value - range), quantile(opt_N, prob = value + range))
-    ] %>%
-    .[,group := value]
+    .[opt_N %between% c(quantile(opt_N, prob = value - range), quantile(opt_N, prob = value + range))] %>%
+    .[, group := value]
 }
@@
   data.table() %>%
-  .[sim==1,.(unique_cell_id, opt_N, alpha, beta, ymax, m_error)]
+  .[sim == 1, .(unique_cell_id, opt_N, alpha, beta, ymax, m_error)]
 
@@
     c(0.01, 0.25, 0.5, 0.75, 0.99),
-    function(x) get_rows_optN(data=prep_coef_dt, value = x, range = .0005)) %>%
+    function(x) get_rows_optN(data = prep_coef_dt, value = x, range = .0005)
+  ) %>%
   bind_rows() %>%
   # --- select one site from each group --- #
-  .[,.SD[sample(.N, size = 1)], by = group]
+  .[, .SD[sample(.N, size = 1)], by = group]
 
 seq_N <-
-  seq(min(coef_dt[,opt_N]) -50, max(coef_dt[,opt_N])+100, by=1) %>%
+  seq(min(coef_dt[, opt_N]) - 50, max(coef_dt[, opt_N]) + 100, by = 1) %>%
   round()
@@
   .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
-  .[, yield := det_yield*(1 + m_error)] %>%
+  .[, yield := det_yield * (1 + m_error)] %>%
   .[, opt_N := round(opt_N)] %>%
@@
   )] %>%
-  .[,group := case_when(
+  .[, group := case_when(
     group == 0.01 ~ "site 1",
@@
 
-#/*--------------------------------*/
+# /*--------------------------------*/
 #' ## Visualization
-#/*--------------------------------*/
-sub_dt <- res_y_dt[variable=="Yield" & N == opt_N]
+# /*--------------------------------*/
+sub_dt <- res_y_dt[variable == "Yield" & N == opt_N]
 
@@
 vis_MB_curve <-
-  ggplot(res_y_dt[variable=="Yield"]) +
+  ggplot(res_y_dt[variable == "Yield"]) +
   geom_line(
-      aes(x=N, y=value, group=factor(group))
-    ) +
-    geom_point(data= sub_dt, aes(x=opt_N, y=value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
+    aes(x = N, y = value, group = factor(group))
+  ) +
+  geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
   # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
@@
     breaks = "Yield at EONR",
-      guide = guide_legend(override.aes = list(linetype = 0,
+    guide = guide_legend(override.aes = list(
+      linetype = 0,
       shape = 16,
-        color = "red")
-        ) 
+      color = "red"
+    ))
   ) +
@@
   theme(legend.title = element_blank()) +
-    guides(color=guide_legend(nrow=2, byrow=TRUE))
+  guides(color = guide_legend(nrow = 2, byrow = TRUE))
 ```
@@
 
-```{r}
+```{r prepare-data-vis, cache = TRUE}
 # /*===========================================*/
-#'=  Prepare illustrative yield response curve estimated by RF =
+#' =  Prepare illustrative yield response curve estimated by RF =
 # /*===========================================*/
 
-#/*--------------------------------*/
+# /*--------------------------------*/
 #' ## Preparation
-#/*--------------------------------*/
+# /*--------------------------------*/
 # --- ML functions --- #
@@
 # === Data === #
-field_subplot_test_dt <- readRDS(here("Shared/Results/for_writing/field_subplot_test_dt.rds"))
+field_subplot_test_dt <-
+  readRDS(here("Shared/Results/for_writing/field_subplot_test_dt.rds"))
 
@@
 # /*===== Train ML =====*/
-temp_var_ls <- c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")
+temp_var_ls <-
+  c(
+    "alpha1", "alpha2", "beta1", "beta2", "ymax1",
+    "ymax2", "theta_1", "theta_2"
+  )
 
@@
 # --- All N experimental rates --- #
-N_rate <- test_dt[,aa_n] %>% unique() %>% sort()
+N_rate <- test_dt[, aa_n] %>%
+  unique() %>%
+  sort()
 # For illustration purpose, we use site where either 2nd and 4th N rates are actually application
-tg_N_rate <- N_rate[c(2,3,4)]
+tg_N_rate <- N_rate[c(2, 3, 4)]
 
@@
 seq_N <-
-  seq(min(N_rate) -30, max(N_rate)+30, by=1)
+  seq(min(N_rate) - 30, max(N_rate) + 30, by = 1)
 # seq_N <-
@@
   .[, N := seq_N, by = unique_subplot_id] %>%
-  .[,det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
-  .[,yield := det_yield*(1 + m_error)]
+  .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
+  .[, yield := det_yield * (1 + m_error)]
 
@@
   .[aa_n %in% tg_N_rate] %>%
-  .[rep(1:nrow(.), each = length(N_rate)),] %>%
+  .[rep(1:nrow(.), each = length(N_rate)), ] %>%
   .[, N := N_rate, by = unique_subplot_id] %>%
-  .[,RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
-  .[,BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
+  .[, RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
+  .[, BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
   melt(id.vars = c("unique_subplot_id", "yield", "aa_n", "N"), measure.vars = c("RF", "BRF"))
@@
   res_pred %>%
-  .[variable == "BRF" & aa_n==N,] %>%
+  .[variable == "BRF" & aa_n == N, ] %>%
   .[, y_diff_brf := abs(yield - value)] %>%
@@
   res_true[unique_subplot_id %in% c("2_18", "6_47")] %>%
-  .[,site := case_when(
+  .[, site := case_when(
     unique_subplot_id == "2_18" ~ "site 1",
@@
   res_pred[unique_subplot_id %in% c("2_18", "6_47")] %>%
-  .[,site := case_when(
+  .[, site := case_when(
     unique_subplot_id == "2_18" ~ "site 1",
     unique_subplot_id == "6_47" ~ "site 2"
-    )]
-
+  )] %>%
+  .[, type := "Predicted"] %>%
+  .[, observed := ifelse(
+    aa_n == N,
+    "Observed Rate",
+    "Unobserved Rate"
+  )] %>%
+  setnames("variable", "model") %>%
+  .[, .(N, value, type, observed, model, site)]
+
+vis_true_points <-
+  vis_res_true[N %in% unique(vis_res_pred$N), ] %>%
+  .[, type := "True"] %>%
+  .[, observed := ifelse(
+    aa_n == N,
+    "Observed Rate",
+    "Unobserved Rate"
+  )] %>%
+  setnames("yield", "value") %>%
+  .[rep(1:.N, 2), ] %>%
+  .[, model := c("RF", "BRF") %>% rep(each = 10)] %>%
+  .[, .(N, value, type, observed, model, site)]
+
+vis_all_points <- rbind(vis_res_pred, vis_true_points)
+```
+
+```{r make-plot-MB-BRF-y}
 vis_MB_BRF_y <-
@@
   geom_line(
-      data=vis_res_true, aes(x=N, y=yield, group = site)
-    ) +
-    # --- Predicted yield points --- #
+    data = vis_res_true,
+    aes(x = N, y = yield, group = site)
+  ) +
   geom_point(
-      data=vis_res_pred, aes(x=N, y=value, group = site, alpha = "Predicts"), shape=2, size = 1.5
-    ) +
-    # --- Yield at applied N rate --- #
-    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
-    facet_wrap(~variable) +
-    scale_alpha_manual(
-      name = NULL,
-      values = c(1, 1),
-      breaks = c("Predicts", "True yield at actual N rate that was applied"),
-      guide = guide_legend(override.aes = list(linetype = c(0, 1),
-        shape = c(2, 16),
-        color = c("black", "blue")) 
-        ) 
-    ) +
+    data = vis_all_points,
+    aes(y = value, x = N, color = observed, shape = type),
+    size = 2
+  ) +
+  geom_line(
+    data = vis_all_points[type == "Predicted", ],
+    aes(y = value, x = N, color = site),
+    linetype = 2,
+    size = 0.5
+  ) +
+  geom_vline(
+    xintercept = vis_res_true$aa_n %>% unique(),
+    color = "red",
+    linetype = 2,
+    size = 0.3
+  ) +
+  annotate(
+    "text",
+    x = 180,  y = 9400,
+    label = "Observed Rate \n = 150 (kg/ha)",
+    family = "Times",
+    size = 3
+  ) +
+  scale_shape_manual(
+    values = c("Predicted" = 2, "True" = 16),
+    name = "Yield Type"
+  ) +
+  scale_color_manual(
+    values = c(
+      "Observed Rate" = "red",
+      "Unobserved Rate" = "blue"
+    ),
+    name = ""
+  ) +
+  facet_grid(. ~ model) +
   labs(y = "Yield (kg/ha)") +
   labs(x = "N (kg/ha)") +
-    theme_dist +
-    theme(legend.title = element_blank()) +
-    guides(color=guide_legend(nrow=2, byrow=TRUE))
+  guides(color = "none") +
+  theme_dist
 ```
@@
   footnote(
-    value = as_paragraph("NOTE: Only in ", as_i("ymax"), " are consistent units of measurement used for Mean, Nugget, and Sill ", "(", as_i("kg"),")."),
+    value = as_paragraph("NOTE: Only in ", as_i("ymax"), " are consistent units of measurement used for Mean, Nugget, and Sill ", "(", as_i("kg"), ")."),
     ref_symbols = NA
@@
 
-one_subplot <- ex_subplots[3,]
+one_subplot <- ex_subplots[3, ]
 
@@
   geom_sf(data = ex_subplots, fill = NA, size = 1) +
-  geom_sf(data = ex_subplots[2,], fill = "skyblue", size = 1) +
+  geom_sf(data = ex_subplots[2, ], fill = "skyblue", size = 1) +
   coord_sf(expand = FALSE) +
@@
   geom_sf(data = ex_cells, fill = NA) +
-  geom_sf(data = ex_cells[2,], fill = "skyblue", size = 1) +
+  geom_sf(data = ex_cells[2, ], fill = "skyblue", size = 1) +
   coord_sf(expand = FALSE) +
@@
   ggplot() +
-  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)+
+  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
   # /*----------------------------------*/
@@
   annotation_custom(grob_plot,
-    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1) +
+    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1
+  ) +
   # --- subplot level --- #
   annotation_custom(grob_subplots_inPlot,
-    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7) + 
+    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7
+  ) +
   # --- cell level --- #
   annotation_custom(grob_cells_inSubplot,
-    xmin = 0.8, xmax = 0.8+0.2, ymin = 0.382, ymax = 0.382 +0.2) +
-  #/*----------------------------------*/
+    xmin = 0.8, xmax = 0.8 + 0.2, ymin = 0.382, ymax = 0.382 + 0.2
+  ) +
+  # /*----------------------------------*/
   #' ## Add braces
-  #/*----------------------------------*/
+  # /*----------------------------------*/
   # --- between plot and subplot --- #
-  geom_brace(aes(c(0.43,0.43+0.1), c(0.372-0.004, 0.645+0.013)), color ="red", rotate = 270, inherit.data=F) +
+  geom_brace(aes(c(0.43, 0.43 + 0.1), c(0.372 - 0.004, 0.645 + 0.013)), color = "red", rotate = 270, inherit.data = F) +
   # --- between subplot and cell --- #
-  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.401-0.002, 0.529 +0.011)), color ="red", rotate = 270, inherit.data=F) +
-  #/*----------------------------------*/
+  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.401 - 0.002, 0.529 + 0.011)), color = "red", rotate = 270, inherit.data = F) +
+  # /*----------------------------------*/
   #' ## add annotations
-  #/*----------------------------------*/
+  # /*----------------------------------*/
   # --- annotation for plot --- #
   geom_segment(aes(x = 0.42, xend = 0.383, y = 0.60, yend = 0.52),
-    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
-  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.02, label = "plot", family="Times New Roman") +
+    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
+  ) +
+  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.02, label = "plot", family = "Times New Roman") +
   # --- annotation for subplot --- #
   geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
-    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
-  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot", , family="Times New Roman") +
+    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
+  ) +
+  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot", , family = "Times New Roman") +
   # --- annotation for cell --- #
   geom_segment(aes(x = 0.9, xend = 0.87, y = 0.365, yend = 0.41),
-    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
-  annotate("text", x = 0.9 + 0.02, y = 0.365 - 0.005, label = "cell", , family="Times New Roman") +
+    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
+  ) +
+  annotate("text", x = 0.9 + 0.02, y = 0.365 - 0.005, label = "cell", , family = "Times New Roman") +
   theme_void()
@@
   scale_fill_viridis_c() +
-  ggtitle(expression("(1) " ~alpha)) +
+  ggtitle(expression("(1) " ~ alpha)) +
   theme(legend.title = element_blank()) +
@@
   scale_fill_viridis_c() +
-  ggtitle(expression("(2) " ~beta)) +
+  ggtitle(expression("(2) " ~ beta)) +
   theme(legend.title = element_blank()) +
@@
   scale_fill_viridis_c() +
-  ggtitle(expression(paste("(4) " ~epsilon, " (kg/ha)"))) +
+  ggtitle(expression(paste("(4) " ~ epsilon, " (kg/ha)"))) +
   theme(legend.title = element_blank()) +
@@
   guides(
-    fill = guide_legend(override.aes=list(shape=21))
-  ) +
-  labs(fill="Simulation Round", shape="Method") +
+    fill = guide_legend(override.aes = list(shape = 21))
+  ) +
+  labs(fill = "Simulation Round", shape = "Method") +
   # guides(fill = "none") +
@@
 # === Function for RMSE Calculation === #
-rmse_general <-function(preds,actual){ 
+rmse_general <- function(preds, actual) {
   sqrt(mean((actual - preds)^2)) %>%
-  round(.,1) %>%
+    round(., 1) %>%
     format(, nsmall = 1)
@@
     rmse_y = rmse_general(pred_yield, yield)
-    ), by= .(Method, Model)]
+  ), by = .(Method, Model)]
 
@@
   .[, .(
-    rmse_y_det = paste0("RMSE = " ,rmse_general(pred_yield, det_yield)),
+    rmse_y_det = paste0("RMSE = ", rmse_general(pred_yield, det_yield)),
     rmse_y = paste0("RMSE = ", rmse_general(pred_yield, yield))
-    ), by= .(Method, Model)]
+  ), by = .(Method, Model)]
 
 vis_y_pred <- ggplot(sample_simRes_test_y) +
-  geom_point(aes(x=det_yield, y=pred_yield), size = 0.5) +
+  geom_point(aes(x = det_yield, y = pred_yield), size = 0.5) +
   geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
-  geom_text(data=rmse, aes(x=-Inf,y=+Inf,label=rmse_y_det),
-              hjust = -0.1,  vjust = 3, size=3.5, family = "Times New Roman") +
+  geom_text(
+    data = rmse, aes(x = -Inf, y = +Inf, label = rmse_y_det),
+    hjust = -0.1, vjust = 3, size = 3.5, family = "Times New Roman"
+  ) +
   facet_grid(Model ~ Method) +
@@
 ```{r, dependson = "source-results"}
-#/*----------------------------------*/
+# /*----------------------------------*/
 #' ## Distribution of RMSE of EONR estimates
-#/*----------------------------------*/
+# /*----------------------------------*/
 plot_dis_optN <-
   allML_summary_bySim %>%
-  .[type=="test",] %>%
+  .[type == "test", ] %>%
   # .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
@@
 
-#/*----------------------------------*/
+# /*----------------------------------*/
 #' ## Summary Table
-#/*----------------------------------*/
+# /*----------------------------------*/
 # === Preparation === #
@@
   table_optN_prep %>%
-  .[type=="train", !"type"] %>%
+  .[type == "train", !"type"] %>%
   mutate(
@@
   table_optN_prep %>%
-  .[type=="test", !"type"] %>%
+  .[type == "test", !"type"] %>%
   mutate(

### 2022-03-18 Writing/CEA_3rd_round/replies_rev.rmd
Edits by TM on many fronts.

@@
 But, any interested readers can replicate our work as the codes will be accessible publicly.
+Please also see the figure below.
+CNN severely underestimates the impact of N and estimated yield response to N is almost flat, but not exactly flat.
 </span>
@@
 
-We actually realized the results presented in Figure 6 is completely invalid.
-As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges.
-The biggest problem of the relationship we identified is that the maximum profit of the field is very different across simulations (the field in some simulations are simply more profitable than the fields in other simulations).
-So, basically, the observed variation in achieved profits by estimated site-specific EONR is dominated simply by how profitable fields are on average.
-For this reason, we eliminated the figure and also dropped our claim that yield prediction and EONR prediction are uncorrelated.
-Thank you so much for spotting this embarrassing mistake from our side.
+We actually realized the results presented in Figure 6 (in the previous round) is completely invalid.
+As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges: comparing across simulation rounds.
+Figure 8 plots RMSE of yield and EONR predictions by model and simulation round for several simulation rounds.
+Figure 6 in the previous round was basically mixing RMSE from all the simulation rounds and finding R^2 of the two relationshiop.
+That is why R^2 was extremely low.
+Therefore, we decided to remove the figure entirely.
+Also, we do not claim that yield and EONR predictions are not correlated at all as we realized that it is a false claim.
+Thank you so much for saving us from claiming the false statement.
 
 However, please note that our claim that better yield prediction does "not necessarily" lead to higher profit remains intact.
-This is evident in Table 1 and the analysis behind this table is valid.
-This happens because you can predict yield well for a "wrong" reason, attributing parts of variations in yield to something other than its true driver.
+According to your suggestions, we provide much more in-depth discussions about why that is the case under section 4.2.
+As you suggested, models that can recover the "structure" of the yield response function will perform well in predicting EONR.
+However, you can predict yield leves at the observed rates (rates that are actually applied in the experiment) without recovering the structure of the yield response function well.
+The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary obejective of predicting yield levels well at the "observed" nitrogen rate for each site well.
+Please see our more detailed discussions on this matter in section 4.2.
 
-approximating yield response function , predicting yield levels at the observed points
-
-Estimating the structure well leads to a better prediction of yield, however better prediction of yield does not necessarily mean a better prediction of the structure of the yield response function (yield response curve) because you can predict yield levels at the observed rate for wrong reasons.
+We understand your suggestion of running simulations under different magnitude of erorr comes from your doubt about why yield and EONR prediction is not correlated.
+But, ee conducted simulations with different degrees of error anyway.
+**The results are shown in Appendix**.
 
@@
 We are listing studies that predict yields (or estimate yield response function to be more precise) and then predict EOIR based on them.
-Also, there is no study that test the performance of EONR using real data.
+Also, there is no study that tests the performance of EONR using real data.
 This is because that is fundamentally impossible as we mentioned above.
@@
 <span style="color:blue">  
+We already discuss our results to the state of the art of the literature.
+The state of the art is sadly trying to predict yield as well as possible.
+We show that such practice can be misleading when your goal is to actually help farmers with making nitrogen application decisions (predicting EONR well).
+There is nothing wrong with our approach in yield prediction as evident in Figure 12.
+We are using ML methods that have been used in the literature of OFE for site-specific input management.
+Those studies were published very recently.
+We added our description about how the size of epsilon affects our results briefly at line xx, page yy.
+But, it is imporatnt to realize that all the models uses the same data.
+That is the models are competing against each other on the even ground.
+Changing the size of error has little effect on the comparative advantage of CF over other models much.
 

### 2022-03-18 Writing/appendix.rmd
Edits by TM on many fronts.

--- 2022-03-17 Writing/appendix.rmd
@@
 ## Appendix E: CNN performance per training epoch
-The below figure shows training and validation loss measured by mean square error (MSE) over the number of epochs in a single simulation round under aabbyytt scenario.
+The figure below shows training and validation loss measured by mean square error (MSE) over the number of epochs in a single simulation round under aabbyytt scenario for CNN as an illustration.
+For readers interested in knowing how CNN is trained for all the simulation rounds, please see the python program available at a Mendeley dataset [@Kakimoto2022codes] or a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.)
 
@@
 knitr::include_graphics(here("GitControlled/Writing/loss_model4_simID1.png"))
-```
-
-\newpage
-
-## Appendix F: MB-yield response curves
-The below figure shows some examples of site-specific Mitscherlich-Baule yield function to illustrate how yield responds to N.
-
-```{r vis-MB-curve, fig.cap = "Figure F.1: Examples of Mitscherlich-Baule yield response curve"}
-vis_MB_curve
-```
-
-\newpage
-
-## Appendix G: The difference between predicting yields and predicting change in yields
-
-```{r, vis-MB-BRF-y, fig.cap = "Figure G.1: Predicted (scenario: aby)"}
-vis_MB_BRF_y
 ```

### 2022-03-18 Writing/manuscript_cea.rmd
Edits by TM on many fronts.

--- 2022-03-17 Writing/manuscript_cea.rmd
@@
 $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen].
+Figure \@ref(fig:vis-MB-curve) presents example visualization of site-specific yield response fuctions for some sites.
+
+```{r vis-MB-curve, fig.cap = "Figure F.1: Examples of Mitscherlich-Baule yield response curve"}
+vis_MB_curve
+```
+
 The error term of the yield $\varepsilon$ represents the composite of all the unobserved factors that affect crop yield beyond $\alpha$, $\beta$, $ymax$ and $N$.
@@
 The Adam optimizer [@kingma2014adam] was used with a learning rate of $0.001 \%$ (default value).
-To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience.
+To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience (see Figure \@ref(cnn-epoch) for an illustration of the convergens of training with respect to the number of epochs).
 
@@
 
-Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations.
+Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations (see Figure \@ref(fig:vis-y-pred) in Appendix xx for example visualizations of predicted and true yields along with RMSE values by model).
 Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN.
@@
 
-Table \@ref(tab:xxx) illustrates the distinction between yield prediction and yield response function prediction.
+Figure \@ref(fig:vis-MB-BRF-y) illustrates the distinction between yield prediction at observed points and yield response function prediction, giving insights into why good yield prediction does not necessarily lead to good EONR prediction in general.
+The black curves are the true yield response functions for two sites in a single simulation round.
+Red symbols represent true (circle) or predicted (triangle) yields at the rate observed in the data: the rate that was actually applied in the experiment.
+That is, 150 kg/ha was applied to the two sites in the experiment.
+Blue symbols represent true (circle) or predicted (triangle) yield at some rates that were not observed (or applied) for the two sites in the experiment.
+Prediciton-oriented ML methods train models to minimize errors in yield level prediction at the "observed" rates (red points).
+Both RF- and BRF-trained models predict yield level at the observed rate well for the two sites (the vertical distance between the red circle and triangle).
+However, as you move away from the observed N rate, yield prediction errors tend to become larger (of course smaller yield prediction erros can be observed at unobserved rates some times).
+More important, connecting the predicted yield points does not trace the true yield response curves well for both RF and BRF.
+Specifically, in this example, the predicted impact of N on yield from RF and BRF are both smaller than the true impact of N.
 
-In essence, good performance in predicinting yield "levels" at the observed points does not mean good performanc ein predicting yield response function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied.
-This happens because you can predict yield leves for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels.
-This is because prediction-oriented ML methods focus on predicting yield levels well at the "observed" points, but not the points that were not seen.
-This is by construction because they are trained to minimize the error in yield "level" prediction at the "observed" points.
-In contrast, CF focuses to recover the yield response functions well (or alternatively the causal impact of N on yield at different discrete rates of N).
-Our results how that this distinction between prediction-oriented ML methods and CF can result in economically meanigful difference, where CF outperforms.
+```{r, vis-MB-BRF-y, fig.width=7, fig.height=5, fig.cap = "The difference between yield level prediction and yield response prediction (scenario: aabbyytt)"}
+vis_MB_BRF_y
+```
 
-<br>
+In essence, Figure \@ref(fig:vis-MB-BRF-y) illustrats that good performance in predicinting yield "levels" at the "observed" points does not mean good performanc in predicting yield "response" function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied.
+This happens because you can predict yield "levels" for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels.
+The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary obejective of predicting yield levels well at the "observed" nitrogen rate for each site well.
+This problem is also observable at Figure \@ref(fig:plot-tre), which shows both RF and BRF understimates the impact of N on yield: or in other words, their predicted site-speific yield response functions tend to be flatter than they truelly are.
+Of course, the CNN approach in our study is an extreme case where it completley fails to recognize the contribution of N on yield.
+But, remember that CNN does performs almost as good as RF and BRF in yield prediction as shown in Table \@ref(tab:table-y).
+
+Since you need to be able to estimate yield curves (yield response function) well at the site level to predict site-specific EONR (not yield level) well, models' ability to predict yield levels well at the observed rates does not guarantee their ability to predict site-specific EONR well.
+In contrast to RF, BRF, and CNN, CF focuses to recover the yield response functions well (or alternatively the causal impact of N on yield at different discrete rates of N).
+We showed that CF can predict the impact of N on yield when N is chaned from an unobserved rate to another unobserved rats as shown in Figure \@ref(fig:plot-tre), which then translated to better performance in predicting EONR and profit.
 
 All previous research has followed a two-step procedure to estimate site-specific EONRs.
-The first step was to select the model that predicts yield most accurately, and the following step used the selected model to predict EONR.
-Table \@ref(tab:count-table) shows that following this process led to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds.
+The first step was to select the model that predicts yield leves most accurately at the observed points, and the following step used the selected model to predict EONR.
+As discussed ealier, this practice can be economically harmful.
+Figure \@ref(fig:vis-RMSE-y-eonr) further illustrates the underlying problem.
+It plots RMSE of yield (x-axis) and EONR (y-axis) predictions by model and simulation round for several simulation rounds.
+As you can see clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation round xx and yy).
+
+```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "Figure I.1: The Relationship between Yield and EONR Prediction Performances ((scenario: aabbyytt)"}
+vis_RMSE_y_eonr
+```
+
+Table \@ref(tab:count-table) summarizes the relationship between yield and EONR prediction RMSE for all the simulation rounds.
+It shows clearly that following the process would lead to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds.
 For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of 1000 iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations.
@@
 Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF.
+It is importnat to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN.
 Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.
@@
 
+We thank Scott Swinton at Michigan State University for providing helpful comments on this publication.
 This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled "Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management," (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled "Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation" (Award Number NR213A7500013G021).

### 2022-03-18 Codes/PrepareResults.R

@@ -1,4 +1,4 @@
-## ----set-up, cache = F--------
+## ----set-up, cache = F--------------------------------------------------------
 library(knitr)
 library(here)
 
@@ -9,7 +9,7 @@ knitr::opts_chunk$set(
   cache = FALSE
 )
 
-## ----packages, cache = FALSE, include = FALSE----
+## ----packages, cache = FALSE, include = FALSE---------------------------------
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -36,19 +36,19 @@ library(officedown)
 library(modelsummary)
 
 
-## -----------------------------
-theme_figure <- 
+## -----------------------------------------------------------------------------
+theme_figure <-
   theme(
     plot.title = element_text(hjust = 0.5),
     axis.text.x = element_blank(),
     axis.text.y = element_blank(),
     axis.ticks = element_blank(),
     rect = element_blank(),
-    text  = element_text(family = "Times New Roman")
-    )
+    text = element_text(family = "Times New Roman")
+  )
 
-theme_dist <- 
-  theme_bw()+
+theme_dist <-
+  theme_bw() +
   theme(
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
@@ -57,15 +57,15 @@ theme_dist <-
     legend.title = element_text(size = 12, face = "bold"),
     legend.text = element_text(size = 12, face = "bold"),
     legend.position = "bottom",
-    text  = element_text(family = "Times New Roman")
-    )
+    text = element_text(family = "Times New Roman")
+  )
 
 set_flextable_defaults(
   font.family = "Times New Roman"
-  )
+)
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE----
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE------------------------
 # === plot-level field data set  === #
 field_plot_sf <-
   here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
@@ -82,10 +82,10 @@ field_cell_sf <-
   readRDS()
 
 
-## -----------------------------
-#/*--------------------------------*/
[…]

### 2022-03-18 Writing/CEA_3rd_round/replies_rev.rmd
change to replies

@@
 
-We appreciate your comments and
+We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version.
+One of your comments was paritculary important and we were able to correct our mistake before this paper is published.
+So, thank you so much.
+We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well.
+Below, you find your comments in black and our replies in blue.
 

### 2022-03-18 Writing/CEA_3rd_round/replies_rev.rmd
Additional simulation with different size of error, figure modification, add figure to the editor's comment

@@
     reference_docx: ../word_template_format.docx
-bibliography: ../ ML_VRA.bib
+bibliography: ../ML_VRA.bib
 ---
 
+```{r echo = F, include = FALSE, cache = F}
+library(knitr)
+library(here)
+here::i_am("GitControlled/Writing/CEA_3rd_round/replies_rev.rmd")
+# opts_knit$set(root.dir = here())
+
+options(htmltools.dir.version = FALSE)
+options(knitr.duplicate.label = "allow")
+
+opts_chunk$set(
+  fig.align = "center",
+  fig.retina = 5,
+  warning = F,
+  message = F,
+  cache = T,
+  echo = F
+)
+
+library(data.table)
+library(ggplot2)
+```
+
 We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version.
-One of your comments was paritculary important and we were able to correct our mistake before this paper is published.
+One of your comments was particularity important and we were able to correct our mistake before this paper is published.
 So, thank you so much.
@@
 CNN severely underestimates the impact of N and estimated yield response to N is almost flat, but not exactly flat.
+Please see the figure below showing some examples of yield response function estimated by CNN with "aabbyytt" modeling scenario.
+Each of the lines indicates yield response curve of a specific site.
+
+```{r, fig.width=7, fig.cap = "An illustrative example of yield response functions estimated by CNN (scenario: aabbyytt)"}
+cnn_simRes_temp <- readRDS(here("Shared/Results/ex_cnn_y_ResCurve.rmd"))
+
+ggplot(cnn_simRes_temp, aes(x=rate, y=pred_yield, colour=factor(unique_subplot_id))) +
+    geom_point(size = 0.7) +
+    geom_smooth(method=lm, se=FALSE, size=0.3) +
+    facet_wrap(~Model, ncol = 2) +
+    theme(
+        legend.title = element_blank(),
+        legend.position = "none"
+    ) +
+  xlab("N (kg/ha)") +
+  ylab("Predicted Yield (kg/ha)")
+```
+
 </span>

### 2022-03-18 Writing/appendix.rmd
Additional simulation with different size of error, figure modification, add figure to the editor's comment

@@
 
-## Appendix E: CNN performance per training epoch
+## Appendix E: CNN Performance per Training Epoch
 The figure below shows training and validation loss measured by mean square error (MSE) over the number of epochs in a single simulation round under aabbyytt scenario for CNN as an illustration.
-For readers interested in knowing how CNN is trained for all the simulation rounds, please see the python program available at a Mendeley dataset [@Kakimoto2022codes] or a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.)
+For readers interested in knowing how CNN is trained for all the simulation rounds, please see the python program available at a Mendeley dataset [@Kakimoto2022codes] or a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.
 
@@
 
-## Appendix H: True Yields vs Predicted Yields by models
+## Appendix H: True Yields vs Predicted Yields by Models
 
@@
 ```
+
+## Appendix I: Simulations with Different Size of Yield Disturbance Term.
+In this section, we present the results of EONR estimation and yield prediction with different size of yield disturbance term ($\varepsilon$).
+We created two additional yield datasets	that are only different in the size of $\varepsilon$ from the yield datasets we used in the study.
+This can be done by just changing the variogram parameter of $psill$ for $\varepsilon$.
+$0.002$ of $psill$ value was used to create low $\varepsilon$, and $0.028$ of $psill$ value was used to create high $\varepsilon$.
+Figure I.1 illustrates examples of generated $\varepsilon$.
+
+```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "Figure I.1: An example of experimental design of N and generated yield at the subplot resolution"}
+field_m_error_low | field_m_error_high
+```
+
+\newpage
+
+Using those yield datasets, we conducted one hundred simulations. The results of EONR estimation and yield prediction are shown in Table XX. (what about CNN reuslts??)
+
+```{r report-table-optN-low, tab.cap = "Table I.1: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low yield disturbance datasets"}
+report_table_optN_low
+```
+
+```{r report-table-y-low, tab.cap = "Table I.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on training datasets on low yield disturbance datasets"}
+report_table_y_low
+```
+
+\newpage
+
+```{r report-table-optN-low, tab.cap = "Table I.3: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low yield disturbance datasets"}
+report_table_optN_high
+```
+
+```{r report-table-y-low, tab.cap = "Table I.4: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on training datasets on low yield disturbance datasets"}
+report_table_y_high
+```

### 2022-03-18 Codes/3_1_1_SimDataAnalysis_main.R

@@ -1,5 +1,6 @@
 # ==========================================================================
 # Objective:
+# For main simulation results, 
 #' + Calculate profit-deficits and RMSE of EONR 
 #' + Calculate RMSE of yield predictions for RF, BRF and CNN
 #'      + For CNN results, estimate  EONR in this codes
@@ -49,7 +50,7 @@ subplots_infiled <- source_dt[,unique_subplot_id] %>% unique()
 
 
 # ==========================================================================
-# 1. Results of RF, BRF and CF
+# 1. Forest simulation regression results 
 # ==========================================================================
 
 # /*=================================================*/
@@ -112,7 +113,7 @@ forest_summary_bySim %>%
 
 
 # ==========================================================================
-# 2.  Results of CNN
+# 2.  CNN results
 # ==========================================================================
 
 # /*=================================================*/
@@ -169,7 +170,9 @@ cnn_simRes_all <-
 # Confirm that the predicted yield response functions are always linear
 cnn_simRes_temp <- 
     cnn_simRes_all %>%
-    .[type=="test" & Model == "aabbyytt" & sim==296 & unique_subplot_id %in% subplots_infiled[1:100],]
+    .[type=="test" & Model == "aabbyytt" & sim==296 & unique_subplot_id %in% subplots_infiled[1:50],]
+
+saveRDS(cnn_simRes_temp, here("Shared/Results/ex_cnn_y_ResCurve.rmd"))
 
 ggplot(cnn_simRes_temp, aes(x=rate, y=pred_yield, colour=factor(unique_subplot_id))) +
     geom_point(size = 0.7) +

### 2022-03-18 Writing/CEA_3rd_round/replies_rev.rmd
changed comment to the editor

--- 2022-03-18 Writing/CEA_3rd_round/replies_rev.rmd
@@
 We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version.
-One of your comments was paritculary important and we were able to correct our mistake before this paper is published.
-So, thank you so much.
+This round of revision turned out to be much more importnat than the previous one.
+One of your comments was paritculary important, and we were able to correct our mistake before this paper is published.
+Thank you so much for making this article better toghether with us.
 We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well.

### 2022-03-18 Codes/PrepareResults.rmd

@@
 
+```{r}
+# === Low error field map === #
+field_cell_low_sf <- 
+  here("Shared/Results/for_writing/sample_field_cell_low_sf.rds") %>%
+  readRDS()
+
+field_m_error_low <- 
+  ggplot(field_cell_low_sf) +
+    geom_sf(aes(fill = yield_error), size = 0) +
+    scale_fill_viridis_c() +
+    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
+    ggtitle("(1) Low error") +
+    theme_figure
+
+# === High error field map === #
+field_cell_high_sf <- 
+  here("Shared/Results/for_writing/sample_field_cell_high_sf.rds") %>%
+  readRDS()
+
+field_m_error_high <- 
+  ggplot(field_cell_high_sf) +
+    geom_sf(aes(fill = yield_error), size = 0) +
+    scale_fill_viridis_c() +
+    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
+    ggtitle("(1) High error") +
+    theme_figure
+```
+
 # Results
@@
 ```{r}
+# sim_no <- c(300, 600, 900)
+# sim_no <- c(10, 20, 30)
+
 vis_RMSE_y_eonr <-
   res_y_test %>%
-  .[sim %in% c(10, 20, 30) & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
+  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
   ggplot() +
@@
     scale_shape_manual(values = c(21, 23, 25)) +
-  guides(
-    fill = guide_legend(override.aes = list(shape = 21))
-  ) +
-  labs(fill = "Simulation Round", shape = "Method") +
-  # guides(fill = "none") +
-  # facet_wrap( ~ Model, ncol = 2) +
     ylim(NA, 95) +
@@
     labs(x = " RMSE of Yield Prediction (kg/ha)") +
-  theme_dist
+    theme_dist +
+    labs(fill="Simulation Round", shape="Method") +
+    guides(fill = guide_legend(override.aes=list(shape=21))) +
+    # guides(fill=guide_legend(nrow=2, byrow=TRUE)) +
+    # guides(shape=guide_legend(nrow=2, byrow=TRUE)) +
+    theme(legend.position="bottom", legend.box="vertical", legend.margin=margin()) +
+    labs(fill="Simulation Round", shape="Method") 
 ```
@@
 ```
+
+# Various Error Size (Appendix)
+
+## Low error
+
+```{r}
+Simres_low <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_low.rds"))
+
+# === Preparation === #
+table_optN_prep_low <-
+  Simres_low%>%
+  .[, .(
+    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
+    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
+  ), by = .(type, Method, Model)] %>%
+  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
+  .[, `:=`(
+    blank1 = NA, blank2 = NA, blank3 = NA
+  )] %>%
+  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CF_base, pi_loss_CF_base)]
+
+# === Summary Table (Testing Data sets) === #
+report_table_optN_low <-
+  table_optN_prep_low %>%
+  .[type == "test", !"type"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  # add_row(.after = 4) %>%
+  flextable(.) %>%
+  border_remove() %>%
+  delete_part(part = "header") %>%
+  add_header(
+    Model = "Model",
+    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
+    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
+    # blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
+    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
+    top = TRUE
+  ) %>%
+  merge_h(part = "header") %>%
+  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
+  add_header(
+    Model = "",
+    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
+    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
+    # blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
+    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
+    top = FALSE
+  ) %>%
+  compose(i = 2, j = c(4, 7, 10), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  # autofit() %>%
+  # width(j = c(2,5,8,11), width=0.3) %>%
+  # fix_border_issues()
+  footnote(
+    # i = 1, j = c(4, 7, 10, 13), part = "header",
+    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
+    ref_symbols = NA
+  ) %>%
+  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
+  autofit() %>%
+  width(j = c(3, 4, 6, 7, 9, 10), width = 0.6) %>%
+  width(j = c(2, 5, 8), width = 0.1)
+
+#/*--------------------------------*/
+#' ## Yield prediction
+#/*--------------------------------*/ 
+report_table_y_low <-
+  Simres_low %>%
+  .[type == "test" & Method %in% c("RF", "BRF")] %>%
+  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
+  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
+  dcast(Model ~ Method, value.var = "rmse_y") %>%
+  .[, CF_base := "-"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  flextable(.) %>%
+  set_header_labels(values = list(
+    Model = "Model",
+    RF = "RF",
+    BRF = "BRF",
+    CF_base = "CF-base"
+  )) %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  #- change the borders just for consistency with other figures -#
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  autofit()
+```
+
+## High error
+
+```{r}
+#/*--------------------------------*/
+#' ## EONR estimation
+#/*--------------------------------*/
+Simres_high <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_high.rds"))
+
+# === Preparation === #
+table_optN_prep_high <-
+  Simres_high%>%
+  .[, .(
+    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
+    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
+  ), by = .(type, Method, Model)] %>%
+  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
+  .[, `:=`(
+    blank1 = NA, blank2 = NA, blank3 = NA
+  )] %>%
+  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CF_base, pi_loss_CF_base)]
+
+# === Summary Table (Testing Data sets) === #
+report_table_optN_high <-
+  table_optN_prep_high %>%
+  .[type == "test", !"type"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  # add_row(.after = 4) %>%
+  flextable(.) %>%
+  border_remove() %>%
+  delete_part(part = "header") %>%
+  add_header(
+    Model = "Model",
+    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
+    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
+    # blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
+    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
+    top = TRUE
+  ) %>%
+  merge_h(part = "header") %>%
+  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
+  add_header(
+    Model = "",
+    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
+    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
+    # blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
+    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
+    top = FALSE
+  ) %>%
+  compose(i = 2, j = c(4, 7, 10), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  # autofit() %>%
+  # width(j = c(2,5,8,11), width=0.3) %>%
+  # fix_border_issues()
+  footnote(
+    # i = 1, j = c(4, 7, 10, 13), part = "header",
+    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
+    ref_symbols = NA
+  ) %>%
+  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
+  autofit() %>%
+  width(j = c(3, 4, 6, 7, 9, 10), width = 0.6) %>%
+  width(j = c(2, 5, 8), width = 0.1)
+
+#/*--------------------------------*/
+#' ## Yield prediction
+#/*--------------------------------*/ 
+report_table_y_high <-
+  Simres_high %>%
+  .[type == "test" & Method %in% c("RF", "BRF")] %>%
+  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
+  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
+  dcast(Model ~ Method, value.var = "rmse_y") %>%
+  .[, CF_base := "-"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  flextable(.) %>%
+  set_header_labels(values = list(
+    Model = "Model",
+    RF = "RF",
+    BRF = "BRF",
+    CF_base = "CF-base"
+  )) %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  #- change the borders just for consistency with other figures -#
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  autofit()
+```

### 2022-03-19 Codes/PrepareResults.rmd
solved sim_no error

--- 2022-03-18 Codes/PrepareResults.rmd
@@
 
+```{r}
+# === Low error field map === #
+field_cell_low_sf <- 
+  here("Shared/Results/for_writing/sample_field_cell_low_sf.rds") %>%
+  readRDS()
+
+field_m_error_low <- 
+  ggplot(field_cell_low_sf) +
+    geom_sf(aes(fill = yield_error), size = 0) +
+    scale_fill_viridis_c() +
+    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
+    ggtitle("(1) Low error") +
+    theme_figure
+
+# === High error field map === #
+field_cell_high_sf <- 
+  here("Shared/Results/for_writing/sample_field_cell_high_sf.rds") %>%
+  readRDS()
+
+field_m_error_high <- 
+  ggplot(field_cell_high_sf) +
+    geom_sf(aes(fill = yield_error), size = 0) +
+    scale_fill_viridis_c() +
+    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
+    ggtitle("(2) High error") +
+    theme_figure
+```
+
 # Results
@@
 ```{r}
+# sim_no <- c(300, 600, 900)
+sim_no <- c(10, 20, 30)
+
 vis_RMSE_y_eonr <-
   res_y_test %>%
-  .[sim %in% c(10, 20, 30) & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
+  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
   ggplot() +
@@
 ```
+
+# Various Error Size (Appendix)
+
+## EONR Estimation
+
+```{r}
+# === Load the data === #
+Simres_low <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_low.rds"))
+
+Simres_high <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_high.rds"))
+
+Simres_low_high<-
+ bind_rows(Simres_low, Simres_high, .id = "Degree") %>%
+ .[, Degree := ifelse(Degree==1, "Low", "High")] %>%
+ .[, Degree := factor(Degree, levels =c("Low", "High"))]
+
+# === Preparation === #
+table_optN_prep_low_high <-
+  Simres_low_high %>%
+  .[, .(
+    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
+    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
+  ), by = .(Degree, type, Method, Model)] %>%
+  dcast(Degree + type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
+  .[, `:=`(
+    blank1 = NA, blank2 = NA, blank3 = NA
+  )] %>%
+  .[, .(Degree, type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CF_base, pi_loss_CF_base)]
+
+# === Summary Table (Testing Data sets) === #
+table_optN_prep_low_high <- 
+  table_optN_prep_low_high %>%
+  .[type == "test", !"type"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  as_grouped_data(, groups = c("Degree")) %>%
+  flextable() %>%
+  border_remove() %>%
+  delete_part(part = "header") %>%
+  add_header(
+    Degree = "Error Size",
+    Model = "Model",
+    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
+    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
+    # blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
+    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
+    top = TRUE
+  ) %>%
+  merge_h(part = "header") %>%
+  hline_bottom(j = c(4:5, 7:8, 10:11), part = "header") %>%
+  add_header(
+    Degree = "",
+    Model = "",
+    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
+    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
+    # blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
+    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
+    top = FALSE
+  ) %>%
+  compose(i = 2, j = c(5, 8, 11), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  # autofit() %>%
+  # width(j = c(2,5,8,11), width=0.3) %>%
+  # fix_border_issues()
+  footnote(
+    # i = 1, j = c(4, 7, 10, 13), part = "header",
+    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
+    ref_symbols = NA
+  ) %>%
+  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
+  autofit() %>%
+  width(j = c(4, 5, 7, 8, 10, 11), width = 0.6) %>%
+  width(j = 1, width = 0.8) %>%
+  width(j = c(3, 6, 9), width = 0.1)
+
+#/*--------------------------------*/
+#' ## Yield prediction
+#/*--------------------------------*/ 
+report_table_y_low_high <-
+  Simres_low_high %>%
+  .[type == "test" & Method %in% c("RF", "BRF")] %>%
+  .[, .(rmse_y = mean(rmse_y)), by = .(Degree, Method, Model)] %>%
+  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
+  dcast(Degree + Model ~ Method, value.var = "rmse_y") %>%
+  .[, CF_base := "-"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  as_grouped_data(, groups = c("Degree")) %>%
+  flextable(.) %>%
+  set_header_labels(values = list(
+    Degree = "Error Size",
+    Model = "Model",
+    RF = "RF",
+    BRF = "BRF",
+    CF_base = "CF-base"
+  )) %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  #- change the borders just for consistency with other figures -#
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  autofit() %>%
+  width(j = 1, width = 0.8)
+```

### 2022-03-19 Codes/PrepareResults.rmd
minor fixes

--- 2022-03-18 Codes/PrepareResults.rmd
@@
   ) +
-  geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
+  # geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
   # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
@@
   theme_dist +
-  theme(legend.title = element_blank()) +
-  guides(color = guide_legend(nrow = 2, byrow = TRUE))
+  theme(legend.title = element_blank())
 ```
@@
   scale_fill_viridis_c() +
-    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
+  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
   ggtitle("(1) Low error") +
@@
   scale_fill_viridis_c() +
-    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
+  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
   ggtitle("(1) High error") +
@@
 # sim_no <- c(300, 600, 900)
-# sim_no <- c(10, 20, 30)
+sim_no <- c(10, 20, 30)
 
@@
   theme_dist +
-    labs(fill="Simulation Round", shape="Method") +
-    guides(fill = guide_legend(override.aes=list(shape=21))) +
+  labs(fill = "Simulation Round", shape = "Method") +
+  guides(fill = guide_legend(override.aes = list(shape = 21))) +
   # guides(fill=guide_legend(nrow=2, byrow=TRUE)) +
   # guides(shape=guide_legend(nrow=2, byrow=TRUE)) +
-    theme(legend.position="bottom", legend.box="vertical", legend.margin=margin()) +
-    labs(fill="Simulation Round", shape="Method") 
+  theme(legend.position = "bottom", legend.box = "vertical", legend.margin = margin()) +
+  labs(fill = "Simulation Round", shape = "Method")
 ```
@@
 table_optN_prep_low <-
-  Simres_low%>%
+  Simres_low %>%
   .[, .(
@@
 
-#/*--------------------------------*/
+# /*--------------------------------*/
 #' ## Yield prediction
-#/*--------------------------------*/ 
+# /*--------------------------------*/
 report_table_y_low <-
@@
 ```{r}
-#/*--------------------------------*/
+# /*--------------------------------*/
 #' ## EONR estimation
-#/*--------------------------------*/
+# /*--------------------------------*/
 Simres_high <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_high.rds"))
@@
 table_optN_prep_high <-
-  Simres_high%>%
+  Simres_high %>%
   .[, .(
@@
 
-#/*--------------------------------*/
+# /*--------------------------------*/
 #' ## Yield prediction
-#/*--------------------------------*/ 
+# /*--------------------------------*/
 report_table_y_high <-

### 2022-03-19 Writing/manuscript_cea.rmd
minor fixes

@@
 
-```{r vis-MB-curve, fig.cap = "Figure F.1: Examples of Mitscherlich-Baule yield response curve"}
+```{r vis-MB-curve, fig.cap = "Examples of site-specific Mitscherlich-Baule yield response curves"}
 vis_MB_curve
@@
 
-```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "Figure I.1: The Relationship between Yield and EONR Prediction Performances ((scenario: aabbyytt)"}
+```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "The Relationship between Yield and EONR Prediction Performances under the aabbyytt scenario"}
 vis_RMSE_y_eonr

### 2022-03-19 Codes/PrepareResults.R

@@ -1,4 +1,4 @@
-## ----set-up, cache = F-------------------------------------------------------------------------
+## ----set-up, cache = F--------
 library(knitr)
 library(here)
 
@@ -9,7 +9,7 @@ knitr::opts_chunk$set(
   cache = FALSE
 )
 
-## ----packages, cache = FALSE, include = FALSE--------------------------------------------------
+## ----packages, cache = FALSE, include = FALSE----
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -36,7 +36,7 @@ library(officedown)
 library(modelsummary)
 
 
-## ----------------------------------------------------------------------------------------------
+## -----------------------------
 theme_figure <-
   theme(
     plot.title = element_text(hjust = 0.5),
@@ -65,7 +65,7 @@ set_flextable_defaults(
 )
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE-----------------------------------------
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE----
 # === plot-level field data set  === #
 field_plot_sf <-
   here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
@@ -82,7 +82,7 @@ field_cell_sf <-
   readRDS()
 
 
-## ----------------------------------------------------------------------------------------------
+## -----------------------------
 # /*--------------------------------*/
 #' ## Preparation
 # /*--------------------------------*/
@@ -169,7 +169,7 @@ vis_MB_curve <-
   guides(color = guide_legend(nrow = 2, byrow = TRUE))
 
 
-## ----prepare-data-vis, cache = TRUE------------------------------------------------------------
+## ----prepare-data-vis, cache = TRUE----
 # /*===========================================*/
 #' =  Prepare illustrative yield response curve estimated by RF =
 # /*===========================================*/
@@ -381,7 +381,7 @@ vis_true_points <-
 vis_all_points <- rbind(vis_res_pred, vis_true_points)
 
 
-## ----make-plot-MB-BRF-y------------------------------------------------------------------------
+## ----make-plot-MB-BRF-y-------
 vis_MB_BRF_y <-
   ggplot() +
   # --- true yield response curve --- #
@@ -431,7 +431,7 @@ vis_MB_BRF_y <-
   theme_dist
 
 
-## ----------------------------------------------------------------------------------------------
+## -----------------------------
 variogram_tb <-
   data.frame(
[…]

### 2022-03-19 Codes/PrepareResults.rmd

--- 2022-03-19 Codes/PrepareResults.rmd
@@
 
-#/*--------------------------------*/
+# /*--------------------------------*/
 #' ## Yield prediction

### 2022-03-19 Writing/appendix.rmd

@@
 
-```{r report-table-optN-low, tab.cap = "Table I.1: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low yield disturbance datasets"}
-report_table_optN_low
-```
-
-```{r report-table-y-low, tab.cap = "Table I.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on training datasets on low yield disturbance datasets"}
-report_table_y_low
+```{r report-table-optN-low, tab.cap = "Table I.1: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
+table_optN_prep_low_high
 ```
@@
 
-```{r report-table-optN-low, tab.cap = "Table I.3: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low yield disturbance datasets"}
-report_table_optN_high
+```{r report-table-optN-low, tab.cap = "Table I.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
+report_table_y_low_high
 ```
-
-```{r report-table-y-low, tab.cap = "Table I.4: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on training datasets on low yield disturbance datasets"}
-report_table_y_high
-```

### 2022-03-19 Codes/PrepareResults.rmd
minor text changes

@@
   labs(x = "N (kg/ha)") +
-  theme_dist +
-  theme(legend.title = element_blank())
+  theme_dist
 ```

### 2022-03-19 Writing/manuscript_cea.rmd
minor text changes

@@
 It plots the estimated treatment effects against true treatment effects by treatment type and ML method under the "aabbyytt" scenario in one of the one thousand simulations rounds.
-Except in the cases of CNN, the figure shows points clustered around the red 1-to-1 line, meaning that the estimated treatment effects did not exhibit significant bias.
-However, the models differed substantially in the accuracy of their treatment effect estimations.
-Points are clustered more tightly about the 1-to-1 line for CF-base than RF, BRF and CNN.
-That is, CF-base estimated treatment effects much more efficiently than did RF and BRF, which focus on yield prediction rather than treatment effect estimation.
+First of all, CNN suffers from severe underestimation of the impact of N in this particular simulation round.
+RF also suffers from underestimation of the impact of N.
+Underestimation of the impact of N generally leads to the underestimation of EONR, which in turn results in profit loss.
+Underestimation bias from BF is not as severe as RF or CNN.
+However, unlike RF, BRF, and CNN, points for CF-base clustered around the red 1-to-1 line, meaning that the estimated treatment effects from CF did not exhibit significant bias in treatment effect estimation.
+Moreover, points are clustered more tightly about the 1-to-1 line for CF-base than BRF.
+That is, CF-base estimated treatment effects more efficiently than did BRF.
 
@@
 `r ftext('NOTE: The red line in the figures denotes the 1-to-1 line to show the ideal relationship between true and estimated treatment effects.', fp_text(font.size = 9, font.family = "Times New Roman"))`
+
+Finally, the simulation results at a smaller and larger size of the error term are presented in Appendix xx as a sensitivity check for interested readers.
+Basically, qualitative results remain the same.
 

### 2022-03-19 Writing/CEA_3rd_round/replies_rev.rmd
modifies comments to the editor

--- 2022-03-18 Writing/CEA_3rd_round/replies_rev.rmd
@@
 ---
+
+We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version.
+This round of revision turned out to be much more importnat than the previous one.
+One of your comments was paritculary important, and we were able to correct our mistake before this paper is published.
+Thank you so much for making this article better toghether with us.
+We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well.
+Below, you find your comments in black and our replies in blue.
 
@@
 
-ggplot(cnn_simRes_temp, aes(x=rate, y=pred_yield, colour=factor(unique_subplot_id))) +
+ggplot(cnn_simRes_temp, aes(x = rate, y = pred_yield, colour = factor(unique_subplot_id))) +
   geom_point(size = 0.7) +
-    geom_smooth(method=lm, se=FALSE, size=0.3) +
+  geom_smooth(method = lm, se = FALSE, size = 0.3) +
   facet_wrap(~Model, ncol = 2) +
@@
 <span style="color:blue">  
-We do not say EOIR cannot be estimated by studies mentioned in 28ff. Indeed, any methods can "estimate" EOIR. However, no method can estimate the "true" EONR and we will 
-"never" know true EONRs for real fields.
+We are not saying EOIR cannot be estimated by studies mentioned in 28ff.
+Indeed, any methods can "estimate" EOIR.
+However, no method can estimate the "true" EONR and we will "never" know true EONRs for real fields.
 We can only estimate them.
@@
 Some may ask, then why don't we use models' yield prediction ability because yield is observable.
-And this is precisely the dangerous practice that we show is wrong.
+And this is precisely the dangerous practice that we show can be harmful.
 
@@
 <span style="color:blue">  
-
+Fiels studies were used to obtain the plausible range of optimal EONR and the size of error. 
 </span>
@@
 Therefore, we decided to remove the figure entirely.
-Also, we do not claim that yield and EONR predictions are not correlated at all as we realized that it is a false claim.
+Also, we no longer claim that yield and EONR predictions are not correlated at all as we realized that it is false.
 Thank you so much for saving us from claiming the false statement.
@@
 As you suggested, models that can recover the "structure" of the yield response function will perform well in predicting EONR.
-However, you can predict yield leves at the observed rates (rates that are actually applied in the experiment) without recovering the structure of the yield response function well.
+However, you can predict yield levels at the observed rates (rates that are actually applied in the experiment) without recovering the structure of the yield response function well (predicting yield levels well for wrong reasons).
 The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary obejective of predicting yield levels well at the "observed" nitrogen rate for each site well.
@@
 We understand your suggestion of running simulations under different magnitude of erorr comes from your doubt about why yield and EONR prediction is not correlated.
-But, ee conducted simulations with different degrees of error anyway.
+But, we conducted simulations with different degrees of error anyway.
 **The results are shown in Appendix**.
@@
 
-Please see Figure F.1 for illustrations of how yield responds to N site-specifically for three sites within a field.
+Please see Figure F.1 for illustrations of how yield responds to N site-specifically for several sites within a field.
 Please note that Figure xxx (Figure 5) presents exactly the models' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc).
@@
 Please see page xx, line xx for a new list of studies that attempt to estimate EONR.
-Please note that this study has no interest in studies that just predict yield without trying to show how they can use it for EONR estimation.
-Prediction of yield is almost always not the goal of farmers.
-We are listing studies that predict yields (or estimate yield response function to be more precise) and then predict EOIR based on them.
-Also, there is no study that tests the performance of EONR using real data.
+Please note that the previous stufies relevant to out study are those that apply ML methods to OFE data with the ultimate intention of estimating site-specific EONR.
+There is no study that tests the performance of EONR using real data.
 This is because that is fundamentally impossible as we mentioned above.
@@
 We consider those studies not very relevant.
-Including those studies will simply bloat the introduction.
+We believe including those studies will simply bloat the introduction.
 </span>
@@
 We already discuss our results to the state of the art of the literature.
-The state of the art is sadly trying to predict yield as well as possible.
-We show that such practice can be misleading when your goal is to actually help farmers with making nitrogen application decisions (predicting EONR well).
+The state of the art is sadly trying to predict yields site-specifically as well as possible.
+We show that such practice can be misleading and economically harmful when your ultimate goal is to actually help farmers make nitrogen application decisions (predicting EONR well).
 There is nothing wrong with our approach in yield prediction as evident in Figure 12.
@@
 We added our description about how the size of epsilon affects our results briefly at line xx, page yy.
-But, it is imporatnt to realize that all the models uses the same data.
-That is the models are competing against each other on the even ground.
-Changing the size of error has little effect on the comparative advantage of CF over other models much.
+But, it is imporatnt to realize that all the models uses the same data in our study.
+That is, the models are competing against each other on the level ground.
+Changing the size of error has little effects on the comparative advantage of CF over other models much.
 

### 2022-03-21 Writing/CEA_3rd_round/replies_rev.rmd
update manuscript, appendix and comments to the editor

@@
 ---
-
-We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version.
-This round of revision turned out to be much more importnat than the previous one.
-One of your comments was paritculary important, and we were able to correct our mistake before this paper is published.
-Thank you so much for making this article better toghether with us.
-We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well.
-Below, you find your comments in black and our replies in blue.
 
@@
 We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version.
+This round of revision turned out to be much more important than the previous one.
+One of your comments was particularity important, and we were able to correct our mistake before this paper is published.
+Thank you so much for making this article better together with us.
+We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well.
+Below, you find your comments in black and our replies in blue.
+
+<!-- We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version.
 One of your comments was particularity important and we were able to correct our mistake before this paper is published.
@@
 Below, you find your comments in black and our replies in blue.
+-->
 
@@
 <span style="color:blue">  
-Please see Figure E.1 in Appendix E that shows the convergence of CNN for a single simulation round.
+Please see Figure D.1 in Appendix D that shows the convergence of CNN for a single simulation round.
 We cannot show this kind of figure for all the simulation rounds.
@@
 CNN severely underestimates the impact of N and estimated yield response to N is almost flat, but not exactly flat.
-Please see the figure below showing some examples of yield response function estimated by CNN with "aabbyytt" modeling scenario.
-Each of the lines indicates yield response curve of a specific site.
+<!-- Please see the figure below showing some examples of yield response function estimated by CNN under "aabbyytt" modeling scenario.
+Each of the lines indicates yield response curve for different sites.
+ -->
 
@@
 <span style="color:blue">  
-Fiels studies were used to obtain the plausible range of optimal EONR and the size of error. 
+Fields studies were used to obtain the plausible range of optimal EONR and the size of error. 
 </span>
@@
 <span style="color:blue">  
-Please see page 19, line 323 and 328 for the precise definition of the RMSE for yield and EONR predictions.
+Please see page 19, Eq. (7) and Eq. (8) for the precise definitions of the RMSE for yield and EONR predictions.
 </span>
@@
 Figure 8 plots RMSE of yield and EONR predictions by model and simulation round for several simulation rounds.
-Figure 6 in the previous round was basically mixing RMSE from all the simulation rounds and finding R^2 of the two relationshiop.
-That is why R^2 was extremely low.
+Figure 6 in the previous round was basically mixing RMSE from all the simulation rounds and finding $R^2$ of the two relationship.
+That is why $R^2$ was extremely low.
 Therefore, we decided to remove the figure entirely.
@@
 However, you can predict yield levels at the observed rates (rates that are actually applied in the experiment) without recovering the structure of the yield response function well (predicting yield levels well for wrong reasons).
-The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary obejective of predicting yield levels well at the "observed" nitrogen rate for each site well.
+The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary objective of predicting yield levels well at the "observed" nitrogen rate for each site well.
 Please see our more detailed discussions on this matter in section 4.2.
 
-We understand your suggestion of running simulations under different magnitude of erorr comes from your doubt about why yield and EONR prediction is not correlated.
+We understand your suggestion of running simulations under different magnitude of error comes from your doubt about why yield and EONR prediction is not correlated.
 But, we conducted simulations with different degrees of error anyway.
-**The results are shown in Appendix**.
+**The results are shown in Appendix G**.
 
@@
 <span style="color:blue">  
-Please see Figure H.1 that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a single simulation round.
+Please see Figure E.1 that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a single simulation round.
 RMSE is presented in the figure as well.
@@
 
-Please see Figure F.1 for illustrations of how yield responds to N site-specifically for several sites within a field.
-Please note that Figure xxx (Figure 5) presents exactly the models' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc).
+Please see Figure 2 for illustrations of how yield responds to N site-specifically for several sites within a field.
+Please note that Figure 6 presents exactly the models' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc).
 As you can see in the figure, RF underestimates the impact of N on yield severely, which leads to the underestimation of EONR.
@@
 That is why CF performs better than RF and BRF in profit.
-Please note that CF does not even estimate (3).
+Please note that CF does not even estimate Eq.
+(3).
 It estimates the change in yield when N is increased from one rate to another rate as discussed in the paper.
@@
 
-<span style="color:blue">  
 Please see page xx, line xx for a new list of studies that attempt to estimate EONR.
-Please note that the previous stufies relevant to out study are those that apply ML methods to OFE data with the ultimate intention of estimating site-specific EONR.
+Please note that the previous studies relevant to our study are those that apply ML methods to OFE data with the ultimate intention of estimating site-specific EONR.
 There is no study that tests the performance of EONR using real data.
 This is because that is fundamentally impossible as we mentioned above.
-There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (Shun cite a paper that does this).
+There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (e.g., @Qin2018; @Ransom2019 @Wang2021; @wen2021machine).
 But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field?
@@
 We believe including those studies will simply bloat the introduction.
-</span>
 
@@
 We show that such practice can be misleading and economically harmful when your ultimate goal is to actually help farmers make nitrogen application decisions (predicting EONR well).
-There is nothing wrong with our approach in yield prediction as evident in Figure 12.
+There is nothing wrong with our approach in yield prediction as evident in Figure E.1<!-- Figure 12 -->.
 We are using ML methods that have been used in the literature of OFE for site-specific input management.
 Those studies were published very recently.
-We added our description about how the size of epsilon affects our results briefly at line xx, page yy.
-But, it is imporatnt to realize that all the models uses the same data in our study.
+We added our description about how the size of epsilon affects our results briefly in Appendix G.
+But, it is important to realize that all the models uses the same data in our study.
 That is, the models are competing against each other on the level ground.
@@
 <br>
+
+# References
+
+<div id="refs"></div>

### 2022-03-21 Writing/manuscript_cea.rmd
update manuscript, appendix and comments to the editor

@@
 The resultant availability of more spatially detailed experiment data has encouraged a resurgence of interest in estimating site-specific yield response functions.
-For example, @barbosa2020modeling, @krause2020random and @Gardner21 used OFPE data to estimate site-specific yield response functions and economically optimal site-specific N fertilizer and/or seed rates.
+For example, @barbosa2020modeling, @barbosa2020risk, @krause2020random and @Gardner21 used OFPE data to estimate site-specific yield response functions and economically optimal site-specific N fertilizer and/or seed rates.
 These recent studies used machine learning (ML) methods extensively in place of more traditional parametric modeling approaches.
-@barbosa2020modeling applied the Convolutional Neural Network approach, @krause2020random used Random Forest-based approaches, and @Gardner21 used the shape-constrained generalized additive model.
+@barbosa2020modeling and @barbosa2020risk applied the Convolutional Neural Network approach, @krause2020random used Random Forest-based approaches, and @Gardner21 used the shape-constrained generalized additive model.
 But this trend of applying ML methods may raises concerns.
@@
 
-Recent studies using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21) and then derive changes in yield associated with changes in input rate to estimate site-specific input recommendations.
+Recent studies using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., @barbosa2020modeling; @barbosa2020risk; @krause2020random; @Gardner21) and then derive changes in yield associated with changes in input rate to estimate site-specific input recommendations.
 On the other hand, Causal Forest is designed specifically to estimate a discrete version of Eq.
@@
 These prices are used consistently for our simulations.
-See Appendix C.1 for further details on how the paremeters were generated and sample maps of the parameters and true economically optimal N rates.
+See Appendix C.1 for further details on how the parameters were generated and sample maps of the parameters and true economically optimal N rates.
 
@@
 The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for CF estimation.
-Just like RF and BRF, hyperparameters were tuned using cross-validatiaon.
+Just like RF and BRF, hyperparameters were tuned using cross-validation.
 
@@
 This architecture also estimated that yield and N rates were perfectly linearly related, and so estimated site-specific EONR poorly.
+
 Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs.
+As an extensional work of @barbosa2020modeling, @barbosa2020risk used an ensemble of @barbosa2020modeling's CNN-LF models to estimate site-specific EOIR for N and seed based on the predicted yields.
+However, they did not evaluate how accuracy the EOIR estimates produced from their models.
+Again, this is simply infeasible in the real-world data because ground-truth EOIR are unobservable.
+Our simulation results suggest that CNN is inferior to RF, BRF and CF-base in estimating site-specific EONR.
 
@@
 Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions.
-It plots the estimated treatment effects against true treatment effects by treatment type and ML method under the "aabbyytt" scenario in one of the one thousand simulations rounds.
+It plots the estimated treatment effects against true treatment effects by treatment type and ML method under the "aabbyytt" scenario in one of the one thousand simulation rounds.
 First of all, CNN suffers from severe underestimation of the impact of N in this particular simulation round.
@@
 
-Finally, the simulation results at a smaller and larger size of the error term are presented in Appendix xx as a sensitivity check for interested readers.
+Finally, the simulation results at a smaller and larger size of the error term are presented in Appendix G as a sensitivity check for interested readers.
 Basically, qualitative results remain the same.
@@
 
-Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations (see Figure \@ref(fig:vis-y-pred) in Appendix xx for example visualizations of predicted and true yields along with RMSE values by model).
+Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations (see Figure \@ref(fig:vis-y-pred) in Appendix E for example visualizations of predicted and true yields along with RMSE values by model).
 Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN.
@@
 Blue symbols represent true (circle) or predicted (triangle) yield at some rates that were not observed (or applied) for the two sites in the experiment.
-Prediciton-oriented ML methods train models to minimize errors in yield level prediction at the "observed" rates (red points).
+Prediction-oriented ML methods train models to minimize errors in yield level prediction at the "observed" rates (red points).
 Both RF- and BRF-trained models predict yield level at the observed rate well for the two sites (the vertical distance between the red circle and triangle).
-However, as you move away from the observed N rate, yield prediction errors tend to become larger (of course smaller yield prediction erros can be observed at unobserved rates some times).
+However, as you move away from the observed N rate, yield prediction errors tend to become larger (of course smaller yield prediction errors can be observed at unobserved rates some times).
 More important, connecting the predicted yield points does not trace the true yield response curves well for both RF and BRF.
@@
 
-In essence, Figure \@ref(fig:vis-MB-BRF-y) illustrats that good performance in predicinting yield "levels" at the "observed" points does not mean good performanc in predicting yield "response" function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied.
+In essence, Figure \@ref(fig:vis-MB-BRF-y) illustrates that good performance in predicting yield "levels" at the "observed" points does not mean good performance in predicting yield "response" function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied.
 This happens because you can predict yield "levels" for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels.
-The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary obejective of predicting yield levels well at the "observed" nitrogen rate for each site well.
-This problem is also observable at Figure \@ref(fig:plot-tre), which shows both RF and BRF understimates the impact of N on yield: or in other words, their predicted site-speific yield response functions tend to be flatter than they truelly are.
-Of course, the CNN approach in our study is an extreme case where it completley fails to recognize the contribution of N on yield.
+The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary objective of predicting yield levels well at the "observed" nitrogen rate for each site well.
+This problem is also observable at Figure \@ref(fig:plot-tre), which shows both RF and BRF underestimates the impact of N on yield: or in other words, their predicted site-specific yield response functions tend to be flatter than they truly are.
+Of course, the CNN approach in our study is an extreme case where it completely fails to recognize the contribution of N on yield.
 But, remember that CNN does performs almost as good as RF and BRF in yield prediction as shown in Table \@ref(tab:table-y).
@@
 In contrast to RF, BRF, and CNN, CF focuses to recover the yield response functions well (or alternatively the causal impact of N on yield at different discrete rates of N).
-We showed that CF can predict the impact of N on yield when N is chaned from an unobserved rate to another unobserved rats as shown in Figure \@ref(fig:plot-tre), which then translated to better performance in predicting EONR and profit.
+We showed that CF can predict the impact of N on yield when N is changed from an unobserved rate to another unobserved rats as shown in Figure \@ref(fig:plot-tre), which then translated to better performance in predicting EONR and profit.
 
 All previous research has followed a two-step procedure to estimate site-specific EONRs.
-The first step was to select the model that predicts yield leves most accurately at the observed points, and the following step used the selected model to predict EONR.
-As discussed ealier, this practice can be economically harmful.
+The first step was to select the model that predicts yield levels most accurately at the observed points, and the following step used the selected model to predict EONR.
+As discussed earlier, this practice can be economically harmful.
 Figure \@ref(fig:vis-RMSE-y-eonr) further illustrates the underlying problem.
 It plots RMSE of yield (x-axis) and EONR (y-axis) predictions by model and simulation round for several simulation rounds.
-As you can see clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation round xx and yy).
+As you can see clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation round 20 and 30).
 
-```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "The Relationship between Yield and EONR Prediction Performances under the aabbyytt scenario"}
+```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "The Relationship between yield and EONR Prediction Performances under the aabbyytt scenario"}
 vis_RMSE_y_eonr
@@
 Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF.
-It is importnat to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN.
+It is important to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN.
 Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.

### 2022-03-21 Codes/1_2_generate_coefficient.R

@@ -32,13 +32,13 @@ xy <- dplyr::select(field, unique_cell_id) %>%
 # --- Range (m) --- #
 Range <- 400
 
+#/*--------------------------------------------------------*/
+#' ## (1) Generate raw coefficients (Medium m_error: psill = 0.015)
+#/*--------------------------------------------------------*/
+
 # --- Number of iterations --- #
 b <- 1000
 
-
-#/*--------------------------------------------------------*/
-#' ## (1) Generate raw coefficients (Medium m_error: psill = 0.015, roughly 1300 sd)
-#/*--------------------------------------------------------*/
 # --- start simulation --- #
 coef_data <- 
   gen_coefs_par(
@@ -48,13 +48,19 @@ coef_data <-
     psill_merror = 0.015
     )
 
-# saveRDS(coef_data, here("Shared/Data/for_Simulations", paste0('coefficients_sprange_',Range,'.rds')))
+saveRDS(coef_data, here("Shared/Data/for_Simulations", paste0('coefficients_sprange_',Range,'.rds')))
+
+
+
 
 #/*--------------------------------------------------------*/
-#' ## (2) Generate raw coefficients (Small m_error: psill = 0.002, roughly 500 sd)
+#' ## (2) Generate raw coefficients (Small m_error: psill = 0.0075)
 #/*--------------------------------------------------------*/
 # --- set seed --- #
 set.seed(39476)
+
+# --- Number of iterations --- #
+b <- 100
 
 # --- start simulation --- #
 coef_data_low <- 
@@ -62,17 +68,24 @@ coef_data_low <-
     B = b, 
     geo_xy = xy,
     sp_range = Range,
-    psill_merror = 0.002
+    psill_merror = 0.0075
     )
+
 
 saveRDS(coef_data_low, here("Shared/Data/for_Simulations", paste0('coefficients_sprange_',Range,'_low_error.rds')))
 
 
+
+
+
 #/*--------------------------------------------------------*/
-#' ## (3) Generate raw coefficients (Large m_error: psill = 0.028, roughly 2000 sd)
+#' ## (3) Generate raw coefficients (Large m_error: psill = 0.0225)
 #/*--------------------------------------------------------*/
 # --- set seed --- #
 set.seed(57864)
+
+# --- Number of iterations --- #
+b <- 100
 
 # --- start simulation --- #
 coef_data_high <- 
[…]

### 2022-03-21 Codes/2_2_Forest_main_sim.R

@@ -44,7 +44,7 @@ var_ls_variations <- list(
 
 
 #/*--------------------------------*/
-#' ## (1) Main sim (Medium m_error: psill = 0.015)
+#' ## (1) Main sim (medium m_error)
 #/*--------------------------------*/
 # --- Data --- #
 reg_data_all <- readRDS("./Shared/Data/for_Simulations/reg_data.rds")
@@ -78,7 +78,7 @@ for (var in var_ls_variations){
 
 
 #/*--------------------------------*/
-#' ## (2) Sub sim (low m_error: psill = 0.002)
+#' ## (2) Sub sim (low m_error)
 #/*--------------------------------*/
 reg_data_low <- readRDS("./Shared/Data/for_Simulations/reg_data_low_error.rds")
 test_data_low <- readRDS("./Shared/Data/for_Simulations/test_data_low_error.rds")
@@ -126,7 +126,7 @@ dt1 %>%
 
 
 #/*--------------------------------*/
-#' ## (3) Sub sim (high: psill = 0.002)
+#' ## (3) Sub sim (high m_error)
 #/*--------------------------------*/
 reg_data_high <- readRDS("./Shared/Data/for_Simulations/reg_data_high_error.rds")
 test_data_high <- readRDS("./Shared/Data/for_Simulations/test_data_high_error.rds")

### 2022-03-21 Codes/PrepareResults.R

@@ -1,4 +1,4 @@
-## ----set-up, cache = F--------
+## ----set-up, cache = F-------------------------------------------------------------------------
 library(knitr)
 library(here)
 
@@ -9,7 +9,7 @@ knitr::opts_chunk$set(
   cache = FALSE
 )
 
-## ----packages, cache = FALSE, include = FALSE----
+## ----packages, cache = FALSE, include = FALSE--------------------------------------------------
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -36,7 +36,7 @@ library(officedown)
 library(modelsummary)
 
 
-## -----------------------------
+## ----------------------------------------------------------------------------------------------
 theme_figure <-
   theme(
     plot.title = element_text(hjust = 0.5),
@@ -65,7 +65,7 @@ set_flextable_defaults(
 )
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE----
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE-----------------------------------------
 # === plot-level field data set  === #
 field_plot_sf <-
   here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
@@ -82,7 +82,7 @@ field_cell_sf <-
   readRDS()
 
 
-## -----------------------------
+## ----------------------------------------------------------------------------------------------
 # /*--------------------------------*/
 #' ## Preparation
 # /*--------------------------------*/
@@ -150,7 +150,7 @@ vis_MB_curve <-
   geom_line(
     aes(x = N, y = value, group = factor(group))
   ) +
-  geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
+  # geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
   # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
   scale_alpha_manual(
     name = NULL,
@@ -164,12 +164,10 @@ vis_MB_curve <-
   ) +
   labs(y = "Yield (kg/ha)") +
   labs(x = "N (kg/ha)") +
-  theme_dist +
-  theme(legend.title = element_blank()) +
-  guides(color = guide_legend(nrow = 2, byrow = TRUE))
+  theme_dist
[…]

### 2022-03-21 Codes/PrepareResults.rmd

@@
   compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sub(as_i("i,j")))) %>%
-  compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sub(as_i("i,j")))) %>%
+  # compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sub(as_i("i,j")))) %>%
+  compose(i = 4, j = 1, part = "body", value = as_paragraph("r", as_sup(as_i(" \U03B5")), as_sub(as_i("i,j")))) %>%
   compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
@@
 
-vis_y_pred <- ggplot(sample_simRes_test_y) +
+vis_y_pred <- 
+  ggplot(sample_simRes_test_y) +
   geom_point(aes(x = det_yield, y = pred_yield), size = 0.5) +
@@
     rmse_y_CNN < rmse_y_BRF & rmse_y_CNN < rmse_y_RF ~ "CNN"
+  )] %>%
+  .[, which_ML_piLoss := case_when(
+    pi_loss_BRF < pi_loss_RF ~ "BRF",
+    pi_loss_RF < pi_loss_BRF ~ "RF"
   )] %>%
@@
   width(j = c(3, 6, 9), width = 0.1)
-
+```
+
+## Yield Prediction
+
+```{r}
 # /*--------------------------------*/
@@
 ```
+
+## Yield Prediction vs EONR estimation : Count Table in terms of profit loss
+
+```{r, dependson = "source-results"}
+# === Preparation === #
+prepare_count_tbl_low_high <-
+  Simres_low_high %>%
+  .[type=="test" & Method %in% c("RF", "BRF")] %>%
+  dcast(Degree + sim + Model ~ Method, value.var = c("pi_loss", "rmse_y")) %>%
+  .[, which_ML_y := case_when(
+    rmse_y_BRF < rmse_y_RF ~ "BRF",
+    rmse_y_RF < rmse_y_BRF ~ "RF"
+  )] %>%
+  .[, which_ML_piLoss := case_when(
+    pi_loss_BRF < pi_loss_RF ~ "BRF",
+    pi_loss_RF < pi_loss_BRF ~ "RF"
+  )] %>%
+  .[, index_cnst_y_piLoss := ifelse(which_ML_piLoss == which_ML_y, 1, 0)] %>%
+  .[, ML_cnst_y_piLoss := ifelse(index_cnst_y_piLoss == 1, which_ML_piLoss, NA)] %>%
+  .[, .(
+    count_BRF = nrow(.SD[ML_cnst_y_piLoss == "BRF", ]),
+    count_RF = nrow(.SD[ML_cnst_y_piLoss == "RF", ]),
+    count_y_BRF = nrow(.SD[which_ML_y == "BRF", ]),
+    count_y_RF = nrow(.SD[which_ML_y == "RF", ]),
+    Total = sum(index_cnst_y_piLoss)
+  ), by = .(Degree, Model)] %>%
+  .[, `:=`(
+    blank1 = NA, blank2 = NA, blank3 = NA
+  )] %>%
+  .[, .(Degree, Model, blank1, count_y_RF, count_RF, blank2, count_y_BRF, count_BRF, blank3, Total)]
+
+# === Table creation === #
+count_tbl_low_high <-
+  prepare_count_tbl_low_high %>%
+  as_grouped_data(, groups = c("Degree")) %>%
+  flextable(.) %>%
+  border_remove() %>%
+  delete_part(part = "header") %>%
+  add_header(
+    Degree = "Error Size",
+    Model = "Model",
+    blank1 = "", count_y_RF = "RF", count_RF = "RF",
+    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
+    blank4 = "", Total = "Total",
+    top = TRUE
+  ) %>%
+  merge_h(part = "header") %>%
+  hline_bottom(j = c(4:5, 7:8), part = "header") %>%
+  add_header(
+    Degree = "",
+    Model = "",
+    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
+    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
+    blank4 = "", Total = "",
+    top = FALSE
+  ) %>%
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  footnote(
+    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction.
+#YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
+    ref_symbols = NA
+  ) %>%
+  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
+  autofit() %>%
+  width(j = c(4, 5, 7, 8, 10), width = 0.6) %>%
+  width(j = 1, width = 0.8) %>%
+  width(j = c(3, 6, 9), width = 0.1)
+```

### 2022-03-21 Writing/appendix.rmd
minor text changes

--- 2022-03-18 Writing/appendix.rmd
@@
 ## Appendix A: Causal Tree Example {-}
-
 Figure A.1 shows an example of a CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$) ($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
@@
 ## Appendix B: Understanding Yield Response Functions Better {-}
-
 Another way to writing Eq. \@ref(eq:eqn3) that may help understanding the yield response Eq. (B.1) better conceptually is as follows:
@@
 
-### C.1 $\quad$ Base parameters **$\alpha$**, **$\beta$**, and **$ymax$** {-}
+### C.1 $\quad$ Base parameters **$\alpha$**, **$\beta$**, **$ymax$**, and **$\varepsilon$** {-}
 Parameters $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$ were modeled as spatially autocorrelated using unconditional Gaussian geostatistical simulation based on the spherical variogram model.
-The `gstat` package (version 2.0.6 [@gstat1; @gstat2]) in R was used for this purpose
+The `gstat` package (version 2.0.6 [@gstat1; @gstat2]) in R was used for this purpose.
 
-Table C.1 shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
-(Codes used to generate parameter values are publicly accessible as a Mendeley dataset [@Kakimoto2022codes], or as a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.) The range and nugget of all parameters were assumed to be $400$ m and 0.
+The size of random yield error $\varepsilon$ should be coordinated with the potential yield level for a site $(i,j)$.
+To do so, we first created spatially autocorrelated weights $r^{\varepsilon}_{i,j} \in (-1,1)$.
+After $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $r^{\varepsilon}_{i,j}$ were generated, then $\varepsilon_{i,j}$ was determined by interacting $r^{\varepsilon}_{i,j}$ with the deterministic part of yield (i.e., $ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i}))$).
+This process can be expressed by rewriting Eq.
+\@ref(eq:eqn3) as follows.
+The observed yield at site $(i, j)$ (i.e., $y_{i,j}$) is:
+
+\begin{align}
+y_{i,j} 
+&=  ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i}))(1+r^{\varepsilon}_{i,j}) \\
+&=  ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) +  ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) \cdot r^{\varepsilon}_{i,j} \\
+&= ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) + \varepsilon_{i,j}
+\end{align}
+, where $\varepsilon_{i,j} = ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) \cdot r^{\varepsilon}_{i,j}$.
+
+Table C.1 shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $r^{\varepsilon}_{i,j}$<!--  $\varepsilon_{i,j}$ -->, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
+(Codes used to generate parameter values are publicly accessible as a Mendeley dataset [@Kakimoto2022codes], or as a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.) <!-- The range and nugget of all parameters were assumed to be $400$ m and 0.
 The means of $\alpha$, $\beta$, $ymax$, and $\varepsilon$ were assumed to be $-0.5$, $0$, $12,000$ kg/ha, and $0$, and their sills were assumed to be $0.02$, $1.0$, $2.0 \times 10^{6}$ kg/ha, and $0.015$.
 See Figure C.1 for an example of the generated parameters.
+-->
 
@@
 ### C.2 $\quad$ Splitting the Base Parameters {-}
-
 For scenarios "aabbyy" and "aabbyytt," each of the base parameters $\alpha$, $\beta$, and $ymax$ are splitted into two part in a spatially correlated manner.
@@
 
-## Appendix D:  Training Accuracy of the ML methods {-}
+## Appendix D: CNN Performance per Training Epoch {-}
+The figure below shows training and validation loss measured by mean square error (MSE) over the number of epochs in a single simulation round under aabbyytt scenario for CNN as an illustration.
+For readers interested in knowing how CNN is trained for all the simulation rounds, please see the python program available at a Mendeley dataset [@Kakimoto2022codes] or a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.
+
+```{r cnn-epoch, fig.width=5, fig.height=4, fig.cap = "Figure D.1: An example of CNN performance per training epoch (scenario: aabbyytt)"}
+knitr::include_graphics(here("GitControlled/Writing/loss_model4_simID1.png"))
+```
+
+\newpage
+
+## Appendix E: True Yields vs Predicted Yields by Models
+
+The figure XX plots the predicted yields against the true yield without error in one of the one thousand simulation rounds by ML method and modeling scenario.
+The predicted points clustered around the red 1-to-1 line, meaning that the prediction-oriented ML methods predicted yields well.
+
+However, as mentioned in section 4.2, please note that even though the yield prediction accuracy evaluated at the actually applied N rate is , it does not necessary mean good performance in predicting yield “response” function which requires counterfactual prediction.
+
+```{r vis-y-pred, fig.width=7, fig.height=7.5, fig.cap = "Figure E.1: True yields without error and predicted yields"}
+vis_y_pred
+```
+
+`r ftext('NOTE: The red line in the figures denotes the 1-to-1 line to show the ideal relationship between true and predicted yields.', fp_text(font.size = 9, font.family = "Times New Roman"))`
+
+\newpage
+
+## Appendix F:  Training Accuracy of the ML methods {-}
 
@@
 
-```{r table-optN-train, tab.cap = "Table D.1: Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on training datasets"}
+```{r table-optN-train, tab.cap = "Table F.1: Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on training datasets"}
 report_table_optN_train
@@
 
-```{r table-y-train, tab.cap = "Table D.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on training datasets"}
+```{r table-y-train, tab.cap = "Table F.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on training datasets"}
 report_table_y_train
@@
 
-## Appendix E: CNN performance per training epoch
-The figure below shows training and validation loss measured by mean square error (MSE) over the number of epochs in a single simulation round under aabbyytt scenario for CNN as an illustration.
-For readers interested in knowing how CNN is trained for all the simulation rounds, please see the python program available at a Mendeley dataset [@Kakimoto2022codes] or a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.)
+## Appendix G: Simulations with Different Size of Yield Disturbance Term.
+In this section, we present the results of EONR estimation and yield prediction with different size of random yield error ($\varepsilon$).
+We created two additional yield datasets	that are only different in the size of $\varepsilon$ from the yield datasets we used in the study by changing the variogram parameter of $psill$ for $r^{\varepsilon}_{i,j}$.
+Half size of $psill$ value ($0.0075$) was used to create yield datasets with low yield error, and one and a half size of $psill$ value ($$0.0225$$) was used to create yield datasets with high yield error.
+Figure G.1 illustrates examples of the generated low and high $\varepsilon$.
 
-```{r cnn-epoch, fig.width=5, fig.height=4, fig.cap = "Figure E.1: An example of CNN performance per training epoch (scenario: aabbyytt)"}
-knitr::include_graphics(here("GitControlled/Writing/loss_model4_simID1.png"))
+```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "Figure G.1: An example of experimental design of N and generated yield at the subplot resolution"}
+field_m_error_low | field_m_error_high
 ```
@@
 
-## Appendix H: True Yields vs Predicted Yields by models
+Using those new yield datasets, we conducted one hundred rounds of simulations respectively.
+The results of EONR estimation and yield prediction are shown in Table G.1 and G.2.
+Table G.3 summarizes the relationship between yield and EONR prediction RMSE.
 
-```{r vis-y-pred, fig.width=7, fig.height=7.5, fig.cap = "Figure H.1: True yields without error and predicted yields"}
-vis_y_pred
+As the size of yield error increases, EONR estimation and yield prediction accuracy becomes improved.
+However, qualitative results about the comparative advantage of CF over other models remain the same, and Table G.3 consistently illustrates that good performance in yield prediction does not necessary indicate good performance in EONR estimation.
+
+```{r report-table-optN-low, tab.cap = "Table G.1: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
+# table_optN_prep_low_high
 ```
+
+\newpage
+
+```{r report-table-optN-low, tab.cap = "Table G.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
+# report_table_y_low_high
+```
+
+```{r count-tbl-low-high, tab.cap = "Table G.3: Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances of prediction-oriented ML methods on low and high degree of yield disturbance datasets"}
+# count_tbl_low_high
+```

### 2022-03-30 Codes/PrepareResults.rmd

--- 2022-03-19 Codes/PrepareResults.rmd
@@
 vis_all_points <- rbind(vis_res_pred, vis_true_points)
+
 ```
@@
 allML_summary_bySim <- readRDS(here("Shared/Results/for_writing/allML_summary_bySim.rds"))
-```
-
-# Yield prediction results
-
-## Report RMSE of of Yield Prediction (RF, BRF, CNN)
-
-```{r, dependson = "source-results"}
+
 # === Set up === #
@@
   .[type == "test" & Method %in% c("RF", "BRF", "CNN")]
-
+```
+
+# Yield prediction results
+
+## Report RMSE of of Yield Prediction (RF, BRF, CNN)
+
+```{r, dependson = "source-results"}
 # ==== Summary Table ====#
@@
     blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
-    blank4 = "", Total = "Total",
+    blank4 = "", Total = "Total #YP",
     top = TRUE
@@
   autofit() %>%
-  width(j = c(3, 4, 6, 7, 9, 10, 12), width = 0.6) %>%
+  width(j = c(3:4, 6:7, 9:10), width = 0.6) %>%
+  width(j = 12, width = 0.82) %>%
+  width(j = 1, width = 0.5) %>%
   width(j = c(2, 5, 8, 11), width = 0.1)
@@
 # === Load the data === #
-Simres_low <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_low.rds"))
-
-Simres_high <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_high.rds"))
+Simres_low <- 
+  here("Shared/Results/for_writing/allML_summary_bySim_low.rds") %>%
+  readRDS()
+
+Simres_high <- 
+  here("Shared/Results/for_writing/allML_summary_bySim_high.rds") %>%
+  readRDS()
 
@@
  .[, Degree := ifelse(Degree==1, "Low", "High")] %>%
- .[, Degree := factor(Degree, levels =c("Low", "High"))]
+ .[, Degree := factor(Degree, levels =c("Low", "High"))] %>%
+ .[type == "test",]
 
@@
     pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
-  ), by = .(Degree, type, Method, Model)] %>%
-  dcast(Degree + type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
+  ), by = .(Degree, Method, Model)] %>%
+  dcast(Degree + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
   .[, `:=`(
-    blank1 = NA, blank2 = NA, blank3 = NA
-  )] %>%
-  .[, .(Degree, type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CF_base, pi_loss_CF_base)]
+    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
+  )] %>%
+  .[, .(Degree, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]
 
 # === Summary Table (Testing Data sets) === #
-table_optN_prep_low_high <- 
+table_optN_low_high <- 
   table_optN_prep_low_high %>%
-  .[type == "test", !"type"] %>%
   mutate(
@@
     blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
-    # blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
+    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
     blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
@@
   merge_h(part = "header") %>%
-  hline_bottom(j = c(4:5, 7:8, 10:11), part = "header") %>%
+  hline_bottom(j = c(4:5, 7:8, 10:11, 13:14), part = "header") %>%
   add_header(
@@
     blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
-    # blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
+    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
     blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
@@
   ) %>%
-  compose(i = 2, j = c(5, 8, 11), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
+  compose(i = 2, j = c(5, 8, 11, 14), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
   hline_bottom(part = "all") %>%
@@
   align(j = 1, align = "left", part = "all") %>%
-  # autofit() %>%
-  # width(j = c(2,5,8,11), width=0.3) %>%
-  # fix_border_issues()
+  width(j = c(2,5,8,11, 14), width=0.3) %>%
   footnote(
@@
   autofit() %>%
-  width(j = c(4, 5, 7, 8, 10, 11), width = 0.6) %>%
-  width(j = 1, width = 0.8) %>%
-  width(j = c(3, 6, 9), width = 0.1)
-
+  width(j = c(4, 5, 7, 8, 10, 11, 13, 14), width = 0.6) %>%
+  width(j = 1, width = 0.82) %>%
+  width(j = 2, width = 0.5) %>%
+  align(j = 2, align = "left", part = "body") %>%
+  width(j = c(3, 6, 9, 12), width = 0.1)
+```
+
+## Yield Prediction
+
+```{r}
 # /*--------------------------------*/
@@
   Simres_low_high %>%
-  .[type == "test" & Method %in% c("RF", "BRF")] %>%
   .[, .(rmse_y = mean(rmse_y)), by = .(Degree, Method, Model)] %>%
@@
     BRF = "BRF",
+    CNN = "CNN",
     CF_base = "CF-base"
@@
   autofit() %>%
-  width(j = 1, width = 0.8)
-```
+  width(j = 1, width = 0.82) %>%
+  align(j = 2, align = "left", part = "body") 
+```
+
+## Yield Prediction vs EONR estimation : Count Table in terms of profit loss
+
+```{r, dependson = "source-results"}
+# === Preparation === #
+prepare_count_tbl_low_high <-
+  Simres_low_high %>%
+  .[Method %in% c("RF", "BRF", "CNN")] %>%
+  dcast(Degree + sim + Model ~ Method, value.var = c("pi_loss", "rmse_y")) %>%
+  .[, which_ML_y := case_when(
+    rmse_y_BRF < rmse_y_RF & rmse_y_BRF < rmse_y_CNN ~ "BRF",
+    rmse_y_RF < rmse_y_BRF & rmse_y_RF < rmse_y_CNN ~ "RF",
+    rmse_y_CNN < rmse_y_BRF & rmse_y_CNN < rmse_y_RF ~ "CNN"
+  )] %>%
+  .[, which_ML_piLoss := case_when(
+    pi_loss_BRF < pi_loss_RF & pi_loss_BRF < pi_loss_CNN ~ "BRF",
+    pi_loss_RF < pi_loss_BRF & pi_loss_RF < pi_loss_CNN ~ "RF",
+    pi_loss_CNN < pi_loss_BRF & pi_loss_CNN < pi_loss_RF ~ "CNN"
+  )] %>%
+  .[, index_cnst_y_piLoss := ifelse(which_ML_piLoss == which_ML_y, 1, 0)] %>%
+  .[, ML_cnst_y_piLoss := ifelse(index_cnst_y_piLoss == 1, which_ML_piLoss, NA)] %>%
+  .[, .(
+    count_BRF = nrow(.SD[ML_cnst_y_piLoss == "BRF", ]),
+    count_RF = nrow(.SD[ML_cnst_y_piLoss == "RF", ]),
+    count_CNN = nrow(.SD[ML_cnst_y_piLoss == "CNN", ]),
+    count_y_BRF = nrow(.SD[which_ML_y == "BRF", ]),
+    count_y_RF = nrow(.SD[which_ML_y == "RF", ]),
+    count_y_CNN = nrow(.SD[which_ML_y == "CNN", ]),
+    Total = sum(index_cnst_y_piLoss)
+  ), by = .(Degree, Model)] %>%
+  .[, `:=`(
+    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
+  )] %>%
+  .[, .(Degree, Model, blank1, count_y_RF, count_RF, blank2, count_y_BRF, count_BRF, blank3, count_y_CNN, count_CNN, blank4, Total)]
+
+# === Table creation === #
+count_tbl_low_high <-
+  prepare_count_tbl_low_high %>%
+  as_grouped_data(, groups = c("Degree")) %>%
+  flextable(.) %>%
+  border_remove() %>%
+  delete_part(part = "header") %>%
+  add_header(
+    Degree = "Error Size",
+    Model = "Model",
+    blank1 = "", count_y_RF = "RF", count_RF = "RF",
+    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
+    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
+    blank4 = "", Total = "Total #YP",
+    top = TRUE
+  ) %>%
+  merge_h(part = "header") %>%
+  hline_bottom(j = c(4:5, 7:8, 10:11), part = "header") %>%
+  add_header(
+    Degree = "",
+    Model = "",
+    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
+    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
+    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
+    blank4 = "", Total = "",
+    top = FALSE
+  ) %>%
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  footnote(
+    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction.
+#YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
+    ref_symbols = NA
+  ) %>%
+  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
+  autofit() %>%
+  width(j = c(4:5, 7:8, 10:11), width = 0.6) %>%
+  width(j = 1, width = 0.82) %>%
+  width(j = 13, width = 0.82) %>%
+  width(j = 2, width = 0.5) %>%
+  align(j = 2, align = "left", part = "body") %>%
+  width(j = c(3, 6, 9, 12), width = 0.1)
+
+```

### 2022-03-30 Writing/appendix.rmd

@@
 ```{r report-table-optN-low, tab.cap = "Table G.1: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
-# table_optN_prep_low_high
+table_optN_low_high
 ```
@@
 ```{r report-table-optN-low, tab.cap = "Table G.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
-# report_table_y_low_high
+report_table_y_low_high
 ```
@@
 ```{r count-tbl-low-high, tab.cap = "Table G.3: Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances of prediction-oriented ML methods on low and high degree of yield disturbance datasets"}
-# count_tbl_low_high
+count_tbl_low_high
 ```

### 2022-03-30 Codes/PrepareResults.rmd
correct some errors and modified our replies to the editor

@@
 
-```{r set-up, cache = F}
-library(knitr)
-library(here)
-
-here::i_am("GitControlled/Writing/manuscript_cea.rmd")
-
-knitr::opts_chunk$set(
-  # cache = TRUE
-  cache = FALSE
-)
-```
 ```{r packages, cache = FALSE, include = FALSE}
@@
 vis_all_points <- rbind(vis_res_pred, vis_true_points)
-
 ```
@@
   scale_fill_viridis_c() +
-    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
+  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
   ggtitle("(2) High error") +
@@
   width(j = 12, width = 0.82) %>%
-  width(j = 1, width = 0.5) %>%
+  width(j = 1, width = 0.8) %>%
   width(j = c(2, 5, 8, 11), width = 0.1)
@@
 
-```{r}
+```{r, cache = F}
 # === Load the data === #
@@
 
-Simres_low_high<-
+Simres_low_high <-
   bind_rows(Simres_low, Simres_high, .id = "Degree") %>%
- .[, Degree := ifelse(Degree==1, "Low", "High")] %>%
- .[, Degree := factor(Degree, levels =c("Low", "High"))] %>%
- .[type == "test",]
+  .[, Degree := ifelse(Degree == 1, "Low", "High")] %>%
+  .[, Degree := factor(Degree, levels = c("Low", "High"))] %>%
+  .[type == "test", ]
 
@@
   align(j = 1, align = "left", part = "all") %>%
-  width(j = c(2,5,8,11, 14), width=0.3) %>%
+  width(j = c(2, 5, 8, 11, 14), width = 0.3) %>%
   footnote(
@@
   autofit() %>%
-  width(j = c(4, 5, 7, 8, 10, 11, 13, 14), width = 0.6) %>%
-  width(j = 1, width = 0.82) %>%
-  width(j = 2, width = 0.5) %>%
+  width(j = c(4, 7, 10, 13), width = 0.6) %>%
+  width(j = c(5, 8, 11, 14), width = 0.5) %>%
+  width(j = 2, width = 0.7) %>%
   align(j = 2, align = "left", part = "body") %>%
-  width(j = c(3, 6, 9, 12), width = 0.1)
+  width(j = c(3, 6, 9, 12), width = 0.05)
 ```
@@
 #' ## Yield prediction
-#/*--------------------------------*/ 
+# /*--------------------------------*/
 report_table_y_low_high <-
@@
   autofit() %>%
-  width(j = c(4:5, 7:8, 10:11), width = 0.6) %>%
-  width(j = 1, width = 0.82) %>%
+  width(j = c(4:5, 7:8, 10:11), width = 0.5) %>%
   width(j = 13, width = 0.82) %>%
-  width(j = 2, width = 0.5) %>%
+  width(j = 2, width = 0.7) %>%
   align(j = 2, align = "left", part = "body") %>%
-  width(j = c(3, 6, 9, 12), width = 0.1)
-
-```
+  width(j = c(3, 6, 9, 12), width = 0.05)
+```

### 2022-03-30 Writing/CEA_3rd_round/replies_rev.rmd
minor edit
correct some errors and modified our replies to the editor

@@
 Thank you so much for saving us from claiming the false statement.
+We conducted simulations with different degrees of error according to your suggestion.
+**The results are shown in Appendix G**.
+By looking at Tables 1, 3, G.1, and G.3, you can see that as the error size decreases, both yield and EONR RMSEs decrease.
+So, in this sense, yield and EONR predictions are indeed correlated as expected.
 
-However, please note that our claim that better yield prediction does "not necessarily" lead to higher profit remains intact.
-According to your suggestions, we provide much more in-depth discussions about why that is the case under section 4.2.
+However, our claim that the models with the highest yield prediction power is not necessarily the best EONR prediciton (or the most profitable) model remains valid.
+Please note that this claim comes from comparisons **across the models** given the **same** dataset (so the same errors).
+Since we consider this a very important point for researchers in this field, we now provide much more in-depth discussions about why that is the case under section 4.2.
 As you suggested, models that can recover the "structure" of the yield response function will perform well in predicting EONR.
@@
 Please see our more detailed discussions on this matter in section 4.2.
-
-We understand your suggestion of running simulations under different magnitude of error comes from your doubt about why yield and EONR prediction is not correlated.
-But, we conducted simulations with different degrees of error anyway.
-**The results are shown in Appendix G**.
 
@@
 We added our description about how the size of epsilon affects our results briefly in Appendix G.
-But, it is important to realize that all the models uses the same data in our study.
-That is, the models are competing against each other on the level ground.
-Changing the size of error has little effects on the comparative advantage of CF over other models much.
+We added the following at line xx page yy:
+
+"Finally, the simulation results at a smaller and larger size of the error term are presented in Appendix G as a sensitivity check for interested readers.
+Basically, qualitative results remain the same."
 

### 2022-03-30 Writing/appendix.rmd
correct some errors and modified our replies to the editor

@@
 We created two additional yield datasets	that are only different in the size of $\varepsilon$ from the yield datasets we used in the study by changing the variogram parameter of $psill$ for $r^{\varepsilon}_{i,j}$.
-Half size of $psill$ value ($0.0075$) was used to create yield datasets with low yield error, and one and a half size of $psill$ value ($$0.0225$$) was used to create yield datasets with high yield error.
+Half size of $psill$ value ($0.0075$) was used to create yield datasets with low yield error, and one and a half size of $psill$ value ($0.0225$) was used to create yield datasets with high yield error.
 Figure G.1 illustrates examples of the generated low and high $\varepsilon$.
 
-```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "Figure G.1: An example of experimental design of N and generated yield at the subplot resolution"}
+```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "Figure G.1: An example of experimental design of N and generated yield at the subplot resolution", cache = TRUE}
 field_m_error_low | field_m_error_high

### 2022-03-30 Writing/manuscript_cea.rmd
correct some errors and modified our replies to the editor

@@
   message = F,
-  cache = T,
+  cache = F,
   echo = F
@@
 ```
-
-```{r analyses, results = "hide", fig.show='hide', cache = FALSE}
-# /*=================================================*/
-#' # Create figures and tables
-# /*=================================================*/
-# --- Convert an Rmd file into a pure R file using purl() ---#
-knitr::purl(
-  here("GitControlled/Codes/PrepareResults.rmd"),
-  output = here("GitControlled/Codes/PrepareResults.R")
-)
-
-# --- Read the simulation results and prepare figures and tables ---#
-source(here("GitControlled/Codes/PrepareResults.R"))
+```{r, include = F, cache = F}
+knit_child(here("GitControlled/Codes/PrepareResults.Rmd"), quiet = TRUE)
 ```

### 2022-03-30 Codes/PrepareResults.R

@@ -1,15 +1,4 @@
-## ----set-up, cache = F-------------------------------------------------------------------------
-library(knitr)
-library(here)
-
-here::i_am("GitControlled/Writing/manuscript_cea.rmd")
-
-knitr::opts_chunk$set(
-  # cache = TRUE
-  cache = FALSE
-)
-
-## ----packages, cache = FALSE, include = FALSE--------------------------------------------------
+## ----packages, cache = FALSE, include = FALSE----
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -36,7 +25,7 @@ library(officedown)
 library(modelsummary)
 
 
-## ----------------------------------------------------------------------------------------------
+## ---- include = F-------------------------
 theme_figure <-
   theme(
     plot.title = element_text(hjust = 0.5),
@@ -65,7 +54,7 @@ set_flextable_defaults(
 )
 
 
-## ----setup, warning=FALSE, message=FALSE, cache= FALSE-----------------------------------------
+## ----setup, include = FALSE---------------
 # === plot-level field data set  === #
 field_plot_sf <-
   here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
@@ -82,7 +71,7 @@ field_cell_sf <-
   readRDS()
 
 
-## ----------------------------------------------------------------------------------------------
+## -----------------------------------------
 # /*--------------------------------*/
 #' ## Preparation
 # /*--------------------------------*/
@@ -167,7 +156,7 @@ vis_MB_curve <-
   theme_dist
 
 
-## ----prepare-data-vis, cache = TRUE------------------------------------------------------------
+## ----prepare-data-vis, cache = TRUE-------
 # /*===========================================*/
 #' =  Prepare illustrative yield response curve estimated by RF =
 # /*===========================================*/
@@ -341,6 +330,7 @@ find_examples_main <-
 #     theme(legend.title = element_blank()) +
 #     guides(color=guide_legend(nrow=2, byrow=TRUE))
 
+
 vis_res_true <-
   res_true[unique_subplot_id %in% c("2_18", "6_47")] %>%
   .[, site := case_when(
@@ -379,7 +369,7 @@ vis_true_points <-
[…]

### 2022-03-30 Writing/manuscript_cea.rmd
further modifications of the text

@@
 Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs.
-As an extensional work of @barbosa2020modeling, @barbosa2020risk used an ensemble of @barbosa2020modeling's CNN-LF models to estimate site-specific EOIR for N and seed based on the predicted yields.
-However, they did not evaluate how accuracy the EOIR estimates produced from their models.
-Again, this is simply infeasible in the real-world data because ground-truth EOIR are unobservable.
-Our simulation results suggest that CNN is inferior to RF, BRF and CF-base in estimating site-specific EONR.
+As its extension, @barbosa2020risk used an ensemble of @barbosa2020modeling's CNN-LF models to estimate site-specific EOIR for N and seed.
+However, they did not evaluate how accurate their EOIR estimates produced from their models.
+This is simply because EONR validation is infeasible using the real-world data because ground-truth site-specific EOIRs are unobservable.
+Our simulation results suggest that CNN is inferior to RF, BRF and CF-base in estimating site-specific EONR at least in our simulation settings.
 
@@
 
-Despite the relatively simple nature of the simulations, results reported provide intriguing evidence of potential advantages of CF over other ML methods when the purpose of the research is to increase the economic efficiency of input management.
+Despite the relatively simple nature of the simulations, results reported provide intriguing evidence of potential advantages of CF over other ML methods when the ultimate goal of the OFPE is to increase the economic efficiency of input management.
 Of course, the reported research did not model all situations, and further research is needed.
@@
 Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF.
-It is important to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN.
+However, it is important to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN.
 Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.
+In particular, CNN is extrememly flexible in its architecture, and it is possible that other architectures than the one tried in this study may perform much better.
 
-We also showed that the model's yield prediction accuracy has little to do with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map.
+We also showed that the best model in predictin yields is not necessarily the best model in predicting EONR and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map.
 Many studies seek to predict yield level accurately using deep learning methods.
-Our results question usefulness of such models in the making of management decisions.
+Our results question the usefulness of such models in the making of management decisions.
 Further examinations into these issues are warranted.

### 2022-03-30 Writing/manuscript_cea.rmd
additional changes

@@
 
-Figure \@ref(fig:vis-MB-BRF-y) illustrates the distinction between yield prediction at observed points and yield response function prediction, giving insights into why good yield prediction does not necessarily lead to good EONR prediction in general.
+Figure \@ref(fig:vis-MB-BRF-y) illustrates the distinction between yield prediction at observed points and yield response function prediction, giving insights into why good yield level prediction does not necessarily lead to good EONR prediction in general.
 The black curves are the true yield response functions for two sites in a single simulation round.
@@
 
-In essence, Figure \@ref(fig:vis-MB-BRF-y) illustrates that good performance in predicting yield "levels" at the "observed" points does not mean good performance in predicting yield "response" function, which is about finding out what "would" happen to yield if rates other than the one actually applied were applied.
+In essence, Figure \@ref(fig:vis-MB-BRF-y) illustrates that good performance in predicting yield "levels" at the "observed" points does not mean good performance in predicting yield "response" function, which is about finding out what "would" have happened to yield if rates other than the one actually applied were applied.
 This happens because you can predict yield "levels" for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels.
@@
 Of course, the CNN approach in our study is an extreme case where it completely fails to recognize the contribution of N on yield.
-But, remember that CNN does performs almost as good as RF and BRF in yield prediction as shown in Table \@ref(tab:table-y).
+But, remember that CNN does performs almost as good as and sometimes surpass RF and BRF in yield prediction as shown in Table \@ref(tab:table-y).
 

### 2022-03-30 Writing/CEA_3rd_round/replies_rev.rmd
small code changes (clean the codes later)

@@
 This is because we can never test the statistical property of a statistical method in principle using the real data.
-For example, please see @Wager2018a and @oprescu2019orthogonal
+For example, please see @Wager2018a and @oprescu2019orthogonal.
 
@@
 
-Please see page xx, line xx for a new list of studies that attempt to estimate EONR.
+Please see page 3, line 35 for a new list of studies that attempt to estimate EONR.
 Please note that the previous studies relevant to our study are those that apply ML methods to OFE data with the ultimate intention of estimating site-specific EONR.
@@
 We added our description about how the size of epsilon affects our results briefly in Appendix G.
-We added the following at line xx page yy:
+We added the following at line 25 page 390:
 

### 2022-03-30 Codes/PrepareResults.R

@@ -1,4 +1,15 @@
-## ----packages, cache = FALSE, include = FALSE----
+## ----set-up, cache = F------------------------------------------------------------------------
+library(knitr)
+library(here)
+
+here::i_am("GitControlled/Writing/manuscript_cea.rmd")
+
+knitr::opts_chunk$set(
+  # cache = TRUE
+  cache = FALSE
+)
+
+## ----packages, cache = FALSE, include = FALSE-------------------------------------------------
 # === packages ===#
 # --- data wrangling--- #
 library(sf)
@@ -25,7 +36,7 @@ library(officedown)
 library(modelsummary)
 
 
-## ---- include = F-------------------------
+## ---------------------------------------------------------------------------------------------
 theme_figure <-
   theme(
     plot.title = element_text(hjust = 0.5),
@@ -54,7 +65,7 @@ set_flextable_defaults(
 )
 
 
-## ----setup, include = FALSE---------------
+## ----setup, warning=FALSE, message=FALSE, cache= FALSE----------------------------------------
 # === plot-level field data set  === #
 field_plot_sf <-
   here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
@@ -71,7 +82,7 @@ field_cell_sf <-
   readRDS()
 
 
-## -----------------------------------------
+## ---------------------------------------------------------------------------------------------
 # /*--------------------------------*/
 #' ## Preparation
 # /*--------------------------------*/
@@ -156,7 +167,7 @@ vis_MB_curve <-
   theme_dist
 
 
-## ----prepare-data-vis, cache = TRUE-------
+## ----prepare-data-vis, cache = TRUE-----------------------------------------------------------
 # /*===========================================*/
 #' =  Prepare illustrative yield response curve estimated by RF =
 # /*===========================================*/
@@ -168,17 +179,21 @@ vis_MB_curve <-
 library(grf)
 source(here("GitControlled/Codes/0_2_functions_main_sim.R"))
 
-# === Data === #
-field_subplot_test_dt <-
[…]

### 2022-03-30 Codes/PrepareResults.rmd

@@
 
-# === Data === #
-field_subplot_test_dt <-
-  readRDS(here("Shared/Results/for_writing/field_subplot_test_dt.rds"))
-
-train_dt <-
-  field_subplot_sf %>%
-  data.table()
-
-test_dt <-
-  field_subplot_test_dt %>%
-  data.table()
+# --- Data --- #
+test_subplot_dt <- 
+  here("Shared/Results/for_writing/test_subplot_dt.rds") %>%
+  readRDS()
+
+# subplots_infiled <- test_subplot_dt[,unique_subplot_id] %>% unique()
+
+# cnn_pred <- 
+#   here("Shared/Results/CNN_rawRes_onEval/alldata_model4.csv") %>%
+#   fread() %>%
+#   .[, c("subplot_id", "strip_id") := tstrsplit(id, "_", fixed=TRUE)] %>%
+#   .[,unique_subplot_id := paste0(strip_id,"_",subplot_id)] %>%
+#   .[sim==x & unique_subplot_id %in% subplots_infiled,] %>%
+#   .[,.(sim, unique_subplot_id, rate, pred)] %>%
+#   setnames(names(.), c("sim", "unique_subplot_id", "N", "CNN"))
 
@@
   RF_run(
-    reg_data = train_dt,
+    reg_data = data.table(field_subplot_sf),
     var_ls = temp_var_ls
@@
   BRF_run(
-    reg_data = train_dt,
+    reg_data = data.table(field_subplot_sf),
     var_ls = temp_var_ls
@@
 
-# === Yield prediction === #
+# /*===== Yield Calculation =====*/
 # --- All N experimental rates --- #
-N_rate <- test_dt[, aa_n] %>%
-  unique() %>%
-  sort()
-# For illustration purpose, we use site where either 2nd and 4th N rates are actually application
-tg_N_rate <- N_rate[c(2, 3, 4)]
+N_rate <- test_subplot_dt[, aa_n] %>% unique() %>% sort()
 
@@
   seq(min(N_rate) - 30, max(N_rate) + 30, by = 1)
-# seq_N <-
-#   seq(min(N_rate), max(N_rate), by=1)
 
 res_true <-
-  test_dt %>%
-  .[aa_n %in% tg_N_rate] %>%
+  test_subplot_dt %>%
+  # .[aa_n %in% tg_N_rate] %>%
   .[rep(1:nrow(.), each = length(seq_N)), ] %>%
@@
 res_pred <-
-  test_dt %>%
-  .[aa_n %in% tg_N_rate] %>%
+  test_subplot_dt %>%
+  # .[aa_n %in% tg_N_rate] %>%
   .[rep(1:nrow(.), each = length(N_rate)), ] %>%
@@
   .[, BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
-  melt(id.vars = c("unique_subplot_id", "yield", "aa_n", "N"), measure.vars = c("RF", "BRF"))
-
-find_examples_main <-
-  res_pred %>%
-  .[variable == "BRF" & aa_n == N, ] %>%
-  .[, y_diff_brf := abs(yield - value)] %>%
-  .[y_diff_brf < 500, unique_subplot_id]
-# .[y_diff_brf < 500 & y_diff_brf < 1000, unique_subplot_id]
-
-# === For visualization === #
-# set.seed(1256)
-
-# low <-
-#   res_true[aa_n == tg_N_rate[3]] %>%
-#   get_rows_optN(data=., value = 0.9, range = 0.1) %>%
-#   .[unique_subplot_id %in% find_examples_main] %>%
-#   # .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1),] %>%
-#   .[, unique_subplot_id] %>%
-#   unique()
-
-# length(low)
-# x <- 16
-# i= x:(x+1)
-# vis_res_true <- res_true[unique_subplot_id %in% low[i]]
-# vis_res_pred <- res_pred[unique_subplot_id %in% low[i]]
-# ggplot() +
-#     geom_line(
-#       data=vis_res_true, aes(x=N, y=yield, color = unique_subplot_id)
-#     ) +
-#     geom_point(
-#       data=vis_res_pred, aes(x=N, y=value, color = unique_subplot_id, alpha = "Predicts"), shape=2, size = 1.5
-#     ) +
-#     geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
-#     facet_wrap(~variable) +
-#     scale_alpha_manual(
-#       name = NULL,
-#       values = c(1, 1),
-#       breaks = c("Predicts", "True yield at actual N rate that was applied"),
-#       guide = guide_legend(override.aes = list(linetype = c(0, 1),
-#         shape = c(2, 16),
-#         color = c("black", "blue"))
-#         )
-#     ) +
-#     labs(y = "Yield (kg/ha)") +
-#     labs(x = "N (kg/ha)") +
-#     theme_dist +
-#     theme(legend.title = element_blank()) +
-#     guides(color=guide_legend(nrow=2, byrow=TRUE))
-
-# tg_N_rate <- N_rate[2]
-# low: 13_41, 15_34, 15_35, 11_40
-# medium: 8_41, *8_42*, *8_43*, 27_10
-# high: 4_21
-
-# tg_N_rate <- N_rate[3]
-# **2_18**, 10_42 ***6_47***
-
-# tg_N_rate <- N_rate[4]
-# 10_49
-
-# final
-# + *2_18* (more than 14500)
-# + *8_42* (11500)
-# + *8_43* (11300)
-# + **6_47** (11100)
-
-# c("2_18", "8_42")
-# c("2_18", "6_47") **
-
-# vis_res_true <- res_true[unique_subplot_id %in% c("2_18", "6_47")]
-# vis_res_pred <- res_pred[unique_subplot_id %in% c("2_18", "6_47")]
-# ggplot() +
-#     geom_line(
-#       data=vis_res_true, aes(x=N, y=yield, color = unique_subplot_id)
-#     ) +
-#     geom_point(
-#       data=vis_res_pred, aes(x=N, y=value, color = unique_subplot_id, alpha = "Predicts"), shape=2, size = 1.5
-#     ) +
-#     geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
-#     facet_wrap(~variable) +
-#     scale_alpha_manual(
-#       name = NULL,
-#       values = c(1, 1),
-#       breaks = c("Predicts", "True yield at actual N rate that was applied"),
-#       guide = guide_legend(override.aes = list(linetype = c(0, 1),
-#         shape = c(2, 16),
-#         color = c("black", "blue"))
-#         )
-#     ) +
-#     labs(y = "Yield (kg/ha)") +
-#     labs(x = "N (kg/ha)") +
-#     theme_dist +
-#     theme(legend.title = element_blank()) +
-#     guides(color=guide_legend(nrow=2, byrow=TRUE))
+  # .[cnn_pred, on = c("sim", "unique_subplot_id", "N")] %>%
+  melt(
+    id.vars = c("unique_subplot_id", "yield", "aa_n", "N"),
+    # measure.vars = c("RF", "BRF", "CNN")
+    measure.vars = c("RF", "BRF")
+    ) %>%
+  .[, observed := ifelse(
+    aa_n == N,
+    "Observed",
+    "Unobserved"
+  )] %>%
+  .[, y_diff := abs(yield - value)]
+
+# /*===== Preparation for plots =====*/
+# new one
+# c("8_43", "2_20")
+# old one
+# c("2_18", "6_47")
 
 vis_res_true <-
-  res_true[unique_subplot_id %in% c("2_18", "6_47")] %>%
-  .[, site := case_when(
-    unique_subplot_id == "2_18" ~ "site 1",
-    unique_subplot_id == "6_47" ~ "site 2"
-  )]
+  res_true[unique_subplot_id %in% c("2_18", "6_47")]
 
@@
   res_pred[unique_subplot_id %in% c("2_18", "6_47")] %>%
-  .[, site := case_when(
-    unique_subplot_id == "2_18" ~ "site 1",
-    unique_subplot_id == "6_47" ~ "site 2"
-  )] %>%
   .[, type := "Predicted"] %>%
-  .[, observed := ifelse(
-    aa_n == N,
-    "Observed Rate",
-    "Unobserved Rate"
-  )] %>%
   setnames("variable", "model") %>%
-  .[, .(N, value, type, observed, model, site)]
+  .[, .(N, value, type, observed, model, unique_subplot_id)]
 
 vis_true_points <-
-  vis_res_true[N %in% unique(vis_res_pred$N), ] %>%
+  vis_res_true %>%
+  .[N %in% unique(vis_res_pred$N), ] %>%
   .[, type := "True"] %>%
@@
   .[, model := c("RF", "BRF") %>% rep(each = 10)] %>%
-  .[, .(N, value, type, observed, model, site)]
+  .[, .(N, value, type, observed, model, unique_subplot_id)]
 
@@
     data = vis_res_true,
-    aes(x = N, y = yield, group = site)
+    aes(x = N, y = yield, group = unique_subplot_id)
   ) +
@@
     data = vis_all_points[type == "Predicted", ],
-    aes(y = value, x = N, color = site),
+    aes(y = value, x = N, color = unique_subplot_id),
     linetype = 2,
@@
   ) +
+  # annotate(
+  #   "text",
+  #   x = 137,  y = 9700,
+  #   label = "Observed Rate \n = 117 (kg/ha)",
+  #   family = "Times",
+  #   size = 2
+  # ) +
   annotate(

### 2022-03-30 Writing/manuscript_cea.rmd

@@
 $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen].
-Figure \@ref(fig:vis-MB-curve) presents example visualization of site-specific yield response fuctions for some sites.
+Figure \@ref(fig:vis-MB-curve) presents example visualization of site-specific yield response functions for some sites.
 
@@
 The Adam optimizer [@kingma2014adam] was used with a learning rate of $0.001 \%$ (default value).
-To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience (see Figure \@ref(cnn-epoch) for an illustration of the convergens of training with respect to the number of epochs).
+To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience (see Figure D.1 in Appendix D for an illustration of the convergence of training with respect to the number of epochs).
 
@@
 
-Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the RMSEs of the EONR estimations and $\hat{\pi}_{def}$ obtained from the 1000 simualtion rounds by ML method and modeling scenario, respectively.
+Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the RMSEs of the EONR estimations and $\hat{\pi}_{def}$ obtained from the one thousand simulation rounds by ML method and modeling scenario, respectively.
 The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios.
@@
 
-Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations (see Figure \@ref(fig:vis-y-pred) in Appendix E for example visualizations of predicted and true yields along with RMSE values by model).
+Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations (see Figure E.1 in Appendix E for example visualizations of predicted and true yields along with RMSE values by model).
 Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN.
@@
 Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.
-In particular, CNN is extrememly flexible in its architecture, and it is possible that other architectures than the one tried in this study may perform much better.
+In particular, CNN is extremely flexible in its architecture, and it is possible that other architectures than the one tried in this study may perform much better.
 
-We also showed that the best model in predictin yields is not necessarily the best model in predicting EONR and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map.
+We also showed that the best model in prediction yields is not necessarily the best model in predicting EONR and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map.
 Many studies seek to predict yield level accurately using deep learning methods.

### 2022-04-07 Writing/manuscript_cea.rmd
minor changes in text

--- 2022-03-30 Writing/manuscript_cea.rmd
@@
 It plots RMSE of yield (x-axis) and EONR (y-axis) predictions by model and simulation round for several simulation rounds.
-As you can see clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation round 20 and 30).
+As you can see clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation rounds 10, 20, and 30).
 
@@
 For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of 1000 iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations.
-That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF model performed the best at yield prediction among RF, BRF, and CNN, but did not provide EONR estimates that led to the highest profit.
+That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds where the RF model performed the best at yield prediction among RF, BRF, and CNN,RF did not provide EONR estimates that led to the highest profit.
 Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously.

### 2022-04-07 Codes/0_1_functions_gen_analysis_data.R

@@ -334,17 +334,17 @@ gen_cluster <- function(data, num_levels, dim) {
 }
 
 # /*=================================================*/
-#' # Make grids within a subplot for base_field 
+#' # Make grids within a subplot for base_field
 # /*=================================================*/
-make_grid_within_subplot <- function(field_base, cell){
+make_grid_within_subplot <- function(field_base, cell) {
   # cell="2_1"
-  temp_cell <- field_base%>%filter(unique_cell_id==cell)
-  res <- st_make_grid(st_boundary(temp_cell),  n = c(6, 1))%>%
-    st_as_sf()%>%
-    mutate(unique_cell_id=cell, cell_in_cell.id=seq(from=1,to=6))
+  temp_cell <- field_base %>% filter(unique_cell_id == cell)
+  res <- st_make_grid(st_boundary(temp_cell), n = c(6, 1)) %>%
+    st_as_sf() %>%
+    mutate(unique_cell_id = cell, cell_in_cell.id = seq(from = 1, to = 6))
 
   return(res)
-} 
+}
 
 
 # /*=================================================*/
@@ -490,13 +490,11 @@ assign_rates <- function(data_sf, rates_ls, pattern = "fixed-latin-square", merg
   }
 }
 
-
-#/*----------------------------------*/
-#' ## Unconditional Gaussian geostatistical Simulation  
-#/*----------------------------------*/
+# /*----------------------------------*/
+#' ## Unconditional Gaussian geostatistical Simulation
+# /*----------------------------------*/
 
 gen_coefs <- function(mean, psill, range, coef_name, nsim, xy) {
-  
   g_N <- gstat(
     formula = z ~ 1,
     locations = ~ X + Y,
@@ -507,13 +505,12 @@ gen_coefs <- function(mean, psill, range, coef_name, nsim, xy) {
       range = range,
       nugget = 0,
       model = "Sph" # changed from "Exp", "Sph"
-
     ),
     nmax = 50 # number of nearest observations
   )
 
   b_sim <- predict(g_N, newdata = xy, nsim = nsim) %>%
-    data.table()%>%
+    data.table() %>%
[…]

### 2022-04-07 Codes/1_2_generate_coefficient.R

@@ -1,6 +1,6 @@
-#/*----------------------------------*/
+# /*----------------------------------*/
 #' ## Preparation
-#/*----------------------------------*/
+# /*----------------------------------*/
 library(here)
 library(tmap)
 library(sp)
@@ -32,30 +32,30 @@ xy <- dplyr::select(field, unique_cell_id) %>%
 # --- Range (m) --- #
 Range <- 400
 
-#/*--------------------------------------------------------*/
+# /*--------------------------------------------------------*/
 #' ## (1) Generate raw coefficients (Medium m_error: psill = 0.015)
-#/*--------------------------------------------------------*/
+# /*--------------------------------------------------------*/
 
 # --- Number of iterations --- #
 b <- 1000
 
 # --- start simulation --- #
-coef_data <- 
+coef_data <-
   gen_coefs_par(
-    B = b, 
+    B = b,
     geo_xy = xy,
     sp_range = Range,
     psill_merror = 0.015
-    )
+  )
 
-saveRDS(coef_data, here("Shared/Data/for_Simulations", paste0('coefficients_sprange_',Range,'.rds')))
-
-
+saveRDS(coef_data, here("Shared/Data/for_Simulations", paste0("coefficients_sprange_", Range, ".rds")))
 
 
-#/*--------------------------------------------------------*/
+
+
+# /*--------------------------------------------------------*/
 #' ## (2) Generate raw coefficients (Small m_error: psill = 0.0075)
-#/*--------------------------------------------------------*/
+# /*--------------------------------------------------------*/
 # --- set seed --- #
 set.seed(39476)
 
@@ -63,24 +63,24 @@ set.seed(39476)
 b <- 100
 
 # --- start simulation --- #
-coef_data_low <- 
+coef_data_low <-
   gen_coefs_par(
-    B = b, 
+    B = b,
     geo_xy = xy,
     sp_range = Range,
     psill_merror = 0.0075
-    )
+  )
 
 
-saveRDS(coef_data_low, here("Shared/Data/for_Simulations", paste0('coefficients_sprange_',Range,'_low_error.rds')))
+saveRDS(coef_data_low, here("Shared/Data/for_Simulations", paste0("coefficients_sprange_", Range, "_low_error.rds")))
 
 
 
 
 
-#/*--------------------------------------------------------*/
+# /*--------------------------------------------------------*/
[…]

### 2022-04-07 Codes/2_1_generate_analysis_data.R

@@ -1,6 +1,6 @@
-#/*----------------------------------*/
+# /*----------------------------------*/
 #' ## Preparation
-#/*----------------------------------*/
+# /*----------------------------------*/
 library(here)
 library(mgcv)
 library(ggplot2)
@@ -20,104 +20,98 @@ pCorn <- price_table[2, pCorn]
 pN <- price_table[2, pN]
 
 # === Load Field data === #
-field <- 
-	here("Shared/Data/for_Simulations/analysis_field.rds") %>%
-	readRDS()
+field <-
+  here("Shared/Data/for_Simulations/analysis_field.rds") %>%
+  readRDS()
 
 
 # /*===========================================*/
-#'= (1) For medium degree of m_error (Main Data)=
+#' = (1) For medium degree of m_error (Main Data)=
 # /*===========================================*/
 
 # === Load coef Data sets === #
-# coef_data <- 
+# coef_data <-
 # 	here("Shared/Data/for_Simulations/coefficients_sprange_400.rds") %>%
 # 	readRDS()
 
-#/*--------------------------------*/
+# /*--------------------------------*/
 #' ## (1)-1 Generate Cell-level Data sets
-#/*--------------------------------*/
+# /*--------------------------------*/
 raw_data <- lapply(
-	1:1000, function(x) {
-		prepare_raw_data(
-			i = x,
-			field = field,
-			coef_data_m = coef_data[sim == x, ],
-			coef_data_t = coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ],
-			app_error="no"
-		)
-	}
+  1:1000,
+  function(x) {
+    prepare_raw_data(
+      i = x,
+      field = field,
+      coef_data_m = coef_data[sim == x, ],
+      coef_data_t = coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ],
+      app_error = "no"
+    )
+  }
 )
 
+reg_raw_data <- sapply(raw_data, "[", 1) %>% rbindlist()
+test_raw_data <- sapply(raw_data, "[", 2) %>% rbindlist()
 
-reg_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
-test_raw_data <- sapply(raw_data,"[",2)%>%rbindlist()
 
-#/*--------------------------------*/
+# /*--------------------------------*/
[…]

### 2022-04-07 Codes/2_2_Forest_main_sim.R

@@ -1,8 +1,8 @@
 # /*===== Run on R GUI =====*/
 
-#/*----------------------------------*/
+# /*----------------------------------*/
 #' ## Preparation
-#/*----------------------------------*/
+# /*----------------------------------*/
 library(grf)
 library(data.table)
 library(tidyverse)
@@ -31,80 +31,82 @@ pN <- price_table[2, pN]
 # + the 1000 simulation results will be saved per each scenario
 
 # === set up for parallel computations === #
-plan(multicore, workers = availableCores()-2)
-options(future.globals.maxSize= 850*1024^2)
+plan(multicore, workers = availableCores() - 2)
+options(future.globals.maxSize = 850 * 1024^2)
 
 # --- modeling scenario --- #
-var_ls_variations <- list(
+var_ls_variations <-
+  list(
     c("alpha", "beta", "ymax"),
     c("alpha", "beta", "ymax", "theta_1", "theta_2"),
     c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2"),
     c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")
   )
 
-
-#/*--------------------------------*/
+# /*--------------------------------*/
 #' ## (1) Main sim (medium m_error)
-#/*--------------------------------*/
+# /*--------------------------------*/
 # --- Data --- #
 reg_data_all <- readRDS("./Shared/Data/for_Simulations/reg_data.rds")
 test_data_all <- readRDS("./Shared/Data/for_Simulations/test_data.rds")
 
 # --- Number of iterations --- #
-B=1000
+B <- 1000
 
 # === start simulation === #
-for (var in var_ls_variations){
-	# var = c("alpha", "beta", "ymax")
-	set.seed(1378)
-	# --- for each modeling scenario run: --- #
-	sim_results <- lapply(1:B, 
-		function(x){
-			sim_par(
-				i = x,
-				var_ls = var,
-				reg_data = reg_data_all[sim==x&padding==1,],
-	      		test_data = test_data_all[sim==x&padding==1,],
-	      		N_levels = reg_data_all[sim==x,]$rate%>%unique()%>%sort()
-	      	)
-		}
-	) %>%
-	rbindlist()
+for (var in var_ls_variations) {
[…]

### 2022-04-07 Writing/appendix.rmd

@@
 
-The size of random yield error $\varepsilon$ should be coordinated with the potential yield level for a site $(i,j)$.
+The size of random yield error $\varepsilon$ needs to be coordinated with the potential yield level for a site $(i,j)$.
 To do so, we first created spatially autocorrelated weights $r^{\varepsilon}_{i,j} \in (-1,1)$.
-After $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $r^{\varepsilon}_{i,j}$ were generated, then $\varepsilon_{i,j}$ was determined by interacting $r^{\varepsilon}_{i,j}$ with the deterministic part of yield (i.e., $ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i}))$).
+After $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $r^{\varepsilon}_{i,j}$ were generated, then $\varepsilon_{i,j}$ was determined by interacting $r^{\varepsilon}_{i,j}$ with the deterministic yield component (i.e., $ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i}))$).
 This process can be expressed by rewriting Eq.
@@
 Table C.1 shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $r^{\varepsilon}_{i,j}$<!--  $\varepsilon_{i,j}$ -->, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project.
-(Codes used to generate parameter values are publicly accessible as a Mendeley dataset [@Kakimoto2022codes], or as a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.) <!-- The range and nugget of all parameters were assumed to be $400$ m and 0.
+(Codes used to generate parameter values are publicly accessible as a Mendeley dataset [@Kakimoto2022codes], or as a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.) See Figure C.1 for an example of the generated parameters.<!-- The range and nugget of all parameters were assumed to be $400$ m and 0.
 The means of $\alpha$, $\beta$, $ymax$, and $\varepsilon$ were assumed to be $-0.5$, $0$, $12,000$ kg/ha, and $0$, and their sills were assumed to be $0.02$, $1.0$, $2.0 \times 10^{6}$ kg/ha, and $0.015$.
@@
 
-The figure XX plots the predicted yields against the true yield without error in one of the one thousand simulation rounds by ML method and modeling scenario.
+Figure E.1 plots the predicted yields against the true yield without error in one of the one thousand simulation rounds by ML method and modeling scenario.
 The predicted points clustered around the red 1-to-1 line, meaning that the prediction-oriented ML methods predicted yields well.
@@
 
-```{r vis-y-pred, fig.width=7, fig.height=7.5, fig.cap = "Figure E.1: True yields without error and predicted yields"}
+```{r vis-y-pred, fig.width=7, fig.height=5, fig.cap = "Figure E.1: True yields without error and predicted yields"}
 vis_y_pred
@@
 In this section, we present the results of EONR estimation and yield prediction with different size of random yield error ($\varepsilon$).
-We created two additional yield datasets	that are only different in the size of $\varepsilon$ from the yield datasets we used in the study by changing the variogram parameter of $psill$ for $r^{\varepsilon}_{i,j}$.
+By changing the variogram parameter of $psill$ for $r^{\varepsilon}_{i,j}$, We created two additional yield datasets	that are only different in the size of $\varepsilon$ from the yield datasets we used in the study.
 Half size of $psill$ value ($0.0075$) was used to create yield datasets with low yield error, and one and a half size of $psill$ value ($0.0225$) was used to create yield datasets with high yield error.
@@
 
-```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "Figure G.1: An example of experimental design of N and generated yield at the subplot resolution", cache = TRUE}
+```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "Figure G.1: An illustrative example of spatial distributions of different size of yield errors", cache = TRUE}
 field_m_error_low | field_m_error_high
@@
 As the size of yield error increases, EONR estimation and yield prediction accuracy becomes improved.
-However, qualitative results about the comparative advantage of CF over other models remain the same, and Table G.3 consistently illustrates that good performance in yield prediction does not necessary indicate good performance in EONR estimation.
+However, qualitative results about the comparative advantage of CF over other models remain the same, and Table G.3 illustrates that good performance in yield prediction does not necessary indicate good performance in EONR estimation.
+
+<br>
 
@@
 
-\newpage
-
 ```{r report-table-optN-low, tab.cap = "Table G.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
@@
 
+\newpage
+
 ```{r count-tbl-low-high, tab.cap = "Table G.3: Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances of prediction-oriented ML methods on low and high degree of yield disturbance datasets"}

### 2022-04-19 Codes/PrepareResults.rmd
large updates for 3rd round submission

@@
 # === packages ===#
+library(here)
 # --- data wrangling--- #
@@
 
-# Read the data
+# Read Field Data
 
@@
 
-# Illustrative yield response curve
-
-+ show to *which degree N affects yield* (yield response to N) 
-+ show how the relation between yield estimation error and the effect of N on yield increase is ()
-
-## MB yield response to N
-+ for comment 8
-+ The figure illustrates how yield responds to N
+# Illustrative Examples of MB Yield Response Curves (Figure 2)
 
@@
   ) +
-  # geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
-  # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
   scale_alpha_manual(
@@
 
-## MB yield response and estimated yield response by BRF
-+ As a response to comment 6
-+ The figure shows the true yield response function and predicted yields at five N experiment by BRF
+# Illustrative Examples of Yield Response Curves Estimated by RF and BRF (Figure 7)
 
 ```{r prepare-data-vis, cache = TRUE}
-# /*===========================================*/
-#' =  Prepare illustrative yield response curve estimated by RF =
-# /*===========================================*/
-
 # /*--------------------------------*/
@@
   readRDS()
-
-# subplots_infiled <- test_subplot_dt[,unique_subplot_id] %>% unique()
-
-# cnn_pred <- 
-#   here("Shared/Results/CNN_rawRes_onEval/alldata_model4.csv") %>%
-#   fread() %>%
-#   .[, c("subplot_id", "strip_id") := tstrsplit(id, "_", fixed=TRUE)] %>%
-#   .[,unique_subplot_id := paste0(strip_id,"_",subplot_id)] %>%
-#   .[sim==x & unique_subplot_id %in% subplots_infiled,] %>%
-#   .[,.(sim, unique_subplot_id, rate, pred)] %>%
-#   setnames(names(.), c("sim", "unique_subplot_id", "N", "CNN"))
 
@@
 # /*===== Preparation for plots =====*/
-# new one
-# c("8_43", "2_20")
-# old one
-# c("2_18", "6_47")
-
 vis_res_true <-
@@
   ) +
-  # annotate(
-  #   "text",
-  #   x = 137,  y = 9700,
-  #   label = "Observed Rate \n = 117 (kg/ha)",
-  #   family = "Times",
-  #   size = 2
-  # ) +
   annotate(
@@
 
-# Variogram Prameter Table
+# Field Maps
+
+## Division of Field: plots, subplots and cells (Figure 1)
+
+```{r field-map-visualization, dependson = "setup"}
+
+# === Preparation === #
+ex_plot <- field_plot_sf[224, ]
+ex_subplots <- field_subplot_sf[ex_plot, , op = st_within]
+
+ex_one_subplot <- ex_subplots[1, ]
+ex_cells <- field_cell_sf[ex_one_subplot, , op = st_within]
+
+one_subplot <- ex_subplots[3, ]
+
+#-- (1) plot-level field map  --#
+
+plot <-
+  ggplot() +
+  geom_sf(data = field_plot_sf) +
+  geom_sf(data = ex_plot, fill = "green", size = 1) +
+  coord_sf(expand = FALSE) +
+  # theme_void() +
+  ggtitle("12 \u00D7 32 plots") +
+  theme_figure
+
+grob_plot <- ggplotGrob(plot)
+
+#-- (2) create a map of subplots in a plot --##
+subplots_inPlot <-
+  ggplot() +
+  geom_sf(data = ex_plot, fill = "green") +
+  geom_sf(data = ex_subplots, fill = NA, size = 1) +
+  geom_sf(data = ex_subplots[2, ], fill = "skyblue", size = 1) +
+  coord_sf(expand = FALSE) +
+  # theme_void() +
+  ggtitle("4 \u00D7 1 subplots") +
+  theme_figure
+
+grob_subplots_inPlot <- ggplotGrob(subplots_inPlot)
+
+#-- (3) create a map of cells in a subplot --#
+cells_inSubplot <-
+  ggplot() +
+  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
+  geom_sf(data = ex_cells, fill = NA) +
+  geom_sf(data = ex_cells[2, ], fill = "skyblue", size = 1) +
+  coord_sf(expand = FALSE) +
+  # theme_void() +
+  ggtitle("6 \u00D7 6 cells") +
+  theme_figure
+
+grob_cells_inSubplot <- ggplotGrob(cells_inSubplot)
+
+#-- (4)put them on the same map --#
+field_structure <-
+  ggplot() +
+  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
+  # /*----------------------------------*/
+  #' ##  base maps
+  # /*----------------------------------*/
+  # --- plot level --- #
+  annotation_custom(grob_plot,
+    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1
+  ) +
+  # --- subplot level --- #
+  annotation_custom(grob_subplots_inPlot,
+    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7
+  ) +
+  # --- cell level --- #
+  annotation_custom(grob_cells_inSubplot,
+    xmin = 0.8, xmax = 0.8 + 0.2, ymin = 0.382, ymax = 0.382 + 0.2
+  ) +
+  # /*----------------------------------*/
+  #' ## Add braces
+  # /*----------------------------------*/
+  # --- between plot and subplot --- #
+  geom_brace(aes(c(0.43, 0.43 + 0.1), c(0.372 - 0.004, 0.645 + 0.013)), color = "red", rotate = 270, inherit.data = F) +
+  # --- between subplot and cell --- #
+  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.401 - 0.002, 0.529 + 0.011)), color = "red", rotate = 270, inherit.data = F) +
+  # /*----------------------------------*/
+  #' ## add annotations
+  # /*----------------------------------*/
+  # --- annotation for plot --- #
+  geom_segment(aes(x = 0.42, xend = 0.383, y = 0.60, yend = 0.52),
+    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
+  ) +
+  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.02, label = "plot", family = "Times New Roman") +
+  # --- annotation for subplot --- #
+  geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
+    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
+  ) +
+  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot", , family = "Times New Roman") +
+  # --- annotation for cell --- #
+  geom_segment(aes(x = 0.9, xend = 0.87, y = 0.365, yend = 0.41),
+    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
+  ) +
+  annotate("text", x = 0.9 + 0.02, y = 0.365 - 0.005, label = "cell", , family = "Times New Roman") +
+  theme_void()
+```
+
+## Experimental N Design (Figure 3 Left)
+
+```{r, dependson = "setup"}
+field_Ndesign <-
+  ggplot() +
+  geom_sf(
+    data = field_plot_sf,
+    aes(fill = factor(rate)), size = 0,
+    inherit.aes = FALSE,
+  ) +
+  scale_fill_viridis_d() +
+  labs(fill = "Nitrogen rate\n  (kg/ha)") +
+  ggtitle("(1) Trial design") +
+  theme_figure
+```
+
+## Yield Map (Figure 3 Right)
+
+```{r, dependson = "setup"}
+# === subplot-level === #
+vis_yield_subplot <-
+  ggplot(field_subplot_sf) +
+  geom_sf(aes(fill = yield), size = 0) +
+  scale_fill_viridis_c() +
+  labs(fill = "Yield level\n  (kg/ha)") +
+  ggtitle("(2) Simulated yield level") +
+  theme_figure
+```
+
+## Field Characteristics Map (Appendix: Figure C.1)
+
+```{r, dependson = "setup"}
+# === alpha map === #
+field_alpha <-
+  ggplot(field_cell_sf) +
+  geom_sf(aes(fill = alpha), size = 0) +
+  scale_fill_viridis_c() +
+  ggtitle(expression("(1) " ~ alpha)) +
+  theme(legend.title = element_blank()) +
+  theme_figure
+
+# === beta map === #
+field_beta <-
+  ggplot(field_cell_sf) +
+  geom_sf(aes(fill = beta), size = 0) +
+  scale_fill_viridis_c() +
+  ggtitle(expression("(2) " ~ beta)) +
+  theme(legend.title = element_blank()) +
+  theme_figure
+
+# === ymax map === #
+field_ymax <-
+  ggplot(field_cell_sf) +
+  geom_sf(aes(fill = ymax), size = 0) +
+  scale_fill_viridis_c() +
+  ggtitle("(3) ymax (kg/ha)") +
+  theme(legend.title = element_blank()) +
+  theme_figure
+
+# === m_error map === #
+field_m_error <-
+  ggplot(field_cell_sf) +
+  geom_sf(aes(fill = yield_error), size = 0) +
+  scale_fill_viridis_c() +
+  ggtitle(expression(paste("(4) " ~ epsilon, " (kg/ha)"))) +
+  theme(legend.title = element_blank()) +
+  theme_figure
+
+# === optN map === #
+field_optN <-
+  ggplot(field_cell_sf) +
+  geom_sf(aes(fill = opt_N), size = 0) +
+  scale_fill_viridis_c() +
+  ggtitle("(5) EONR (kg/ha)") +
+  theme(legend.title = element_blank()) +
+  theme_figure
+```
+
+## Low and High Yield Error Maps (Appendix: Figure G.1)
+
+```{r}
+# === Low error field map === #
+field_cell_low_sf <-
+  here("Shared/Results/for_writing/sample_field_cell_low_sf.rds") %>%
+  readRDS()
+
+field_m_error_low <-
+  ggplot(field_cell_low_sf) +
+  geom_sf(aes(fill = yield_error), size = 0) +
+  scale_fill_viridis_c() +
+  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
+  ggtitle("(1) Low error") +
+  theme_figure
+
+# === High error field map === #
+field_cell_high_sf <-
+  here("Shared/Results/for_writing/sample_field_cell_high_sf.rds") %>%
+  readRDS()
+
+field_m_error_high <-
+  ggplot(field_cell_high_sf) +
+  geom_sf(aes(fill = yield_error), size = 0) +
+  scale_fill_viridis_c() +
+  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
+  ggtitle("(2) High error") +
+  theme_figure
+```
+
+# Simulation Results
+
+## Load the Results
+
+```{r source-results, message=FALSE, warning=FALSE, cache= FALSE}
+# === Load Results === #
+allML_summary_bySim <- readRDS(here("Shared/Results/for_writing/allML_summary_bySim.rds"))
+
+# === Set up === #
+res_y_train <-
+  allML_summary_bySim %>%
+  .[type == "train" & Method %in% c("RF", "BRF", "CNN")]
+
+res_y_test <-
+  allML_summary_bySim %>%
+  .[type == "test" & Method %in% c("RF", "BRF", "CNN")]
+```
+
+# Yield Prediction Results from the Main Simulations
+
+## Summary Table for RMSE of of Yield Prediction
+
+### on Training Datasets (Appendix: Table F.2)
+
+```{r, dependson = "source-results"}
+# /*===== On training datasets =====*/
+report_table_y_train <-
+  res_y_train %>%
+  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
+  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
+  dcast(Model ~ Method, value.var = "rmse_y") %>%
+  .[, CF_base := "-"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  flextable(.) %>%
+  set_header_labels(values = list(
+    Model = "Model",
+    RF = "RF",
+    BRF = "BRF",
+    CNN = "CNN",
+    CF_base = "CF-base"
+  )) %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  #- change the borders just for consistency with other figures -#
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  autofit()
+```
+
+### on Testing Datasets (Table 2)
+
+```{r, dependson = "source-results"}
+# --- on testing data sets--- #
+report_table_y <-
+  res_y_test %>%
+  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
+  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
+  dcast(Model ~ Method, value.var = "rmse_y") %>%
+  .[, CF_base := "-"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  flextable(.) %>%
+  set_header_labels(values = list(
+    Model = "Model",
+    RF = "RF",
+    BRF = "BRF",
+    CNN = "CNN",
+    CF_base = "CF-base"
+  )) %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  #- change the borders just for consistency with other figures -#
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  autofit()
+```
+
+## The Relationship between yield and EONR Prediction Performances under the aabbyytt scenario (Figure 8)
+
+```{r}
+sim_no <- c(10, 20, 30)
+
+vis_RMSE_y_eonr <-
+  res_y_test %>%
+  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
+  ggplot() +
+  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
+  scale_shape_manual(values = c(21, 23, 25)) +
+  ylim(NA, 95) +
+  labs(y = " RMSE of EONR Estimation (kg/ha)") +
+  labs(x = " RMSE of Yield Prediction (kg/ha)") +
+  theme_dist +
+  labs(fill = "Simulation Round", shape = "Method") +
+  guides(fill = guide_legend(override.aes = list(shape = 21))) +
+  theme(legend.position = "bottom", legend.box = "vertical", legend.margin = margin()) +
+  labs(fill = "Simulation Round", shape = "Method")
+```
+
+## True Yields without Error vs Predicted Yields (Appendix: Figure E.1)
+
+```{r}
+sample_simRes_test_y <- readRDS(here("Shared/Results/for_writing/sample_simRes_test_y.rds"))
+
+# === Function for RMSE Calculation === #
+rmse_general <- function(preds, actual) {
+  sqrt(mean((actual - preds)^2)) %>%
+    round(., 1) %>%
+    format(, nsmall = 1)
+}
+
+rmse <- sample_simRes_test_y %>%
+  .[, .(
+    rmse_y_det = rmse_general(pred_yield, det_yield),
+    rmse_y = rmse_general(pred_yield, yield)
+  ), by = .(Method, Model)]
+
+rmse <- sample_simRes_test_y %>%
+  .[, .(
+    rmse_y_det = paste0("RMSE = ", rmse_general(pred_yield, det_yield)),
+    rmse_y = paste0("RMSE = ", rmse_general(pred_yield, yield))
+  ), by = .(Method, Model)]
+
+vis_y_pred <-
+  ggplot(sample_simRes_test_y) +
+  geom_point(aes(x = det_yield, y = pred_yield), size = 0.5) +
+  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
+  geom_text(
+    data = rmse, aes(x = -Inf, y = +Inf, label = rmse_y_det),
+    hjust = -0.1, vjust = 3, size = 3.5, family = "Times New Roman"
+  ) +
+  facet_grid(Model ~ Method) +
+  guides(
+    fill = guide_legend(keywidth = 1, keyheight = 1),
+    linetype = guide_legend(keywidth = 3, keyheight = 1),
+    colour = guide_legend(keywidth = 3, keyheight = 1)
+  ) +
+  labs(y = "Predicted Yield (kg/ha)") +
+  labs(x = "True Yield without error (kg/ha)") +
+  theme_dist
+```
+
+## Yield Prediction vs EONR estimation : Count Table in terms of profit loss (Table 3)
+
+```{r, dependson = "source-results"}
+# === Preparation === #
+prepare_count_tab <-
+  res_y_test %>%
+  dcast(sim + Model ~ Method, value.var = c("pi_loss", "rmse_y")) %>%
+  .[, which_ML_y := case_when(
+    rmse_y_BRF < rmse_y_RF & rmse_y_BRF < rmse_y_CNN ~ "BRF",
+    rmse_y_RF < rmse_y_BRF & rmse_y_RF < rmse_y_CNN ~ "RF",
+    rmse_y_CNN < rmse_y_BRF & rmse_y_CNN < rmse_y_RF ~ "CNN"
+  )] %>%
+  .[, which_ML_piLoss := case_when(
+    pi_loss_BRF < pi_loss_RF & pi_loss_BRF < pi_loss_CNN ~ "BRF",
+    pi_loss_RF < pi_loss_BRF & pi_loss_RF < pi_loss_CNN ~ "RF",
+    pi_loss_CNN < pi_loss_BRF & pi_loss_CNN < pi_loss_RF ~ "CNN"
+  )] %>%
+  .[, index_cnst_y_piLoss := ifelse(which_ML_piLoss == which_ML_y, 1, 0)] %>%
+  .[, ML_cnst_y_piLoss := ifelse(index_cnst_y_piLoss == 1, which_ML_piLoss, NA)]
+
+# === Summary Table === #
+summary_res_CNN_RF_BRF <-
+  prepare_count_tab %>%
+  .[, .(
+    count_BRF = nrow(.SD[ML_cnst_y_piLoss == "BRF", ]),
+    count_RF = nrow(.SD[ML_cnst_y_piLoss == "RF", ]),
+    count_CNN = nrow(.SD[ML_cnst_y_piLoss == "CNN", ]),
+    count_y_BRF = nrow(.SD[which_ML_y == "BRF", ]),
+    count_y_RF = nrow(.SD[which_ML_y == "RF", ]),
+    count_y_CNN = nrow(.SD[which_ML_y == "CNN", ]),
+    Total = sum(index_cnst_y_piLoss)
+  ), by = Model] %>%
+  .[, `:=`(
+    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
+  )] %>%
+  .[, .(Model, blank1, count_y_RF, count_RF, blank2, count_y_BRF, count_BRF, blank3, count_y_CNN, count_CNN, blank4, Total)]
+
+# === Table creation === #
+report_summary_res_CNN_RF_BRF <-
+  summary_res_CNN_RF_BRF %>%
+  flextable(.) %>%
+  border_remove() %>%
+  delete_part(part = "header") %>%
+  add_header(
+    Model = "Model",
+    blank1 = "", count_y_RF = "RF", count_RF = "RF",
+    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
+    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
+    blank4 = "", Total = "Total #YP",
+    top = TRUE
+  ) %>%
+  merge_h(part = "header") %>%
+  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
+  add_header(
+    Model = "",
+    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
+    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
+    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
+    blank4 = "", Total = "",
+    top = FALSE
+  ) %>%
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  footnote(
+    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction.
+#YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
+    ref_symbols = NA
+  ) %>%
+  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
+  autofit() %>%
+  width(j = c(3:4, 6:7, 9:10), width = 0.6) %>%
+  width(j = 12, width = 0.82) %>%
+  width(j = 1, width = 0.8) %>%
+  width(j = c(2, 5, 8, 11), width = 0.1)
+```
+
+# EONR Estimation from the Main Simulations
+
+## Distributions of RMSE of EONR estimation over simulations (Figure 4)
+
+```{r, dependson = "source-results"}
+# /*----------------------------------*/
+#' ## Distribution of RMSE of EONR estimates
+# /*----------------------------------*/
+plot_dis_optN <-
+  allML_summary_bySim %>%
+  .[type == "test", ] %>%
+  # .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
+  .[Method == "CF_base", Method := "CF-base"] %>%
+  .[, Model := case_when(
+    Model == "aby" ~ "Scenario: aby",
+    Model == "abytt" ~ "Scenario: abytt",
+    Model == "aabbyy" ~ "Scenario: aabbyy",
+    Model == "aabbyytt" ~ "Scenario: aabbyytt"
+  )] %>%
+  .[, Model := factor(Model,
+    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
+  )] %>%
+  ggplot() +
+  geom_density(aes(x = rmse_optN, fill = Method), alpha = 0.7) +
+  facet_wrap(~Model, ncol = 1) +
+  labs(x = "RMSE (kg/ha)") +
+  theme_dist
+
+```
+
+## Summary Table for RMSE of EONR estimation
+
+### on Training Datasets (Appendix: Table F.1)
+
+```{r, dependson = "source-results"}
+# /*----------------------------------*/
+#' ## Summary Table
+# /*----------------------------------*/
+# === Preparation === #
+table_optN_prep <-
+  allML_summary_bySim %>%
+  .[, .(
+    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
+    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
+  ), by = .(type, Method, Model)] %>%
+  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
+  .[, `:=`(
+    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA, blank5 = NA
+  )] %>%
+  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]
+
+# === Summary Table (Training Data sets) === #
+report_table_optN_train <-
+  table_optN_prep %>%
+  .[type == "train", !"type"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  # add_row(.after = 4) %>%
+  flextable(.) %>%
+  border_remove() %>%
+  delete_part(part = "header") %>%
+  add_header(
+    Model = "Model",
+    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
+    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
+    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
+    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
+    top = TRUE
+  ) %>%
+  merge_h(part = "header") %>%
+  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
+  add_header(
+    Model = "",
+    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
+    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
+    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
+    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
+    top = FALSE
+  ) %>%
+  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  # autofit() %>%
+  # width(j = c(2,5,8,11), width=0.3) %>%
+  # fix_border_issues()
+  footnote(
+    # i = 1, j = c(4, 7, 10, 13), part = "header",
+    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
+    ref_symbols = NA
+  ) %>%
+  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
+  autofit() %>%
+  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
+  width(j = c(2, 5, 8, 11), width = 0.1)
+
+```
+
+### on Testing Datasets (Table 1)
+
+```{r, dependson = "source-results"}
+# === Summary Table (Testing Data sets) === #
+report_table_optN <-
+  table_optN_prep %>%
+  .[type == "test", !"type"] %>%
+  mutate(
+    across(
+      everything(),
+      as.character
+    )
+  ) %>%
+  # add_row(.after = 4) %>%
+  flextable(.) %>%
+  border_remove() %>%
+  delete_part(part = "header") %>%
+  add_header(
+    Model = "Model",
+    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
+    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
+    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
+    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
+    top = TRUE
+  ) %>%
+  merge_h(part = "header") %>%
+  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
+  add_header(
+    Model = "",
+    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
+    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
+    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
+    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
+    top = FALSE
+  ) %>%
+  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
+  hline_bottom(part = "all") %>%
+  hline_top(part = "header") %>%
+  align(align = "center", part = "all") %>%
+  align(j = 1, align = "left", part = "all") %>%
+  # autofit() %>%
+  # width(j = c(2,5,8,11), width=0.3) %>%
+  # fix_border_issues()
+  footnote(
+    # i = 1, j = c(4, 7, 10, 13), part = "header",
+    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
+    ref_symbols = NA
+  ) %>%
+  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
+  autofit() %>%
+  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
+  width(j = c(2, 5, 8, 11), width = 0.1)
+```
+
+## Distributions of profit deficit over simulations (Figure 5)
+
+```{r}
+piLoss_density <-
+  allML_summary_bySim %>%
+  .[type == "test", ] %>%
+  .[Method == "CF_base", Method := "CF-base"] %>%
+  .[, Model := case_when(
+    Model == "aby" ~ "Scenario: aby",
+    Model == "abytt" ~ "Scenario: abytt",
+    Model == "aabbyy" ~ "Scenario: aabbyy",
+    Model == "aabbyytt" ~ "Scenario: aabbyytt"
+  )] %>%
+  .[, Model := factor(Model,
+    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
+  )] %>%
+  ggplot() +
+  geom_density(aes(x = pi_loss, fill = Method), alpha = 0.7) +
+  labs(x = expression(paste(hat(pi)[italic("def")], " ($/ha)"))) +
+  facet_wrap(~Model, ncol = 1) +
+  theme_dist
+```
+
+## Treatment effect comparison (Figure 6)
+
+```{r}
+figure_te <-
+  here("Shared/Results/for_writing/dt_TEcomparison.rds") %>%
+  readRDS() %>%
+  .[Method == "CF_base", Method := "CF-base"] %>%
+  ggplot() +
+  geom_point(aes(x = true_te_base, y = te_base), size = 0.5) +
+  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
+  facet_grid(Treatment ~ Method) +
+  guides(
+    fill = guide_legend(keywidth = 1, keyheight = 1),
+    linetype = guide_legend(keywidth = 3, keyheight = 1),
+    colour = guide_legend(keywidth = 3, keyheight = 1)
+  ) +
+  labs(y = "Estimated Treatment Effect (kg/ha)") +
+  labs(x = "True Treatment Effect (kg/ha)") +
+  theme_dist
+```
+
+# Appendix
+
+## Variogram Prameter Table (Appendix: Table C.1)
 
@@
 
-# Field Maps
-
-## Division of field: plots, subplots and cells (Visualization)
-
-```{r field-map-visualization, dependson = "setup"}
-
-# === Preparation === #
-ex_plot <- field_plot_sf[224, ]
-ex_subplots <- field_subplot_sf[ex_plot, , op = st_within]
-
-ex_one_subplot <- ex_subplots[1, ]
-ex_cells <- field_cell_sf[ex_one_subplot, , op = st_within]
-
-one_subplot <- ex_subplots[3, ]
-
-#-- (1) plot-level field map  --#
-
-plot <-
-  ggplot() +
-  geom_sf(data = field_plot_sf) +
-  geom_sf(data = ex_plot, fill = "green", size = 1) +
-  coord_sf(expand = FALSE) +
-  # theme_void() +
-  ggtitle("12 \u00D7 32 plots") +
-  theme_figure
-
-grob_plot <- ggplotGrob(plot)
-
-#-- (2) create a map of subplots in a plot --##
-subplots_inPlot <-
-  ggplot() +
-  geom_sf(data = ex_plot, fill = "green") +
-  geom_sf(data = ex_subplots, fill = NA, size = 1) +
-  geom_sf(data = ex_subplots[2, ], fill = "skyblue", size = 1) +
-  coord_sf(expand = FALSE) +
-  # theme_void() +
-  ggtitle("4 \u00D7 1 subplots") +
-  theme_figure
-
-grob_subplots_inPlot <- ggplotGrob(subplots_inPlot)
-
-#-- (3) create a map of cells in a subplot --#
-cells_inSubplot <-
-  ggplot() +
-  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
-  geom_sf(data = ex_cells, fill = NA) +
-  geom_sf(data = ex_cells[2, ], fill = "skyblue", size = 1) +
-  coord_sf(expand = FALSE) +
-  # theme_void() +
-  ggtitle("6 \u00D7 6 cells") +
-  theme_figure
-
-grob_cells_inSubplot <- ggplotGrob(cells_inSubplot)
-
-#-- (4)put them on the same map --#
-field_structure <-
-  ggplot() +
-  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
-  # /*----------------------------------*/
-  #' ##  base maps
-  # /*----------------------------------*/
-  # --- plot level --- #
-  annotation_custom(grob_plot,
-    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1
-  ) +
-  # --- subplot level --- #
-  annotation_custom(grob_subplots_inPlot,
-    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7
-  ) +
-  # --- cell level --- #
-  annotation_custom(grob_cells_inSubplot,
-    xmin = 0.8, xmax = 0.8 + 0.2, ymin = 0.382, ymax = 0.382 + 0.2
-  ) +
-  # /*----------------------------------*/
-  #' ## Add braces
-  # /*----------------------------------*/
-  # --- between plot and subplot --- #
-  geom_brace(aes(c(0.43, 0.43 + 0.1), c(0.372 - 0.004, 0.645 + 0.013)), color = "red", rotate = 270, inherit.data = F) +
-  # --- between subplot and cell --- #
-  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.401 - 0.002, 0.529 + 0.011)), color = "red", rotate = 270, inherit.data = F) +
-  # /*----------------------------------*/
-  #' ## add annotations
-  # /*----------------------------------*/
-  # --- annotation for plot --- #
-  geom_segment(aes(x = 0.42, xend = 0.383, y = 0.60, yend = 0.52),
-    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
-  ) +
-  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.02, label = "plot", family = "Times New Roman") +
-  # --- annotation for subplot --- #
-  geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
-    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
-  ) +
-  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot", , family = "Times New Roman") +
-  # --- annotation for cell --- #
-  geom_segment(aes(x = 0.9, xend = 0.87, y = 0.365, yend = 0.41),
-    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
-  ) +
-  annotate("text", x = 0.9 + 0.02, y = 0.365 - 0.005, label = "cell", , family = "Times New Roman") +
-  theme_void()
-```
-
-# Distribution Map of Field Characteristics
-
-## Experimental N design
-
-```{r, dependson = "setup"}
-field_Ndesign <-
-  ggplot() +
-  geom_sf(
-    data = field_plot_sf,
-    aes(fill = factor(rate)), size = 0,
-    inherit.aes = FALSE,
-  ) +
-  scale_fill_viridis_d() +
-  labs(fill = "Nitrogen rate\n  (kg/ha)") +
-  ggtitle("(1) Trial design") +
-  theme_figure
-```
-
-## Yield map
-
-```{r, dependson = "setup"}
-# === subplot-level === #
-vis_yield_subplot <-
-  ggplot(field_subplot_sf) +
-  geom_sf(aes(fill = yield), size = 0) +
-  scale_fill_viridis_c() +
-  labs(fill = "Yield level\n  (kg/ha)") +
-  ggtitle("(2) Simulated yield level") +
-  theme_figure
-```
-
-## opt_N map
-
-```{r, dependson = "setup"}
-
-```
-
-## Field Characteristics Map
-
-```{r, dependson = "setup"}
-# === alpha map === #
-field_alpha <-
-  ggplot(field_cell_sf) +
-  geom_sf(aes(fill = alpha), size = 0) +
-  scale_fill_viridis_c() +
-  ggtitle(expression("(1) " ~ alpha)) +
-  theme(legend.title = element_blank()) +
-  theme_figure
-
-# === beta map === #
-field_beta <-
-  ggplot(field_cell_sf) +
-  geom_sf(aes(fill = beta), size = 0) +
-  scale_fill_viridis_c() +
-  ggtitle(expression("(2) " ~ beta)) +
-  theme(legend.title = element_blank()) +
-  theme_figure
-
-# === ymax map === #
-field_ymax <-
-  ggplot(field_cell_sf) +
-  geom_sf(aes(fill = ymax), size = 0) +
-  scale_fill_viridis_c() +
-  ggtitle("(3) ymax (kg/ha)") +
-  theme(legend.title = element_blank()) +
-  theme_figure
-
-# === m_error map === #
-field_m_error <-
-  ggplot(field_cell_sf) +
-  geom_sf(aes(fill = yield_error), size = 0) +
-  scale_fill_viridis_c() +
-  ggtitle(expression(paste("(4) " ~ epsilon, " (kg/ha)"))) +
-  theme(legend.title = element_blank()) +
-  theme_figure
-
-# === optN map === #
-field_optN <-
-  ggplot(field_cell_sf) +
-  geom_sf(aes(fill = opt_N), size = 0) +
-  scale_fill_viridis_c() +
-  ggtitle("(5) EONR (kg/ha)") +
-  theme(legend.title = element_blank()) +
-  theme_figure
-```
-
-```{r}
-# === Low error field map === #
-field_cell_low_sf <-
-  here("Shared/Results/for_writing/sample_field_cell_low_sf.rds") %>%
-  readRDS()
-
-field_m_error_low <-
-  ggplot(field_cell_low_sf) +
-  geom_sf(aes(fill = yield_error), size = 0) +
-  scale_fill_viridis_c() +
-  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
-  ggtitle("(1) Low error") +
-  theme_figure
-
-# === High error field map === #
-field_cell_high_sf <-
-  here("Shared/Results/for_writing/sample_field_cell_high_sf.rds") %>%
-  readRDS()
-
-field_m_error_high <-
-  ggplot(field_cell_high_sf) +
-  geom_sf(aes(fill = yield_error), size = 0) +
-  scale_fill_viridis_c() +
-  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
-  ggtitle("(2) High error") +
-  theme_figure
-```
-
-# Results
-
-## Source Results
-
-```{r source-results, message=FALSE, warning=FALSE, cache= FALSE}
-# === Load Results === #
-allML_summary_bySim <- readRDS(here("Shared/Results/for_writing/allML_summary_bySim.rds"))
-
-# === Set up === #
-res_y_train <-
-  allML_summary_bySim %>%
-  .[type == "train" & Method %in% c("RF", "BRF", "CNN")]
-
-res_y_test <-
-  allML_summary_bySim %>%
-  .[type == "test" & Method %in% c("RF", "BRF", "CNN")]
-```
-
-# Yield prediction results
-
-## Report RMSE of of Yield Prediction (RF, BRF, CNN)
-
-```{r, dependson = "source-results"}
-# ==== Summary Table ====#
-# --- on training data sets--- #
-report_table_y_train <-
-  res_y_train %>%
-  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
-  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
-  dcast(Model ~ Method, value.var = "rmse_y") %>%
-  .[, CF_base := "-"] %>%
-  mutate(
-    across(
-      everything(),
-      as.character
-    )
-  ) %>%
-  flextable(.) %>%
-  set_header_labels(values = list(
-    Model = "Model",
-    RF = "RF",
-    BRF = "BRF",
-    CNN = "CNN",
-    CF_base = "CF-base"
-  )) %>%
-  align(align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  #- change the borders just for consistency with other figures -#
-  hline_bottom(part = "all") %>%
-  hline_top(part = "header") %>%
-  autofit()
-
-# --- on testing data sets--- #
-report_table_y <-
-  res_y_test %>%
-  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
-  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
-  dcast(Model ~ Method, value.var = "rmse_y") %>%
-  .[, CF_base := "-"] %>%
-  mutate(
-    across(
-      everything(),
-      as.character
-    )
-  ) %>%
-  flextable(.) %>%
-  set_header_labels(values = list(
-    Model = "Model",
-    RF = "RF",
-    BRF = "BRF",
-    CNN = "CNN",
-    CF_base = "CF-base"
-  )) %>%
-  align(align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  #- change the borders just for consistency with other figures -#
-  hline_bottom(part = "all") %>%
-  hline_top(part = "header") %>%
-  autofit()
-```
-
-## Figure (RMSE of EONR vs RMSE of yield for RF and BRF)
-
-```{r}
-# fig_y_optN <-
-# res_y_test %>%
-# .[Method %in% c("RF", "BRF", "CNN")] %>%
-# ggplot(aes(x = rmse_y, y = rmse_optN)) +
-# geom_point(size = 0.5) +
-# facet_grid(Model ~ Method) +
-# geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
-# stat_regline_equation(
-#   label.x = 2050, label.y = 90,
-#   aes(label = ..rr.label..),
-#   size = 3
-# ) +
-# guides(
-#   fill = guide_legend(keywidth = 1, keyheight = 1),
-#   linetype = guide_legend(keywidth = 3, keyheight = 1),
-#   colour = guide_legend(keywidth = 3, keyheight = 1)
-# ) +
-# ylim(NA, 95) +
-# labs(y = " RMSE of EONR Estimation (kg/ha)") +
-# labs(x = " RMSE of Yield Prediction (kg/ha)") +
-# theme_dist
-```
-
-```{r}
-# sim_no <- c(300, 600, 900)
-sim_no <- c(10, 20, 30)
-
-vis_RMSE_y_eonr <-
-  res_y_test %>%
-  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
-  ggplot() +
-  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
-  scale_shape_manual(values = c(21, 23, 25)) +
-  ylim(NA, 95) +
-  labs(y = " RMSE of EONR Estimation (kg/ha)") +
-  labs(x = " RMSE of Yield Prediction (kg/ha)") +
-  theme_dist +
-  labs(fill = "Simulation Round", shape = "Method") +
-  guides(fill = guide_legend(override.aes = list(shape = 21))) +
-  # guides(fill=guide_legend(nrow=2, byrow=TRUE)) +
-  # guides(shape=guide_legend(nrow=2, byrow=TRUE)) +
-  theme(legend.position = "bottom", legend.box = "vertical", legend.margin = margin()) +
-  labs(fill = "Simulation Round", shape = "Method")
-```
-
-## True Yields vs Predicted Yields by models
-+ for comment 7
-+ a figure plots true yields (without error, epsilon) against predicted yields by model (without CF of course) for a single simulation round with RMSE printed for each model.
-
-```{r}
-sample_simRes_test_y <- readRDS(here("Shared/Results/for_writing/sample_simRes_test_y.rds"))
-
-# === Function for RMSE Calculation === #
-rmse_general <- function(preds, actual) {
-  sqrt(mean((actual - preds)^2)) %>%
-    round(., 1) %>%
-    format(, nsmall = 1)
-}
-
-rmse <- sample_simRes_test_y %>%
-  .[, .(
-    rmse_y_det = rmse_general(pred_yield, det_yield),
-    rmse_y = rmse_general(pred_yield, yield)
-  ), by = .(Method, Model)]
-
-rmse <- sample_simRes_test_y %>%
-  .[, .(
-    rmse_y_det = paste0("RMSE = ", rmse_general(pred_yield, det_yield)),
-    rmse_y = paste0("RMSE = ", rmse_general(pred_yield, yield))
-  ), by = .(Method, Model)]
-
-vis_y_pred <-
-  ggplot(sample_simRes_test_y) +
-  geom_point(aes(x = det_yield, y = pred_yield), size = 0.5) +
-  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
-  geom_text(
-    data = rmse, aes(x = -Inf, y = +Inf, label = rmse_y_det),
-    hjust = -0.1, vjust = 3, size = 3.5, family = "Times New Roman"
-  ) +
-  facet_grid(Model ~ Method) +
-  guides(
-    fill = guide_legend(keywidth = 1, keyheight = 1),
-    linetype = guide_legend(keywidth = 3, keyheight = 1),
-    colour = guide_legend(keywidth = 3, keyheight = 1)
-  ) +
-  labs(y = "Predicted Yield (kg/ha)") +
-  labs(x = "True Yield without error (kg/ha)") +
-  theme_dist
-```
-
-## Yield Prediction vs EONR estimation : Count Table in terms of profit loss
-
-```{r, dependson = "source-results"}
-# === Preparation === #
-prepare_count_tab <-
-  res_y_test %>%
-  dcast(sim + Model ~ Method, value.var = c("pi_loss", "rmse_y")) %>%
-  .[, which_ML_y := case_when(
-    rmse_y_BRF < rmse_y_RF & rmse_y_BRF < rmse_y_CNN ~ "BRF",
-    rmse_y_RF < rmse_y_BRF & rmse_y_RF < rmse_y_CNN ~ "RF",
-    rmse_y_CNN < rmse_y_BRF & rmse_y_CNN < rmse_y_RF ~ "CNN"
-  )] %>%
-  .[, which_ML_piLoss := case_when(
-    pi_loss_BRF < pi_loss_RF & pi_loss_BRF < pi_loss_CNN ~ "BRF",
-    pi_loss_RF < pi_loss_BRF & pi_loss_RF < pi_loss_CNN ~ "RF",
-    pi_loss_CNN < pi_loss_BRF & pi_loss_CNN < pi_loss_RF ~ "CNN"
-  )] %>%
-  .[, index_cnst_y_piLoss := ifelse(which_ML_piLoss == which_ML_y, 1, 0)] %>%
-  .[, ML_cnst_y_piLoss := ifelse(index_cnst_y_piLoss == 1, which_ML_piLoss, NA)]
-
-# === Summary Table === #
-summary_res_CNN_RF_BRF <-
-  prepare_count_tab %>%
-  .[, .(
-    count_BRF = nrow(.SD[ML_cnst_y_piLoss == "BRF", ]),
-    count_RF = nrow(.SD[ML_cnst_y_piLoss == "RF", ]),
-    count_CNN = nrow(.SD[ML_cnst_y_piLoss == "CNN", ]),
-    count_y_BRF = nrow(.SD[which_ML_y == "BRF", ]),
-    count_y_RF = nrow(.SD[which_ML_y == "RF", ]),
-    count_y_CNN = nrow(.SD[which_ML_y == "CNN", ]),
-    Total = sum(index_cnst_y_piLoss)
-  ), by = Model] %>%
-  .[, `:=`(
-    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
-  )] %>%
-  .[, .(Model, blank1, count_y_RF, count_RF, blank2, count_y_BRF, count_BRF, blank3, count_y_CNN, count_CNN, blank4, Total)]
-
-# === Table creation === #
-report_summary_res_CNN_RF_BRF <-
-  summary_res_CNN_RF_BRF %>%
-  flextable(.) %>%
-  border_remove() %>%
-  delete_part(part = "header") %>%
-  add_header(
-    Model = "Model",
-    blank1 = "", count_y_RF = "RF", count_RF = "RF",
-    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
-    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
-    blank4 = "", Total = "Total #YP",
-    top = TRUE
-  ) %>%
-  merge_h(part = "header") %>%
-  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
-  add_header(
-    Model = "",
-    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
-    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
-    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
-    blank4 = "", Total = "",
-    top = FALSE
-  ) %>%
-  hline_bottom(part = "all") %>%
-  hline_top(part = "header") %>%
-  align(align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  footnote(
-    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction.
-#YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
-    ref_symbols = NA
-  ) %>%
-  # set_table_properties(width = .7, layout = "autofit") %>%
-  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
-  autofit() %>%
-  width(j = c(3:4, 6:7, 9:10), width = 0.6) %>%
-  width(j = 12, width = 0.82) %>%
-  width(j = 1, width = 0.8) %>%
-  width(j = c(2, 5, 8, 11), width = 0.1)
-```
-
-# EONR Estimation
-
-```{r, dependson = "source-results"}
-# /*----------------------------------*/
-#' ## Distribution of RMSE of EONR estimates
-# /*----------------------------------*/
-plot_dis_optN <-
-  allML_summary_bySim %>%
-  .[type == "test", ] %>%
-  # .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
-  .[Method == "CF_base", Method := "CF-base"] %>%
-  .[, Model := case_when(
-    Model == "aby" ~ "Scenario: aby",
-    Model == "abytt" ~ "Scenario: abytt",
-    Model == "aabbyy" ~ "Scenario: aabbyy",
-    Model == "aabbyytt" ~ "Scenario: aabbyytt"
-  )] %>%
-  .[, Model := factor(Model,
-    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
-  )] %>%
-  ggplot() +
-  geom_density(aes(x = rmse_optN, fill = Method), alpha = 0.7) +
-  facet_wrap(~Model, ncol = 1) +
-  labs(x = "RMSE (kg/ha)") +
-  theme_dist
-
-# /*----------------------------------*/
-#' ## Summary Table
-# /*----------------------------------*/
-# === Preparation === #
-table_optN_prep <-
-  allML_summary_bySim %>%
-  .[, .(
-    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
-    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
-  ), by = .(type, Method, Model)] %>%
-  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
-  .[, `:=`(
-    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA, blank5 = NA
-  )] %>%
-  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]
-
-# === Summary Table (Training Data sets) === #
-report_table_optN_train <-
-  table_optN_prep %>%
-  .[type == "train", !"type"] %>%
-  mutate(
-    across(
-      everything(),
-      as.character
-    )
-  ) %>%
-  # add_row(.after = 4) %>%
-  flextable(.) %>%
-  border_remove() %>%
-  delete_part(part = "header") %>%
-  add_header(
-    Model = "Model",
-    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
-    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
-    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
-    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
-    top = TRUE
-  ) %>%
-  merge_h(part = "header") %>%
-  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
-  add_header(
-    Model = "",
-    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
-    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
-    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
-    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
-    top = FALSE
-  ) %>%
-  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
-  hline_bottom(part = "all") %>%
-  hline_top(part = "header") %>%
-  align(align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  # autofit() %>%
-  # width(j = c(2,5,8,11), width=0.3) %>%
-  # fix_border_issues()
-  footnote(
-    # i = 1, j = c(4, 7, 10, 13), part = "header",
-    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
-The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
-    ref_symbols = NA
-  ) %>%
-  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
-  autofit() %>%
-  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
-  width(j = c(2, 5, 8, 11), width = 0.1)
-
-# === Summary Table (Testing Data sets) === #
-report_table_optN <-
-  table_optN_prep %>%
-  .[type == "test", !"type"] %>%
-  mutate(
-    across(
-      everything(),
-      as.character
-    )
-  ) %>%
-  # add_row(.after = 4) %>%
-  flextable(.) %>%
-  border_remove() %>%
-  delete_part(part = "header") %>%
-  add_header(
-    Model = "Model",
-    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
-    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
-    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
-    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
-    top = TRUE
-  ) %>%
-  merge_h(part = "header") %>%
-  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
-  add_header(
-    Model = "",
-    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
-    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
-    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
-    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
-    top = FALSE
-  ) %>%
-  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
-  hline_bottom(part = "all") %>%
-  hline_top(part = "header") %>%
-  align(align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  # autofit() %>%
-  # width(j = c(2,5,8,11), width=0.3) %>%
-  # fix_border_issues()
-  footnote(
-    # i = 1, j = c(4, 7, 10, 13), part = "header",
-    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
-The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
-    ref_symbols = NA
-  ) %>%
-  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
-  autofit() %>%
-  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
-  width(j = c(2, 5, 8, 11), width = 0.1)
-```
-
-# Profit Loss
-
-## Profit loss summary and distributions
-```{r}
-piLoss_density <-
-  allML_summary_bySim %>%
-  .[type == "test", ] %>%
-  .[Method == "CF_base", Method := "CF-base"] %>%
-  .[, Model := case_when(
-    Model == "aby" ~ "Scenario: aby",
-    Model == "abytt" ~ "Scenario: abytt",
-    Model == "aabbyy" ~ "Scenario: aabbyy",
-    Model == "aabbyytt" ~ "Scenario: aabbyytt"
-  )] %>%
-  .[, Model := factor(Model,
-    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
-  )] %>%
-  ggplot() +
-  geom_density(aes(x = pi_loss, fill = Method), alpha = 0.7) +
-  labs(x = expression(paste(hat(pi)[italic("def")], " ($/ha)"))) +
-  facet_wrap(~Model, ncol = 1) +
-  theme_dist
-```
-
-# Treatment effect comparison
-
-```{r}
-figure_te <-
-  here("Shared/Results/for_writing/dt_TEcomparison.rds") %>%
-  readRDS() %>%
-  .[Method == "CF_base", Method := "CF-base"] %>%
-  ggplot() +
-  geom_point(aes(x = true_te_base, y = te_base), size = 0.5) +
-  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
-  facet_grid(Treatment ~ Method) +
-  guides(
-    fill = guide_legend(keywidth = 1, keyheight = 1),
-    linetype = guide_legend(keywidth = 3, keyheight = 1),
-    colour = guide_legend(keywidth = 3, keyheight = 1)
-  ) +
-  labs(y = "Estimated Treatment Effect (kg/ha)") +
-  labs(x = "True Treatment Effect (kg/ha)") +
-  theme_dist
-```
-
-# An Example of a Causal Tree
+## An Example of a Causal Tree (Appendix: Figure A.1)
 
@@
 
-# Various Error Size (Appendix)
-
-## EONR Estimation
+## Various Error Size - EONR Estimation (Appendix: Table G.1)
 
@@
 
-## Yield Prediction
+## Various Error Size - Yield Prediction (Appendix: Table G.2)
 

### 2022-04-19 Writing/CEA_3rd_round/replies_rev.rmd
large updates for 3rd round submission

@@
 
-We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version.
+Thank you for your comments.
+In response to them, we made significant changes that greatly clarified our explanation in section 4.2 of why predicting yield levels well at the observed points need not imply accurate prediction of EONRs.
+Below, please find your comments in black and our replies in blue.
+
+<!-- We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version.
 This round of revision turned out to be much more important than the previous one.
@@
 Thank you so much for making this article better together with us.
-We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well.
-Below, you find your comments in black and our replies in blue.
-
-<!-- We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version.
-One of your comments was particularity important and we were able to correct our mistake before this paper is published.
-So, thank you so much.
 We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well.
@@
 <span style="color:blue"> 
-Please see Figure D.1 in Appendix D that shows the convergence of CNN for a single simulation round.
-We cannot show this kind of figure for all the simulation rounds.
-But, any interested readers can replicate our work as the codes will be accessible publicly.
+Please see Figure D.1 in Appendix D, which shows the convergence of CNN for a single simulation round.
+We cannot show this kind of figure for all the simulation rounds, but any interested readers can replicate our work as the codes will be publicly accessible.
 Please also see the figure below.
 CNN severely underestimates the impact of N and estimated yield response to N is almost flat, but not exactly flat.
+</span>
+
 <!-- Please see the figure below showing some examples of yield response function estimated by CNN under "aabbyytt" modeling scenario.
@@
 
-</span>
-
 <br>
@@
 <span style="color:blue">  
-We are not saying EOIR cannot be estimated by studies mentioned in 28ff.
-Indeed, any methods can "estimate" EOIR.
-However, no method can estimate the "true" EONR and we will "never" know true EONRs for real fields.
-We can only estimate them.
+We are not saying that the studies mentioned in 28ff did not estimate EOIRs.
+However, "true" EONRs on real fields and sites cannot be known with certainty, but can only be estimated.
 This principle is at the core of statistical analysis.
-We never observe how data is generated (the underlying laws that govern how the world works whether it is physical, biological, or economic), but we can "estimate" (approximate) what they look like.
+We never observe the underlying laws that govern how the world works but we can "estimate" those processes.
 This means that when we try to evaluate how different models perform in predicting EONR using real data, we simply do not have a valid benchmark to compare against.
-Some may ask, then why don't we use models' yield prediction ability because yield is observable.
+Some may ask, then why don't we use models' yield prediction ability because yield is observable?
 And this is precisely the dangerous practice that we show can be harmful.
@@
 However, that is not the case for EOIR.
-This is why you need MC simulations where the data generating process (how yield responds to N, and how field characteristics affect yield response to N) is "known" to the researcher.
-This way, we can test model's ability to predict EONR, not yield.
-Any journal article that proposes a new statistical method always accompany the theory of why their method works (consistency of their estimation, etc) with MC simulations where the researchers determines how data is generated and apply their method.
+This is why MC simulations are needed for which the underlying data generating process (how yield responds to N, and how field characteristics affect yield response to N) is "known" to the researcher.
+This way, we can test a model's ability to predict EONR, not yield.
+This approach is commonly used in statistical journals when new statistical methods are proposed.
 This is because we can never test the statistical property of a statistical method in principle using the real data.
 For example, please see @Wager2018a and @oprescu2019orthogonal.
-
 </span>
@@
 <span style="color:blue">  
-Fields studies were used to obtain the plausible range of optimal EONR and the size of error. 
+Some of the authors have significant experience designing, conducting and analyzing hundreds of on-farm precision experiments.
+The general results of those experiments provided plausible ranges of the optimal EONR and error size.
 </span>
@@
 <span style="color:blue">  
-
-We actually realized the results presented in Figure 6 (in the previous round) is completely invalid.
-As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges: comparing across simulation rounds.
-Figure 8 plots RMSE of yield and EONR predictions by model and simulation round for several simulation rounds.
-Figure 6 in the previous round was basically mixing RMSE from all the simulation rounds and finding $R^2$ of the two relationship.
+We agree that the results presented in Figure 6 of the previous manuscript were invalid and basically compared apples and oranges.
+The figure was mixing RMSEs from all the simulation rounds and finding the $R^2$ of the two relationships.
 That is why $R^2$ was extremely low.
 Therefore, we decided to remove the figure entirely.
-Also, we no longer claim that yield and EONR predictions are not correlated at all as we realized that it is false.
-Thank you so much for saving us from claiming the false statement.
-We conducted simulations with different degrees of error according to your suggestion.
+Also, we no longer make the claim that yield and EONR predictions are completely uncorrelated.
+Thank you for the heads-up.
+Figure 8 of the revised manuscript plots RMSE of yield and EONR predictions by model and simulation round for several simulation rounds (simulation round 10, 20, and 30).
+
+In addition, we followed your suggestion to conduct simulations with different degrees of error.
 **The results are shown in Appendix G**.
-By looking at Tables 1, 3, G.1, and G.3, you can see that as the error size decreases, both yield and EONR RMSEs decrease.
-So, in this sense, yield and EONR predictions are indeed correlated as expected.
+Examination of Tables 1, 2, G.1, and G.2 reveals that as the error size decreases, both yield and EONR RMSEs decrease.
+So, in this sense, yield and EONR predictions were indeed correlated, as expected.
 
-However, our claim that the models with the highest yield prediction power is not necessarily the best EONR prediciton (or the most profitable) model remains valid.
+We maintain in the revised manuscript our claim that the models with the highest yield prediction power need not provide the best (or the most profitable) EONR prediction.
 Please note that this claim comes from comparisons **across the models** given the **same** dataset (so the same errors).
-Since we consider this a very important point for researchers in this field, we now provide much more in-depth discussions about why that is the case under section 4.2.
+Since we consider this a very important point for researchers in this field, in the revised manuscript's section 4.2 we provide a more in-depth discussion.
 As you suggested, models that can recover the "structure" of the yield response function will perform well in predicting EONR.
-However, you can predict yield levels at the observed rates (rates that are actually applied in the experiment) without recovering the structure of the yield response function well (predicting yield levels well for wrong reasons).
-The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary objective of predicting yield levels well at the "observed" nitrogen rate for each site well.
+However, yield levels can sometimes be predicted well but for "wrong reasons," making it possible to predict yield levels at the observed rates (rates that are actually applied in the experiment) without recovering the structure of the yield response function.
+The training process of prediction-oriented ML methods may twist the reasoning behind why yield varies, and do so in a way that sacrifices its ability to recover the yield response function as long as it fits the primary objective of predicting yield levels well at the "observed" nitrogen rate for each site.
 Please see our more detailed discussions on this matter in section 4.2.
-
 </span>
@@
 <span style="color:blue">  
-Please see Figure E.1 that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a single simulation round.
-RMSE is presented in the figure as well.
-As we have 1000 simulations, it is simply infeasible to present figures like this for all the simulation rounds.
-But, this figure provides a better sense of the value of RMSE and how good the fit is.
+Please see Figure E.1, which plots true yields (without error, epsilon) against predicted yields by model for a single simulation round.
+(CF is not presented as it does not predict yield levels, as discussed in the article.) RMSE is presented in the figure as well.
+As we have 1000 simulations, it is infeasible to present figures like this for all the simulation rounds.
+But, this figure provides a better sense of the value of RMSE and the goodness of fit.
 </span>
@@
 
+<span style="color:blue">  
 Please see Figure 2 for illustrations of how yield responds to N site-specifically for several sites within a field.
-Please note that Figure 6 presents exactly the models' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc).
-As you can see in the figure, RF underestimates the impact of N on yield severely, which leads to the underestimation of EONR.
+Figure 6 illustrates exactly the models' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc).
+The figure shows that RF dramatically underestimates the impact of N on yield, which leads to the underestimation of EONR.
 BRF suffers negative bias as well.
-On the contrary, CF does not suffer this bias.
-Of course, the worst of all is CNN, which thinks that the impact of N on yield is almost nascent as you can see in Figure 5.
-On top of negative bias RF and BRF suffer, their estimation of the impact of N is also less accurate than CF.
-That is why CF performs better than RF and BRF in profit.
-Please note that CF does not even estimate Eq.
-(3).
-It estimates the change in yield when N is increased from one rate to another rate as discussed in the paper.
-
-<span style="color:blue">
-
+CF does not suffer this bias.
+Of course, CNN is the worst, which thinks that the impact of N on yield is almost nothing<!-- nascent --> as you can see in Figure 6 in the revised manuscript and Figure 1 in this document<!-- Figure 5 -->.
+In addition to the negative biases from RF and BRF, their estimation of the impact of N is less accurate than CF.
+That is why CF provides higher profits than do RF and BRF.
+CF does not even estimate Eq.
+(3), but rather estimates the change in yield when N is increased discretely, as is discussed in the revised manuscript.
 </span>
@@
 
-Please see page 3, line 35 for a new list of studies that attempt to estimate EONR.
-Please note that the previous studies relevant to our study are those that apply ML methods to OFE data with the ultimate intention of estimating site-specific EONR.
-There is no study that tests the performance of EONR using real data.
-This is because that is fundamentally impossible as we mentioned above.
-There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (e.g., @Qin2018; @Ransom2019 @Wang2021; @wen2021machine).
-But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field?
-That is because they do not (and will never) know the true EONR for each field.
+<span style="color:blue">
+Please see page 3, line 35 for a newly listed study (@barbosa2020risk)  that attempts to estimate EONR.
+Please note that the previous studies relevant to our study apply ML methods to OFE data with the ultimate intention of estimating site-specific EONR.
+There is no study that tests the performance of EONR using real data, which is fundamentally impossible, as mentioned above.
+There are studies that predict field-level (but not site-specific within a field) EONRs for individual fields.
+Some use a traditional regression approach then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (e.g., @Qin2018; @Ransom2019 @Wang2021; @wen2021machine).
+But, please note that the field-level EONRs they compare against are "estimated." Of course, they had to "estimate" the EONR for each field because they did not (and could not) know the true EONR for each field.
 Moreover, the objective of such studies are fundamentally different from ours.
-Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR.
-We consider those studies not very relevant.
-We believe including those studies will simply bloat the introduction.
+Our focus is on site-specific EONR within a field, theirs are on field-specific EONR.
+We consider those studies not very relevant to our purposes, and have left discussion of them out of the introduction for brevity.
+</span>
 
@@
 <span style="color:blue">  
-We already discuss our results to the state of the art of the literature.
-The state of the art is sadly trying to predict yields site-specifically as well as possible.
-We show that such practice can be misleading and economically harmful when your ultimate goal is to actually help farmers make nitrogen application decisions (predicting EONR well).
+We discussed our results with regard to the state of the art literature.
+(Please see lines 352-357, and lines 442-475.) The state of the art is sadly trying to predict yields site-specifically as well as possible.
+We show that such practice can be misleading and economically harmful when the ultimate goal is to help farmers make more profitable nitrogen application decisions (predicting EONR well).
 There is nothing wrong with our approach in yield prediction as evident in Figure E.1<!-- Figure 12 -->.
-We are using ML methods that have been used in the literature of OFE for site-specific input management.
+We are using ML methods that have been used in the on-farm experimentation literature for site-specific input management.
 Those studies were published very recently.
 We added our description about how the size of epsilon affects our results briefly in Appendix G.
-We added the following at line 25 page 390:
+We added the following at line 381 page 24:
 
-"Finally, the simulation results at a smaller and larger size of the error term are presented in Appendix G as a sensitivity check for interested readers.
-Basically, qualitative results remain the same."
+"*To check for model robustness, simulations were also run assuming smaller and larger error term sizes. Results presented in Appendix G show qualitative results basically unchanged.*"
 

### 2022-04-19 Writing/appendix.rmd
large updates for 3rd round submission

@@
 ## Appendix B: Understanding Yield Response Functions Better {-}
-Another way to writing Eq. \@ref(eq:eqn3) that may help understanding the yield response Eq. (B.1) better conceptually is as follows:
+Another way to write Eq. \@ref(eq:eqn3) that may help to better understand the yield response of Eq. (B.1) is as follows:
 
@@
 
-In this formulation, it is made clear that the base parameters $\alpha$, $\beta$, and $ymax$ are functions of a vector of field characteristics variables $\mathbf{c}=(c_1,\dots,c_K)$, which vary spatially on the field.
+In this formulation, it is made clear that the base parameters $\alpha$, $\beta$, and $ymax$ are functions of a vector of field characteristics variables $\mathbf{c}=(c_1,\dots,c_K)$, which vary spatially on the field,
 
-Which of $c_1,\dots,c_K$ has an influence vary by the parameters.
+$c_1,\dots,c_K$ has an influence that varies by parameter.
 For example, $\alpha$ represents what the yield would be when no nitrogen is applied in conjunction with $ymax$ because when $N = 0$, $yield = ymax * (1-exp(\alpha))$.
@@
 $\beta$ reflects how efficiently the crop uses N to create grain mass.
-So, it may be a function of soil properties that affect the availability of applied N fertilizer to the crop, such as N immobilization, leaching, denitrification, and volatilization among $\mathbf{c}$.
+It may be a function of soil properties that affect the availability of applied N fertilizer to the crop, such as N immobilization, leaching, denitrification, and volatilization among $\mathbf{c}$.
 
@@
 &=  ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i}))(1+r^{\varepsilon}_{i,j}) \\
-&=  ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) +  ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) \cdot r^{\varepsilon}_{i,j} \\
+&=  ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) +  ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) \cdot r^{\varepsilon}_{i,j} \qquad \text{(C.1)}\\
 &= ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i})) + \varepsilon_{i,j}
@@
 ```{r cnn-epoch, fig.width=5, fig.height=4, fig.cap = "Figure D.1: An example of CNN performance per training epoch (scenario: aabbyytt)"}
-knitr::include_graphics(here("GitControlled/Writing/loss_model4_simID1.png"))
+knitr::include_graphics(here("GitControlled/Writing/Loss_epoch.eps"))
 ```
@@
 
-Figure E.1 plots the predicted yields against the true yield without error in one of the one thousand simulation rounds by ML method and modeling scenario.
-The predicted points clustered around the red 1-to-1 line, meaning that the prediction-oriented ML methods predicted yields well.
-
-However, as mentioned in section 4.2, please note that even though the yield prediction accuracy evaluated at the actually applied N rate is , it does not necessary mean good performance in predicting yield “response” function which requires counterfactual prediction.
+Figure E.1 plots the predicted yields against the true yield in one of the one thousand simulation rounds by ML method and modeling scenario.
+The RMSEs are presented in the figure as well.
+Since CF-base does not predict yield, the figure only reports the results from RF, BRF and CNN.
+The predicted points clustered around the red 1-to-1 line, meaning that the prediction-oriented ML methods predicted yield levels well.
+<!-- However, as mentioned in section 4.2, even though the yield prediction accuracy evaluated at the actually applied N rate is good, it does not necessarily mean good performance in predicting yield “response” function which requires counterfactual prediction.
+-->
 
@@
 
-Table D.1 shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the one thousand simulations using the training datasets as testing datasets.
+Table F.1 shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the one thousand simulations using the training datasets as testing datasets.
 RF and BRF performs slightly better compared to the case when they are evaluated against the separate testing datasets.
@@
 
-Table D.2 presents the training accuracy of yield prediction: namely, the yield prediction accuracy when the trained model is evaluated using the training datasets as opposed to separate testing datasets.
+Table F.2 presents the training accuracy of yield prediction: namely, the yield prediction accuracy when the trained model is evaluated using the training datasets as opposed to separate testing datasets.
 
@@
 The results of EONR estimation and yield prediction are shown in Table G.1 and G.2.
-Table G.3 summarizes the relationship between yield and EONR prediction RMSE.
+Table G.3, which summarize the relationship between yield and EONR prediction RMSE.
 

### 2022-04-19 Writing/manuscript_cea.rmd
large updates for 3rd round submission

--- 2022-03-30 Writing/manuscript_cea.rmd
@@
       - "Eq"
-abstract: "Estimating site-specific crop yield response to changes in input (e.g., seed, fertilizer) management is a critical step in making economically optimal site-specific input recommendations.
+abstract: "Estimating site-specific crop yield response to changes to input (e.g., seed, fertilizer) management is a critical step in making economically optimal site-specific input management recommendations.
 Past studies have attempted to estimate yield response functions using various Machine Learning (ML) methods, including the Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN) methods.
@@
 CF's estimations of site-specific EONRs were superior under all scenarios considered.
-Furthermore, we also show that the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions."
+We also show that the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions."
 ---
@@
 Information about crop yield response input management is critical for the identification of site-specific economically optimal input rates (EOIRs) [@bullock1998does], and the difficulty in estimating site-specific yield response functions accurately within a field is the primary explanation of the persistent relatively low the adoption rate of variable rate crop input application technology [@lowenberg2019setting].
-Historically, site-specific yield response functions have been estimated using the data generated from strip trials conducted on only parts of fields [@makowski2001statistical; @scharf2002corn; @bullock2002adding; @mamo2003spatial; @hurley2004estimating; @anselin2004spatial; @scharf2005field; @ruffo2006site; @Miao2006; @puntel2019development].
+Historically, site-specific yield response functions have been estimated using the data generated from strip trials conducted on only parts of fields [@anselin2004spatial; @bullock2002adding; @hurley2004estimating; @makowski2001statistical; @mamo2003spatial; @Miao2006; @puntel2019development; @ruffo2006site; @scharf2002corn; @scharf2005field].
 But recently whole-field on-farm precision experimentation (OFPE) [@bullock2019] has allowed implementation of improved statistical experimental designs (e.g., Latin Square, Randomized Block) on entire fields [@laurent_kyveryga_makowski_miguez_2019; @licht_witt_2019].
@@
 The resultant availability of more spatially detailed experiment data has encouraged a resurgence of interest in estimating site-specific yield response functions.
-For example, @barbosa2020modeling, @barbosa2020risk, @krause2020random and @Gardner21 used OFPE data to estimate site-specific yield response functions and economically optimal site-specific N fertilizer and/or seed rates.
+For example, Barbosa et al.
+[-@barbosa2020risk; -@barbosa2020modeling], @krause2020random and @Gardner21 used OFPE data to estimate site-specific yield response functions and economically optimal site-specific N fertilizer and/or seed rates.
 These recent studies used machine learning (ML) methods extensively in place of more traditional parametric modeling approaches.
-@barbosa2020modeling and @barbosa2020risk applied the Convolutional Neural Network approach, @krause2020random used Random Forest-based approaches, and @Gardner21 used the shape-constrained generalized additive model.
-But this trend of applying ML methods may raises concerns.
+Barbosa et al.
+[-@barbosa2020risk; -@barbosa2020modeling] took a Convolutional Neural Network approach, @krause2020random used Random Forest-based approaches, and @Gardner21 used the shape-constrained generalized additive model.
+But this trend of applying ML methods may raise concerns.
 Historically, agronomists have worked meticulously to develop clever experimental designs to identify causes of yield response to input management.
-But the aforementioned recent applications of ML methodologies pay little attention to identify such causes, instead attempting to validate their models by estimating yield prediction accuracy.
+But the aforementioned recent applications of ML methodologies pay little attention to identifying such causes, but instead attempt to validate their models by estimating yield prediction accuracy.
 But the ultimate goal of OFPE is the accurate prediction of EOIRs, not yields.
@@
 Unlike traditional prediction-oriented ML methods, CML focuses on identifying causal impacts of an event (in our context, of an increase or decrease in the input application rate).
-The growing academic literature applying CML methods includes @richens2020improving, who's medical research pointed out that the inability of the traditional ML methods to identify cause-and-effect relationships between disease and patients' characteristics could lead to misdiagnoses, and showed that CML-based diagnoses could improve the accuracy of diagnostic prediction.
-In addition, @carbo2020machine used a CML to identify characteristics causing bank customers to adopt online banking services, and @bozorgi2020process applied CML to study the mining processes.
+The growing academic literature applying CML methods includes @richens2020improving, whose medical research pointed out that the inability of the traditional ML methods to identify cause-and-effect relationships between disease and patients' characteristics could lead to misdiagnoses, and showed that CML-based diagnoses could improve the accuracy of diagnostic prediction.
+In addition, @carbo2020machine used a CML to identify characteristics causing bank customers to adopt online banking services, and @bozorgi2020process applied CML to study mining processes.
 
-In this paper, we use the Causal Forest (CF) approach developed by @athey2016recursive and @Wager2018a to examine the accuracy of methods that estimate site-specific economically optimal N fertilizer rates (EONRs).
-We compare the EONR prediction performances of our CF-based approach to the widely used ML methods Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN), and we examine how yield prediction performance is related to EONR prediction performance, which allow us to examine whether model selection should be based on yield prediction accuracy when the ultimate goal is EOIR identification.
+We use the Causal Forest (CF) approach developed by @athey2016recursive and @Wager2018a to examine the accuracy of methods that estimate site-specific economically optimal N fertilizer rates (EONRs).
+We compare the EONR prediction performances of our CF-based approach to the widely used ML methods Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN), and we examine the relation between yield prediction performance and EONR prediction performance, which allows us to study whether model selection should be based on yield prediction accuracy when the ultimate goal is EOIR identification.
 We use Monte Carlo simulations in which we synthetically generate yield and soil/field characteristics datasets to create stylized "field." Because real-world "true" EOIRs are unobservable, real-world data cannot be used to test the accuracy of statistical methods estimating EOIRs.
@@
 In the following, we describe the fundamental information necessary to identify EOIR in general: the site-specific treatment effect of input application on yield.
-We then discuss the causal forest method in detail, show how it is particularly suitable to obtain this fundamental information, and contrast it to more traditional prediction-oriented ML methods, such as RF, BRF, and CNN.
+We then discuss the causal forest method in detail, show how it is particularly suited to the gathering of this fundamental information, and contrast it to more traditional prediction-oriented ML methods, such as RF, BRF, and CNN.
 
@@
 
-Recent studies using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., @barbosa2020modeling; @barbosa2020risk; @krause2020random; @Gardner21) and then derive changes in yield associated with changes in input rate to estimate site-specific input recommendations.
+Recent studies using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., Barbosa et al.
+[-@barbosa2020risk; -@barbosa2020modeling]; @krause2020random; and @Gardner21) and then derive changes in yield associated with changes in the input rate to estimate site-specific input application recommendations.
 On the other hand, Causal Forest is designed specifically to estimate a discrete version of Eq.
@@
 It may be suspected that CF will outperform other ML methods that identify EOIR indirectly through yield prediction.
-We now details how CF works below and why CF may perform better in predicting EOIR than other prediction-oriented ML methods used in the previous studies.
+Below we offer details about how CF works and may perform better in predicting EOIR than other prediction-oriented ML methods previously reported.
 
@@
 CF was developed specifically for identifying heterogeneous treatment effects [@athey2016recursive; @Wager2018a].
-Like RF, CF works by building an ensemble of trees, called *causal trees* (CTs), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf (see Appendix A for an example of a CT that can help further clarify how CF works).
+Like RF, CF works by building an ensemble of trees, called *causal trees* (CTs), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here yield) of the treated and control observations that belong to the leaf.
+(See Appendix A for an example.)
 
@@
 Consequently, by splitting samples in a way that maximizes the variance of treatment effects across the resulting two leaves, CF overcomes the fundamental problem created by the unobservability of true treatment effects.
-CF requires that the tree-building process is "honest" for treatment effects estimation to be unbiased.
-Honest tree-building first randomly splits in two the training data samples, then uses one of the subsamples to determine how to split the tree, and uses the other to estimate the treatment effects [@athey2016recursive; @Wager2018a].
+CF requires that the tree-building process be "honest" for treatment effects estimation to be unbiased.
+Honest tree-building first randomly splits the training data samples in two, then uses one of the subsamples to determine how to split the tree, and the other to estimate the treatment effects [@athey2016recursive; @Wager2018a].
 This honest subsampling technique avoids overestimation of the heterogeneity of estimated treatment effects.
@@
 
-Whether the indirect (yield-prediction-first) and direct approach is used can lead to meaningful statistical differences when it comes to EOIR estimation.
-The conventional prediction-oriented ML methods are designed to predict yield, $y_i(I,\mathbf{c})$, well, but not necessarily treatment effects.
-Since the loss function used in prediction-oriented ML uses (typically squared) residuals in yield prediction, prediction-oriented ML is naturally optimized for predicting the "level" of yield instead of identifying the causal impact of the input on yield.
-CF, on the other hand, is designed specifically to estimate the causal impact of input.
-Indeed, @Wager2018a used Monte Carlo simulations to show that CF provided more accurate estimates of heterogeneous treatment effects than those provided by RF.
-However, the underlying data generating process of their simulations was extremely simple, with the treatment effect influenced by only a single variable.
+Whether the indirect (yield-prediction-first) or direct approach is used can lead to meaningful statistical differences when it comes to EOIR estimation.
+The conventional prediction-oriented ML methods are designed to predict yield $y_i(I,\mathbf{c})$ well, but not necessarily treatment effects.
+Since the loss function used in prediction-oriented ML uses (typically squared) residuals in yield prediction, prediction-oriented ML is naturally optimized for predicting the "level" of yield instead of identifying this causal impact of the input on yield.
+CF, on the other hand, is designed specifically to estimate this causal impact.
+Indeed, Wager and Athey’s[-@Wager2018a] Monte Carlo simulations showed that the estimates of heterogeneous treatment effects provided by CF were more accurate than those provided by RF.
+However, their simulations' underlying data-generating process was extremely simple, with the treatment effect influenced by only a single variable.
 CF has not been tested for more complicated data generating processes, such as those represented by yield response functions in which the treatment effect of an input can be affected by multiple variables in a non-linear fashion.
@@
 
-Monte Carlo simulations were conducted for nitrogen experiments for corn production to estimate site-specific EONRs.
+Estimates of site-specific EONRs were conducted using Monte Carlo simulations of nitrogen fertilizer application experiments for corn production.
 The simulations' first step generated one thousand synthetic fields that "resembled" an actual field.
@@
 Detailed descriptions of these steps are provided below.
-The R and python codes that implement the simulation analyses are publicly accessible as a Mendeley dataset [@Kakimoto2022codes], or as a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.
+The R and Python codes that implement the simulation analyses are publicly accessible as a Mendeley dataset [@Kakimoto2022codes], or as a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.
 
@@
 Each plot was made up of four (4-rows $\times$ 1-column) 18.3 m $\times$ 18.3 m "subplots," which were unit of analysis used in subsequent statistical analysis.
-Each subplot contained of a 6-rows $\times$ 6-columns grid of thirty-six 3.05 m $\times$ 3.05 m "cells." All field characteristics and yield data were generated at the cell level.
+Each subplot contained a 6-row $\times$ 6-column grid of thirty-six 3.05 m $\times$ 3.05 m "cells." All field characteristics and yield data were generated at the cell level.
 
@@
 $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen].
-Figure \@ref(fig:vis-MB-curve) presents example visualization of site-specific yield response functions for some sites.
+Figure \@ref(fig:vis-MB-curve) presents examples of site-specific yield response functions for five sites.
 
@@
 
-The error term of the yield $\varepsilon$ represents the composite of all the unobserved factors that affect crop yield beyond $\alpha$, $\beta$, $ymax$ and $N$.
-Each cell $(i,j)$'s "true" optimal N application rate, denoted $N^{opt}_{i,j}$, was calculated by solving a profit maximization problem by cell assuming that the prices of corn and N fertilizer were $\$0.138/kg$ and $\$1.323/kg$, respectively.
-These prices are used consistently for our simulations.
+The yield error term $\varepsilon$ represents the impact of the composite of all the unobserved factors that affect crop yield that are not accounted for by $\alpha$, $\beta$, $ymax$ and $N$.
+Each cell $(i,j)$'s "true" optimal N application rate, denoted $N^{opt}_{i,j}$, was calculated by solving a profit maximization problem by cell assuming that the prices of corn and N fertilizer were $\$0.138/kg$ and $\$1.323/kg$ in all simulations.
 See Appendix C.1 for further details on how the parameters were generated and sample maps of the parameters and true economically optimal N rates.
@@
 In each simulation round, five field-trial N rates were determined based on the range of the round's cell-specific EONRs. 
-Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percent quantile of the round's cell-specific EONRs.
+Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percentile of the round's cell-specific EONRs.
 Then, the five trial design rates were $N_1 = Q_{0.05} - 20$, $N_5 = Q_{0.95} + 20$, $N_2 = N_1 + 0.25(N_5 - N_1)$, $N_3 = N_1 + 0.50(N_5 - N_1)$, $N_4 = N_1 + 0.75(N_5 - N_1)$.
-In each round, a Latin square design was followed to assign each plot one of the five N rates so established.
+In each round, a Latin square design was followed to assign to each plot one of the five N rates so established.
 The left-most panel of Figure \@ref(fig:fig-nExp-yield) shows an example of a trial design.
-The N rate was orthogonal to the error term in every simulation's example of trial design.
-This is important because if they were correlated, bias in the estimation of the impact of N on yield would be introduced into all the ML methods.
-Since the treatment effect at each leaf is obtained simply by taking the difference of the average value of the dependent variable between the control and treated group within the leaf, CF requires the exogeneity of the treatment conditional on the independent variables to estimate the treatment effect consistently.
-Note that the violation of this condition would lead to biased estimation using the CF and the other ML methods.
+The N rate was orthogonal to the error term in every simulation's trial design.
+This is important because correlation between N and the error term would introduce bias in the estimation of the impact of N on yield for all ML methods.
+Since the treatment effect at each leaf is obtained simply by taking the difference of the average value of the dependent variable between the control and treated group within the leaf, to estimate the treatment effect consistently CF requires the exogeneity of the treatment conditional on the independent variables.
+Note that violation of this condition would lead to biased estimation using the CF and the other ML methods.
 
@@
 \@ref(eq:eqn3).
-The cell-level data were then aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation.
-The subplot data were therefore
+The cell-level data were then aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation of the generated dataset:
 
@@
 To evaluate the performances of RF, BRF, CNN and CF, we examined four modeling scenarios, each defined by a dataset assumed to be available to the researcher.
-The first modeling scenario, denoted "aby" assumed that the researcher has a dataset of the actual values $\alpha_{i}$, $\beta_{i}$, $ymax_{i}$ in the yield response function for every subplot $i$ and use $\alpha$, $\beta$ and $ymax$ as covariates in the ML models.
-This scenario represents an ideal situation for the researcher, in which all the relevant variables are observed, but the true functional form of heterogeneous yield response functions are not known.
-More realistic scenarios can be compared with this ideal scenario.
+The first modeling scenario, denoted "aby" assumed that the researcher has a dataset of the actual values of yield function parameters $\alpha_{i}$, $\beta_{i}$, and $ymax_{i}$ for every subplot $i$ and uses them as covariates in the ML models.
+This scenario represents an ideal situation for the researcher in which all the relevant variables are observed, but the true functional form of the heterogeneous yield response functions are not known.
+More realistic scenarios could be compared with this ideal scenario.
 
@@
 In the second scenario, denoted "abytt," we introduced additional variables $\theta^1$ and $\theta^2$, and the researcher's dataset contained values of $\alpha_{i}$, $\beta_{i}$, $ymax_{i}$, $\theta^1_{i}$ and $\theta^2_{i}$ for all subplots $i=1,\dots,1536$.
-$\theta^1$ and $\theta^2$ had no effect on yield, but they were spatially correlated with $\beta_{i}$.
+$\theta^1$ and $\theta^2$ had no effect on yield, but were spatially correlated with $\beta_{i}$.
 This scenario was meant to reflect the lack of scientific consensus about which variables explain heterogeneous yield response to N, making it likely that the researcher would include irrelevant variables like $\theta^1$ and $\theta^2$ in real-world data analysis.
@@
 Rather, it contained subplot-level values of permutations of $\alpha$, $\beta$, and $ymax$.
-Each of the three parameters were split into two parts in a spatially correlated manner, and six new covariates were created (see Appendix C.2 for the details about this parameter-splitting process).
-These were $\alpha^{1}_{i}$, $\alpha^{2}_{i}$, $\beta^{1}_{i}$, $\beta^{2}_{i}$, $ymax^{1}_{i}$, and $ymax^{2}_{i}$.
+Each of the three parameters was split into two parts in a spatially correlated manner, and six new covariates were created.
+(See Appendix C.2 for the details about this parameter-splitting process.) These were $\alpha^{1}_{i}$, $\alpha^{2}_{i}$, $\beta^{1}_{i}$, $\beta^{2}_{i}$, $ymax^{1}_{i}$, and $ymax^{2}_{i}$.
 The two split variables were spatially correlated to reflect that many of the soil/field characteristics used to analyze OFPE data are spatially correlated.
@@
 
-The RF, BRF, and CNN methods all followed the same conceptual steps to estimate site-specific EONR: 1) estimate the yield production functions and 2) calculate site-specific EONRs based on that estimated function.
+The RF, BRF, and CNN methods all followed the same conceptual steps to estimate site-specific EONRs: 1) estimate the yield production functions and 2) use those estimated functions to calculate site-specific EONRs.
 For the given modeling scenario, RF, BRF and CNN predict yield by using all the available covariates as explanatory variables in the estimation process.
 The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for RF and BRF modeling.
-RF ann BRF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving an honest tree-building process), and the optimal values for these parameters were selected by cross-validation.
+RF and BRF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving an honest tree-building process), the optimal values of which were selected by cross-validation.
 Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same dataset was used.
-To reduce the variance of predictions for prediction accuracy, we set the number of trees (*num.trees*) at a high value, $2000$.
+To reduce the variance of predictions for prediction accuracy, the number of trees (*num.trees*) was set at $2000$, a high value.
 
 CNN leaves room for researchers to determine its architecture.
-We used a slightly modified version of one of the multi-stream CNN architectures proposed by @barbosa2020modeling, called "Late Fusion." Briefly stated, explanatory variables except N rate (e.g.
-$\alpha_{i,j}$, $\beta_{i,j}$, etc.) entered the model as a set of $6 \times 6$ element rasters.The input size of the N rate is treated as $1 \times 1$ because it is spatially homogeneous within each subplot.
-First, each input was connected to an independent convolutional layer with eight $3 \times 3$ filters each with stride one, followed by a $2 \times 2$ max-pooling layer with stride two.
+We used a slightly modified version of one of the multi-stream CNN architectures proposed by @barbosa2020modeling, called "Late Fusion." Briefly stated, explanatory variables except N rate ($\alpha_{i,j}$, $\beta_{i,j}$, etc.) entered the model as a set of $6 \times 6$ element rasters.
+The input size of the N rate was treated as $1 \times 1$ because it was spatially homogeneous within each subplot.
+First, each input was connected to an independent convolutional layer with eight $3 \times 3$ filters of stride one, followed by a $2 \times 2$ max-pooling layer of stride two.
 Then, a fully-connected rectified linear unit (ReLU) layer with sixteen neurons was added after each max-pooling layer, followed by a single ReLU neuron.
 Finally, multiple neurons were concatenated and fed to the fully-connected ReLU layer with sixteen neurons, followed by an output with a linear activation function.
-@barbosa2020modeling demonstrated that among several CNN architectures, this architecture modeled crop yield response to N rate management best.
+@barbosa2020modeling demonstrated that this architecture modeled crop yield response to N rate management best among several CNN architectures.
 CNN was implemented in Python v3.7.6 using Pytorch v1.7.0 [@paszke2017automatic].
 The Adam optimizer [@kingma2014adam] was used with a learning rate of $0.001 \%$ (default value).
-To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience (see Figure D.1 in Appendix D for an illustration of the convergence of training with respect to the number of epochs).
+To avoid over-fitting, early stopping was used to monitor validation loss with a ten epochs of patience.
+(See Figure D.1 in Appendix D for an illustration of the convergence of training with respect to the number of epochs.)
 
 Let $\mathbf{\Omega_{i}}$ denote a list of subplot-level explanatory variables (soil/field characteristics).
-Further, let $\hat{g}_m(N,\mathbf{\Omega})$ denote an estimated yield response function, estimated by model $m$ ($m$ = RF, BRF, or CNN).
-Then, yield at $i$ from model $m$ is $\hat{g}_m(N,\mathbf{\Omega_{i}})$.
+Let $\hat{g}_m(N,\mathbf{\Omega})$ denote a yield response function estimated by model $m$ ($m$ = RF, BRF, or CNN).
+The estimated yield response function at $i$ from model $m$ is $\hat{g}_m(N,\mathbf{\Omega_{i}})$.
 The site-specific EONR for each model can then be found by solving the following profit maximization problem for all $i$ for each of the models:
@@
 Unlike RF, BRF, and CNN, CF estimates the impact of a binary treatment.
-In our context, CF estimates changes in yields (i.e., $\hat{\tau}_{N^{con} \rightarrow N^{tre}}(\mathbf{\Omega_{i}})$) caused by changes in N application rates from one experimental rate (control N rate, i.e., $N^{con}$) to another experimental rate (treatment N rate, i.e., $N^{tre}$).
+In our context, CF estimates changes in yields (i.e., $\hat{\tau}_{N^{con} \rightarrow N^{tre}}(\mathbf{\Omega_{i}})$) caused by changes in N application rates from one experimental rate (the control N rate, denoted $N^{con}$) to another experimental rate (a treatment N rate, denoted $N^{tre}$).
 Since we have five N application rates, four "experiments" (treatments) are identified based on four ($N^{con}$, $N^{tre}$) combinations.
@@
 Let $\Delta Y_{N_1 \rightarrow N_m}(\mathbf{\Omega_{i}})$ be the the estimated treatment effect of changing subplot $i$'s application rate from $N_1$ to $N_m$ for site $i$.
-
 Since the CF-base approach always estimates the treatment effects using the lowest treatment rate $N_1$, the predicted treatment effects already represent differences in yields from yield at $N_1$:
@@
 
-For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset.
-For example, for simulation number 1, the training dataset from simulation number 2 was used as the test dataset.
-This process works because the training datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$).
+In every simulation round a dataset from a different simulation round was used as the test dataset for evaluation of yield and EONR predictions.
+This process works because the training datasets were generated by the same data generating process, yet had different underlying field parameters ($\alpha$, $\beta$, $ymax$).
 Further, all training datasets were generated independently, so for any particular simulation round, the dataset from any other round could serve as a valid test dataset.
@@
 
-The accuracy of EONR estimation was judged based on RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level:
+The accuracy of EONR estimation was judged based on the RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level:
 
@@
 
-Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N^{opt}_{i}$.
+We also used the EONR estimates to calculate $\hat{\pi}_{def}$, estimated per-ha profit-deficits relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N^{opt}_{i}$.
 For RF, BRF, and CNN, the accuracy of yield prediction was judged based on the RMSE ($kg/ha$) of the yield prediction against the true yields at the subplot level:
@@
 The constant marginal product caused the estimated EONR to take on either the lowest or highest experimental N application rate.
-To examine whether this problem is a product solely of the specific choice of CNN architecture, we also tested another CNN model, which was analogous to CNN-ST proposed by @barbosa2020modeling.
-This architecture also estimated that yield and N rates were perfectly linearly related, and so estimated site-specific EONR poorly.
+We also tested another CNN model to examine whether this problem resulted solely from the specific choice of CNN architecture, which was analogous to CNN-ST proposed by @barbosa2020modeling.
+This architecture also estimated that yield and N rates were linearly related, and so estimated site-specific EONR poorly.
+Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs.
+@barbosa2020risk extended @barbosa2020modeling's CNN-LF models to estimate site-specific EOIRs for N and seed.
+But they did not evaluate the accuracy of the EOIR estimates generated by their models.
+EOIR validation is infeasible using real-world data because ground-truthed site-specific EOIRs are unobservable.
 
-Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs.
-As its extension, @barbosa2020risk used an ensemble of @barbosa2020modeling's CNN-LF models to estimate site-specific EOIR for N and seed.
-However, they did not evaluate how accurate their EOIR estimates produced from their models.
-This is simply because EONR validation is infeasible using the real-world data because ground-truth site-specific EOIRs are unobservable.
-Our simulation results suggest that CNN is inferior to RF, BRF and CF-base in estimating site-specific EONR at least in our simulation settings.
-
-Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the RMSEs of the EONR estimations and $\hat{\pi}_{def}$ obtained from the one thousand simulation rounds by ML method and modeling scenario, respectively.
-The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios.
+Figures \@ref(fig:dist-optN) and \@ref(fig:dist-piLoss) show the distributions of the RMSEs of the EONR estimations and $\hat{\pi}_{def}$ obtained from the one thousand simulation rounds by the ML method and the modeling scenario, respectively.
+The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all modeling scenarios.
 Interestingly, RF seems particularly vulnerable to the inclusion of more variables, with RMSE ($\hat{\pi}_{def}$) increasing from `r table_optN_prep[type=="test" & Model=="aby",rmse_optN_RF]` (`r table_optN_prep[type=="test" & Model=="aby", pi_loss_RF]`) in the "aby" scenario to `r table_optN_prep[type=="test" & Model=="aabbyytt", rmse_optN_RF]` (`r table_optN_prep[type=="test" & Model=="aabbyytt", pi_loss_RF]`) in the "aabbyytt" scenario.
@@
 Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions.
-It plots the estimated treatment effects against true treatment effects by treatment type and ML method under the "aabbyytt" scenario in one of the one thousand simulation rounds.
-First of all, CNN suffers from severe underestimation of the impact of N in this particular simulation round.
-RF also suffers from underestimation of the impact of N.
+For one of the one thousand simulation rounds, it plots the estimated treatment effects against true treatment effects by treatment type and ML method under the "aabbyytt" scenario, and shows that CNN substantially underestimates the impact of N.
+RF also underestimates the impact of N.
 Underestimation of the impact of N generally leads to the underestimation of EONR, which in turn results in profit loss.
-Underestimation bias from BF is not as severe as RF or CNN.
-However, unlike RF, BRF, and CNN, points for CF-base clustered around the red 1-to-1 line, meaning that the estimated treatment effects from CF did not exhibit significant bias in treatment effect estimation.
+Underestimation bias from BRF is less pronounced than from RF and CNN.
+However, unlike RF, BRF, and CNN, points for CF-base clustered around the red 1-to-1 line, meaning that the estimations of treatment effects did not exhibit significant bias.
 Moreover, points are clustered more tightly about the 1-to-1 line for CF-base than BRF.
 That is, CF-base estimated treatment effects more efficiently than did BRF.
+To check for model robustness, simulations were also run assuming smaller and larger error term sizes.
+Results presented in Appendix G show qualitative results basically unchanged.
 
@@
 
-Finally, the simulation results at a smaller and larger size of the error term are presented in Appendix G as a sensitivity check for interested readers.
-Basically, qualitative results remain the same.
-
 ## The Relationship between Yield and EONR Prediction Performances.
 
-Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations (see Figure E.1 in Appendix E for example visualizations of predicted and true yields along with RMSE values by model).
-Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN.
-Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact along with the poor performance of RF in predicting EONR presented in \@ref(tab:table-optN) show that strong predictive power of yield levels does not imply accurate prediction of EONR.
+Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations.
+(See Figure E.1 in Appendix E for examples of visualizations of predicted and true yields along with RMSE values, by model.) Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN.
+Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact, along with the poor performance of RF in predicting EONR presented in \@ref(tab:table-optN), shows that strong predictive power of yield levels does not imply accurate prediction of EONR.
 Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well.
@@
 
-Figure \@ref(fig:vis-MB-BRF-y) illustrates the distinction between yield prediction at observed points and yield response function prediction, giving insights into why good yield level prediction does not necessarily lead to good EONR prediction in general.
+By illustrating the distinction between yield prediction at observed points and yield response function prediction, Figure \@ref(fig:vis-MB-BRF-y) provides insight into why good yield level prediction does not necessarily lead to good EONR prediction in general.
 The black curves are the true yield response functions for two sites in a single simulation round.
 Red symbols represent true (circle) or predicted (triangle) yields at the rate observed in the data: the rate that was actually applied in the experiment.
-That is, 150 kg/ha was applied to the two sites in the experiment.
+That is, 150 kg/ha were applied to the two sites in the experiment.
 Blue symbols represent true (circle) or predicted (triangle) yield at some rates that were not observed (or applied) for the two sites in the experiment.
 Prediction-oriented ML methods train models to minimize errors in yield level prediction at the "observed" rates (red points).
-Both RF- and BRF-trained models predict yield level at the observed rate well for the two sites (the vertical distance between the red circle and triangle).
-However, as you move away from the observed N rate, yield prediction errors tend to become larger (of course smaller yield prediction errors can be observed at unobserved rates some times).
-More important, connecting the predicted yield points does not trace the true yield response curves well for both RF and BRF.
-Specifically, in this example, the predicted impact of N on yield from RF and BRF are both smaller than the true impact of N.
+Both RF- and BRF-trained models predicted yield level at the observed rate well for the two sites (the vertical distance between the red circle and triangle).
+However, moving the N rate away its observed value tends to increase yield prediction error sizes.
+More importantly, connecting the predicted yield points does not trace the true yield response curves well for either RF or BRF.
+Specifically, in this example, the predicted impact of N on yield from RF and BRF are both smaller than the true impact.
 
@@
 
-In essence, Figure \@ref(fig:vis-MB-BRF-y) illustrates that good performance in predicting yield "levels" at the "observed" points does not mean good performance in predicting yield "response" function, which is about finding out what "would" have happened to yield if rates other than the one actually applied were applied.
-This happens because you can predict yield "levels" for wrong reasons by giving wrong amount of credit to wrong drivers (variables) of yield levels.
-The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary objective of predicting yield levels well at the "observed" nitrogen rate for each site well.
-This problem is also observable at Figure \@ref(fig:plot-tre), which shows both RF and BRF underestimates the impact of N on yield: or in other words, their predicted site-specific yield response functions tend to be flatter than they truly are.
-Of course, the CNN approach in our study is an extreme case where it completely fails to recognize the contribution of N on yield.
-But, remember that CNN does performs almost as good as and sometimes surpass RF and BRF in yield prediction as shown in Table \@ref(tab:table-y).
+In essence, Figure \@ref(fig:vis-MB-BRF-y) illustrates that good performance in predicting yield "levels" at the "observed" points does not mean good performance in predicting the yield "response" function, which is about finding out what would have happened to yield had N rates other than the one actually applied been applied.
+Such poor performance can happen when the wrong variables are credited for driving yield results.
+The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary objective of predicting yield levels well at the "observed" N rate for each site well.
+This problem is also observable at Figure \@ref(fig:plot-tre), which shows both RF and BRF underestimate the impact of N on yield: or in other words, their predicted site-specific yield response functions tend to be too flat.
+Of course, the CNN approach in our study is an extreme case which completely fails to recognize the contribution of N on yield.
+But Table \@ref(tab:table-y) shows that CNN capable of even outperforming RF and BRF in yield prediction.
 
-Since you need to be able to estimate yield curves (yield response function) well at the site level to predict site-specific EONR (not yield level) well, models' ability to predict yield levels well at the observed rates does not guarantee their ability to predict site-specific EONR well.
-In contrast to RF, BRF, and CNN, CF focuses to recover the yield response functions well (or alternatively the causal impact of N on yield at different discrete rates of N).
-We showed that CF can predict the impact of N on yield when N is changed from an unobserved rate to another unobserved rats as shown in Figure \@ref(fig:plot-tre), which then translated to better performance in predicting EONR and profit.
+Since you need to be able to estimate yield curves (yield response function) well at the site level to predict site-specific EONR (not yield level) well, a model's ability to predict yield levels well at the observed N rates does not guarantee its ability to predict site-specific EONR well.
+In contrast to RF, BRF, and CNN, CF focuses on recovering the yield response functions well (or alternatively the causal impact of N on yield at different discrete rates of N).
+We showed that CF can predict the impact of N on yield when N is changed from an unobserved rate to another, as shown in Figure \@ref(fig:plot-tre), which then translated to better performance in predicting EONR and profit.
 
 All previous research has followed a two-step procedure to estimate site-specific EONRs.
-The first step was to select the model that predicts yield levels most accurately at the observed points, and the following step used the selected model to predict EONR.
+The first step was to select the model that predicts yield levels most accurately at the observed N rates, and the second was to use the selected model to predict EONR.
 As discussed earlier, this practice can be economically harmful.
@@
 It plots RMSE of yield (x-axis) and EONR (y-axis) predictions by model and simulation round for several simulation rounds.
-As you can see clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation round 20 and 30).
+Clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation round 20 and 30).
 
@@
 
-Table \@ref(tab:count-table) summarizes the relationship between yield and EONR prediction RMSE for all the simulation rounds.
+Table \@ref(tab:count-table) summarizes the relationship between the yield prediction RMSE and the EONR prediction RMSE for all the simulation rounds.
 It shows clearly that following the process would lead to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds.
@@
 
-Virtually all the previous studies have used yield prediction accuracy to rank and select models.
+Virtually all previous studies have used yield prediction accuracy to rank and select models.
 This is understandable, since whereas yield can be "ground-truthed" the true causal impact of a treatment cannot be determined from real-world data, making it impossible to cross-validate EONR prediction.
@@
 
-Third, another interesting subject for future research is the potential of combining the ML methods with post-estimation spatial smoothing of the estimated EONR.
+Third, another interesting subject for future research is the potential of combining ML methods with post-estimation spatial smoothing of the estimated EONR.
 It is well known that soil/field characteristics are spatially correlated [@f2007methods;@goovaerts1999geostatistics]; this spatial correlation is likely to cause spatial correlation in EONRs, which would suggest that post-estimation spatial smoothing of EONRs may further improve the accuracy of EONR estimation.
@@
 Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN.
-CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation.
-Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF.
+CF consistently outperformed the other methods across all modeling scenarios in terms of EONR prediction and profit generation.
+Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF's.
 However, it is important to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN.
@@
 
-We also showed that the best model in prediction yields is not necessarily the best model in predicting EONR and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map.
+We also showed that the best model in prediction yields is not necessarily the best model in predicting EONRs and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map.
 Many studies seek to predict yield level accurately using deep learning methods.
@@
 We thank Scott Swinton at Michigan State University for providing helpful comments on this publication.
-This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled "Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management," (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled "Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation" (Award Number NR213A7500013G021).
+This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled "Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management," (Accession Number 2016-68004-24769), by the USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled "Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation" (Award Number NR213A7500013G021), and by the USDA National Institute of Food and Agriculture, Hatch project ILLU-470-333.
 

### 2022-04-19 Codes/1_2_generate_coefficients.R

@@ -1,0 +1,55 @@
+#/*----------------------------------*/
+#' ## Preparation
+#/*----------------------------------*/
+library(here)
+library(tmap)
+library(sp)
+library(sf)
+library(agricolae)
+library(lwgeom)
+library(measurements)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(gstat)
+
+# === Load Functions === #
+source(here("GitControlled/Codes/0_1_functions_gen_analysis_data.R"))
+
+# === Load Field data === #
+field <- readRDS(here("Shared/Data/for_Simulations/analysis_field.rds"))
+
+# /*=================================================*/
+#' # Unconditional Gaussian geostatistical Simulation
+# /*=================================================*/
+
+# === Set up === #
+
+# --- Geographical locations of Cells --- #
+xy <- dplyr::select(field, unique_cell_id) %>%
+  cbind(., st_coordinates(st_centroid(.))) %>%
+  st_drop_geometry() %>%
+  data.table()
+
+# --- Number of iterations --- #
+b = 1000
+
+# --- Range (m) --- #
+Range = 400
+
+# --- yield error size  --- #
+Error = 0.015 
+
+
+# === Generate coefficients === #
+coef_data <- 
+  gen_coefs_par(
+    B = b, 
+    geo_xy = xy,
+    sp_range = Range,
+    psill_merror = Error
+    )
+
+saveRDS(coef_data, here("Shared/Data/for_Simulations", paste0('coefficients_sprange_',Range,'.rds')))
+
+

### 2022-04-19 Codes/1_3_generate_analysis_data.R

@@ -1,0 +1,88 @@
+#/*----------------------------------*/
+#' ## Preparation
+#/*----------------------------------*/
+library(here)
+library(mgcv)
+library(ggplot2)
+library(grf)
+library(sf)
+library(measurements)
+library(data.table)
+library(tidyverse)
+library(future.apply)
+library(parallel)
+
+# === Load Functions === #
+source(here("GitControlled/Codes/0_1_functions_gen_analysis_data.R"))
+
+# === Prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+# === Load Field data === #
+field <- 
+	here("Shared/Data/for_Simulations/analysis_field.rds") %>%
+	readRDS()
+
+# === Load coef datasets === #
+coef_data <- 
+	here("Shared/Data/for_Simulations/coefficients_sprange_400.rds") %>%
+	readRDS()
+
+#/*---------------------------------------*/
+#' ## (1)-1 Generate Cell-level datasets
+#/*---------------------------------------*/
+raw_data <- lapply(
+	1:1000, function(x) {
+		prepare_raw_data(
+			i = x,
+			field = field,
+			coef_data_m = coef_data[sim == x, ],
+			coef_data_t = coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ],
+			app_error="no"
+		)
+	}
+)
+
+
+# === Note cell-level data will be used for simulations for CNN === #
+reg_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
+test_raw_data <- sapply(raw_data,"[",2)%>%rbindlist()
+
+
+#/*----------------------------------------------------*/
+#' ## (1)-2 Generate subplot-level analysis datasets
+#/*----------------------------------------------------*/
+reg_raw_data <- 
+	here("Shared/Data/for_Simulations/reg_raw_data.rds") %>%
+	readRDS()
+
+test_raw_data <- 
+	here("Shared/Data/for_Simulations/test_raw_data.rds") %>%
+	readRDS()
+
+##== Aggregate Cell-Level Field Data to Subplot-Level Field Data ==##
+sim_data <- lapply(
+	1:1000, function(x) {
+		# print(paste0("working on ", x, " th iteration."))
+		prepare_data_for_sim(
+			reg_raw_data = reg_raw_data[sim==x,],
[…]

### 2022-04-19 Codes/2_1_MCsim_Forest.R

@@ -1,0 +1,71 @@
+# /*===== Run on R GUI =====*/
+
+#/*----------------------------------*/
+#' ## Preparation
+#/*----------------------------------*/
+library(grf)
+library(data.table)
+library(tidyverse)
+library(future.apply)
+
+# === Source Functions === #
+setwd("~/Dropbox/ResearchProject/CF_for_VRA")
+source("./GitControlled/Codes/0_2_functions_main_sim.R")
+
+# /*----------------------------------*/
+#' ## Datasets
+# /*----------------------------------*/
+# === prices ===#
+pCorn <- price_table[2, pCorn]
+pN <- price_table[2, pN]
+
+# x=1
+# train_dt <- reg_data_all[sim==x&padding==1,]
+# test_dt <- test_data_all[sim==x&padding==1,]
+# N_levels <- reg_data_all[sim==x,]$rate%>%unique()%>%sort()
+
+
+
+# /*=================================================*/
+#' # Simulation by scenarios
+# /*=================================================*/
+
+# === set up for parallel computations === #
+plan(multicore, workers = availableCores()-2)
+options(future.globals.maxSize= 850*1024^2)
+
+# --- modeling scenario --- #
+var_ls_variations <- list(
+    c("alpha", "beta", "ymax"),
+    c("alpha", "beta", "ymax", "theta_1", "theta_2"),
+    c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2"),
+    c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")
+  )
+
+# --- Number of iterations --- #
+B=1000
+
+# --- Data --- #
+reg_data_all <- readRDS("./Shared/Data/for_Simulations/reg_data.rds")
+test_data_all <- readRDS("./Shared/Data/for_Simulations/test_data.rds")
+
+
+# === start simulations === #
+for (var in var_ls_variations){
+	set.seed(1378)
+	# --- for each modeling scenario run: --- #
+	sim_results <- lapply(1:B, 
+		function(x){
+			sim_par(
+				i = x,
+				var_ls = var,
+				reg_data = reg_data_all[sim==x&padding==1,],
+	      		test_data = test_data_all[sim==x&padding==1,],
+	      		N_levels = reg_data_all[sim==x,]$rate%>%unique()%>%sort()
+	      	)
+		}
+	) %>%
+	rbindlist()
+
[…]

### 2022-04-19 Codes/3_1_SimDataAnalysis.R

@@ -277,15 +277,6 @@ saveRDS(cnn_summry_bySim, here("Shared/Results/for_writing/cnn_summry_bySim.rds"
 # ==========================================================================
 # Merge Forest results and CNN results
 # ==========================================================================
-# === Merge === #
-
-allML_summary_raw <- 
-    rbind(forest_optN_piLoss, cnn_optN_piLoss[, names(forest_optN_piLoss), with = FALSE])
-
-saveRDS(allML_summary_raw, here("Shared/Results/for_writing/allML_summary_raw.rds"))
-
-
-
 allML_summary_bySim <-
   rbind(forest_summary_bySim, cnn_summry_bySim) %>%
   .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF_base"))] %>%
@@ -295,15 +286,6 @@ saveRDS(allML_summary_bySim, here("Shared/Results/for_writing/allML_summary_bySi
 
 
 
-allML_summary_bySim <- readRDS(here("Shared/Results/for_writing/allML_summary_bySim.rds"))
-
-
-allML_summary_bySim %>% 
-    .[type=="test" & Model == "aabbyytt"] %>%
-    .[sim %in% agg_slope_model4$sim]
-
-allML_summary_bySim %>% 
-    .[type=="test" & Model == "aabbyytt" & sim==1]
 
 
 

### 2022-04-19 Codes/3_2_CompTeEstimation.R

@@ -48,7 +48,7 @@ true_te_dt <-
 
 
 # /*================================================================*/
-#' # (1) Treatment Effect Calculation by CF-base, RF, BRF
+#' # (1) Treatment Effect Estimation by CF-base, RF, BRF
 # /*================================================================*/
 # === all the cases to be considered === #
 te_var_ls_variations <- list(
@@ -61,18 +61,12 @@ te_case_data <- expand.grid(
   ) %>%
   tibble()
 
-
-# === set up for parallel computations === #
-plan(multicore, workers = availableCores()-2)
-options(future.globals.maxSize= 850*1024^2)
-set.seed(1378)
-
-
-# === treatment effect calculation === #
+# === treatment effect estimation === #
+set.seed(1378)   	
 forest_te_dt <- 
 	te_case_data %>%
 	mutate(
-		te_data = future_lapply(
+		te_data = lapply(
 			seq_len(nrow(.)),
 			function(x) {
 				get_te_dt(
@@ -82,7 +76,7 @@ forest_te_dt <-
             	rates_ls = N_levels,
             	Method = .$Method[[x]]
             	)
-			}, future.seed = TRUE
+			}
     	)
   	)%>%
   	unnest(., cols= "te_data")%>%
@@ -93,7 +87,7 @@ forest_te_dt <-
 
 
 # /*================================================================*/
-#' # (2) Treatment Effect Calculation by CNN
+#' # (2) Treatment Effect Estimation by CNN
 # /*================================================================*/
 
 # === load CNN results (case: aabbyytt) === #

### 2022-04-19 Codes/4_1_Appendix_generate_coefficients.R

@@ -29,71 +29,47 @@ xy <- dplyr::select(field, unique_cell_id) %>%
   st_drop_geometry() %>%
   data.table()
 
-# --- Range (m) --- #
-Range <- 400
-
-#/*--------------------------------------------------------*/
-#' ## (1) Generate raw coefficients (Medium m_error: psill = 0.015)
-#/*--------------------------------------------------------*/
-
 # --- Number of iterations --- #
-b <- 1000
+b = 100
+# --- Range (m) --- #
+Range = 400
 
-# --- start simulation --- #
-coef_data <- 
-  gen_coefs_par(
-    B = b, 
-    geo_xy = xy,
-    sp_range = Range,
-    psill_merror = 0.015
-    )
+#/*-------------------------------------*/
+#' ## (1) Small degree of yield error
+#/*-------------------------------------*/
+# --- yield error size  --- #
+Error_small = 0.0075
 
-saveRDS(coef_data, here("Shared/Data/for_Simulations", paste0('coefficients_sprange_',Range,'.rds')))
-
-
-
-
-#/*--------------------------------------------------------*/
-#' ## (2) Generate raw coefficients (Small m_error: psill = 0.0075)
-#/*--------------------------------------------------------*/
-# --- set seed --- #
+# === Generate coefficients === #
 set.seed(39476)
 
-# --- Number of iterations --- #
-b <- 100
-
-# --- start simulation --- #
 coef_data_low <- 
   gen_coefs_par(
     B = b, 
     geo_xy = xy,
     sp_range = Range,
-    psill_merror = 0.0075
+    psill_merror = Error_small
     )
 
 
 saveRDS(coef_data_low, here("Shared/Data/for_Simulations", paste0('coefficients_sprange_',Range,'_low_error.rds')))
 
 
+#/*-------------------------------------*/
+#' ## (2) Large degree of yield error
+#/*-------------------------------------*/
+# --- yield error size --- #
+Error_large = 0.0225
 
-
-
-#/*--------------------------------------------------------*/
-#' ## (3) Generate raw coefficients (Large m_error: psill = 0.0225)
-#/*--------------------------------------------------------*/
-# --- set seed --- #
+# === Generate coefficients === #
 set.seed(57864)
 
-# --- Number of iterations --- #
-b <- 100
-
-# --- start simulation --- #
 coef_data_high <- 
   gen_coefs_par(
     B = b, 
     geo_xy = xy,
[…]

### 2022-04-19 Codes/4_2_Appendix_generate_analysis_data.R

@@ -25,84 +25,21 @@ field <-
 	readRDS()
 
 
-# /*===========================================*/
-#'= (1) For medium degree of m_error (Main Data)=
-# /*===========================================*/
-
-# === Load coef Data sets === #
-# coef_data <- 
-# 	here("Shared/Data/for_Simulations/coefficients_sprange_400.rds") %>%
-# 	readRDS()
-
-#/*--------------------------------*/
-#' ## (1)-1 Generate Cell-level Data sets
-#/*--------------------------------*/
-raw_data <- lapply(
-	1:1000, function(x) {
-		prepare_raw_data(
-			i = x,
-			field = field,
-			coef_data_m = coef_data[sim == x, ],
-			coef_data_t = coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ],
-			app_error="no"
-		)
-	}
-)
-
-
-reg_raw_data <- sapply(raw_data,"[",1)%>%rbindlist()
-test_raw_data <- sapply(raw_data,"[",2)%>%rbindlist()
-
-#/*--------------------------------*/
-#' ## (1)-2 Generate analysis dataset (subplot-level)
-#/*--------------------------------*/
-reg_raw_data <- 
-	here("Shared/Data/for_Simulations/reg_raw_data.rds") %>%
-	readRDS()
-
-test_raw_data <- 
-	here("Shared/Data/for_Simulations/test_raw_data.rds") %>%
-	readRDS()
-
-##== Aggregate Cell-Level Field Data to Subplot-Level Field Data ==##
-sim_data <- lapply(
-	1:1000, function(x) {
-		# print(paste0("working on ", x, " th iteration."))
-		prepare_data_for_sim(
-			reg_raw_data = reg_raw_data[sim==x,],
-			test_raw_data = test_raw_data[sim==x,]
-		)
-	}
-)
-
-reg_data <- sapply(sim_data,"[",1)%>%rbindlist()
-test_data <- sapply(sim_data,"[",2)%>%rbindlist()
-
-# saveRDS(reg_data, here("Shared/Data/for_Simulations/reg_data.rds"))
-# saveRDS(test_data, here("Shared/Data/for_Simulations/test_data.rds"))
-
-
-
-
-
-
-
-
 
 
 # /*===========================================*/
-#'=  (2) For low degree of m_error =
+#'=  (1) Small degree of yield error 
 # /*===========================================*/
 
-# === Load coef Data sets === #
+# === Load coef datasets === #
 coef_data_low <- 
[…]

### 2022-04-19 Codes/4_3_Appendix_MCsim_Forest.R

@@ -19,16 +19,10 @@ source("./GitControlled/Codes/0_2_functions_main_sim.R")
 pCorn <- price_table[2, pCorn]
 pN <- price_table[2, pN]
 
-# x=1
-# train_dt <- reg_data_all[sim==x&padding==1,]
-# test_dt <- test_data_all[sim==x&padding==1,]
-# N_levels <- reg_data_all[sim==x,]$rate%>%unique()%>%sort()
 
 # /*=================================================*/
 #' # Simulation by scenarios
 # /*=================================================*/
-# + run 1000 simulations by individual scenarios
-# + the 1000 simulation results will be saved per each scenario
 
 # === set up for parallel computations === #
 plan(multicore, workers = availableCores()-2)
@@ -42,51 +36,17 @@ var_ls_variations <- list(
     c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")
   )
 
-
-#/*--------------------------------*/
-#' ## (1) Main sim (medium m_error)
-#/*--------------------------------*/
-# --- Data --- #
-reg_data_all <- readRDS("./Shared/Data/for_Simulations/reg_data.rds")
-test_data_all <- readRDS("./Shared/Data/for_Simulations/test_data.rds")
-
-# --- Number of iterations --- #
-B=1000
-
-# === start simulation === #
-for (var in var_ls_variations){
-	# var = c("alpha", "beta", "ymax")
-	set.seed(1378)
-	# --- for each modeling scenario run: --- #
-	sim_results <- lapply(1:B, 
-		function(x){
-			sim_par(
-				i = x,
-				var_ls = var,
-				reg_data = reg_data_all[sim==x&padding==1,],
-	      		test_data = test_data_all[sim==x&padding==1,],
-	      		N_levels = reg_data_all[sim==x,]$rate%>%unique()%>%sort()
-	      	)
-		}
-	) %>%
-	rbindlist()
-
-	saveRDS(sim_results, paste0("./Shared/Results/Forest_rawRes/forest_SimRes_", paste0(var, collapse = "_"), ".rds"))
-}
-
-
-
-
-#/*--------------------------------*/
-#' ## (2) Sub sim (low m_error)
-#/*--------------------------------*/
-reg_data_low <- readRDS("./Shared/Data/for_Simulations/reg_data_low_error.rds")
[…]

### 2022-04-19 Codes/5_prepare_results.R

@@ -83,32 +83,31 @@ field_subplot_sf <-
 
 saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
 
-
 field_subplot_test_dt <- 
   sample_test_cell_dt %>%
   .[padding==1,] %>%
-  group_by(subplot_id, strip_id) %>%
-  summarise(
+  .[,.(
     sim = mean(sim),
-      yield = mean(yield),
-      opt_N = mean(opt_N),
-      rate = mean(rate),
-      aa_n = mean(aa_n), 
-      alpha = mean(alpha),
-      beta = mean(beta),
-      ymax = mean(ymax),
-      m_error = mean(m_error),
-      alpha1 = mean(alpha1),
-      alpha2 = mean(alpha2),
-      beta1 = mean(beta1),
-      beta2 = mean(beta2),
-      ymax1 = mean(ymax1),
-      ymax2 = mean(ymax2),
-      theta_1 = mean(theta_1),
-      theta_2 = mean(theta_2)
-  ) %>%
-  mutate(unique_subplot_id = paste0(strip_id,"_",subplot_id))%>%
-  dplyr::select(!c(strip_id, subplot_id))
+    yield = mean(yield),
+    opt_N = mean(opt_N),
+    rate = mean(rate),
+    aa_n = mean(aa_n), 
+    alpha = mean(alpha),
+    beta = mean(beta),
+    ymax = mean(ymax),
+    m_error = mean(m_error),
+    alpha1 = mean(alpha1),
+    alpha2 = mean(alpha2),
+    beta1 = mean(beta1),
+    beta2 = mean(beta2),
+    ymax1 = mean(ymax1),
+    ymax2 = mean(ymax2),
+    theta_1 = mean(theta_1),
+    theta_2 = mean(theta_2)
+    ), by = .(subplot_id, strip_id)
+  ] %>%
+  .[,unique_subplot_id := paste0(strip_id,"_",subplot_id)] %>%
+  .[, `:=` (strip_id=NULL, subplot_id=NULL)]
 
 saveRDS(field_subplot_test_dt, here("Shared/Results/for_writing/field_subplot_test_dt.rds"))
 

### 2022-06-09 Writing/CEA_3rd_round/replies_rev.rmd
modification for the final submission

@@
 ---
-title: "Reply to Editor"
+title: "Response to Editor"
 output:

### 2022-06-09 Writing/manuscript_cea.rmd
modification for the final submission

@@
 
-Elementary calculus shows that the necessary condition for maximization is, that $\partial f(I, \mathbf{c})/\partial I - w =0$, which implicitly defines the economically optimal input application rate as a function of prices and soil/field characteristics, and may be arranged as \@ref(eq:eqn2):
+Elementary calculus shows that the necessary condition for maximization is, that $p (\partial f(I, \mathbf{c})/\partial I) - w =0$, which implicitly defines the economically optimal input application rate as a function of prices and soil/field characteristics, and may be arranged as \@ref(eq:eqn2):
 
@@
 (See Figure E.1 in Appendix E for examples of visualizations of predicted and true yields along with RMSE values, by model.) Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN.
-Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact, along with the poor performance of RF in predicting EONR presented in \@ref(tab:table-optN), shows that strong predictive power of yield levels does not imply accurate prediction of EONR.
+Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact, along with the poor performance of RF in predicting EONR presented in Table \@ref(tab:table-optN), shows that strong predictive power of yield levels does not imply accurate prediction of EONR.
 Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well.
@@
 
-```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "The Relationship between yield and EONR Prediction Performances under the aabbyytt scenario"}
+```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "The relationship between yield and EONR prediction performances under the aabbyytt scenario"}
 vis_RMSE_y_eonr
@@
 
-We also showed that the best model in prediction yields is not necessarily the best model in predicting EONRs and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map.
+We also showed that the best model in predicting yields is not necessarily the best model in predicting EONRs and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map.
 Many studies seek to predict yield level accurately using deep learning methods.

### 2022-06-09 Codes/PrepareResults.rmd

@@
   font.family = "Times New Roman"
+  # font.family = "Cambria Math"
 )
@@
   theme_figure
+
+vis_yield_cell <-
+  ggplot(field_cell_sf) +
+  geom_sf(aes(fill = yield), size = 0) +
+  scale_fill_viridis_c() +
+  labs(fill = "Yield level\n  (kg/ha)") +
+  ggtitle("(2) Simulated yield level") +
+  theme_figure
 ```
@@
   theme_figure
+```
+
+```{r}
+
 ```
@@
 # === Summary Table (Training Data sets) === #
+pi_symb <- as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))
+pi_symb[[1]]$font.family <- "Cambria Math"
+
 report_table_optN_train <-
@@
   ) %>%
-  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
+  # compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
+  # font(i = 2, j = c(4, 7, 10, 13), fontname = "Cambria Math", part = "header") %>%
+  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = pi_symb) %>%
   hline_bottom(part = "all") %>%
@@
   align(j = 1, align = "left", part = "all") %>%
-  # autofit() %>%
   # width(j = c(2,5,8,11), width=0.3) %>%
-  # fix_border_issues()
-  footnote(
-    # i = 1, j = c(4, 7, 10, 13), part = "header",
-    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+  # --- footer --- #
+  add_footer_lines(values = "") %>%
+  compose(value = as_paragraph("Note: "), part = "footer") %>%
+  footnote(part = "body", ref_symbols = NA, inline = T, sep = "",
+    value = pi_symb
+  ) %>%
+  footnote(part = "body", ref_symbols = NA, sep = "", inline = T,
+    value = as_paragraph(" indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), ".")
+  ) %>%
+  # footnote(
+  #   value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
 The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
-    ref_symbols = NA
-  ) %>%
+  #   ref_symbols = NA
+  # ) %>%
   fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
@@
 # === Summary Table (Testing Data sets) === #
+pi_symb <- as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))
+pi_symb[[1]]$font.family <- "Cambria Math"
+
 report_table_optN <-
@@
   align(j = 1, align = "left", part = "all") %>%
-  # autofit() %>%
-  # width(j = c(2,5,8,11), width=0.3) %>%
-  # fix_border_issues()
-  footnote(
-    # i = 1, j = c(4, 7, 10, 13), part = "header",
-    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+  # --- footer --- #
+  add_footer_lines(values = "") %>%
+  compose(value = as_paragraph("Note: "), part = "footer") %>%
+  footnote(part = "body", ref_symbols = NA, inline = T, sep = "",
+    value = pi_symb
+  ) %>%
+  footnote(part = "body", ref_symbols = NA, sep = "", inline = T,
+    value = as_paragraph(" indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), ".")
+  ) %>%
+  # footnote(
+  #   # i = 1, j = c(4, 7, 10, 13), part = "header",
+  #   value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
 The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
-    ref_symbols = NA
-  ) %>%
+  #   ref_symbols = NA
+  # ) %>%
   fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
@@
 # === Summary Table (Testing Data sets) === #
+pi_symb <- as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))
+pi_symb[[1]]$font.family <- "Cambria Math"
+
 table_optN_low_high <-
@@
   ) %>%
-  compose(i = 2, j = c(5, 8, 11, 14), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
+  # compose(i = 2, j = c(5, 8, 11, 14), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
+  # font(i = 2, j = c(5, 8, 11, 14), fontname = "Cambria Math", part = "header") %>%
+  compose(i = 2, j = c(5, 8, 11, 14), part = "header", value = pi_symb) %>%
   hline_bottom(part = "all") %>%
@@
   width(j = c(2, 5, 8, 11, 14), width = 0.3) %>%
-  footnote(
-    # i = 1, j = c(4, 7, 10, 13), part = "header",
-    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+  # --- footer --- #
+  add_footer_lines(values = "") %>%
+  compose(value = as_paragraph("Note: "), part = "footer") %>%
+  footnote(part = "body", ref_symbols = NA, inline = T, sep = "",
+    value = pi_symb
+  ) %>%
+  footnote(part = "body", ref_symbols = NA, sep = "", inline = T,
+    value = as_paragraph(" indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), ".")
+  ) %>%
+  # footnote(
+  #   # i = 1, j = c(4, 7, 10, 13), part = "header",
+  #   value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
 The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
-    ref_symbols = NA
-  ) %>%
+  #   ref_symbols = NA
+  # ) %>%
   fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
@@
   width(j = c(3, 6, 9, 12), width = 0.05)
+
+# flextable(head(iris)) %>%
+#   autofit() %>%
+#   add_footer_lines(values = "") %>%
+#   compose(value = as_paragraph("Note: "), part = "footer") %>%
+#   footnote(part = "body", ref_symbols = NA, inline = T, sep = "",
+#     value = pi_symb
+#     ) %>%
+#   footnote(part = "body", ref_symbols = NA, sep = "", inline = T,
+#     value = as_paragraph(" indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level.
+The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), ".")
+#     )
 ```

### 2022-06-09 Writing/CEA_final_submission/CoverLetter.rmd

--- 2022-02-06 Writing/JournalSubmission/CoverLetter.rmd
@@
     global_numbering: true
-    reference_docx: word_template.docx
-    # reference_docx: word_template_format.docx
-    # pandoc_args: ["-Fpandoc-crossref"]
+    reference_docx: ../word_template.docx
 ---

### 2022-06-09 Writing/CEA_final_submission/Highlights.rmd

--- 2022-02-06 Writing/CEA_submission/Highlights.rmd
@@
     global_numbering: true
-    reference_docx: word_template.docx
-    # reference_docx: word_template_format.docx
-    # pandoc_args: ["-Fpandoc-crossref"]
-bibliography: ML_VRA.bib
-csl: computers-and-electronics-in-agriculture.csl
-eqnPrefix: 
-      - "Eq"
+    reference_docx: ../word_template.docx
 ---

### 2022-06-09 Writing/appendix.rmd

@@
 ## Appendix A: Causal Tree Example {-}
-Figure A.1 shows an example of a CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$) ($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
+Figure A.1 shows an example of a CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with electrical conductivity ($\textit{ecs}$) ($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment.
 
